### 2019-05-16 README.Rmd
Initial commit

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below. 
Title <- "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
Authors <- "Suparna Chaudhry and Andrew Heiss"
Year <- "2019"
```

# `r Title`

[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of Political Science • Christopher Newport University  
[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University

# Abstract

Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions. While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of laws—many of which appear mundane on their face—represent a bureaucratic form of repressive that could be indicative of more severe human rights abuses and backsliding. This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space. In this paper, we ask: do legal crackdowns on NGOs predict broader civil society repression? We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it. These laws also make it easier for states to prevent and deter future large-scale popular mobilization. Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of attacks on journalists, independent media, academic freedom, and freedoms of expression and association. This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deteriorations in space for civil society.

---

This repository contains the data and code for our paper:

> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`.

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

## How to cite

Please cite this compendium as:

> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`.

### How to download or install

You can either [download the compendium as a ZIP file](/archive/master.zip) or use GitHub to clone or fork the compendium repository (see the green "Clone or download" button at the top of the GitHub page).

In order to reproduce this project, you'll need to install the compendium as an R package. After downloading the compendium, do the following:

### Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))

**Code:** All code is licensed under the [MIT License](LICENSE.md).

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2019-05-16 analysis/01_get-merge-data.Rmd
Initial commit

---
title: "Process and merge data"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

TODO: Get and merge all the data here.

### 2019-05-16 analysis/index.Rmd
Initial commit

--- 2019-05-16 README.Rmd
@@
 ---
-output: github_document
+title: "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
+author: "Suparna Chaudhry and Andrew Heiss"
+date: "Last run: `r format(Sys.time(), '%F')`"
 ---
 
-<!-- README.md is generated from README.Rmd. Please edit that file -->
-
-```{r, echo = FALSE}
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  fig.path = "README-"
-)
-# Please put your title here to include it in the file below. 
-Title <- "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
-Authors <- "Suparna Chaudhry and Andrew Heiss"
-Year <- "2019"
-```
-
-# `r Title`
-
-[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of Political Science • Christopher Newport University  
-[Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University
-
-# Abstract
+## Abstract
 
@@
 This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deteriorations in space for civil society.
-
----
-
-This repository contains the data and code for our paper:
-
-> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`.
-
-Our pre-print is online here:
-
-> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
-
-## How to cite
-
-Please cite this compendium as:
-
-> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`.
-
-### How to download or install
-
-You can either [download the compendium as a ZIP file](/archive/master.zip) or use GitHub to clone or fork the compendium repository (see the green "Clone or download" button at the top of the GitHub page).
-
-In order to reproduce this project, you'll need to install the compendium as an R package. After downloading the compendium, do the following:
-
-### Licenses
-
-**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/))
-
-**Code:** All code is licensed under the [MIT License](LICENSE.md).
-
-### Contributions
-
-We welcome contributions from everyone.
-Before you get started, please see our [contributor guidelines](CONTRIBUTING.md).
-Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
-By participating in this project you agree to abide by its terms.

### 2019-05-16 R/canaryNGOs-package.R

@@ -1,0 +1,9 @@
+#' The 'canaryNGOs' package.
+#'
+#' @description Research on how restrictions on NGOs foreshadow other forms of
+#'   human rights repression
+#'
+#' @docType package
+#' @name canaryNGOs-package
+#' @aliases canaryNGOs
+NULL

### 2019-05-16 analysis/options.R

@@ -1,0 +1,28 @@
+# Universal pandoc options ------------------------------------------------
+
+panderOptions("table.split.table", Inf)
+panderOptions("table.split.cells", Inf)
+panderOptions("missing", "")
+panderOptions("big.mark", ",")
+panderOptions("digits", 3)
+panderOptions("round", 3)
+panderOptions("table.alignment.default", "left")
+
+
+# Bayes options -----------------------------------------------------------
+
+CHAINS <- 4
+ITER <- 4000
+WARMUP <- 2000
+BAYES_SEED <- 1234
+options(mc.cores = parallel::detectCores())
+
+
+# Ordered factor modeling setup -------------------------------------------
+
+# By default, R uses polynomial contrasts for ordered factors in linear models
+# options("contrasts") 
+# So make ordered factors use treatment contrasts instead
+options(contrasts = rep("contr.treatment", 2))
+# Or do it on a single variable:
+# contrasts(df$x) <- "contr.treatment"

### 2019-05-16 manuscript/pandoc/bin/word_count.R

@@ -1,0 +1,41 @@
+suppressPackageStartupMessages(library(tidyverse))
+suppressPackageStartupMessages(library(rvest))
+suppressPackageStartupMessages(library(here))
+suppressPackageStartupMessages(library(stringi))
+
+ms_raw <- read_html(here("manuscript", "manuscript.html"))
+
+# Extract just the article, ignoring title, abstract, etc.
+ms <- ms_raw %>% 
+  html_nodes("article") 
+
+# Get rid of figures, tables, and math
+xml_remove(ms %>% html_nodes("figure"))
+xml_remove(ms %>% html_nodes("table"))
+xml_remove(ms %>% html_nodes(".display"))  # Block math
+xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>% 
+  invisible()
+
+# Go through each child element in the article and extract it
+ms_cleaned_list <- map(html_children(ms), ~ {
+  .x %>% 
+    html_text(trim = TRUE) %>% 
+    # ICU counts hyphenated words as multiple words, so replace - with DASH
+    str_replace_all("\\-", "DASH") %>% 
+    # ICU also counts / as multiple words, so URLs go crazy. Replace / with SLASH
+    str_replace_all("\\/", "SLASH") %>% 
+    # ICU *also* counts [things] in bracketss multiple times, so kill those too
+    str_replace_all("\\[|\\]", "") %>% 
+    # Other things to ignore
+    str_replace_all("×", "")
+  })
+
+# Get count of words! (close enough to Word)
+cat(scales::comma(sum(stri_count_words(ms_cleaned_list))), "words in manuscript\n")
+
+# Word counts in each paragraph
+# stri_count_words(ms_cleaned_list)
+
+# Export intermediate Word file for comparison
+# paste(ms_cleaned_list, collapse = "\n\n") %>%
+#   pander::Pandoc.convert(text = ., format = "docx")

### 2020-03-07 R/graphics.R
Add graphics functions

@@ -1,0 +1,70 @@
+# ggplot themes -----------------------------------------------------------
+
+#' theme_ngo
+#'
+#' A custom ggplot2 theme used throughout this project
+#'
+#' @param base_size base font size (default is 9)
+#' @param base_family base font family (default is Roboto Condensed)
+#'
+#' @export
+#'
+#' @examples
+#' library(ggplot2)
+#'
+#' ggplot(mtcars, aes(x = mpg, y = wt)) +
+#'   geom_point() +
+#'   theme_ngo()
+theme_ngo <- function(base_size = 9, base_family = "Inter Light") {
+  ret <- theme_bw(base_size, base_family) +
+    theme(plot.title = element_text(size = rel(1.4), face = "bold",
+                                    family = "Inter"),
+          plot.subtitle = element_text(size = rel(1), face = "plain",
+                                       family = "Inter Medium"),
+          plot.caption = element_text(size = rel(0.8), color = "grey50", face = "plain",
+                                      family = "Inter Light",
+                                      margin = margin(t = 10)),
+          panel.border = element_rect(color = "grey50", fill = NA, size = 0.15),
+          panel.spacing = unit(1, "lines"),
+          panel.grid = element_line(size = 0.30),
+          panel.grid.minor = element_blank(),
+          strip.text = element_text(size = rel(0.9), hjust = 0,
+                                    family = "Inter", face = "bold"),
+          strip.background = element_rect(fill = "grey85", colour = NA),
+          axis.ticks = element_blank(),
+          axis.title.x = element_text(margin = margin(t = 10)),
+          axis.title.y = element_text(margin = margin(r = 10)),
+          axis.text = element_text(family = "Inter Light", face = "plain"),
+          axis.title = element_text(family = "Inter Medium", face = "plain"),
+          legend.key = element_blank(),
+          legend.text = element_text(size = rel(1), family = "Inter Light", face = "plain"),
+          legend.spacing = unit(0.1, "lines"),
+          legend.box.margin = margin(t = -0.5, unit = "lines"),
+          legend.margin = margin(t = 0),
+          legend.position = "bottom")
+
+  ret
+}
+
+
+# Conversion and formatting help ------------------------------------------
+
+#' Convert mms to pts
+#'
[…]

### 2020-03-08 analysis/01_get-merge-data.Rmd
PHEW import and process and clean all data

@@
 
-TODO: Get and merge all the data here.
+```{r setup, warning=FALSE, message=FALSE}
+knitr::opts_chunk$set(fig.retina = 2,
+                      tidy.opts = list(width.cutoff = 120),  # For code
+                      options(width = 100))  # For output
+
+library(tidyverse)
+library(canaryNGOs)
+library(readxl)
+library(haven)
+library(countrycode)
+library(states)
+library(WDI)
+library(lubridate)
+library(DT)
+library(naniar)
+library(scales)
+library(here)
+
+# The PTS data and journalist data are saved as .RData files, so they load into
+# R with their original object names. This function lets you load an .RData file
+# directly to a new object instead of bringing in the original name. 
+# (via https://stackoverflow.com/a/25455968/120898)
+load_rdata <- function(filename) {
+  load(filename)
+  get(ls()[ls() != "filename"])
+}
+```
+
+# Load raw data
+
+```{r load-raw-data, cache=TRUE, warning=FALSE, message=FALSE}
+# Chaudhry restrictions
+chaudhry_raw <- read_dta(here("data", "raw_data", "Chaudhry restrictions", "SC_Expanded.dta"))
+
+# PTS
+pts_raw <- load_rdata(here("data", "raw_data", "Political Terror Scale", 
+                           "PTS-2019.RData")) %>% as_tibble()
+
+# V-Dem
+vdem_raw <- read_rds(here("data", "raw_data", "Country_Year_V-Dem_Full+others_R_v9", 
+                          "V-Dem-CY-Full+Others-v9.rds")) %>% as_tibble()
+
+# Gohdes Carey journalist killings
+gh_journalists_raw <- load_rdata(here("data", "raw_data", "Gohdes Carey journalists", 
+                                      "journalist-data-incl-pts.RData")) %>% as_tibble()
+
+# gh_analysis_raw <- load_rdata(here("data", "raw_data", "Gohdes Carey journalists", 
+#                                    "analysis-data.RData")) %>% as_tibble()
+
+# World Bank World Development Indicators (WDI)
+# http://data.worldbank.org/data-catalog/world-development-indicators
+wdi_indicators <- c("NY.GDP.PCAP.PP.KD",  # GDP per capita, ppp (constant 2011 international $)
+                    "NY.GDP.MKTP.PP.KD",  # GDP, ppp (constant 2010 international $)
+                    "SP.POP.TOTL")     # Population, total
+
+wdi_raw <- WDI(country = "all", wdi_indicators, extra = TRUE, start = 1990, end = 2018)
+
+# UCDP/PRIO Armed Conflict
+ucdp_prio_raw <- read_csv(here("data", "raw_data", "UCDP PRIO", 
+                               "ucdp-prio-acd-191.csv"))
+```
+
+# Create country-year skeleton
+
+We use [Gleditsch-Ward country codes](http://ksgleditsch.com/data-4.html) to identify each country across the different datasets we merge. We omit microstates.
+
+Importantly, when converting GW codes to COW codes, [following Gleditsch and Ward](https://www.andybeger.com/states/articles/differences-gw-cow.html), we treat post-2006 Serbia as 345 (a continuation of Serbia & Montenegro).
+
+```{r build-skeleton}
+microstates <- gwstates %>% 
+  filter(microstate) %>% distinct(gwcode) %>% pull(gwcode)
+
+# In both COW and GW codes, modern Vietnam is 816, but countrycode() thinks the
+# COW code is 817, which is old South Vietnam (see issue
+# https://github.com/vincentarelbundock/countrycode/issues/16), so we use
+# custom_match to force 816 to recode to 816
+#
+# Also, following Gleditsch and Ward, we treat Serbia after 2006 dissolution of
+# Serbia & Montenegro as 345 in COW codes (see
+# https://www.andybeger.com/states/articles/differences-gw-cow.html)
+#
+# Also, because the World Bank doesn't include it in the WDI, we omit Taiwan
+
+panel_skeleton <- state_panel(1995, 2014, partial = "any") %>% 
+  filter(!(gwcode %in% microstates)) %>% 
+  mutate(year = year(date)) %>% 
+  mutate(cowcode = countrycode(gwcode, origin = "gwn", destination = "cown",
+                               custom_match = c("816" = 816L, "340" = 345L)),
+         country = countrycode(cowcode, origin = "cown", destination = "country.name"),
+         iso2 = countrycode(cowcode, origin = "cown", destination = "iso2c",
+                            custom_match = c("345" = "RS", "347" = "XK", "678" = "YE")),
+         iso3 = countrycode(cowcode, origin = "cown", destination = "iso3c",
+                            custom_match = c("345" = "SRB", "347" = "XKK", "678" = "YEM"))) %>% 
+  # There are two entries for "Yugoslavia" in 2006 after recoding 340 as 345;
+  # get rid of one
+  filter(!(gwcode == 340 & cowcode == 345 & year == 2006)) %>% 
+  # Remove Taiwan
+  filter(gwcode != 713) %>% 
+  # Remove the Bahamas, Belize, and Brunei
+  filter(!(gwcode %in% c(31, 80, 835))) %>% 
+  # Make Serbia 345 in GW codes too, for joining with other datasets
+  mutate(gwcode = recode(gwcode, `340` = 345L)) %>% 
+  select(-date)
+```
+
+Here's a lookup table of all the codes:
+
+```{r show-gw-codes}
+panel_skeleton %>% group_by(gwcode) %>% slice(1) %>% 
+  arrange(country) %>% select(-year) %>% datatable()
+```
+
+# Chaudhry NGO restrictions
+
+We create several indexes for each of the categories of regulation, following Christensen and Weinstein’s classification:
+
+- `entry` (Q2b, Q2c, Q2d; 3 points maximum, actual max = 3 points maximum): barriers to entry
+  - Q2c is reversed, so not being allowed to appeal registration status earns 1 point.
+  - Q2a is omitted because it’s benign
+- `funding` (Q3b, Q3c, Q3d, Q3e, Q3f; 5 points maximum, actual max = 4.5): barriers to funding
+  - Q3a is omitted because it’s benign
+  - Scores that range between 0–2 are rescaled to 0–1 (so 1 becomes 0.5)
+- `advocacy` (Q4a, Q4c; 2 points maximum, actual max = 2): barriers to advocacy
+  - Q4b is omitted because it’s not a law
+  - Scores that range between 0–2 are rescaled to 0–1 (so 1 becomes 0.5)
+- `barriers_total` (10 points maximum, actual max = 8.5): sum of all three indexes
+
+These indexes are also standardized by dividing by the maximum, yielding the following variables:
+
+- `entry_std`: 1 point maximum, actual max = 1
+- `funding_std`: 1 point maximum, actual max = 1
+- `advocacy_std`: 1 point maximum, actual max = 1
+- `barriers_total_std`: 3 points maximum, actual max = 2.5
+
+```{r clean-chaudhry-ngos}
+regulation_categories <- tribble(
+  ~question, ~category,
+  "q2a", "omit",
+  "q2b", "entry",
+  "q2c", "entry",
+  "q2d", "entry",
+  "q3a", "omit",
+  "q3b", "funding",
+  "q3c", "funding", 
+  "q3d", "funding",
+  "q3e", "funding",
+  "q3f", "funding",
+  "q4a", "advocacy",
+  "q4c", "advocacy"
+)
+
+# In this data Sudan (625) splits into North Sudan (626) and South Sudan (525)
+# in 2011, but in the other datasets regular Sudan stays 625 and South Sudan
+# becomes 626, so adjust the numbers here
+chaudhry_raw_fixed_sudan <- chaudhry_raw %>% 
+  mutate(ccode = case_when(
+    scode == "SSU" ~ 626,
+    scode == "SDN" ~ 625,
+    TRUE ~ ccode
+  ))
+
+chaudhry_2014 <- expand_grid(ccode = unique(chaudhry_raw_fixed_sudan$ccode), 
+                             year = 2014)
+
+chaudhry_summed <- chaudhry_raw_fixed_sudan %>% 
+  # Bring in 2014 rows
+  bind_rows(chaudhry_2014) %>% 
+  arrange(ccode, year) %>% 
+  # Reverse values for q2c
+  mutate(q2c = 1 - q2c) %>% 
+  # Rescale 2-point questions to 0-1 scale
+  mutate_at(vars(q3e, q3f, q4a), ~rescale(., to = c(0, 1), from = c(0, 2))) %>% 
+  # q2d and q4c use -1 to indicate less restriction/burdensomeness. Since we're
+  # concerned with an index of restriction, we make the negative values zero
+  mutate_at(vars(q2d, q4c), ~ifelse(. == -1, 0, .)) %>% 
+  pivot_longer(cols = starts_with("q"), names_to = "question") %>% 
+  left_join(regulation_categories, by = "question") %>% 
+  filter(category != "omit") %>% 
+  group_by(ccode) %>%
+  mutate(all_missing = all(is.na(value))) %>%
+  group_by(ccode, question) %>% 
+  # Bring most recent legislation forward in time
+  fill(value) %>% 
+  # For older NA legislation that can't be brought forward, set sensible
+  # defaults. Leave countries that are 100% 0 as NA.
+  mutate(value = ifelse(!all_missing & is.na(value), 0, value)) %>% 
+  group_by(ccode, year, category) %>% 
+  summarize(total = sum(value)) %>% 
+  ungroup()
+
+chaudhry_clean <- chaudhry_summed %>% 
+  pivot_wider(names_from = category, values_from = total) %>% 
+  mutate_at(vars(entry, funding, advocacy), 
+            list(std = ~. / max(., na.rm = TRUE))) %>% 
+  mutate(barriers_total = advocacy + entry + funding,
+         barriers_total_std = advocacy_std + entry_std + funding_std) %>% 
+  mutate(gwcode = countrycode(ccode, origin = "cown", destination = "gwn",
+                              custom_match = c("679" = 678L, "818" = 816L,
+                                               "342" = 345L, "341" = 347L,
+                                               "348" = 341L))) %>% 
+  select(gwcode, everything(), -ccode)
+
+glimpse(chaudhry_clean)
+```
+
+# Political Terror Scale (PTS)
+
+We use data from the [Political Terror Scale (PTS) project](http://www.politicalterrorscale.org/) to measure state repression.
+This project uses reports from the US State Department, Amnesty International, and Human Rights Watch and codes political repression on a scale of 1-5:
+
+- **Level 1**: Countries under a secure rule of law, people are not imprisoned for their view, and torture is rare or exceptional. Political murders are extremely rare.
+- **Level 2**: There is a limited amount of imprisonment for nonviolent political activity. However, few persons are affected, torture and beatings are exceptional. Political murder is rare.
+- **Level 3**: There is extensive political imprisonment, or a recent history of such imprisonment.
+Execution or other political murders and brutality may be common.
+Unlimited detention, with or without a trial, for political views is accepted.
+- **Level 4**: Civil and political rights violations have expanded to large numbers of the population.
+Murders, disappearances, and torture are a common part of life.
+In spite of its generality, on this level terror affects primarily those who interest themselves in politics or ideas.
+- **Level 5**: The terrors of Level 4 have been extended to the whole population.
+The leaders of these societies place no limits on the means or thoroughness with which they pursue personal or ideological goals.
+
+Following Gohdes and Carey, we use the State Department score, unless it's missing, in which case we use Amnesty's score.
+
+```{r clean-pts}
+# 260: West Germany
+# 678/680: North/South Yemen. COW uses 679 for modern Yemen; GW uses 678
+# 946: Kiribati
+# 947: Tuvalu
+# 955: Tonga
+
+pts_clean <- pts_raw %>% 
+  filter(!(COW_Code_N %in% c(microstates, 260, 678, 680, 946, 947, 955))) %>% 
+  # Get rid of Soviet-era Yugoslavia, combine Yugoslavia/Serbia and Montenegro
+  # (1991-2006) with Serbia (2007-2018)
+  filter(Country_OLD != "Yugoslavia", 
+         !(Country_OLD == "Serbia" & Year <= 2006),
+         !(Country_OLD == "Yugoslavia/Serbia and Montenegro" & Year >= 2007)) %>% 
+  mutate(COW_Code_N = ifelse(Country_OLD == "Serbia", 345, COW_Code_N)) %>% 
+  # Use the State Department score unless it's missing, then use Amnesty's
+  mutate(PTS = coalesce(PTS_S, PTS_A)) %>% 
+  mutate(gwcode = countrycode(COW_Code_N, origin = "cown", destination = "gwn",
+                              custom_match = c("679" = 678L, "816" = 816L))) %>% 
+  select(year = Year, gwcode, PTS) %>%
+  mutate(PTS_factor = factor(PTS, levels = 1:5, labels = paste0("Level ", 1:5)))
+
+glimpse(pts_clean)
+```
+
+# Gohdes and Carey journalist deaths
+
+We use data from [Gohdes and Carey (2017)](https://doi.org/10.1177/0022343316680859) for the number of journalists murdered between 2002 and 2014.
+They provide two `.Rdata` files in their replication materials—one is a list of all journalist deaths, and one is a TSCS dataset they use in their main analysis, with summary values of journalist deaths for each country/year.
+Their panel data does not include 2002 for some reason, so we ignore the panel data and recreate the summary values by hand here.
+
+```{r clean-gh-journalists}
+gh_journalists <- gh_journalists_raw %>% 
+  select(year = Year, gwno, country = Country, in_rog, in_cpj, in_ipi, date = Date,
+         perpetrator = Perpetrator, foreigner = Foreigner, perp_cat = perp.cat, pts,
+         intra, inter, international, minor, major, armedconf)
+
+# Count of perpetrators
+killings_perp <- gh_journalists %>% 
+  mutate(perp_cat = recode(perp_cat, "non-state" = "polgroup")) %>% 
+  group_by(year, gwno, perp_cat) %>% 
+  summarize(n = n()) %>% 
+  pivot_wider(names_from = perp_cat, values_from = n)
+
+# Count of foreign vs. local journalist
+killings_foreigner <- gh_journalists %>% 
+  mutate(foreigner = recode(foreigner, "no" = "local", "yes" = "foreign")) %>% 
+  group_by(year, gwno, foreigner) %>% 
+  summarize(n = n()) %>% 
+  pivot_wider(names_from = foreigner, values_from = n)
+
+# Combine everything
+killings_all <- gh_journalists %>% 
+  group_by(year, gwno) %>% 
+  summarize(alljourn = n()) %>% 
+  left_join(killings_perp, by = c("year", "gwno")) %>% 
+  left_join(killings_foreigner, by = c("year", "gwno")) %>% 
+  mutate_at(vars(-year, -gwno), ~coalesce(., 0L)) %>%  # Replace all NAs with 0
+  mutate(stateunknown = state + unknown) %>% 
+  rename_at(vars(-year, -gwno), ~paste0("gh_", .)) %>% 
+  rename(gwcode = gwno)
+
+glimpse(killings_all)
+```
+
+# Varieties of Democracy (V-Dem)
+
+We use a bunch of variables from the [Varieties of Democracy project](https://www.v-dem.net/en/):
+
+- Freedom of expression and alternative sources of information index: `v2x_freexp_altinf`
+- Freedom of academic and cultural expression: `v2clacfree`
+- CSO consultation: `v2cscnsult`
+- CSO participatory environment: `v2csprtcpt`
+- CSO repression: `v2csreprss`
+- Core civil society index: `v2xcs_ccsi` (`v2cseeorgs` + `v2csreprss` + `v2csprtcpt`)
+- Religious organization repression: `v2csrlgrep`
+- Govt censorship effort - media: `v2mecenefm`
+- Internet censorship effort: `v2mecenefi`
+- Harassment of journalists: `v2meharjrn`
+- Media self-censorship: `v2meslfcen`
+- Physical violence index: `v2x_clphy`
+- Political civil liberties index: `v2x_clpol`
+- Private civil liberties index: `v2x_clpriv`
+- Freedom of expression index: `v2x_freexp`
+- Polity: `e_polity2`
+- Electoral democracy index: `v2x_polyarchy`
+- Population: `e_wb_pop`
+- GDP: `e_migdppc` and `e_migdppcln (logged)`
+
+```{r clean-vdem}
+# 403: Sao Tome and Principe
+# 591: Seychelles
+# 679: Yemen (change to 678 for GW)
+# 935: Vanuatu
+
+vdem_clean <- vdem_raw %>% 
+  filter(year >= 1995) %>% 
+  select(country_name, year, cowcode = COWcode, 
+         e_migdppc,  # Maddison Project Database GDP/capita
+         # Civil society stuff
+         v2xcs_ccsi, v2cscnsult, v2csprtcpt, v2csreprss,
+         # Freedom of expression stuff
+         v2x_freexp, v2x_freexp_altinf, v2clacfree, v2meslfcen,
+         # Repression stuff
+         v2csrlgrep, v2mecenefm, v2mecenefi, v2meharjrn, v2x_clphy,
+         # Rights indexes
+         v2x_clpol, v2x_clpriv, 
+         # Democracy
+         e_polity2, v2x_polyarchy) %>% 
+  mutate(gwcode = countrycode(cowcode, origin = "cown", destination = "gwn",
+                              custom_match = c("403" = 403L, "591" = 591L,
+                                               "679" = 678L, "935" = 935L, 
+                                               "816" = 816L))) %>% 
+  select(-country_name, -cowcode)
+
+glimpse(vdem_clean)
+```
+
+# World Bank development indicators
+
+We use data from the [World Bank](http://data.worldbank.org/) for general demographic data: population and GDP.
+
+```{r clean-wdi}
+wdi_clean <- wdi_raw %>%
+  filter(iso2c %in% unique(panel_skeleton$iso2)) %>%
+  mutate_at(vars(income, region), as.character) %>%  # Don't use factors
+  rename(gdpcap = NY.GDP.PCAP.PP.KD, gdp = NY.GDP.MKTP.PP.KD, population = SP.POP.TOTL) %>%
+  mutate(gwcode = countrycode(iso2c, origin = "iso2c", destination = "gwn",
+                              custom_match = c("YE" = 678L, "XK" = 347L, 
+                                               "VN" = 816L, "RS" = 345L))) %>% 
+  mutate(region = ifelse(gwcode == 343, "Europe & Central Asia", region),
+         income = ifelse(gwcode == 343, "Upper middle income", income)) %>% 
+  select(gwcode, year, region, income, wb_gdpcap = gdpcap, starts_with("pop"))
+
+glimpse(wdi_clean)
+```
+
+# UCDP/PRIO Armed Conflict
+
+Following [Gohdes and Carey (2017)](https://doi.org/10.1177/0022343316680859), we use [UCDP/PRIO Armed Conflict data](https://ucdp.uu.se/downloads/index.html#armedconflict) to create an indicator marking if a country-year was involved in armed conflict that resulted in at least 25 battle-related deaths.
+
+```{r clean-ucdp-prio}
+ucdp_prio_clean <- ucdp_prio_raw %>% 
+  mutate(gwcode_raw = str_split(gwno_a, pattern = ", ")) %>% 
+  unnest(gwcode_raw) %>% 
+  mutate(gwcode = as.integer(gwcode_raw)) %>% 
+  group_by(gwcode, year) %>% 
+  summarize(armed_conflict = sum(intensity_level) > 0)
+
+glimpse(ucdp_prio_clean)
+```
+
+# Final clean combined data
+
+Finally, we join everything together and save the final clean data in `data/derived_data/`.
+
+Most countries have GDP per capita data from the World Bank (2011 international dollars, PPP: `NY.GDP.PCAP.PP.KD`), except four:
+
+- Cuba (40)
+- Djibouti (522)
+- Syria (652)
+- North Korea (731)
+
+We fill these gaps with data from the [Maddison Project Database](https://www.rug.nl/ggdc/historicaldevelopment/maddison/releases/maddison-project-database-2018), which has data for these countries (also 2011 dollars, PPP, but with slight discrepancies from the World Bank).
+The MPD doesn't include data for all countries, though, and the World Bank seems to have more complete data than the MPD, so we prefer the World Bank over MPD.
+In cases where data is missing for the whole country, like Cuba, Djibouti, Syria, and North Korea, we use MPD.
+
+Somalia has no GDP/capita data in either MPD or the World Bank; Eritrea is missing GDP/capita data for 2012-2014; Afghanistan is missing 2000-2001.
+
+Also, for whatever reason, V-Dem doesn't include any data for the Bahamas (31), Belize (80), and Brunei (835), so we exclude them.
+
+```{r combine-lag-everything}
+panel_done <- panel_skeleton %>% 
+  left_join(wdi_clean, by = c("gwcode", "year")) %>% 
+  left_join(chaudhry_clean, by = c("gwcode", "year")) %>% 
+  left_join(pts_clean, by = c("gwcode", "year")) %>%
+  left_join(killings_all, by = c("gwcode", "year")) %>% 
+  mutate_at(vars(starts_with("gh")), ~coalesce(., 0L)) %>% 
+  left_join(vdem_clean, by = c("gwcode", "year")) %>% 
+  left_join(ucdp_prio_clean, by = c("gwcode", "year")) %>% 
+  mutate(armed_conflict = coalesce(armed_conflict, FALSE),
+         armed_conflict_num = as.numeric(armed_conflict)) %>% 
+  # Use MPD GDP/capita if needed, otherwise use the World Bank's
+  mutate(gdpcap = ifelse(gwcode %in% c(40, 522, 652, 731), e_migdppc, wb_gdpcap),
+         gdpcap_log = log(gdpcap), population_log = log(population)) %>% 
+  # Get rid of other GDP/capitas
+  select(-e_migdppc, -wb_gdpcap)
+
+testthat::expect_equal(nrow(panel_skeleton), 
+                       nrow(panel_done))
+
+panel_done_trimmed <- panel_done %>% 
+  filter(year >= 2000)
+
+panel_done_lagged <- panel_done %>% 
+  group_by(gwcode) %>% 
+  # Lag all the time-varying variables
+  mutate_at(vars(starts_with("advocacy"), starts_with("entry"), 
+                 starts_with("funding"), starts_with("barriers"), 
+                 starts_with("population"), starts_with("PTS"), 
+                 starts_with("gh"), starts_with("v2"), e_polity2, 
+                 starts_with("armed_"), starts_with("gdp")),
+            list(lag1 = ~lag(., 1), lag2 = ~lag(., 2), lag3 = ~lag(., 3),
+                 lag4 = ~lag(., 4), lag5 = ~lag(., 5))) %>% 
+  # Lead PTS in case we want to use PTS_lead1 instead of IVs_lag1
+  mutate_at(vars(PTS, PTS_factor), 
+            list(lead1 = ~lead(., 1), lead2 = ~lead(., 2), lead3 = ~lead(., 3),
+                 lead4 = ~lead(., 4), lead5 = ~lead(., 5))) %>% 
+  ungroup() %>% 
+  # Lop off earlier years now that everything is time shifted
+  filter(year >= 2000)
+
+testthat::expect_equal(nrow(filter(panel_skeleton, year >= 2000)), 
+                       nrow(panel_done_lagged))
+```
+
+```{r}
+glimpse(panel_done_trimmed)
+```
+
+Because lagging and leading inflates the number of columns in the data, here's what the lagged/leaded data looks like with just PTS
+
+```{r show-lagged}
+panel_done_lagged %>% 
+  select(gwcode, year, country, starts_with("PTS_factor")) %>% 
+  glimpse()
+```
+
+```{r save-everything}
+write_rds(panel_done_trimmed, here("data", "derived_data", "canary_clean.rds"), 
+          compress = "gz")
+write_csv(panel_done_trimmed, here("data", "derived_data", "canary_clean.csv"))
+
+write_rds(panel_done_lagged, here("data", "derived_data", "canary_clean_lagged.rds"), 
+          compress = "gz")
+write_csv(panel_done_lagged, here("data", "derived_data", "canary_clean_lagged.csv"))
+```
+
+# Basic data details
+
+Number of countries and years:
+
+```{r show-country-years-summary, results="asis"}
+panel_done_trimmed %>% 
+  summarize(num_countries = length(unique(gwcode)),
+            num_years = length(unique(year)),
+            first_year = min(year),
+            last_year = max(year)) %>% 
+  pander::pandoc.table()
+```
+
+Countries across years:
+
+```{r show-country-year-count, results="asis"}
+panel_done_trimmed %>% 
+  count(year, name = "n_countries") %>% 
+  pander::pandoc.table()
+```
+
+# Check missing data
+
+```{r include=FALSE}
+no_ngo_data <- panel_done_trimmed %>% 
+  group_by(gwcode) %>% 
+  mutate(all_ngo_missing = all(is.na(barriers_total))) %>% 
+  filter(all_ngo_missing) %>% 
+  ungroup() %>% 
+  count(gwcode) %>% nrow()
+```
+
+There are `r no_ngo_data` countries without any NGO restriction data.
+The only other variable that has any substantial missingness is Polity IV, but we don't use it in our analysis (we use V-Dem's polyarchy index instead).
+We keep Polity in our data just for reference and comparison with the polyarchy index.
+
+```{r}
+vis_miss(panel_done_trimmed) +
+  theme_ngo() +
+  theme(axis.text.x = element_text(hjust = 0, angle = 45))
+```
+
+Here we see again that the NGO restrictions data is the most mossing, followed by Polity. The others are randomish blips of missing GDP, PTS, internet censorship, and population.
+
+```{r}
+gg_miss_var(panel_done_trimmed) +
+  theme_ngo()
+```

### 2020-03-08 analysis/02_descriptive-analysis.Rmd
Finally commit descriptive stuff

---
title: "Descriptive analysis"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
params:
  fig_width: 6
  fig_height: 3.6
  fig_height_taller: 5
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(canaryNGOs)
library(brms)
library(broom)
library(tidybayes)
library(sf)
library(scico)
library(scales)
library(patchwork)
library(ggtext)
library(here)

CHAINS <- 4
ITER <- 2000
WARMUP <- 1000
BAYES_SEED <- 1234
options(mc.cores = parallel::detectCores())  # Use all cores

canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))

# https://www.naturalearthdata.com/downloads/110m-cultural-vectors/
country_borders <- read_sf(here("data", "raw_data", "Natural Earth", 
                                "ne_110m_admin_0_countries", 
                                "ne_110m_admin_0_countries.shp"))
```

# Civil society restrictions over time

```{r make-map-data}
things_to_map <- canary %>% 
  filter(year %in% c(2000, 2014)) %>% 
  select(country, year, iso3, barriers_total, PTS_factor, v2csreprss) %>% 
  pivot_wider(names_from = year, values_from = c(barriers_total, PTS_factor, v2csreprss)) %>% 
  mutate(new_laws = barriers_total_2014 - barriers_total_2000,
         new_laws = ifelse(new_laws <= 0, 0, new_laws),
         new_laws = ceiling(new_laws)) %>% 
  mutate(diff_csrepress = v2csreprss_2014 - v2csreprss_2000,
         diff_csrepress_trunc = case_when(
           diff_csrepress >= 2 ~ 2,
           diff_csrepress <= -2 ~ -2,
           TRUE ~ diff_csrepress
         )) %>% 
  mutate(pct_change_csrepress = diff_csrepress / v2csreprss_2000,
         pct_change_csrepress_trunc = case_when(
           pct_change_csrepress >= 5 ~ 5,
           pct_change_csrepress <= -5 ~ -5,
           TRUE ~ pct_change_csrepress
         ))

map_data <- country_borders %>% 
  left_join(things_to_map, by = c("ADM0_A3_IS" = "iso3")) %>% 
  filter(ISO_A3 != "ATA")
```

## Legislation

```{r map-ngo-laws, fig.width=params$fig_width, fig.height=params$fig_height_taller}
map_ngo_laws <- ggplot() +
  geom_sf(data = map_data, aes(fill = factor(new_laws)),
          color = "black", size = 0.1) +
  coord_sf(crs = 54030, datum = NA, expand = FALSE) + 
  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 7)), 
                    na.value = "grey80", breaks = 0:6) +
  # scale_fill_manual(values = scico(7, palette = "devon", direction = -1), 
  #                   na.value = "grey80", breaks = 0:6) +
  guides(fill = guide_legend(nrow = 1, label.position = "bottom",
                             keywidth = unit(1, units = "lines"),
                             keyheight = unit(0.6, units = "lines"))) +
  labs(fill = "Restrictive NGO laws passed between 2000 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.spacing.x = unit(0, "pt"),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(10, "lines"),
                                              padding = margin(r = 10)))
map_ngo_laws
```

## Civil society repression

```{r map-cs-repression, fig.width=params$fig_width, fig.height=params$fig_height_taller}
map_cs_repression <- ggplot() +
  geom_sf(data = map_data, aes(fill = diff_csrepress_trunc),
          color = "black", size = 0.1) +
  coord_sf(crs = 54030, datum = NA, expand = FALSE) + 
  scale_fill_scico(palette = "vik", direction = -1,
                   limits = c(-1, 1) * max(abs(map_data$diff_csrepress_trunc), na.rm = TRUE),
                   breaks = seq(-4, 4, 1), na.value = "grey80") +
  guides(fill = guide_colorbar(reverse = TRUE, ticks = FALSE,
                               barwidth = unit(7, units = "lines"),
                               barheight = unit(0.5, units = "lines"))) +
  labs(fill = "Change in V-Dem civil society repression between 2000 and 2014") +
  theme_ngo() +
  theme(panel.border = element_blank(),
        legend.box.margin = margin(t = 5),
        legend.title = element_textbox_simple(halign = 1,
                                              lineheight = 1.3,
                                              minwidth = unit(2, "lines"),
                                              maxwidth = unit(12, "lines"),
                                              padding = margin(r = 10)))
map_cs_repression
```

# PTS and civil society restrictions

## V-Dem civil society repression and the PTS

```{r model-pts-cs, cache=TRUE, message=FALSE, results="hide"}
diff_cs_pts <- brm(
  bf(v2csreprss ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = filter(canary, year == 2010) %>% select(v2csreprss, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_pts")
)
```

```{r draws-pts-cs}
diff_cs_pts_summary <- diff_cs_pts %>%
  gather_draws(`b_PTS.*`, regex = TRUE) %>% 
  median_hdci(.width = 0.95) %>% 
  to_broom_names()

diff_cs_pts_draws <- diff_cs_pts %>% 
  gather_draws(`b_PTS.*`, regex = TRUE) %>% 
  ungroup() %>% 
  mutate(.variable = str_replace(.variable, "b_PTS_factorLevel", "Level ")) %>% 
  mutate(pts_level = fct_rev(.variable))

diff_cs_pts_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(PTS_factor) %>% 
  add_fitted_draws(diff_cs_pts, seed = BAYES_SEED)
```

```{r plot-draws-pts-cs, fig.width=params$fig_width, fig.height=params$fig_height}
ggplot(diff_cs_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
  geom_halfeyeh() +
  scale_x_reverse() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)") +
  theme_ngo()
```

```{r plot-posterior-preds-pts-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_cs_pts_posterior, aes(x = .value, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()

# ggsave("~/Desktop/plot1.pdf", device = cairo_pdf, width = 5, height = 3, units = "in")
# ggsave("~/Desktop/plot1.png", type = "cairo", dpi = 300, width = 6, height = 3.6, units = "in")
```

## Chaudhry NGO regulations and V-Dem's `v2csreprss`

```{r vdem-suparna-plot, warning=FALSE, message=FALSE, fig.width=params$fig_width, fig.height=params$fig_height_taller}
canary_barriers <- canary %>% 
  pivot_longer(cols = c(advocacy, entry, funding, barriers_total), 
               names_to = "barrier", values_to = "count") %>% 
  mutate(barrier = recode(barrier, advocacy = "Barriers to advocacy",
                          entry = "Barriers to entry", 
                          funding = "Barriers to funding",
                          barriers_total = "Total NGO barriers"))

ggplot(canary_barriers, aes(x = count, y = v2csreprss)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm") +
  labs(x = "Number of restrictive NGO laws", 
       y = "V-Dem's civil society repression score") +
  facet_wrap(vars(barrier), scales = "free_x") +
  theme_ngo()
```

## Chaudhry NGO regulations and the PTS

```{r model-pts-restrictions, cache=TRUE, message=FALSE, results="hide"}
diff_ngo_pts <- brm(
  bf(barriers_total ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
  family = student,
  data = select(canary, barriers_total, PTS_factor),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_ngo_pts")
)
```

```{r draws-pts-ngo}
diff_ngo_pts_summary <- diff_ngo_pts %>%
  gather_draws(`b_PTS.*`, regex = TRUE) %>% 
  median_hdci(.width = 0.95) %>% 
  to_broom_names()

diff_ngo_pts_draws <- diff_ngo_pts %>% 
  gather_draws(`b_PTS.*`, regex = TRUE) %>% 
  ungroup() %>% 
  mutate(.variable = str_replace(.variable, "b_PTS_factorLevel", "Level ")) %>% 
  mutate(pts_level = fct_rev(.variable))

diff_ngo_pts_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(PTS_factor) %>% 
  add_fitted_draws(diff_ngo_pts, seed = BAYES_SEED)
```

```{r plot-draws-pts-ngo, fig.width=params$fig_width, fig.height=params$fig_height}
ggplot(diff_ngo_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
  geom_halfeyeh() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)") +
  theme_ngo()
```

```{r plot-posterior-preds-pts-ngo, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_ngo_pts_posterior, aes(x = .value, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

# Conflict and civil society restrictions

```{r model-conflict-cs, cache=TRUE, message=FALSE, results="hide"}
diff_cs_conflict <- brm(
  bf(v2csreprss ~ 0 + armed_conflict, sigma ~ 0 + armed_conflict),
  family = student,
  data = select(canary, v2csreprss, armed_conflict),
  prior = c(
    # Set group mean prior
    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
    # Set group variance priors. We keep the less informative cauchy(0, 1).
    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
    set_prior("exponential(1.0/29)", class = "nu")
  ),
  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
  file = here("analysis", "cache", "diff_cs_conflict")
)
```

```{r draws-conflict-cs}
diff_cs_conflict_summary <- diff_cs_conflict %>%
  gather_draws(`b_armed.*`, regex = TRUE) %>% 
  median_hdci(.width = 0.95) %>% 
  to_broom_names()

diff_cs_conflict_draws <- diff_cs_conflict %>% 
  gather_draws(`b_armed.*`, regex = TRUE) %>% 
  ungroup() %>% 
  mutate(.variable = recode(.variable, `b_armed_conflictFALSE` = "No armed conflict",
                            `b_armed_conflictTRUE` = "Armed conflict"))

diff_cs_conflict_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(armed_conflict) %>% 
  add_fitted_draws(diff_cs_conflict, seed = BAYES_SEED) %>% 
  ungroup() %>% 
  mutate(armed_conflict = factor(armed_conflict, labels = c("No armed conflict", "Armed conflict")))
```

```{r plot-draws-conflict-cs, fig.width=params$fig_width, fig.height=params$fig_height}
ggplot(diff_cs_conflict_draws, aes(y = .variable, x = .value, fill = .variable)) + 
  geom_halfeyeh() +
  scale_x_reverse() +
  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict") +
  theme_ngo()
```

```{r plot-posterior-preds-conflict-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_cs_conflict_posterior, aes(x = .value, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()

# ggsave("~/Desktop/plot1.pdf", device = cairo_pdf, width = 5, height = 3, units = "in")
# ggsave("~/Desktop/plot1.png", type = "cairo", dpi = 300, width = 6, height = 3.6, units = "in")
```

# Civil society restrictions and other kinds of repression

```{r repression-matrix, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
library(GGally)
repression_only <- canary %>% 
  filter(year == 2014) %>% 
  select(barriers_total, PTS, gh_alljourn, 
         v2clacfree, v2csrlgrep, v2mecenefm, v2mecenefi, v2meharjrn, v2meslfcen,
         v2x_clphy, v2x_clpol, v2x_clpriv, v2x_freexp, v2csreprss)

ggscatmat(repression_only, alpha = 0.4) + 
  theme_ngo(base_size = 6)
```

### 2020-03-08 analysis/03_models.Rmd
Add TODOs for models and predictions

---
title: "Models"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)

canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))
```

TODO:

- Causal model
- Run actual models
- Show marginal effects - change in predicted probability of PTS levels as CS restriction changes
- Use matching (https://cran.r-project.org/web/packages/PanelMatch/vignettes/using_panelmatch.html), IPW (BlackwellGlynn:2018) to isolate effect
- Careful selection of confounders, following BellemareMasakiPepinsky:2017 and Samii:2016
- Use MSMs or whatever BlackwellGlynn:2018 suggest?

### 2020-03-08 analysis/04_predictions.Rmd
Add TODOs for models and predictions

---
title: "Predictions"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)

canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))
```

TODO:

- Split into training/test data
- Generate predictions
- Compare correctness, AUC, etc. for models with and without CS restrictions

### 2020-03-08 analysis/02_descriptive-analysis.Rmd
Turn off warnings

@@
 
-```{r model-pts-restrictions, cache=TRUE, message=FALSE, results="hide"}
+```{r model-pts-restrictions, cache=TRUE, message=FALSE, warning=FALSE, results="hide"}
 diff_ngo_pts <- brm(

### 2020-03-08 analysis/02_descriptive-analysis.Rmd
Ha, use predicted draws for real

@@
   modelr::data_grid(PTS_factor) %>% 
-  add_fitted_draws(diff_cs_pts, seed = BAYES_SEED)
+  add_predicted_draws(diff_cs_pts, seed = BAYES_SEED)
 ```
@@
 ```{r plot-posterior-preds-pts-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
-ggplot(diff_cs_pts_posterior, aes(x = .value, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
+ggplot(diff_cs_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
   stat_dotsh(quantiles = 100, shape = 19) +
@@
   modelr::data_grid(PTS_factor) %>% 
-  add_fitted_draws(diff_ngo_pts, seed = BAYES_SEED)
+  add_predicted_draws(diff_ngo_pts, seed = BAYES_SEED)
 ```
@@
 ```{r plot-posterior-preds-pts-ngo, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
-ggplot(diff_ngo_pts_posterior, aes(x = .value, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
+ggplot(diff_ngo_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
   stat_dotsh(quantiles = 100, shape = 19) +
@@
   modelr::data_grid(armed_conflict) %>% 
-  add_fitted_draws(diff_cs_conflict, seed = BAYES_SEED) %>% 
+  add_predicted_draws(diff_cs_conflict, seed = BAYES_SEED) %>% 
   ungroup() %>% 
@@
 ```{r plot-posterior-preds-conflict-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
-ggplot(diff_cs_conflict_posterior, aes(x = .value, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
+ggplot(diff_cs_conflict_posterior, aes(x = .prediction, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
   stat_dotsh(quantiles = 100, shape = 19) +

### 2021-03-23 README.Rmd
Depackagify

@@
 Authors <- "Suparna Chaudhry and Andrew Heiss"
-Year <- "2019"
+Year <- "2021"
 ```
@@
 
-In order to reproduce this project, you'll need to install the compendium as an R package. After downloading the compendium, do the following:
+In order to reproduce this project, you'll need to install ASDF:
 

### 2021-03-23 analysis/01_get-merge-data.Rmd
Depackagify

@@
 date: "Last run: `r format(Sys.time(), '%F')`"
+editor_options: 
+  chunk_output_type: console
 ---
@@
 ```{r setup, warning=FALSE, message=FALSE}
-knitr::opts_chunk$set(fig.retina = 2,
+knitr::opts_chunk$set(fig.retina = 3,
                       tidy.opts = list(width.cutoff = 120),  # For code
@@
 library(tidyverse)
-library(canaryNGOs)
 library(readxl)

### 2021-03-23 analysis/02_descriptive-analysis.Rmd
Depackagify

@@
 library(tidyverse)
-library(canaryNGOs)
 library(brms)

### 2021-03-23 R/canaryNGOs-package.R

@@ -1,9 +1,0 @@
-#' The 'canaryNGOs' package.
-#'
-#' @description Research on how restrictions on NGOs foreshadow other forms of
-#'   human rights repression
-#'
-#' @docType package
-#' @name canaryNGOs-package
-#' @aliases canaryNGOs
-NULL

### 2021-03-23 manuscript/pandoc/bin/anonymize.py
Better pandoc support

@@ -1,0 +1,55 @@
+#!/usr/bin/env python3
+
+# Replace text with different text for anonymity.
+#
+# You must specify the replacement dictionary in a CSV file with columns named
+# "original" and "replacement":
+#
+#   original,replacement
+#   old text,new text
+#
+# usage: anonymize.py [-h] replacements [input_file] [output]
+#
+# Recommended usage: Send the Markdown output to stdout (default) and pipe
+# into pandoc for instant preprocessing:
+#
+#   anonymize.py replacements.csv document.md | pandoc -f markdown -t html -o document.html
+
+# Load libraries
+import argparse
+import sys
+import re
+import csv
+
+# Get command line arguments
+parser = argparse.ArgumentParser(description='Replace text with different text for anonymity.')
+parser.add_argument('replacements', type=argparse.FileType('r'),
+                    help='CSV file of replacements (with columns named "original" and "replacement")')
+parser.add_argument('input_file', type=argparse.FileType('r'),
+                    nargs='?', default=sys.stdin,
+                    help='file to anonymize')
+parser.add_argument('output', type=argparse.FileType('w'),
+                    nargs='?', default=sys.stdout,
+                    help='the name of the output file (defaults to stdout)')
+args = parser.parse_args()
+
+
+# Load replacements CSV as a dictionary
+with args.replacements as file:
+    reader = csv.DictReader(file, skipinitialspace=True)
+    replacements = {row['original']: row['replacement'] for row in reader}
+
+
+# Replace keys in the dictionary with values
+def anonymize(text, repl):
+    # Sort keys by length, in reverse
+    for item in sorted(repl.keys(), key=len, reverse=True):
+        # Replace stuff
+        text = re.sub(item, repl[item], text)
+
+    return(text)
+
+
+# All done!
+with args.output as f:
+    f.write(anonymize(args.input_file.read(), replacements))

### 2021-03-23 manuscript/pandoc/bin/render_docx.R

@@ -1,0 +1,23 @@
+#!/usr/bin/env Rscript
+
+args <- R.utils::cmdArgs()
+
+# Check arguments
+stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
+          "Specify an output file using -output\n(e.g. `-output manuscript.docx`)" = is.character(args$output),
+          "Specify a CSL file using -csl\n(e.g. `-csl pandoc/csl/apa.csl`)" = is.character(args$csl))
+
+pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
+
+# Knit
+rmarkdown::render(
+  input = args$input,
+  output_file = args$output,
+  bookdown::word_document2(
+    reference_docx = paste0(pandoc_suport, "/templates/ath-manuscript.docx"),
+    pandoc_args = c(paste0("--csl=", args$csl)),
+    md_extensions = "+raw_tex+smart-autolink_bare_uris",
+    toc = FALSE,
+    number_sections = FALSE
+  )
+)

### 2021-03-23 manuscript/pandoc/bin/render_html.R

@@ -1,0 +1,37 @@
+#!/usr/bin/env Rscript
+
+args <- R.utils::cmdArgs()
+
+# Check arguments
+stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
+          "Specify an output file using -output\n(e.g. `-output manuscript.html`)" = is.character(args$output),
+          "Specify a CSL file using -csl\n(e.g. `-csl pandoc/csl/apa.csl`)" = is.character(args$csl))
+
+pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
+
+# Add CSS file as a dependency so it goes into the _files directory
+dep <- htmltools::htmlDependency(
+  name = "ath",
+  version = "1.0.0",
+  paste0(pandoc_suport, "/css"),
+  stylesheet = "ath-clean.css"
+)
+extra_dependencies <- list(dep)
+
+# Knit
+rmarkdown::render(
+  input = args$input,
+  output_file = args$output,
+  bookdown::html_document2(
+    template = paste0(pandoc_suport, "/templates/html.html"),
+    pandoc_args = c("--metadata", "link-citations=true",
+                    "--metadata", "linkReferences=true",
+                    paste0("--csl=", args$csl)),
+    md_extensions = "+raw_tex+smart-autolink_bare_uris+ascii_identifiers",
+    toc = TRUE,
+    number_sections = FALSE,
+    self_contained = FALSE,
+    theme = NULL,
+    extra_dependencies = extra_dependencies
+  )
+)

### 2021-03-23 manuscript/pandoc/bin/render_odt.R

@@ -1,0 +1,24 @@
+#!/usr/bin/env Rscript
+
+args <- R.utils::cmdArgs()
+
+# Check arguments
+stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
+          "Specify an output file using -output\n(e.g. `-output manuscript.odt`)" = is.character(args$output),
+          "Specify a CSL file using -csl\n(e.g. `-csl pandoc/csl/apa.csl`)" = is.character(args$csl))
+
+pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
+
+# Knit
+rmarkdown::render(
+  input = args$input,
+  output_file = args$output,
+  bookdown::odt_document2(
+    template = paste0(pandoc_suport, "/templates/odt.odt"),
+    reference_odt = paste0(pandoc_suport, "/templates/reference.odt"),
+    pandoc_args = c(paste0("--csl=", args$csl)),
+    md_extensions = "+raw_tex+smart-autolink_bare_uris+ascii_identifiers",
+    toc = FALSE,
+    number_sections = FALSE
+  )
+)

### 2021-03-23 manuscript/pandoc/bin/render_pdf-ms.R

@@ -1,0 +1,31 @@
+#!/usr/bin/env Rscript
+
+args <- R.utils::cmdArgs()
+
+# Check arguments
+stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
+          "Specify an output file using -output\n(e.g. `-output manuscript-ms.pdf`)" = is.character(args$output),
+          "Specify one of these options using -bibstyle:
+- bibstyle-chicago-notes
+- bibstyle-chicago-authordate
+- bibstyle-apa
+(e.g. `-bibstyle bibstyle-chicago-notes`)" = is.character(args$bibstyle))
+
+pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
+
+rmarkdown::render(
+  input = args$input,
+  output_file = args$output,
+  bookdown::pdf_document2(
+    template = paste0(pandoc_suport, "/templates/xelatex-manuscript.tex"),
+    latex_engine = "xelatex", 
+    dev = "cairo_pdf",
+    pandoc_args = c("--top-level-division=section", 
+                    "--shift-heading-level-by=0", 
+                    "-V", args$bibstyle),
+    md_extensions = "+raw_tex+smart-autolink_bare_uris",
+    toc = FALSE,
+    keep_tex = FALSE,
+    citation_package = "biblatex"
+  )
+)

### 2021-03-23 manuscript/pandoc/bin/render_pdf.R

@@ -1,0 +1,32 @@
+#!/usr/bin/env Rscript
+
+args <- R.utils::cmdArgs()
+
+# Check arguments
+stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
+          "Specify an output file using -output\n(e.g. `-output manuscript.pdf`)" = is.character(args$output),
+          "Specify one of these options using -bibstyle:
+- bibstyle-chicago-notes
+- bibstyle-chicago-authordate
+- bibstyle-apa
+(e.g. `-bibstyle bibstyle-chicago-notes`)" = is.character(args$bibstyle))
+
+pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
+
+rmarkdown::render(
+  input = args$input,
+  output_file = args$output,
+  bookdown::pdf_document2(
+    template = paste0(pandoc_suport, "/templates/xelatex.tex"),
+    latex_engine = "xelatex",
+    dev = "cairo_pdf",
+    pandoc_args = c("--top-level-division=section",
+                    "--shift-heading-level-by=0",
+                    "-V", args$bibstyle,
+                    "-V", "chapterstyle=hikma-article"),
+    md_extensions = "+raw_tex+smart-autolink_bare_uris",
+    toc = FALSE,
+    keep_tex = FALSE,
+    citation_package = "biblatex"
+  )
+)

### 2021-03-23 manuscript/pandoc/bin/word_count.R

@@ -1,37 +1,67 @@
-suppressPackageStartupMessages(library(tidyverse))
+#!/usr/bin/env Rscript
+
+# string::stri_count_words() counts, um, words. That's its whole job. But it
+# doesn't count them like Microsoft Word counts them, and academic publishing
+# portals tend to care about Word-like counts. For instance, Word considers
+# hyphenated words to be one word, while stringr counts them as two (and even
+# worse, stringi counts / as word boundaries, so URLs can severely inflate your
+# word count).
+#
+# Also, academic writing typically doesn't count the title, abstract, table
+# text, figure captions, or equations as words in the manuscript (and it
+# SHOULDN'T count bibliographies, but it always seems to ugh).
+#
+# This script parses the rendered manuscript HTML, removes extra elements,
+# adjusts the text so that stringi treats it more like Word, and then provides a
+# more accurate word count.
+
+suppressPackageStartupMessages(library(magrittr))
+suppressPackageStartupMessages(library(stringr))
+suppressPackageStartupMessages(library(purrr))
 suppressPackageStartupMessages(library(rvest))
-suppressPackageStartupMessages(library(here))
 suppressPackageStartupMessages(library(stringi))
 
-ms_raw <- read_html(here("manuscript", "manuscript.html"))
+args <- commandArgs(trailingOnly = TRUE)
+
+if (length(args) < 1) {
+  ms_file <- "paper.html"
+} else {
+  ms_file <- args[1]
+}
+
+# Read the HTML file
+ms_raw <- read_html(ms_file)
 
 # Extract just the article, ignoring title, abstract, etc.
-ms <- ms_raw %>% 
-  html_nodes("article") 
+ms <- ms_raw %>%
+  html_nodes("article")
 
 # Get rid of figures, tables, and math
 xml_remove(ms %>% html_nodes("figure"))
 xml_remove(ms %>% html_nodes("table"))
 xml_remove(ms %>% html_nodes(".display"))  # Block math
-xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>% 
+xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>%
   invisible()
 
 # Go through each child element in the article and extract it
 ms_cleaned_list <- map(html_children(ms), ~ {
-  .x %>% 
-    html_text(trim = TRUE) %>% 
[…]

### 2021-03-23 manuscript/manuscript.Rmd
Add initial manuscript

---
title: "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
short-title: "Canary in the Coal Mine"
author:
- name: Suparna Chaudhry
  affiliation: Lewis & Clark College
  email: schaudhry@lclark.edu
  url: http://www.suparnachaudhry.com/
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  url: https://www.andrewheiss.com/
date: "March 23, 2021"
published: This is an early draft of a working paper.
git-repo: https://github.com/andrewheiss/canary-ngos
abstract: >-
  Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions. While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of laws—many of which appear mundane on their face—represent a bureaucratic form of repressive that could be indicative of more severe human rights abuses and backsliding. This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space. In this paper, we ask: do legal crackdowns on NGOs predict broader civil society repression? We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it. These laws also make it easier for states to prevent and deter future large-scale popular mobilization. Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of attacks on journalists, independent media, academic freedom, and freedoms of expression and association. This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deteriorations in space for civil society. 
keywords: "civil society restrictions, human rights, journalists"
reference-section-title: References
bibliography: bibliography.bib
csl: pandoc/csl/chicago-author-date.csl
title-page: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# Figure out output format
is_docx <- knitr::pandoc_to("docx") | knitr::pandoc_to("odt")
is_latex <- knitr::pandoc_to("latex")
is_html <- knitr::pandoc_to("html")

# Word-specific things
table_format <- ifelse(is_docx, "huxtable", "kableExtra")  # Huxtable tables
conditional_dpi <- ifelse(is_docx, 300, 300)  # Higher DPI
conditional_align <- ifelse(is_docx, "default", "center")  # Word doesn't support align

# Knitr options
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  tidy.opts = list(width.cutoff = 120),  # Code width
  fig.retina = 3, dpi = conditional_dpi,
  fig.width = 7, fig.asp = 0.618,
  fig.align = conditional_align, out.width = "85%",
  fig.path = "output/figures/",
  cache.path = "output/_cache/",
  fig.process = function(x) {  # Remove "-1" from figure names
    x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
    if (file.rename(x, x2)) x2 else x
  }
)

# R options
options(
  width = 90,  # Output width
  dplyr.summarise.inform = FALSE,  # Turn off dplyr's summarize() auto messages
  knitr.kable.NA = "",  # Make NAs blank in kables
  kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
  modelsummary_default = table_format  # Set modelsummary backend
)

library(tidyverse)
library(here)

source(here("lib", "graphics.R"))
```

Governments across the globe have been cracking down on civil society organizations (CSOs) -- a phenomenon referred to as closing civic space in policy arena. The non-violent nature of this repression is particularly notable.The last two decades have
seen a proliferation of laws designed to limit the influence of civil society organizations,
with more than 100 countries obstructing, repressing, or closing the legal
environment for civil society have required that funds
to NGOs be routed through state-owned banks, mandated that funds cannot be used
for political purposes, or prohibited NGOs from accepting any funds from foreign
sources (Carothers, DPR, Chaudhry, Heiss)

As someone points out, states have toned down 'open, violent confrontation' and favor the development of a 'civilized' oppression. The use of legal tools instead of violent repression means that NGOs have to  their practices to stay within the bounds of permitted activities and operations.  This has led to depoliticization, avoidance of direct political activism. But that state cannot soften or neutralize all forms of political activities in subtle, legal ways that they have with NGOs. Soon or later, states need to deal with threats in a more violent, confrontational manner. Studying these NGO laws can thus be the canary in the coal mine which signals the states that intend to continue down this repressive path, especially in their short to medium term trajectories.

What does their targeting tell us about a state's broader respect for civil society and the overall level of human rights repression? Can the crackdown on NGOs act as an indicator for subsequent increasing repression?

Information about crackdown can be a valuable indicator of human rights trajectories. Can act as an early warning signal for worsening repression, suggesting which countries are testing the waters with comparatively 'milder' forms of repression before enacting more violent forms of crackdown.

Structural factors such as levels of democracy, economic development, electoral competitiveness can identify countries that are likely to have more or less respect for civic freedoms, but these factors are also slow to change over time. Thus, they may not be particularly suitable for forecasting short-term trajectories, especially for moderatively repressive countries.

# Assessing Changes in Government Repression

Why we look as NGOs
From an economic perspective, the foreign aid community prefers NGOs since
they overcome many failures associated with channeling funds through the state
(Dietrich 2013). They provide services to large parts of the population in the Global
South, especially where governments are unable to do so on a consistent basis.

## Structural factors explaining repression

## Exploring non-violent forms of repression
Why might repressive states start with non-violent forms of repression?

# State repression of NGOs

A robust, strong civil society is widely considered as an important component on democratic transition and consolidation.
Accountability
Corruption
Monitoring
In addition, services when the state falls short
Leaders want to avoid accountability. Shape the narrative of their performance both domestically and internationally. Don't like being shamed.
Can be the beginning of a deteriorating human rights situation.

In the aftermath of the failed coup attempt in Turkey in 2016, the government initiated a widespread crackdown on civil society, leading to the closure of almost 1500 NGOs soon after the group. However, this crackdown, ``spiraled far beyond those with any possible connection to the coup itself." In October 2017, the government levied terrorism charges against human rights activists, including on Amnesty International's Turkey Director and Chair.  The government also imprisoned an increasing number of journalists in 2017 and 2018, and issued arrest warrants for numerous academics in 2018.

### 2021-03-23 analysis/03_models.Rmd
A bunch of changes I made back in March 2020 but then covid happened and I have no idea where I was going with it all so I'll just commit it here and hope for the best

@@
 library(tidyverse)
+library(broom)
 library(here)
+library(brms)
+library(lme4)
+
+CHAINS <- 4
+ITER <- 2000
+WARMUP <- 1000
+BAYES_SEED <- 1234
+options(mc.cores = parallel::detectCores())  # Use all cores
 
 canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))
+canary_lagged <- read_rds(here("data", "derived_data", "canary_clean_lagged.rds"))
 ```
+
+TODO: (from the envelope on my desk):
+
+1. Null model: PTS ~ (1 | year) + (1 | country)
+2. PTS ~ repression + (1 | year) + (1 | country)
+3. PTS + repression within/between + (1 | year) + (1 | country)
+4. Fuller models with more controls - region dummies vs. (1 | region / country)
+5. Switch to ordered logit
+6. Logs and SNMM combination
+7. Make sure selection on observables is okay
+8. IPW?
 
@@
 - Use MSMs or whatever BlackwellGlynn:2018 suggest?
+
+- Use four versions of each coefficient - within/between year/country
+- When interpreting, focus on within (moving up/down from average level).
+Within country = in a typical country, the effect/association of x on y (i.e.
+increasing 1 more above average in a normal country is associated with β change in Y).
+Within year = in a typical year, the effect association of x on y (i.e.
+increasing 1 more above average in a given year is associated with a β change in Y)
+
+- Within country = increasing 1 unit of X above the average in a typical country is associated with β change in Y
+- Within year = increasing 1 unit of X above the average during a typical year is associated with a β change in Y
+- Between country = countries with higher average X are associated with a β higher level of Y 
+- Between country = years with higher average X are associated with a β higher level of Y
+
+> I'd just go with the basic one unit change marginal effects language.
+You can talk about it in ranges too since the groups are actually meaningful.
+The effect of X on Y was twice as great in 2012 as it was in 2008 or something.
+https://twitter.com/DavidPoe223/status/1236864935537278976
+
+> When you add a 1 inside (1 + year|continent/country), you are essentially allowing the countries to have their intercepts specified as "global intercept + country-specific displacement from global intecept + continent-specific displacement from global intercept".
+https://twitter.com/IsabellaGhement/status/1236849235275829248
+
+> Yes, that model would allow temporal trends specific to each country, while also estimating how trends differ across countries and also across continents relative to the trend for a "typical" country in a "typical" continent (all else being equal).
+https://twitter.com/IsabellaGhement/status/1236850446016188416
+
+# Within/between effects (aka Mundlak device)
+PTS ~ 1 + CS_repress_demeaned + CS_repress_mean + controls_demeaned + controls_meaned +
+  year +  # Allow for year global trend
+  (1 + year | country)  # Random country intercepts
+
+https://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#model-specification
+
+https://rpubs.com/jebyrnes/causal_mods
+
+http://methods.johndavidpoe.com/2019/02/05/my-talk-at-iu/
+
+```{r}
+canary_demeaned <- canary_lagged %>% 
+  mutate(gwcode = as.factor(gwcode)) %>% 
+  group_by(gwcode) %>% 
+  mutate_at(vars(v2csreprss, v2x_polyarchy, gdpcap_log),
+            list(between = ~mean(., na.rm = TRUE),  # Between, for countries
+                 within = ~. - mean(., na.rm = TRUE)))  # Within, for countries
+
+model_asdf <- lmer(PTS_lead1 ~  # Overall terror/repression level
+                     v2csreprss_within + v2csreprss_between +  # Civil society repression
+                     v2x_polyarchy_within + v2x_polyarchy_between +  # Democracy
+                     gdpcap_log_within + gdpcap_log_between +  # GDP per capita
+                     armed_conflict +  # Government involved in conflict with 25+ battle deaths
+                     splines::bs(year) +  # Non-linear year trend
+                     (1 + v2csreprss_within | region/gwcode) +  # Random slopes for within CS repression
+                     (1 + v2csreprss_between | region/gwcode),  # Random slopes for between CS repression
+                   data = canary_demeaned)
+
+tidy(model_asdf, effects = "fixed")
+coef(model_asdf)$`gwcode:region` %>% rownames_to_column() %>% as_tibble() %>% head()
+coef(model_asdf)$region %>% rownames_to_column() %>% as_tibble()
+```
+
+```{r}
+model_lag1 <- lm(PTS_lead1 ~ barriers_total + v2x_polyarchy + region + gdpcap_log + as.factor(year),
+                 data = canary_lagged)
+tidy(model_lag1)
+
+modelx_lag1 <- lm(PTS_lead1 ~ v2csreprss + v2x_polyarchy + region + gdpcap_log + as.factor(year),
+                 data = canary_lagged)
+tidy(modelx_lag1)
+
+modelx_lag1 <- lm(PTS_lead1 ~ v2csreprss,
+                 data = canary_lagged)
+tidy(modelx_lag1)
+```
+
+```{r}
+thing1 <- brm(
+  bf(PTS_lead1 ~ v2csreprss + v2x_polyarchy + region + gdpcap_log + 
+       year + (1 + year | gwcode)),
+  family = gaussian, inits = 0,
+  control = list(adapt_delta = 0.99),
+  data = canary_lagged %>% select(PTS_lead1, v2csreprss, v2x_polyarchy, 
+                                  region, gdpcap_log, year, gwcode),
+  prior = c(set_prior("normal(0, 10)", class = "Intercept"),
+            set_prior("normal(0, 2.5)", class = "b"),
+            set_prior("normal(0, 2.5)", class = "sd")),
+  chains = CHAINS, iter = 8000, warmup = WARMUP, seed = BAYES_SEED,
+  file = here("analysis", "cache", "thing_8000")
+)
+
+tidy(thing1)
+tidy(thing)
+
+# Random intercepts & random slopes?
+lmer(outcome ~ explanatory + controls + (1 | year) + (1 | countrycode))
+
+# Partial pooling?
+lmer(outcome ~ explanatory + controls + (1 + year | countrycode))
+
+brm(bf(outcome ~ explanatory + controls + year + (1 + year | countrycode)))
+
+PTS ~ CS_repress + controls + as.factor(year) + 
+  (1 + as.factor(year) | countrycode) + (1 + region | )
+
+# Super rich model with country, year, and region effects - information flows through the whole structure: https://twitter.com/statwonk/status/1236794927683698688
+PTS ~ CS_repress + controls +
+  (1 | continent/country/year)
+
+# Effect of each year and also each country has its own year effects:
+(1 | year) + (1 | country) + (1 | year:country)
+
+# Slopes vs. shocks
+# https://twitter.com/statwonk/status/1236785673853681664
+as.factor(year) + (1 | year) + (1 | country) + (1 | year:country)
+
+PTS ~ CS_repress + controls +
+  year + (1 + year | country) +  # Random year slopes within countries
+  (1 | continent/country/year)  # Random intercepts nested inside continent/country/year
+
+PTS ~ CS_repress + controls +
+  year + (1 + year | country) +  # Random year slopes within countries
+  (1 | continent/country/year)  # Random intercepts nested inside continent/country/year
+
+# Nested continent/country effects
+PTS ~ CS_repress + controls +
+  (1 | year) +  # Allow for year shocks
+  (1 + year | continent / country)  # Random nested continent/country intercepts
+
+# Within/between effects (aka Mundlak device)
+PTS ~ 1 + CS_repress_demeaned + CS_repress_mean + controls_demeaned + controls_meaned +
+  year +  # Allow for year global trend
+  (1 + year | continent / country)  # Random nested continent/country intercepts
+
+PTS ~ CS_repress + controls +
+  year + (1 | year) +  # YOLO trend + shocks
+  (1 + year | continent / country)  # Random nested continent/country intercepts
+
+# Just country effects
+PTS ~ CS_repress + controls +
+  (1 | year) +  # Allow for year shocks
+  (1 + year | country)  # Random nested country intercepts
+
+PTS ~ CS_repress + controls +
+  year +  # Allow for year global trend
+  (1 + year | country)  # Random nested country intercepts
+
+PTS ~ CS_repress + controls +
+  year + (1 | year) +  # YOLO trend + shocks
+  (1 + year | country)  # Random nested country intercepts
+
+get_prior(bf(PTS_lead1 ~ v2csreprss + v2x_polyarchy + region + gdpcap_log + (1 | year) + (1 | gwcode)),
+  family = gaussian,
+  data = canary_lagged)
+
+diff_cs_pts <- brm(
+  bf(v2csreprss ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
+  family = student, 
+  data = filter(canary, year == 2010) %>% select(v2csreprss, PTS_factor),
+  prior = c(
+    # Set group mean prior
+    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
+    # Set group variance priors. We keep the less informative cauchy(0, 1).
+    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
+    set_prior("exponential(1.0/29)", class = "nu")
+  ),
+  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
+  file = here("analysis", "cache", "diff_cs_pts")
+)
+
+tidy(thing)
+
+lag1 <- lm(I(sqrt(terrorinclead) - coef(out)["totspendrevlog"]*totspendrevlog) ~ l(totspendrevlog, cow)  + l(govleft, cow) + l(democ, cow) + l(poplog, cow) + l(govcap, cow) + l(conflict, cow) + l(tradelog, cow) + europe +africa + asia + america + sqrt(l(terrorinc, cow))+ sqrt(l(terrorinc, cow, 2))+ as.factor(year), data=reasonabledata)
+
+lag2 <- lm(I(sqrt(terrorinclead) - coef(out)["totspendrevlog"]*totspendrevlog - coef(lag1)["l(totspendrevlog, cow)"]*l(totspendrevlog, cow))~l(totspendrevlog, cow, 2)  + l(govleft, cow, 2) + l(democ, cow, 2) + l(democ, cow, 3) + l(poplog, cow, 2) + l(govcap, cow, 2) + l(conflict, cow, 2) + l(tradelog, cow, 2) + europe +africa + asia + america + sqrt(l(terrorinc, cow, 2))+ sqrt(l(terrorinc, cow,3))+ as.factor(year), data=reasonabledata)
+```

### 2021-03-23 analysis/index.Rmd
A bunch of changes I made back in March 2020 but then covid happened and I have no idea where I was going with it all so I'll just commit it here and hope for the best

@@
 Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions.
-While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of laws—many of which appear mundane on their face—represent a bureaucratic form of repressive that could be indicative of more severe human rights abuses and backsliding.
+While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of laws—many of which appear mundane on their face—represent a bureaucratic form of repression that could indicate more severe human rights abuses and backsliding.
 This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
-In this paper, we ask: do legal crackdowns on NGOs predict broader civil society repression?
-We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
-These laws also make it easier for states to prevent and deter future large-scale popular mobilization.
+Do legal crackdowns on NGOs predict broader civil society repression?
+We argue they do, given that anti-NGO laws are among the most subtle means of repression and attract the least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
 Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of attacks on journalists, independent media, academic freedom, and freedoms of expression and association.

### 2021-03-27 analysis/01_data-overview.Rmd
{targets}ification

---
title: "Process and merge data"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knit_print.data.frame <- function(x, ...) {
  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
  asis_output(res)
}

registerS3method("knit_print", "data.frame", knit_print.data.frame)
registerS3method("knit_print", "grouped_df", knit_print.data.frame)

knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "85%")

options(dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(scales)
library(patchwork)
library(DT)
library(naniar)
library(here)

# Generated via random.org
set.seed(9936)

# Load data
# Need to use this withr thing because tar_read() and tar_load() need to see the
# _targets folder in the current directory, but this .Rmd file is in a subfolder
withr::with_dir(here::here(), {
  source(tar_read(plot_funs))

  tar_load(skeleton)
  tar_load(chaudhry_clean)
  tar_load(pts_clean)
  tar_load(killings_all)
  tar_load(vdem_clean)
  tar_load(wdi_clean)
  tar_load(un_pop)
  tar_load(un_gdp)
  tar_load(ucdp_prio_clean)

  tar_load(panel_done_trimmed)
})
```

# Data processing

## Country-year skeleton

We use [Gleditsch-Ward country codes](http://ksgleditsch.com/data-4.html) to identify each country across the different datasets we merge. We omit a bunch of things though:

- We omit microstates
- Because the World Bank doesn't include it in the WDI, we omit Taiwan (713)
- We only use countries in Suparna's anti-NGO law data

To get consistency in country codes, we do this:

- When converting GW codes to COW codes, [following Gleditsch and Ward](https://www.andybeger.com/states/articles/differences-gw-cow.html), we treat post-2006 Serbia as 345 (a continuation of Serbia & Montenegro). And we also treat Serbia as a continuation of Yugoslavia with 345 (following V-Dem, which does that too)
- In both COW and GW codes, modern Vietnam is 816, but `countrycode()` thinks the COW code is 817, which is old South Vietnam (see [issue](https://github.com/vincentarelbundock/countrycode/issues/16)), so we use `custom_match` to force 816 to recode to 816.
- Also, following V-Dem, we treat Czechoslovakia (GW/COW 315) and Czech Republic (GW/COW 316) as the same continuous country (V-Dem has both use ID 157).

We have `r panel_done_trimmed %>% distinct(gwcode) %>% nrow()` countries in this data, spanning `r panel_done_trimmed %>% distinct(year) %>% nrow()` possible years. Here's a lookup table of all the countries included:

```{r show-final-countries}
skeleton$skeleton_lookup %>% 
  filter(gwcode %in% unique(chaudhry_clean$gwcode)) %>% 
  select(-years_included) %>% 
  datatable()
```

## Chaudhry NGO restrictions

We create several indexes for each of the categories of regulation, following Christensen and Weinstein’s classification:

- `entry` (Q2b, Q2c, Q2d; 3 points maximum, actual max = 3 points maximum): barriers to entry
  - Q2c is reversed, so not being allowed to appeal registration status earns 1 point.
  - Q2a is omitted because it’s benign
- `funding` (Q3b, Q3c, Q3d, Q3e, Q3f; 5 points maximum, actual max = 4.5): barriers to funding
  - Q3a is omitted because it’s benign
  - Scores that range between 0–2 are rescaled to 0–1 (so 1 becomes 0.5)
- `advocacy` (Q4a, Q4c; 2 points maximum, actual max = 2): barriers to advocacy
  - Q4b is omitted because it’s not a law
  - Scores that range between 0–2 are rescaled to 0–1 (so 1 becomes 0.5)
- `barriers_total` (10 points maximum, actual max = 8.5): sum of all three indexes

These indexes are also standardized by dividing by the maximum, yielding the following variables:

- `entry_std`: 1 point maximum, actual max = 1
- `funding_std`: 1 point maximum, actual max = 1
- `advocacy_std`: 1 point maximum, actual max = 1
- `barriers_total_std`: 3 points maximum, actual max = 2.5

```{r glimpse-chaudhry-ngos}
glimpse(chaudhry_clean)
```

## Political Terror Scale (PTS)

We use data from the [Political Terror Scale (PTS) project](http://www.politicalterrorscale.org/) to measure state repression. This project uses reports from the US State Department, Amnesty International, and Human Rights Watch and codes political repression on a scale of 1-5:

- **Level 1**: Countries under a secure rule of law, people are not imprisoned for their view, and torture is rare or exceptional. Political murders are extremely rare.
- **Level 2**: There is a limited amount of imprisonment for nonviolent political activity. However, few persons are affected, torture and beatings are exceptional. Political murder is rare.
- **Level 3**: There is extensive political imprisonment, or a recent history of such imprisonment. Execution or other political murders and brutality may be common. Unlimited detention, with or without a trial, for political views is accepted.
- **Level 4**: Civil and political rights violations have expanded to large numbers of the population. Murders, disappearances, and torture are a common part of life. In spite of its generality, on this level terror affects primarily those who interest themselves in politics or ideas.
- **Level 5**: The terrors of Level 4 have been extended to the whole population. The leaders of these societies place no limits on the means or thoroughness with which they pursue personal or ideological goals.

Following Gohdes and Carey, we use the State Department score, unless it's missing, in which case we use Amnesty's score.

```{r glimpse-pts}
glimpse(pts_clean)
```

## Gohdes and Carey journalist deaths

We use data from [Gohdes and Carey (2017)](https://doi.org/10.1177/0022343316680859) for the number of journalists murdered between 2002 and 2014. They provide two `.Rdata` files in their replication materials—one is a list of all journalist deaths, and one is a TSCS dataset they use in their main analysis, with summary values of journalist deaths for each country/year. Their panel data does not include 2002 for some reason, so we ignore the panel data and recreate the summary values by hand here.

```{r glimpse-gh-journalists}
glimpse(killings_all)
```

## Varieties of Democracy (V-Dem)

We use a bunch of variables from the [Varieties of Democracy project](https://www.v-dem.net/en/):

- **Civil society stuff**
  - CSO entry and exit: `v2cseeorgs`
  - CSO repression: `v2csreprss`
  - CSO consultation: `v2cscnsult`
  - CSO participatory environment: `v2csprtcpt`
  - CSO women's participation: `v2csgender`
  - CSO anti-system movements: `v2csantimv`
  - Core civil society index (entry/exit, repression, participatory env): `v2xcs_ccsi`
- **Freedom of expression stuff**
  - Freedom of expression index: `v2x_freexp`
  - Freedom of expression and alternative sources of information index: `v2x_freexp_altinf`
  - Freedom of academic and cultural expression: `v2clacfree`
  - Media self-censorship: `v2meslfcen`
- **Repression stuff**
  - Religious organization repression: `v2csrlgrep`
  - Govt censorship effort - media: `v2mecenefm`
  - Harassment of journalists: `v2meharjrn`
- **Rights indexes**
  - Civil liberties index: `v2x_civlib`
  - Physical violence index: `v2x_clphy`
  - Private civil liberties index: `v2x_clpriv`
  - Political civil liberties index: `v2x_clpol`
- **Democracy**
  - Polyarchy index: `v2x_polyarchy`
  - Regimes of the world category: `v2x_regime_amb`

```{r glimpse-vdem}
glimpse(vdem_clean)
```

## World Bank development indicators

We don't really use anything from the World Bank's data except for population data for Kosovo.

```{r wlimpse-wdi}
glimpse(wdi_clean)
```

## UNData

The reason we don't just use WDI data for GDP and % of GDP from trade is that the WDI data is incomplete (especially pre-1990, but that's not an issue in this project) To get around that, we create our own GDP and trade measures using data directly from the UN (at [UNData](https://data.un.org/)). They don't have a neat API like the World Bank, so you have to go to their website and export the data manually.

We collect three variables: [GDP at constant 2015 prices](http://data.un.org/Data.aspx?q=gdp&d=SNAAMA&f=grID%3a102%3bcurrID%3aUSD%3bpcFlag%3a0), [GDP at current prices](http://data.un.org/Data.aspx?q=gdp&d=SNAAMA&f=grID%3a101%3bcurrID%3aUSD%3bpcFlag%3a0), and [population](https://population.un.org/wpp/Download/Standard/Population/).

```{r glimpse-un-pop}
glimpse(un_pop)
```

```{r glimpse-un-gdp}
glimpse(un_gdp)
```

## UCDP/PRIO Armed Conflict

Following [Gohdes and Carey (2017)](https://doi.org/10.1177/0022343316680859), we use [UCDP/PRIO Armed Conflict data](https://ucdp.uu.se/downloads/index.html#armedconflict) to create an indicator marking if a country-year was involved in armed conflict that resulted in at least 25 battle-related deaths.

```{r glimpse-ucdp-prio}
glimpse(ucdp_prio_clean)
```

## Final clean combined data

Finally, we join everything together in one nice clean panel:

```{r glimpse-combined}
glimpse(panel_done_trimmed)
```

\

# Basic data details

```{r show-country-years-summary}
panel_done_trimmed %>% 
  summarize(`Number of countries` = length(unique(gwcode)),
            `Number of years` = length(unique(year)),
            `First year` = min(year),
            `Last year` = max(year)) %>% 
  kbl(align = "c") %>% 
  kable_styling()
```

Countries across years:

```{r show-country-year-count}
panel_done_trimmed %>% 
  count(Year = year, name = "Number of countries") %>% 
  kbl(align = "c") %>% 
  kable_styling()
```

\

# Missingness

We were super careful to ensure that our data is as complete as possible.

```{r plot-missing}
panel_done_trimmed %>% 
  vis_miss() +
  theme_ngo() +
  theme(axis.text.x = element_text(hjust = 0, angle = 45),
        panel.grid.major = element_blank())
```

There are only a tiny handful of rows with missing data: Serbia pre-2006.

```{r show-missing-rows, class.source="fold-show"}
panel_done_trimmed %>% 
  filter(is.na(advocacy)) %>% 
  select(gwcode, year, country, iso3, advocacy, entry, funding)
```

That's because our anti-NGO data doesn't include data for those years. That's fine, though. In models where we look at anti-NGO laws, we exclude those rows and only include rows where our `laws` indicator variable is TRUE. In models where we look at the general civil society environment, we do include these rows because V-Dem has data for them.

There are just two instances of missing data with PTS scores:

```{r show-missing-pts, class.source="fold-show"}
panel_done_trimmed %>% 
  filter(is.na(PTS)) %>% 
  select(gwcode, year, country, iso3, PTS, PTS_factor)
```

We just ignore them, I guess.

With that, here's our actual final cleaned data:

```{r plot-missing-laws}
panel_done_trimmed %>% 
  filter(laws) %>% 
  vis_miss() +
  theme_ngo() +
  theme(axis.text.x = element_text(hjust = 0, angle = 45),
        panel.grid.major = element_blank())
```

Beautiful.

\

# `targets` pipeline

Here's the general process for building and running this analysis. This is all done with [the magical **`targets`** package](https://docs.ropensci.org/targets/), which orchestrates all the dependencies automatically.

```{r show-targets-pipeline, echo=FALSE}
withr::with_dir(here::here(), {
  targets::tar_glimpse()
})
```

\

# Actual code

All the data processing is handled with dataset-specific functions that live in `R/funs_data-cleaning.R`, which **`targets`** then runs as needed. For the sake of transparency, here's that code:

```{r, code=xfun::read_utf8(here::here("R", "funs_data-cleaning.R")), eval=FALSE, class.source="fold-show"}
```

### 2021-03-27 analysis/02_descriptive-analysis.Rmd
{targets}ification

@@
     code_folding: hide
-params:
-  fig_width: 6
-  fig_height: 3.6
-  fig_height_taller: 5
+editor_options: 
+  chunk_output_type: console
 ---
 
-```{r setup, warning=FALSE, message=FALSE}
+```{r setup, include=FALSE}
+library(knitr)
+library(kableExtra)
+knit_print.data.frame <- function(x, ...) {
+  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
+  asis_output(res)
+}
+
+registerS3method("knit_print", "data.frame", knit_print.data.frame)
+registerS3method("knit_print", "grouped_df", knit_print.data.frame)
+
+knitr::opts_chunk$set(fig.retina = 3,
+                      tidy.opts = list(width.cutoff = 120),  # For code
+                      options(width = 90),  # For output
+                      fig.asp = 0.618, fig.width = 7, 
+                      fig.align = "center", out.width = "85%")
+
+options(dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+```
+
+```{r load-libraries-data, message=FALSE, warning=FALSE}
 library(tidyverse)
+library(targets)
 library(brms)
@@
 
-canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))
+# Generated via random.org
+set.seed(9936)
 
-# https://www.naturalearthdata.com/downloads/110m-cultural-vectors/
-country_borders <- read_sf(here("data", "raw_data", "Natural Earth", 
-                                "ne_110m_admin_0_countries", 
-                                "ne_110m_admin_0_countries.shp"))
+# Load data
+# Need to use this withr thing because tar_read() and tar_load() need to see the
+# _targets folder in the current directory, but this .Rmd file is in a subfolder
+withr::with_dir(here::here(), {
+  source(tar_read(plot_funs))
+
+  canary <- tar_read(panel_done_trimmed)
+  tar_load(world_map)
+})
 ```
@@
 
-map_data <- country_borders %>% 
-  left_join(things_to_map, by = c("ADM0_A3_IS" = "iso3")) %>% 
-  filter(ISO_A3 != "ATA")
+map_data <- world_map %>% 
+  left_join(things_to_map, by = c("ADM0_A3_IS" = "iso3"))
 ```
@@
 
-```{r map-ngo-laws, fig.width=params$fig_width, fig.height=params$fig_height_taller}
+```{r map-ngo-laws}
 map_ngo_laws <- ggplot() +
@@
           color = "black", size = 0.1) +
-  coord_sf(crs = 54030, datum = NA, expand = FALSE) + 
+  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
   scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 7)), 
@@
 
-```{r map-cs-repression, fig.width=params$fig_width, fig.height=params$fig_height_taller}
+```{r map-cs-repression}
 map_cs_repression <- ggplot() +
@@
           color = "black", size = 0.1) +
-  coord_sf(crs = 54030, datum = NA, expand = FALSE) + 
+  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
   scale_fill_scico(palette = "vik", direction = -1,
@@
 
-```{r model-pts-cs, cache=TRUE, message=FALSE, results="hide"}
+```{r model-pts-cs, message=FALSE, results="hide"}
 diff_cs_pts <- brm(
@@
 
-```{r plot-draws-pts-cs, fig.width=params$fig_width, fig.height=params$fig_height}
+```{r plot-draws-pts-cs}
 ggplot(diff_cs_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
-  geom_halfeyeh() +
+  stat_halfeye() +
   scale_x_reverse() +
@@
 
-```{r plot-posterior-preds-pts-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
+```{r plot-posterior-preds-pts-cs, warning=FALSE, message=FALSE}
 ggplot(diff_cs_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
-  stat_dotsh(quantiles = 100, shape = 19) +
-  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
+  stat_dots(quantiles = 100, shape = 19) +
+  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
@@
   theme_ngo()
-
-# ggsave("~/Desktop/plot1.pdf", device = cairo_pdf, width = 5, height = 3, units = "in")
-# ggsave("~/Desktop/plot1.png", type = "cairo", dpi = 300, width = 6, height = 3.6, units = "in")
 ```
@@
 
-```{r vdem-suparna-plot, warning=FALSE, message=FALSE, fig.width=params$fig_width, fig.height=params$fig_height_taller}
+```{r vdem-suparna-plot, warning=FALSE, message=FALSE}
 canary_barriers <- canary %>% 
@@
 
-```{r model-pts-restrictions, cache=TRUE, message=FALSE, warning=FALSE, results="hide"}
+```{r model-pts-restrictions, message=FALSE, warning=FALSE, results="hide"}
 diff_ngo_pts <- brm(
@@
 
-```{r plot-draws-pts-ngo, fig.width=params$fig_width, fig.height=params$fig_height}
+```{r plot-draws-pts-ngo}
 ggplot(diff_ngo_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
-  geom_halfeyeh() +
+  stat_halfeye() +
   scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
@@
 
-```{r plot-posterior-preds-pts-ngo, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
+```{r plot-posterior-preds-pts-ngo, warning=FALSE, message=FALSE}
 ggplot(diff_ngo_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
-  stat_dotsh(quantiles = 100, shape = 19) +
-  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
+  stat_dots(quantiles = 100, shape = 19) +
+  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
@@
 
-```{r model-conflict-cs, cache=TRUE, message=FALSE, results="hide"}
+```{r model-conflict-cs, message=FALSE, results="hide"}
 diff_cs_conflict <- brm(
@@
 
-```{r plot-draws-conflict-cs, fig.width=params$fig_width, fig.height=params$fig_height}
+```{r plot-draws-conflict-cs}
 ggplot(diff_cs_conflict_draws, aes(y = .variable, x = .value, fill = .variable)) + 
-  geom_halfeyeh() +
+  stat_halfeye() +
   scale_x_reverse() +
@@
 
-```{r plot-posterior-preds-conflict-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
+```{r plot-posterior-preds-conflict-cs, warning=FALSE, message=FALSE}
 ggplot(diff_cs_conflict_posterior, aes(x = .prediction, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
-  stat_dotsh(quantiles = 100, shape = 19) +
-  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
+  stat_dots(quantiles = 100, shape = 19) +
+  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
@@
   select(barriers_total, PTS, gh_alljourn, 
-         v2clacfree, v2csrlgrep, v2mecenefm, v2mecenefi, v2meharjrn, v2meslfcen,
+         v2clacfree, v2csrlgrep, v2mecenefm, v2meharjrn, v2meslfcen,
          v2x_clphy, v2x_clpol, v2x_clpriv, v2x_freexp, v2csreprss)

### 2021-03-27 analysis/03_models.Rmd
{targets}ification

@@
 date: "Last run: `r format(Sys.time(), '%F')`"
+output: 
+  html_document:
+    code_folding: show
+editor_options: 
+  chunk_output_type: console
 ---
 
-```{r setup, warning=FALSE, message=FALSE}
+```{r setup, include=FALSE}
+library(knitr)
+library(kableExtra)
+knit_print.data.frame <- function(x, ...) {
+  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
+  asis_output(res)
+}
+
+registerS3method("knit_print", "data.frame", knit_print.data.frame)
+registerS3method("knit_print", "grouped_df", knit_print.data.frame)
+
+knitr::opts_chunk$set(fig.retina = 3,
+                      tidy.opts = list(width.cutoff = 120),  # For code
+                      options(width = 90),  # For output
+                      fig.asp = 0.618, fig.width = 7, 
+                      fig.align = "center", out.width = "85%")
+
+options(dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+```
+
+```{r load-libraries-data, message=FALSE, warning=FALSE}
 library(tidyverse)
+library(targets)
 library(broom)
+library(broom.mixed)
 library(here)
@@
 library(lme4)
+library(modelsummary)
 
@@
 
-canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))
-canary_lagged <- read_rds(here("data", "derived_data", "canary_clean_lagged.rds"))
+# Generated via random.org
+set.seed(9936)
+
+# Load data
+# Need to use this withr thing because tar_read() and tar_load() need to see the
+# _targets folder in the current directory, but this .Rmd file is in a subfolder
+withr::with_dir(here::here(), {
+  source(tar_read(plot_funs))
+
+  canary <- tar_read(panel_done_trimmed)
+  canary_lagged <- tar_read(panel_lagged_trimmed)
+})
 ```
@@
 
+**I ran all these models in March 2020 pre-pandemic and I have no idea why??**
+
 ```{r}
@@
                      splines::bs(year) +  # Non-linear year trend
-                     (1 + v2csreprss_within | region/gwcode) +  # Random slopes for within CS repression
-                     (1 + v2csreprss_between | region/gwcode),  # Random slopes for between CS repression
+                     (1 + v2csreprss_within | gwcode) +  # Random slopes for within CS repression
+                     # (1 + v2csreprss_within | region/gwcode) +  # Random slopes for within CS repression
+                     (1 + v2csreprss_between | gwcode),  # Random slopes for within CS repression
+                     # (1 + v2csreprss_between | region/gwcode),  # Random slopes for between CS repression
                    data = canary_demeaned)
 
+# modelsummary(list(model_asdf))
 tidy(model_asdf, effects = "fixed")
-coef(model_asdf)$`gwcode:region` %>% rownames_to_column() %>% as_tibble() %>% head()
-coef(model_asdf)$region %>% rownames_to_column() %>% as_tibble()
+# coef(model_asdf)$`gwcode` %>% rownames_to_column() %>% as_tibble() %>% head()
+# coef(model_asdf)$region %>% rownames_to_column() %>% as_tibble()
 ```
@@
 ```{r}
-model_lag1 <- lm(PTS_lead1 ~ barriers_total + v2x_polyarchy + region + gdpcap_log + as.factor(year),
+model_lag1 <- lm(PTS_lead1 ~ barriers_total + v2x_polyarchy + gdpcap_log + as.factor(year),
                  data = canary_lagged)
-tidy(model_lag1)
 
-modelx_lag1 <- lm(PTS_lead1 ~ v2csreprss + v2x_polyarchy + region + gdpcap_log + as.factor(year),
+modelx_lag1 <- lm(PTS_lead1 ~ v2csreprss + v2x_polyarchy + gdpcap_log + as.factor(year),
                  data = canary_lagged)
-tidy(modelx_lag1)
 
-modelx_lag1 <- lm(PTS_lead1 ~ v2csreprss,
+modelxx_lag1 <- lm(PTS_lead1 ~ v2csreprss,
                    data = canary_lagged)
-tidy(modelx_lag1)
+
+modelsummary(list(model_lag1, modelx_lag1, modelxx_lag1),
+             coef_omit = "^as.factor",
+             stars = TRUE, gof_omit = "IC|F|Log.|R2$") %>% 
+  row_spec(10, extra_css = "border-bottom: 2px solid")
 ```
 
-```{r}
+**¿What even is this stuff?**
+
+```{r eval=FALSE}
 thing1 <- brm(
@@
 )
-
-tidy(thing)
-
-lag1 <- lm(I(sqrt(terrorinclead) - coef(out)["totspendrevlog"]*totspendrevlog) ~ l(totspendrevlog, cow)  + l(govleft, cow) + l(democ, cow) + l(poplog, cow) + l(govcap, cow) + l(conflict, cow) + l(tradelog, cow) + europe +africa + asia + america + sqrt(l(terrorinc, cow))+ sqrt(l(terrorinc, cow, 2))+ as.factor(year), data=reasonabledata)
-
-lag2 <- lm(I(sqrt(terrorinclead) - coef(out)["totspendrevlog"]*totspendrevlog - coef(lag1)["l(totspendrevlog, cow)"]*l(totspendrevlog, cow))~l(totspendrevlog, cow, 2)  + l(govleft, cow, 2) + l(democ, cow, 2) + l(democ, cow, 3) + l(poplog, cow, 2) + l(govcap, cow, 2) + l(conflict, cow, 2) + l(tradelog, cow, 2) + europe +africa + asia + america + sqrt(l(terrorinc, cow, 2))+ sqrt(l(terrorinc, cow,3))+ as.factor(year), data=reasonabledata)
 ```

### 2021-03-27 analysis/04_predictions.Rmd
{targets}ification

@@
 date: "Last run: `r format(Sys.time(), '%F')`"
+output: 
+  html_document:
+    code_folding: show
+editor_options: 
+  chunk_output_type: console
 ---
 
-```{r setup, warning=FALSE, message=FALSE}
+```{r setup, include=FALSE}
+library(knitr)
+library(kableExtra)
+knit_print.data.frame <- function(x, ...) {
+  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
+  asis_output(res)
+}
+
+registerS3method("knit_print", "data.frame", knit_print.data.frame)
+registerS3method("knit_print", "grouped_df", knit_print.data.frame)
+
+knitr::opts_chunk$set(fig.retina = 3,
+                      tidy.opts = list(width.cutoff = 120),  # For code
+                      options(width = 90),  # For output
+                      fig.asp = 0.618, fig.width = 7, 
+                      fig.align = "center", out.width = "85%")
+
+options(dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+```
+
+```{r load-libraries-data, message=FALSE, warning=FALSE}
 library(tidyverse)
+library(targets)
 library(here)
 
-canary <- read_rds(here("data", "derived_data", "canary_clean.rds"))
+# Load data
+# Need to use this withr thing because tar_read() and tar_load() need to see the
+# _targets folder in the current directory, but this .Rmd file is in a subfolder
+withr::with_dir(here::here(), {
+  source(tar_read(plot_funs))
+
+  canary <- tar_read(panel_done_trimmed)
+})
 ```

### 2021-03-27 R/funs_data-cleaning.R

@@ -1,0 +1,463 @@
+# The PTS data and journalist data are saved as .RData files, so they load into
+# R with their original object names. This function lets you load an .RData file
+# directly to a new object instead of bringing in the original name.
+# (via https://stackoverflow.com/a/25455968/120898)
+load_rdata <- function(filename) {
+  load(filename)
+  get(ls()[ls() != "filename"])
+}
+
+
+create_panel_skeleton <- function() {
+  microstates <- gwstates %>%
+    filter(microstate) %>% distinct(gwcode)
+
+  # In both COW and GW codes, modern Vietnam is 816, but countrycode() thinks the
+  # COW code is 817, which is old South Vietnam (see issue
+  # https://github.com/vincentarelbundock/countrycode/issues/16), so we use
+  # custom_match to force 816 to recode to 816
+  #
+  # Also, following Gleditsch and Ward, we treat Serbia after 2006 dissolution of
+  # Serbia & Montenegro as 345 in COW codes (see
+  # https://www.andybeger.com/states/articles/differences-gw-cow.html)
+  #
+  # Also, because the World Bank doesn't include it in the WDI, we omit Taiwan (713)
+
+  panel_skeleton <- state_panel(1995, 2014, partial = "any") %>%
+    # Remove microstates
+    filter(!(gwcode %in% microstates$gwcode)) %>%
+    # Remove Taiwan, the Bahamas, Belize, and Brunei
+    filter(!(gwcode %in% c(713, 31, 80, 835))) %>%
+    mutate(cowcode = countrycode(gwcode, origin = "gwn", destination = "cown",
+                                 custom_match = c("816" = 816L, "340" = 345L)),
+           country = countrycode(cowcode, origin = "cown", destination = "country.name",
+                                 custom_match = c("678" = "Yemen")),
+           iso2 = countrycode(cowcode, origin = "cown", destination = "iso2c",
+                              custom_match = c("345" = "RS", "347" = "XK", "678" = "YE")),
+           iso3 = countrycode(cowcode, origin = "cown", destination = "iso3c",
+                              custom_match = c("345" = "SRB", "347" = "XKK", "678" = "YEM")),
+           # Use 999 as the UN country code for Kosovo
[…]

### 2021-03-27 R/funs_knitting.R

@@ -1,0 +1,80 @@
+render_html <- function(input, output, csl) {
+  # Add CSS file as a dependency so it goes into the _files directory
+  dep <- htmltools::htmlDependency(
+    name = "ath",
+    version = "1.0.0",
+    "pandoc/css",
+    stylesheet = "ath-clean.css"
+  )
+  extra_dependencies <- list(dep)
+
+  rmarkdown::render(
+    input = input,
+    output_file = output,
+    bookdown::html_document2(
+      template = "pandoc/templates/html.html",
+      pandoc_args = c("--metadata", "link-citations=true",
+                      "--metadata", "linkReferences=true",
+                      paste0("--csl=", csl)),
+      md_extensions = "+raw_tex+smart-autolink_bare_uris+ascii_identifiers",
+      toc = TRUE,
+      number_sections = FALSE,
+      self_contained = FALSE,
+      theme = NULL,
+      extra_dependencies = extra_dependencies
+    )
+  )
+}
+
+render_pdf <- function(input, output, bibstyle) {
+  rmarkdown::render(
+    input = input,
+    output_file = output,
+    bookdown::pdf_document2(
+      template = "pandoc/templates/xelatex.tex",
+      latex_engine = "xelatex",
+      dev = "cairo_pdf",
+      pandoc_args = c("--top-level-division=section",
+                      "--shift-heading-level-by=0",
+                      "-V", bibstyle,
+                      "-V", "chapterstyle=hikma-article"),
+      md_extensions = "+raw_tex+smart-autolink_bare_uris",
+      toc = FALSE,
+      keep_tex = FALSE,
+      citation_package = "biblatex"
+    )
+  )
+}
+
+render_pdf_ms <- function(input, output, bibstyle) {
+  rmarkdown::render(
+    input = input,
+    output_file = output,
+    bookdown::pdf_document2(
+      template = "pandoc/templates/xelatex-manuscript.tex",
+      latex_engine = "xelatex",
+      dev = "cairo_pdf",
+      pandoc_args = c("--top-level-division=section",
+                      "--shift-heading-level-by=0",
+                      "-V", bibstyle),
+      md_extensions = "+raw_tex+smart-autolink_bare_uris",
+      toc = FALSE,
+      keep_tex = FALSE,
+      citation_package = "biblatex"
+    )
+  )
+}
+
+render_docx <- function(input, output, csl) {
+  rmarkdown::render(
+    input = input,
[…]

### 2021-03-27 R/funs_notebook.R

@@ -1,0 +1,84 @@
+# This is adapted from TJ Mahr's {notestar}
+# (https://github.com/tjmahr/notestar/blob/main/R/tar-notebook.R).
+#
+# He did all the hard work figuring out how to dynamically generate targets
+# based on a bunch of files, while also checking for targets dependencies with
+# tarchetypes::tar_knitr_deps(), based on this issue in {tarchetypes}:
+# https://github.com/ropensci/tarchetypes/issues/23
+#
+# I just adapted it for an R Markdown website
+
+notebook_rmd_collate <- function(dir_notebook = "analysis") {
+  index <- file.path(dir_notebook, "index.Rmd")
+  posts <- list.files(
+    path = dir_notebook,
+    pattern = "\\d.+.Rmd",
+    full.names = TRUE
+  )
+  c(index, posts)
+}
+
+rmd_to_html <- function(x) gsub("[.]Rmd$", ".html", x = x)
+html_to_rmd <- function(x) gsub("[.]html$", ".Rmd", x = x)
+
+lazy_list <- function(...) {
+  q <- rlang::enexprs(..., .named = TRUE, .check_assign = TRUE)
+  data <- list()
+  for (x in seq_along(q)) {
+    data[names(q[x])] <- list(rlang::eval_tidy(q[[x]], data = data))
+  }
+  data
+}
+
+knit_notebook_page <- function(rmd_in, html_out) {
+  rmarkdown::render_site(rmd_in, encoding = "UTF-8")
+  html_out
+}
+
+tar_notebook_pages <- function(
+  dir_notebook = "analysis",
+  dir_html = "analysis/_site",
+  yaml_config = "analysis/_site.yml"
+) {
+
+  rmds <- notebook_rmd_collate(dir_notebook)
+
+  values <- lazy_list(
+    rmd_file = !! rmds,
+    rmd_page = basename(.data$rmd_file),
+    sym_rmd_page = rlang::syms(.data$rmd_page),
+    rmd_deps = lapply(.data$rmd_file, tarchetypes::tar_knitr_deps_expr),
+    html_page = rmd_to_html(.data$rmd_page),
+    html_file = file.path(!! dir_html, .data$html_page)
+  )
+
+  list(
+    # Add _site.yml as a dependency
+    # Have to use tar_target_raw() instead of tar_target() so that yaml_config is usable
+    tar_target_raw("site_yml", yaml_config, format = "file"),
+
[…]

### 2021-03-27 _targets.R

@@ -1,0 +1,119 @@
+library(targets)
+library(tarchetypes)
+
+# General variables
+csl <- "pandoc/csl/apa.csl"
+bibstyle <- "bibstyle-chicago-authordate"
+
+source("R/funs_data-cleaning.R")
+# source("R/funs_knitting.R")
+source("R/funs_notebook.R")
+
+options(tidyverse.quiet = TRUE,
+        dplyr.summarise.inform = FALSE)
+
+future::plan(future::multisession)
+
+tar_option_set(packages = c("tidyverse", "countrycode", "states", "WDI", "here",
+                            "readxl", "haven", "sf", "lubridate", "scales", "naniar",
+                            "janitor", "kableExtra", "huxtable", "modelsummary",
+                            "knitr", "withr", "flextable", "testthat", "DT",
+                            "brms", "tidybayes", "broom", "broom.mixed", "scico",
+                            "ggtext", "GGally", "colorspace", "lme4"))
+
+list(
+  # Define raw data files
+  tar_target(chaudhry_raw_file,
+             here("data", "raw_data", "Chaudhry restrictions", "SC_Expanded.dta"),
+             format = "file"),
+  tar_target(pts_raw_file,
+             here("data", "raw_data", "Political Terror Scale", "PTS-2019.RData"),
+             format = "file"),
+  tar_target(journalists_raw_file,
+             here("data", "raw_data", "Gohdes Carey journalists",
+                  "journalist-data-incl-pts.RData"),
+             format = "file"),
+  tar_target(ucdp_raw_file,
+             here("data", "raw_data", "UCDP PRIO", "ucdp-prio-acd-191.csv"),
+             format = "file"),
+  tar_target(vdem_raw_file,
+             here("data", "raw_data", "Country_Year_V-Dem_Full+others_R_v10",
+                  "V-Dem-CY-Full+Others-v10.rds"),
+             format = "file"),
+  tar_target(un_pop_raw_file,
+             here("data", "raw_data", "UN data",
+                  "WPP2019_POP_F01_1_TOTAL_POPULATION_BOTH_SEXES.xlsx"),
+             format = "file"),
+  tar_target(un_gdp_constant_raw_file,
+             here("data", "raw_data", "UN data",
+                  "UNdata_Export_20210118_034054729.csv"),
+             format = "file"),
+  tar_target(un_gdp_current_raw_file,
+             here("data", "raw_data", "UN data",
+                  "UNdata_Export_20210118_034311252.csv"),
[…]

### 2021-03-27 _packages.R
{renv}ification

@@ -1,0 +1,40 @@
+# Generated by targets::tar_renv(): do not edit by hand
+library(brms)
+library(broom)
+library(broom.mixed)
+library(bs4Dash)
+library(clustermq)
+library(colorspace)
+library(countrycode)
+library(DT)
+library(flextable)
+library(future)
+library(GGally)
+library(ggtext)
+library(gt)
+library(haven)
+library(here)
+library(huxtable)
+library(janitor)
+library(kableExtra)
+library(knitr)
+library(lme4)
+library(lubridate)
+library(modelsummary)
+library(naniar)
+library(pingr)
+library(readxl)
+library(rstudioapi)
+library(scales)
+library(scico)
+library(sf)
+library(shiny)
+library(shinycssloaders)
+library(shinyWidgets)
+library(states)
+library(testthat)
+library(tidybayes)
+library(tidyverse)
+library(visNetwork)
+library(WDI)
+library(withr)

### 2021-03-27 manuscript/manuscript.Rmd
Suparna additions

@@
 
-Governments across the globe have been cracking down on civil society organizations (CSOs) -- a phenomenon referred to as closing civic space in policy arena.
-The non-violent nature of this repression is particularly notable.The last two decades have
-seen a proliferation of laws designed to limit the influence of civil society organizations,
-with more than 100 countries obstructing, repressing, or closing the legal
-environment for civil society have required that funds
-to NGOs be routed through state-owned banks, mandated that funds cannot be used
-for political purposes, or prohibited NGOs from accepting any funds from foreign
-sources (Carothers, DPR, Chaudhry, Heiss)
+Governments across the globe have been cracking down on civil society organizations (CSOs) -- a phenomenon referred to as closing civic space or shrinking civic space (CITE).
+The non-violent nature of this repression is particularly notable.
+The last two decades have seen a proliferation of laws designed to limit the influence of civil society organizations, with more than 100 countries obstructing, repressing, or closing the legal environment for civil society.
+Since 2013, 91 countries had proposed or enacted 244 measures restricting civil society [@icnl:2021].
+In Human Rights Watch's 2016 World Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory, and over the past decade, the majority of the world has seen a substantial narrowing of allowable civic space.
+As seen in Figure \@ref(fig:civicus-map), by the end of 2020, only `r civicus$Open$prop_nice` of countries had open and unrestricted civil societies [@civicusmonitor; @ChaudhryHeiss:2021].
 
-As someone points out, states have toned down 'open, violent confrontation' and favor the development of a 'civilized' oppression.
-The use of legal tools instead of violent repression means that NGOs have to  their practices to stay within the bounds of permitted activities and operations.
-This has led to depoliticization, avoidance of direct political activism.
-But that state cannot soften or neutralize all forms of political activities in subtle, legal ways that they have with NGOs.
+WHAT KINDS OF LAWS, WHAT DO THESE LAWS DO.
+
+The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations.
+While in some cases this has led to the depoliticization of NGOs and avoidance of direct political activism by CSOs, states cannot soften or neutralize all forms of political activities in subtle, legal ways that they have with NGOs.
 Soon or later, states need to deal with threats in a more violent, confrontational manner.
-Studying these NGO laws can thus be the canary in the coal mine which signals the states that intend to continue down this repressive path, especially in their short to medium term trajectories.
-
-What does their targeting tell us about a state's broader respect for civil society and the overall level of human rights repression?
+Studying these NGO laws can thus be the canary in the coal mine which signals the states that intend to continue down this repressive path.
+What does state targeting of NGOs tell us about a state's broader respect for civil society and the overall level of human rights repression?
 Can the crackdown on NGOs act as an indicator for subsequent increasing repression?
 
-Information about crackdown can be a valuable indicator of human rights trajectories.
-Can act as an early warning signal for worsening repression, suggesting which countries are testing the waters with comparatively 'milder' forms of repression before enacting more violent forms of crackdown.
+ARGUMENT, METHODS, AND FINDINGS. 
+In this paper, we argue that information about NGO crackdown can be a valuable indicator of human rights trajectories.
+Such crackdown can act as an early warning signal for worsening repression, suggesting which countries are testing the waters with comparatively 'milder' forms of repression before enacting more violent forms of crackdown.
+To assess if attacks on NGOs and activists can provide us useful information about future repression, we use an original dataset on state crackdown on NGOs using legal repression across all countries from 1990-2013.
+WHAT ELSE DO WE USE.
+Our analysis shows FILL
 
-Structural factors such as levels of democracy, economic development, electoral competitiveness can identify countries that are likely to have more or less respect for civic freedoms, but these factors are also slow to change over time.
-Thus, they may not be particularly suitable for forecasting short-term trajectories, especially for moderatively repressive countries.
+Our paper makes an important contribution in predicting (IS THIS THE RIGHT WORD) the onset of repressive state policies.
+While structural factors such as levels of democracy, economic development, electoral competitiveness can identify countries that are likely to have more or less respect for civic freedoms, these factors are also slow to change over time.
+As such, they may not be particularly suitable for forecasting short-term trajectories, especially for moderatively repressive countries.
+On the other hand, state repression of NGOs is more dynamic and provides information about changing levels of human rights standards and repression in subsequent years.
+
+ROADMAP
 
@@
 
-Why we look as NGOs
-From an economic perspective, the foreign aid community prefers NGOs since
-they overcome many failures associated with channeling funds through the state
-(Dietrich 2013). They provide services to large parts of the population in the Global
-South, especially where governments are unable to do so on a consistent basis.
+Repression is the use of coercive action against an individual or organization, within the territorial jurisdiction of the state, for the purpose of imposing a cost on the target as well as deterring specific activities and/or beliefs perceived to be challenging to government personnel, practices, or institutions (Goldstein 1978, xxvii; Poe and Tate 1994; Davenport 2007b; and Ritter and Conrad 2016).
 
-## Structural factors explaining repression
+One part of the existing literature focuses on the role of structural factors such as levels of democracy, economic development, electoral competitiveness in predisposing a state to increased use of repression.
+Most notably, both democracies and democratization is found to have a pacifying effect on state repression (Davenport and Armstrong 2004, Krain 1997, Richards 1999).
+Democracies are found to have a negative effect on repression largely because of the increased probability of sanctions against authorities for undesirable behavior (Davenport 2007, 41).
 
-## Exploring non-violent forms of repression
+Another strand of research focuses on how the behavior of various actors shapes government response.
+One of the most consistent findings in the political violence literature is that authorities repress to counter ongoing challenges to the status quo.
+In other words, dissent increases repressive behavior (Davenport 2007).
+However, dissent and repression have an endogenous relationship - state authorities also frequently engage in preventive repression to undermine or restrict groups’ abilities to dissent (Ritter and Conrad 2016; and Conrad and Ritter 2019.) In addition to attacking groups’ willingness to organize against states, such
+preventive repression also damages their capacity to impose costs (Davenport 2007a, 47.)
+
+NGOs are one actor that can pose challenges to political authorities, and state repression of these actors, especially through legal restrictions or administrative crackdown can also be considered a form of preventive repression.
+Below, we explore why government repress NGOs, especially through subtle, legal means.
+
+## State repression of NGOs
+
+A robust, strong civil society is widely considered as an important component on democratic transition and consolidation (Putnam).
+Politically, as important civil society actors, NGOs enable citizens to voice their grievances, seek redress, and carry out lobbying and advocacy activities to further their interests.
+They help keep government accountable, monitor human rights violations and corruption.
+From an economic perspective, NGOs provide services when the state falls short.
+
+As a result of these roles, NGOs can wield real influence, which can be threatening to states.
+State crackdown on NGOs has become pervasive as these organizations have the ability to influence electoral politics (Dupuy, Ron, and Prakash 2016, Weiss 2009), aid mobilization (Murdie and Bhasin 2011; Bell et al.
+2013; and Boulding 2014), and threaten a state’s economic interests (Dietrich and Murdie 2017; Lebovic and Voeten 2009; and Nielsen 2013.).
+
 Why might repressive states start with non-violent forms of repression?
+WHY THE GROWTH IN THESE LAWS
+As someone points out, states have toned down 'open, violent confrontation' and favor the development of a 'civilized' oppression.
 
-# State repression of NGOs
-
-A robust, strong civil society is widely considered as an important component on democratic transition and consolidation.
-Accountability
-Corruption
-Monitoring
-In addition, services when the state falls short
 Leaders want to avoid accountability. Shape the narrative of their performance both domestically and internationally. Don't like being shamed.
@@
 The government also imprisoned an increasing number of journalists in 2017 and 2018, and issued arrest warrants for numerous academics in 2018.
+
+##Expectations
+
+#Methods
+
+#Results and Analysis
+
+#Conclusion and Implications

### 2021-04-02 analysis/01_data-overview.Rmd
Run all models and predictions!

@@
 
-  tar_load(panel_done_trimmed)
+  tar_load(panel)
 })
@@
 
-We have `r panel_done_trimmed %>% distinct(gwcode) %>% nrow()` countries in this data, spanning `r panel_done_trimmed %>% distinct(year) %>% nrow()` possible years.
-Here's a lookup table of all the countries included:
+We have `r panel %>% distinct(gwcode) %>% nrow()` countries in this data, spanning `r panel %>% distinct(year) %>% nrow()` possible years. Here's a lookup table of all the countries included:
 
@@
   - Political civil liberties index: `v2x_clpol`
-- **Democracy**
-  - Polyarchy index: `v2x_polyarchy`
-  - Regimes of the world category: `v2x_regime_amb`
+- **Democracy and governance stuff**
+  - Polyarchy index (for electoral democracies): `v2x_polyarchy`
+  - Liberal democracy index (for democracies in general): `v2x_libdem`
+  - Regimes of the world category: `v2x_regime`
+  - Political corruption index: `v2x_corr` (less to more, 0-1) (public sector + executive + legislative + judicial corruption)
+  - Rule of law index: `v2x_rule`
 
@@
 ```{r glimpse-combined}
-glimpse(panel_done_trimmed)
+glimpse(panel)
 ```
@@
 ```{r show-country-years-summary}
-panel_done_trimmed %>% 
+panel %>% 
   summarize(`Number of countries` = length(unique(gwcode)),
@@
 ```{r show-country-year-count}
-panel_done_trimmed %>% 
+panel %>% 
   count(Year = year, name = "Number of countries") %>% 
@@
 ```{r plot-missing}
-panel_done_trimmed %>% 
+panel %>% 
   vis_miss() +
@@
 ```{r show-missing-rows, class.source="fold-show"}
-panel_done_trimmed %>% 
+panel %>% 
   filter(is.na(advocacy)) %>% 
@@
 ```{r show-missing-pts, class.source="fold-show"}
-panel_done_trimmed %>% 
+panel %>% 
   filter(is.na(PTS)) %>% 
@@
 ```{r plot-missing-laws}
-panel_done_trimmed %>% 
+panel %>% 
   filter(laws) %>% 

### 2021-04-02 analysis/02_descriptive-analysis.Rmd
Run all models and predictions!

@@
 
-  canary <- tar_read(panel_done_trimmed)
+  canary <- tar_read(panel)
   tar_load(world_map)
@@
 things_to_map <- canary %>% 
-  filter(year %in% c(2000, 2014)) %>% 
+  filter(year %in% c(1990, 2013)) %>% 
   select(country, year, iso3, barriers_total, PTS_factor, v2csreprss) %>% 
   pivot_wider(names_from = year, values_from = c(barriers_total, PTS_factor, v2csreprss)) %>% 
-  mutate(new_laws = barriers_total_2014 - barriers_total_2000,
+  mutate(new_laws = barriers_total_2013 - barriers_total_1990,
          new_laws = ifelse(new_laws <= 0, 0, new_laws),
          new_laws = ceiling(new_laws)) %>% 
-  mutate(diff_csrepress = v2csreprss_2014 - v2csreprss_2000,
+  mutate(diff_csrepress = v2csreprss_2013 - v2csreprss_1990,
          diff_csrepress_trunc = case_when(
@@
          )) %>% 
-  mutate(pct_change_csrepress = diff_csrepress / v2csreprss_2000,
+  mutate(pct_change_csrepress = diff_csrepress / v2csreprss_1990,
          pct_change_csrepress_trunc = case_when(
@@
   coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
-  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 7)), 
+  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 8)), 
                     na.value = "grey80", breaks = 0:6) +
@@
                              keyheight = unit(0.6, units = "lines"))) +
-  labs(fill = "Restrictive NGO laws passed between 2000 and 2014") +
+  labs(fill = "Restrictive NGO laws passed between 1990 and 2014") +
   theme_ngo() +
@@
                    breaks = seq(-4, 4, 1), na.value = "grey80") +
-  guides(fill = guide_colorbar(reverse = TRUE, ticks = FALSE,
+  guides(fill = guide_colorbar(reverse = FALSE, ticks = FALSE,
                                barwidth = unit(7, units = "lines"),
                                barheight = unit(0.5, units = "lines"))) +
-  labs(fill = "Change in V-Dem civil society repression between 2000 and 2014") +
+  labs(fill = "Change in V-Dem civil society repression between 1990 and 2013") +
   theme_ngo() +
@@
 ```
-
-# Civil society restrictions and other kinds of repression
-
-```{r repression-matrix, fig.width=12, fig.height=12, warning=FALSE, message=FALSE}
-library(GGally)
-repression_only <- canary %>% 
-  filter(year == 2014) %>% 
-  select(barriers_total, PTS, gh_alljourn, 
-         v2clacfree, v2csrlgrep, v2mecenefm, v2meharjrn, v2meslfcen,
-         v2x_clphy, v2x_clpol, v2x_clpriv, v2x_freexp, v2csreprss)
-
-ggscatmat(repression_only, alpha = 0.4) + 
-  theme_ngo(base_size = 6)
-```

### 2021-04-02 analysis/03_environment-repression.Rmd
Run all models and predictions!

---
title: "E~2~: Civil society environment predicts deteriorating human rights"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knit_print.data.frame <- function(x, ...) {
  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
  asis_output(res)
}

registerS3method("knit_print", "data.frame", knit_print.data.frame)
registerS3method("knit_print", "grouped_df", knit_print.data.frame)

knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "85%")

options(dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(broom.mixed)
library(tidybayes)
library(glue)
library(brms)
library(scales)
library(kableExtra)
library(modelsummary)
library(here)

# Generated via random.org
set.seed(9936)

# Load data and models
withr::with_dir(here::here(), {
  source(tar_read(plot_funs))

  # Load big list of models
  model_df <- tar_read(model_df) %>% 
    filter(str_detect(model, "baseline") | str_detect(model, "v2csreprss"))

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_v2csreprss, 
             m_pts_baseline_rewb, m_pts_v2csreprss_rewb, 
             m_clphy_baseline, m_clphy_v2csreprss, 
             m_clphy_baseline_rewb, m_clphy_v2csreprss_rewb, 
             m_clpriv_baseline, m_clpriv_v2csreprss, 
             m_clpriv_baseline_rewb, m_clpriv_v2csreprss_rewb))

  # Load regression tables
  tar_load(c(models_tbl_e2a, models_tbl_e2b, models_tbl_e2c))

  # Load lookup list for coefficients in regression tables
  tar_load(coef_list)
})
```

```{r clean-data, message=FALSE, warning=FALSE}
models <- model_df %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))

coefs_clean <- tribble(
  ~coef, ~coef_clean,
  "b_v2csreprss", "Civil society repression",
  "b_v2csreprss_lag1", "Civil society repression (t - 1)",
  "b_v2csreprss_within", "Civil society repression (within)",
  "b_v2csreprss_lag1_within", "Civil society repression (within; t - 1)"
) %>% 
  mutate(across(everything(), ~fct_inorder(., ordered = TRUE))) %>% 
  mutate(lagging = str_detect(coef, "lag1"))
```

# E~2a~: Civil society environment and political terror

## Results table

```{r tbl-e2a}
# Build nicer column names
models_for_table_e2a <- models %>% 
  filter(outcome_var == "Political terror") %>% 
  mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
         explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

# Make a named vector of original model names and nice names
model_names_tbl_e2a <- models_for_table_e2a %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e2a$model)

# Rename the columns
names(models_tbl_e2a) <- recode(names(models_tbl_e2a), !!!model_names_tbl_e2a)

modelsummary(models_tbl_e2a,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

## Coefficients

```{r plot-coefs-e2a}
coef_plots <- models %>% 
  filter(str_detect(model, "m_pts_v2csreprss")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 1, scales = "free_y") +
  theme_ngo()
```

## Marginal effects

```{r plot-mfx-e2a}
mfx <- models %>% 
  filter(str_detect(model, "m_pts_v2csreprss")) %>% 
  mutate(plot_vars = case_when(
    re == "RE" ~ "v2csreprss",
    re == "REWB" ~ "v2csreprss_within"
  )) %>% 
  mutate(fx = map2(actual_model, plot_vars, 
                   ~conditional_effects(.x, effects = .y,
                                        categorical = TRUE)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  filter(model == "m_pts_v2csreprss") %>% 
  ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, color = NA) +
  geom_line(size = 1) +
  labs(x = "Civil society repression\n(higher values = less repression)",
       y = "Predicted probability of category",
       color = "Political terror scale", fill = "Political terror scale") +
  theme_ngo()

mfx %>% 
  filter(model == "m_pts_v2csreprss_rewb") %>% 
  ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, color = NA) +
  geom_line(size = 1) +
  labs(x = "Difference from average level of civil society repression\n(higher values = less repression)",
       y = "Predicted probability of category",
       color = "Political terror scale", fill = "Political terror scale") +
  theme_ngo()
```

\

# E~2b~: Civil society environment and physical violence

## Results table

```{r tbl-e2b}
# Build nicer column names
models_for_table_e2b <- models %>% 
  filter(outcome_var == "Physical violence") %>% 
  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

# Make a named vector of original model names and nice names
model_names_tbl_e2b <- models_for_table_e2b %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e2b$model)

# Rename the columns
names(models_tbl_e2b) <- recode(names(models_tbl_e2b), !!!model_names_tbl_e2b)

modelsummary(models_tbl_e2b,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

## Coefficients

```{r plot-coefs-e2b}
coef_plots <- models %>% 
  filter(str_detect(model, "m_clphy_v2csreprss")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 1, scales = "free_y") +
  theme_ngo()
```

## Marginal effects

```{r plot-mfx-e2b}
mfx <- models %>% 
  filter(str_detect(model, "m_clphy_v2csreprss")) %>% 
  mutate(plot_vars = case_when(
    re == "RE" ~ "v2csreprss",
    re == "REWB" ~ "v2csreprss_within"
  )) %>% 
  mutate(fx = map2(actual_model, plot_vars, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  filter(model == "m_clphy_v2csreprss") %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#FF4136", color = NA) +
  geom_line(size = 1, color = "#FF4136") +
  labs(x = "Civil society repression\n(higher values = less repression)",
       y = "Predicted physical violence index\n(higher values = less violence)") +
  theme_ngo()

mfx %>% 
  filter(model == "m_clphy_v2csreprss_rewb") %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#FF4136", color = NA) +
  geom_line(size = 1, color = "#FF4136") +
  labs(x = "Difference from average level of civil society repression\n(higher values = less repression)",
       y = "Predicted physical violence index\n(higher values = less violence)") +
  theme_ngo()
```

\

# E~2c~: Civil society environment and civil liberties

```{r tbl-e2c}
# Build nicer column names
models_for_table_e2c <- models %>% 
  filter(outcome_var == "Private civil liberties") %>% 
  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

# Make a named vector of original model names and nice names
model_names_tbl_e2c <- models_for_table_e2c %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e2c$model)

# Rename the columns
names(models_tbl_e2c) <- recode(names(models_tbl_e2c), !!!model_names_tbl_e2c)

modelsummary(models_tbl_e2c,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

## Coefficients

```{r plot-coefs-e2c}
coef_plots <- models %>% 
  filter(str_detect(model, "m_clpriv_v2csreprss")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 1, scales = "free_y") +
  theme_ngo()
```

## Marginal effects

```{r plot-mfx-e2c}
mfx <- models %>% 
  filter(str_detect(model, "m_clpriv_v2csreprss")) %>% 
  mutate(plot_vars = case_when(
    re == "RE" ~ "v2csreprss",
    re == "REWB" ~ "v2csreprss_within"
  )) %>% 
  mutate(fx = map2(actual_model, plot_vars, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  filter(model == "m_clpriv_v2csreprss") %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#FF4136", color = NA) +
  geom_line(size = 1, color = "#FF4136") +
  labs(x = "Civil society repression\n(higher values = less repression)",
       y = "Predicted civil liberties index\n(higher values = less violence)") +
  theme_ngo()

mfx %>% 
  filter(model == "m_clpriv_v2csreprss_rewb") %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#FF4136", color = NA) +
  geom_line(size = 1, color = "#FF4136") +
  labs(x = "Difference from average level of civil society repression\n(higher values = less repression)",
       y = "Predicted civil liberties index\n(higher values = less violence)") +
  theme_ngo()
```

### 2021-04-02 analysis/03_laws-repression.Rmd
Run all models and predictions!

---
title: "E~1~: Laws predict deteriorating human rights"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knit_print.data.frame <- function(x, ...) {
  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
  asis_output(res)
}

registerS3method("knit_print", "data.frame", knit_print.data.frame)
registerS3method("knit_print", "grouped_df", knit_print.data.frame)

knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "85%")

options(dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(broom.mixed)
library(tidybayes)
library(glue)
library(brms)
library(scales)
library(kableExtra)
library(modelsummary)
library(lubridate)
library(here)

# Generated via random.org
set.seed(9936)

# Load data and models
withr::with_dir(here::here(), {
  source(tar_read(plot_funs))

  # Load big list of models
  model_df <- tar_read(model_df) %>% 
    filter(!str_detect(model, "v2csreprss"))

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_pts_baseline_rewb, m_pts_total_rewb, m_pts_advocacy_rewb, m_pts_entry_rewb, m_pts_funding_rewb, 
             m_clphy_baseline, m_clphy_total, m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
             m_clphy_baseline_rewb, m_clphy_total_rewb, m_clphy_advocacy_rewb, m_clphy_entry_rewb, m_clphy_funding_rewb, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
             m_clpriv_baseline_rewb, m_clpriv_total_rewb, m_clpriv_advocacy_rewb, m_clpriv_entry_rewb, m_clpriv_funding_rewb))

  # Load regression tables
  tar_load(c(models_tbl_e1a_re, models_tbl_e1a_rewb, 
             models_tbl_e1b_re, models_tbl_e1c_re))

  # Load lookup list for coefficients in regression tables
  tar_load(coef_list)
})
```

```{r clean-data}
models <- model_df %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))

coefs_clean <- tribble(
  ~coef, ~coef_clean,
  "b_barriers_total", "Total legal barriers",
  "b_barriers_total_lag1", "Total legal barriers (t - 1)",
  "b_advocacy", "Barriers to advocacy",
  "b_advocacy_lag1", "Barriers to advocacy (t - 1)",
  "b_entry", "Barriers to entry",
  "b_entry_lag1", "Barriers to entry (t - 1)",
  "b_funding", "Barriers to funding",
  "b_funding_lag1", "Barriers to funding (t - 1)",
  "b_barriers_total_within", "Total legal barriers (within)",
  "b_barriers_total_lag1_within", "Total legal barriers (within; t - 1)",
  "b_advocacy_within", "Barriers to advocacy (within)",
  "b_advocacy_lag1_within", "Barriers to advocacy (within; t - 1)",
  "b_entry_within", "Barriers to entry (within)",
  "b_entry_lag1_within", "Barriers to entry (within; t - 1)",
  "b_funding_within", "Barriers to funding (within)",
  "b_funding_lag1_within", "Barriers to funding (within; t - 1)"
) %>% 
  mutate(across(everything(), ~fct_inorder(., ordered = TRUE))) %>% 
  mutate(lagging = str_detect(coef, "lag1"))
```

# Confounders

Time-varying:

- `v2x_polyarchy`
- GDP_log
- population_log
- armed_conflict
- un_trade_pct_gdp

# E~1a~: NGO laws and political terror

## Results table

```{r tbl-e1a-re}
# Build nicer column names
models_for_table_e1a_re <- models %>% 
  filter(outcome_var == "Political terror", re == "RE") %>% 
  mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
         explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

# Make a named vector of original model names and nice names
models_names_table_e1a_re <- models_for_table_e1a_re %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1a_re$model)

# Rename the columns
names(models_tbl_e1a_re) <- recode(names(models_tbl_e1a_re), 
                                   !!!models_names_table_e1a_re)

modelsummary(models_tbl_e1a_re,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

```{r tbl-e1a-rewb}
models_for_table_e1a_rewb <- models %>% 
  filter(outcome_var == "Political terror", re == "REWB") %>% 
  mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
         explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

models_names_table_e1a_rewb <- models_for_table_e1a_rewb %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1a_rewb$model)

names(models_tbl_e1a_rewb) <- recode(names(models_tbl_e1a_rewb), 
                                     !!!models_names_table_e1a_rewb)

modelsummary(models_tbl_e1a_rewb,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

## Coefficients

```{r plot-coefs-e1a}
coef_plots <- models %>% 
  filter(str_detect(model, "pts_"), !str_detect(model, "baseline")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 2, scales = "free_y") +
  theme_ngo()
```

## Marginal effects

```{r plot-mfx-e1a}
plot_pts_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_pts_total", "barriers_total", "Total legal barriers",
  "m_pts_advocacy", "advocacy", "Barriers to advocacy",
  "m_pts_entry", "entry", "Barriers to entry",
  "m_pts_funding", "funding", "Barriers to funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

mfx <- models %>% 
  filter(str_detect(model, "_pts"), !str_detect(model, "rewb|baseline")) %>% 
  left_join(plot_pts_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y,
                                        categorical = TRUE)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, effect2__, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = effect2__)) +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  position = position_dodge(width = 0.2),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_color_viridis_d(option = "viridis", end = 0.95) +
  labs(x = "Count of legal barriers\n",
       y = "Predicted probability of category",
       color = "Political terror scale", fill = "Political terror scale") + 
  facet_wrap(vars(plot_var_nice), scales = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

\

# E~1b~: NGO laws and physical violence

## Results table

```{r tbl-e1b-re}
models_for_table_e1b_re <- models %>% 
  filter(outcome_var == "Physical violence", re == "RE") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

model_names_tbl_e1b_re <- models_for_table_e1b_re %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1b_re$model)

names(models_tbl_e1b_re) <- recode(names(models_tbl_e1b_re), 
                                   !!!model_names_tbl_e1b_re)

modelsummary(models_tbl_e1b_re,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

## Coefficients

```{r plot-coefs-e1b}
coef_plots <- models %>% 
  filter(str_detect(model, "clphy"), !str_detect(model, "baseline")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 2, scales = "free_y") +
  theme_ngo()
```

## Marginal effects

```{r plot-mfx-e1b}
plot_clphy_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_clphy_total", "barriers_total", "Total legal barriers",
  "m_clphy_advocacy", "advocacy", "Advocacy",
  "m_clphy_entry", "entry", "Entry",
  "m_clphy_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

mfx <- models %>% 
  filter(str_detect(model, "clphy"), !str_detect(model, "rewb|baseline")) %>% 
  left_join(plot_clphy_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted physical violence index\n(higher values = less violence)") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

\

# E~1c~: NGO laws and civil liberties

## Results table

```{r tbl-e1c-re}
models_for_table_e1c_re <- models %>% 
  filter(outcome_var == "Private civil liberties", re == "RE") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

model_names_tbl_e1c_re <- models_for_table_e1c_re %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1c_re$model)

names(models_tbl_e1c_re) <- recode(names(models_tbl_e1c_re), 
                                   !!!model_names_tbl_e1c_re)

modelsummary(models_tbl_e1c_re,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

## Coefficients

```{r plot-coefs-e1c}
coef_plots <- models %>% 
  filter(str_detect(model, "clpriv"), !str_detect(model, "baseline")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

coef_plots %>% 
  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  guides(fill = FALSE, alpha = FALSE) +
  scale_alpha_manual(values = c(1, 0.4)) +
  labs(x = "Coefficient", y = NULL) +
  facet_wrap(vars(re_fancy), ncol = 2, scales = "free_y") +
  theme_ngo()
```

## Marginal effects

```{r plot-mfx-e1c}
plot_clpriv_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_clpriv_total", "barriers_total", "Total legal barriers",
  "m_clpriv_advocacy", "advocacy", "Advocacy",
  "m_clpriv_entry", "entry", "Entry",
  "m_clpriv_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

mfx <- models %>% 
  filter(str_detect(model, "clpriv"), !str_detect(model, "rewb|baseline")) %>% 
  left_join(plot_clpriv_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted civil liberties index\n(higher values = less violence)") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

### 2021-04-02 analysis/03_model-details.Rmd
Run all models and predictions!

---
title: "Model details and diagnostics"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knit_print.data.frame <- function(x, ...) {
  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
  asis_output(res)
}

registerS3method("knit_print", "data.frame", knit_print.data.frame)
registerS3method("knit_print", "grouped_df", knit_print.data.frame)

knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "85%")

options(dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(broom.mixed)
library(tidybayes)
library(glue)
library(brms)
library(scales)
library(kableExtra)
library(modelsummary)
library(lubridate)
library(here)

# Generated via random.org
set.seed(9936)

# Load models
withr::with_dir(here::here(), {
  source(tar_read(plot_funs))

  # Load big list of models
  tar_load(model_df)

  # Load actual model objects
  # This works, but doesn't put the models in the dependency network for some reason
  # tar_load(model_df$model)

  # This also works but again doesn't register correctly as dependencies
  # tar_load(starts_with("m_clpriv"))

  # So we do it this manual way
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_advocacy, 
             m_pts_entry, m_pts_funding, m_pts_v2csreprss, 
             m_pts_baseline_rewb, m_pts_total_rewb, m_pts_advocacy_rewb, 
             m_pts_entry_rewb, m_pts_funding_rewb, m_pts_v2csreprss_rewb, 
             m_clphy_baseline, m_clphy_total, m_clphy_advocacy, 
             m_clphy_entry, m_clphy_funding, m_clphy_v2csreprss, 
             m_clphy_baseline_rewb, m_clphy_total_rewb, m_clphy_advocacy_rewb, 
             m_clphy_entry_rewb, m_clphy_funding_rewb, m_clphy_v2csreprss_rewb, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_advocacy, 
             m_clpriv_entry, m_clpriv_funding, m_clpriv_v2csreprss, 
             m_clpriv_baseline_rewb, m_clpriv_total_rewb, m_clpriv_advocacy_rewb, 
             m_clpriv_entry_rewb, m_clpriv_funding_rewb, m_clpriv_v2csreprss_rewb))
})
```

# Model run times

## Models for E~1~ (civil society laws)

```{r running-time-e1}
models_e1 <- model_df %>% 
  filter(!str_detect(model, "v2csreprss")) %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))

model_time_e1 <- models_e1 %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

total_row_e1 <- tibble(Outcome = "Total", 
                       `Total time (i.e. longest chain)` = 
                         as.duration(sum(model_time_e1$`Total time (i.e. longest chain)`)))

model_time_e1 <- model_time_e1 %>% 
  bind_rows(total_row_e1)

model_time_e1 %>% 
  select(-Outcome) %>% 
  kbl(escape = FALSE) %>% 
  pack_rows(index = table(fct_inorder(model_time_e1$Outcome))) %>% 
  kable_styling()
```

## Models for E~2~ (civil society environment)

```{r running-time-e2}
models_e2 <- model_df %>% 
  filter(str_detect(model, "baseline") | str_detect(model, "v2csreprss")) %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))

model_time_e2 <- models_e2 %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

total_row_e2 <- tibble(Outcome = "Total", 
                       `Total time (i.e. longest chain)` = 
                         as.duration(sum(model_time_e2$`Total time (i.e. longest chain)`)))

model_time_e2 <- model_time_e2 %>% 
  bind_rows(total_row_e2)

model_time_e2 %>% 
  select(-Outcome) %>% 
  kbl(escape = FALSE) %>% 
  pack_rows(index = table(fct_inorder(model_time_e2$Outcome))) %>% 
  kable_styling()
```

\

# Actual code

All the models are run with a **`targets`** pipeline with dataset-specific functions that live in these files:

- `R/models_pts.R` (for PTS-based models)
- `R/models_clphy.R` (for V-Dem physical violence-based models)
- `R/models_clpriv.R` (for V-Dem private civil liberties-based models)

To keep the analysis relatively self contained here in the analysis notebook, and to make it so there's no need to hunt through the GitHub repository to find the actual code, here's that code:

#### `R/models_pts.R`

```{r, code=xfun::read_utf8(here::here("R", "models_pts.R")), eval=FALSE, class.source="fold-hide"}
```

#### `R/models_clphy.R`

```{r, code=xfun::read_utf8(here::here("R", "models_clphy.R")), eval=FALSE, class.source="fold-hide"}
```

#### `R/models_clpriv.R`

```{r, code=xfun::read_utf8(here::here("R", "models_clpriv.R")), eval=FALSE, class.source="fold-hide"}
```

### 2021-04-02 analysis/03_modeling-choices.Rmd
Run all models and predictions!

---
title: "Modeling choices"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knit_print.data.frame <- function(x, ...) {
  res <- paste(c('', '', kable_styling(kable(x, booktabs = TRUE))), collapse = '\n')
  asis_output(res)
}

registerS3method("knit_print", "data.frame", knit_print.data.frame)
registerS3method("knit_print", "grouped_df", knit_print.data.frame)

knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "85%")

options(dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(janitor)
library(brms)
library(lme4)
library(lmtest)  # For log ratio tests
library(performance)  # For ICCs
library(scales)
library(modelsummary)
library(here)

CHAINS <- 4
ITER <- 2000
WARMUP <- 1000
BAYES_SEED <- 1234

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr")

# Generated via random.org
set.seed(9936)

# Load data
# Need to use this withr thing because tar_read() and tar_load() need to see the
# _targets folder in the current directory, but this .Rmd file is in a subfolder
withr::with_dir(here::here(), {
  source(tar_read(plot_funs))

  canary <- tar_read(panel_lagged)
})

# canary <- canary %>%
#   mutate(gwcode = as.factor(gwcode), year = as.factor(year)) %>%  # Make a factor
#   mutate(PTS_factor_lead1 = ordered(PTS_factor_lead1)) %>%  # Make this ordered
#   # To do fancy Bell and Jones adjustment (https://doi.org/10.1017/psrm.2014.7)
#   # (aka Mundlak devices), explanatory variables should be split into a meaned
#   # version (\bar{x}) and a de-meaned version (x - \bar{x}) so that they can
#   # explain the within-group and between-group variation. We de-mean three variables here:
#   group_by(gwcode) %>%
#   mutate_at(vars(v2csreprss, v2x_polyarchy, gdpcap_log),
#             list(between = ~mean(., na.rm = TRUE),  # Between, for countries
#                  within = ~. - mean(., na.rm = TRUE))) %>%   # Within, for countries
#   ungroup()
```

# Interpretation reminders

I always forget how to interpret these dang within/between coefficients in REWB models, so here's a reminder:

- "Within" coefficients show what happens as you move up and down from the average level.
  - Template = increasing 1 unit of `x` above the average in a typical country is associated with a β change in `y`
- "Between" coefficients show what happens as you move the whole average up. They're trickier (and less important) to interpret. [This post](https://statisticalhorizons.com/between-within-contextual-effects) explains more, along with [Bell, Fairbrother, and Jones (2018)](https://doi.org/10.1007/s11135-018-0802-x).

# Check if multilevel models are warranted

First we can start with a simple null model to see what the effect of country and year is on our outcome (i.e. how much do country and year alone explain the variation in repression?)

```{r null-models}
m0_pts <- lmer(PTS_lead1 ~ (1 | year) + (1 | gwcode),
               REML = FALSE, data = canary)
m0_clphy <- lmer(v2x_clphy_lead1 ~ (1 | year) + (1 | gwcode),
               REML = FALSE, data = canary)
m0_clpriv <- lmer(v2x_clpriv_lead1 ~ (1 | year) + (1 | gwcode),
               REML = FALSE, data = canary)
```

We then calculate the intraclass correlation coefficients (ICC) for year and country:

```{r icc-models}
# This shows just the ICC. modelsummary() helpfully includes it.
# icc(m0_pts)

modelsummary(list(m0_pts, m0_clphy, m0_clpriv),
             estimate = "{estimate}", statistic = NULL,
             gof_map = list(list("raw" = "icc", "clean" = "ICC", "fmt" = 4)))
```

These values represent the variation in the outcome variable that can be explained by the country/year structure, which is a *ton*! For the PTS model, for instance, the ICC is `r round(icc(m0_pts)$ICC_adjusted, 4)`, meaning that the random effects structure explains `r percent(icc(m0_pts)$ICC_adjusted)` of the variation in PTS.

We can also look at how each of the levels are related to the outcome

```{r icc-models-by-group}
icc(m0_pts, by_group = TRUE)
icc(m0_clphy, by_group = TRUE)
icc(m0_clpriv, by_group = TRUE)
```

It looks like pretty much all the variability in PTS is explained at a country level and not at a year level, which makes sense, since there's probably a ton of autocorrelation in human rights practices within a country, while global human rights levels probably don't move simultaneously across years.

Just because the bulk of the relative variation is at at the country level doesn't mean that there isn't significant variability within countries over time. Thus, we should really used a multilevel model because the country-year structure matters *a lot* when explaining human rights abuses

# Gradually build up the model

Understanding all the different country/year dynamics can get complicated, so [John Poe](http://www.johndavidpoe.com/) suggests slowly building up the model and inspecting it to see what's going on.

```{r basic-model}
# First we add the main variable of interest (civil society repression here)
m1 <- lmer(PTS_lead1 ~ v2csreprss + (1 | year) + (1 | gwcode),
           REML = FALSE, data = canary)
modelsummary(list("Null model" = m1),
             coef_omit = "sd__")
```

```{r model-details, include=FALSE}
m1_out <- broom.mixed::tidy(m1) %>% 
  filter(effect == "fixed") %>% 
  mutate(term = make_clean_names(term)) %>% 
  split(.$term)

# For fun, we can see the effects of specific countries/years with ranef()
# lme4::ranef(m1)$gwcode %>% rownames_to_column() %>% as_tibble()
# lme4::ranef(m1)$year %>% rownames_to_column() %>% as_tibble()
```

On average, increasing civil society repression by a point leads to a decrease of `r abs(round(m1_out$v2csreprss$estimate, 3))` points of human rights repression in the following year.

Finally, we can see if adding `v2csreprss` is an improvement over the null `m0_pts` model:

```{r check-against-m0}
lrtest(m0_pts, m1) %>% as_tibble()
```

It is! `m1` is definitely an improvement over `m0_pts` (p < 0.001).

Next, we can split civil society repression into its within and between versions and see how that performs and how it changes the results

```{r mundlak-model}
m2 <- lmer(PTS_lead1 ~ v2csreprss_within + v2csreprss_between +
             (1 | year) + (1 | gwcode),
           REML = FALSE, data = canary)

modelsummary(list("Null model" = m1, "Within/between model" = m2),
             coef_omit = "sd__")
```

```{r m2-details, include=FALSE}
m2_out <- broom.mixed::tidy(m2) %>% 
  filter(effect == "fixed") %>% 
  mutate(term = make_clean_names(term)) %>% 
  split(.$term)
```

On average, a one-unit increase beyond a country's average level of civil society repression (i.e. the within-country effect) is associated with a `r abs(round(m2_out$v2csreprss_within$estimate, 3))` point decrease in overall repression the following year

Also, the `v2csreprss_between` coefficient can be interpreted somehow, but I'm not 100% sure how. (I think something like "as a country's average civil society repression increases, general repression worsens by `r abs(round(m2_out$v2csreprss_between$estimate, 3))`" or something).

And we can check if `m2` is an improvement over `m1` (it is!):

```{r check-against-m1}
lrtest(m1, m2) %>% as_tibble()
```

# Thus…

So, using a Mundlak within/between split of time-varying covariates is warranted, as is using a country/year random effects structure. Woot.

### 2021-04-02 analysis/04_predictions.Rmd
Run all models and predictions!

@@
   html_document:
-    code_folding: show
+    code_folding: hide
 editor_options: 
@@
 library(targets)
+library(yardstick)
+library(broom)
+library(patchwork)
+library(scales)
 library(here)
@@
 
-  canary <- tar_read(panel_done_trimmed)
+  canary_testing_lagged <- tar_read(panel_testing_lagged)
+
+  # Load big list of models
+  model_df <- tar_read(model_df) %>% 
+    filter(str_detect(model, "baseline") | str_detect(model, "v2csreprss"))
+
+  # Load actual model objects
+  tar_load(c(m_pts_baseline_train, m_pts_v2csreprss_train,
+             m_pts_total_train, m_pts_advocacy_train, 
+             m_pts_entry_train, m_pts_funding_train,
+             m_pts_baseline_rewb_train, m_pts_v2csreprss_rewb_train, 
+             m_clphy_baseline_train, m_clphy_v2csreprss_train, 
+             m_clphy_total_train, m_clphy_advocacy_train, 
+             m_clphy_entry_train, m_clphy_funding_train,
+             m_clpriv_baseline_train, m_clpriv_v2csreprss_train,
+             m_clpriv_total_train, m_clpriv_advocacy_train, 
+             m_clpriv_entry_train, m_clpriv_funding_train))
 })
+
+pts_levels <- levels(canary_testing_lagged$PTS_factor)
+
+# Returns a data frame of predicted probabilities with actual = 1 
+# when the response outcome happens
+match_actual <- function(x, pred, actual) {
+  pred %>% 
+    select(fitted = {{x}}) %>% 
+    mutate(actual = as.numeric(actual == colnames(pred[x])),
+           plot_level = colnames(pred[x]))
+}
 ```
 
-TODO:
+```{r kludgy-bandaid-for-weird-data-issues}
+# OOOOOOOF OH NO for some reason PTS_lead1 and all leaded V-Dem values missing
+# for 2013 (i.e. 2014 values) and I don't want to go back and rerun all these
+# models yet, so we do a temporary fix here and manually add the values from
+# pts_clean and vdem_clean
+withr::with_dir(here::here(), {
+  tar_load(pts_clean)
+  tar_load(vdem_clean)
+})
 
-- Split into training/test data
-- Generate predictions
-- Compare correctness, AUC, etc. for models with and without CS restrictions
+pts_2014 <- pts_clean %>% 
+  group_by(gwcode) %>% 
+  mutate(across(c(PTS, PTS_factor),
+                  list(lead1_2014 = ~lead(., 1)))) %>% 
+  ungroup() %>% 
+  filter(year == 2013) %>% 
+  select(-PTS, -PTS_factor)
+
+vdem_2014 <- vdem_clean %>% 
+  group_by(gwcode) %>% 
+  mutate(across(c(v2x_clphy, v2x_clpriv),
+                  list(lead1_2014 = ~lead(., 1)))) %>% 
+  ungroup() %>% 
+  filter(year == 2013) %>% 
+  select(gwcode, year, v2x_clphy_lead1_2014, v2x_clpriv_lead1_2014)
+
+canary_testing_lagged <- canary_testing_lagged %>% 
+  left_join(pts_2014, by = c("year", "gwcode")) %>% 
+  left_join(vdem_2014, by = c("year", "gwcode")) %>% 
+  mutate(PTS_lead1 = coalesce(PTS_lead1, PTS_lead1_2014),
+         PTS_factor_lead1 = coalesce(PTS_factor_lead1, PTS_factor_lead1_2014),
+         v2x_clphy_lead1 = coalesce(v2x_clphy_lead1, v2x_clphy_lead1_2014),
+         v2x_clpriv_lead1 = coalesce(v2x_clpriv_lead1, v2x_clpriv_lead1_2014)) %>% 
+  select(-contains("_2014"))
+```
+
+# E~1a~: NGO laws and political terror
+
+```{r e1a-predictions, warning=FALSE}
+seed_pts_prediction <- 5494  # From random.org
+
+set.seed(seed_pts_prediction)
+pred_pts_baseline <- predict(
+  m_pts_baseline_train, 
+  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
+  allow_new_levels = TRUE
+) %>% 
+  as_tibble() %>% 
+  magrittr::set_colnames(pts_levels)
+
+set.seed(seed_pts_prediction)
+pred_pts_total <- predict(
+  m_pts_total_train, 
+  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
+  allow_new_levels = TRUE
+) %>% 
+  as_tibble() %>% 
+  magrittr::set_colnames(pts_levels)
+
+set.seed(seed_pts_prediction)
+pred_pts_advocacy <- predict(
+  m_pts_advocacy_train, 
+  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
+  allow_new_levels = TRUE
+) %>% 
+  as_tibble() %>% 
+  magrittr::set_colnames(pts_levels)
+
+set.seed(seed_pts_prediction)
+pred_pts_entry <- predict(
+  m_pts_entry_train, 
+  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
+  allow_new_levels = TRUE
+) %>% 
+  as_tibble() %>% 
+  magrittr::set_colnames(pts_levels)
+
+set.seed(seed_pts_prediction)
+pred_pts_funding <- predict(
+  m_pts_funding_train, 
+  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
+  allow_new_levels = TRUE
+) %>% 
+  as_tibble() %>% 
+  magrittr::set_colnames(pts_levels)
+```
+
+## Separation plots
+
+### Baseline models
+
+```{r e1a-separation-baseline}
+# Match each column in pred_mat (predicted probabilities for each response level)
+pred_long_list <- lapply(1:ncol(pred_pts_baseline), 
+                         FUN = match_actual, 
+                         pred = pred_pts_baseline, 
+                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
+
+plot_data <- pred_long_list %>% 
+  bind_rows() %>% 
+  filter(!is.nan(fitted), !is.na(actual)) %>% 
+  group_by(plot_level) %>% 
+  arrange(plot_level, fitted) %>% 
+  mutate(index = row_number()) %>% 
+  ungroup()
+
+markers <- plot_data %>% 
+  group_by(plot_level) %>%
+  summarize(obs = n(), expected = sum(fitted),
+            marker = obs - expected + 1)
+
+n_in_group <- nrow(pred_pts_baseline)
+
+plot_data_condensed <- plot_data %>% 
+  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
+  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
+  mutate(rleid = cumsum(rleid)) %>% 
+  group_by(plot_level, rleid) %>% 
+  slice(1) %>% 
+  group_by(plot_level) %>% 
+  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
+  ungroup()
+
+ggplot(plot_data_condensed) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
+  geom_line(aes(x = index, y = fitted), size = 0.3) +
+  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
+  scale_fill_manual(values = c("grey90", "#2ECC40")) +
+  guides(fill = FALSE) +
+  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
+  theme_void(base_family = "Inter Bold")
+```
+
+### Models with NGO laws
+
+#### Total legal barriers
+
+```{r e1a-separation-total}
+# Match each column in pred_mat (predicted probabilities for each response level)
+pred_long_list <- lapply(1:ncol(pred_pts_total), 
+                         FUN = match_actual, 
+                         pred = pred_pts_total, 
+                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
+
+plot_data <- pred_long_list %>% 
+  bind_rows() %>% 
+  filter(!is.nan(fitted), !is.na(actual)) %>% 
+  group_by(plot_level) %>% 
+  arrange(plot_level, fitted) %>% 
+  mutate(index = row_number()) %>% 
+  ungroup()
+
+markers <- plot_data %>% 
+  group_by(plot_level) %>%
+  summarize(obs = n(), expected = sum(fitted),
+            marker = obs - expected + 1)
+
+n_in_group <- nrow(pred_pts_total)
+
+plot_data_condensed <- plot_data %>% 
+  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
+  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
+  mutate(rleid = cumsum(rleid)) %>% 
+  group_by(plot_level, rleid) %>% 
+  slice(1) %>% 
+  group_by(plot_level) %>% 
+  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
+  ungroup()
+
+ggplot(plot_data_condensed) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
+  geom_line(aes(x = index, y = fitted), size = 0.3) +
+  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
+  scale_fill_manual(values = c("grey90", "#2ECC40")) +
+  guides(fill = FALSE) +
+  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
+  theme_void(base_family = "Inter Bold")
+```
+
+#### Barriers to advocacy
+
+```{r e1a-separation-advocacy}
+# Match each column in pred_mat (predicted probabilities for each response level)
+pred_long_list <- lapply(1:ncol(pred_pts_advocacy), 
+                         FUN = match_actual, 
+                         pred = pred_pts_advocacy, 
+                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
+
+plot_data <- pred_long_list %>% 
+  bind_rows() %>% 
+  filter(!is.nan(fitted), !is.na(actual)) %>% 
+  group_by(plot_level) %>% 
+  arrange(plot_level, fitted) %>% 
+  mutate(index = row_number()) %>% 
+  ungroup()
+
+markers <- plot_data %>% 
+  group_by(plot_level) %>%
+  summarize(obs = n(), expected = sum(fitted),
+            marker = obs - expected + 1)
+
+n_in_group <- nrow(pred_pts_advocacy)
+
+plot_data_condensed <- plot_data %>% 
+  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
+  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
+  mutate(rleid = cumsum(rleid)) %>% 
+  group_by(plot_level, rleid) %>% 
+  slice(1) %>% 
+  group_by(plot_level) %>% 
+  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
+  ungroup()
+
+ggplot(plot_data_condensed) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
+  geom_line(aes(x = index, y = fitted), size = 0.3) +
+  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
+  scale_fill_manual(values = c("grey90", "#2ECC40")) +
+  guides(fill = FALSE) +
+  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
+  theme_void(base_family = "Inter Bold")
+```
+
+#### Barriers to entry
+
+```{r e1a-separation-entry}
+# Match each column in pred_mat (predicted probabilities for each response level)
+pred_long_list <- lapply(1:ncol(pred_pts_entry), 
+                         FUN = match_actual, 
+                         pred = pred_pts_entry, 
+                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
+
+plot_data <- pred_long_list %>% 
+  bind_rows() %>% 
+  filter(!is.nan(fitted), !is.na(actual)) %>% 
+  group_by(plot_level) %>% 
+  arrange(plot_level, fitted) %>% 
+  mutate(index = row_number()) %>% 
+  ungroup()
+
+markers <- plot_data %>% 
+  group_by(plot_level) %>%
+  summarize(obs = n(), expected = sum(fitted),
+            marker = obs - expected + 1)
+
+n_in_group <- nrow(pred_pts_entry)
+
+plot_data_condensed <- plot_data %>% 
+  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
+  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
+  mutate(rleid = cumsum(rleid)) %>% 
+  group_by(plot_level, rleid) %>% 
+  slice(1) %>% 
+  group_by(plot_level) %>% 
+  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
+  ungroup()
+
+ggplot(plot_data_condensed) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
+  geom_line(aes(x = index, y = fitted), size = 0.3) +
+  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
+  scale_fill_manual(values = c("grey90", "#2ECC40")) +
+  guides(fill = FALSE) +
+  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
+  theme_void(base_family = "Inter Bold")
+```
+
+#### Barriers to funding
+
+```{r e1a-separation-funding}
+# Match each column in pred_mat (predicted probabilities for each response level)
+pred_long_list <- lapply(1:ncol(pred_pts_funding), 
+                         FUN = match_actual, 
+                         pred = pred_pts_funding, 
+                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
+
+plot_data <- pred_long_list %>% 
+  bind_rows() %>% 
+  filter(!is.nan(fitted), !is.na(actual)) %>% 
+  group_by(plot_level) %>% 
+  arrange(plot_level, fitted) %>% 
+  mutate(index = row_number()) %>% 
+  ungroup()
+
+markers <- plot_data %>% 
+  group_by(plot_level) %>%
+  summarize(obs = n(), expected = sum(fitted),
+            marker = obs - expected + 1)
+
+n_in_group <- nrow(pred_pts_funding)
+
+plot_data_condensed <- plot_data %>% 
+  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
+  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
+  mutate(rleid = cumsum(rleid)) %>% 
+  group_by(plot_level, rleid) %>% 
+  slice(1) %>% 
+  group_by(plot_level) %>% 
+  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
+  ungroup()
+
+ggplot(plot_data_condensed) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
+  geom_line(aes(x = index, y = fitted), size = 0.3) +
+  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
+  scale_fill_manual(values = c("grey90", "#2ECC40")) +
+  guides(fill = FALSE) +
+  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
+  theme_void(base_family = "Inter Bold")
+```
+
+## Prediction diagnostics
+
+```{r e1a-improved-cases}
+pred_pts_baseline_categories <- pred_pts_baseline %>% 
+  rownames_to_column() %>% 
+  pivot_longer(-rowname) %>% 
+  group_by(rowname) %>% 
+  filter(rank(-value, ties.method = "last") == 1) %>% 
+  ungroup() %>% 
+  select(predicted = name)
+
+pred_pts_total_categories <- pred_pts_total %>% 
+  rownames_to_column() %>% 
+  pivot_longer(-rowname) %>% 
+  group_by(rowname) %>% 
+  filter(rank(-value, ties.method = "last") == 1) %>% 
+  ungroup() %>% 
+  select(predicted = name)
+
+pred_pts_advocacy_categories <- pred_pts_advocacy %>% 
+  rownames_to_column() %>% 
+  pivot_longer(-rowname) %>% 
+  group_by(rowname) %>% 
+  filter(rank(-value, ties.method = "last") == 1) %>% 
+  ungroup() %>% 
+  select(predicted = name)
+
+pred_pts_entry_categories <- pred_pts_entry %>% 
+  rownames_to_column() %>% 
+  pivot_longer(-rowname) %>% 
+  group_by(rowname) %>% 
+  filter(rank(-value, ties.method = "last") == 1) %>% 
+  ungroup() %>% 
+  select(predicted = name)
+
+pred_pts_funding_categories <- pred_pts_funding %>% 
+  rownames_to_column() %>% 
+  pivot_longer(-rowname) %>% 
+  group_by(rowname) %>% 
+  filter(rank(-value, ties.method = "last") == 1) %>% 
+  ungroup() %>% 
+  select(predicted = name)
+
+pts_cat_preds <- canary_testing_lagged %>% 
+  select(country, year, actual = PTS_factor_lead1) %>% 
+  mutate(pred_baseline = pred_pts_baseline_categories$predicted,
+         pred_total = pred_pts_total_categories$predicted,
+         pred_advocacy = pred_pts_advocacy_categories$predicted,
+         pred_entry = pred_pts_entry_categories$predicted,
+         pred_funding = pred_pts_funding_categories$predicted) %>% 
+  filter(!is.na(actual)) %>%
+  mutate(is_correct_baseline = actual == pred_baseline,
+         is_correct_total = actual == pred_total,
+         is_correct_advocacy = actual == pred_advocacy,
+         is_correct_entry = actual == pred_entry,
+         is_correct_funding = actual == pred_funding)
+
+# Improved predictions
+pts_improved_total <- pts_cat_preds %>% 
+  filter(!is_correct_baseline & is_correct_total) %>% 
+  select(Country = country, Year = year, Actual = actual,
+         `CS repression included` = pred_total,
+         `Baseline` = pred_baseline)
+
+pts_improved_advocacy <- pts_cat_preds %>% 
+  filter(!is_correct_baseline & is_correct_advocacy) %>% 
+  select(Country = country, Year = year, Actual = actual,
+         `CS repression included` = pred_advocacy,
+         `Baseline` = pred_baseline)
+
+pts_improved_entry <- pts_cat_preds %>% 
+  filter(!is_correct_baseline & is_correct_entry) %>% 
+  select(Country = country, Year = year, Actual = actual,
+         `CS repression included` = pred_entry,
+         `Baseline` = pred_baseline)
+
+pts_improved_funding <- pts_cat_preds %>% 
+  filter(!is_correct_baseline & is_correct_funding) %>% 
+  select(Country = country, Year = year, Actual = actual,
+         `CS repression included` = pred_funding,
+         `Baseline` = pred_baseline)
+
+pts_improved_total %>% 
+  kbl(caption = "Cases improved with total legal barriers") %>% 
+  kable_styling()
+
+pts_improved_advocacy %>% 
+  kbl(caption = "Cases improved with barriers to advocacy") %>% 
+  kable_styling()
+
+pts_improved_entry %>% 
+  kbl(caption = "Cases improved with barriers to entry") %>% 
+  kable_styling()
+
+pts_improved_funding %>% 
+  kbl(caption = "Cases improved with barriers to funding") %>% 
+  kable_styling()
+```
+
+```{r e1a-correct-not-correct}
+correct_lookup <- tribble(
+  ~name, ~nice_name,
+  "is_correct_total", "Total legal barriers included",
+  "is_correct_advocacy", "Barriers to advocacy included",
+  "is_correct_entry", "Barriers to entry included",
+  "is_correct_funding", "Barriers to funding included",
+  "is_correct_baseline", "Baseline"
+) %>% mutate(nice_name = fct_inorder(nice_name, ordered = TRUE))
+
+pts_pred_table <- pts_cat_preds %>% 
+  pivot_longer(starts_with("is_correct")) %>% 
+  group_by(name, value) %>% 
+  summarize(n = n()) %>% 
+  ungroup() %>% 
+  left_join(correct_lookup, by = "name") %>% 
+  mutate(Prediction = ifelse(value == TRUE, "Correct", "Wrong")) %>% 
+  arrange(nice_name) %>% 
+  select(-name, -value) %>% 
+  pivot_wider(names_from = "nice_name", values_from = "n")
+
+pts_pred_table %>% 
+  kbl(align = "lcccc") %>% 
+  kable_styling()
+```
+
+\
+
+# E~1b~: NGO laws and physical violence
+
+```{r e1b-predictions, warning=FALSE}
+seed_clphy_prediction <- 7285  # From random.org
+
+set.seed(seed_clphy_prediction)
+pred_clphy_baseline <- predict(m_clphy_baseline_train, 
+                               newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
+                               allow_new_levels = TRUE)
+
+set.seed(seed_clphy_prediction)
+pred_clphy_total <- predict(m_clphy_total_train, 
+                            newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
+                            allow_new_levels = TRUE)
+
+set.seed(seed_clphy_prediction)
+pred_clphy_advocacy <- predict(m_clphy_advocacy_train, 
+                               newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
+                               allow_new_levels = TRUE)
+
+set.seed(seed_clphy_prediction)
+pred_clphy_entry <- predict(m_clphy_entry_train, 
+                            newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
+                            allow_new_levels = TRUE)
+
+set.seed(seed_clphy_prediction)
+pred_clphy_funding <- predict(m_clphy_funding_train, 
+                              newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
+                              allow_new_levels = TRUE)
+
+pred_clphy_baseline_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clphy_lead1) %>% 
+  bind_cols(as_tibble(pred_clphy_baseline)) %>% 
+  filter(!is.na(v2x_clphy_lead1))
+
+pred_clphy_total_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clphy_lead1) %>% 
+  bind_cols(as_tibble(pred_clphy_total)) %>% 
+  filter(!is.na(v2x_clphy_lead1))
+
+pred_clphy_advocacy_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clphy_lead1) %>% 
+  bind_cols(as_tibble(pred_clphy_advocacy)) %>% 
+  filter(!is.na(v2x_clphy_lead1))
+
+pred_clphy_entry_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clphy_lead1) %>% 
+  bind_cols(as_tibble(pred_clphy_entry)) %>% 
+  filter(!is.na(v2x_clphy_lead1))
+
+pred_clphy_funding_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clphy_lead1) %>% 
+  bind_cols(as_tibble(pred_clphy_funding)) %>% 
+  filter(!is.na(v2x_clphy_lead1))
+```
+
+## Improvement from baseline models
+
+```{r e1b-pred-plots, warning=FALSE}
+plot_baseline <- ggplot(pred_clphy_baseline_test, 
+                        aes(x = v2x_clphy_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Baseline",
+       x = "Actual physical violence index (t + 1)",
+       y = "Predicted physical violence index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_total <- ggplot(pred_clphy_total_test, 
+                     aes(x = v2x_clphy_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Total legal barriers",
+       x = "Actual physical violence index (t + 1)",
+       y = "Predicted physical violence index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_advocacy <- ggplot(pred_clphy_advocacy_test, 
+                        aes(x = v2x_clphy_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Barriers to advocacy",
+       x = "Actual physical violence index (t + 1)",
+       y = "Predicted physical violence index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_entry <- ggplot(pred_clphy_entry_test, 
+                     aes(x = v2x_clphy_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Barriers to entry",
+       x = "Actual physical violence index (t + 1)",
+       y = "Predicted physical violence index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_funding <- ggplot(pred_clphy_funding_test, 
+                       aes(x = v2x_clphy_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Barriers to funding",
+       x = "Actual physical violence index (t + 1)",
+       y = "Predicted physical violence index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+(plot_baseline | plot_total) / (plot_advocacy | plot_entry | plot_funding)
+```
+
+```{r e1b-metrics}
+lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
+
+bind_rows(lotsa_metrics(pred_clphy_baseline_test, 
+                        truth = v2x_clphy_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Baseline"),
+          lotsa_metrics(pred_clphy_total_test, 
+                        truth = v2x_clphy_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Total legal barriers"),
+          lotsa_metrics(pred_clphy_advocacy_test, 
+                        truth = v2x_clphy_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Barriers to advocacy"),
+          lotsa_metrics(pred_clphy_entry_test, 
+                        truth = v2x_clphy_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Barriers to entry"),
+          lotsa_metrics(pred_clphy_funding_test, 
+                        truth = v2x_clphy_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Barriers to funding")) %>% 
+  select(Model, .metric, .estimate) %>% 
+  pivot_wider(names_from = ".metric", values_from = ".estimate")
+```
+
+## Most improved countries
+
+### Total legal barriers
+
+```{r e1b-most-improved-total}
+most_improved_clphy_total <- bind_cols(
+  pred_clphy_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
+    select(country, gwcode, year, v2x_clphy_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clphy_total_test %>% 
+    mutate(error_total = Estimate - v2x_clphy_lead1) %>% 
+    select(estimate_total = Estimate, error_total)
+) %>% 
+  mutate(improved = error_total < 0 & abs(error_total) < abs(error_baseline)) %>% 
+  mutate(diff = error_total - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clphy_total)
+
+most_improved_clphy_total %>% 
+  select(Country = country, Year = year, 
+         `Actual physical violence index (t + 1)` =  v2x_clphy_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_total,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+### Barriers to advocacy
+
+```{r e1b-most-improved-advocacy}
+most_improved_clphy_advocacy <- bind_cols(
+  pred_clphy_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
+    select(country, gwcode, year, v2x_clphy_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clphy_advocacy_test %>% 
+    mutate(error_advocacy = Estimate - v2x_clphy_lead1) %>% 
+    select(estimate_advocacy = Estimate, error_advocacy)
+) %>% 
+  mutate(improved = error_advocacy < 0 & abs(error_advocacy) < abs(error_baseline)) %>% 
+  mutate(diff = error_advocacy - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clphy_advocacy)
+
+most_improved_clphy_advocacy %>% 
+  select(Country = country, Year = year, 
+         `Actual physical violence index (t + 1)` =  v2x_clphy_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_advocacy,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+### Barriers to entry
+
+```{r e1b-most-improved-entry}
+most_improved_clphy_entry <- bind_cols(
+  pred_clphy_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
+    select(country, gwcode, year, v2x_clphy_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clphy_entry_test %>% 
+    mutate(error_entry = Estimate - v2x_clphy_lead1) %>% 
+    select(estimate_entry = Estimate, error_entry)
+) %>% 
+  mutate(improved = error_entry < 0 & abs(error_entry) < abs(error_baseline)) %>% 
+  mutate(diff = error_entry - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clphy_entry)
+
+most_improved_clphy_entry %>% 
+  select(Country = country, Year = year, 
+         `Actual physical violence index (t + 1)` =  v2x_clphy_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_entry,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+### Barriers to funding
+
+```{r e1b-most-improved-funding}
+most_improved_clphy_funding <- bind_cols(
+  pred_clphy_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
+    select(country, gwcode, year, v2x_clphy_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clphy_funding_test %>% 
+    mutate(error_funding = Estimate - v2x_clphy_lead1) %>% 
+    select(estimate_funding = Estimate, error_funding)
+) %>% 
+  mutate(improved = error_funding < 0 & abs(error_funding) < abs(error_baseline)) %>% 
+  mutate(diff = error_funding - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clphy_funding)
+
+most_improved_clphy_funding %>% 
+  select(Country = country, Year = year, 
+         `Actual physical violence index (t + 1)` =  v2x_clphy_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_funding,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+\
+
+# E~1c~: NGO laws and civil liberties
+
+```{r e1c-predictions, warning=FALSE}
+seed_clpriv_prediction <- 6670  # From random.org
+
+set.seed(seed_clpriv_prediction)
+pred_clpriv_baseline <- predict(m_clpriv_baseline_train, 
+                                newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
+                                allow_new_levels = TRUE)
+
+set.seed(seed_clpriv_prediction)
+pred_clpriv_total <- predict(m_clpriv_total_train, 
+                             newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
+                             allow_new_levels = TRUE)
+
+set.seed(seed_clpriv_prediction)
+pred_clpriv_advocacy <- predict(m_clpriv_advocacy_train, 
+                                newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
+                                allow_new_levels = TRUE)
+
+set.seed(seed_clpriv_prediction)
+pred_clpriv_entry <- predict(m_clpriv_entry_train, 
+                             newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
+                             allow_new_levels = TRUE)
+
+set.seed(seed_clpriv_prediction)
+pred_clpriv_funding <- predict(m_clpriv_funding_train, 
+                               newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
+                               allow_new_levels = TRUE)
+
+pred_clpriv_baseline_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
+  bind_cols(as_tibble(pred_clpriv_baseline)) %>% 
+  filter(!is.na(v2x_clpriv_lead1))
+
+pred_clpriv_total_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
+  bind_cols(as_tibble(pred_clpriv_total)) %>% 
+  filter(!is.na(v2x_clpriv_lead1))
+
+pred_clpriv_advocacy_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
+  bind_cols(as_tibble(pred_clpriv_advocacy)) %>% 
+  filter(!is.na(v2x_clpriv_lead1))
+
+pred_clpriv_entry_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
+  bind_cols(as_tibble(pred_clpriv_entry)) %>% 
+  filter(!is.na(v2x_clpriv_lead1))
+
+pred_clpriv_funding_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
+  bind_cols(as_tibble(pred_clpriv_funding)) %>% 
+  filter(!is.na(v2x_clpriv_lead1))
+```
+
+## Improvement from baseline models
+
+```{r e1c-pred-plots, warning=FALSE}
+plot_baseline <- ggplot(pred_clpriv_baseline_test, 
+                        aes(x = v2x_clpriv_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Baseline",
+       x = "Actual private civil liberties index (t + 1)",
+       y = "Predicted private civil liberties index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_total <- ggplot(pred_clpriv_total_test, 
+                     aes(x = v2x_clpriv_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Total legal barriers",
+       x = "Actual private civil liberties index (t + 1)",
+       y = "Predicted private civil liberties index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_advocacy <- ggplot(pred_clpriv_advocacy_test, 
+                        aes(x = v2x_clpriv_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Barriers to advocacy",
+       x = "Actual private civil liberties index (t + 1)",
+       y = "Predicted private civil liberties index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_entry <- ggplot(pred_clpriv_entry_test, 
+                     aes(x = v2x_clpriv_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Barriers to entry",
+       x = "Actual private civil liberties index (t + 1)",
+       y = "Predicted private civil liberties index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_funding <- ggplot(pred_clpriv_funding_test, 
+                       aes(x = v2x_clpriv_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Barriers to funding",
+       x = "Actual private civil liberties index (t + 1)",
+       y = "Predicted private civil liberties index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+(plot_baseline | plot_total) / (plot_advocacy | plot_entry | plot_funding)
+```
+
+```{r e1c-metrics}
+lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
+
+bind_rows(lotsa_metrics(pred_clpriv_baseline_test, 
+                        truth = v2x_clpriv_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Baseline"),
+          lotsa_metrics(pred_clpriv_total_test, 
+                        truth = v2x_clpriv_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Total legal barriers"),
+          lotsa_metrics(pred_clpriv_advocacy_test, 
+                        truth = v2x_clpriv_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Barriers to advocacy"),
+          lotsa_metrics(pred_clpriv_entry_test, 
+                        truth = v2x_clpriv_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Barriers to entry"),
+          lotsa_metrics(pred_clpriv_funding_test, 
+                        truth = v2x_clpriv_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Barriers to funding")) %>% 
+  select(Model, .metric, .estimate) %>% 
+  pivot_wider(names_from = ".metric", values_from = ".estimate")
+```
+
+## Most improved countries
+
+### Total legal barriers
+
+```{r e1c-most-improved-total}
+most_improved_clpriv_total <- bind_cols(
+  pred_clpriv_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
+    select(country, gwcode, year, v2x_clpriv_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clpriv_total_test %>% 
+    mutate(error_total = Estimate - v2x_clpriv_lead1) %>% 
+    select(estimate_total = Estimate, error_total)
+) %>% 
+  mutate(improved = error_total < 0 & abs(error_total) < abs(error_baseline)) %>% 
+  mutate(diff = error_total - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clpriv_total)
+
+most_improved_clpriv_total %>% 
+  select(Country = country, Year = year, 
+         `Actual physical violence index (t + 1)` =  v2x_clpriv_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_total,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+### Barriers to advocacy
+
+```{r e1c-most-improved-advocacy}
+most_improved_clpriv_advocacy <- bind_cols(
+  pred_clpriv_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
+    select(country, gwcode, year, v2x_clpriv_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clpriv_advocacy_test %>% 
+    mutate(error_advocacy = Estimate - v2x_clpriv_lead1) %>% 
+    select(estimate_advocacy = Estimate, error_advocacy)
+) %>% 
+  mutate(improved = error_advocacy < 0 & abs(error_advocacy) < abs(error_baseline)) %>% 
+  mutate(diff = error_advocacy - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clpriv_advocacy)
+
+most_improved_clpriv_advocacy %>% 
+  select(Country = country, Year = year, 
+         `Actual physical violence index (t + 1)` =  v2x_clpriv_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_advocacy,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+### Barriers to entry
+
+```{r e1c-most-improved-entry}
+most_improved_clpriv_entry <- bind_cols(
+  pred_clpriv_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
+    select(country, gwcode, year, v2x_clpriv_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clpriv_entry_test %>% 
+    mutate(error_entry = Estimate - v2x_clpriv_lead1) %>% 
+    select(estimate_entry = Estimate, error_entry)
+) %>% 
+  mutate(improved = error_entry < 0 & abs(error_entry) < abs(error_baseline)) %>% 
+  mutate(diff = error_entry - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clpriv_entry)
+
+most_improved_clpriv_entry %>% 
+  select(Country = country, Year = year, 
+         `Actual physical violence index (t + 1)` =  v2x_clpriv_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_entry,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+### Barriers to funding
+
+```{r e1c-most-improved-funding}
+most_improved_clpriv_funding <- bind_cols(
+  pred_clpriv_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
+    select(country, gwcode, year, v2x_clpriv_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clpriv_funding_test %>% 
+    mutate(error_funding = Estimate - v2x_clpriv_lead1) %>% 
+    select(estimate_funding = Estimate, error_funding)
+) %>% 
+  mutate(improved = error_funding < 0 & abs(error_funding) < abs(error_baseline)) %>% 
+  mutate(diff = error_funding - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clpriv_funding)
+
+most_improved_clpriv_funding %>% 
+  select(Country = country, Year = year, 
+         `Actual physical violence index (t + 1)` =  v2x_clpriv_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_funding,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+\
+
+---
+
+\
+
+# E~2a~: Civil society environment and political terror
+
+```{r e2a-predictions, warning=FALSE}
+seed_pts_prediction <- 5494  # From random.org
+
+set.seed(seed_pts_prediction)
+pred_pts_baseline <- predict(
+  m_pts_baseline_train, 
+  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
+  allow_new_levels = TRUE
+) %>% 
+  as_tibble() %>% 
+  magrittr::set_colnames(pts_levels)
+
+set.seed(seed_pts_prediction)
+pred_pts_v2csreprss <- predict(
+  m_pts_v2csreprss_train, 
+  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
+  allow_new_levels = TRUE
+) %>% 
+  as_tibble() %>% 
+  magrittr::set_colnames(pts_levels)
+
+set.seed(seed_pts_prediction)
+pred_pts_baseline_rewb <- predict(
+  m_pts_baseline_rewb_train, 
+  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
+  allow_new_levels = TRUE
+) %>% 
+  as_tibble() %>% 
+  magrittr::set_colnames(pts_levels)
+
+set.seed(seed_pts_prediction)
+pred_pts_v2csreprss_rewb <- predict(
+  m_pts_v2csreprss_rewb_train, 
+  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
+  allow_new_levels = TRUE
+) %>% 
+  as_tibble() %>% 
+  magrittr::set_colnames(pts_levels)
+```
+
+## Separation plots
+
+### Baseline model
+
+```{r e2a-separation-baseline}
+# Match each column in pred_mat (predicted probabilities for each response level)
+pred_long_list <- lapply(1:ncol(pred_pts_baseline), 
+                         FUN = match_actual, 
+                         pred = pred_pts_baseline, 
+                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
+
+plot_data <- pred_long_list %>% 
+  bind_rows() %>% 
+  filter(!is.nan(fitted), !is.na(actual)) %>% 
+  group_by(plot_level) %>% 
+  arrange(plot_level, fitted) %>% 
+  mutate(index = row_number()) %>% 
+  ungroup()
+
+markers <- plot_data %>% 
+  group_by(plot_level) %>%
+  summarize(obs = n(), expected = sum(fitted),
+            marker = obs - expected + 1)
+
+n_in_group <- nrow(pred_pts_baseline)
+
+plot_data_condensed <- plot_data %>% 
+  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
+  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
+  mutate(rleid = cumsum(rleid)) %>% 
+  group_by(plot_level, rleid) %>% 
+  slice(1) %>% 
+  group_by(plot_level) %>% 
+  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
+  ungroup()
+
+ggplot(plot_data_condensed) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
+  geom_line(aes(x = index, y = fitted), size = 0.3) +
+  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
+  scale_fill_manual(values = c("grey90", "#2ECC40")) +
+  guides(fill = FALSE) +
+  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
+  theme_void(base_family = "Inter Bold")
+```
+
+### Model with civil society repression
+
+```{r e2a-separation-cs}
+pred_long_list <- lapply(1:ncol(pred_pts_v2csreprss), 
+                         FUN = match_actual, 
+                         pred = pred_pts_v2csreprss, 
+                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
+
+plot_data <- pred_long_list %>% 
+  bind_rows() %>% 
+  filter(!is.nan(fitted), !is.na(actual)) %>% 
+  group_by(plot_level) %>% 
+  arrange(plot_level, fitted) %>% 
+  mutate(index = row_number()) %>% 
+  ungroup()
+
+markers <- plot_data %>% 
+  group_by(plot_level) %>%
+  summarize(obs = n(), expected = sum(fitted),
+            marker = obs - expected + 1)
+
+n_in_group <- nrow(pred_pts_v2csreprss)
+
+plot_data_condensed <- plot_data %>% 
+  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
+  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
+  mutate(rleid = cumsum(rleid)) %>% 
+  group_by(plot_level, rleid) %>% 
+  slice(1) %>% 
+  group_by(plot_level) %>% 
+  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
+  ungroup()
+
+ggplot(plot_data_condensed) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
+  geom_line(aes(x = index, y = fitted), size = 0.3) +
+  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
+  scale_fill_manual(values = c("grey90", "#2ECC40")) +
+  guides(fill = FALSE) +
+  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
+  theme_void(base_family = "Inter Bold")
+```
+
+### Baseline model (REWB)
+
+```{r e2a-separation-baseline-rewb}
+# Match each column in pred_mat (predicted probabilities for each response level)
+pred_long_list <- lapply(1:ncol(pred_pts_baseline_rewb), 
+                         FUN = match_actual, 
+                         pred = pred_pts_baseline_rewb, 
+                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
+
+plot_data <- pred_long_list %>% 
+  bind_rows() %>% 
+  filter(!is.nan(fitted), !is.na(actual)) %>% 
+  group_by(plot_level) %>% 
+  arrange(plot_level, fitted) %>% 
+  mutate(index = row_number()) %>% 
+  ungroup()
+
+markers <- plot_data %>% 
+  group_by(plot_level) %>%
+  summarize(obs = n(), expected = sum(fitted),
+            marker = obs - expected + 1)
+
+n_in_group <- nrow(pred_pts_baseline_rewb)
+
+plot_data_condensed <- plot_data %>% 
+  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
+  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
+  mutate(rleid = cumsum(rleid)) %>% 
+  group_by(plot_level, rleid) %>% 
+  slice(1) %>% 
+  group_by(plot_level) %>% 
+  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
+  ungroup()
+
+ggplot(plot_data_condensed) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
+  geom_line(aes(x = index, y = fitted), size = 0.3) +
+  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
+  scale_fill_manual(values = c("grey90", "#2ECC40")) +
+  guides(fill = FALSE) +
+  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
+  theme_void(base_family = "Inter Bold")
+```
+
+### Model with civil society repression (REWB)
+
+```{r e2a-separation-cs-rewb}
+pred_long_list <- lapply(1:ncol(pred_pts_v2csreprss_rewb), 
+                         FUN = match_actual, 
+                         pred = pred_pts_v2csreprss_rewb, 
+                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
+
+plot_data <- pred_long_list %>% 
+  bind_rows() %>% 
+  filter(!is.nan(fitted), !is.na(actual)) %>% 
+  group_by(plot_level) %>% 
+  arrange(plot_level, fitted) %>% 
+  mutate(index = row_number()) %>% 
+  ungroup()
+
+markers <- plot_data %>% 
+  group_by(plot_level) %>%
+  summarize(obs = n(), expected = sum(fitted),
+            marker = obs - expected + 1)
+
+n_in_group <- nrow(pred_pts_v2csreprss_rewb)
+
+plot_data_condensed <- plot_data %>% 
+  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
+  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
+  mutate(rleid = cumsum(rleid)) %>% 
+  group_by(plot_level, rleid) %>% 
+  slice(1) %>% 
+  group_by(plot_level) %>% 
+  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
+  ungroup()
+
+ggplot(plot_data_condensed) +
+  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
+  geom_line(aes(x = index, y = fitted), size = 0.3) +
+  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
+  scale_fill_manual(values = c("grey90", "#2ECC40")) +
+  guides(fill = FALSE) +
+  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
+  theme_void(base_family = "Inter Bold")
+```
+
+## Prediction diagnostics
+
+```{r e2a-improved-cases}
+pred_pts_baseline_categories <- pred_pts_baseline %>% 
+  rownames_to_column() %>% 
+  pivot_longer(-rowname) %>% 
+  group_by(rowname) %>% 
+  filter(rank(-value, ties.method = "last") == 1) %>% 
+  ungroup() %>% 
+  select(predicted = name)
+
+pred_pts_v2csreprss_categories <- pred_pts_v2csreprss %>% 
+  rownames_to_column() %>% 
+  pivot_longer(-rowname) %>% 
+  group_by(rowname) %>% 
+  filter(rank(-value, ties.method = "last") == 1) %>% 
+  ungroup() %>% 
+  select(predicted = name)
+
+pred_pts_baseline_categories_rewb <- pred_pts_baseline_rewb %>% 
+  rownames_to_column() %>% 
+  pivot_longer(-rowname) %>% 
+  group_by(rowname) %>% 
+  filter(rank(-value, ties.method = "last") == 1) %>% 
+  ungroup() %>% 
+  select(predicted = name)
+
+pred_pts_v2csreprss_categories_rewb <- pred_pts_v2csreprss_rewb %>% 
+  rownames_to_column() %>% 
+  pivot_longer(-rowname) %>% 
+  group_by(rowname) %>% 
+  filter(rank(-value, ties.method = "last") == 1) %>% 
+  ungroup() %>% 
+  select(predicted = name)
+
+pts_cat_preds <- canary_testing_lagged %>% 
+  select(country, year, actual = PTS_factor_lead1) %>% 
+  mutate(pred_baseline = pred_pts_baseline_categories$predicted,
+         pred_v2csreprss = pred_pts_v2csreprss_categories$predicted) %>% 
+  filter(!is.na(actual)) %>%
+  mutate(is_correct_baseline = actual == pred_baseline,
+         is_correct_v2csreprss = actual == pred_v2csreprss)
+
+pts_cat_preds_rewb <- canary_testing_lagged %>% 
+  select(country, year, actual = PTS_factor_lead1) %>% 
+  mutate(pred_baseline = pred_pts_baseline_categories_rewb$predicted,
+         pred_v2csreprss = pred_pts_v2csreprss_categories_rewb$predicted) %>% 
+  filter(!is.na(actual)) %>%
+  mutate(is_correct_baseline = actual == pred_baseline,
+         is_correct_v2csreprss = actual == pred_v2csreprss)
+
+# Improved predictions
+pts_improved <- pts_cat_preds %>% 
+  filter(!is_correct_baseline & is_correct_v2csreprss) %>% 
+  select(Country = country, Year = year, Actual = actual,
+         `CS repression included` = pred_v2csreprss,
+         `Baseline` = pred_baseline)
+
+pts_improved_rewb <- pts_cat_preds_rewb %>% 
+  filter(!is_correct_baseline & is_correct_v2csreprss) %>% 
+  select(Country = country, Year = year, Actual = actual,
+         `CS repression included` = pred_v2csreprss,
+         `Baseline` = pred_baseline)
+
+pts_improved %>% 
+  kbl() %>% 
+  kable_styling()
+```
+
+```{r e2a-correct-not-correct}
+correct_lookup <- tribble(
+  ~name, ~nice_name,
+  "is_correct_v2csreprss", "CS repression included",
+  "is_correct_baseline", "Baseline"
+) %>% mutate(nice_name = fct_inorder(nice_name, ordered = TRUE))
+
+pts_pred_table <- pts_cat_preds %>% 
+  pivot_longer(starts_with("is_correct")) %>% 
+  group_by(name, value) %>% 
+  summarize(n = n()) %>% 
+  ungroup() %>% 
+  left_join(correct_lookup, by = "name") %>% 
+  mutate(Prediction = ifelse(value == TRUE, "Correct", "Wrong")) %>% 
+  arrange(nice_name) %>% 
+  select(-name, -value) %>% 
+  pivot_wider(names_from = "nice_name", values_from = "n")
+
+pts_pred_table_rewb <- pts_cat_preds_rewb %>% 
+  pivot_longer(starts_with("is_correct")) %>% 
+  group_by(name, value) %>% 
+  summarize(n = n()) %>% 
+  ungroup() %>% 
+  left_join(correct_lookup, by = "name") %>% 
+  mutate(Prediction = ifelse(value == TRUE, "Correct", "Wrong")) %>% 
+  arrange(nice_name) %>% 
+  select(-name, -value) %>% 
+  pivot_wider(names_from = "nice_name", values_from = "n")
+
+pts_pred_table %>% 
+  kbl(align = "lcc") %>% 
+  kable_styling()
+
+pts_pred_table_rewb %>% 
+  kbl(align = "lcc") %>% 
+  kable_styling()
+```
+
+\
+
+# E~2b~: Civil society environment and physical violence
+
+```{r e2b-predictions, warning=FALSE}
+seed_clphy_prediction <- 7285  # From random.org
+
+set.seed(seed_clphy_prediction)
+pred_clphy_baseline <- predict(m_clphy_baseline_train, 
+                          newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
+                          allow_new_levels = TRUE)
+
+set.seed(seed_clphy_prediction)
+pred_clphy_v2csreprss <- predict(m_clphy_v2csreprss_train, 
+                 newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
+                 allow_new_levels = TRUE)
+
+pred_clphy_baseline_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clphy_lead1) %>% 
+  bind_cols(as_tibble(pred_clphy_baseline)) %>% 
+  filter(!is.na(v2x_clphy_lead1))
+
+pred_clphy_v2csreprss_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clphy_lead1) %>% 
+  bind_cols(as_tibble(pred_clphy_v2csreprss)) %>% 
+  filter(!is.na(v2x_clphy_lead1))
+```
+
+## Improvement from baseline models
+
+```{r e2b-pred-plots, warning=FALSE}
+plot_baseline <- ggplot(pred_clphy_baseline_test, 
+                        aes(x = v2x_clphy_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Baseline",
+       x = "Actual physical violence index (t + 1)",
+       y = "Predicted physical violence index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_v2csreprss <- ggplot(pred_clphy_v2csreprss_test, 
+                          aes(x = v2x_clphy_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Added predictor",
+       x = "Actual physical violence index (t + 1)",
+       y = "Predicted physical violence index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_baseline | plot_v2csreprss
+```
+
+```{r e2b-metrics}
+lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
+
+bind_rows(lotsa_metrics(pred_clphy_baseline_test, 
+                        truth = v2x_clphy_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Baseline"),
+          lotsa_metrics(pred_clphy_v2csreprss_test, 
+                        truth = v2x_clphy_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Added predictor")) %>% 
+  select(Model, .metric, .estimate) %>% 
+  pivot_wider(names_from = ".metric", values_from = ".estimate")
+```
+
+## Most improved countries
+
+```{r e2b-most-improved}
+most_improved_clphy <- bind_cols(
+  pred_clphy_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
+    select(country, gwcode, year, v2x_clphy_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clphy_v2csreprss_test %>% 
+    mutate(error_v2csreprss = Estimate - v2x_clphy_lead1) %>% 
+    select(estimate_v2csreprss = Estimate, error_v2csreprss)
+) %>% 
+  # mutate(across(starts_with("error"), ~round(., 4))) %>% 
+  mutate(improved = error_v2csreprss < 0 & abs(error_v2csreprss) < abs(error_baseline)) %>% 
+  mutate(diff = error_v2csreprss - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clphy)
+
+most_improved_clphy %>% 
+  select(Country = country, Year = year, 
+         `Actual physical violence index (t + 1)` =  v2x_clphy_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_v2csreprss,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+\
+
+# E~2c~: Civil society environment and civil liberties
+
+```{r e2c-predictions, warning=FALSE}
+seed_clpriv_prediction <- 6670  # From random.org
+
+set.seed(seed_clpriv_prediction)
+pred_clpriv_baseline <- predict(m_clpriv_baseline_train, 
+                                newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
+                                allow_new_levels = TRUE)
+
+set.seed(seed_clpriv_prediction)
+pred_clpriv_v2csreprss <- predict(m_clpriv_v2csreprss_train, 
+                                  newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
+                                  allow_new_levels = TRUE)
+
+pred_clpriv_baseline_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
+  bind_cols(as_tibble(pred_clpriv_baseline)) %>% 
+  filter(!is.na(v2x_clpriv_lead1))
+
+pred_clpriv_v2csreprss_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
+  bind_cols(as_tibble(pred_clpriv_v2csreprss)) %>% 
+  filter(!is.na(v2x_clpriv_lead1))
+```
+
+## Improvement from baseline models
+
+```{r e2c-pred-plots, warning=FALSE}
+plot_baseline <- ggplot(pred_clpriv_baseline_test, 
+                        aes(x = v2x_clpriv_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Baseline",
+       x = "Actual private civil liberties index (t + 1)",
+       y = "Predicted private civil liberties index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_v2csreprss <- ggplot(pred_clpriv_v2csreprss_test, 
+                          aes(x = v2x_clpriv_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Added predictor",
+       x = "Actual private civil liberties index (t + 1)",
+       y = "Predicted private civil liberties index (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_baseline | plot_v2csreprss
+```
+
+```{r e2c-metrics}
+lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
+
+bind_rows(lotsa_metrics(pred_clpriv_baseline_test, 
+                        truth = v2x_clpriv_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Baseline"),
+          lotsa_metrics(pred_clpriv_v2csreprss_test, 
+                        truth = v2x_clpriv_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Added predictor")) %>% 
+  select(Model, .metric, .estimate) %>% 
+  pivot_wider(names_from = ".metric", values_from = ".estimate")
+```
+
+Hey! This one has a somewhat better change in MSE!
+
+```{r}
+percent_format(accuracy = 0.01)((0.0332 - 0.0339) / 0.0339)
+```
+
+## Most improved countries
+
+```{r e2c-most-improved}
+most_improved_clpriv <- bind_cols(
+  pred_clpriv_baseline_test %>% 
+    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
+    select(country, gwcode, year, v2x_clpriv_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_clpriv_v2csreprss_test %>% 
+    mutate(error_v2csreprss = Estimate - v2x_clpriv_lead1) %>% 
+    select(estimate_v2csreprss = Estimate, error_v2csreprss)
+) %>% 
+  # mutate(across(starts_with("error"), ~round(., 4))) %>% 
+  mutate(improved = error_v2csreprss < 0 & abs(error_v2csreprss) < abs(error_baseline)) %>% 
+  mutate(diff = error_v2csreprss - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_clpriv)
+
+most_improved_clpriv %>% 
+  select(Country = country, Year = year, 
+         `Actual private civil liberties index (t + 1)` =  v2x_clpriv_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_v2csreprss,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```

### 2021-04-02 R/funs_data-cleaning.R

@@ -21,13 +21,19 @@ create_panel_skeleton <- function() {
   # Serbia & Montenegro as 345 in COW codes (see
   # https://www.andybeger.com/states/articles/differences-gw-cow.html)
   #
-  # Also, because the World Bank doesn't include it in the WDI, we omit Taiwan (713)
+  # Following V-Dem, we treat Czechoslovakia (GW/COW 315) and Czech Republic
+  # (GW/COW 316) as the same continuous country (V-Dem has both use ID 157).
+  #
+  # Also, because the World Bank doesn't include it in the WDI, we omit
+  # Taiwan (713). We also omit East Germany (265) and South Yemen (680).
 
-  panel_skeleton <- state_panel(1995, 2014, partial = "any") %>%
+  panel_skeleton <- state_panel(1990, 2014, partial = "any") %>%
     # Remove microstates
     filter(!(gwcode %in% microstates$gwcode)) %>%
-    # Remove Taiwan, the Bahamas, Belize, and Brunei
-    filter(!(gwcode %in% c(713, 31, 80, 835))) %>%
+    # Deal with Czechia
+    mutate(gwcode = recode(gwcode, `315` = 316L)) %>%
+    # Remove East Germany, South Yemen, Taiwan, the Bahamas, Belize, and Brunei
+    filter(!(gwcode %in% c(265, 680, 713, 31, 80, 835))) %>%
     mutate(cowcode = countrycode(gwcode, origin = "gwn", destination = "cown",
                                  custom_match = c("816" = 816L, "340" = 345L)),
            country = countrycode(cowcode, origin = "cown", destination = "country.name",
@@ -172,8 +178,12 @@ load_clean_pts <- function(path, skeleton) {
     mutate(PTS = coalesce(PTS_S, PTS_A)) %>%
     mutate(gwcode = countrycode(COW_Code_N, origin = "cown", destination = "gwn",
                                 custom_match = c("679" = 678L, "816" = 816L))) %>%
+    # Get rid of things like the EU, USSR, Crimea, Palestine, and Western Sahara
+    filter(!is.na(gwcode)) %>%
     select(year = Year, gwcode, PTS) %>%
-    mutate(PTS_factor = factor(PTS, levels = 1:5, labels = paste0("Level ", 1:5)))
+    mutate(PTS_factor = factor(PTS, levels = 1:5,
+                               labels = paste0("Level ", 1:5),
+                               ordered = TRUE))
 
   return(pts_clean)
 }
[…]

### 2021-04-02 R/models_clphy.R

@@ -1,0 +1,288 @@
+# Settings ----------------------------------------------------------------
+
+clphy_setup <- function() {
+  # Settings
+  CHAINS <- 4
+  ITER <- 2000
+  WARMUP <- 1000
+  BAYES_SEED <- 4045  # From random.org
+
+  # Priors
+  priors_vague <- c(set_prior("normal(0, 10)", class = "Intercept"),
+                    set_prior("normal(0, 3)", class = "b"),
+                    set_prior("cauchy(0, 1)", class = "sd"))
+
+  return(list(chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
+              priors_vague = priors_vague))
+}
+
+clphy_settings <- clphy_setup()
+
+
+# Regular models ----------------------------------------------------------
+
+f_clphy_baseline <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(v2x_clphy_lead1 ~ v2x_clphy +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = gaussian(),
+    prior = clphy_settings$priors_vague,
+    control = list(adapt_delta = 0.9),
+    data = dat,
+    chains = clphy_settings$chains, iter = clphy_settings$iter,
+    warmup = clphy_settings$warmup, seed = clphy_settings$seed)
+
+  return(model)
+}
+
+f_clphy_total <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(v2x_clphy_lead1 ~ barriers_total + barriers_total_lag1 +
+         v2x_clphy +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = gaussian(),
+    prior = clphy_settings$priors_vague,
+    control = list(adapt_delta = 0.9),
+    data = dat,
+    chains = clphy_settings$chains, iter = clphy_settings$iter,
+    warmup = clphy_settings$warmup, seed = clphy_settings$seed)
+
+  return(model)
+}
+
+f_clphy_advocacy <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(v2x_clphy_lead1 ~ advocacy + advocacy_lag1 +
+         v2x_clphy +
[…]

### 2021-04-02 R/models_clpriv.R

@@ -1,0 +1,288 @@
+# Settings ----------------------------------------------------------------
+
+clpriv_setup <- function() {
+  # Settings
+  CHAINS <- 4
+  ITER <- 2000
+  WARMUP <- 1000
+  BAYES_SEED <- 9324  # From random.org
+
+  # Priors
+  priors_vague <- c(set_prior("normal(0, 10)", class = "Intercept"),
+                    set_prior("normal(0, 3)", class = "b"),
+                    set_prior("cauchy(0, 1)", class = "sd"))
+
+  return(list(chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
+              priors_vague = priors_vague))
+}
+
+clpriv_settings <- clpriv_setup()
+
+
+# Regular models ----------------------------------------------------------
+
+f_clpriv_baseline <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(v2x_clpriv_lead1 ~ v2x_clpriv +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = gaussian(),
+    prior = clpriv_settings$priors_vague,
+    control = list(adapt_delta = 0.9),
+    data = dat,
+    chains = clpriv_settings$chains, iter = clpriv_settings$iter,
+    warmup = clpriv_settings$warmup, seed = clpriv_settings$seed)
+
+  return(model)
+}
+
+f_clpriv_total <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(v2x_clpriv_lead1 ~ barriers_total + barriers_total_lag1 +
+         v2x_clpriv +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = gaussian(),
+    prior = clpriv_settings$priors_vague,
+    control = list(adapt_delta = 0.9),
+    data = dat,
+    chains = clpriv_settings$chains, iter = clpriv_settings$iter,
+    warmup = clpriv_settings$warmup, seed = clpriv_settings$seed)
+
+  return(model)
+}
+
+f_clpriv_advocacy <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
[…]

### 2021-04-02 R/models_details.R

@@ -1,0 +1,127 @@
+create_model_df <- function() {
+  models <- tribble(
+    ~model, ~outcome_var, ~explan_var,
+    # Models for the political terror score (PTS)
+    "m_pts_baseline", "Political terror", "Baseline",
+    "m_pts_total", "Political terror", "Total legal barriers",
+    "m_pts_advocacy", "Political terror", "Barriers to advocacy",
+    "m_pts_entry", "Political terror", "Barriers to entry",
+    "m_pts_funding", "Political terror", "Barriers to funding",
+    "m_pts_v2csreprss", "Political terror", "Civil society repression",
+
+    "m_pts_baseline_rewb", "Political terror", "Baseline",
+    "m_pts_total_rewb", "Political terror", "Total legal barriers",
+    "m_pts_advocacy_rewb", "Political terror", "Barriers to advocacy",
+    "m_pts_entry_rewb", "Political terror", "Barriers to entry",
+    "m_pts_funding_rewb", "Political terror", "Barriers to funding",
+    "m_pts_v2csreprss_rewb", "Political terror", "Civil society repression",
+
+    # Models for physical violence (v2x_clphy)
+    "m_clphy_baseline", "Physical violence", "Baseline",
+    "m_clphy_total", "Physical violence", "Total legal barriers",
+    "m_clphy_advocacy", "Physical violence", "Barriers to advocacy",
+    "m_clphy_entry", "Physical violence", "Barriers to entry",
+    "m_clphy_funding", "Physical violence", "Barriers to funding",
+    "m_clphy_v2csreprss", "Physical violence", "Civil society repression",
+
+    "m_clphy_baseline_rewb", "Physical violence", "Baseline",
+    "m_clphy_total_rewb", "Physical violence", "Total legal barriers",
+    "m_clphy_advocacy_rewb", "Physical violence", "Barriers to advocacy",
+    "m_clphy_entry_rewb", "Physical violence", "Barriers to entry",
+    "m_clphy_funding_rewb", "Physical violence", "Barriers to funding",
+    "m_clphy_v2csreprss_rewb", "Physical violence", "Civil society repression",
+
+    # Models for private civil liberties (v2x_clpriv)
+    "m_clpriv_baseline", "Private civil liberties", "Baseline",
+    "m_clpriv_total", "Private civil liberties", "Total legal barriers",
[…]

### 2021-04-02 R/models_pts.R

@@ -1,0 +1,276 @@
+# Settings ----------------------------------------------------------------
+
+pts_setup <- function() {
+  # Settings
+  CHAINS <- 4
+  ITER <- 2000
+  WARMUP <- 1000
+  BAYES_SEED <- 2009  # From random.org
+
+  # Priors
+  priors_vague <- c(set_prior("normal(0, 10)", class = "Intercept"),
+                    set_prior("normal(0, 3)", class = "b"),
+                    set_prior("cauchy(0, 1)", class = "sd"))
+
+  return(list(chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
+              priors_vague = priors_vague))
+}
+
+pts_settings <- pts_setup()
+
+
+# Regular models ----------------------------------------------------------
+
+f_pts_baseline <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(PTS_factor_lead1 ~ PTS_factor +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = cumulative(),
+    prior = pts_settings$priors_vague,
+    data = dat,
+    chains = pts_settings$chains, iter = pts_settings$iter,
+    warmup = pts_settings$warmup, seed = pts_settings$seed)
+
+  return(model)
+}
+
+f_pts_total <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(PTS_factor_lead1 ~ barriers_total + barriers_total_lag1 +
+         PTS_factor +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = cumulative(),
+    prior = pts_settings$priors_vague,
+    data = dat,
+    chains = pts_settings$chains, iter = pts_settings$iter,
+    warmup = pts_settings$warmup, seed = pts_settings$seed)
+
+  return(model)
+}
+
+f_pts_advocacy <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(PTS_factor_lead1 ~ advocacy + advocacy_lag1 +
+         PTS_factor +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
[…]

### 2021-04-02 _packages.R

@@ -4,12 +4,12 @@ library(broom)
 library(broom.mixed)
 library(bs4Dash)
 library(clustermq)
+library(cmdstanr)
 library(colorspace)
 library(countrycode)
 library(DT)
 library(flextable)
 library(future)
-library(GGally)
 library(ggtext)
 library(gt)
 library(haven)

### 2021-04-02 _targets.R

@@ -1,13 +1,25 @@
 library(targets)
 library(tarchetypes)
+library(tibble)
 
 # General variables
 csl <- "pandoc/csl/apa.csl"
 bibstyle <- "bibstyle-chicago-authordate"
 
-source("R/funs_data-cleaning.R")
-# source("R/funs_knitting.R")
-source("R/funs_notebook.R")
+suppressPackageStartupMessages(library(brms))
+
+# By default, R uses polynomial contrasts for ordered factors in linear models
+# options("contrasts")
+# So make ordered factors use treatment contrasts instead
+options(contrasts = rep("contr.treatment", 2))
+# Or do it on a single variable:
+# contrasts(df$x) <- "contr.treatment"
+
+set.seed(9936)  # From random.org
+
+# Bayes-specific stuff
+options(mc.cores = parallel::detectCores(),
+        brms.backend = "cmdstanr")
 
 options(tidyverse.quiet = TRUE,
         dplyr.summarise.inform = FALSE)
@@ -19,7 +31,15 @@ tar_option_set(packages = c("tidyverse", "countrycode", "states", "WDI", "here",
                             "janitor", "kableExtra", "huxtable", "modelsummary",
                             "knitr", "withr", "flextable", "testthat", "DT",
                             "brms", "tidybayes", "broom", "broom.mixed", "scico",
-                            "ggtext", "GGally", "colorspace", "lme4"))
+                            "ggtext", "colorspace", "lme4", "cmdstanr"))
+
+source("R/funs_data-cleaning.R")
+# source("R/funs_knitting.R")
+source("R/funs_notebook.R")
+source("R/models_details.R")
+source("R/models_pts.R")
+source("R/models_clphy.R")
+source("R/models_clpriv.R")
 
 list(
   # Define raw data files
@@ -72,12 +92,143 @@ list(
   tar_target(un_pop, load_clean_un_pop(un_pop_raw_file, skeleton, wdi_clean)),
   tar_target(un_gdp, load_clean_un_gdp(un_gdp_constant_raw_file,
                                        un_gdp_current_raw_file, skeleton)),
-  tar_target(panel_done, combine_data(skeleton, chaudhry_clean, pts_clean,
[…]

### 2021-04-02 manuscript/manuscript.Rmd
Suparna additions

@@
   Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions.
-While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of laws—many of which appear mundane on their face—represent a bureaucratic form of repressive that could be indicative of more severe human rights abuses and backsliding.
+While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of attempts to repress civil society organization-many of which are sanctioned by law—represent a bureaucratic form of repression that could be indicative of more severe human rights abuses and backsliding.
 This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
-In this paper, we ask: do legal crackdowns on NGOs predict broader civil society repression?
+In this paper, we ask: do crackdowns on NGOs predict broader civil society repression?
 We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
@@
 
-Governments across the globe have been cracking down on civil society organizations (CSOs) -- a phenomenon referred to as closing civic space or shrinking civic space (CITE).
+Governments across the globe have been cracking down on civil society organizations (CSOs) -- a phenomenon referred to as closing civic space or shrinking civic space (Carothers & Brechenmacher, 2014; Dupuy, Ron, & Prakash, 2016; Chaudhry, 2016; Dupuy & Prakash, 2018).
 The non-violent nature of this repression is particularly notable.
-The last two decades have seen a proliferation of laws designed to limit the influence of civil society organizations, with more than 100 countries obstructing, repressing, or closing the legal environment for civil society.
+The last two decades have seen a proliferation of steps designed to limit the influence of civil society organizations, with more than 100 countries obstructing, repressing, or foricbly shutting down non-governmental organizations (NGOs).
 Since 2013, 91 countries had proposed or enacted 244 measures restricting civil society [@icnl:2021].
@@
 
-WHAT KINDS OF LAWS, WHAT DO THESE LAWS DO.
+Such hostility is not unique to autocratic governments or even “illiberal democracies” – as Viktor
+Orban referred to in his vision for Hungary [https://www.foreignaffairs.com/articles/central-europe/2018-04-06/how-illiberal-leaders-attack-civil-society].
+It is increasingly pervasive, including among
+democracies.
+Over the past decade, India has canceled the licenses of tens of thousands of NGOs.
+It also targeted major groups such as Greenpeace International and Ford Foundation (Press Trust of India.
+(2019, December 4).
+14,5000 NGOs banned by government from receiving foreign funds.
+LiveMint.
+Retrieved from: https://www.livemint.com/news/india/14-500-ngos-banned-by-govt-from-receiving-foreign-funds-11575456836000.html).
+In Canada, several prominent
+environmental NGOs were targeted for opposing the Northern Gateway pipeline and Canadian mining companies’ initiatives abroad [Achtenberg.
+1992.
+\Environmental Advocacy: Challenges to Environmental Groups Rights
+to Assemble, Associate and Express their Opinions." Global Trends in NGO Law 7
+(1)].
 
+There is no doubt that violent attacks on these groups are often an effective means of curbing dissent.
+But states have also started implementing ‘administrative crackdown,’ or the passage of laws to create barriers to entry, funding, and advocacy by NGOs (Chaudhry, 2016).
 The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations.
 While in some cases this has led to the depoliticization of NGOs and avoidance of direct political activism by CSOs, states cannot soften or neutralize all forms of political activities in subtle, legal ways that they have with NGOs.
-Soon or later, states need to deal with threats in a more violent, confrontational manner.
-Studying these NGO laws can thus be the canary in the coal mine which signals the states that intend to continue down this repressive path.
+Sooner or later, states need to deal with threats in a more violent, confrontational manner.
+Studying these NGO laws can thus be the canary in the coal mine which signals the states which intend to continue down this repressive path.
 What does state targeting of NGOs tell us about a state's broader respect for civil society and the overall level of human rights repression?
@@
 Our analysis shows FILL
+MAKE DIFFERENCE BETWEEN DE JURE AND DE FACTO CLEAR
 
@@
 
-ROADMAP
+Below, we first look at existing literature on repression and political violence, outlining state motivations to repress NGOs.
+We then elaborate on why attacking NGOs may be an important predictor of subsequent repression.
+Using both original data as well as data from the V-DEM dataset, we show that ...
 
@@
 
-## State repression of NGOs
+## State repression of NGOs and effects on subsequent repression
 
@@
 
-Why might repressive states start with non-violent forms of repression?
-WHY THE GROWTH IN THESE LAWS
-As someone points out, states have toned down 'open, violent confrontation' and favor the development of a 'civilized' oppression.
+There is no doubt that violence is often effective at curbing dissent. But it can also backfire,
+leading to widespread protests, decreasing leaders’ legitimacy, while increasing their criminal
+liability (Kim and Sikkink 2010, Sikkink 2011).
+In contrast to violence, administrative crackdown has fewer adverse consequences – citizens may see it as regulation rather than repression, resulting in little to no counter-mobilization.
+It may also circumvent concerns among state security or bureaucratic agents about illegitimate orders based on violent repression (Stephan and Chenoweth, 2008).
+The international consequences are also fewer, since laws, unlike violence, rarely invite condemnation or threats of aid withdrawal (Carothers and Brechenmacher 2014).
 
-Leaders want to avoid accountability. Shape the narrative of their performance both domestically and internationally. Don't like being shamed.
-Can be the beginning of a deteriorating human rights situation.
+We argue that this crackdown on NGOs foreshadows future government transgressions.
+Leaders want to avoid accountability.
+Civil society organizations, including NGOs, can help shape the narrative of leaders' performance both domestically and internationally.
+Monitoring by NGOs and subsequent shaming can
+include significant external revenue loss to states in the form of loss of aid, trade, and
+foreign direct investments (Keck and Sikkink 1998; and Barry, Chad Clay, and Flynn 2013)
 
-In the aftermath of the failed coup attempt in Turkey in 2016, the government initiated a widespread crackdown on civil society, leading to the closure of almost 1500 NGOs soon after the group.
-However, this crackdown, ``spiraled far beyond those with any possible connection to the coup itself." In October 2017, the government levied terrorism charges against human rights activists, including on Amnesty International's Turkey Director and Chair.
-The government also imprisoned an increasing number of journalists in 2017 and 2018, and issued arrest warrants for numerous academics in 2018.
+Government attempts to repress NGOs for the above can be the beginning of a deteriorating human rights situation.
+Such repression reflects the government's willingness and capability to use measures that can make it avoid accountability.
+Once a state targets NGOs, over time it may grow less hesitant to apply repression more widely.
 
-##Expectations
+In exploring the impact of state crackdown on NGOs on subsequent human rights conditions, we look at both de jure steps-formal legislation that seeks to repress NGOs, as well as the de facto implementation of these steps.
+This is because while states may pass anti-NGO laws, these laws can also lie dormant.
+For instance, Russia passed its 2015 Undesirable Organizations Law with the purpose of targeting and eliminating specific foreign-connected NGOs it deemed dangerous.
+One of the law's sponsors, Aleksandr Tarnavsky, described the law as a preventative measure that would not affect the majority of NGOs working in Russia.
+Rather, the law would be a "weapon hanging on the wall that never fires" and stand as a warning to potentially uncooperative NGOs [@Kozenko:2015].
 
-#Methods
+Simply noting the passage of (or counting) these laws may therefore miss the effect of their de facto implementation.
+Moreover, the implementation of these laws may not be limited to its legal character.
+The govenment may also engage in harassment of NGOs and activists to dissuage NGOs from operation or expressing themselves.
+This may include measures such as detentions, short-term incarceration, as well as beatings, threats to families and destruction of valuable property.
 
-#Results and Analysis
+As prior research in Egypt, Ethiopia and Russia points out, "rather than systematically enforcing all repressive legal measures-often impossible owing to capacity constraints," governments may choose to use extra-legal means to intimidate, harass or prosecute a few NGOs or activists.
+These cases, especially during moments or crises or contention, "highlight to the wider NGO community-and citizenry-that the government is willing and capable of using the law to repress dissent." [https://carnegieendowment.org/2017/05/18/repression-and-responses-cross-cutting-themes-pub-69961]
 
-#Conclusion and Implications
+- Expectation 1a [de jure]: If a country imposes an anti-NGO law, then it is likely to signal subsequent deteriorating human rights conditions
+- 
+- Expectation 1b [de facto]: If a country represses CSOs, then it is likely to see subsequent deteriorating human rights conditions
+
+# Methods
+
+I WANTED TO KEEP THE HYPOTHESES SIMPLE, YOU CAN TALK ABOUT THE DIFFERENT MEASURES HERE
+- Expectation 1a: Imposing an anti-NGO law (Chaudhry; total, advocacy, entry, funding) is likely to signal deteriorating human rights conditions: political terror (`PTS`)
+- E1b: Imposing an anti-NGO law (Chaudhry; total, advocacy, entry, funding) is likely to signal deteriorating human rights conditions: physical violence (`v2x_clphy`)
+- E1c: Imposing an anti-NGO law (Chaudhry; total, advocacy, entry, funding) is likely to signal deteriorating human rights conditions: private civil liberties (`v2x_clpriv`)
+
+- E2a: The reduction of civic space (`v2csreprss`) is likely to signal deteriorating human rights conditions: political terror (`PTS`)
+- E2b: The reduction of civic space (`v2csreprss`) is likely to signal deteriorating human rights conditions: physical violence (`v2x_clphy`)
+- E2c: The reduction of civic space (`v2csreprss`) is likely to signal deteriorating human rights conditions: private civil liberties (`v2x_clpriv`)
+
+# Results and Analysis
+
+# Conclusion and Implications
+Strengthening civil society is an important precondition for democratic transition and
+consolidation. It keeps governments accountable and protects civilians from the worst excesses
+of an abusive government

### 2021-04-04 analysis/02_descriptive-analysis.Rmd
PHEWWWW ALL READY FOR ISA

@@
 things_to_map <- canary %>% 
-  filter(year %in% c(1990, 2013)) %>% 
+  filter(year %in% c(1993, 2013)) %>% 
   select(country, year, iso3, barriers_total, PTS_factor, v2csreprss) %>% 
   pivot_wider(names_from = year, values_from = c(barriers_total, PTS_factor, v2csreprss)) %>% 
-  mutate(new_laws = barriers_total_2013 - barriers_total_1990,
+  mutate(new_laws = barriers_total_2013 - barriers_total_1993,
          new_laws = ifelse(new_laws <= 0, 0, new_laws),
-         new_laws = ceiling(new_laws)) %>% 
-  mutate(diff_csrepress = v2csreprss_2013 - v2csreprss_1990,
+         new_laws = ceiling(new_laws),
+         new_laws_cat = ifelse(new_laws >= 5, "5+", as.character(new_laws))) %>% 
+  mutate(diff_csrepress = v2csreprss_2013 - v2csreprss_1993,
          diff_csrepress_trunc = case_when(
@@
          )) %>% 
-  mutate(pct_change_csrepress = diff_csrepress / v2csreprss_1990,
+  mutate(pct_change_csrepress = diff_csrepress / v2csreprss_1993,
          pct_change_csrepress_trunc = case_when(
@@
 map_ngo_laws <- ggplot() +
-  geom_sf(data = map_data, aes(fill = factor(new_laws)),
+  geom_sf(data = map_data, aes(fill = factor(new_laws_cat)),
           color = "black", size = 0.1) +
   coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
-  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#BF0404")(seq(0, 1, length.out = 8)), 
-                    na.value = "grey80", breaks = 0:6) +
+  scale_fill_manual(values = seq_gradient_pal("#FFFFFF", "#CF4446")(seq(0, 1, length.out = 6)),
+                    na.value = "grey95", breaks = c(as.character(0:4), "5+")) +
   # scale_fill_manual(values = scico(7, palette = "devon", direction = -1),
@@
                              keyheight = unit(0.6, units = "lines"))) +
-  labs(fill = "Restrictive NGO laws passed between 1990 and 2014") +
+  labs(fill = "Restrictive NGO laws passed between 1993 and 2013") +
   theme_ngo() +

### 2021-04-04 analysis/03_laws-repression.Rmd
PHEWWWW ALL READY FOR ISA

@@
   labs(x = "Count of legal barriers",
-       y = "Predicted civil liberties index\n(higher values = less violence)") +
+       y = "Predicted civil liberties index\n(higher values = better protection)") +
   facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +

### 2021-04-04 manuscript/manuscript.Rmd
PHEWWWW ALL READY FOR ISA

--- 2021-03-27 manuscript/manuscript.Rmd
@@
   url: https://www.andrewheiss.com/
-date: "March 23, 2021"
+date: "April 3, 2021"
 published: This is an early draft of a working paper.
@@
   Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions.
-While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of laws—many of which appear mundane on their face—represent a bureaucratic form of repressive that could be indicative of more severe human rights abuses and backsliding.
+This new wave of attempts to repress civil society organization-many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
 This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
-In this paper, we ask: do legal crackdowns on NGOs predict broader civil society repression?
+In this paper, we ask: do crackdowns on NGOs predict broader human rights repression?
 We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
 These laws also make it easier for states to prevent and deter future large-scale popular mobilization.
-Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of attacks on journalists, independent media, academic freedom, and freedoms of expression and association.
+Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, physical violence, and violations of private civil liberties.
 This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deteriorations in space for civil society.
-keywords: "civil society restrictions, human rights, journalists"
+keywords: "civil society restrictions, human rights, political terror, civil liberties"
 reference-section-title: References
 bibliography: bibliography.bib
-csl: pandoc/csl/chicago-author-date.csl
 title-page: true
@@
 )
-
-library(tidyverse)
-library(here)
-
-source(here("lib", "graphics.R"))
 ```
 
-Governments across the globe have been cracking down on civil society organizations (CSOs) -- a phenomenon referred to as closing civic space or shrinking civic space (CITE).
-The non-violent nature of this repression is particularly notable.
-The last two decades have seen a proliferation of laws designed to limit the influence of civil society organizations, with more than 100 countries obstructing, repressing, or closing the legal environment for civil society.
-Since 2013, 91 countries had proposed or enacted 244 measures restricting civil society [@icnl:2021].
+```{r libraries-data, include=FALSE}
+library(tidyverse)
+library(targets)
+library(kableExtra)
+library(modelsummary)
+library(patchwork)
+library(scales)
+library(ggtext)
+library(sf)
+library(here)
+library(brms)
+
+withr::with_dir(here::here(), {
+  source(tar_read(plot_funs))
+
+  canary <- tar_read(panel)
+  tar_load(civicus_map_data)
+  tar_load(civicus_clean)
+
+  tar_load(c(m_pts_total, m_pts_advocacy, m_pts_entry, m_pts_funding,
+             m_clphy_total, m_clphy_advocacy, m_clphy_entry, m_clphy_funding,
+             m_clpriv_total, m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding,
+             m_pts_v2csreprss, m_clphy_v2csreprss, m_clpriv_v2csreprss))
+
+  # Model tables
+  tar_load(c(models_paper_pts, models_paper_clphy, models_paper_clpriv))
+
+  # Load lookup list for coefficients in regression tables
+  tar_load(coef_list)
+})
+
+# Temporary fake cache stuff
+mfx_e1a <- readRDS(here("temp_cache", "mfx_e1a.rds"))
+mfx_e1b <- readRDS(here("temp_cache", "mfx_e1b.rds"))
+mfx_e1c <- readRDS(here("temp_cache", "mfx_e1c.rds"))
+df_mfx_e2a <- readRDS(here("temp_cache", "df_mfx_e2a.rds"))
+df_mfx_e2b <- readRDS(here("temp_cache", "df_mfx_e2b.rds"))
+df_mfx_e2c <- readRDS(here("temp_cache", "df_mfx_e2c.rds"))
+```
+
+```{r calc-civicus}
+civicus <- civicus_clean %>%
+  count(category) %>% 
+  mutate(prop = n / sum(n)) %>% 
+  mutate(prop_nice = percent_format(accuracy = 1)(prop)) %>% 
+  split(.$category)
+```
+
+Governments across the globe have been cracking down on civil society organizations (CSOs), a phenomenon commonly referred to the closing or shrinking of civic space [@CarothersBrechenmacher:2014; @DPR:2016; @Chaudhry:2016; @DupuyPrakash:2018].
+The last two decades have seen a proliferation of steps designed to limit the influence of CSOs and non-governmental organizations (NGOs), and more than 100 countries have proposed or enacted 244 measures restricting, repressing, or shutting down civil society since 2013 [@icnl:2021].
 In Human Rights Watch's 2016 World Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory, and over the past decade, the majority of the world has seen a substantial narrowing of allowable civic space.
@@
 
-WHAT KINDS OF LAWS, WHAT DO THESE LAWS DO.
+```{r civicus-map, fig.cap="2020 CIVICUS Monitor civic space ratings"}
+ggplot() +
+  geom_sf(data = civicus_map_data, aes(fill = fct_rev(category)), size = 0.15, color = "black") +
+  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
+  scale_fill_viridis_d(option = "plasma", end = 0.9, 
+                       na.translate = FALSE, name = "Civic space") +
+  theme_void(base_size = 9, base_family = "Inter Light") +
+  theme(legend.position = "bottom",
+        legend.key.size = unit(0.7, "lines"))
+```
 
-The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations.
+This hostility to civil society is not unique to autocratic governments or even illiberal democracies [@AbramowitzSchenkkan:2018]—long-established liberal democracies have also increased restrictions on civil society in their countries.
+Over the past decade, India has canceled the licenses of tens of thousands of NGOs, targeted major groups such as Greenpeace International and Ford Foundation, and has banned 5,000 NGOs from receiving foreign funds [@press-trust-india:2015; @press-trust-india:2019].
+In 2013 Canada attempted to revoke the charitable status of civil society organizations for opposing the Northern Gateway pipeline and Canadian mining companies' initiatives abroad [@CIVICUS:2013].
+In 2019, activists from the US-based nonprofit No More Deaths were arrested for providing food and water to migrants a the US-Mexico border and faced a 20-year prison sentence before their convictions were overturned in 2020 [@Cramer:2020].
+
+Anti-civil society measures are occasionally violent, but notably, government repression of NGOs is generally non-violent.
+Rather than publicly arrest or beat activists, states implement "administrative crackdown," or the passage of laws to create barriers to NGO advocacy, entry, funding [@Chaudhry:2016].
+The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations [@Heiss:2019; @Heiss:2017].
 While in some cases this has led to the depoliticization of NGOs and avoidance of direct political activism by CSOs, states cannot soften or neutralize all forms of political activities in subtle, legal ways that they have with NGOs.
-Soon or later, states need to deal with threats in a more violent, confrontational manner.
-Studying these NGO laws can thus be the canary in the coal mine which signals the states that intend to continue down this repressive path.
+Sooner or later, states need to deal with threats to their stability in a more direct, violent, confrontational manner.
+Administrative NGO laws and general civil society repression could be an important early warning sign—or a canary in the coal mine—of worsening human rights repression in a state, signaling that a state will continue down the path of further repression.
 What does state targeting of NGOs tell us about a state's broader respect for civil society and the overall level of human rights repression?
@@
 
-ARGUMENT, METHODS, AND FINDINGS. 
-In this paper, we argue that information about NGO crackdown can be a valuable indicator of human rights trajectories.
-Such crackdown can act as an early warning signal for worsening repression, suggesting which countries are testing the waters with comparatively 'milder' forms of repression before enacting more violent forms of crackdown.
-To assess if attacks on NGOs and activists can provide us useful information about future repression, we use an original dataset on state crackdown on NGOs using legal repression across all countries from 1990-2013.
-WHAT ELSE DO WE USE.
-Our analysis shows FILL
+In this paper, we explore the power of anti-NGO repression in predicting human rights abuses, political terror, physical violence, and violations of private civil liberties.
+We argue that information about NGO crackdown can be a valuable indicator of human rights trajectories.
+In some cases, such crackdown can act as an early warning signal for worsening repression, suggesting which countries are testing the waters with comparatively "milder" methods of crackdown before enacting more violent forms of repression.
+To assess if attacks on NGOs and activists can provide us useful information about future repression, we use an original dataset on state crackdown on NGOs using legal repression across all countries from 1990–2013.
+We differentiate between two forms of civil society repression: official de jure anti-NGO restrictions that are codified in law, and general de facto levels of civil society repression.
+We propose and test two empirical expectations—that de jure and de factor restrictions predict future political terror, physical violence, and government encroachment on private civil liberties.
+Using multilevel Bayesian modeling, we find that formal de jure laws provide very little additional information when attempting to predict future repression.
+However, we find that accounting for more general civil society repression does boost our models' predictive power.
+Increasing de facto civil society repression predicts an increase in the probability of moderate political terror and results in a 3% decrease in indexes of physical violence and private civil liberties.
 
-Our paper makes an important contribution in predicting (IS THIS THE RIGHT WORD) the onset of repressive state policies.
+Our paper makes an important contribution in predicting the onset of repressive state policies.
 While structural factors such as levels of democracy, economic development, electoral competitiveness can identify countries that are likely to have more or less respect for civic freedoms, these factors are also slow to change over time.
-As such, they may not be particularly suitable for forecasting short-term trajectories, especially for moderatively repressive countries.
+As such, they may not be particularly suitable for forecasting short-term trajectories, especially for moderately repressive countries.
 On the other hand, state repression of NGOs is more dynamic and provides information about changing levels of human rights standards and repression in subsequent years.
 
-ROADMAP
+Below, we first look at existing literature on repression and political violence, outlining state motivations to repress NGOs.
+We then elaborate on why attacking NGOs may be an important predictor of subsequent repression.
+Using both original data as well as data from several existing datasets, we build an ensemble of predictive models and explore (1) the marginal effects of civil society repression on different forms of broader human rights repression, and (2) the out-of-sample predictive performance of each model.
+We conclude with a discussion of our findings and their implications for assessing the repression of human rights.
 
-# Assessing Changes in Government Repression
+# Government repression and NGO restrictions
 
-Repression is the use of coercive action against an individual or organization, within the territorial jurisdiction of the state, for the purpose of imposing a cost on the target as well as deterring specific activities and/or beliefs perceived to be challenging to government personnel, practices, or institutions (Goldstein 1978, xxvii; Poe and Tate 1994; Davenport 2007b; and Ritter and Conrad 2016).
+Repression is the use of coercive action against an individual or organization, within the territorial jurisdiction of the state, for the purpose of imposing a cost on the target as well as deterring specific activities and/or beliefs perceived to be challenging to government personnel, practices, or institutions [@Goldstein:1978, p.
+xxvii; @PoeTate:1994; @Davenport:2007; and @RitterConrad:2016].
 
 One part of the existing literature focuses on the role of structural factors such as levels of democracy, economic development, electoral competitiveness in predisposing a state to increased use of repression.
-Most notably, both democracies and democratization is found to have a pacifying effect on state repression (Davenport and Armstrong 2004, Krain 1997, Richards 1999).
-Democracies are found to have a negative effect on repression largely because of the increased probability of sanctions against authorities for undesirable behavior (Davenport 2007, 41).
+Most notably, democratic forms of government—and democratization in general—has a pacifying effect on state repression [@DavenportArmstrong:2004; @Krain:1997; @Richards:1999].
+Democracies have a negative effect on repression largely because of the increased probability of sanctions against authorities for undesirable behavior [@Davenport:2007a, 47].
 
@@
 One of the most consistent findings in the political violence literature is that authorities repress to counter ongoing challenges to the status quo.
-In other words, dissent increases repressive behavior (Davenport 2007).
-However, dissent and repression have an endogenous relationship - state authorities also frequently engage in preventive repression to undermine or restrict groups’ abilities to dissent (Ritter and Conrad 2016; and Conrad and Ritter 2019.) In addition to attacking groups’ willingness to organize against states, such
-preventive repression also damages their capacity to impose costs (Davenport 2007a, 47.)
+In other words, dissent increases repressive behavior [@Davenport:2007].
+However, dissent and repression have an endogenous relationship: state authorities also frequently engage in preventive repression to undermine or restrict groups' abilities to dissent [@RitterConrad:2016; @ConradRitter:2019].
+In addition to attacking groups willingness to organize against states, such preventive repression also damages states' capacity to impose costs [@Davenport:2007a, 47].
 
 NGOs are one actor that can pose challenges to political authorities, and state repression of these actors, especially through legal restrictions or administrative crackdown can also be considered a form of preventive repression.
-Below, we explore why government repress NGOs, especially through subtle, legal means.
-
-## State repression of NGOs
-
-A robust, strong civil society is widely considered as an important component on democratic transition and consolidation (Putnam).
+A robust, strong civil society is widely considered as an important component on democratic transition and consolidation [@Putnam:1994].
 Politically, as important civil society actors, NGOs enable citizens to voice their grievances, seek redress, and carry out lobbying and advocacy activities to further their interests.
@@
 From an economic perspective, NGOs provide services when the state falls short.
+As a result of these roles, NGOs can wield real influence, which can be threatening to states.
+State crackdown on NGOs has become pervasive as these organizations have the ability to influence electoral politics [@DPR:2016; @Weiss:2009], aid mobilization [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
 
-As a result of these roles, NGOs can wield real influence, which can be threatening to states.
-State crackdown on NGOs has become pervasive as these organizations have the ability to influence electoral politics (Dupuy, Ron, and Prakash 2016, Weiss 2009), aid mobilization (Murdie and Bhasin 2011; Bell et al.
-2013; and Boulding 2014), and threaten a state’s economic interests (Dietrich and Murdie 2017; Lebovic and Voeten 2009; and Nielsen 2013.).
+There is no doubt that violence is often effective at curbing dissent.
+But it can also backfire, leading to widespread protests, decreasing leaders' legitimacy and increasing their criminal liability [@KimSikkink:2010; @Sikkink:2011].
+In contrast to violence, administrative crackdown has fewer adverse consequences—citizens may see it as regulation rather than repression, resulting in little to no counter-mobilization.
+It may also circumvent concerns among state security or bureaucratic agents about illegitimate orders based on violent repression [@StephanChenoweth:2008].
+There are also fewer international consequences since laws—unlike violence—rarely invite condemnation or threats of aid withdrawal [@CarothersBrechenmacher:2014].
 
-Why might repressive states start with non-violent forms of repression?
-WHY THE GROWTH IN THESE LAWS
-As someone points out, states have toned down 'open, violent confrontation' and favor the development of a 'civilized' oppression.
+We argue that crackdown on NGOs foreshadows future government transgressions.
+Autocratic leaders want to avoid accountability, and NGOs often stand in conflict with that goal.
+Civil society organizations, including NGOs, can help shape the narrative of leaders' performance both domestically and internationally.
+Monitoring by NGOs and subsequent shaming can include significant external revenue loss to states in the form of loss of aid, trade, and foreign direct investments [@KeckSikkink:1998; @BarryClayFlynn:2013].
+Government attempts to repress NGOs can signal the beginning of a deteriorating human rights situation.
+Such repression reflects the government's willingness and capability to use measures that can make it avoid accountability.
+Once a state targets NGOs, over time it may grow less hesitant to apply repression more widely and more severely.
 
-Leaders want to avoid accountability. Shape the narrative of their performance both domestically and internationally. Don't like being shamed.
-Can be the beginning of a deteriorating human rights situation.
+In exploring the impact of state crackdown on NGOs on subsequent human rights conditions, we look at both *de jure* measures—or formal legislation that seeks to repress NGOs—as well as the *de facto* implementation of these measures.
+This distinction is important.
+While states may pass anti-NGO laws, these laws can also lie dormant.
+For instance, Russia passed its 2015 Undesirable Organizations Law with the purpose of targeting and eliminating specific foreign-connected NGOs it deemed dangerous.
+One of the law's sponsors, Aleksandr Tarnavsky, described the law as a preventative measure that would not affect the majority of NGOs working in Russia.
+Rather, the law would be a "weapon hanging on the wall that never fires" and stand as a warning to potentially uncooperative NGOs [@Kozenko:2015].
 
-In the aftermath of the failed coup attempt in Turkey in 2016, the government initiated a widespread crackdown on civil society, leading to the closure of almost 1500 NGOs soon after the group.
-However, this crackdown, ``spiraled far beyond those with any possible connection to the coup itself." In October 2017, the government levied terrorism charges against human rights activists, including on Amnesty International's Turkey Director and Chair.
-The government also imprisoned an increasing number of journalists in 2017 and 2018, and issued arrest warrants for numerous academics in 2018.
+Simply noting the passage of (or counting) these laws may therefore miss the effect of their de facto implementation.
+Moreover, the implementation of these laws may not be limited to its legal character.
+The government may also engage in harassment of NGOs and activists to dissuade NGOs from operation or expressing themselves.
+This may include measures such as detentions, short-term incarceration, as well as beatings, threats to families and destruction of valuable property.
+Finally, counting official laws can also undermeasure civil society repression because governments can repress NGOs without passing or relying on formal laws.
+As prior research in Egypt, Ethiopia, and Russia points out, "rather than systematically enforcing all repressive legal measures-often impossible owing to capacity constraints," governments may choose to use extra-legal means to intimidate, harass or prosecute a few NGOs or activists.
+These cases, especially during moments or crises or contention, "highlight to the wider NGO community-and citizenry-that the government is willing and capable of using the law to repress dissent" [@Brechenmacher:2017, 94].
 
-##Expectations
+Based on these purposes of civil society restrictions and the different methods states use to implement them, we propose two empirical expectations about the relationship between civil society repression and general human rights:
 
-#Methods
+- **Empirical expectation 1**: If a country imposes a formal anti-NGO law, then it is likely to signal future deteriorating human rights conditions.
+- **Empirical expectation 2**: If a country represses civil society, then it is likely to signal future deteriorating human rights conditions.
 
-#Results and Analysis
+# Data and modeling approach
 
-#Conclusion and Implications
+To test these empirical expectations, we use a new dataset of civil society laws, as well as measures from several other larger datasets focused on human rights, political terror, and democratization.
+Table \@ref(tab:var-summary) provides a summary of our key variables.
+
+```{r var-summary}
+tribble(
+  ~Measure, ~Category, ~Description, ~Source,
+  "Political Terror Scale (PTS)", NA, "Ordered category ranging from 1 (least terror) to 5 (most terror)", "Gibney et al. (2019)",
+  "Physical violence index", NA, "0–1; higher values indicate less violence", "Coppedge et al. (2020); v2x_clphy",
+  "Private civil liberties index", NA, "0–1; higher values indicate greater respect for civil liberties", "Coppedge et al. (2020); v2x_clpriv",
+  "Total legal barriers", "De jure laws", "Count of all anti-NGO legal barriers", "Chaudhry (2016)",
+  "Barriers to advocacy", "De jure laws", "Count of laws restricting NGO advocacy", "Chaudhry (2016)",
+  "Barriers to entry", "De jure laws", "Count of laws restricting NGO entry, including registration", "Chaudhry (2016)",
+  "Barriers to funding", "De jure laws", "Count of laws restricting NGO funding sources", "Chaudhry (2016)",
+  "CSO repression", "De facto repression", "≈ −3–3; higher values indicate less repression", "Coppedge et al. (2020); v2csreprss"
+) %>%
+  kbl(caption = "Outcomes and predictors",
+      booktabs = TRUE, linesep = "\\addlinespace") %>% 
+  kable_styling(font_size = 8) %>% 
+  row_spec(0, bold = TRUE) %>% 
+  column_spec(1, width = "0.14\\\\textwidth") %>% 
+  column_spec(2, width = "0.14\\\\textwidth") %>% 
+  column_spec(3, width = "0.4\\\\textwidth") %>% 
+  column_spec(4, width = "0.2\\\\textwidth") %>% 
+  pack_rows(index = c("Outcomes" = 3, "Predictors" = 5))
+```
+
+```{r var-summary1, eval=FALSE, include=FALSE}
+tribble(
+  ~Measure, ~Category, ~Description, ~Source,
+  "Political Terror Scale (PTS)", NA, "Ordered category ranging from 1 (least terror) to 5 (most terror)", "@GibneyCornettWood:2019",
+  "Physical violence index", NA, "0–1; higher values indicate less violence", "@vdem-v10; v2x_clphy",
+  "Private civil liberties index", NA, "0–1; higher values indicate greater respect for civil liberties", "@vdem-v10; v2x_clpriv",
+  "Total legal barriers", "De jure laws", "Count of all anti-NGO legal barriers", "\\@Chaudhry:2016",
+  "Barriers to advocacy", "De jure laws", "Count of laws restricting NGO advocacy", "\\@Chaudhry:2016",
+  "Barriers to entry", "De jure laws", "Count of laws restricting NGO entry, including registration", "@Chaudhry:2016",
+  "Barriers to funding", "De jure laws", "Count of laws restricting NGO funding sources", "@Chaudhry:2016",
+  "CSO repression", "De facto repression", "≈ −3–3; higher values indicate less repression", "@vdem-v10; v2csreprss"
+) %>%
+  kbl(caption = "Outcomes and predictors",
+      booktabs = TRUE, linesep = "") %>% 
+  kable_styling(font_size = 8.5) %>% 
+  row_spec(0, bold = TRUE) %>% 
+  column_spec(1, width = "0.14\\\\textwidth") %>% 
+  column_spec(2, width = "0.14\\\\textwidth") %>% 
+  column_spec(3, width = "0.5\\\\textwidth") %>% 
+  column_spec(4, width = "0.2\\\\textwidth") %>% 
+  pack_rows(index = c("Outcomes" = 3, "Predictors" = 5))
+```
+
+## Measuring de jure and de facto civil society repression
+
+@christensen2013 collected data on formal NGO regulations in 90 countries to explore the determinants of laws that restrict NGO foreign funding laws specifically.
+@Chaudhry:2016 expanded this data so that it now includes official NGO laws for 162 countries between 1990 and 2013.
+We create indexes of the total number of laws passed in each country based on three broad categories, and we also sum each of these indexes to create a count of total legal barriers:
+
+- Barriers to advocacy (2 possible barriers): NGOs are restricted from engaging in political activities, and advocacy restrictions differ if the NGO receives foreign funding
+- Barriers to entry (3 possible barriers): registration is burdensome, NGOs are not allowed to appeal if denied registration, and entry requirements differ if the NGO receives foreign funding
+- Barriers to funding (5 possible barriers): NGOs need prior approval to receive foreign funding, NGOS are required to channel foreign funding to state-owned banks, NGOS face additional restrictions if receiving foreign funding, and NGOs are prohibited from receiving foreign funding
+
+```{r barriers, fig.width=7, fig.height=6, fig.asp=NULL, fig.cap="Number of legal barriers to NGO activity per country over time (de jure legislation) and average level of CSO repression across democracies and non-democracies (de facto implementation)"}
+regulations <- tribble(
+    ~question, ~barrier,       ~question_clean,                  ~ignore_in_index, ~question_display,
+    "q1a",     "association",  "const_assoc",                    TRUE,             "Constitutional associational rights",
+    "q1b",     "association",  "political_parties",              TRUE,             "Citizens form political parties",
+    "q4b",     "advocacy",     "ngo_politics_intimidation",      TRUE,             "NGOs intimidated from politics",
+    "q4c",     "advocacy",     "ngo_politics_foreign_fund",      FALSE,            "Political barriers differentXXXif foreign funds involved",
+    "q2a",     "entry",        "ngo_register",                   TRUE,             "NGO registration required",
+    "q2b",     "entry",        "ngo_register_burden",            FALSE,            "NGO registration burdensome",
+    "q2c",     "entry",        "ngo_register_appeal",            FALSE,            "NGO registration appealXXXnot allowed",
+    "q2d",     "entry",        "ngo_barrier_foreign_funds",      FALSE,            "Registration barriers differentXXXif foreign funds involved",
+    "q3a",     "funding",      "ngo_disclose_funds",             TRUE,             "Funds must be disclosed",
+    "q3b",     "funding",      "ngo_foreign_fund_approval",      FALSE,            "Prior approval requiredXXXfor foreign funds",
+    "q3c",     "funding",      "ngo_foreign_fund_channel",       FALSE,            "Foreign funds channeledXXXthrough government",
+    "q3d",     "funding",      "ngo_foreign_fund_restrict",      FALSE,            "Foreign funds restricted",
+    "q3e",     "funding",      "ngo_foreign_fund_prohibit",      FALSE,            "Foreign funds prohibited",
+    "q3f",     "funding",      "ngo_type_foreign_fund_prohibit", FALSE,            "Foreign funds prohibitedXXXfor some types of NGOs",
+    "q4a",     "advocacy",     "ngo_politics",                   FALSE,            "NGOs restricted from politics"
+) %>% 
+  filter(!ignore_in_index) %>% 
+  mutate(barrier_group = paste0("Barriers to ", str_to_lower(barrier))) %>% 
+  select(barrier_group, barrier = question_clean, barrier_display = question_display)
+
+df_barriers <- canary %>% 
+  group_by(gwcode, year) %>% 
+  summarize(across(one_of(regulations$barrier), ~. > 0)) %>% 
+  group_by(year) %>% 
+  summarize(across(-gwcode, ~sum(., na.rm = TRUE))) %>% 
+  ungroup() %>% 
+  pivot_longer(names_to = "barrier", values_to = "value", -year) %>% 
+  left_join(regulations, by = "barrier") %>% 
+  mutate(barrier_display = str_replace(barrier_display, "XXX", "\n")) %>%
+  arrange(desc(value)) %>% 
+  mutate(barrier_display = fct_inorder(barrier_display, ordered = TRUE))
+
+num_countries <- length(unique(canary$gwcode))
+
+entry_plot <- ggplot(filter(df_barriers, 
+                            barrier_group == "Barriers to entry"), 
+                     aes(x = year, y = value, 
+                         color = barrier_display,
+                         linetype = barrier_display)) +
+  geom_line(size = 0.75) +
+  expand_limits(y = c(0, 90)) +
+  scale_y_continuous(sec.axis = sec_axis(~ . / num_countries,
+                                         labels = percent_format(accuracy = 1)),
+                     expand = c(0, 0)) +
+  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  scale_linetype_manual(values = c("solid", "solid", "21"), name = NULL) +
+  coord_cartesian(xlim = c(1990, 2015), ylim = c(0, 90)) +
+  guides(color = guide_legend(nrow = 2)) +
+  labs(x = NULL, y = "Number of countries") +
+  theme_ngo(9) + 
+  theme(legend.justification = "left") +
+  facet_wrap(vars(barrier_group))
+
+funding_plot <- ggplot(filter(df_barriers, 
+                              barrier_group == "Barriers to funding"), 
+                       aes(x = year, y = value, 
+                           color = barrier_display,
+                           linetype = barrier_display)) +
+  geom_line(size = 0.75) +
+  scale_y_continuous(sec.axis = sec_axis(~ . / num_countries,
+                                         labels = percent_format(accuracy = 1)),
+                     expand = c(0, 0)) +
+  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  scale_linetype_manual(values = c("solid", "solid", "solid", "21", "21"), name = NULL) +
+  coord_cartesian(xlim = c(1990, 2015), ylim = c(0, 45)) +
+  guides(color = guide_legend(nrow = 3),
+         linetype = guide_legend(nrow = 3)) +
+  labs(x = NULL, y = "Number of countries") +
+  theme_ngo(9) + 
+  theme(legend.justification = "left") +
+  facet_wrap(vars(barrier_group))
+
+advocacy_plot <- ggplot(filter(df_barriers, 
+                               barrier_group == "Barriers to advocacy"), 
+                        aes(x = year, y = value, 
+                            color = barrier_display)) +
+  geom_line(size = 0.75) +
+  scale_y_continuous(sec.axis = sec_axis(~ . / num_countries,
+                                         labels = percent_format(accuracy = 1)),
+                     expand = c(0, 0)) +
+  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  coord_cartesian(xlim = c(1990, 2015), ylim = c(0, 60)) +
+  guides(color = guide_legend(nrow = 2)) +
+  labs(x = NULL, y = "Number of countries") +
+  theme_ngo(9) + 
+  theme(legend.justification = "left") +
+  facet_wrap(vars(barrier_group))
+
+df_csreprss_plot <- canary %>%
+  group_by(year, autocracy = v2x_regime <= 1) %>%
+  nest() %>% 
+  mutate(cis = data %>% map(~ mean_cl_normal(.$v2csreprss))) %>% 
+  unnest(cis) %>% 
+  ungroup() %>% 
+  filter(!is.na(autocracy)) %>% 
+  mutate(fake_facet_title = "CSO repression",
+         autocracy = factor(autocracy, 
+                            labels = c("Democracies (Regimes of the World > 1)",
+                                       "Non-democracies (Regimes of the World ≤ 1)"), 
+                            ordered = TRUE))
+
+csreprss_plot <- ggplot(df_csreprss_plot, aes(x = year, y = y)) +
+  geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = autocracy), alpha = 0.2,) +
+  geom_line(aes(color = autocracy), size = 0.75) +
+  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  scale_fill_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  coord_cartesian(xlim = c(1990, 2015)) +
+  guides(color = guide_legend(nrow = 2)) +
+  labs(y = "Average CSO repression", x = NULL) +
+  theme_ngo(9) +
+  theme(legend.justification = "left") +
+  facet_wrap(vars(fake_facet_title))
+
+barriers_summary <- 
+  ((advocacy_plot | funding_plot) / 
+     (funding_plot | csreprss_plot)) &
+  theme(legend.text = element_text(size = rel(0.7)),
+        axis.title.y = element_text(margin = margin(r = 3)),
+        legend.box.margin = margin(t = -0.5, unit = "lines"))
+
+barriers_summary
+```
+
+As mentioned previously, simply counting the number of NGO laws does not necessarily capture the restrictiveness of the general civil society environment in a country.
+Governments might repress civil society without formal laws or pass restrictive laws that they can keep in reserve for later emergencies.
+To measure the general level of civil society repression in a country, we use V-Dem's CSO repression indicator (`v2csreprss` in @vdem-v10), which captures the extent to which governments harass, deter, liquidate, and arrest members of civil society organizations.
+Figure \@ref(fig:barriers) shows each of these types of legal barriers per country over time, as well as average levels of civil society repression by regime type.
+While anti-NGO laws have increased steadily since 1990—particularly laws related to foreign funding—there has not necessarily been a corresponding rise in civil society repression, which has remained fairly constant across different regime types.
+This divergence is likely indicative of the split between de jure laws and their de facto implementation—a rise in laws is not necessarily tied to direct CSO repression.
+
+## Measuring repression
+
+We measure general human rights repression in three different ways.
+First, following @GohdesCarey:2017, who use the killing of journalists to predict worsening human rights conditions, we use the Political Terror Scale (PTS), which assigns countries to five different categories of repression each year [@GibneyCornettWood:2019], with Level 5 representing widespread political violence, including arrests, political murders, disappearances, and torture.
+As seen in the left panel of Figure \@ref(fig:repression), the number of countries at Level 5 has decreased since the 1990s, while most countries are coded as Levels 2 and 3.
+To supplement the PTS, we also turn to two indicators from V-Dem: a physical violence index (`v2x_clphy`) that measures freedom from torture and political killings specifically, and a private civil liberties index (`v2x_clpriv`) that measures respect for property rights, labor rights, freedom of religion, freedom of movement, and other non-political human rights.
+V-Dem includes several other rights indicators, including one for political civil liberties that captures many of the same dimensions as the PTS, but civil society repression is included as a factor for these other indexes, making it inappropriate to use as an outcome variable.
+The right panel of Figure \@ref(fig:repression) shows that the average level of these two rights indexes has improved over time.
+
+```{r repression, fig.width=7, fig.height=3, fig.asp=NULL, fig.cap="Key measures of repression over time"}
+pts_plot <- canary %>% 
+  filter(!is.na(PTS_factor)) %>% 
+  group_by(PTS_factor, year) %>% 
+  summarize(count = n()) %>% 
+  mutate(fake_facet_title = "Political Terror Scale") %>% 
+  ggplot(aes(x = year, y = count, color = PTS_factor)) +
+  geom_line(size = 0.75) +
+  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  coord_cartesian(xlim = c(1990, 2015)) +
+  guides(color = guide_legend(nrow = 2)) +
+  labs(y = "Number of countries", x = NULL) +
+  theme_ngo(9) +
+  theme(legend.justification = "left") +
+  facet_wrap(vars(fake_facet_title))
+
+labs_lookup <- tribble(
+  ~name, ~nice_name,
+  "v2x_clphy", "Physical violence index",
+  "v2x_clpriv", "Private civil liberties index"
+) %>% 
+  mutate(nice_name = fct_inorder(nice_name, ordered = TRUE))
+
+df_outcome_plot <- canary %>%
+  select(year, v2x_clphy, v2x_clpriv) %>% 
+  pivot_longer(starts_with("v2x")) %>% 
+  group_by(year, name) %>% 
+  nest() %>% 
+  mutate(cis = data %>% map(~ mean_cl_normal(.$value))) %>% 
+  unnest(cis) %>% 
+  ungroup() %>% 
+  mutate(fake_facet_title = "V-Dem repression") %>% 
+  left_join(labs_lookup, by = "name")
+
+vdem_outcome_plot <- ggplot(df_outcome_plot, aes(x = year, y = y)) +
+  geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = nice_name), alpha = 0.2,) +
+  geom_line(aes(color = nice_name), size = 0.75) +
+  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  scale_fill_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  coord_cartesian(xlim = c(1990, 2015)) +
+  guides(color = guide_legend(nrow = 2, reverse = TRUE),
+         fill = guide_legend(nrow = 2, reverse = TRUE)) +
+  labs(y = "Average index value\n(Higher values = less repression)", x = NULL) +
+  theme_ngo(9) +
+  theme(legend.justification = "left") +
+  facet_wrap(vars(fake_facet_title))
+
+(pts_plot | vdem_outcome_plot) &
+  theme(legend.text = element_text(size = rel(0.7)),
+        axis.title.y = element_text(margin = margin(r = 3)),
+        legend.box.margin = margin(t = -0.5, unit = "lines"))
+```
+
+## Modeling approach
+
+Our main question in this paper is whether civil society laws and restrictions serve as an early warning signal to other future forms of repression.
+As such, we are primarily interested in *predicting* repression and not isolating the causal effect of civil society repression on general human rights abuses.
+We do not include a complete set of covariates to remove confounding relationships, but instead use a more parsimonious set of explanatory variables that strongly predict repression.
+Following @GohdesCarey:2017, we control for a country's previous level of repression, its level of democracy as measured by V-Dem's polyarchy index, its logged GDP per capita (measured by the UN), the percent of GDP attributed to trade (measured by the UN), and an indicator for whether the country witnessed more than 25 battle-related deaths (measured by @ucdp2020; @GleditschWallensteenEriksson:2002).
+Because changes in the human rights environment take time to be reflected by these larger indexes, we model the effect of lagged explanatory variables on repression one year in the future.
+We also include the lag of civil society laws or repression to account for serial correlation.
+
+We extend @GohdesCarey:2017's previous modeling approach by accounting for country-level variation in repression with multilevel modeling and we include random effects for each country.
+Accounting for the country this way results in intraclass correlation coefficients of around 0.7 for each of our three outcome variables, which means that the country-based structure of the data explains more than 70% of the variation in outcome, resulting in model estimates that are arguably more precisely measured.
+Additionally, as a robustness check, we account for within-country and between-country variation by splitting each numeric explanatory variable into its country-level mean and its variation from the mean, following @BellJones:2015.
+The results from these random effects—within/between (REWB) models are nearly identical to those with the untransformed covariates, so for the sake of simplicity here, we only include results from basic multilevel random effects models.
+
+We run multiple models for each of our empirical expectations, based on different combinations of our outcomes and key explanatory variables:
+
+- **Expectation 1~a~**: Anti-NGO laws (total, advocacy, entry, funding separately) signal worsening political terror
+- **Expectation 1~b~**: Anti-NGO laws signal worsening physical violence
+- **Expectation 1~c~**: Anti-NGO laws signal constricting private civil liberties
+- **Expectation 2~a~**: Civil society repression signals worsening political terror
+- **Expectation 2~b~**: Civil society repression signals worsening physical violence
+- **Expectation 2~c~**: Civil society repression signals constricting private civil liberties
+
+We generate our predictions with two families of Bayesian regression models.
+Because the Political Terror Scale is measured as an ordered category, we use ordered logistic regression to predict future values of the PTS.
+As V-Dem's physical violence index and private civil liberties index are both measured continuously, we predict these values with Gaussian models.
+We use median values from the models' posterior distributions as our point estimates and provide credible intervals using the 95% highest posterior density.[^bayes] We declare an effect statistically "significant" if the posterior probability of being different from zero exceeds 0.95.
+
+[^bayes]: We use Stan [@stan] through R [@r-project] and brms [@brms-jss] to estimate our models.
+We generate 4 MCMC chains with 2,000 iterations in each chain, 1,000 of which are used for warmup.
+All chains converge; we assess convergence with visual inspection.
+
+Complete results from all the models (including REWB models), along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion website at <https://stats.andrewheiss.com/canary-ngos/>.
+Our general modeling approach can be summarized as follows:
+
+\footnotesize
+
+$$
+\begin{aligned}
+y_{i, t+1} \mid u_i, x_{i, t} \sim&\ \operatorname{Ordered Logistic}(y^*_{i, t + 1}, \sigma^2_m) & \text{[likelihood for ordinal PTS models]} \\
+y_{i, t+1} \mid u_i, x_{i, t} \sim&\ \mathcal{N}(y^*_{i, t + 1}, \sigma^2_m) & \text{[likelihood for Gaussian V-Dem models]} \\
+y^*_{i, t + 1} =&\ \beta_0 + \beta_1 \text{Civil society repression}_{i, t} + & \text{[model with covariates]}\\
+&\ \beta_2 \text{Civil society repression}_{i, t - 1} + \\
+&\ \beta_3 \text{Outcome}_{i, t} + \beta_4 \text{Polyarchy}_{i, t} + \\
+&\ \beta_5 \log (\text{GDP per capita}) + \\
+&\ \beta_6 \text{Trade as } \% \text{ of GDP}_{i, t} + \\
+&\ \beta_7 \text{Armed conflict}_{i, t} + u_i + \sigma^2_e \\
+u_i =&\ \mathcal{N}(0, \sigma^2_u) & \text{[country-specific intercepts]} \\
+\ \\
+\beta_0 \sim&\ \mathcal{N}(0, 10) & \text{[prior population intercept]} \\
+\beta_{1-7} \sim&\ \mathcal{N}(0, 3) & \text{[prior population effects]} \\
+\sigma^2_m, \sigma^2_e, \sigma^2_u \sim&\ \operatorname{Cauchy}(0, 1) & \text{[prior sd for model, population, and country error]} \\
+\end{aligned}
+$$
+\normalsize
+
+# Results and analysis
+
+We present the results of our models in two stages.
+First, in order to see how minor shifts in civil society laws and repression influence future human rights, we examine the marginal effects of our main explanatory variables when all other model covariates are held constant.
+These effects are by no means causal—rather, they demonstrate how much variation in predicted human rights is possible as the legal environment for civil society shifts up and down within a typical country.
+Second, we present predictive diagnostics for each of our models to examine the improvements in predictions.
+The results of the ordered logistic regression models can be unwieldy to interpret with plain numbers due to varying intercepts and thresholds between PTS levels.
+Accordingly, we present graphical results for all our models wherever possible and include complete tables of model results in the appendix (see Tables \@ref(tab:tbl-models-pts), \@ref(tab:tbl-models-clphy), and \@ref(tab:tbl-models-clpriv)).
+For the sake of making it easier to compare the count of NGO laws with civil society repression, we reverse the x-axis in the marginal effects plots for our second empirical expectation so that increasing the civil society repression represents *worse* repression rather than less.
+
+## Marginal results
+
+### How does repression change following increases in NGO laws?
+
+In general, when holding all other covariates constant, the passage of an additional anti-NGO legal barrier is generally associated with a higher probability of more severe level of political terror in the following year.
+The probability of seeing different levels of political terror varies across different possible counts of NGO laws (see Figure \@ref(fig:plot-mfx-e1a)).
+In the absence of formal legal barriers, Level 2 of the PTS—an environment where political imprisonment, torture, and beatings are rare—is the most likely category of political terror across all models, appearing a predicted 60% of the time.
+Level 1, where a country is under secure rule of law, is the second most likely outcome at slightly under 40%.
+The other categories of the PTS are extremely rare when there are no anti-NGO laws.
+
+```{r plot-mfx-e1a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on the probability of specific levels of political terror"}
+plot_e1a_mfx <- tribble(
+  ~model, ~plot_var, ~plot_var_nice,
+  m_pts_total, "barriers_total", "Total legal barriers",
+  m_pts_advocacy, "advocacy", "Barriers to advocacy",
+  m_pts_entry, "entry", "Barriers to entry",
+  m_pts_funding, "funding", "Barriers to funding"
+) %>% 
+  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
+
+# mfx_e1a <- plot_e1a_mfx %>% 
+#   mutate(fx = map2(model, plot_var, 
+#                    ~conditional_effects(.x, effects = .y,
+#                                         categorical = TRUE)[[1]])) %>% 
+#   select(-model) %>% 
+#   unnest(fx)
+# saveRDS(mfx_e1a, here("temp_cache", "mfx_e1a.rds"))
+
+mfx_e1a %>% 
+  mutate(x_rounded = floor(effect1__)) %>% 
+  group_by(x_rounded, effect2__, plot_var_nice) %>% 
+  slice(1) %>% 
+  ungroup() %>% 
+  ggplot(aes(x = x_rounded, y = estimate__, color = effect2__)) +
+  geom_line(aes(group = effect2__), size = 0.5, color = "grey90") +
+  geom_pointrange(aes(ymin = lower__, ymax = upper__),
+                  position = position_dodge(width = 0.2),
+                  fatten = 1) +
+  scale_x_continuous(breaks = 0:9) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_color_viridis_d(option = "plasma", end = 0.9) +
+  labs(x = "Count of legal barriers\n",
+       y = "Predicted probability of category",
+       color = "Predicted political terror scale", fill = "Predicted political terror scale",
+       title = "Political terror scale") + 
+  facet_wrap(vars(plot_var_nice), scales = "free_x") +
+  theme_ngo() +
+  theme(panel.grid.major.x = element_blank())
+```
+
+As new laws are added, though, the distribution of probabilities for each of the PTS levels shifts.
+Adding new barriers to advocacy, entry, and funding decreases the likelihood of seeing Level 1 and increases the probability of a country turning to either Level 2 or Level 3 (with extensive political imprisonment and trial-free detention).
+The marginal effects of all forms of NGO laws results in this turn from Level 1 to Levels 2 or 3, but this switching effect is strongest following additional barriers to advocacy.
+Anti-NGO laws do not predict more dramatic shifts in the PTS.
+Across all counts of legal barriers, the overall probability of seeing Levels 4 and 5 is minuscule, and the adding new laws does little to shift that probability.
+
+Figure \@ref(fig:plot-mfx-e1b-e1c) shows the marginal effects of additional NGO legislation on V-Dem's physical violence index and private civil liberties index.
+Across all four models for different categories of legal barriers, holding all other values constant, neither rights index moves much in response to new NGO laws.
+Each barrier-based posterior coefficient is essentially zero with narrow credible intervals that include large proportions of both negative and positive values.
+The marginal effects of additional laws on physical violence appear to show a positive relationship—that additional laws lead to less violence in the future—but the uncertainty in these estimates eliminates such an interpretation.
+Within the categories of anti-NGO laws, it appears that additional advocacy and entry laws might reduce future violence, but again, these predictions are indistinguishable from each other.
+The null effect of legal barriers on private civil liberties is even more stark—a typical country is predicted to have a score of 0.69 regardless of the addition of any kind of NGO law.
+
+At a marginal level, therefore, adding additional anti-NGO laws in countries with low levels of political terror could signal (albeit weakly) that higher levels of political repression are more likely in the future.
+Limited repression remains the most likely possible outcome, but the chance of seeing robust rule of law decreases rapidly as more laws are passed, all else equal.
+When looking at other forms of political repression, though, such as physical violence and private civil liberties, NGO legal barriers do not change predicted values in any meaningful way.
+
+```{r plot-mfx-e1b-e1c, fig.width=7.5, fig.height=5.5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on V-Dem rights indexes"}
+plot_e1b_mfx <- tribble(
+  ~model, ~plot_var, ~plot_var_nice,
+  m_clphy_total, "barriers_total", "Total legal barriers",
+  m_clphy_advocacy, "advocacy", "Advocacy",
+  m_clphy_entry, "entry", "Entry",
+  m_clphy_funding, "funding", "Funding"
+) %>% 
+  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
+
+# mfx_e1b <- plot_e1b_mfx %>% 
+#   mutate(fx = map2(model, plot_var, 
+#                    ~conditional_effects(.x, effects = .y)[[1]])) %>% 
+#   select(-model) %>% 
+#   unnest(fx)
+# saveRDS(mfx_e1b, here("temp_cache", "mfx_e1b.rds"))
+
+plot_e1c_mfx <- tribble(
+  ~model, ~plot_var, ~plot_var_nice,
+  m_clpriv_total, "barriers_total", "Total legal barriers",
+  m_clpriv_advocacy, "advocacy", "Advocacy",
+  m_clpriv_entry, "entry", "Entry",
+  m_clpriv_funding, "funding", "Funding"
+) %>% 
+  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
+
+# mfx_e1c <- plot_e1c_mfx %>% 
+#   mutate(fx = map2(model, plot_var, 
+#                    ~conditional_effects(.x, effects = .y)[[1]])) %>% 
+#   select(-model) %>% 
+#   unnest(fx)
+# saveRDS(mfx_e1c, here("temp_cache", "mfx_e1c.rds"))
+
+out_mfx_e1b <- mfx_e1b %>% 
+  mutate(x_rounded = floor(effect1__)) %>% 
+  group_by(x_rounded, plot_var_nice) %>% 
+  slice(1) %>% 
+  ungroup() %>% 
+  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
+  geom_line(size = 0.5, color = "grey90") +
+  geom_pointrange(aes(ymin = lower__, ymax = upper__),
+                  fatten = 1) +
+  scale_x_continuous(breaks = 0:9) +
+  scale_color_viridis_d(option = "plasma", end = 0.8) +
+  coord_cartesian(ylim = c(0.60, 0.71)) +
+  guides(color = FALSE) +
+  labs(x = NULL,
+       y = "Predicted physical violence index\n(higher values = less violence)",
+       title = "Physical violence index") +
+  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
+  theme_ngo() +
+  theme(panel.grid.major.x = element_blank())
+
+out_mfx_e1c <- mfx_e1c %>% 
+  mutate(x_rounded = floor(effect1__)) %>% 
+  group_by(x_rounded, plot_var_nice) %>% 
+  slice(1) %>% 
+  ungroup() %>% 
+  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
+  geom_line(size = 0.5, color = "grey90") +
+  geom_pointrange(aes(ymin = lower__, ymax = upper__),
+                  fatten = 1) +
+  scale_x_continuous(breaks = 0:9) +
+  scale_color_viridis_d(option = "plasma", end = 0.8) +
+  coord_cartesian(ylim = c(0.60, 0.71)) +
+  guides(color = FALSE) +
+  labs(x = "Count of legal barriers",
+       y = "Predicted civil liberties index\n(higher values = better protection)",
+       title = "Private civil liberties index") +
+  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
+  theme_ngo() +
+  theme(panel.grid.major.x = element_blank())
+
+out_mfx_e1b / out_mfx_e1c
+```
+
+### How does general repression change following civil society repression?
+
+The weak (or even non-existent) predictive power of formal NGO laws is likely attributable to fact that de jure NGO legislation is rare and slow-moving and not always explicitly linked to repression—again, states that engage in political repression can do so with or without legal justification.
+De facto civil society repression, on the other hand, represents the actual implementation of anti-NGO strategies—both legal and extralegal—and might be more indicative of future human rights abuses.
+The results from our second set of models, using V-Dem's civil society repression index as the key predictor, confirm this.
+
+The effect of civil society repression on predicted values of the Political Terror Scale mirrors what we found previously with our first empirical expectation.
+As seen in Figure \@ref(fig:plot-mfx-e2a), at the lowest levels of repression, Levels 1 and 2 are the most common predicted outcomes and are each equiprobable at roughly 50%.
+As de facto CSO repression increases, though, the probability of seeing Level 1 decreases and is replaced with either Level 2 or Level 3.
+More severe levels of political terror remain exceptionally improbable at any level of preceding civil society repression.
+
+```{r plot-mfx-e2a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on the probability of specific levels of political terror"}
+# df_mfx_e2a <- conditional_effects(m_pts_v2csreprss,
+#                                   effects = "v2csreprss",
+#                                   categorical = TRUE)[[1]]
+# saveRDS(df_mfx_e2a, here("temp_cache", "df_mfx_e2a.rds"))
+
+out_mfx_e2a <- df_mfx_e2a %>% 
+  ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
+  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, color = NA) +
+  geom_line(size = 0.75) +
+  scale_x_reverse() +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_color_viridis_d(option = "plasma", end = 0.9) +
+  scale_fill_viridis_d(option = "plasma", end = 0.9) +
+  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
+       y = "Predicted probability of category",
+       color = "Political terror scale", fill = "Political terror scale",
+       title = "Political terror scale") +
+  theme_ngo()
+out_mfx_e2a
+```
+
+In contrast with formal laws, civil society repression does have a noticeable effect on the predicted values of the other rights indexes (see Figure \@ref(fig:plot-mfx-e2b-e2c)).
+When holding all other model parameters at their typical values, increased civil society repression predicts increases in both the physical violence index and the private civil liberties index: a one standard deviation change in civil society repression is associated with a 0.02 change in overall rights.
+In other words, a typical country with a civil society repression score of 0 is predicted to have a physical violence index of 0.62 and civil liberties index of 0.67.
+This implies that an increase in de facto NGO restrictions predicts a `r percent_format(accuracy = 1)((0.62 - (0.62 - 0.02)) / (0.62 - 0.02))` decline in both protection from physical violence and respect for private civil liberties in the following year.
+
+When holding all other factors equal, the de factor implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passing of formal de jure laws.
+Increasing civil society repression in countries with low levels of political terror can again potentially serve as a weak signal of more a more general increase in political violence in the future, while crackdowns on civil society predict more substantial changes in physical violence and threats to civil liberties.
+
+```{r plot-mfx-e2b-e2c, fig.width=7.5, fig.height=3.5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on V-Dem rights indexes"}
+# df_mfx_e2b <- conditional_effects(m_clphy_v2csreprss,
+#                                   effects = "v2csreprss")[[1]]
+# df_mfx_e2c <- conditional_effects(m_clpriv_v2csreprss,
+#                                   effects = "v2csreprss")[[1]]
+# saveRDS(df_mfx_e2b, here("temp_cache", "df_mfx_e2b.rds"))
+# saveRDS(df_mfx_e2c, here("temp_cache", "df_mfx_e2c.rds"))
+
+out_mfx_e2b <- df_mfx_e2b %>% 
+  ggplot(aes(x = effect1__, y = estimate__)) +
+  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
+              fill = "#433E85", color = NA) +
+  geom_line(size = 0.75, color = "#433E85") +
+  scale_x_reverse() +
+  coord_cartesian(ylim = c(0.5, 0.75)) +
+  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
+       y = "Predicted physical violence index\n(higher values = less violence)",
+       title = "Physical violence index") +
+  theme_ngo()
+
+out_mfx_e2c <- df_mfx_e2c %>% 
+  ggplot(aes(x = effect1__, y = estimate__)) +
+  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
+              fill = "#4DC36B", color = NA) +
+  geom_line(size = 0.75, color = "#4DC36B") +
+  scale_x_reverse() +
+  coord_cartesian(ylim = c(0.5, 0.75)) +
+  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
+       y = "Predicted civil liberties index\n(higher values = less violence)",
+       title = "Private civil liberties index") +
+  theme_ngo()
+
+out_mfx_e2b | out_mfx_e2c
+```
+
+## Predictions
+
+These predicted probabilities and outcomes are conditional on all other model parameters being held at their average values and show the effect of hypothetically changing a single predictor to different values.
+They do not show how well these models work with actual data.
+Following @WardBeger:2017 and @GohdesCarey:2017, test the predictive power of both sets of our models using out-of-sample prediction.
+We divide our complete data into a training set and a test set—the training set includes data from all countries from 1990–2010, and the test set includes the last three years of data (2011–2013).
+We re-run each of our models using our training data and then use the estimated parameters to predict political terror, physical violence, and private civil liberties for the test data.
+Additionally, we estimate a model for each outcome without predictor variables for civil society laws or repression as a baseline measure of model performance.
+
+```{r correct-not-correct}
+pts_pred_table <- tribble(
+  ~Prediction, ~Baseline, ~total, ~advocacy, ~entry, ~funding, ~repression,
+  "Wrong",     108,       108,    110,       108,    109,      111,
+  "Correct",   377,       377,    375,       377,    376,      374
+) %>% 
+  rename("Total legal barriers included" = total,
+         "Barriers to advocacy included" = advocacy,
+         "Barriers to entry included" = entry,
+         "Barriers to funding included" = funding,
+         "Civil society repression included" = repression)
+
+pts_pred_table %>% 
+  kbl(align = "lcccccc",
+      booktabs = TRUE, linesep = "",
+      caption = "Counts of correctly and incorrectly predicted cases across different PTS models") %>% 
+  kable_styling(font_size = 8.5) %>%
+  kable_styling() %>% 
+  row_spec(0, bold = TRUE) %>% 
+  column_spec(1, width = "0.05\\\\textwidth") %>% 
+  column_spec(2:7, width = "0.14\\\\textwidth")
+```
+
+We assess predictive power in a few different ways, depending on the model used to predict the outcome.
+For the ordinal Political Terror Scale, Table \@ref(tab:correct-not-correct) shows a count of correct and incorrect predictions from each model.
+Because the physical violence and private civil liberties indexes are predicted with Gaussian models, we measure predictive accuracy with the root mean squared error, provided in Table \@ref(tab:tbl-rmse).
+In the appendix we include lists of country-year cases that see improved predictions when taking civil society laws and repression into account.
+
+Including civil society restrictions—both de jure and de facto—does very little to improve predictions of political terror.
+As seen in Table \@ref(tab:correct-not-correct), no model provides more correct predictions than the baseline model, and some models perform worse.
+Accounting for anti-NGO activities does improve predictions in eight cases (see Table \@ref(tab:tbl-improved-pts)), but it also results in an equal number of incorrect predictions.
+
+```{r tbl-rmse}
+tbl_rmse <- tribble(
+                      ~Model,     ~RMSE, ~`% change from baseline`,
+                  "Baseline", 0.0462298,                       "—",
+      "Total legal barriers", 0.0460839,                  "-0.32%",
+      "Barriers to advocacy", 0.0460425,                  "-0.41%",
+         "Barriers to entry", 0.0461553,                  "-0.16%",
+       "Barriers to funding", 0.0462081,                  "-0.05%",
+  "Civil society repression",  0.046175,                  "-0.12%",
+                  "Baseline",  0.033909,                       "—",
+      "Total legal barriers", 0.0333961,                  "-1.51%",
+      "Barriers to advocacy", 0.0336028,                  "-0.90%",
+         "Barriers to entry", 0.0334257,                  "-1.43%",
+       "Barriers to funding", 0.0335855,                  "-0.95%",
+  "Civil society repression", 0.0332081,                  "-2.07%"
+) %>% 
+  mutate(RMSE = round(RMSE, 4))
+
+tbl_rmse %>% 
+  kbl(align = "lcc",
+      booktabs = TRUE, linesep = "",
+      caption = "Root mean squared error across models predicting physical violence and private civil liberties") %>% 
+  pack_rows(index = c("Physical violence index" = 6, "Private civil liberties index" = 6)) %>% 
+  kable_styling()
+```
+
+When looking at the level of physical violence in a country, including civil society laws and repression also does very little to improve predictive accuracy.
+As Table \@ref(tab:tbl-rmse) shows, accounting for legal barriers and civil society repression only reduces the RMSE by at most 0.4% compared to the baseline model.
+This is likely related to the lack of improvements in predicting political terror—both indexes measure similar phenomena.
+However, including civil society-related predictors when modeling private civil liberties does result in small gains in accuracy, reducing the RMSE by as much as 2% compared to the baseline model.
+
+While these gains in predictive power appear negligible, they are somewhat comparable with the findings of previous work.
+For instance, in their work on the effect of the murder of journalists on predicting future political terror, @GohdesCarey:2017 find that accounting for violence against the media adds five correctly predicted cases of PTS scores and improves predictions in seven cases.
+
+# Conclusion and implications
+
+Strengthening civil society is an important precondition for democratic transition and consolidation.
+It keeps governments accountable and protects civilians from the worst excesses of an abusive government.
+When governments restrict civil society, it reduces these organizations' ability to maintain accountability and protect against abuse.
+Given this potential protective power, in this paper, we posited that the ongoing global crackdown on civil society could predict worsening human rights in a country interested in political and civil repression.
+Passing restrictive laws, imposing barriers to NGO advocacy, entry, and funding, and arresting and expelling NGO staff could pave the way for future repression.
+
+We outline two empirical expectations: that (1) official de jure anti-NGO laws and (2) general de facto civil society restrictions would predict future repression in a country, including political terror, physical violence, and violations of private civil liberties.
+We find little support for the predictive power of de jure restriction.
+Marginal predictions show that, all else held equal, adding new anti-NGO laws increases the probability of seeing moderate levels of political terror, but does not change predicted values of physical violence or civil liberties.
+When comparing out-of-sample predictions to a baseline model, including de jure restrictions as predictors does not improve our models' predictive accuracy.
+
+We do, however, find some predictive power when accounting for general civil society restrictions.
+As with formal laws, rising civil society repression tends to increase the probability of more moderate political terror.
+Additionally, increasing civil society repression is associated with a 3% decrease in indexes that measure safety from physical violence and respect for civil liberties in the future.
+In out-of-sample predictions, including civil society restrictions improves model accuracy by 1–2% over the baseline.
+
+Importantly, the lack of predictive power when modeling political violence and the modest improvements in predictive power when modeling civil liberties likely reflects the purpose of civil society restrictions.
+Encroachments on private civil liberties such as restricting freedom of association are not nearly as violent as events like government-sponsored murders.
+The global shrinking of civil society is thus not likely an early warning sign for future violent repression—states typically signal their future repressive intentions with more violent methods, such as the persecution and murder of activists and the media.
+Instead, civil society is a possible "canary in the coal mine" for impending violations of other civil rights, such as the freedom of religion, labor rights, property rights, and the freedom of movement.
+
+\clearpage
+
+# Appendix
+
+```{r tbl-improved-pts}
+tbl_improved_pts <- tibble::tribble(
+               ~Country, ~Year,   ~Actual, ~`Baseline prediction`, ~`Total NGO barriers included`, ~`Civil society repression included`,
+            "Guatemala", 2013L, "Level 3", "Level 2",                    "Level 3",                          "Level 3",
+               "Kosovo", 2012L, "Level 1", "Level 2",                    "Level 1",                          "Level 1",
+         "Sierra Leone", 2011L, "Level 3", "Level 2",                    "Level 3",                                "—",
+  "Congo - Brazzaville", 2011L, "Level 3", "Level 2",                    "Level 3",                          "Level 3",
+              "Somalia", 2013L, "Level 5", "Level 4",                    "Level 5",                                "—",
+              "Bahrain", 2011L, "Level 3", "Level 2",                    "Level 3",                          "Level 3",
+              "Bahrain", 2013L, "Level 3", "Level 2",                    "Level 3",                          "Level 3",
+                "Libya", 2011L, "Level 4", "Level 5",                          "—",                          "Level 4"
+  )
+
+tbl_improved_pts %>% 
+  kbl(align = "llcccc",
+      booktabs = TRUE, linesep = "\\addlinespace",
+      caption = "Country-year cases where including civil society restrictions improved PTS predictions") %>% 
+  kable_styling(latex_options = c("hold_position")) %>% 
+  row_spec(0, bold = TRUE) %>% 
+  column_spec(1, width = "0.1\\\\textwidth") %>% 
+  column_spec(2, width = "0.05\\\\textwidth") %>% 
+  column_spec(3:6, width = "0.16\\\\textwidth")
+```
+
+\newpage
+
+```{r tbl-models-pts}
+model_names_tbl_pts <- c("Total barriers\n(t + 1)",
+                         "Barriers to advocacy\n(t + 1)",
+                         "Barriers to entry\n(t + 1)",
+                         "Barriers to funding\n(t + 1)",
+                         "Civil society repression\n(t + 1)")
+
+names(models_paper_pts) <- model_names_tbl_pts
+
+modelsummary(models_paper_pts,
+             output = "kableExtra",
+             statistic = "[{conf.low}, {conf.high}]",
+             coef_map = coef_list,
+             gof_omit = "ELPD",
+             escape = FALSE,
+             caption = "Full results from ordered logistic regression models predicting political terror",
+             notes = list("Posterior means; 95% credible intervals in brackets")) %>% 
+  kable_styling(font_size = 6) %>% 
+  column_spec(1, width = "0.10\\\\textwidth") %>% 
+  column_spec(2:6, width = "0.14\\\\textwidth")
+```
+
+\clearpage
+
+```{r tbl-models-clphy}
+model_names_tbl_clphy <- c("Total barriers\n(t + 1)",
+                           "Barriers to advocacy\n(t + 1)",
+                           "Barriers to entry\n(t + 1)",
+                           "Barriers to funding\n(t + 1)",
+                           "Civil society repression\n(t + 1)")
+
+names(models_paper_clphy) <- model_names_tbl_clphy
+
+modelsummary(models_paper_clphy,
+             output = "kableExtra",
+             statistic = "[{conf.low}, {conf.high}]",
+             coef_map = coef_list,
+             gof_omit = "ELPD",
+             escape = FALSE,
+             caption = "Full results from Gaussian regression models predicting physical violence",
+             notes = list("Posterior means; 95% credible intervals in brackets")) %>% 
+  kable_styling(font_size = 7.5) %>% 
+  column_spec(1, width = "0.10\\\\textwidth") %>% 
+  column_spec(2:6, width = "0.14\\\\textwidth")
+```
+
+\clearpage
+
+```{r tbl-models-clpriv}
+model_names_tbl_clpriv <- c("Total barriers\n(t + 1)",
+                            "Barriers to advocacy\n(t + 1)",
+                            "Barriers to entry\n(t + 1)",
+                            "Barriers to funding\n(t + 1)",
+                            "Civil society repression\n(t + 1)")
+
+names(models_paper_clpriv) <- model_names_tbl_clpriv
+
+modelsummary(models_paper_clpriv,
+             output = "kableExtra",
+             statistic = "[{conf.low}, {conf.high}]",
+             coef_map = coef_list,
+             gof_omit = "ELPD",
+             escape = FALSE,
+             caption = "Full results from Gaussian regression models predicting private civil liberties",
+             notes = list("Posterior means; 95% credible intervals in brackets")) %>% 
+  kable_styling(font_size = 7.5) %>% 
+  column_spec(1, width = "0.10\\\\textwidth") %>% 
+  column_spec(2:6, width = "0.14\\\\textwidth")
+```
+
+\clearpage

### 2021-04-04 R/funs_data-cleaning.R

@@ -496,3 +496,56 @@ load_world_map <- function(path) {
 
   return(world_map)
 }
+
+# Civicus Monitor
+# We downloaded the standalone embeddable widget
+# (https://monitor.civicus.org/widgets/world/) as an HTML file with
+# `wget https://monitor.civicus.org/widgets/world/` and saved it as index_2021-03-19.html
+#
+# We then extracted the COUNTRIES_DATA variable embedded in a <script> tag
+# (xpath = /html/body/script[5]), which is JSON-ish, but not quite. jsonlite
+# can't parse it for whatever reason, but some online JSON formatter and
+# validator could, so we ran it through that and saved the resulting clean file
+load_clean_civicus <- function(path) {
+  civicus_raw <- read_json(path) %>% as_tibble() %>% slice(1)
+
+  civicus_lookup <- tribble(
+    ~value, ~category,
+    1, "Closed",
+    2, "Repressed",
+    3, "Obstructed",
+    4, "Narrowed",
+    5, "Open"
+  ) %>%
+    mutate(category = fct_inorder(category, ordered = TRUE))
+
+  civicus_clean <- civicus_raw %>%
+    pivot_longer(everything(), names_to = "name", values_to = "value") %>%
+    mutate(value = map_chr(value, ~.)) %>%
+    mutate(value = parse_number(value, na = c("", "NA", "None"))) %>%
+    mutate(country_name = countrycode(name, "iso3c", "country.name",
+                                      custom_match = c("KOSOVO" = "XKK",
+                                                       "SVT" = "VCT")),
+           iso3c = countrycode(country_name, "country.name", "iso3c",
+                               custom_match = c("XKK" = "Kosovo",
+                                                "VCT" = "Saint Vincent and the Grenadines"))) %>%
+    left_join(civicus_lookup, by = "value") %>%
+    select(-name, -value, -country_name)
+
+  return(civicus_clean)
+}
+
+create_civicus_map_data <- function(civicus, map) {
+  map_with_civicus <- map %>%
+    # Fix some Natural Earth ISO weirdness
+    mutate(ISO_A3 = ifelse(ISO_A3 == "-99", as.character(ISO_A3_EH), as.character(ISO_A3))) %>%
+    mutate(ISO_A3 = case_when(
+      .$ISO_A3 == "GRL" ~ "DNK",
+      .$NAME == "Norway" ~ "NOR",
[…]

### 2021-04-04 _targets.R

@@ -3,7 +3,7 @@ library(tarchetypes)
 library(tibble)
 
 # General variables
-csl <- "pandoc/csl/apa.csl"
+csl <- "pandoc/csl/chicago-author-date.csl"
 bibstyle <- "bibstyle-chicago-authordate"
 
 suppressPackageStartupMessages(library(brms))
@@ -31,10 +31,10 @@ tar_option_set(packages = c("tidyverse", "countrycode", "states", "WDI", "here",
                             "janitor", "kableExtra", "huxtable", "modelsummary",
                             "knitr", "withr", "flextable", "testthat", "DT",
                             "brms", "tidybayes", "broom", "broom.mixed", "scico",
-                            "ggtext", "colorspace", "lme4", "cmdstanr"))
+                            "ggtext", "colorspace", "lme4", "cmdstanr", "jsonlite"))
 
 source("R/funs_data-cleaning.R")
-# source("R/funs_knitting.R")
+source("R/funs_knitting.R")
 source("R/funs_notebook.R")
 source("R/models_details.R")
 source("R/models_pts.R")
@@ -76,12 +76,18 @@ list(
              here("data", "raw_data", "ne_110m_admin_0_countries",
                   "ne_110m_admin_0_countries.shp"),
              format = "file"),
+  tar_target(civicus_raw_file,
+             here("data", "raw_data", "Civicus", "civicus_2021-03-19.json"),
+             format = "file"),
 
   # Define helper functions
   tar_target(plot_funs, here("lib", "graphics.R"), format = "file"),
 
   # Load and clean data
   tar_target(world_map, load_world_map(naturalearth_raw_file)),
+  tar_target(civicus_clean, load_clean_civicus(civicus_raw_file)),
+  tar_target(civicus_map_data, create_civicus_map_data(civicus_clean, world_map)),
+
   tar_target(skeleton, create_panel_skeleton()),
   tar_target(wdi_clean, load_clean_wdi(skeleton)),
   tar_target(chaudhry_clean, load_clean_chaudhry(chaudhry_raw_file)),
@@ -230,8 +236,19 @@ list(
              build_modelsummary(lst(m_clpriv_baseline, m_clpriv_v2csreprss,
                                     m_clpriv_baseline_rewb, m_clpriv_v2csreprss_rewb))),
 
+  # Models for paper
+  tar_target(models_paper_pts,
+             build_modelsummary(lst(m_pts_total, m_pts_advocacy, m_pts_entry,
[…]

### 2021-04-04 manuscript/manuscript.Rmd
Fix pandoc citations in table
See https://github.com/haozhu233/kableExtra/issues/214

@@
 ---
-title: "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
+title: "Canary in the Coal Mine? Civil Society Repression as a Predictor of Human Rights Abuses"
 short-title: "Canary in the Coal Mine"
@@
 
+(ref:pts) @GibneyCornettWood:2019
+
+(ref:vdem) @vdem-v10
+
+(ref:chaudhry) @Chaudhry:2016
+
 ```{r var-summary}
+# For whatever reason, bookdown::pdf_document2 can't process in-table citations
+# like @vdem-v10; it just skips them. bookdown::html_document2 works just fine,
+# though. This is a known issue (see
+# https://github.com/haozhu233/kableExtra/issues/214#issuecomment-421706528),
+# and the solution is to use bookdown text references
+# (https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#text-references)
+# out in the main text and then include the reference key in the table:
+# 
+# In the text:
+# (ref:vdem) @vdem-v10
+#
+# In the table:
+# (ref:vdem)
+# 
+# It's weird, but it works
+
 tribble(
   ~Measure, ~Category, ~Description, ~Source,
-  "Political Terror Scale (PTS)", NA, "Ordered category ranging from 1 (least terror) to 5 (most terror)", "Gibney et al. (2019)",
-  "Physical violence index", NA, "0–1; higher values indicate less violence", "Coppedge et al. (2020); v2x_clphy",
-  "Private civil liberties index", NA, "0–1; higher values indicate greater respect for civil liberties", "Coppedge et al. (2020); v2x_clpriv",
-  "Total legal barriers", "De jure laws", "Count of all anti-NGO legal barriers", "Chaudhry (2016)",
-  "Barriers to advocacy", "De jure laws", "Count of laws restricting NGO advocacy", "Chaudhry (2016)",
-  "Barriers to entry", "De jure laws", "Count of laws restricting NGO entry, including registration", "Chaudhry (2016)",
-  "Barriers to funding", "De jure laws", "Count of laws restricting NGO funding sources", "Chaudhry (2016)",
-  "CSO repression", "De facto repression", "≈ −3–3; higher values indicate less repression", "Coppedge et al. (2020); v2csreprss"
-) %>%
-  kbl(caption = "Outcomes and predictors",
-      booktabs = TRUE, linesep = "\\addlinespace") %>% 
-  kable_styling(font_size = 8) %>% 
-  row_spec(0, bold = TRUE) %>% 
-  column_spec(1, width = "0.14\\\\textwidth") %>% 
-  column_spec(2, width = "0.14\\\\textwidth") %>% 
-  column_spec(3, width = "0.4\\\\textwidth") %>% 
-  column_spec(4, width = "0.2\\\\textwidth") %>% 
-  pack_rows(index = c("Outcomes" = 3, "Predictors" = 5))
-```
-
-```{r var-summary1, eval=FALSE, include=FALSE}
-tribble(
-  ~Measure, ~Category, ~Description, ~Source,
-  "Political Terror Scale (PTS)", NA, "Ordered category ranging from 1 (least terror) to 5 (most terror)", "@GibneyCornettWood:2019",
-  "Physical violence index", NA, "0–1; higher values indicate less violence", "@vdem-v10; v2x_clphy",
-  "Private civil liberties index", NA, "0–1; higher values indicate greater respect for civil liberties", "@vdem-v10; v2x_clpriv",
-  "Total legal barriers", "De jure laws", "Count of all anti-NGO legal barriers", "\\@Chaudhry:2016",
-  "Barriers to advocacy", "De jure laws", "Count of laws restricting NGO advocacy", "\\@Chaudhry:2016",
-  "Barriers to entry", "De jure laws", "Count of laws restricting NGO entry, including registration", "@Chaudhry:2016",
-  "Barriers to funding", "De jure laws", "Count of laws restricting NGO funding sources", "@Chaudhry:2016",
-  "CSO repression", "De facto repression", "≈ −3–3; higher values indicate less repression", "@vdem-v10; v2csreprss"
+  "Political Terror Scale (PTS)", NA, "Ordered category ranging from 1 (least terror) to 5 (most terror)", "(ref:pts)",
+  "Physical violence index", NA, "0–1; higher values indicate less violence", "(ref:vdem); v2x_clphy",
+  "Private civil liberties index", NA, "0–1; higher values indicate greater respect for civil liberties", "(ref:vdem); v2x_clpriv",
+  "Total legal barriers", "De jure laws", "Count of all anti-NGO legal barriers", "(ref:chaudhry)",
+  "Barriers to advocacy", "De jure laws", "Count of laws restricting NGO advocacy", "(ref:chaudhry)",
+  "Barriers to entry", "De jure laws", "Count of laws restricting NGO entry, including registration", "(ref:chaudhry)",
+  "Barriers to funding", "De jure laws", "Count of laws restricting NGO funding sources", "(ref:chaudhry)",
+  "CSO repression", "De facto repression", "≈ −3–3; higher values indicate less repression", "(ref:vdem); v2csreprss"
 ) %>%

### 2021-04-04 manuscript/manuscript.Rmd
Manuscript knits to all outputs now

@@
   Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions.
-This new wave of attempts to repress civil society organization-many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
+This new wave of attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
 This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
@@
 title-page: true
+endnotes: false
+endfloat: false
+mainfont: Cochineal
+sansfont: Inter
 editor_options: 
@@
 
-tribble(
+tbl_var_summary_caption <- "Outcomes and predictors"
+
+tbl_var_summary <- tribble(
   ~Measure, ~Category, ~Description, ~Source,
@@
   "CSO repression", "De facto repression", "≈ −3–3; higher values indicate less repression", "(ref:vdem); v2csreprss"
-) %>%
-  kbl(caption = "Outcomes and predictors",
+)
+
+if (!is_docx) {
+  tbl_var_summary %>%
+    kbl(caption = tbl_var_summary_caption,
         booktabs = TRUE, linesep = "") %>% 
-  kable_styling(font_size = 8.5) %>% 
+    pack_rows(index = c("Outcomes" = 3, "Predictors" = 5)) %>% 
+    kable_styling(font_size = ifelse(is_latex, 8.5, NA)) %>% 
     row_spec(0, bold = TRUE) %>% 
@@
     column_spec(3, width = "0.5\\\\textwidth") %>% 
-  column_spec(4, width = "0.2\\\\textwidth") %>% 
-  pack_rows(index = c("Outcomes" = 3, "Predictors" = 5))
+    column_spec(4, width = "0.2\\\\textwidth")
+} else {
+  tbl_var_summary %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    insert_row("Outcomes", "", "", "", after = 1) %>% 
+    insert_row("Predictors", "", "", "", after = 5) %>% 
+    set_bold(1, everywhere) %>%
+    set_bold(c(2, 6), everywhere) %>%
+    set_bottom_border(c(2, 6), everywhere) %>%
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_var_summary_caption) %>% 
+    huxtable::as_flextable()
+}
 ```
@@
 
+pts_pred_table_caption <- "Counts of correctly and incorrectly predicted cases across different PTS models"
+
+if (!is_docx) {
   pts_pred_table %>% 
@@
         booktabs = TRUE, linesep = "",
-      caption = "Counts of correctly and incorrectly predicted cases across different PTS models") %>% 
-  kable_styling(font_size = 8.5) %>%
+        caption = pts_pred_table_caption) %>% 
+    kable_styling(font_size = ifelse(is_latex, 8.5, NA)) %>%
     kable_styling() %>% 
@@
     column_spec(2:7, width = "0.14\\\\textwidth")
+} else {
+  pts_pred_table %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    set_bold(1, everywhere) %>%
+    set_bottom_border(1, everywhere) %>%
+    # set_col_width(1, 0.05) %>%
+    # set_col_width(2:7, 0.14) %>% 
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(pts_pred_table_caption) %>% 
+    huxtable::as_flextable()
+}
 ```
@@
 
+tbl_rmse_caption <- "Root mean squared error across models predicting physical violence and private civil liberties"
+
+if (!is_docx) {
   tbl_rmse %>% 
@@
         booktabs = TRUE, linesep = "",
-      caption = "Root mean squared error across models predicting physical violence and private civil liberties") %>% 
+        caption = tbl_rmse_caption) %>% 
     pack_rows(index = c("Physical violence index" = 6, "Private civil liberties index" = 6)) %>% 
     kable_styling()
+} else {
+  tbl_rmse %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    set_align(everywhere, 1, "left") %>% 
+    set_align(everywhere, 2:3, "center") %>% 
+    insert_row("Physical violence index", "", "", after = 1) %>% 
+    insert_row("Private civil liberties index", "", "", after = 8) %>% 
+    set_bold(1, everywhere) %>%
+    set_bold(c(2, 9), everywhere) %>%
+    set_bottom_border(c(2, 9), everywhere) %>%
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_rmse_caption) %>% 
+    huxtable::as_flextable()
+}
 ```
@@
 ```{r tbl-improved-pts}
-tbl_improved_pts <- tibble::tribble(
+tbl_improved_pts <- tribble(
                ~Country, ~Year,   ~Actual, ~`Baseline prediction`, ~`Total NGO barriers included`, ~`Civil society repression included`,
@@
 
+tbl_improved_pts_caption <- "Country-year cases where including civil society restrictions improved PTS predictions"
+
+if (!is_docx) {
   tbl_improved_pts %>% 
@@
         booktabs = TRUE, linesep = "\\addlinespace",
-      caption = "Country-year cases where including civil society restrictions improved PTS predictions") %>% 
+        caption = tbl_improved_pts_caption) %>% 
     kable_styling(latex_options = c("hold_position")) %>% 
@@
     column_spec(3:6, width = "0.16\\\\textwidth")
+} else {
+  tbl_improved_pts %>% 
+    hux() %>% 
+    set_font_size(10) %>%
+    set_all_padding(3) %>% 
+    set_align(everywhere, 1:2, "left") %>% 
+    set_align(everywhere, 3:6, "center") %>% 
+    set_bold(1, everywhere) %>%
+    set_bottom_border(1, everywhere) %>%
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_improved_pts_caption) %>% 
+    huxtable::as_flextable()
+}
 ```
@@
 
-modelsummary(models_paper_pts,
-             output = "kableExtra",
+tbl_reg_pts_caption <- "Full results from ordered logistic regression models predicting political terror"
+
+tbl_reg_pts <- modelsummary(models_paper_pts,
+                            output = table_format,
                             statistic = "[{conf.low}, {conf.high}]",
@@
                             escape = FALSE,
-             caption = "Full results from ordered logistic regression models predicting political terror",
-             notes = list("Posterior means; 95% credible intervals in brackets")) %>% 
-  kable_styling(font_size = 6) %>% 
+                            caption = tbl_reg_pts_caption,
+                            notes = list("Posterior means; 95% credible intervals in brackets"))
+
+if (!is_docx) {
+  tbl_reg_pts %>% 
+    kable_styling(font_size = ifelse(is_latex, 7, NA)) %>% 
     column_spec(1, width = "0.10\\\\textwidth") %>% 
     column_spec(2:6, width = "0.14\\\\textwidth")
+} else {
+  tbl_reg_pts %>% 
+    set_font_size(10) %>% 
+    set_all_padding(1) %>% 
+    set_align(everywhere, 2:6, "center") %>% 
+    set_bold(1, everywhere) %>% 
+    # set_col_width(1, 0.1) %>% 
+    # set_col_width(2:6, 0.14) %>% 
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_reg_pts_caption) %>% 
+    huxtable::as_flextable()
+}
 ```
@@
 
-modelsummary(models_paper_clphy,
-             output = "kableExtra",
+tbl_reg_clphy_caption <- "Full results from Gaussian regression models predicting physical violence"
+
+tbl_reg_clphy <- modelsummary(models_paper_clphy,
+                              output = table_format,
                               statistic = "[{conf.low}, {conf.high}]",
@@
                               escape = FALSE,
-             caption = "Full results from Gaussian regression models predicting physical violence",
-             notes = list("Posterior means; 95% credible intervals in brackets")) %>% 
-  kable_styling(font_size = 7.5) %>% 
+                              caption = tbl_reg_clphy_caption,
+                              notes = list("Posterior means; 95% credible intervals in brackets"))
+
+if (!is_docx) {
+  tbl_reg_clphy %>% 
+    kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
     column_spec(1, width = "0.10\\\\textwidth") %>% 
     column_spec(2:6, width = "0.14\\\\textwidth")
+} else {
+  tbl_reg_clphy %>% 
+    set_font_size(10) %>% 
+    set_all_padding(1) %>% 
+    set_align(everywhere, 2:6, "center") %>% 
+    set_bold(1, everywhere) %>% 
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_reg_clphy_caption) %>% 
+    huxtable::as_flextable()
+}
 ```
@@
 
-modelsummary(models_paper_clpriv,
-             output = "kableExtra",
+tbl_reg_clpriv_caption <- "Full results from Gaussian regression models predicting private civil liberties"
+
+tbl_reg_clpriv <- modelsummary(models_paper_clpriv,
+                               output = table_format,
                                statistic = "[{conf.low}, {conf.high}]",
@@
                                escape = FALSE,
-             caption = "Full results from Gaussian regression models predicting private civil liberties",
-             notes = list("Posterior means; 95% credible intervals in brackets")) %>% 
-  kable_styling(font_size = 7.5) %>% 
+                               caption = tbl_reg_clpriv_caption,
+                               notes = list("Posterior means; 95% credible intervals in brackets"))
+
+if (!is_docx) {
+  tbl_reg_clpriv %>% 
+    kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
     column_spec(1, width = "0.10\\\\textwidth") %>% 
     column_spec(2:6, width = "0.14\\\\textwidth")
+} else {
+  tbl_reg_clpriv %>% 
+    set_font_size(10) %>% 
+    set_all_padding(1) %>% 
+    set_align(everywhere, 2:6, "center") %>% 
+    set_bold(1, everywhere) %>% 
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_reg_clpriv_caption) %>% 
+    huxtable::as_flextable()
+}
 ```

### 2021-04-04 R/funs_knitting.R

@@ -1,4 +1,4 @@
-render_html <- function(input, output, csl) {
+render_html <- function(input, output, csl, ...) {
   # Add CSS file as a dependency so it goes into the _files directory
   dep <- htmltools::htmlDependency(
     name = "ath",
@@ -26,7 +26,7 @@ render_html <- function(input, output, csl) {
   )
 }
 
-render_pdf <- function(input, output, bibstyle) {
+render_pdf <- function(input, output, bibstyle, ...) {
   rmarkdown::render(
     input = input,
     output_file = output,
@@ -46,7 +46,7 @@ render_pdf <- function(input, output, bibstyle) {
   )
 }
 
-render_pdf_ms <- function(input, output, bibstyle) {
+render_pdf_ms <- function(input, output, bibstyle, ...) {
   rmarkdown::render(
     input = input,
     output_file = output,
@@ -65,7 +65,7 @@ render_pdf_ms <- function(input, output, bibstyle) {
   )
 }
 
-render_docx <- function(input, output, csl) {
+render_docx <- function(input, output, csl, ...) {
   rmarkdown::render(
     input = input,
     output_file = output,

### 2021-04-04 _targets.R

@@ -257,31 +257,40 @@ list(
   #      to detect the target dependencies in the Rmd file
   #   2. Use a bunch of other file-based targets to actually render the document
   #      through different custom functions
+  tar_target(bib_file,
+             here("manuscript", "bibliography.bib"),
+             format = "file"),
+
   tar_target_raw("main_manuscript", "manuscript/manuscript.Rmd",
                  format = "file",
-                 deps = tar_knitr_deps("manuscript/manuscript.Rmd")),
+                 deps = c("bib_file",
+                          tar_knitr_deps("manuscript/manuscript.Rmd"))),
   tar_target(html,
              render_html(
                input = main_manuscript,
                output = "output/manuscript.html",
-               csl = csl),
+               csl = csl,
+               bib_file),
              format = "file"),
   tar_target(pdf,
              render_pdf(
                input = main_manuscript,
                output = "output/manuscript.pdf",
-               bibstyle = bibstyle),
-             format = "file")#,
-  # tar_target(rendered_mspdf,
-  #            render_pdf_ms(
-  #              input = main_manuscript,
-  #              output = "output/manuscript-ms.pdf",
-  #              bibstyle = bibstyle),
-  #            format = "file"),
-  # tar_target(rendered_docx,
-  #            render_docx(
-  #              input = main_manuscript,
-  #              output = "output/manuscript.docx",
-  #              csl = csl),
-  #            format = "file")
+               bibstyle = bibstyle,
+               bib_file),
+             format = "file"),
+  tar_target(ms_pdf,
+             render_pdf_ms(
+               input = main_manuscript,
+               output = "output/manuscript-ms.pdf",
+               bibstyle = bibstyle,
+               bib_file),
+             format = "file"),
+  tar_target(docx,
+             render_docx(
+               input = main_manuscript,
+               output = "output/manuscript.docx",
+               csl = csl,
+               bib_file),
+             format = "file")
 )

### 2021-04-05 manuscript/manuscript.Rmd
Make targets for marginal effects calculations instead of the janky caching thing I had earlier

@@
   tar_load(coef_list)
+
+  # Load marginal effects
+  tar_load(c(mfx_e1a_pts, mfx_e1b_clphy, mfx_e1c_clpriv,
+             mfx_e2a_pts, mfx_e2b_clphy, mfx_e2c_clpriv))
 })
-
-# Temporary fake cache stuff
-mfx_e1a <- readRDS(here("temp_cache", "mfx_e1a.rds"))
-mfx_e1b <- readRDS(here("temp_cache", "mfx_e1b.rds"))
-mfx_e1c <- readRDS(here("temp_cache", "mfx_e1c.rds"))
-df_mfx_e2a <- readRDS(here("temp_cache", "df_mfx_e2a.rds"))
-df_mfx_e2b <- readRDS(here("temp_cache", "df_mfx_e2b.rds"))
-df_mfx_e2c <- readRDS(here("temp_cache", "df_mfx_e2c.rds"))
 ```
@@
 ```{r plot-mfx-e1a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on the probability of specific levels of political terror"}
-plot_e1a_mfx <- tribble(
-  ~model, ~plot_var, ~plot_var_nice,
-  m_pts_total, "barriers_total", "Total legal barriers",
-  m_pts_advocacy, "advocacy", "Barriers to advocacy",
-  m_pts_entry, "entry", "Barriers to entry",
-  m_pts_funding, "funding", "Barriers to funding"
-) %>% 
-  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
-
-# mfx_e1a <- plot_e1a_mfx %>% 
-#   mutate(fx = map2(model, plot_var, 
-#                    ~conditional_effects(.x, effects = .y,
-#                                         categorical = TRUE)[[1]])) %>% 
-#   select(-model) %>% 
-#   unnest(fx)
-# saveRDS(mfx_e1a, here("temp_cache", "mfx_e1a.rds"))
-
-mfx_e1a %>% 
+mfx_e1a_pts %>% 
   mutate(x_rounded = floor(effect1__)) %>% 
@@
 ```{r plot-mfx-e1b-e1c, fig.width=7.5, fig.height=5.5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on V-Dem rights indexes"}
-plot_e1b_mfx <- tribble(
-  ~model, ~plot_var, ~plot_var_nice,
-  m_clphy_total, "barriers_total", "Total legal barriers",
-  m_clphy_advocacy, "advocacy", "Advocacy",
-  m_clphy_entry, "entry", "Entry",
-  m_clphy_funding, "funding", "Funding"
-) %>% 
-  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
-
-# mfx_e1b <- plot_e1b_mfx %>% 
-#   mutate(fx = map2(model, plot_var, 
-#                    ~conditional_effects(.x, effects = .y)[[1]])) %>% 
-#   select(-model) %>% 
-#   unnest(fx)
-# saveRDS(mfx_e1b, here("temp_cache", "mfx_e1b.rds"))
-
-plot_e1c_mfx <- tribble(
-  ~model, ~plot_var, ~plot_var_nice,
-  m_clpriv_total, "barriers_total", "Total legal barriers",
-  m_clpriv_advocacy, "advocacy", "Advocacy",
-  m_clpriv_entry, "entry", "Entry",
-  m_clpriv_funding, "funding", "Funding"
-) %>% 
-  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
-
-# mfx_e1c <- plot_e1c_mfx %>% 
-#   mutate(fx = map2(model, plot_var, 
-#                    ~conditional_effects(.x, effects = .y)[[1]])) %>% 
-#   select(-model) %>% 
-#   unnest(fx)
-# saveRDS(mfx_e1c, here("temp_cache", "mfx_e1c.rds"))
-
-out_mfx_e1b <- mfx_e1b %>% 
+out_mfx_e1b <- mfx_e1b_clphy %>% 
   mutate(x_rounded = floor(effect1__)) %>% 
@@
 
-out_mfx_e1c <- mfx_e1c %>% 
+out_mfx_e1c <- mfx_e1c_clpriv %>% 
   mutate(x_rounded = floor(effect1__)) %>% 
@@
 ```{r plot-mfx-e2a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on the probability of specific levels of political terror"}
-# df_mfx_e2a <- conditional_effects(m_pts_v2csreprss,
-#                                   effects = "v2csreprss",
-#                                   categorical = TRUE)[[1]]
-# saveRDS(df_mfx_e2a, here("temp_cache", "df_mfx_e2a.rds"))
-
-out_mfx_e2a <- df_mfx_e2a %>% 
+out_mfx_e2a <- mfx_e2a_pts %>% 
   ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
@@
 ```{r plot-mfx-e2b-e2c, fig.width=7.5, fig.height=3.5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on V-Dem rights indexes"}
-# df_mfx_e2b <- conditional_effects(m_clphy_v2csreprss,
-#                                   effects = "v2csreprss")[[1]]
-# df_mfx_e2c <- conditional_effects(m_clpriv_v2csreprss,
-#                                   effects = "v2csreprss")[[1]]
-# saveRDS(df_mfx_e2b, here("temp_cache", "df_mfx_e2b.rds"))
-# saveRDS(df_mfx_e2c, here("temp_cache", "df_mfx_e2c.rds"))
-
-out_mfx_e2b <- df_mfx_e2b %>% 
+out_mfx_e2b <- mfx_e2b_clphy %>% 
   ggplot(aes(x = effect1__, y = estimate__)) +
@@
 
-out_mfx_e2c <- df_mfx_e2c %>% 
+out_mfx_e2c <- mfx_e2c_clpriv %>% 
   ggplot(aes(x = effect1__, y = estimate__)) +

### 2021-04-05 R/models_analysis.R

@@ -1,0 +1,13 @@
+generate_mfx <- function(models, is_categorical = FALSE) {
+  models <- models %>%
+    mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
+
+  mfx <- models %>%
+    mutate(fx = map2(model, plot_var,
+                     ~conditional_effects(.x, effects = .y,
+                                          categorical = is_categorical)[[1]])) %>%
+    select(-model) %>%
+    unnest(fx)
+
+  return(mfx)
+}

### 2021-04-05 _targets.R

@@ -37,6 +37,7 @@ source("R/funs_data-cleaning.R")
 source("R/funs_knitting.R")
 source("R/funs_notebook.R")
 source("R/models_details.R")
+source("R/models_analysis.R")
 source("R/models_pts.R")
 source("R/models_clphy.R")
 source("R/models_clpriv.R")
@@ -202,6 +203,42 @@ list(
 
   # Big dataframe of model names for full models
   tar_target(model_df, create_model_df()),
+
+  # Calculate marginal effects
+  tar_target(mfx_e1a_pts, generate_mfx(
+    tibble(model = list(m_pts_total, m_pts_advocacy, m_pts_entry, m_pts_funding),
+           plot_var = c("barriers_total", "advocacy", "entry", "funding"),
+           plot_var_nice = c("Total legal barriers", "Barriers to advocacy",
+                             "Barriers to entry", "Barriers to funding")),
+    is_categorical = TRUE)),
+
+  tar_target(mfx_e1b_clphy, generate_mfx(
+    tibble(model = list(m_clphy_total, m_clphy_advocacy, m_clphy_entry, m_clphy_funding),
+           plot_var = c("barriers_total", "advocacy", "entry", "funding"),
+           plot_var_nice = c("Total legal barriers", "Barriers to advocacy",
+                             "Barriers to entry", "Barriers to funding")))),
+
+  tar_target(mfx_e1c_clpriv, generate_mfx(
+    tibble(model = list(m_clpriv_total, m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding),
+           plot_var = c("barriers_total", "advocacy", "entry", "funding"),
+           plot_var_nice = c("Total legal barriers", "Barriers to advocacy",
+                             "Barriers to entry", "Barriers to funding")))),
+
+  tar_target(mfx_e2a_pts, generate_mfx(
+    tibble(model = list(m_pts_v2csreprss),
+           plot_var = c("v2csreprss"),
+           plot_var_nice = c("Civil society repression")),
+    is_categorical = TRUE)),
+
+  tar_target(mfx_e2b_clphy, generate_mfx(
+    tibble(model = list(m_clphy_v2csreprss),
+           plot_var = c("v2csreprss"),
+           plot_var_nice = c("Civil society repression")))),
+
+  tar_target(mfx_e2c_clpriv, generate_mfx(
+    tibble(model = list(m_clpriv_v2csreprss),
+           plot_var = c("v2csreprss"),
[…]

### 2021-04-05 analysis/index.Rmd
Add links to manuscript output

--- 2019-05-16 analysis/index.Rmd
@@
 ---
-title: "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
+title: "Canary in the Coal Mine: Civil Society Repression as a Predictor of Human Rights Abuses"
 author: "Suparna Chaudhry and Andrew Heiss"
@@
 Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions.
-While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of laws—many of which appear mundane on their face—represent a bureaucratic form of repressive that could be indicative of more severe human rights abuses and backsliding.
+This new wave of attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
 This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
-In this paper, we ask: do legal crackdowns on NGOs predict broader civil society repression?
+In this paper, we ask: do crackdowns on NGOs predict broader human rights repression?
 We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
 These laws also make it easier for states to prevent and deter future large-scale popular mobilization.
-Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of attacks on journalists, independent media, academic freedom, and freedoms of expression and association.
+Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, physical violence, and violations of private civil liberties.
 This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deteriorations in space for civil society.

### 2021-04-05 manuscript/manuscript.Rmd
Add code repo note

@@
 published: This is an early draft of a working paper.
-git-repo: https://github.com/andrewheiss/canary-ngos
+code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/canary-ngos/>"
 abstract: >-

### 2021-04-05 manuscript/manuscript.Rmd
Add note about citations in flextables with bookdown::word_document2

@@
 # It's weird, but it works
+#
+# BUT it doesn't work with Word, and flextable specifically. (ref:vdem) gets
+# correctly replaced with @vdem-10, but then it doesn't get processed by pandoc.
+# One way around this is to use the ftExtra package, which has colformat_md()
+# that will treat a column like Markdown and will allow pandoc to process
+# citations (see https://github.com/davidgohel/flextable/issues/243 and
+# ftExtra's citation support here:
+# https://ftextra.atusy.net/articles/format_columns.html#citations). BUT BUT the
+# ordering of bookdown's text references replacement messes with flextable's
+# citation processing or something, so pandoc references that are inserted with
+# (ref:vdem) remain as @vdem-10 when knitted. The way around *this* is to use
+# the raw @citekey in the table. Oof.
+#
+# Here's a minimal example:
+#
+# bloop <- tribble(
+#   ~Thing, ~Source, ~Source_word,
+#   "This *is* a test", "(ref:vdem)", "@vdem-v10"
+# ) 
+# 
+# if (is_docx) {
+#   bloop %>% 
+#     select(Thing, Source = Source_word) %>% 
+#     hux() %>% 
+#     huxtable::as_flextable() %>% 
+#     ftExtra::colformat_md() 
+# } else {
+#   bloop %>% 
+#     select(-Source_word) %>% 
+#     kbl(booktabs = TRUE) %>% 
+#     kable_styling()
+# }
 

### 2021-04-06 R/funs_knitting.R
Extract citations!

@@ -1,3 +1,5 @@
+library(bib2df)
+
 render_html <- function(input, output, csl, ...) {
   # Add CSS file as a dependency so it goes into the _files directory
   dep <- htmltools::htmlDependency(
@@ -77,4 +79,58 @@ render_docx <- function(input, output, csl, ...) {
       number_sections = FALSE
     )
   )
+}
+
+extract_bib <- function(input_rmd, input_bib, output, ...) {
+  # Load the document
+  document <- readLines(input_rmd)
+
+  # Find all the citation-looking things in the document. This picks up e-mail
+  # addresses (like example@gsu.edu) and it picks up bookdown-style references,
+  # like \@ref(fig:thing). I filter out the "ref" entries, but leave the e-mail
+  # addresses because there's too much possible variation there to easily remove
+  # them. As long as there aren't citation keys like "gsu" or "gmail", it should
+  # be fine. I also remove pandoc-crossref-style references like @fig:thing,
+  # @tbl:thing, @eq:thing, and @sec:thing
+  found_citations <- document %>%
+    map(~as_tibble(str_match_all(., "@([[:alnum:]:&!~=_+-]+)")[[1]][,2])) %>%
+    bind_rows() %>%
+    filter(value != "ref",
+           !str_starts(value, "fig:"),
+           !str_starts(value, "tbl:"),
+           !str_starts(value, "eq:"),
+           !str_starts(value, "sec:")) %>%
+    distinct(value) %>%
+    pull(value)
+
+  # Load the bibliography and convert to a data frame
+  # When year is the last key in an entry and the closing entry brace is on the
+  # same line, like `Year = {2006}}`, bib2df() parses the year as "2006}" and
+  # includes the closing }, which then causes warnings about year not being an
+  # integer. So here I remove all curly braces from the YEAR column
+  suppressWarnings(suppressMessages({
+    bib_df <- bib2df(input_bib) %>%
+      mutate(YEAR = str_remove_all(YEAR, "\\{|\\}"))
+  }))
+
+  # In biblatex, entries can be cross-referenced using the crossref key. When
+  # including something that's cross-referenced, like an incollection item, the
+  # containing item should also be extracted
+  if (any(names(bib_df) == "CROSSREF")) {
+    crossrefs <- bib_df %>%
+      filter(BIBTEXKEY %in% found_citations) %>%
[…]

### 2021-04-06 _targets.R

@@ -329,5 +329,11 @@ list(
                output = "output/manuscript.docx",
                csl = csl,
                bib_file),
+             format = "file"),
+  tar_target(bib,
+             extract_bib(
+               input_rmd = main_manuscript,
+               input_bib = bib_file,
+               output = "manuscript/output/extracted-citations.bib"),
              format = "file")
 )

### 2021-04-06 _targets.R
Use relative here::here()

@@ -26,7 +26,7 @@ options(tidyverse.quiet = TRUE,
 
 future::plan(future::multisession)
 
-tar_option_set(packages = c("tidyverse", "countrycode", "states", "WDI", "here",
+tar_option_set(packages = c("tidyverse", "countrycode", "states", "WDI", "here", "fs",
                             "readxl", "haven", "sf", "lubridate", "scales", "naniar",
                             "janitor", "kableExtra", "huxtable", "modelsummary",
                             "knitr", "withr", "flextable", "testthat", "DT",
@@ -41,6 +41,14 @@ source("R/models_analysis.R")
 source("R/models_pts.R")
 source("R/models_clphy.R")
 source("R/models_clpriv.R")
+
+# here::here() returns an absolute path, which then gets stored in tar_meta and
+# becomes computer-specific (i.e. /Users/andrew/Research/blah/thing.Rmd).
+# There's no way to get a relative path directly out of here::here(), but
+# fs::path_rel() works fine with it (see
+# https://github.com/r-lib/here/issues/36#issuecomment-530894167)
+here_rel <- function(...) {fs::path_rel(here::here(...))}
+
 
 list(
   # Define raw data files
@@ -74,15 +82,15 @@ list(
                   "UNdata_Export_20210118_034311252.csv"),
              format = "file"),
   tar_target(naturalearth_raw_file,
-             here("data", "raw_data", "ne_110m_admin_0_countries",
-                  "ne_110m_admin_0_countries.shp"),
+             here_rel("data", "raw_data", "ne_110m_admin_0_countries",
+                      "ne_110m_admin_0_countries.shp"),
              format = "file"),
   tar_target(civicus_raw_file,
-             here("data", "raw_data", "Civicus", "civicus_2021-03-19.json"),
+             here_rel("data", "raw_data", "Civicus", "civicus_2021-03-19.json"),
              format = "file"),
 
   # Define helper functions
-  tar_target(plot_funs, here("lib", "graphics.R"), format = "file"),
+  tar_target(plot_funs, here_rel("lib", "graphics.R"), format = "file"),
 
   # Load and clean data
   tar_target(world_map, load_world_map(naturalearth_raw_file)),
@@ -295,38 +303,38 @@ list(
   #   2. Use a bunch of other file-based targets to actually render the document
   #      through different custom functions
   tar_target(bib_file,
-             here("manuscript", "bibliography.bib"),
[…]

### 2021-04-06 manuscript/pandoc/bin/render_docx.R
Remove old pandoc support files

@@ -1,23 +1,0 @@
-#!/usr/bin/env Rscript
-
-args <- R.utils::cmdArgs()
-
-# Check arguments
-stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
-          "Specify an output file using -output\n(e.g. `-output manuscript.docx`)" = is.character(args$output),
-          "Specify a CSL file using -csl\n(e.g. `-csl pandoc/csl/apa.csl`)" = is.character(args$csl))
-
-pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
-
-# Knit
-rmarkdown::render(
-  input = args$input,
-  output_file = args$output,
-  bookdown::word_document2(
-    reference_docx = paste0(pandoc_suport, "/templates/ath-manuscript.docx"),
-    pandoc_args = c(paste0("--csl=", args$csl)),
-    md_extensions = "+raw_tex+smart-autolink_bare_uris",
-    toc = FALSE,
-    number_sections = FALSE
-  )
-)

### 2021-04-06 manuscript/pandoc/bin/render_html.R

@@ -1,37 +1,0 @@
-#!/usr/bin/env Rscript
-
-args <- R.utils::cmdArgs()
-
-# Check arguments
-stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
-          "Specify an output file using -output\n(e.g. `-output manuscript.html`)" = is.character(args$output),
-          "Specify a CSL file using -csl\n(e.g. `-csl pandoc/csl/apa.csl`)" = is.character(args$csl))
-
-pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
-
-# Add CSS file as a dependency so it goes into the _files directory
-dep <- htmltools::htmlDependency(
-  name = "ath",
-  version = "1.0.0",
-  paste0(pandoc_suport, "/css"),
-  stylesheet = "ath-clean.css"
-)
-extra_dependencies <- list(dep)
-
-# Knit
-rmarkdown::render(
-  input = args$input,
-  output_file = args$output,
-  bookdown::html_document2(
-    template = paste0(pandoc_suport, "/templates/html.html"),
-    pandoc_args = c("--metadata", "link-citations=true",
-                    "--metadata", "linkReferences=true",
-                    paste0("--csl=", args$csl)),
-    md_extensions = "+raw_tex+smart-autolink_bare_uris+ascii_identifiers",
-    toc = TRUE,
-    number_sections = FALSE,
-    self_contained = FALSE,
-    theme = NULL,
-    extra_dependencies = extra_dependencies
-  )
-)

### 2021-04-06 manuscript/pandoc/bin/render_odt.R

@@ -1,24 +1,0 @@
-#!/usr/bin/env Rscript
-
-args <- R.utils::cmdArgs()
-
-# Check arguments
-stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
-          "Specify an output file using -output\n(e.g. `-output manuscript.odt`)" = is.character(args$output),
-          "Specify a CSL file using -csl\n(e.g. `-csl pandoc/csl/apa.csl`)" = is.character(args$csl))
-
-pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
-
-# Knit
-rmarkdown::render(
-  input = args$input,
-  output_file = args$output,
-  bookdown::odt_document2(
-    template = paste0(pandoc_suport, "/templates/odt.odt"),
-    reference_odt = paste0(pandoc_suport, "/templates/reference.odt"),
-    pandoc_args = c(paste0("--csl=", args$csl)),
-    md_extensions = "+raw_tex+smart-autolink_bare_uris+ascii_identifiers",
-    toc = FALSE,
-    number_sections = FALSE
-  )
-)

### 2021-04-06 manuscript/pandoc/bin/render_pdf-ms.R

@@ -1,31 +1,0 @@
-#!/usr/bin/env Rscript
-
-args <- R.utils::cmdArgs()
-
-# Check arguments
-stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
-          "Specify an output file using -output\n(e.g. `-output manuscript-ms.pdf`)" = is.character(args$output),
-          "Specify one of these options using -bibstyle:
-- bibstyle-chicago-notes
-- bibstyle-chicago-authordate
-- bibstyle-apa
-(e.g. `-bibstyle bibstyle-chicago-notes`)" = is.character(args$bibstyle))
-
-pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
-
-rmarkdown::render(
-  input = args$input,
-  output_file = args$output,
-  bookdown::pdf_document2(
-    template = paste0(pandoc_suport, "/templates/xelatex-manuscript.tex"),
-    latex_engine = "xelatex", 
-    dev = "cairo_pdf",
-    pandoc_args = c("--top-level-division=section", 
-                    "--shift-heading-level-by=0", 
-                    "-V", args$bibstyle),
-    md_extensions = "+raw_tex+smart-autolink_bare_uris",
-    toc = FALSE,
-    keep_tex = FALSE,
-    citation_package = "biblatex"
-  )
-)

### 2021-04-06 manuscript/pandoc/bin/render_pdf.R

@@ -1,32 +1,0 @@
-#!/usr/bin/env Rscript
-
-args <- R.utils::cmdArgs()
-
-# Check arguments
-stopifnot("Specify an input file using -input\n(e.g. `-input manuscript.Rmd`)" = is.character(args$input),
-          "Specify an output file using -output\n(e.g. `-output manuscript.pdf`)" = is.character(args$output),
-          "Specify one of these options using -bibstyle:
-- bibstyle-chicago-notes
-- bibstyle-chicago-authordate
-- bibstyle-apa
-(e.g. `-bibstyle bibstyle-chicago-notes`)" = is.character(args$bibstyle))
-
-pandoc_suport <- ifelse(is.null(args$pandoc), "pandoc", args$pandoc)
-
-rmarkdown::render(
-  input = args$input,
-  output_file = args$output,
-  bookdown::pdf_document2(
-    template = paste0(pandoc_suport, "/templates/xelatex.tex"),
-    latex_engine = "xelatex",
-    dev = "cairo_pdf",
-    pandoc_args = c("--top-level-division=section",
-                    "--shift-heading-level-by=0",
-                    "-V", args$bibstyle,
-                    "-V", "chapterstyle=hikma-article"),
-    md_extensions = "+raw_tex+smart-autolink_bare_uris",
-    toc = FALSE,
-    keep_tex = FALSE,
-    citation_package = "biblatex"
-  )
-)

### 2021-04-06 R/funs_knitting.R
Return relative-to-project paths for knitted things

@@ -10,7 +10,7 @@ render_html <- function(input, output, csl, ...) {
   )
   extra_dependencies <- list(dep)
 
-  rmarkdown::render(
+  out <- rmarkdown::render(
     input = input,
     output_file = output,
     bookdown::html_document2(
@@ -26,10 +26,12 @@ render_html <- function(input, output, csl, ...) {
       extra_dependencies = extra_dependencies
     )
   )
+
+  return(fs::path_rel(out))
 }
 
 render_pdf <- function(input, output, bibstyle, ...) {
-  rmarkdown::render(
+  out <- rmarkdown::render(
     input = input,
     output_file = output,
     bookdown::pdf_document2(
@@ -46,10 +48,12 @@ render_pdf <- function(input, output, bibstyle, ...) {
       citation_package = "biblatex"
     )
   )
+
+  return(fs::path_rel(out))
 }
 
 render_pdf_ms <- function(input, output, bibstyle, ...) {
-  rmarkdown::render(
+  out <- rmarkdown::render(
     input = input,
     output_file = output,
     bookdown::pdf_document2(
@@ -65,10 +69,12 @@ render_pdf_ms <- function(input, output, bibstyle, ...) {
       citation_package = "biblatex"
     )
   )
+
+  return(fs::path_rel(out))
 }
 
 render_docx <- function(input, output, csl, ...) {
-  rmarkdown::render(
+  out <- rmarkdown::render(
     input = input,
     output_file = output,
     bookdown::word_document2(
@@ -79,6 +85,8 @@ render_docx <- function(input, output, csl, ...) {
       number_sections = FALSE
     )
   )
+
+  return(fs::path_rel(out))
 }
 
 extract_bib <- function(input_rmd, input_bib, output, ...) {

### 2021-04-06 manuscript/manuscript.Rmd
oops replace this duplicate panel

@@
 barriers_summary <- 
-  ((advocacy_plot | funding_plot) / 
+  ((advocacy_plot | entry_plot) / 
      (funding_plot | csreprss_plot)) &

### 2021-04-07 R/funs_knitting.R
Fix the mysterious missing _files folder by putting HTML dependencies in their own specific folder
Related to https://github.com/rstudio/bookdown/issues/838

@@ -1,6 +1,6 @@
 library(bib2df)
 
-render_html <- function(input, output, csl, ...) {
+render_html <- function(input, output, csl, support_folder, ...) {
   # Add CSS file as a dependency so it goes into the _files directory
   dep <- htmltools::htmlDependency(
     name = "ath",
@@ -9,6 +9,12 @@ render_html <- function(input, output, csl, ...) {
     stylesheet = "ath-clean.css"
   )
   extra_dependencies <- list(dep)
+
+  # IMPORTANT
+  # When knitting to docx, bookdown deletes the _files directory for whatever
+  # reason, so if you knit to HTML and then docx, you get a nice *_files
+  # directly that then disappears when the Word file is done. One way around
+  # this is to specify lib_dir here in rmarkdown::render()
 
   out <- rmarkdown::render(
     input = input,
@@ -23,7 +29,8 @@ render_html <- function(input, output, csl, ...) {
       number_sections = FALSE,
       self_contained = FALSE,
       theme = NULL,
-      extra_dependencies = extra_dependencies
+      extra_dependencies = extra_dependencies,
+      lib_dir = support_folder
     )
   )
 

### 2021-04-07 _targets.R

@@ -315,7 +315,8 @@ list(
                input = main_manuscript,
                output = here_rel("manuscript", "output", "manuscript.html"),
                csl = csl,
-               bib_file),
+               bib_file,
+               support_folder = "output/html-support"),
              format = "file"),
   tar_target(pdf,
              render_pdf(

### 2021-04-07 analysis/04_predictions.Rmd
PHEWWWW ALL READY FOR ISA
Fix trimming issues with 2014 + use relative paths for data

@@
 }
-```
-
-```{r kludgy-bandaid-for-weird-data-issues}
-# OOOOOOOF OH NO for some reason PTS_lead1 and all leaded V-Dem values missing
-# for 2013 (i.e. 2014 values) and I don't want to go back and rerun all these
-# models yet, so we do a temporary fix here and manually add the values from
-# pts_clean and vdem_clean
-withr::with_dir(here::here(), {
-  tar_load(pts_clean)
-  tar_load(vdem_clean)
-})
-
-pts_2014 <- pts_clean %>% 
-  group_by(gwcode) %>% 
-  mutate(across(c(PTS, PTS_factor),
-                  list(lead1_2014 = ~lead(., 1)))) %>% 
-  ungroup() %>% 
-  filter(year == 2013) %>% 
-  select(-PTS, -PTS_factor)
-
-vdem_2014 <- vdem_clean %>% 
-  group_by(gwcode) %>% 
-  mutate(across(c(v2x_clphy, v2x_clpriv),
-                  list(lead1_2014 = ~lead(., 1)))) %>% 
-  ungroup() %>% 
-  filter(year == 2013) %>% 
-  select(gwcode, year, v2x_clphy_lead1_2014, v2x_clpriv_lead1_2014)
-
-canary_testing_lagged <- canary_testing_lagged %>% 
-  left_join(pts_2014, by = c("year", "gwcode")) %>% 
-  left_join(vdem_2014, by = c("year", "gwcode")) %>% 
-  mutate(PTS_lead1 = coalesce(PTS_lead1, PTS_lead1_2014),
-         PTS_factor_lead1 = coalesce(PTS_factor_lead1, PTS_factor_lead1_2014),
-         v2x_clphy_lead1 = coalesce(v2x_clphy_lead1, v2x_clphy_lead1_2014),
-         v2x_clpriv_lead1 = coalesce(v2x_clpriv_lead1, v2x_clpriv_lead1_2014)) %>% 
-  select(-contains("_2014"))
 ```
@@
 pts_pred_table %>% 
-  kbl(align = "lcccc") %>% 
+  kbl(align = "lccccc") %>% 
   kable_styling()

### 2021-04-07 R/funs_data-cleaning.R

@@ -446,8 +446,6 @@ combine_data <- function(skeleton, chaudhry_clean, pts_clean, killings_all,
   testthat::expect_equal(nrow(panel_skeleton),
                          nrow(panel_done))
 
-  panel_done <- panel_done %>% filter(year < 2014)
-
   return(panel_done)
 }
 
@@ -487,6 +485,10 @@ create_training <- function(df) {
 
 create_testing <- function(df) {
   df %>% filter(pred_group == "Testing")
+}
+
+trim_data <- function(df) {
+  df %>% filter(year < 2014)
 }
 
 

### 2021-04-07 _targets.R

@@ -53,32 +53,32 @@ here_rel <- function(...) {fs::path_rel(here::here(...))}
 list(
   # Define raw data files
   tar_target(chaudhry_raw_file,
-             here("data", "raw_data", "Chaudhry restrictions", "SC_Expanded.dta"),
+             here_rel("data", "raw_data", "Chaudhry restrictions", "SC_Expanded.dta"),
              format = "file"),
   tar_target(pts_raw_file,
-             here("data", "raw_data", "Political Terror Scale", "PTS-2019.RData"),
+             here_rel("data", "raw_data", "Political Terror Scale", "PTS-2019.RData"),
              format = "file"),
   tar_target(journalists_raw_file,
-             here("data", "raw_data", "Gohdes Carey journalists",
+             here_rel("data", "raw_data", "Gohdes Carey journalists",
                   "journalist-data-incl-pts.RData"),
              format = "file"),
   tar_target(ucdp_raw_file,
-             here("data", "raw_data", "UCDP PRIO", "ucdp-prio-acd-191.csv"),
+             here_rel("data", "raw_data", "UCDP PRIO", "ucdp-prio-acd-191.csv"),
              format = "file"),
   tar_target(vdem_raw_file,
-             here("data", "raw_data", "Country_Year_V-Dem_Full+others_R_v10",
+             here_rel("data", "raw_data", "Country_Year_V-Dem_Full+others_R_v10",
                   "V-Dem-CY-Full+Others-v10.rds"),
              format = "file"),
   tar_target(un_pop_raw_file,
-             here("data", "raw_data", "UN data",
+             here_rel("data", "raw_data", "UN data",
                   "WPP2019_POP_F01_1_TOTAL_POPULATION_BOTH_SEXES.xlsx"),
              format = "file"),
   tar_target(un_gdp_constant_raw_file,
-             here("data", "raw_data", "UN data",
+             here_rel("data", "raw_data", "UN data",
                   "UNdata_Export_20210118_034054729.csv"),
              format = "file"),
   tar_target(un_gdp_current_raw_file,
-             here("data", "raw_data", "UN data",
+             here_rel("data", "raw_data", "UN data",
                   "UNdata_Export_20210118_034311252.csv"),
              format = "file"),
   tar_target(naturalearth_raw_file,
@@ -107,13 +107,21 @@ list(
   tar_target(un_pop, load_clean_un_pop(un_pop_raw_file, skeleton, wdi_clean)),
[…]

### 2021-04-08 lib/presentation_graphs.R
Presentation-specific graphs

@@ -1,0 +1,185 @@
+library(tidyverse)
+library(targets)
+library(patchwork)
+library(sf)
+library(here)
+
+# Load data from targets --------------------------------------------------
+withr::with_dir(here(), {
+  source(tar_read(plot_funs))
+
+  canary <- tar_read(panel)
+  tar_load(civicus_map_data)
+  tar_load(civicus_clean)
+
+  # Load marginal effects
+  tar_load(c(mfx_e1a_pts, mfx_e1b_clphy, mfx_e1c_clpriv,
+             mfx_e2a_pts, mfx_e2b_clphy, mfx_e2c_clpriv))
+})
+
+
+# Map of restrictions -----------------------------------------------------
+ggplot() +
+  geom_sf(data = civicus_map_data, aes(fill = fct_rev(category)), size = 0.15, color = "black") +
+  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
+  scale_fill_viridis_d(option = "plasma", end = 0.9,
+                       na.translate = FALSE, name = NULL) +
+  theme_void(base_size = 18, base_family = "Inter Light") +
+  theme(legend.position = "bottom",
+        legend.key.size = unit(0.7, "lines"))
+
+ggsave(here("admin", "Presentations", "figures", "civicus_map.pdf"),
+       width = 40/3, height = 6.1, units = "in", device = cairo_pdf)
+
+
+# E1a marginal effects (total laws) ---------------------------------------
+mfx_e1a_pts %>%
+  mutate(x_rounded = floor(effect1__)) %>%
+  group_by(x_rounded, effect2__, plot_var_nice) %>%
+  slice(1) %>%
+  ungroup() %>%
+  filter(plot_var == "barriers_total") %>%
+  ggplot(aes(x = x_rounded, y = estimate__, color = effect2__)) +
+  geom_line(aes(group = effect2__), size = 0.5, color = "grey90") +
+  geom_pointrange(aes(ymin = lower__, ymax = upper__),
+                  size = 2.5,
+                  position = position_dodge(width = 0.2),
+                  fatten = 1.5) +
+  scale_x_continuous(breaks = 0:9) +
+  scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  scale_color_viridis_d(option = "plasma", end = 0.9) +
+  guides(color = guide_legend(override.aes = list(size = 0.5))) +
+  labs(x = "Count of legal barriers\n",
[…]

### 2021-04-08 R/funs_knitting.R
Add word count stuff as function instead of external script

@@ -1,4 +1,7 @@
 library(bib2df)
+library(rvest)
+library(xml2)
+library(stringi)
 
 render_html <- function(input, output, csl, support_folder, ...) {
   # Add CSS file as a dependency so it goes into the _files directory
@@ -148,4 +151,60 @@ extract_bib <- function(input_rmd, input_bib, output, ...) {
            -starts_with("DATE."), -KEYWORDS) %>%
     arrange(CATEGORY, BIBTEXKEY) %>%
     df2bib(output)
+}
+
+
+# string::stri_count_words() counts, um, words. That's its whole job. But it
+# doesn't count them like Microsoft Word counts them, and academic publishing
+# portals tend to care about Word-like counts. For instance, Word considers
+# hyphenated words to be one word, while stringr counts them as two (and even
+# worse, stringi counts / as word boundaries, so URLs can severely inflate your
+# word count).
+#
+# Also, academic writing typically doesn't count the title, abstract, table
+# text, figure captions, or equations as words in the manuscript (and it
+# SHOULDN'T count bibliographies, but it always seems to ugh).
+#
+# This parses the rendered HTML, removes extra elements, adjusts the text so
+# that stringi treats it more like Word, and then finally provides a more
+# accurate word count.
+count_words <- function(html) {
+  # Read the HTML file
+  ms_raw <- read_html(html)
+
+  # Extract just the article, ignoring title, abstract, etc.
+  ms <- ms_raw %>%
+    html_nodes("article")
+
+  # Get rid of figures, tables, and math
+  xml_remove(ms %>% html_nodes("figure"))
+  xml_remove(ms %>% html_nodes("table"))
+  xml_remove(ms %>% html_nodes(".display"))  # Block math
+  xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>%
+    invisible()
+
+  # Go through each child element in the article and extract it
+  ms_cleaned_list <- map(html_children(ms), ~ {
+    .x %>%
+      html_text(trim = TRUE) %>%
+      # ICU counts hyphenated words as multiple words, so replace - with DASH
+      str_replace_all("\\-", "DASH") %>%
+      # ICU also counts / as multiple words, so URLs go crazy. Replace / with SLASH
+      str_replace_all("\\/", "SLASH") %>%
+      # ICU *also* counts [things] in brackets multiple times, so kill those too
[…]

### 2021-04-08 manuscript/pandoc/bin/word_count.R

@@ -1,71 +1,0 @@
-#!/usr/bin/env Rscript
-
-# string::stri_count_words() counts, um, words. That's its whole job. But it
-# doesn't count them like Microsoft Word counts them, and academic publishing
-# portals tend to care about Word-like counts. For instance, Word considers
-# hyphenated words to be one word, while stringr counts them as two (and even
-# worse, stringi counts / as word boundaries, so URLs can severely inflate your
-# word count).
-#
-# Also, academic writing typically doesn't count the title, abstract, table
-# text, figure captions, or equations as words in the manuscript (and it
-# SHOULDN'T count bibliographies, but it always seems to ugh).
-#
-# This script parses the rendered manuscript HTML, removes extra elements,
-# adjusts the text so that stringi treats it more like Word, and then provides a
-# more accurate word count.
-
-suppressPackageStartupMessages(library(magrittr))
-suppressPackageStartupMessages(library(stringr))
-suppressPackageStartupMessages(library(purrr))
-suppressPackageStartupMessages(library(rvest))
-suppressPackageStartupMessages(library(stringi))
-
-args <- commandArgs(trailingOnly = TRUE)
-
-if (length(args) < 1) {
-  ms_file <- "paper.html"
-} else {
-  ms_file <- args[1]
-}
-
-# Read the HTML file
-ms_raw <- read_html(ms_file)
-
-# Extract just the article, ignoring title, abstract, etc.
-ms <- ms_raw %>%
-  html_nodes("article")
-
-# Get rid of figures, tables, and math
-xml_remove(ms %>% html_nodes("figure"))
-xml_remove(ms %>% html_nodes("table"))
-xml_remove(ms %>% html_nodes(".display"))  # Block math
-xml_replace(ms %>% html_nodes(".inline"), read_xml("<span>MATH</span>")) %>%
-  invisible()
-
-# Go through each child element in the article and extract it
-ms_cleaned_list <- map(html_children(ms), ~ {
-  .x %>%
-    html_text(trim = TRUE) %>%
-    # ICU counts hyphenated words as multiple words, so replace - with DASH
-    str_replace_all("\\-", "DASH") %>%
-    # ICU also counts / as multiple words, so URLs go crazy. Replace / with SLASH
-    str_replace_all("\\/", "SLASH") %>%
-    # ICU *also* counts [things] in bracketss multiple times, so kill those too
[…]

### 2021-04-08 R/funs_knitting.R
Be explicit about encoding

@@ -34,7 +34,8 @@ render_html <- function(input, output, csl, support_folder, ...) {
       theme = NULL,
       extra_dependencies = extra_dependencies,
       lib_dir = support_folder
-    )
+    ),
+    encoding = "UTF-8"
   )
 
   return(fs::path_rel(out))
@@ -56,7 +57,8 @@ render_pdf <- function(input, output, bibstyle, ...) {
       toc = FALSE,
       keep_tex = FALSE,
       citation_package = "biblatex"
-    )
+    ),
+    encoding = "UTF-8"
   )
 
   return(fs::path_rel(out))
@@ -77,7 +79,8 @@ render_pdf_ms <- function(input, output, bibstyle, ...) {
       toc = FALSE,
       keep_tex = FALSE,
       citation_package = "biblatex"
-    )
+    ),
+    encoding = "UTF-8"
   )
 
   return(fs::path_rel(out))
@@ -93,11 +96,13 @@ render_docx <- function(input, output, csl, ...) {
       md_extensions = "+raw_tex+smart-autolink_bare_uris",
       toc = FALSE,
       number_sections = FALSE
-    )
+    ),
+    encoding = "UTF-8"
   )
 
   return(fs::path_rel(out))
 }
+
 
 extract_bib <- function(input_rmd, input_bib, output, ...) {
   # Load the document

### 2021-04-10 R/models_pts.R
Move brms options to separate function so future workers can use them
This is because things set in options() don't get passed on to workers 🤷‍♂️ https://github.com/HenrikBengtsson/future/issues/134

@@ -1,6 +1,10 @@
 # Settings ----------------------------------------------------------------
 
+# Run this inside each model function instead of outside so that future workers
+# use these options internally
 pts_setup <- function() {
+  options(worker_options)
+
   # Settings
   CHAINS <- 4
   ITER <- 2000
@@ -16,12 +20,12 @@ pts_setup <- function() {
               priors_vague = priors_vague))
 }
 
-pts_settings <- pts_setup()
-
 
 # Regular models ----------------------------------------------------------
 
 f_pts_baseline <- function(dat) {
+  pts_settings <- pts_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -36,12 +40,15 @@ f_pts_baseline <- function(dat) {
     prior = pts_settings$priors_vague,
     data = dat,
     chains = pts_settings$chains, iter = pts_settings$iter,
-    warmup = pts_settings$warmup, seed = pts_settings$seed)
+    warmup = pts_settings$warmup, seed = pts_settings$seed,
+    threads = threading(getOption("n.threads", default = 1)))
 
   return(model)
 }
 
 f_pts_total <- function(dat) {
+  pts_settings <- pts_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -57,12 +64,39 @@ f_pts_total <- function(dat) {
     prior = pts_settings$priors_vague,
     data = dat,
     chains = pts_settings$chains, iter = pts_settings$iter,
-    warmup = pts_settings$warmup, seed = pts_settings$seed)
+    warmup = pts_settings$warmup, seed = pts_settings$seed,
+    threads = threading(getOption("n.threads", default = 1)))
+
+  return(model)
+}
+
+f_pts_total_new <- function(dat) {
+  pts_settings <- pts_setup()
+
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(PTS_factor_lead1 ~ barriers_total_new + barriers_total_new_lag1 +
+         PTS_factor +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = cumulative(),
[…]

### 2021-04-10 _targets.R

@@ -8,6 +8,14 @@ bibstyle <- "bibstyle-chicago-authordate"
 
 suppressPackageStartupMessages(library(brms))
 
+
+# Bayes-specific stuff
+options(mc.cores = 4,
+        brms.backend = "cmdstanr")
+
+options(tidyverse.quiet = TRUE,
+        dplyr.summarise.inform = FALSE)
+
 # By default, R uses polynomial contrasts for ordered factors in linear models
 # options("contrasts")
 # So make ordered factors use treatment contrasts instead
@@ -15,23 +23,32 @@ options(contrasts = rep("contr.treatment", 2))
 # Or do it on a single variable:
 # contrasts(df$x) <- "contr.treatment"
 
+# Things that get set in options() are not passed down to workers in future (see
+# https://github.com/HenrikBengtsson/future/issues/134), which means all these
+# neat options we set here disappear when running tar_make_future() (like
+# ordered treatment contrasts and the number of cores used, etc.). The official
+# recommendation is to add options() calls to the individual workers.
+#
+# We do this by including options() in the functions where we define model
+# priors and other settings (i.e. pts_settings()). But setting options there
+# inside a bunch of files can get tedious, since the number of cores, workers,
+# etc. depends on the computer we run this on (i.e. my 4-core personal laptop
+# vs. my 16-core work laptop).
+
+# Pass these options to workers using options(worker_options)
+worker_options <- options()[c("mc.cores", "brms.backend",
+                              "contrasts", "tidyverse.quiet",
+                              "dplyr.summarise.inform")]
+
 set.seed(9936)  # From random.org
-
-# Bayes-specific stuff
-options(mc.cores = parallel::detectCores(),
-        brms.backend = "cmdstanr")
-
-options(tidyverse.quiet = TRUE,
-        dplyr.summarise.inform = FALSE)
 
 future::plan(future::multisession)
 
 tar_option_set(packages = c("tidyverse", "countrycode", "states", "WDI", "here", "fs",
-                            "readxl", "haven", "sf", "lubridate", "scales", "naniar",
+                            "readxl", "haven", "sf", "lubridate", "scales",
[…]

### 2021-04-10 analysis/01_data-overview.Rmd
Include latent human rights measure

@@
   tar_load(pts_clean)
+  tar_load(latent_hr_clean)
   tar_load(killings_all)
@@
 glimpse(pts_clean)
+```
+
+## Latent Human Rights Protection Scores
+
+We also use Chris Fariss's [Latent Human Rights Protection Scores](https://doi.org/10.7910/DVN/RQ85GK), which are estimates from fancy Bayesian models that capture a country's respect for physical integrity rights.
+We use the posterior mean of the latent variable from the model (θ), and we keep the standard deviation of θ just in case we want to fancier things in the future and incorporate the uncertainty of θ in the models.
+We rename θ to `latent_hr_mean`.
+
+In this measure, high values represent strong respect for physical integrity rights:
+
+```{r showh-lhr-min-max}
+latent_hr_clean %>% 
+  filter(latent_hr_mean == max(latent_hr_mean) | 
+           latent_hr_mean == min(latent_hr_mean)) %>% 
+  left_join(select(skeleton$skeleton_lookup, gwcode, country),
+            by = "gwcode") %>% 
+  select(country, everything())
+```
+
+```{r glimpse-lhr}
+glimpse(latent_hr_clean)
 ```

### 2021-04-10 R/funs_data-cleaning.R

@@ -406,8 +406,25 @@ load_clean_un_gdp <- function(path_constant, path_current, skeleton) {
 }
 
 
-combine_data <- function(skeleton, chaudhry_clean, pts_clean, killings_all,
-                         ucdp_prio_clean, vdem_clean, un_pop, un_gdp) {
+load_clean_latent_hr <- function(path, skeleton) {
+  latent_hr_raw <- read_csv(path, col_types = cols())
+
+  latent_hr <- latent_hr_raw %>%
+    filter(YEAR >= 1990, COW %in% c(skeleton$skeleton_lookup$cowcode, 679),
+           COW != 678) %>%
+    # Deal with Yemen and Vietnam
+    mutate(gwcode = countrycode(COW, "cown", "gwn",
+                                custom_match = c("679" = 678L, "816" = 816))) %>%
+    select(year = YEAR, gwcode,
+           latent_hr_mean = theta_mean, latent_hr_sd = theta_sd)
+
+  return(latent_hr)
+}
+
+
+combine_data <- function(skeleton, chaudhry_clean,
+                         pts_clean, latent_hr, killings_all, ucdp_prio_clean,
+                         vdem_clean, un_pop, un_gdp) {
   # Only look at countries in Suparna's data
   chaudhry_countries <- chaudhry_clean %>% distinct(gwcode)
 
@@ -434,6 +451,7 @@ combine_data <- function(skeleton, chaudhry_clean, pts_clean, killings_all,
       TRUE ~ laws  # Otherwise, use FALSE
     )) %>%
     left_join(pts_clean, by = c("gwcode", "year")) %>%
+    left_join(latent_hr, by = c("gwcode", "year")) %>%
     left_join(killings_all, by = c("gwcode", "year")) %>%
     mutate(across(starts_with("gh"), ~coalesce(., 0L))) %>%
     mutate(gh_range = year >= 2002) %>%
@@ -453,6 +471,15 @@ combine_data <- function(skeleton, chaudhry_clean, pts_clean, killings_all,
 lag_data <- function(df) {
   panel_lagged <- df %>%
     group_by(gwcode) %>%
+    # Indicate changes in laws
+    mutate(across(c(advocacy, entry, funding, barriers_total),
+                  list(new = ~. - lag(.),
+                       worse = ~(. - lag(.)) > 0,
+                       cat = ~cut(. - lag(.),
+                                  breaks = c(-Inf, -1, 0, Inf),
+                                  labels = c("New better law", "No new laws",
+                                             "New worse law"),
[…]

### 2021-04-10 analysis/02_descriptive-analysis.Rmd
Minor renv changes

@@
 library(scico)
+library(colorspace)
 library(scales)

### 2021-04-10 R/models_clphy.R
Add new law models

@@ -64,6 +64,28 @@ f_clphy_total <- function(dat) {
   return(model)
 }
 
+f_clphy_total_new <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(v2x_clphy_lead1 ~ barriers_total_new + barriers_total_new_lag1 +
+         v2x_clphy +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = gaussian(),
+    prior = clphy_settings$priors_vague,
+    control = list(adapt_delta = 0.9),
+    data = dat,
+    chains = clphy_settings$chains, iter = clphy_settings$iter,
+    warmup = clphy_settings$warmup, seed = clphy_settings$seed)
+
+  return(model)
+}
+
 f_clphy_advocacy <- function(dat) {
   dat <- dat %>% filter(laws)
 

### 2021-04-10 R/models_clpriv.R

@@ -64,6 +64,28 @@ f_clpriv_total <- function(dat) {
   return(model)
 }
 
+f_clpriv_total_new <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(v2x_clpriv_lead1 ~ barriers_total_new + barriers_total_new_lag1 +
+         v2x_clpriv +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = gaussian(),
+    prior = clpriv_settings$priors_vague,
+    control = list(adapt_delta = 0.9),
+    data = dat,
+    chains = clpriv_settings$chains, iter = clpriv_settings$iter,
+    warmup = clpriv_settings$warmup, seed = clpriv_settings$seed)
+
+  return(model)
+}
+
 f_clpriv_advocacy <- function(dat) {
   dat <- dat %>% filter(laws)
 

### 2021-04-10 R/models_lhr.R
Add latent human rights models

@@ -1,0 +1,310 @@
+# Settings ----------------------------------------------------------------
+
+lhr_setup <- function() {
+  # Settings
+  CHAINS <- 4
+  ITER <- 2000
+  WARMUP <- 1000
+  BAYES_SEED <- 4045  # From random.org
+
+  # Priors
+  priors_vague <- c(set_prior("normal(0, 10)", class = "Intercept"),
+                    set_prior("normal(0, 3)", class = "b"),
+                    set_prior("cauchy(0, 1)", class = "sd"))
+
+  return(list(chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
+              priors_vague = priors_vague))
+}
+
+lhr_settings <- lhr_setup()
+
+
+# Regular models ----------------------------------------------------------
+
+f_lhr_baseline <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(latent_hr_mean_lead1 ~ latent_hr_mean +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = gaussian(),
+    prior = lhr_settings$priors_vague,
+    control = list(adapt_delta = 0.9),
+    data = dat,
+    chains = lhr_settings$chains, iter = lhr_settings$iter,
+    warmup = lhr_settings$warmup, seed = lhr_settings$seed)
+
+  return(model)
+}
+
+f_lhr_total <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
+    bf(latent_hr_mean_lead1 ~ barriers_total + barriers_total_lag1 +
+         latent_hr_mean +
+         v2x_polyarchy +
+         gdpcap_log +
+         un_trade_pct_gdp +
+         armed_conflict +
+         (1 | gwcode)
+    ),
+    family = gaussian(),
+    prior = lhr_settings$priors_vague,
+    control = list(adapt_delta = 0.9),
+    data = dat,
+    chains = lhr_settings$chains, iter = lhr_settings$iter,
+    warmup = lhr_settings$warmup, seed = lhr_settings$seed)
+
+  return(model)
+}
+
+f_lhr_total_new <- function(dat) {
+  dat <- dat %>% filter(laws)
+
+  model <- brm(
[…]

### 2021-04-10 analysis/03_environment-repression.Rmd
Update analysis notebook to include new laws + latent human rights

@@
   model_df <- tar_read(model_df) %>% 
-    filter(str_detect(model, "baseline") | str_detect(model, "v2csreprss"))
+    filter(str_detect(model, "baseline") | str_detect(model, "v2csreprss")) %>% 
+    filter(!str_detect(model, "_train"))
 
@@
              m_clpriv_baseline, m_clpriv_v2csreprss, 
-             m_clpriv_baseline_rewb, m_clpriv_v2csreprss_rewb))
+             m_clpriv_baseline_rewb, m_clpriv_v2csreprss_rewb,
+             m_lhr_baseline, m_lhr_v2csreprss))
 
   # Load regression tables
-  tar_load(c(models_tbl_e2a, models_tbl_e2b, models_tbl_e2c))
+  tar_load(c(models_tbl_e2a, models_tbl_e2b, models_tbl_e2c, models_tbl_e2d))
 
@@
 ```
+
+\
+
+# E~2d~: Civil society environment and latent physical integrity rights
+
+```{r tbl-e2d}
+# Build nicer column names
+models_for_table_e2d <- models %>% 
+  filter(outcome_var == "Latent human rights") %>% 
+  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
+  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))
+
+# Make a named vector of original model names and nice names
+model_names_tbl_e2d <- models_for_table_e2d %>% 
+  pull(model_name) %>% 
+  set_names(models_for_table_e2d$model)
+
+# Rename the columns
+names(models_tbl_e2d) <- recode(names(models_tbl_e2d), !!!model_names_tbl_e2d)
+
+modelsummary(models_tbl_e2d,
+             statistic = "[{conf.low}, {conf.high}]",
+             coef_map = coef_list,
+             gof_omit = "ELPD",
+             escape = FALSE,
+             notes = list("Posterior means; 95% credible intervals in brackets"))
+```
+
+## Coefficients
+
+```{r plot-coefs-e2d}
+coef_plots <- models %>% 
+  filter(str_detect(model, "m_lhr_v2csreprss")) %>% 
+  mutate(re_fancy = case_when(
+    re == "RE" ~ "Random effects models",
+    re == "REWB" ~ "Random effects—within/between models"
+  )) %>% 
+  mutate(coef_draws = map(
+    actual_model, 
+    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
+  select(-actual_model) %>% 
+  unnest(coef_draws) %>% 
+  filter(!str_detect(.variable, "between")) %>% 
+  left_join(coefs_clean, by = c(".variable" = "coef"))
+
+coef_plots %>% 
+  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
+  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
+  geom_vline(xintercept = 0) +
+  guides(fill = FALSE, alpha = FALSE) +
+  scale_alpha_manual(values = c(1, 0.4)) +
+  labs(x = "Coefficient", y = NULL) +
+  facet_wrap(vars(re_fancy), ncol = 1, scales = "free_y") +
+  theme_ngo()
+```
+
+## Marginal effects
+
+```{r plot-mfx-e2d}
+mfx <- models %>% 
+  filter(str_detect(model, "m_lhr_v2csreprss")) %>% 
+  mutate(fx = map2(actual_model, "v2csreprss",
+                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
+  select(-actual_model) %>% 
+  unnest(fx)
+
+mfx %>% 
+  filter(model == "m_lhr_v2csreprss") %>% 
+  ggplot(aes(x = effect1__, y = estimate__)) +
+  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
+              fill = "#FF4136", color = NA) +
+  geom_line(size = 1, color = "#FF4136") +
+  labs(x = "Civil society repression\n(higher values = less repression)",
+       y = "Predicted latent human rights\n(higher values = less violence)") +
+  theme_ngo()
+```

### 2021-04-10 analysis/03_laws-repression.Rmd
Update analysis notebook to include new laws + latent human rights

@@
   # Load actual model objects
-  tar_load(c(m_pts_baseline, m_pts_total, m_pts_advocacy, m_pts_entry, m_pts_funding, 
-             m_pts_baseline_rewb, m_pts_total_rewb, m_pts_advocacy_rewb, m_pts_entry_rewb, m_pts_funding_rewb, 
-             m_clphy_baseline, m_clphy_total, m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
-             m_clphy_baseline_rewb, m_clphy_total_rewb, m_clphy_advocacy_rewb, m_clphy_entry_rewb, m_clphy_funding_rewb, 
-             m_clpriv_baseline, m_clpriv_total, m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
-             m_clpriv_baseline_rewb, m_clpriv_total_rewb, m_clpriv_advocacy_rewb, m_clpriv_entry_rewb, m_clpriv_funding_rewb))
+  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
+             m_pts_advocacy, m_pts_entry, m_pts_funding, 
+             m_pts_baseline_rewb, m_pts_total_rewb, 
+             m_pts_advocacy_rewb, m_pts_entry_rewb, m_pts_funding_rewb, 
+             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
+             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
+             m_clphy_baseline_rewb, m_clphy_total_rewb, 
+             m_clphy_advocacy_rewb, m_clphy_entry_rewb, m_clphy_funding_rewb, 
+             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new,
+             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
+             m_clpriv_baseline_rewb, m_clpriv_total_rewb, 
+             m_clpriv_advocacy_rewb, m_clpriv_entry_rewb, m_clpriv_funding_rewb,
+             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
+             m_lhr_advocacy, m_lhr_entry, m_lhr_funding))
 
@@
   tar_load(c(models_tbl_e1a_re, models_tbl_e1a_rewb, 
-             models_tbl_e1b_re, models_tbl_e1c_re))
+             models_tbl_e1b_re, models_tbl_e1c_re, models_tbl_e1d_re))
 
@@
 models <- model_df %>% 
+  filter(!str_detect(model, "train")) %>% 
   mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
@@
   "b_barriers_total_lag1", "Total legal barriers (t - 1)",
+  "b_barriers_total_new", "New legal barriers",
+  "b_barriers_total_new_lag1", "New legal barriers (t - 1)",
   "b_advocacy", "Barriers to advocacy",
@@
   "m_pts_total", "barriers_total", "Total legal barriers",
+  "m_pts_total_new", "barriers_total_new", "New legal barriers",
   "m_pts_advocacy", "advocacy", "Barriers to advocacy",
@@
   "m_clphy_total", "barriers_total", "Total legal barriers",
+  "m_clphy_total_new", "barriers_total_new", "New legal barriers",
   "m_clphy_advocacy", "advocacy", "Advocacy",
@@
   "m_clpriv_total", "barriers_total", "Total legal barriers",
+  "m_clpriv_total_new", "barriers_total_new", "New legal barriers",
   "m_clpriv_advocacy", "advocacy", "Advocacy",
@@
 ```
+
+\
+
+# E~1d~: NGO laws and latent physical integrity rights
+
+## Results table
+
+```{r tbl-e1d-re}
+models_for_table_e1d_re <- models %>% 
+  filter(outcome_var == "Latent human rights", re == "RE") %>% 
+  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))
+
+model_names_tbl_e1d_re <- models_for_table_e1d_re %>% 
+  pull(model_name) %>% 
+  set_names(models_for_table_e1d_re$model)
+
+names(models_tbl_e1d_re) <- recode(names(models_tbl_e1d_re), 
+                                   !!!model_names_tbl_e1d_re)
+
+modelsummary(models_tbl_e1d_re,
+             statistic = "[{conf.low}, {conf.high}]",
+             coef_map = coef_list,
+             gof_omit = "ELPD",
+             escape = FALSE,
+             notes = list("Posterior means; 95% credible intervals in brackets"))
+```
+
+## Coefficients
+
+```{r plot-coefs-e1d}
+coef_plots <- models %>% 
+  filter(str_detect(model, "lhr"), !str_detect(model, "baseline")) %>% 
+  mutate(re_fancy = case_when(
+    re == "RE" ~ "Random effects models",
+    re == "REWB" ~ "Random effects—within/between models"
+  )) %>% 
+  mutate(coef_draws = map(
+    actual_model, 
+    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
+  select(-actual_model) %>% 
+  unnest(coef_draws) %>% 
+  filter(!str_detect(.variable, "between")) %>% 
+  left_join(coefs_clean, by = c(".variable" = "coef"))
+
+coef_plots %>% 
+  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
+  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
+  geom_vline(xintercept = 0) +
+  guides(fill = FALSE, alpha = FALSE) +
+  scale_alpha_manual(values = c(1, 0.4)) +
+  labs(x = "Coefficient", y = NULL) +
+  facet_wrap(vars(re_fancy), ncol = 2, scales = "free_y") +
+  theme_ngo()
+```
+
+## Marginal effects
+
+```{r plot-mfx-e1d}
+plot_lhr_vars_lookup <- tribble(
+  ~model, ~plot_var, ~plot_var_nice,
+  "m_lhr_total", "barriers_total", "Total legal barriers",
+  "m_lhr_total_new", "barriers_total_new", "New legal barriers",
+  "m_lhr_advocacy", "advocacy", "Advocacy",
+  "m_lhr_entry", "entry", "Entry",
+  "m_lhr_funding", "funding", "Funding"
+) %>% 
+  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
+
+mfx <- models %>% 
+  filter(str_detect(model, "lhr"), !str_detect(model, "rewb|baseline")) %>% 
+  left_join(plot_lhr_vars_lookup, by = "model") %>% 
+  mutate(fx = map2(actual_model, plot_var, 
+                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
+  select(-actual_model) %>% 
+  unnest(fx)
+
+mfx %>% 
+  mutate(x_rounded = floor(effect1__)) %>% 
+  group_by(x_rounded, plot_var_nice) %>% 
+  slice(1) %>% 
+  ungroup() %>% 
+  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
+  geom_line(size = 0.5, color = "grey90") +
+  geom_pointrange(aes(ymin = lower__, ymax = upper__),
+                  fatten = 1) +
+  scale_x_continuous(breaks = 0:9) +
+  scale_color_viridis_d(option = "plasma", end = 0.8) +
+  guides(color = FALSE) +
+  labs(x = "Count of legal barriers",
+       y = "Predicted latent human rights value\n(higher values = better human rights)") +
+  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
+  theme_ngo() +
+  theme(panel.grid.major.x = element_blank())
+```

### 2021-04-10 analysis/03_model-details.Rmd
Update analysis notebook to include new laws + latent human rights

@@
   # So we do it this manual way
-  tar_load(c(m_pts_baseline, m_pts_total, m_pts_advocacy, 
-             m_pts_entry, m_pts_funding, m_pts_v2csreprss, 
-             m_pts_baseline_rewb, m_pts_total_rewb, m_pts_advocacy_rewb, 
-             m_pts_entry_rewb, m_pts_funding_rewb, m_pts_v2csreprss_rewb, 
-             m_clphy_baseline, m_clphy_total, m_clphy_advocacy, 
-             m_clphy_entry, m_clphy_funding, m_clphy_v2csreprss, 
-             m_clphy_baseline_rewb, m_clphy_total_rewb, m_clphy_advocacy_rewb, 
-             m_clphy_entry_rewb, m_clphy_funding_rewb, m_clphy_v2csreprss_rewb, 
-             m_clpriv_baseline, m_clpriv_total, m_clpriv_advocacy, 
-             m_clpriv_entry, m_clpriv_funding, m_clpriv_v2csreprss, 
-             m_clpriv_baseline_rewb, m_clpriv_total_rewb, m_clpriv_advocacy_rewb, 
-             m_clpriv_entry_rewb, m_clpriv_funding_rewb, m_clpriv_v2csreprss_rewb))
+  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
+             m_pts_advocacy, m_pts_entry, m_pts_funding, 
+             m_pts_v2csreprss, 
+             m_pts_baseline_rewb, m_pts_total_rewb, 
+             m_pts_advocacy_rewb, m_pts_entry_rewb, m_pts_funding_rewb, 
+             m_pts_v2csreprss_rewb, 
+             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
+             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
+             m_clphy_v2csreprss, 
+             m_clphy_baseline_rewb, m_clphy_total_rewb, 
+             m_clphy_advocacy_rewb, m_clphy_entry_rewb, m_clphy_funding_rewb, 
+             m_clphy_v2csreprss_rewb, 
+             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new, 
+             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
+             m_clpriv_v2csreprss, 
+             m_clpriv_baseline_rewb, m_clpriv_total_rewb, 
+             m_clpriv_advocacy_rewb, m_clpriv_entry_rewb, m_clpriv_funding_rewb, 
+             m_clpriv_v2csreprss_rewb, 
+             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
+             m_lhr_advocacy, m_lhr_entry, m_lhr_funding, 
+             m_lhr_v2csreprss, 
+             m_pts_baseline_train, m_pts_total_train, 
+             m_pts_advocacy_train, m_pts_entry_train, m_pts_funding_train, 
+             m_pts_v2csreprss_train, 
+             m_pts_baseline_rewb_train, m_pts_total_rewb_train, 
+             m_pts_advocacy_rewb_train, m_pts_entry_rewb_train, m_pts_funding_rewb_train, 
+             m_pts_v2csreprss_rewb_train, 
+             m_clphy_baseline_train, m_clphy_total_train, 
+             m_clphy_advocacy_train, m_clphy_entry_train, m_clphy_funding_train, 
+             m_clphy_v2csreprss_train, 
+             m_clphy_baseline_rewb_train, m_clphy_total_rewb_train, 
+             m_clphy_advocacy_rewb_train, m_clphy_entry_rewb_train, m_clphy_funding_rewb_train, 
+             m_clphy_v2csreprss_rewb_train, 
+             m_clpriv_baseline_train, m_clpriv_total_train, 
+             m_clpriv_advocacy_train, m_clpriv_entry_train, m_clpriv_funding_train, 
+             m_clpriv_v2csreprss_train, 
+             m_clpriv_baseline_rewb_train, m_clpriv_total_rewb_train, 
+             m_clpriv_advocacy_rewb_train, m_clpriv_entry_rewb_train, m_clpriv_funding_rewb_train, 
+             m_clpriv_v2csreprss_rewb_train))
 })
 ```
+
+```{r set-computer-details}
+computer <- "Work"
+
+if (computer == "Work") {
+  computer_details <- "2019 MacBook Pro with 16 cores and 32 GB of RAM, using Stan through brms through cmdstanr"
+} else {
+  computer_details <- "2016 MacBook Pro with 4 cores and 16 GB of RAM, using Stan through brms through cmdstanr"
+}
+```
+
+We ran these models on a `r computer_details`.
+
+\
 
@@
 ## Models for E~1~ (civil society laws)
+
+### Full data
 
@@
 model_time_e1 <- models_e1 %>% 
+  filter(training == "Full data") %>% 
+  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
+         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
+  select(-actual_model) %>% 
+  unnest(duration) %>% 
+  mutate(model = glue("<code>{model}</code>")) %>% 
+  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
+           `Random effects` = re, `Family` = family) %>% 
+  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
+  ungroup() %>% 
+  arrange(Outcome, `Main predictor`, `Random effects`)
+
+total_row_e1 <- tibble(Outcome = "Total", 
+                       `Total time (i.e. longest chain)` = 
+                         as.duration(sum(model_time_e1$`Total time (i.e. longest chain)`)))
+
+model_time_e1 <- model_time_e1 %>% 
+  bind_rows(total_row_e1)
+
+model_time_e1 %>% 
+  select(-Outcome) %>% 
+  kbl(escape = FALSE) %>% 
+  pack_rows(index = table(fct_inorder(model_time_e1$Outcome))) %>% 
+  kable_styling()
+```
+
+### Training data
+
+```{r running-time-e1-training}
+model_time_e1 <- models_e1 %>% 
+  filter(training == "Training") %>% 
   mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
@@
 
+### Full data
+
 ```{r running-time-e2}
@@
 model_time_e2 <- models_e2 %>% 
+  filter(training == "Full data") %>% 
+  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
+         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
+  select(-actual_model) %>% 
+  unnest(duration) %>% 
+  mutate(model = glue("<code>{model}</code>")) %>% 
+  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
+           `Random effects` = re, `Family` = family) %>% 
+  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
+  ungroup() %>% 
+  arrange(Outcome, `Main predictor`, `Random effects`)
+
+total_row_e2 <- tibble(Outcome = "Total", 
+                       `Total time (i.e. longest chain)` = 
+                         as.duration(sum(model_time_e2$`Total time (i.e. longest chain)`)))
+
+model_time_e2 <- model_time_e2 %>% 
+  bind_rows(total_row_e2)
+
+model_time_e2 %>% 
+  select(-Outcome) %>% 
+  kbl(escape = FALSE) %>% 
+  pack_rows(index = table(fct_inorder(model_time_e2$Outcome))) %>% 
+  kable_styling()
+```
+
+### Training data
+
+```{r running-time-e2-training}
+model_time_e2 <- models_e2 %>% 
+  filter(training == "Training") %>% 
   mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
@@
 - `R/models_clpriv.R` (for V-Dem private civil liberties-based models)
+- `R/models_lhr.R` (for latent human rights-based models)
 
@@
 ```
+
+#### `R/models_lhr.R`
+
+```{r, code=xfun::read_utf8(here::here("R", "models_lhr.R")), eval=FALSE, class.source="fold-hide"}
+```

### 2021-04-10 analysis/03_modeling-choices.Rmd
Update analysis notebook to include new laws + latent human rights

@@
 Just because the bulk of the relative variation is at at the country level doesn't mean that there isn't significant variability within countries over time.
-Thus, we should really used a multilevel model because the country-year structure matters *a lot* when explaining human rights abuses
+However, the lagged DV seems to soak up pretty much all year-based variability, so we should really use a multilevel model because the country structure matters *a lot* when explaining human rights abuses.
+There aren't really too many gains in efficiency or predictive power when including `(1 | year)` though.
 

### 2021-04-10 R/models_details.R

@@ -4,6 +4,7 @@ create_model_df <- function() {
     # Models for the political terror score (PTS)
     "m_pts_baseline", "Political terror", "Baseline",
     "m_pts_total", "Political terror", "Total legal barriers",
+    "m_pts_total_new", "Political terror", "New legal barriers",
     "m_pts_advocacy", "Political terror", "Barriers to advocacy",
     "m_pts_entry", "Political terror", "Barriers to entry",
     "m_pts_funding", "Political terror", "Barriers to funding",
@@ -19,6 +20,7 @@ create_model_df <- function() {
     # Models for physical violence (v2x_clphy)
     "m_clphy_baseline", "Physical violence", "Baseline",
     "m_clphy_total", "Physical violence", "Total legal barriers",
+    "m_clphy_total_new", "Physical violence", "New legal barriers",
     "m_clphy_advocacy", "Physical violence", "Barriers to advocacy",
     "m_clphy_entry", "Physical violence", "Barriers to entry",
     "m_clphy_funding", "Physical violence", "Barriers to funding",
@@ -34,6 +36,7 @@ create_model_df <- function() {
     # Models for private civil liberties (v2x_clpriv)
     "m_clpriv_baseline", "Private civil liberties", "Baseline",
     "m_clpriv_total", "Private civil liberties", "Total legal barriers",
+    "m_clpriv_total_new", "Private civil liberties", "New legal barriers",
     "m_clpriv_advocacy", "Private civil liberties", "Barriers to advocacy",
     "m_clpriv_entry", "Private civil liberties", "Barriers to entry",
     "m_clpriv_funding", "Private civil liberties", "Barriers to funding",
@@ -44,10 +47,65 @@ create_model_df <- function() {
     "m_clpriv_advocacy_rewb", "Private civil liberties", "Barriers to advocacy",
     "m_clpriv_entry_rewb", "Private civil liberties", "Barriers to entry",
     "m_clpriv_funding_rewb", "Private civil liberties", "Barriers to funding",
-    "m_clpriv_v2csreprss_rewb", "Private civil liberties", "Civil society repression"
+    "m_clpriv_v2csreprss_rewb", "Private civil liberties", "Civil society repression",
+
+    # Models for latent human rights (latent_hr_mean)
[…]

### 2021-04-10 R/models_clphy.R
Pass options to workers for all models

@@ -1,6 +1,8 @@
 # Settings ----------------------------------------------------------------
 
 clphy_setup <- function() {
+  options(worker_options)
+
   # Settings
   CHAINS <- 4
   ITER <- 2000
@@ -16,12 +18,12 @@ clphy_setup <- function() {
               priors_vague = priors_vague))
 }
 
-clphy_settings <- clphy_setup()
-
 
 # Regular models ----------------------------------------------------------
 
 f_clphy_baseline <- function(dat) {
+  clphy_settings <- clphy_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -43,6 +45,8 @@ f_clphy_baseline <- function(dat) {
 }
 
 f_clphy_total <- function(dat) {
+  clphy_settings <- clphy_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -65,6 +69,8 @@ f_clphy_total <- function(dat) {
 }
 
 f_clphy_total_new <- function(dat) {
+  clphy_settings <- clphy_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -87,6 +93,8 @@ f_clphy_total_new <- function(dat) {
 }
 
 f_clphy_advocacy <- function(dat) {
+  clphy_settings <- clphy_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -109,6 +117,8 @@ f_clphy_advocacy <- function(dat) {
 }
 
 f_clphy_entry <- function(dat) {
+  clphy_settings <- clphy_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -131,6 +141,8 @@ f_clphy_entry <- function(dat) {
 }
 
 f_clphy_funding <- function(dat) {
+  clphy_settings <- clphy_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -153,6 +165,8 @@ f_clphy_funding <- function(dat) {
 }
 
 f_clphy_v2csreprss <- function(dat) {
+  clphy_settings <- clphy_setup()
+
   model <- brm(
     bf(v2x_clphy_lead1 ~ v2csreprss + v2csreprss_lag1 +
          v2x_clphy +
@@ -176,6 +190,8 @@ f_clphy_v2csreprss <- function(dat) {
[…]

### 2021-04-10 R/models_clpriv.R

@@ -1,6 +1,8 @@
 # Settings ----------------------------------------------------------------
 
 clpriv_setup <- function() {
+  options(worker_options)
+
   # Settings
   CHAINS <- 4
   ITER <- 2000
@@ -16,12 +18,12 @@ clpriv_setup <- function() {
               priors_vague = priors_vague))
 }
 
-clpriv_settings <- clpriv_setup()
-
 
 # Regular models ----------------------------------------------------------
 
 f_clpriv_baseline <- function(dat) {
+  clpriv_settings <- clpriv_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -43,6 +45,8 @@ f_clpriv_baseline <- function(dat) {
 }
 
 f_clpriv_total <- function(dat) {
+  clpriv_settings <- clpriv_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -65,6 +69,8 @@ f_clpriv_total <- function(dat) {
 }
 
 f_clpriv_total_new <- function(dat) {
+  clpriv_settings <- clpriv_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -87,6 +93,8 @@ f_clpriv_total_new <- function(dat) {
 }
 
 f_clpriv_advocacy <- function(dat) {
+  clpriv_settings <- clpriv_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -109,6 +117,8 @@ f_clpriv_advocacy <- function(dat) {
 }
 
 f_clpriv_entry <- function(dat) {
+  clpriv_settings <- clpriv_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -131,6 +141,8 @@ f_clpriv_entry <- function(dat) {
 }
 
 f_clpriv_funding <- function(dat) {
+  clpriv_settings <- clpriv_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -153,6 +165,8 @@ f_clpriv_funding <- function(dat) {
 }
 
 f_clpriv_v2csreprss <- function(dat) {
+  clpriv_settings <- clpriv_setup()
+
   model <- brm(
     bf(v2x_clpriv_lead1 ~ v2csreprss + v2csreprss_lag1 +
          v2x_clpriv +
[…]

### 2021-04-10 R/models_lhr.R

@@ -1,6 +1,8 @@
 # Settings ----------------------------------------------------------------
 
 lhr_setup <- function() {
+  options(worker_options)
+
   # Settings
   CHAINS <- 4
   ITER <- 2000
@@ -16,12 +18,12 @@ lhr_setup <- function() {
               priors_vague = priors_vague))
 }
 
-lhr_settings <- lhr_setup()
-
 
 # Regular models ----------------------------------------------------------
 
 f_lhr_baseline <- function(dat) {
+  lhr_settings <- lhr_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -43,6 +45,8 @@ f_lhr_baseline <- function(dat) {
 }
 
 f_lhr_total <- function(dat) {
+  lhr_settings <- lhr_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -65,6 +69,8 @@ f_lhr_total <- function(dat) {
 }
 
 f_lhr_total_new <- function(dat) {
+  lhr_settings <- lhr_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -87,6 +93,8 @@ f_lhr_total_new <- function(dat) {
 }
 
 f_lhr_advocacy <- function(dat) {
+  lhr_settings <- lhr_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -109,6 +117,8 @@ f_lhr_advocacy <- function(dat) {
 }
 
 f_lhr_entry <- function(dat) {
+  lhr_settings <- lhr_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -131,6 +141,8 @@ f_lhr_entry <- function(dat) {
 }
 
 f_lhr_funding <- function(dat) {
+  lhr_settings <- lhr_setup()
+
   dat <- dat %>% filter(laws)
 
   model <- brm(
@@ -153,6 +165,8 @@ f_lhr_funding <- function(dat) {
 }
 
 f_lhr_v2csreprss <- function(dat) {
+  lhr_settings <- lhr_setup()
+
   model <- brm(
     bf(latent_hr_mean_lead1 ~ v2csreprss + v2csreprss_lag1 +
          latent_hr_mean +
@@ -176,6 +190,8 @@ f_lhr_v2csreprss <- function(dat) {
[…]

### 2021-04-10 R/models_pts.R

@@ -40,8 +40,7 @@ f_pts_baseline <- function(dat) {
     prior = pts_settings$priors_vague,
     data = dat,
     chains = pts_settings$chains, iter = pts_settings$iter,
-    warmup = pts_settings$warmup, seed = pts_settings$seed,
-    threads = threading(getOption("n.threads", default = 1)))
+    warmup = pts_settings$warmup, seed = pts_settings$seed)
 
   return(model)
 }
@@ -64,8 +63,7 @@ f_pts_total <- function(dat) {
     prior = pts_settings$priors_vague,
     data = dat,
     chains = pts_settings$chains, iter = pts_settings$iter,
-    warmup = pts_settings$warmup, seed = pts_settings$seed,
-    threads = threading(getOption("n.threads", default = 1)))
+    warmup = pts_settings$warmup, seed = pts_settings$seed)
 
   return(model)
 }
@@ -88,8 +86,7 @@ f_pts_total_new <- function(dat) {
     prior = pts_settings$priors_vague,
     data = dat,
     chains = pts_settings$chains, iter = pts_settings$iter,
-    warmup = pts_settings$warmup, seed = pts_settings$seed,
-    threads = threading(getOption("n.threads", default = 1)))
+    warmup = pts_settings$warmup, seed = pts_settings$seed)
 
   return(model)
 }
@@ -112,8 +109,7 @@ f_pts_advocacy <- function(dat) {
     prior = pts_settings$priors_vague,
     data = dat,
     chains = pts_settings$chains, iter = pts_settings$iter,
-    warmup = pts_settings$warmup, seed = pts_settings$seed,
-    threads = threading(getOption("n.threads", default = 1)))
+    warmup = pts_settings$warmup, seed = pts_settings$seed)
 
   return(model)
 }

### 2021-04-10 analysis/04_predictions.Rmd
Do prediction stuff with latent human rights

@@
              m_clpriv_total_train, m_clpriv_advocacy_train, 
-             m_clpriv_entry_train, m_clpriv_funding_train))
+             m_clpriv_entry_train, m_clpriv_funding_train,
+             m_lhr_baseline_train, m_lhr_v2csreprss_train,
+             m_lhr_total_train, m_lhr_advocacy_train, 
+             m_lhr_entry_train, m_lhr_funding_train))
 })
@@
 
+# E~1d~: NGO laws and latent human rights
+
+```{r e1d-predictions, warning=FALSE}
+seed_lhr_prediction <- 3207  # From random.org
+
+set.seed(seed_lhr_prediction)
+pred_lhr_baseline <- predict(m_lhr_baseline_train, 
+                             newdata = select(canary_testing_lagged, -latent_hr_mean_lead1),
+                             allow_new_levels = TRUE)
+
+set.seed(seed_lhr_prediction)
+pred_lhr_total <- predict(m_lhr_total_train, 
+                          newdata = select(canary_testing_lagged, -latent_hr_mean_lead1),
+                          allow_new_levels = TRUE)
+
+set.seed(seed_lhr_prediction)
+pred_lhr_advocacy <- predict(m_lhr_advocacy_train, 
+                             newdata = select(canary_testing_lagged, -latent_hr_mean_lead1),
+                             allow_new_levels = TRUE)
+
+set.seed(seed_lhr_prediction)
+pred_lhr_entry <- predict(m_lhr_entry_train, 
+                          newdata = select(canary_testing_lagged, -latent_hr_mean_lead1),
+                          allow_new_levels = TRUE)
+
+set.seed(seed_lhr_prediction)
+pred_lhr_funding <- predict(m_lhr_funding_train, 
+                            newdata = select(canary_testing_lagged, -latent_hr_mean_lead1),
+                            allow_new_levels = TRUE)
+
+pred_lhr_baseline_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, latent_hr_mean_lead1) %>% 
+  bind_cols(as_tibble(pred_lhr_baseline)) %>% 
+  filter(!is.na(latent_hr_mean_lead1))
+
+pred_lhr_total_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, latent_hr_mean_lead1) %>% 
+  bind_cols(as_tibble(pred_lhr_total)) %>% 
+  filter(!is.na(latent_hr_mean_lead1))
+
+pred_lhr_advocacy_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, latent_hr_mean_lead1) %>% 
+  bind_cols(as_tibble(pred_lhr_advocacy)) %>% 
+  filter(!is.na(latent_hr_mean_lead1))
+
+pred_lhr_entry_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, latent_hr_mean_lead1) %>% 
+  bind_cols(as_tibble(pred_lhr_entry)) %>% 
+  filter(!is.na(latent_hr_mean_lead1))
+
+pred_lhr_funding_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, latent_hr_mean_lead1) %>% 
+  bind_cols(as_tibble(pred_lhr_funding)) %>% 
+  filter(!is.na(latent_hr_mean_lead1))
+```
+
+## Improvement from baseline models
+
+```{r e1d-pred-plots, warning=FALSE}
+plot_baseline <- ggplot(pred_lhr_baseline_test, 
+                        aes(x = latent_hr_mean_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Baseline",
+       x = "Actual latent human rights value (t + 1)",
+       y = "Predicted latent human rights value (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_total <- ggplot(pred_lhr_total_test, 
+                     aes(x = latent_hr_mean_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Total legal barriers",
+       x = "Actual latent human rights value (t + 1)",
+       y = "Predicted latent human rights value (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_advocacy <- ggplot(pred_lhr_advocacy_test, 
+                        aes(x = latent_hr_mean_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Barriers to advocacy",
+       x = "Actual latent human rights value (t + 1)",
+       y = "Predicted latent human rights value (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_entry <- ggplot(pred_lhr_entry_test, 
+                     aes(x = latent_hr_mean_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Barriers to entry",
+       x = "Actual latent human rights value (t + 1)",
+       y = "Predicted latent human rights value (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_funding <- ggplot(pred_lhr_funding_test, 
+                       aes(x = latent_hr_mean_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Barriers to funding",
+       x = "Actual latent human rights value (t + 1)",
+       y = "Predicted latent human rights value (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+(plot_baseline | plot_total) / (plot_advocacy | plot_entry | plot_funding)
+```
+
+```{r e1d-metrics}
+lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
+
+bind_rows(lotsa_metrics(pred_lhr_baseline_test, 
+                        truth = latent_hr_mean_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Baseline"),
+          lotsa_metrics(pred_lhr_total_test, 
+                        truth = latent_hr_mean_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Total legal barriers"),
+          lotsa_metrics(pred_lhr_advocacy_test, 
+                        truth = latent_hr_mean_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Barriers to advocacy"),
+          lotsa_metrics(pred_lhr_entry_test, 
+                        truth = latent_hr_mean_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Barriers to entry"),
+          lotsa_metrics(pred_lhr_funding_test, 
+                        truth = latent_hr_mean_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Barriers to funding")) %>% 
+  select(Model, .metric, .estimate) %>% 
+  pivot_wider(names_from = ".metric", values_from = ".estimate")
+```
+
+## Most improved countries
+
+### Total legal barriers
+
+```{r e1d-most-improved-total}
+most_improved_lhr_total <- bind_cols(
+  pred_lhr_baseline_test %>% 
+    mutate(error_baseline = Estimate - latent_hr_mean_lead1) %>% 
+    select(country, gwcode, year, latent_hr_mean_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_lhr_total_test %>% 
+    mutate(error_total = Estimate - latent_hr_mean_lead1) %>% 
+    select(estimate_total = Estimate, error_total)
+) %>% 
+  mutate(improved = error_total < 0 & abs(error_total) < abs(error_baseline)) %>% 
+  mutate(diff = error_total - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_lhr_total)
+
+most_improved_lhr_total %>% 
+  select(Country = country, Year = year, 
+         `Actual latent human rights value (t + 1)` = latent_hr_mean_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_total,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+### Barriers to advocacy
+
+```{r e1d-most-improved-advocacy}
+most_improved_lhr_advocacy <- bind_cols(
+  pred_lhr_baseline_test %>% 
+    mutate(error_baseline = Estimate - latent_hr_mean_lead1) %>% 
+    select(country, gwcode, year, latent_hr_mean_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_lhr_advocacy_test %>% 
+    mutate(error_advocacy = Estimate - latent_hr_mean_lead1) %>% 
+    select(estimate_advocacy = Estimate, error_advocacy)
+) %>% 
+  mutate(improved = error_advocacy < 0 & abs(error_advocacy) < abs(error_baseline)) %>% 
+  mutate(diff = error_advocacy - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_lhr_advocacy)
+
+most_improved_lhr_advocacy %>% 
+  select(Country = country, Year = year, 
+         `Actual latent human rights value (t + 1)` = latent_hr_mean_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_advocacy,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+### Barriers to entry
+
+```{r e1d-most-improved-entry}
+most_improved_lhr_entry <- bind_cols(
+  pred_lhr_baseline_test %>% 
+    mutate(error_baseline = Estimate - latent_hr_mean_lead1) %>% 
+    select(country, gwcode, year, latent_hr_mean_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_lhr_entry_test %>% 
+    mutate(error_entry = Estimate - latent_hr_mean_lead1) %>% 
+    select(estimate_entry = Estimate, error_entry)
+) %>% 
+  mutate(improved = error_entry < 0 & abs(error_entry) < abs(error_baseline)) %>% 
+  mutate(diff = error_entry - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_lhr_entry)
+
+most_improved_lhr_entry %>% 
+  select(Country = country, Year = year, 
+         `Actual latent human rights value (t + 1)` = latent_hr_mean_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_entry,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+### Barriers to funding
+
+```{r e1d-most-improved-funding}
+most_improved_lhr_funding <- bind_cols(
+  pred_lhr_baseline_test %>% 
+    mutate(error_baseline = Estimate - latent_hr_mean_lead1) %>% 
+    select(country, gwcode, year, latent_hr_mean_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_lhr_funding_test %>% 
+    mutate(error_funding = Estimate - latent_hr_mean_lead1) %>% 
+    select(estimate_funding = Estimate, error_funding)
+) %>% 
+  mutate(improved = error_funding < 0 & abs(error_funding) < abs(error_baseline)) %>% 
+  mutate(diff = error_funding - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_lhr_funding)
+
+most_improved_lhr_funding %>% 
+  select(Country = country, Year = year, 
+         `Actual latent human rights value (t + 1)` = latent_hr_mean_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_funding,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```
+
+\
+
 ---
@@
 ```
+
+\
+
+# E~2d~: Civil society environment and latent human rights
+
+```{r e2d-predictions, warning=FALSE}
+seed_lhr_prediction <- 3207  # From random.org
+
+set.seed(seed_lhr_prediction)
+pred_lhr_baseline <- predict(m_lhr_baseline_train, 
+                                newdata = select(canary_testing_lagged, -latent_hr_mean_lead1),
+                                allow_new_levels = TRUE)
+
+set.seed(seed_lhr_prediction)
+pred_lhr_v2csreprss <- predict(m_lhr_v2csreprss_train, 
+                                  newdata = select(canary_testing_lagged, -latent_hr_mean_lead1),
+                                  allow_new_levels = TRUE)
+
+pred_lhr_baseline_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, latent_hr_mean_lead1) %>% 
+  bind_cols(as_tibble(pred_lhr_baseline)) %>% 
+  filter(!is.na(latent_hr_mean_lead1))
+
+pred_lhr_v2csreprss_test <- canary_testing_lagged %>% 
+  select(country, gwcode, year, latent_hr_mean_lead1) %>% 
+  bind_cols(as_tibble(pred_lhr_v2csreprss)) %>% 
+  filter(!is.na(latent_hr_mean_lead1))
+```
+
+## Improvement from baseline models
+
+```{r e2d-pred-plots, warning=FALSE}
+plot_baseline <- ggplot(pred_lhr_baseline_test, 
+                        aes(x = latent_hr_mean_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Baseline",
+       x = "Actual latent human rights value (t + 1)",
+       y = "Predicted latent human rights value (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_v2csreprss <- ggplot(pred_lhr_v2csreprss_test, 
+                          aes(x = latent_hr_mean_lead1, y = Estimate)) +
+  geom_abline(lty = 2) +
+  geom_point(alpha = 0.5) +
+  labs(title = "Added predictor",
+       x = "Actual latent human rights value (t + 1)",
+       y = "Predicted latent human rights value (t + 1)") +
+  coord_equal() +
+  theme_ngo()
+
+plot_baseline | plot_v2csreprss
+```
+
+```{r e2d-metrics}
+lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
+
+bind_rows(lotsa_metrics(pred_lhr_baseline_test, 
+                        truth = latent_hr_mean_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Baseline"),
+          lotsa_metrics(pred_lhr_v2csreprss_test, 
+                        truth = latent_hr_mean_lead1, 
+                        estimate = Estimate) %>% 
+            mutate(Model = "Added predictor")) %>% 
+  select(Model, .metric, .estimate) %>% 
+  pivot_wider(names_from = ".metric", values_from = ".estimate")
+```
+
+## Most improved countries
+
+```{r e2d-most-improved}
+most_improved_lhr <- bind_cols(
+  pred_lhr_baseline_test %>% 
+    mutate(error_baseline = Estimate - latent_hr_mean_lead1) %>% 
+    select(country, gwcode, year, latent_hr_mean_lead1, 
+           estimate_baseline = Estimate, error_baseline),
+  pred_lhr_v2csreprss_test %>% 
+    mutate(error_v2csreprss = Estimate - latent_hr_mean_lead1) %>% 
+    select(estimate_v2csreprss = Estimate, error_v2csreprss)
+) %>% 
+  # mutate(across(starts_with("error"), ~round(., 4))) %>% 
+  mutate(improved = error_v2csreprss < 0 & abs(error_v2csreprss) < abs(error_baseline)) %>% 
+  mutate(diff = error_v2csreprss - error_baseline) %>% 
+  mutate(abs_diff = abs(diff)) %>% 
+  filter(improved) %>% 
+  arrange(desc(abs_diff))
+
+nrow(most_improved_lhr)
+
+most_improved_lhr %>% 
+  select(Country = country, Year = year, 
+         `Actual latent human rights value (t + 1)` = latent_hr_mean_lead1,
+         `Predicted (baseline)` = estimate_baseline,
+         `Predicted (CS repression)` = estimate_v2csreprss,
+         `|CS repression − baseline|` = abs_diff) %>% 
+  head(5) %>% 
+  kbl(digits = 3, align = "lccccc") %>% 
+  kable_styling()
+```

### 2021-04-10 _targets.R

@@ -254,6 +254,14 @@ list(
   tar_target(m_lhr_funding, f_lhr_funding(panel_lagged)),
   tar_target(m_lhr_v2csreprss, f_lhr_v2csreprss(panel_lagged)),
 
+  tar_target(m_lhr_baseline_train, f_lhr_baseline(panel_training_lagged)),
+  tar_target(m_lhr_total_train, f_lhr_total(panel_training_lagged)),
+  tar_target(m_lhr_total_new_train, f_lhr_total_new(panel_training_lagged)),
+  tar_target(m_lhr_advocacy_train, f_lhr_advocacy(panel_training_lagged)),
+  tar_target(m_lhr_entry_train, f_lhr_entry(panel_training_lagged)),
+  tar_target(m_lhr_funding_train, f_lhr_funding(panel_training_lagged)),
+  tar_target(m_lhr_v2csreprss_train, f_lhr_v2csreprss(panel_training_lagged)),
+
   # Big dataframe of model names for full models
   tar_target(model_df, create_model_df()),
 

### 2021-04-11 analysis/index.Rmd
Post-ISA edits and additions

@@
 
-Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions.
-This new wave of attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
+Many countries across the globe use legal restrictions to crack down and limit civil society.
+These attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
 This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
-In this paper, we ask: do crackdowns on NGOs predict broader human rights repression?
+In this paper, we explore if crackdowns on NGOs predict broader human rights repression.
 We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
@@
 Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, physical violence, and violations of private civil liberties.
-This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deteriorations in space for civil society.
+This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deterioration in space for civil society.

### 2021-04-11 manuscript/manuscript.Rmd
Post-ISA edits and additions

@@
   url: https://www.andrewheiss.com/
-date: "April 3, 2021"
+date: "April 10, 2021"
 published: This is an early draft of a working paper.
@@
 abstract: >-
-  Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions.
-This new wave of attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
+  Many countries across the globe use legal restrictions to crack down and limit civil society.
+These attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
 This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
-In this paper, we ask: do crackdowns on NGOs predict broader human rights repression?
+In this paper, we explore if crackdowns on NGOs predict broader human rights repression.
 We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
@@
 Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, physical violence, and violations of private civil liberties.
-This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deteriorations in space for civil society.
+This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deterioration in space for civil society.
 keywords: "civil society restrictions, human rights, political terror, civil liberties"
@@
   fig.width = 7, fig.asp = 0.618,
-  fig.align = conditional_align, out.width = "85%",
+  fig.align = conditional_align, out.width = "100%",
   fig.path = "output/figures/",
@@
   # Model tables
-  tar_load(c(models_paper_pts, models_paper_clphy, models_paper_clpriv))
+  tar_load(c(models_paper_pts, models_paper_clphy, 
+             models_paper_clpriv, models_paper_lhr))
 
@@
   # Load marginal effects
-  tar_load(c(mfx_e1a_pts, mfx_e1b_clphy, mfx_e1c_clpriv,
-             mfx_e2a_pts, mfx_e2b_clphy, mfx_e2c_clpriv))
+  tar_load(c(mfx_e1a_pts, mfx_e1b_clphy, mfx_e1c_clpriv, mfx_e1d_lhr,
+             mfx_e2a_pts, mfx_e2b_clphy, mfx_e2c_clpriv, mfx_e2d_lhr))
 })
@@
 (ref:vdem) @vdem-v10
+
+(ref:lhr) @FarissKenwickReuning:2020
 
@@
   "Private civil liberties index", NA, "0–1; higher values indicate greater respect for civil liberties", "(ref:vdem); v2x_clpriv",
+  "Latent human rights values", NA, "≈ -3–5; higher values indicate greater respect for human rights", "(ref:lhr)",
   "Total legal barriers", "De jure laws", "Count of all anti-NGO legal barriers", "(ref:chaudhry)",
@@
     kbl(caption = tbl_var_summary_caption,
-        booktabs = TRUE, linesep = "") %>% 
-    pack_rows(index = c("Outcomes" = 3, "Predictors" = 5)) %>% 
+        booktabs = TRUE, linesep = "\\addlinespace") %>% 
+    pack_rows(index = c("Outcomes" = 4, "Predictors" = 5),
+              indent = FALSE) %>% 
     kable_styling(font_size = ifelse(is_latex, 8.5, NA)) %>% 
-    row_spec(0, bold = TRUE) %>% 
-    column_spec(1, width = "0.14\\\\textwidth") %>% 
-    column_spec(2, width = "0.14\\\\textwidth") %>% 
-    column_spec(3, width = "0.5\\\\textwidth") %>% 
+    column_spec(1, width = "0.16\\\\textwidth") %>% 
+    column_spec(2, width = "0.1\\\\textwidth") %>% 
+    column_spec(3, width = "0.4\\\\textwidth") %>% 
     column_spec(4, width = "0.2\\\\textwidth")
@@
     insert_row("Outcomes", "", "", "", after = 1) %>% 
-    insert_row("Predictors", "", "", "", after = 5) %>% 
+    insert_row("Predictors", "", "", "", after = 6) %>% 
     set_bold(1, everywhere) %>%
-    set_bold(c(2, 6), everywhere) %>%
-    set_bottom_border(c(2, 6), everywhere) %>%
+    set_bold(c(2, 7), everywhere) %>%
+    set_bottom_border(c(2, 7), everywhere) %>%
     set_width(1) %>% 
@@
 @Chaudhry:2016 expanded this data so that it now includes official NGO laws for 162 countries between 1990 and 2013.
-We create indexes of the total number of laws passed in each country based on three broad categories, and we also sum each of these indexes to create a count of total legal barriers:
+We create indexes of the total number of laws passed in each country based on three broad categories, and we also sum each of these indexes to create a count of total legal barriers.
+We also create a yearly indicator variable to show if a country increased its count of anti-NGO laws (models using this outcome are included in the online appendix).
 
@@
                      aes(x = year, y = value, 
-                         color = barrier_display,
-                         linetype = barrier_display)) +
+                         color = barrier_display)) +
   geom_line(size = 0.75) +
@@
   scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
-  scale_linetype_manual(values = c("solid", "solid", "21"), name = NULL) +
   coord_cartesian(xlim = c(1990, 2015), ylim = c(0, 90)) +
@@
   theme_ngo(9) + 
-  theme(legend.justification = "left") +
+  theme(legend.justification = "left",
+        legend.key.size = unit(0.7, "lines")) +
   facet_wrap(vars(barrier_group))
@@
   scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
-  scale_linetype_manual(values = c("solid", "solid", "solid", "21", "21"), name = NULL) +
+  scale_linetype_manual(values = c("solid", "21", "solid", "21", "solid"), name = NULL) +
   coord_cartesian(xlim = c(1990, 2015), ylim = c(0, 45)) +
@@
   guides(color = guide_legend(nrow = 2)) +
-  labs(x = NULL, y = "Number of countries") +
+  labs(x = NULL, y = "Number of countries",
+       legend.key.size = unit(0.7, "lines")) +
   theme_ngo(9) + 
@@
   theme_ngo(9) +
-  theme(legend.justification = "left") +
+  theme(legend.justification = "left",
+        legend.key.size = unit(0.7, "lines")) +
   facet_wrap(vars(fake_facet_title))
@@
 
-We measure general human rights repression in three different ways.
+To see how both de jure and de facto civil society restrictions influence general human rights repression, we use four different quantitative measures of repression, each of which capture different dimensions of political and civil violence.
 First, following @GohdesCarey:2017, who use the killing of journalists to predict worsening human rights conditions, we use the Political Terror Scale (PTS), which assigns countries to five different categories of repression each year [@GibneyCornettWood:2019], with Level 5 representing widespread political violence, including arrests, political murders, disappearances, and torture.
 As seen in the left panel of Figure \@ref(fig:repression), the number of countries at Level 5 has decreased since the 1990s, while most countries are coded as Levels 2 and 3.
-To supplement the PTS, we also turn to two indicators from V-Dem: a physical violence index (`v2x_clphy`) that measures freedom from torture and political killings specifically, and a private civil liberties index (`v2x_clpriv`) that measures respect for property rights, labor rights, freedom of religion, freedom of movement, and other non-political human rights.
+
+Because the PTS captures broad notions of political terror with only five possible categories, we also look at three continuous measures of repression.
+From V-Dem, we use a physical violence index (`v2x_clphy`) that measures freedom from torture and political killings specifically, and a private civil liberties index (`v2x_clpriv`) that measures respect for property rights, labor rights, freedom of religion, freedom of movement, and other non-political human rights.
 V-Dem includes several other rights indicators, including one for political civil liberties that captures many of the same dimensions as the PTS, but civil society repression is included as a factor for these other indexes, making it inappropriate to use as an outcome variable.
-The right panel of Figure \@ref(fig:repression) shows that the average level of these two rights indexes has improved over time.
-
-```{r repression, fig.width=7, fig.height=3, fig.asp=NULL, fig.cap="Key measures of repression over time"}
+The middle panel of Figure \@ref(fig:repression) shows that the average level of these two rights indexes has improved over time.
+
+Finally, looking at political terror, physical violence, and private civil liberties captures specific dimensions of a country's respect for human rights, but isolating these trends in repression can prove difficult.
+@SchnakenbergFariss:2014, @Fariss:2014, and others have argued that a country's latent and underlying human rights environment causes a state to engage in specific actions related to human rights, such as engaging in political violence, arresting activists, or restricting freedom of religion.
+Measuring this underlying respect for human rights is difficult, however, as it is by definition unobserved.
+@FarissKenwickReuning:2020 use a Bayesian measurement model to generate estimates of latent respect for physical integrity rights.
+We use the posterior mean of their latent variable ($\theta$) as our final measure of repression in order to see how civil society restrictions predict changes in a country's future underlying human rights environment.
+The right panel of Figure \@ref(fig:repression) demonstrates the global increase in average latent human rights values over time.
+
+```{r repression, fig.width=7.5, fig.height=2.5, fig.asp=NULL, fig.cap="Key measures of repression over time"}
 pts_plot <- canary %>% 
@@
   theme_ngo(9) +
+  theme(legend.justification = "left",
+        legend.key.size = unit(0.7, "lines")) +
+  facet_wrap(vars(fake_facet_title))
+
+df_lhr_plot <- canary %>% 
+  as_tibble() %>% 
+  select(year, latent_hr_mean) %>% 
+  group_by(year) %>% 
+  nest() %>% 
+  mutate(cis = data %>% map(~ mean_cl_normal(.$latent_hr_mean))) %>% 
+  unnest(cis) %>% 
+  ungroup() %>% 
+  mutate(fake_facet_title = "Latent human rights")
+
+lhr_plot <- ggplot(df_lhr_plot, aes(x = year, y = y)) +
+  geom_ribbon(aes(ymin = ymin, ymax = ymax), alpha = 0.2, fill = "#433E85") +
+  geom_line(size = 0.75, color = "#433E85") +
+  coord_cartesian(xlim = c(1990, 2015)) +
+  guides(color = guide_legend(nrow = 2, reverse = TRUE),
+         fill = guide_legend(nrow = 2, reverse = TRUE)) +
+  labs(y = "Average value\n(Higher values = less repression)", x = NULL) +
+  theme_ngo(9) +
   theme(legend.justification = "left") +
@@
 
-(pts_plot | vdem_outcome_plot) &
+(pts_plot | vdem_outcome_plot | lhr_plot) &
   theme(legend.text = element_text(size = rel(0.7)),
@@
 - **Expectation 1~c~**: Anti-NGO laws signal constricting private civil liberties
+- **Expectation 1~d~**: Anti-NGO laws signal decreasing latent human rights
 - **Expectation 2~a~**: Civil society repression signals worsening political terror
@@
 - **Expectation 2~c~**: Civil society repression signals constricting private civil liberties
+- **Expectation 2~d~**: Civil society repression signals decreasing latent human rights
 
@@
 Because the Political Terror Scale is measured as an ordered category, we use ordered logistic regression to predict future values of the PTS.
-As V-Dem's physical violence index and private civil liberties index are both measured continuously, we predict these values with Gaussian models.
+As V-Dem's physical violence index and private civil liberties index and latent human rights values are all measured continuously, we predict these values with Gaussian models.
 We use median values from the models' posterior distributions as our point estimates and provide credible intervals using the 95% highest posterior density.[^bayes] We declare an effect statistically "significant" if the posterior probability of being different from zero exceeds 0.95.
@@
 [^bayes]: We use Stan [@stan] through R [@r-project] and brms [@brms-jss] to estimate our models.
-We generate 4 MCMC chains with 2,000 iterations in each chain, 1,000 of which are used for warmup.
+We generate 4 MCMC chains for each model with 2,000 iterations in each chain, 1,000 of which are used for warmup.
 All chains converge; we assess convergence with visual inspection.
@@
 The results of the ordered logistic regression models can be unwieldy to interpret with plain numbers due to varying intercepts and thresholds between PTS levels.
-Accordingly, we present graphical results for all our models wherever possible and include complete tables of model results in the appendix (see Tables \@ref(tab:tbl-models-pts), \@ref(tab:tbl-models-clphy), and \@ref(tab:tbl-models-clpriv)).
-For the sake of making it easier to compare the count of NGO laws with civil society repression, we reverse the x-axis in the marginal effects plots for our second empirical expectation so that increasing the civil society repression represents *worse* repression rather than less.
+Accordingly, we present graphical results for all our models wherever possible and include complete tables of model results in the appendix (see Tables \@ref(tab:tbl-models-pts), \@ref(tab:tbl-models-clphy), \@ref(tab:tbl-models-clpriv), and \@ref(tab:tbl-models-lhr)).
+For ease in comparing the count of NGO laws with civil society repression, we reverse the x-axis in the marginal effects plots for our second empirical expectation so that increasing the civil society repression represents *worse* repression rather than less.
 
@@
 
-Figure \@ref(fig:plot-mfx-e1b-e1c) shows the marginal effects of additional NGO legislation on V-Dem's physical violence index and private civil liberties index.
+Figure \@ref(fig:plot-mfx-e1b-e1d) shows the marginal effects of additional NGO legislation on V-Dem's physical violence index and private civil liberties index.
 Across all four models for different categories of legal barriers, holding all other values constant, neither rights index moves much in response to new NGO laws.
@@
 The null effect of legal barriers on private civil liberties is even more stark—a typical country is predicted to have a score of 0.69 regardless of the addition of any kind of NGO law.
+However, when looking at latent human rights values, adding a new NGO law is associated with a -0.013 decline in the level of respect for human rights in the following year, on average.
+The marginal effect is larger (-0.02) for additional barriers to advocacy and entry, which represent more burdensome restrictions than limits to funding.
 
@@
 Limited repression remains the most likely possible outcome, but the chance of seeing robust rule of law decreases rapidly as more laws are passed, all else equal.
-When looking at other forms of political repression, though, such as physical violence and private civil liberties, NGO legal barriers do not change predicted values in any meaningful way.
-
-```{r plot-mfx-e1b-e1c, fig.width=7.5, fig.height=5.5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on V-Dem rights indexes"}
+When looking at other specific forms of political repression, though, such as physical violence and private civil liberties, NGO legal barriers do not change predicted values in any meaningful way.
+But looking more broadly, civil society laws are associated with a worse predicted underlying human rights environment.
+
+```{r plot-mfx-e1b-e1d, fig.width=7.5, fig.height=7.5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on V-Dem rights indexes and latent human rights"}
 out_mfx_e1b <- mfx_e1b_clphy %>% 
@@
   ungroup() %>% 
+  mutate(plot_var_nice = fct_relabel(plot_var_nice, ~str_to_sentence(str_remove(., "Barriers to ")))) %>% 
   ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
@@
   guides(color = FALSE) +
-  labs(x = "Count of legal barriers",
+  labs(x = NULL,
        y = "Predicted civil liberties index\n(higher values = better protection)",
@@
 
-out_mfx_e1b / out_mfx_e1c
+out_mfx_e1d <- mfx_e1d_lhr %>% 
+  mutate(x_rounded = floor(effect1__)) %>% 
+  group_by(x_rounded, plot_var_nice) %>% 
+  slice(1) %>% 
+  ungroup() %>% 
+  mutate(plot_var_nice = fct_relabel(plot_var_nice, ~str_to_sentence(str_remove(., "Barriers to ")))) %>% 
+  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
+  geom_line(size = 0.5, color = "grey90") +
+  geom_pointrange(aes(ymin = lower__, ymax = upper__),
+                  fatten = 1) +
+  scale_x_continuous(breaks = 0:9) +
+  scale_color_viridis_d(option = "plasma", end = 0.8) +
+  guides(color = FALSE) +
+  labs(x = "Count of legal barriers",
+       y = "Predicted latent human rights value\n(higher values = better protection)",
+       title = "Latent human rights") +
+  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
+  theme_ngo() +
+  theme(panel.grid.major.x = element_blank())
+
+out_mfx_e1b / out_mfx_e1c / out_mfx_e1d
 ```
@@
 
-```{r plot-mfx-e2a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on the probability of specific levels of political terror"}
+```{r plot-mfx-e2a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on the probability of specific levels of political terror", out.width="75%"}
 out_mfx_e2a <- mfx_e2a_pts %>% 
@@
 
-In contrast with formal laws, civil society repression does have a noticeable effect on the predicted values of the other rights indexes (see Figure \@ref(fig:plot-mfx-e2b-e2c)).
-When holding all other model parameters at their typical values, increased civil society repression predicts increases in both the physical violence index and the private civil liberties index: a one standard deviation change in civil society repression is associated with a 0.02 change in overall rights.
+In contrast with formal laws, civil society repression does have a noticeable effect on the predicted values of the other rights indexes (see Figure \@ref(fig:plot-mfx-e2b-e2d)).
+When holding all other model parameters at their typical values, increased civil society repression predicts increases in both the physical violence index and private civil liberties index: a one standard deviation change in civil society repression is associated with a 0.02 change in overall rights.
 In other words, a typical country with a civil society repression score of 0 is predicted to have a physical violence index of 0.62 and civil liberties index of 0.67.
 This implies that an increase in de facto NGO restrictions predicts a `r percent_format(accuracy = 1)((0.62 - (0.62 - 0.02)) / (0.62 - 0.02))` decline in both protection from physical violence and respect for private civil liberties in the following year.
+Moreover, worsening civil society repression is strongly associated with a worse future human rights environment, as seen in the right panel of Figure \@ref(fig:plot-mfx-e2b-e2d)
 
 When holding all other factors equal, the de factor implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passing of formal de jure laws.
-Increasing civil society repression in countries with low levels of political terror can again potentially serve as a weak signal of more a more general increase in political violence in the future, while crackdowns on civil society predict more substantial changes in physical violence and threats to civil liberties.
-
-```{r plot-mfx-e2b-e2c, fig.width=7.5, fig.height=3.5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on V-Dem rights indexes"}
+Increasing civil society repression in countries with low levels of political terror can again potentially serve as a weak signal of more a more general increase in political violence in the future, while crackdowns on civil society predict more substantial changes in physical violence, threats to civil liberties, and latent respect for human rights more broadly.
+
+```{r plot-mfx-e2b-e2d, fig.width=9.5, fig.height=3.5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on V-Dem rights indexes and latent human rights"}
 out_mfx_e2b <- mfx_e2b_clphy %>% 
@@
   coord_cartesian(ylim = c(0.5, 0.75)) +
-  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
+  labs(x = "Civil society repression\n(scale reversed; greater repression on right)\n",
        y = "Predicted physical violence index\n(higher values = less violence)",
        title = "Physical violence index") +
-  theme_ngo()
+  theme_ngo(8)
 
@@
   coord_cartesian(ylim = c(0.5, 0.75)) +
-  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
-       y = "Predicted civil liberties index\n(higher values = less violence)",
+  labs(x = "Civil society repression\n(scale reversed; greater repression on right)\n",
+       y = "Predicted civil liberties index\n(higher values = better protection)",
        title = "Private civil liberties index") +
-  theme_ngo()
-
-out_mfx_e2b | out_mfx_e2c
+  theme_ngo(8)
+
+out_mfx_e2d <- mfx_e2d_lhr %>% 
+  ggplot(aes(x = effect1__, y = estimate__)) +
+  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
+              fill = "#FF4136", color = NA) +
+  geom_line(size = 0.75, color = "#FF4136") +
+  scale_x_reverse() +
+  labs(x = "Civil society repression\n(scale reversed; greater repression on right)\n",
+       y = "Predicted latent human rights value\n(higher values = better protection)",
+       title = "Latent human rights") +
+  theme_ngo(8)
+
+out_mfx_e2b | out_mfx_e2c | out_mfx_e2d
 ```
@@
     kable_styling() %>% 
-    row_spec(0, bold = TRUE) %>% 
-    column_spec(1, width = "0.05\\\\textwidth") %>% 
-    column_spec(2:7, width = "0.14\\\\textwidth")
+    column_spec(1, width = "0.07\\\\textwidth") %>% 
+    column_spec(2, width = "0.05\\\\textwidth") %>% 
+    column_spec(3:7, width = "0.13\\\\textwidth")
 } else {
@@
        "Barriers to funding", 0.0335855,                  "-0.95%",
-  "Civil society repression", 0.0332081,                  "-2.07%"
+  "Civil society repression", 0.0332081,                  "-2.07%",
+                  "Baseline", 0.1861944,                       "—",
+      "Total legal barriers", 0.1872427,                   "0.56%",
+      "Barriers to advocacy", 0.1871498,                   "0.51%",
+         "Barriers to entry", 0.1862244,                   "0.02%",
+       "Barriers to funding", 0.1879829,                   "0.96%",
+  "Civil society repression", 0.1856543,                  "-0.29%"
 ) %>% 
@@
 
-tbl_rmse_caption <- "Root mean squared error across models predicting physical violence and private civil liberties"
+tbl_rmse_caption <- "Root mean squared error across models predicting physical violence, private civil liberties, and latent human rights"
 
@@
         caption = tbl_rmse_caption) %>% 
-    pack_rows(index = c("Physical violence index" = 6, "Private civil liberties index" = 6)) %>% 
+    pack_rows(index = c("Physical violence index" = 6, 
+                        "Private civil liberties index" = 6,
+                        "Latent human rights values" = 6)) %>% 
     kable_styling()
@@
     insert_row("Private civil liberties index", "", "", after = 8) %>% 
+    insert_row("Latent human rights values", "", "", after = 15) %>% 
     set_bold(1, everywhere) %>%
-    set_bold(c(2, 9), everywhere) %>%
-    set_bottom_border(c(2, 9), everywhere) %>%
+    set_bold(c(2, 9, 16), everywhere) %>%
+    set_bottom_border(c(2, 9, 16), everywhere) %>%
     set_width(1) %>% 
@@
 This is likely related to the lack of improvements in predicting political terror—both indexes measure similar phenomena.
+Similarly, accounting for civil society repression when modeling latent human rights only results in slight changes to the RMSE.
 However, including civil society-related predictors when modeling private civil liberties does result in small gains in accuracy, reducing the RMSE by as much as 2% compared to the baseline model.
@@
 \clearpage
+
+```{r tbl-models-lhr}
+model_names_tbl_lhr <- c("Total barriers\n(t + 1)",
+                         "Barriers to advocacy\n(t + 1)",
+                         "Barriers to entry\n(t + 1)",
+                         "Barriers to funding\n(t + 1)",
+                         "Civil society repression\n(t + 1)")
+
+names(models_paper_lhr) <- model_names_tbl_lhr
+
+tbl_reg_lhr_caption <- "Full results from Gaussian regression models predicting latent human rights"
+
+tbl_reg_lhr <- modelsummary(models_paper_lhr,
+                            output = table_format,
+                            statistic = "[{conf.low}, {conf.high}]",
+                            coef_map = coef_list,
+                            gof_omit = "ELPD",
+                            escape = FALSE,
+                            caption = tbl_reg_lhr_caption,
+                            notes = list("Posterior means; 95% credible intervals in brackets"))
+
+if (!is_docx) {
+  tbl_reg_lhr %>% 
+    kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
+    column_spec(1, width = "0.10\\\\textwidth") %>% 
+    column_spec(2:6, width = "0.14\\\\textwidth")
+} else {
+  tbl_reg_lhr %>% 
+    set_font_size(10) %>% 
+    set_all_padding(1) %>% 
+    set_align(everywhere, 2:6, "center") %>% 
+    set_bold(1, everywhere) %>% 
+    set_width(1) %>% 
+    set_wrap(TRUE) %>% 
+    huxtable::set_caption(tbl_reg_lhr_caption) %>% 
+    huxtable::as_flextable()
+}
+```
+
+\clearpage

### 2021-04-11 _targets.R

@@ -285,6 +285,12 @@ list(
            plot_var_nice = c("Total legal barriers", "Barriers to advocacy",
                              "Barriers to entry", "Barriers to funding")))),
 
+  tar_target(mfx_e1d_lhr, generate_mfx(
+    tibble(model = list(m_lhr_total, m_lhr_advocacy, m_lhr_entry, m_lhr_funding),
+           plot_var = c("barriers_total", "advocacy", "entry", "funding"),
+           plot_var_nice = c("Total legal barriers", "Barriers to advocacy",
+                             "Barriers to entry", "Barriers to funding")))),
+
   tar_target(mfx_e2a_pts, generate_mfx(
     tibble(model = list(m_pts_v2csreprss),
            plot_var = c("v2csreprss"),
@@ -298,6 +304,11 @@ list(
 
   tar_target(mfx_e2c_clpriv, generate_mfx(
     tibble(model = list(m_clpriv_v2csreprss),
+           plot_var = c("v2csreprss"),
+           plot_var_nice = c("Civil society repression")))),
+
+  tar_target(mfx_e2d_lhr, generate_mfx(
+    tibble(model = list(m_lhr_v2csreprss),
            plot_var = c("v2csreprss"),
            plot_var_nice = c("Civil society repression")))),
 
@@ -350,6 +361,9 @@ list(
   tar_target(models_paper_clpriv,
              build_modelsummary(lst(m_clpriv_total, m_clpriv_advocacy, m_clpriv_entry,
                                     m_clpriv_funding, m_clpriv_v2csreprss))),
+  tar_target(models_paper_lhr,
+             build_modelsummary(lst(m_lhr_total, m_lhr_advocacy, m_lhr_entry,
+                                    m_lhr_funding, m_lhr_v2csreprss))),
 
   # Render the analysis notebook
   tar_notebook_pages(),

### 2021-04-12 manuscript/manuscript.Rmd
Add thing about PTS ceiling effect

@@
   url: https://www.andrewheiss.com/
-date: "April 10, 2021"
+date: "April 12, 2021"
 published: This is an early draft of a working paper.
@@
 Across all counts of legal barriers, the overall probability of seeing Levels 4 and 5 is minuscule, and the adding new laws does little to shift that probability.
+This is not unexpected however—the PTS has a natural ceiling at Level 5, and few countries that engage in such severe repression compared to lower levels of the index.
+The majority of movement across PTS categories should thus occur between Levels 1–3.
 

### 2021-04-13 manuscript/manuscript.Rmd
Pre-AZ edits

@@
 abstract: >-
-  Many countries across the globe use legal restrictions to crack down and limit civil society.
+  Many countries across the globe have increasingly cracked down on NGOs over the last few decades.
 These attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
-This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
+This is especially the case for electoral democracies, which unlike autocracies, may not aggressively attack civic space.
 In this paper, we explore if crackdowns on NGOs predict broader human rights repression.
-We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
-These laws also make it easier for states to prevent and deter future large-scale popular mobilization.
-Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, physical violence, and violations of private civil liberties.
-This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deterioration in space for civil society.
+Anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
+These laws may also make it easier for states to prevent and deter future large-scale popular mobilization.
+Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, physical integrity rights violations, and violations of private civil liberties.
+We find that while formal de jure laws provide little information in predicting future repression, de facto civil society repression predicts worsening respect for physical integrity rights and civil liberties.
 keywords: "civil society restrictions, human rights, political terror, civil liberties"
+thanks: >-
+  We would like to thank participants of the 2021 International Studies Association (ISA) convention for their comments and feedback.
 reference-section-title: References
@@
 
+\memSingle
+
 Governments across the globe have been cracking down on civil society organizations (CSOs), a phenomenon commonly referred to the closing or shrinking of civic space [@CarothersBrechenmacher:2014; @DPR:2016; @Chaudhry:2016; @DupuyPrakash:2018].
@@
 
-```{r civicus-map, fig.cap="2020 CIVICUS Monitor civic space ratings"}
+```{r civicus-map, fig.cap="2020 CIVICUS Monitor civic space ratings", fig.pos="h"}
 ggplot() +
@@
 
-Anti-civil society measures are occasionally violent, but notably, government repression of NGOs is generally non-violent.
-Rather than publicly arrest or beat activists, states implement "administrative crackdown," or the passage of laws to create barriers to NGO advocacy, entry, funding [@Chaudhry:2016].
+Anti-civil society measures are occasionally violent, but recently, government repression of NGOs has generally been non-violent.
+Rather than publicly arrest or beat activists, states implement "administrative crackdown," or the passage of laws to create barriers to NGO advocacy, entry, and funding [@Chaudhry:2016].
 The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations [@Heiss:2019; @Heiss:2017].
-While in some cases this has led to the depoliticization of NGOs and avoidance of direct political activism by CSOs, states cannot soften or neutralize all forms of political activities in subtle, legal ways that they have with NGOs.
+While in some cases this has led to the depoliticization of NGOs and avoidance of direct political activism by CSOs, states cannot soften or neutralize all forms of political activities in subtle, legal ways like they have with NGOs.
 Sooner or later, states need to deal with threats to their stability in a more direct, violent, confrontational manner.
 Administrative NGO laws and general civil society repression could be an important early warning sign—or a canary in the coal mine—of worsening human rights repression in a state, signaling that a state will continue down the path of further repression.
-What does state targeting of NGOs tell us about a state's broader respect for civil society and the overall level of human rights repression?
+What does state targeting of NGOs tell us about the state's broader respect for civil society and the overall level of human rights repression?
 Can the crackdown on NGOs act as an indicator for subsequent increasing repression?
@@
 We differentiate between two forms of civil society repression: official de jure anti-NGO restrictions that are codified in law, and general de facto levels of civil society repression.
-We propose and test two empirical expectations—that de jure and de factor restrictions predict future political terror, physical violence, and government encroachment on private civil liberties.
+We propose and test two empirical expectations—that de jure and de factor restrictions predict future political terror, physical integrity rights violations, and government encroachment on private civil liberties.
+
 Using multilevel Bayesian modeling, we find that formal de jure laws provide very little additional information when attempting to predict future repression.
 However, we find that accounting for more general civil society repression does boost our models' predictive power.
-Increasing de facto civil society repression predicts an increase in the probability of moderate political terror and results in a 3% decrease in indexes of physical violence and private civil liberties.
+Increasing de facto civil society repression predicts an increase in the probability of moderate political terror and results in worsening violations of physical integrity rights and civil liberties.
 
@@
 
-One part of the existing literature focuses on the role of structural factors such as levels of democracy, economic development, electoral competitiveness in predisposing a state to increased use of repression.
+Early literature on repression focused on the role of structural factors such as levels of democracy, economic development, electoral competitiveness in predisposing a state to increased use of repression.
 Most notably, democratic forms of government—and democratization in general—has a pacifying effect on state repression [@DavenportArmstrong:2004; @Krain:1997; @Richards:1999].
@@
 
-Another strand of research focuses on how the behavior of various actors shapes government response.
+More recent research focuses on how the behavior of various actors shapes government response.
 One of the most consistent findings in the political violence literature is that authorities repress to counter ongoing challenges to the status quo.
@@
 In addition to attacking groups willingness to organize against states, such preventive repression also damages states' capacity to impose costs [@Davenport:2007a, 47].
-
-NGOs are one actor that can pose challenges to political authorities, and state repression of these actors, especially through legal restrictions or administrative crackdown can also be considered a form of preventive repression.
+NGOs are one actor that can pose challenges to political authorities, and state repression of these actors, especially through legal restrictions or administrative crackdown can also be considered a form of preventive repression [@Chaudhry:2016].
+
 A robust, strong civil society is widely considered as an important component on democratic transition and consolidation [@Putnam:1994].
@@
 This may include measures such as detentions, short-term incarceration, as well as beatings, threats to families and destruction of valuable property.
+
 Finally, counting official laws can also undermeasure civil society repression because governments can repress NGOs without passing or relying on formal laws.
@@
 
-- **Empirical expectation 1**: If a country imposes a formal anti-NGO law, then it is likely to signal future deteriorating human rights conditions.
-- **Empirical expectation 2**: If a country represses civil society, then it is likely to signal future deteriorating human rights conditions.
+- **Empirical expectation 1** (effect of de jure NGO repression): If a country imposes a formal anti-NGO law, then it is likely to signal future deteriorating human rights conditions.
+- **Empirical expectation 2** (effect of de facto NGO repression): If a country represses civil society, then it is likely to signal future deteriorating human rights conditions.
 
@@
 
-@christensen2013 collected data on formal NGO regulations in 90 countries to explore the determinants of laws that restrict NGO foreign funding laws specifically.
-@Chaudhry:2016 expanded this data so that it now includes official NGO laws for 162 countries between 1990 and 2013.
-We create indexes of the total number of laws passed in each country based on three broad categories, and we also sum each of these indexes to create a count of total legal barriers.
+To measure de jure repression, we use data on anti-NGO laws from @Chaudhry:2016 which includes official NGO laws for 162 countries between 1990 and 2013.
+We create indexes of the total number of laws passed in each country based on three broad categories of laws related to barriers to entry, funding, and advocacy, and we also sum each of these indexes to create a count of total legal barriers.
 We also create a yearly indicator variable to show if a country increased its count of anti-NGO laws (models using this outcome are included in the online appendix).
@@
 From V-Dem, we use a physical violence index (`v2x_clphy`) that measures freedom from torture and political killings specifically, and a private civil liberties index (`v2x_clpriv`) that measures respect for property rights, labor rights, freedom of religion, freedom of movement, and other non-political human rights.
-V-Dem includes several other rights indicators, including one for political civil liberties that captures many of the same dimensions as the PTS, but civil society repression is included as a factor for these other indexes, making it inappropriate to use as an outcome variable.
 The middle panel of Figure \@ref(fig:repression) shows that the average level of these two rights indexes has improved over time.
 
-Finally, looking at political terror, physical violence, and private civil liberties captures specific dimensions of a country's respect for human rights, but isolating these trends in repression can prove difficult.
+However, looking at political terror, physical integrity rights, and private civil liberties captures specific dimensions of a country's respect for human rights, but isolating these trends in repression can prove difficult.
 @SchnakenbergFariss:2014, @Fariss:2014, and others have argued that a country's latent and underlying human rights environment causes a state to engage in specific actions related to human rights, such as engaging in political violence, arresting activists, or restricting freedom of religion.
@@
 Across all counts of legal barriers, the overall probability of seeing Levels 4 and 5 is minuscule, and the adding new laws does little to shift that probability.
-This is not unexpected however—the PTS has a natural ceiling at Level 5, and few countries that engage in such severe repression compared to lower levels of the index.
+This is not unexpected however—the PTS has a natural ceiling at Level 5.
+Specifically, in addition to measuring the scope and intensity of government violence, the PTS scale also looks at the proportion of population targeted for abuse.
+Countries that receive a 5 are rare, as this score captures physical abuses routinely perpetrated against citizens not involved in politics, and includes cases where governments engage in "scorched earth" counterinsurgency policies or summary executions based on class or ethnic affiliation [@GibneyCornettWood:2019].
 The majority of movement across PTS categories should thus occur between Levels 1–3.
@@
 When holding all other factors equal, the de factor implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passing of formal de jure laws.
-Increasing civil society repression in countries with low levels of political terror can again potentially serve as a weak signal of more a more general increase in political violence in the future, while crackdowns on civil society predict more substantial changes in physical violence, threats to civil liberties, and latent respect for human rights more broadly.
+Increasing civil society repression in countries with low levels of political terror can again potentially serve as a weak signal of more a more general increase in political violence in the future, while crackdowns on civil society predict more substantial changes in physical integrity rights, threats to civil liberties, and latent respect for human rights more broadly.
 
@@
 When governments restrict civil society, it reduces these organizations' ability to maintain accountability and protect against abuse.
-Given this potential protective power, in this paper, we posited that the ongoing global crackdown on civil society could predict worsening human rights in a country interested in political and civil repression.
+Given these potential knock-on effects, in this paper, we posited that the ongoing global crackdown on civil society could predict worsening human rights in a country interested in political and civil repression.
 Passing restrictive laws, imposing barriers to NGO advocacy, entry, and funding, and arresting and expelling NGO staff could pave the way for future repression.
@@
 We find little support for the predictive power of de jure restriction.
-Marginal predictions show that, all else held equal, adding new anti-NGO laws increases the probability of seeing moderate levels of political terror, but does not change predicted values of physical violence or civil liberties.
+Marginal predictions show that, all else held equal, adding new anti-NGO laws increases the probability of seeing moderate levels of political terror, but does not change predicted values of physical integrity or civil liberties rights violations.
 When comparing out-of-sample predictions to a baseline model, including de jure restrictions as predictors does not improve our models' predictive accuracy.
@@
 As with formal laws, rising civil society repression tends to increase the probability of more moderate political terror.
-Additionally, increasing civil society repression is associated with a 3% decrease in indexes that measure safety from physical violence and respect for civil liberties in the future.
+Additionally, increasing civil society repression is associated with worsening respect for physical integrity rights and civil liberties in the future.
 In out-of-sample predictions, including civil society restrictions improves model accuracy by 1–2% over the baseline.
@@
 
+\memSingleSmall
+
 ```{r tbl-models-pts}
@@
 \clearpage
+
+\memSingle

### 2021-07-17 analysis/03_environment-repression.Rmd
Remove REWB stuff

--- 2021-04-02 analysis/03_environment-repression.Rmd
@@
   tar_load(c(m_pts_baseline, m_pts_v2csreprss, 
-             m_pts_baseline_rewb, m_pts_v2csreprss_rewb, 
              m_clphy_baseline, m_clphy_v2csreprss, 
-             m_clphy_baseline_rewb, m_clphy_v2csreprss_rewb, 
              m_clpriv_baseline, m_clpriv_v2csreprss, 
-             m_clpriv_baseline_rewb, m_clpriv_v2csreprss_rewb))
+             m_lhr_baseline, m_lhr_v2csreprss))
 
   # Load regression tables
-  tar_load(c(models_tbl_e2a, models_tbl_e2b, models_tbl_e2c))
+  tar_load(c(models_tbl_e2a, models_tbl_e2b, models_tbl_e2c, models_tbl_e2d))
 
@@
   mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
-  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))
+  mutate(across(c(outcome_var, explan_var, family), ~fct_inorder(., ordered = TRUE)))
 
@@
          explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))
+  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
 
@@
 coef_plots <- models %>% 
-  filter(str_detect(model, "m_pts_v2csreprss")) %>% 
-  mutate(re_fancy = case_when(
-    re == "RE" ~ "Random effects models",
-    re == "REWB" ~ "Random effects—within/between models"
-  )) %>% 
+  filter(model == "m_pts_v2csreprss") %>% 
   mutate(coef_draws = map(
@@
   unnest(coef_draws) %>% 
-  filter(!str_detect(.variable, "between")) %>% 
   left_join(coefs_clean, by = c(".variable" = "coef"))
@@
 coef_plots %>% 
-  ggplot(aes(y = fct_rev(coef_clean), x = .value, fill = re_fancy)) +
+  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
   stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
@@
   labs(x = "Coefficient", y = NULL) +
-  facet_wrap(vars(re_fancy), ncol = 1, scales = "free_y") +
   theme_ngo()
@@
 mfx <- models %>% 
-  filter(str_detect(model, "m_pts_v2csreprss")) %>% 
-  mutate(plot_vars = case_when(
-    re == "RE" ~ "v2csreprss",
-    re == "REWB" ~ "v2csreprss_within"
-  )) %>% 
+  filter(model == "m_pts_v2csreprss") %>% 
+  mutate(plot_vars = "v2csreprss") %>% 
   mutate(fx = map2(actual_model, plot_vars, 
@@
 mfx %>% 
-  filter(model == "m_pts_v2csreprss") %>% 
   ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
@@
   labs(x = "Civil society repression\n(higher values = less repression)",
-       y = "Predicted probability of category",
-       color = "Political terror scale", fill = "Political terror scale") +
-  theme_ngo()
-
-mfx %>% 
-  filter(model == "m_pts_v2csreprss_rewb") %>% 
-  ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
-  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, color = NA) +
-  geom_line(size = 1) +
-  labs(x = "Difference from average level of civil society repression\n(higher values = less repression)",
        y = "Predicted probability of category",
@@
   mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))
+  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
 
@@
 coef_plots <- models %>% 
-  filter(str_detect(model, "m_clphy_v2csreprss")) %>% 
-  mutate(re_fancy = case_when(
-    re == "RE" ~ "Random effects models",
-    re == "REWB" ~ "Random effects—within/between models"
-  )) %>% 
+  filter(model == "m_clphy_v2csreprss") %>% 
   mutate(coef_draws = map(
@@
 mfx <- models %>% 
-  filter(str_detect(model, "m_clphy_v2csreprss")) %>% 
-  mutate(plot_vars = case_when(
-    re == "RE" ~ "v2csreprss",
-    re == "REWB" ~ "v2csreprss_within"
-  )) %>% 
+  filter(model == "m_clphy_v2csreprss") %>% 
+  mutate(plot_vars = "v2csreprss") %>% 
   mutate(fx = map2(actual_model, plot_vars, 
@@
 mfx %>% 
-  filter(model == "m_clphy_v2csreprss") %>% 
   ggplot(aes(x = effect1__, y = estimate__)) +
@@
   labs(x = "Civil society repression\n(higher values = less repression)",
-       y = "Predicted physical violence index\n(higher values = less violence)") +
-  theme_ngo()
-
-mfx %>% 
-  filter(model == "m_clphy_v2csreprss_rewb") %>% 
-  ggplot(aes(x = effect1__, y = estimate__)) +
-  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
-              fill = "#FF4136", color = NA) +
-  geom_line(size = 1, color = "#FF4136") +
-  labs(x = "Difference from average level of civil society repression\n(higher values = less repression)",
        y = "Predicted physical violence index\n(higher values = less violence)") +
@@
 coef_plots <- models %>% 
-  filter(str_detect(model, "m_clpriv_v2csreprss")) %>% 
-  mutate(re_fancy = case_when(
-    re == "RE" ~ "Random effects models",
-    re == "REWB" ~ "Random effects—within/between models"
-  )) %>% 
+  filter(model == "m_clpriv_v2csreprss") %>% 
   mutate(coef_draws = map(
@@
 mfx <- models %>% 
-  filter(str_detect(model, "m_clpriv_v2csreprss")) %>% 
-  mutate(plot_vars = case_when(
-    re == "RE" ~ "v2csreprss",
-    re == "REWB" ~ "v2csreprss_within"
-  )) %>% 
+  filter(model == "m_clpriv_v2csreprss") %>% 
+  mutate(plot_vars = "v2csreprss") %>% 
   mutate(fx = map2(actual_model, plot_vars, 
@@
 mfx %>% 
-  filter(model == "m_clpriv_v2csreprss") %>% 
   ggplot(aes(x = effect1__, y = estimate__)) +
@@
   theme_ngo()
+```
+
+\
+
+# E~2d~: Civil society environment and latent physical integrity rights
+
+```{r tbl-e2d}
+# Build nicer column names
+models_for_table_e2d <- models %>% 
+  filter(outcome_var == "Latent human rights") %>% 
+  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
+  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
+
+# Make a named vector of original model names and nice names
+model_names_tbl_e2d <- models_for_table_e2d %>% 
+  pull(model_name) %>% 
+  set_names(models_for_table_e2d$model)
+
+# Rename the columns
+names(models_tbl_e2d) <- recode(names(models_tbl_e2d), !!!model_names_tbl_e2d)
+
+modelsummary(models_tbl_e2d,
+             statistic = "[{conf.low}, {conf.high}]",
+             coef_map = coef_list,
+             gof_omit = "ELPD",
+             escape = FALSE,
+             notes = list("Posterior means; 95% credible intervals in brackets"))
+```
+
+## Coefficients
+
+```{r plot-coefs-e2d}
+coef_plots <- models %>% 
+  filter(model == "m_lhr_v2csreprss") %>% 
+  mutate(coef_draws = map(
+    actual_model, 
+    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
+  select(-actual_model) %>% 
+  unnest(coef_draws) %>% 
+  left_join(coefs_clean, by = c(".variable" = "coef"))
+
+coef_plots %>% 
+  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
+  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
+  geom_vline(xintercept = 0) +
+  guides(fill = FALSE, alpha = FALSE) +
+  scale_alpha_manual(values = c(1, 0.4)) +
+  labs(x = "Coefficient", y = NULL) +
+  theme_ngo()
+```
+
+## Marginal effects
+
+```{r plot-mfx-e2d}
+mfx <- models %>% 
+  filter(model == "m_lhr_v2csreprss") %>% 
+  mutate(fx = map2(actual_model, "v2csreprss",
+                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
+  select(-actual_model) %>% 
+  unnest(fx)
 
 mfx %>% 
-  filter(model == "m_clpriv_v2csreprss_rewb") %>% 
   ggplot(aes(x = effect1__, y = estimate__)) +
@@
   geom_line(size = 1, color = "#FF4136") +
-  labs(x = "Difference from average level of civil society repression\n(higher values = less repression)",
-       y = "Predicted civil liberties index\n(higher values = less violence)") +
+  labs(x = "Civil society repression\n(higher values = less repression)",
+       y = "Predicted latent human rights\n(higher values = less violence)") +
   theme_ngo()

### 2021-07-17 analysis/03_laws-repression.Rmd
Remove REWB stuff

@@
              m_pts_advocacy, m_pts_entry, m_pts_funding, 
-             m_pts_baseline_rewb, m_pts_total_rewb, 
-             m_pts_advocacy_rewb, m_pts_entry_rewb, m_pts_funding_rewb, 
              m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
              m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
-             m_clphy_baseline_rewb, m_clphy_total_rewb, 
-             m_clphy_advocacy_rewb, m_clphy_entry_rewb, m_clphy_funding_rewb, 
              m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new,
              m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
-             m_clpriv_baseline_rewb, m_clpriv_total_rewb, 
-             m_clpriv_advocacy_rewb, m_clpriv_entry_rewb, m_clpriv_funding_rewb,
              m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
@@
   # Load regression tables
-  tar_load(c(models_tbl_e1a_re, models_tbl_e1a_rewb, 
-             models_tbl_e1b_re, models_tbl_e1c_re, models_tbl_e1d_re))
+  tar_load(c(models_tbl_e1a_re, models_tbl_e1b_re, 
+             models_tbl_e1c_re, models_tbl_e1d_re))
 
@@
 models_for_table_e1a_re <- models %>% 
-  filter(outcome_var == "Political terror", re == "RE") %>% 
+  filter(outcome_var == "Political terror") %>% 
   mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
          explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))
+  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
 
@@
 
-```{r tbl-e1a-rewb}
-models_for_table_e1a_rewb <- models %>% 
-  filter(outcome_var == "Political terror", re == "REWB") %>% 
-  mutate(outcome_var = recode(outcome_var, "Political terror" = "PTS"),
-         explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))
-
-models_names_table_e1a_rewb <- models_for_table_e1a_rewb %>% 
-  pull(model_name) %>% 
-  set_names(models_for_table_e1a_rewb$model)
-
-names(models_tbl_e1a_rewb) <- recode(names(models_tbl_e1a_rewb), 
-                                     !!!models_names_table_e1a_rewb)
-
-modelsummary(models_tbl_e1a_rewb,
-             statistic = "[{conf.low}, {conf.high}]",
-             coef_map = coef_list,
-             gof_omit = "ELPD",
-             escape = FALSE,
-             notes = list("Posterior means; 95% credible intervals in brackets"))
-```
-
 ## Coefficients
@@
   filter(str_detect(model, "pts_"), !str_detect(model, "baseline")) %>% 
-  mutate(re_fancy = case_when(
-    re == "RE" ~ "Random effects models",
-    re == "REWB" ~ "Random effects—within/between models"
-  )) %>% 
   mutate(coef_draws = map(
@@
   labs(x = "Coefficient", y = NULL) +
-  facet_wrap(vars(re_fancy), ncol = 2, scales = "free_y") +
   theme_ngo()
@@
 mfx <- models %>% 
-  filter(str_detect(model, "_pts"), !str_detect(model, "rewb|baseline")) %>% 
+  filter(str_detect(model, "_pts"), !str_detect(model, "baseline|new")) %>% 
   left_join(plot_pts_vars_lookup, by = "model") %>% 
@@
 models_for_table_e1b_re <- models %>% 
-  filter(outcome_var == "Physical violence", re == "RE") %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))
+  filter(outcome_var == "Physical violence") %>% 
+  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
 
@@
   filter(str_detect(model, "clphy"), !str_detect(model, "baseline")) %>% 
-  mutate(re_fancy = case_when(
-    re == "RE" ~ "Random effects models",
-    re == "REWB" ~ "Random effects—within/between models"
-  )) %>% 
   mutate(coef_draws = map(
@@
 mfx <- models %>% 
-  filter(str_detect(model, "clphy"), !str_detect(model, "rewb|baseline")) %>% 
+  filter(str_detect(model, "clphy"), !str_detect(model, "new|baseline")) %>% 
   left_join(plot_clphy_vars_lookup, by = "model") %>% 
@@
 models_for_table_e1c_re <- models %>% 
-  filter(outcome_var == "Private civil liberties", re == "RE") %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))
+  filter(outcome_var == "Private civil liberties") %>% 
+  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
 
@@
   filter(str_detect(model, "clpriv"), !str_detect(model, "baseline")) %>% 
-  mutate(re_fancy = case_when(
-    re == "RE" ~ "Random effects models",
-    re == "REWB" ~ "Random effects—within/between models"
-  )) %>% 
   mutate(coef_draws = map(
@@
 mfx <- models %>% 
-  filter(str_detect(model, "clpriv"), !str_detect(model, "rewb|baseline")) %>% 
+  filter(str_detect(model, "clpriv"), !str_detect(model, "new|baseline")) %>% 
   left_join(plot_clpriv_vars_lookup, by = "model") %>% 
@@
 models_for_table_e1d_re <- models %>% 
-  filter(outcome_var == "Latent human rights", re == "RE") %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))
+  filter(outcome_var == "Latent human rights") %>% 
+  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
 
@@
   filter(str_detect(model, "lhr"), !str_detect(model, "baseline")) %>% 
-  mutate(re_fancy = case_when(
-    re == "RE" ~ "Random effects models",
-    re == "REWB" ~ "Random effects—within/between models"
-  )) %>% 
   mutate(coef_draws = map(
@@
 mfx <- models %>% 
-  filter(str_detect(model, "lhr"), !str_detect(model, "rewb|baseline")) %>% 
+  filter(str_detect(model, "lhr"), !str_detect(model, "new|baseline")) %>% 
   left_join(plot_lhr_vars_lookup, by = "model") %>% 

### 2021-07-17 analysis/03_model-details.Rmd
Remove REWB stuff

--- 2021-04-02 analysis/03_model-details.Rmd
@@
   # So we do it this manual way
-  tar_load(c(m_pts_baseline, m_pts_total, m_pts_advocacy, 
-             m_pts_entry, m_pts_funding, m_pts_v2csreprss, 
-             m_pts_baseline_rewb, m_pts_total_rewb, m_pts_advocacy_rewb, 
-             m_pts_entry_rewb, m_pts_funding_rewb, m_pts_v2csreprss_rewb, 
-             m_clphy_baseline, m_clphy_total, m_clphy_advocacy, 
-             m_clphy_entry, m_clphy_funding, m_clphy_v2csreprss, 
-             m_clphy_baseline_rewb, m_clphy_total_rewb, m_clphy_advocacy_rewb, 
-             m_clphy_entry_rewb, m_clphy_funding_rewb, m_clphy_v2csreprss_rewb, 
-             m_clpriv_baseline, m_clpriv_total, m_clpriv_advocacy, 
-             m_clpriv_entry, m_clpriv_funding, m_clpriv_v2csreprss, 
-             m_clpriv_baseline_rewb, m_clpriv_total_rewb, m_clpriv_advocacy_rewb, 
-             m_clpriv_entry_rewb, m_clpriv_funding_rewb, m_clpriv_v2csreprss_rewb))
+  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
+             m_pts_advocacy, m_pts_entry, m_pts_funding, 
+             m_pts_v2csreprss, 
+             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
+             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
+             m_clphy_v2csreprss, 
+             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new, 
+             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
+             m_clpriv_v2csreprss, 
+             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
+             m_lhr_advocacy, m_lhr_entry, m_lhr_funding, 
+             m_lhr_v2csreprss, 
+             m_pts_baseline_train, m_pts_total_train, 
+             m_pts_advocacy_train, m_pts_entry_train, m_pts_funding_train, 
+             m_pts_v2csreprss_train, 
+             m_clphy_baseline_train, m_clphy_total_train, 
+             m_clphy_advocacy_train, m_clphy_entry_train, m_clphy_funding_train, 
+             m_clphy_v2csreprss_train, 
+             m_clpriv_baseline_train, m_clpriv_total_train, 
+             m_clpriv_advocacy_train, m_clpriv_entry_train, m_clpriv_funding_train, 
+             m_clpriv_v2csreprss_train))
 })
 ```
+
+```{r set-computer-details}
+computer <- "Work"
+
+if (computer == "Work") {
+  computer_details <- "2019 MacBook Pro with 16 cores and 32 GB of RAM, using Stan through brms through cmdstanr"
+} else {
+  computer_details <- "2016 MacBook Pro with 4 cores and 16 GB of RAM, using Stan through brms through cmdstanr"
+}
+```
+
+We ran these models on a `r computer_details`.
+
+\
 
@@
 
+### Full data
+
 ```{r running-time-e1}
@@
   mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
-  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))
+  mutate(across(c(outcome_var, explan_var, family), ~fct_inorder(., ordered = TRUE)))
 
 model_time_e1 <- models_e1 %>% 
+  filter(training == "Full data") %>% 
   mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
@@
   mutate(model = glue("<code>{model}</code>")) %>% 
-  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
-           `Random effects` = re, `Family` = family) %>% 
+  group_by(Model = model, Outcome = outcome_var, 
+           `Main predictor` = explan_var, `Family` = family) %>% 
   summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
   ungroup() %>% 
-  arrange(Outcome, `Main predictor`, `Random effects`)
+  arrange(Outcome, `Main predictor`)
+
+total_row_e1 <- tibble(Outcome = "Total", 
+                       `Total time (i.e. longest chain)` = 
+                         as.duration(sum(model_time_e1$`Total time (i.e. longest chain)`)))
+
+model_time_e1 <- model_time_e1 %>% 
+  bind_rows(total_row_e1)
+
+model_time_e1 %>% 
+  select(-Outcome) %>% 
+  kbl(escape = FALSE) %>% 
+  pack_rows(index = table(fct_inorder(model_time_e1$Outcome))) %>% 
+  kable_styling()
+```
+
+### Training data
+
+```{r running-time-e1-training}
+model_time_e1 <- models_e1 %>% 
+  filter(training == "Training") %>% 
+  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
+         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
+  select(-actual_model) %>% 
+  unnest(duration) %>% 
+  mutate(model = glue("<code>{model}</code>")) %>% 
+  group_by(Model = model, Outcome = outcome_var, 
+           `Main predictor` = explan_var, `Family` = family) %>% 
+  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
+  ungroup() %>% 
+  arrange(Outcome, `Main predictor`)
 
@@
   mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
-  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))
+  mutate(across(c(outcome_var, explan_var, family), ~fct_inorder(., ordered = TRUE)))
 
 model_time_e2 <- models_e2 %>% 
+  filter(training == "Full data") %>% 
   mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
@@
   mutate(model = glue("<code>{model}</code>")) %>% 
-  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
-           `Random effects` = re, `Family` = family) %>% 
+  group_by(Model = model, Outcome = outcome_var, 
+           `Main predictor` = explan_var, `Family` = family) %>% 
   summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
   ungroup() %>% 
-  arrange(Outcome, `Main predictor`, `Random effects`)
+  arrange(Outcome, `Main predictor`)
+
+total_row_e2 <- tibble(Outcome = "Total", 
+                       `Total time (i.e. longest chain)` = 
+                         as.duration(sum(model_time_e2$`Total time (i.e. longest chain)`)))
+
+model_time_e2 <- model_time_e2 %>% 
+  bind_rows(total_row_e2)
+
+model_time_e2 %>% 
+  select(-Outcome) %>% 
+  kbl(escape = FALSE) %>% 
+  pack_rows(index = table(fct_inorder(model_time_e2$Outcome))) %>% 
+  kable_styling()
+```
+
+### Training data
+
+```{r running-time-e2-training}
+model_time_e2 <- models_e2 %>% 
+  filter(training == "Training") %>% 
+  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
+         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
+  select(-actual_model) %>% 
+  unnest(duration) %>% 
+  mutate(model = glue("<code>{model}</code>")) %>% 
+  group_by(Model = model, Outcome = outcome_var, 
+           `Main predictor` = explan_var, `Family` = family) %>% 
+  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
+  ungroup() %>% 
+  arrange(Outcome, `Main predictor`)
 

### 2021-07-17 analysis/03_modeling-choices.Rmd
Remove REWB stuff

@@
 })
-
-# canary <- canary %>%
-#   mutate(gwcode = as.factor(gwcode), year = as.factor(year)) %>%  # Make a factor
-#   mutate(PTS_factor_lead1 = ordered(PTS_factor_lead1)) %>%  # Make this ordered
-#   # To do fancy Bell and Jones adjustment (https://doi.org/10.1017/psrm.2014.7)
-#   # (aka Mundlak devices), explanatory variables should be split into a meaned
-#   # version (\bar{x}) and a de-meaned version (x - \bar{x}) so that they can
-#   # explain the within-group and between-group variation. We de-mean three variables here:
-#   group_by(gwcode) %>%
-#   mutate_at(vars(v2csreprss, v2x_polyarchy, gdpcap_log),
-#             list(between = ~mean(., na.rm = TRUE),  # Between, for countries
-#                  within = ~. - mean(., na.rm = TRUE))) %>%   # Within, for countries
-#   ungroup()
 ```
@@
 So, using a Mundlak within/between split of time-varying covariates is warranted, as is using a country/year random effects structure. Woot.
+
+BUT for the sake of computational efficiency, we omit the within/between split.
+It takes 30-120 minutes to run one within/between model, and running dozens can take all day.
+The predictive results are nearly identical to models without the split, and since we're more interested in prediction than in individual coefficient effects, we don't need to wait hours for the same results we'd get with the original non-demeaned values.

### 2021-07-17 analysis/04_predictions.Rmd
Remove REWB stuff

@@
              m_pts_entry_train, m_pts_funding_train,
-             m_pts_baseline_rewb_train, m_pts_v2csreprss_rewb_train, 
              m_clphy_baseline_train, m_clphy_v2csreprss_train, 
@@
   magrittr::set_colnames(pts_levels)
-
-set.seed(seed_pts_prediction)
-pred_pts_baseline_rewb <- predict(
-  m_pts_baseline_rewb_train, 
-  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
-  allow_new_levels = TRUE
-) %>% 
-  as_tibble() %>% 
-  magrittr::set_colnames(pts_levels)
-
-set.seed(seed_pts_prediction)
-pred_pts_v2csreprss_rewb <- predict(
-  m_pts_v2csreprss_rewb_train, 
-  newdata = select(canary_testing_lagged, -PTS_factor_lead1),
-  allow_new_levels = TRUE
-) %>% 
-  as_tibble() %>% 
-  magrittr::set_colnames(pts_levels)
 ```
@@
 
-### Baseline model (REWB)
-
-```{r e2a-separation-baseline-rewb}
-# Match each column in pred_mat (predicted probabilities for each response level)
-pred_long_list <- lapply(1:ncol(pred_pts_baseline_rewb), 
-                         FUN = match_actual, 
-                         pred = pred_pts_baseline_rewb, 
-                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
-
-plot_data <- pred_long_list %>% 
-  bind_rows() %>% 
-  filter(!is.nan(fitted), !is.na(actual)) %>% 
-  group_by(plot_level) %>% 
-  arrange(plot_level, fitted) %>% 
-  mutate(index = row_number()) %>% 
-  ungroup()
-
-markers <- plot_data %>% 
-  group_by(plot_level) %>%
-  summarize(obs = n(), expected = sum(fitted),
-            marker = obs - expected + 1)
-
-n_in_group <- nrow(pred_pts_baseline_rewb)
-
-plot_data_condensed <- plot_data %>% 
-  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
-  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
-  mutate(rleid = cumsum(rleid)) %>% 
-  group_by(plot_level, rleid) %>% 
-  slice(1) %>% 
-  group_by(plot_level) %>% 
-  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
-  ungroup()
-
-ggplot(plot_data_condensed) +
-  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
-  geom_line(aes(x = index, y = fitted), size = 0.3) +
-  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
-  scale_fill_manual(values = c("grey90", "#2ECC40")) +
-  guides(fill = FALSE) +
-  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
-  theme_void(base_family = "Inter Bold")
-```
-
-### Model with civil society repression (REWB)
-
-```{r e2a-separation-cs-rewb}
-pred_long_list <- lapply(1:ncol(pred_pts_v2csreprss_rewb), 
-                         FUN = match_actual, 
-                         pred = pred_pts_v2csreprss_rewb, 
-                         actual = as.character(canary_testing_lagged$PTS_factor_lead1))
-
-plot_data <- pred_long_list %>% 
-  bind_rows() %>% 
-  filter(!is.nan(fitted), !is.na(actual)) %>% 
-  group_by(plot_level) %>% 
-  arrange(plot_level, fitted) %>% 
-  mutate(index = row_number()) %>% 
-  ungroup()
-
-markers <- plot_data %>% 
-  group_by(plot_level) %>%
-  summarize(obs = n(), expected = sum(fitted),
-            marker = obs - expected + 1)
-
-n_in_group <- nrow(pred_pts_v2csreprss_rewb)
-
-plot_data_condensed <- plot_data %>% 
-  # rle(), dplyr-style: https://stackoverflow.com/a/33510765/120898
-  mutate(rleid = (actual != lag(actual, 1, default = 0))) %>%
-  mutate(rleid = cumsum(rleid)) %>% 
-  group_by(plot_level, rleid) %>% 
-  slice(1) %>% 
-  group_by(plot_level) %>% 
-  mutate(xmin = index, xmax = lead(index, default = n_in_group)) %>% 
-  ungroup()
-
-ggplot(plot_data_condensed) +
-  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 1, fill = as.factor(actual))) + 
-  geom_line(aes(x = index, y = fitted), size = 0.3) +
-  geom_point(data = markers, aes(x = marker, y = -0.05), shape = 17, size = 3) + 
-  scale_fill_manual(values = c("grey90", "#2ECC40")) +
-  guides(fill = FALSE) +
-  facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
-  theme_void(base_family = "Inter Bold")
-```
-
 ## Prediction diagnostics
@@
 
-pred_pts_baseline_categories_rewb <- pred_pts_baseline_rewb %>% 
-  rownames_to_column() %>% 
-  pivot_longer(-rowname) %>% 
-  group_by(rowname) %>% 
-  filter(rank(-value, ties.method = "last") == 1) %>% 
-  ungroup() %>% 
-  select(predicted = name)
-
-pred_pts_v2csreprss_categories_rewb <- pred_pts_v2csreprss_rewb %>% 
-  rownames_to_column() %>% 
-  pivot_longer(-rowname) %>% 
-  group_by(rowname) %>% 
-  filter(rank(-value, ties.method = "last") == 1) %>% 
-  ungroup() %>% 
-  select(predicted = name)
-
 pts_cat_preds <- canary_testing_lagged %>% 
@@
 
-pts_cat_preds_rewb <- canary_testing_lagged %>% 
-  select(country, year, actual = PTS_factor_lead1) %>% 
-  mutate(pred_baseline = pred_pts_baseline_categories_rewb$predicted,
-         pred_v2csreprss = pred_pts_v2csreprss_categories_rewb$predicted) %>% 
-  filter(!is.na(actual)) %>%
-  mutate(is_correct_baseline = actual == pred_baseline,
-         is_correct_v2csreprss = actual == pred_v2csreprss)
-
 # Improved predictions
 pts_improved <- pts_cat_preds %>% 
-  filter(!is_correct_baseline & is_correct_v2csreprss) %>% 
-  select(Country = country, Year = year, Actual = actual,
-         `CS repression included` = pred_v2csreprss,
-         `Baseline` = pred_baseline)
-
-pts_improved_rewb <- pts_cat_preds_rewb %>% 
   filter(!is_correct_baseline & is_correct_v2csreprss) %>% 
@@
 
-pts_pred_table_rewb <- pts_cat_preds_rewb %>% 
-  pivot_longer(starts_with("is_correct")) %>% 
-  group_by(name, value) %>% 
-  summarize(n = n()) %>% 
-  ungroup() %>% 
-  left_join(correct_lookup, by = "name") %>% 
-  mutate(Prediction = ifelse(value == TRUE, "Correct", "Wrong")) %>% 
-  arrange(nice_name) %>% 
-  select(-name, -value) %>% 
-  pivot_wider(names_from = "nice_name", values_from = "n")
-
 pts_pred_table %>% 
-  kbl(align = "lcc") %>% 
-  kable_styling()
-
-pts_pred_table_rewb %>% 
   kbl(align = "lcc") %>% 

### 2021-07-17 R/models_clphy.R

@@ -185,152 +185,3 @@ f_clphy_v2csreprss <- function(dat) {
 
   return(model)
 }
-
-
-# REWB models -------------------------------------------------------------
-
-f_clphy_baseline_rewb <- function(dat) {
-  clphy_settings <- clphy_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clphy_lead1 ~ v2x_clphy +
-         v2x_polyarchy_within + v2x_polyarchy_between +
-         gdpcap_log_within + gdpcap_log_between +
-         un_trade_pct_gdp_within + un_trade_pct_gdp_between +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = clphy_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = clphy_settings$chains, iter = clphy_settings$iter,
-    warmup = clphy_settings$warmup, seed = clphy_settings$seed)
-
-  return(model)
-}
-
-f_clphy_total_rewb <- function(dat) {
-  clphy_settings <- clphy_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clphy_lead1 ~ barriers_total_within + barriers_total_between +
-         barriers_total_lag1_within + barriers_total_lag1_between +
-         v2x_clphy +
-         v2x_polyarchy_within + v2x_polyarchy_between +
-         gdpcap_log_within + gdpcap_log_between +
-         un_trade_pct_gdp_within + un_trade_pct_gdp_between +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = clphy_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = clphy_settings$chains, iter = clphy_settings$iter,
-    warmup = clphy_settings$warmup, seed = clphy_settings$seed)
-
-  return(model)
-}
-
-f_clphy_advocacy_rewb <- function(dat) {
-  clphy_settings <- clphy_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clphy_lead1 ~ advocacy_within + advocacy_between +
-         advocacy_lag1_within + advocacy_lag1_between +
-         v2x_clphy +
-         v2x_polyarchy_within + v2x_polyarchy_between +
[…]

### 2021-07-17 R/models_clpriv.R

@@ -185,152 +185,3 @@ f_clpriv_v2csreprss <- function(dat) {
 
   return(model)
 }
-
-
-# REWB models -------------------------------------------------------------
-
-f_clpriv_baseline_rewb <- function(dat) {
-  clpriv_settings <- clpriv_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clpriv_lead1 ~ v2x_clpriv +
-         v2x_polyarchy_within + v2x_polyarchy_between +
-         gdpcap_log_within + gdpcap_log_between +
-         un_trade_pct_gdp_within + un_trade_pct_gdp_between +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = clpriv_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = clpriv_settings$chains, iter = clpriv_settings$iter,
-    warmup = clpriv_settings$warmup, seed = clpriv_settings$seed)
-
-  return(model)
-}
-
-f_clpriv_total_rewb <- function(dat) {
-  clpriv_settings <- clpriv_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clpriv_lead1 ~ barriers_total_within + barriers_total_between +
-         barriers_total_lag1_within + barriers_total_lag1_between +
-         v2x_clpriv +
-         v2x_polyarchy_within + v2x_polyarchy_between +
-         gdpcap_log_within + gdpcap_log_between +
-         un_trade_pct_gdp_within + un_trade_pct_gdp_between +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = clpriv_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = clpriv_settings$chains, iter = clpriv_settings$iter,
-    warmup = clpriv_settings$warmup, seed = clpriv_settings$seed)
-
-  return(model)
-}
-
-f_clpriv_advocacy_rewb <- function(dat) {
-  clpriv_settings <- clpriv_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clpriv_lead1 ~ advocacy_within + advocacy_between +
-         advocacy_lag1_within + advocacy_lag1_between +
-         v2x_clpriv +
[…]

### 2021-07-17 R/models_details.R

@@ -10,13 +10,6 @@ create_model_df <- function() {
     "m_pts_funding", "Political terror", "Barriers to funding",
     "m_pts_v2csreprss", "Political terror", "Civil society repression",
 
-    "m_pts_baseline_rewb", "Political terror", "Baseline",
-    "m_pts_total_rewb", "Political terror", "Total legal barriers",
-    "m_pts_advocacy_rewb", "Political terror", "Barriers to advocacy",
-    "m_pts_entry_rewb", "Political terror", "Barriers to entry",
-    "m_pts_funding_rewb", "Political terror", "Barriers to funding",
-    "m_pts_v2csreprss_rewb", "Political terror", "Civil society repression",
-
     # Models for physical violence (v2x_clphy)
     "m_clphy_baseline", "Physical violence", "Baseline",
     "m_clphy_total", "Physical violence", "Total legal barriers",
@@ -26,13 +19,6 @@ create_model_df <- function() {
     "m_clphy_funding", "Physical violence", "Barriers to funding",
     "m_clphy_v2csreprss", "Physical violence", "Civil society repression",
 
-    "m_clphy_baseline_rewb", "Physical violence", "Baseline",
-    "m_clphy_total_rewb", "Physical violence", "Total legal barriers",
-    "m_clphy_advocacy_rewb", "Physical violence", "Barriers to advocacy",
-    "m_clphy_entry_rewb", "Physical violence", "Barriers to entry",
-    "m_clphy_funding_rewb", "Physical violence", "Barriers to funding",
-    "m_clphy_v2csreprss_rewb", "Physical violence", "Civil society repression",
-
     # Models for private civil liberties (v2x_clpriv)
     "m_clpriv_baseline", "Private civil liberties", "Baseline",
     "m_clpriv_total", "Private civil liberties", "Total legal barriers",
@@ -41,13 +27,6 @@ create_model_df <- function() {
     "m_clpriv_entry", "Private civil liberties", "Barriers to entry",
     "m_clpriv_funding", "Private civil liberties", "Barriers to funding",
     "m_clpriv_v2csreprss", "Private civil liberties", "Civil society repression",
-
-    "m_clpriv_baseline_rewb", "Private civil liberties", "Baseline",
-    "m_clpriv_total_rewb", "Private civil liberties", "Total legal barriers",
[…]

### 2021-07-17 R/models_lhr.R

@@ -185,152 +185,3 @@ f_lhr_v2csreprss <- function(dat) {
 
   return(model)
 }
-
-
-# REWB models -------------------------------------------------------------
-
-f_lhr_baseline_rewb <- function(dat) {
-  lhr_settings <- lhr_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(latent_hr_mean_lead1 ~ latent_hr_mean +
-         v2x_polyarchy_within + v2x_polyarchy_between +
-         gdpcap_log_within + gdpcap_log_between +
-         un_trade_pct_gdp_within + un_trade_pct_gdp_between +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = lhr_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = lhr_settings$chains, iter = lhr_settings$iter,
-    warmup = lhr_settings$warmup, seed = lhr_settings$seed)
-
-  return(model)
-}
-
-f_lhr_total_rewb <- function(dat) {
-  lhr_settings <- lhr_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(latent_hr_mean_lead1 ~ barriers_total_within + barriers_total_between +
-         barriers_total_lag1_within + barriers_total_lag1_between +
-         latent_hr_mean +
-         v2x_polyarchy_within + v2x_polyarchy_between +
-         gdpcap_log_within + gdpcap_log_between +
-         un_trade_pct_gdp_within + un_trade_pct_gdp_between +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = lhr_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = lhr_settings$chains, iter = lhr_settings$iter,
-    warmup = lhr_settings$warmup, seed = lhr_settings$seed)
-
-  return(model)
-}
-
-f_lhr_advocacy_rewb <- function(dat) {
-  lhr_settings <- lhr_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(latent_hr_mean_lead1 ~ advocacy_within + advocacy_between +
-         advocacy_lag1_within + advocacy_lag1_between +
-         latent_hr_mean +
-         v2x_polyarchy_within + v2x_polyarchy_between +
[…]

### 2021-07-17 R/models_pts.R

@@ -180,146 +180,3 @@ f_pts_v2csreprss <- function(dat) {
 
   return(model)
 }
-
-
-# REWB models -------------------------------------------------------------
-
-f_pts_baseline_rewb <- function(dat) {
-  pts_settings <- pts_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(PTS_factor_lead1 ~ PTS_factor +
-         v2x_polyarchy_within + v2x_polyarchy_between +
-         gdpcap_log_within + gdpcap_log_between +
-         un_trade_pct_gdp_within + un_trade_pct_gdp_between +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = cumulative(),
-    prior = pts_settings$priors_vague,
-    data = dat,
-    chains = pts_settings$chains, iter = pts_settings$iter,
-    warmup = pts_settings$warmup, seed = pts_settings$seed)
-
-  return(model)
-}
-
-f_pts_total_rewb <- function(dat) {
-  pts_settings <- pts_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(PTS_factor_lead1 ~ barriers_total_within + barriers_total_between +
-         barriers_total_lag1_within + barriers_total_lag1_between +
-         PTS_factor +
-         v2x_polyarchy_within + v2x_polyarchy_between +
-         gdpcap_log_within + gdpcap_log_between +
-         un_trade_pct_gdp_within + un_trade_pct_gdp_between +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = cumulative(),
-    prior = pts_settings$priors_vague,
-    data = dat,
-    chains = pts_settings$chains, iter = pts_settings$iter,
-    warmup = pts_settings$warmup, seed = pts_settings$seed)
-
-  return(model)
-}
-
-f_pts_advocacy_rewb <- function(dat) {
-  pts_settings <- pts_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(PTS_factor_lead1 ~ advocacy_within + advocacy_between +
-         advocacy_lag1_within + advocacy_lag1_between +
-         PTS_factor +
-         v2x_polyarchy_within + v2x_polyarchy_between +
-         gdpcap_log_within + gdpcap_log_between +
-         un_trade_pct_gdp_within + un_trade_pct_gdp_between +
-         armed_conflict +
[…]

### 2021-07-17 _targets.R

@@ -158,13 +158,6 @@ list(
   tar_target(m_pts_funding, f_pts_funding(panel_lagged)),
   tar_target(m_pts_v2csreprss, f_pts_v2csreprss(panel_lagged)),
 
-  tar_target(m_pts_baseline_rewb, f_pts_baseline_rewb(panel_lagged)),
-  tar_target(m_pts_total_rewb, f_pts_total_rewb(panel_lagged)),
-  tar_target(m_pts_advocacy_rewb, f_pts_advocacy_rewb(panel_lagged)),
-  tar_target(m_pts_entry_rewb, f_pts_entry_rewb(panel_lagged)),
-  tar_target(m_pts_funding_rewb, f_pts_funding_rewb(panel_lagged)),
-  tar_target(m_pts_v2csreprss_rewb, f_pts_v2csreprss_rewb(panel_lagged)),
-
   ## Models using training data
   tar_target(m_pts_baseline_train, f_pts_baseline(panel_training_lagged)),
   tar_target(m_pts_total_train, f_pts_total(panel_training_lagged)),
@@ -172,13 +165,6 @@ list(
   tar_target(m_pts_entry_train, f_pts_entry(panel_training_lagged)),
   tar_target(m_pts_funding_train, f_pts_funding(panel_training_lagged)),
   tar_target(m_pts_v2csreprss_train, f_pts_v2csreprss(panel_training_lagged)),
-
-  tar_target(m_pts_baseline_rewb_train, f_pts_baseline_rewb(panel_training_lagged)),
-  tar_target(m_pts_total_rewb_train, f_pts_total_rewb(panel_training_lagged)),
-  tar_target(m_pts_advocacy_rewb_train, f_pts_advocacy_rewb(panel_training_lagged)),
-  tar_target(m_pts_entry_rewb_train, f_pts_entry_rewb(panel_training_lagged)),
-  tar_target(m_pts_funding_rewb_train, f_pts_funding_rewb(panel_training_lagged)),
-  tar_target(m_pts_v2csreprss_rewb_train, f_pts_v2csreprss_rewb(panel_training_lagged)),
 
   # Models for physical violence (v2x_clphy)
   ## Models using full data
@@ -190,13 +176,6 @@ list(
   tar_target(m_clphy_funding, f_clphy_funding(panel_lagged)),
   tar_target(m_clphy_v2csreprss, f_clphy_v2csreprss(panel_lagged)),
 
[…]

### 2021-07-17 manuscript/manuscript.Rmd
Suparna edits

@@
 abstract: >-
-  Many countries across the globe have increasingly cracked down on NGOs over the last few decades.
-These attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding.
+  An increasing number of countries cracked down on NGOs over the last few decades.
+These attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding in the future.
 This is especially the case for electoral democracies, which unlike autocracies, may not aggressively attack civic space.
 In this paper, we explore if crackdowns on NGOs predict broader human rights repression.
-Anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
-These laws may also make it easier for states to prevent and deter future large-scale popular mobilization.
+Anti-NGO laws are among the most subtle means of repression and attract much less domestic and international condemnation compared to the use of violence, as many audiences mistake this repression as regulation.
+These laws may also make it easier for states to prevent future large-scale popular mobilization.
 Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, physical integrity rights violations, and violations of private civil liberties.
-We find that while formal de jure laws provide little information in predicting future repression, de facto civil society repression predicts worsening respect for physical integrity rights and civil liberties.
-keywords: "civil society restrictions, human rights, political terror, civil liberties"
+We find that while formal de jure laws provide little information in predicting future repression, their patterns of implementation or de facto civil society repression predicts worsening respect for physical integrity rights and civil liberties.
+keywords: "civil society, NGOs, repression, human rights, political terror, civil liberties"
 thanks: >-
-  We would like to thank participants of the 2021 International Studies Association (ISA) convention for their comments and feedback.
+  We would like to thank participants of the 2021 International Studies Association (ISA) convention, and the Human Rights on the Edge: The Future of International Human Rights Law and Practice hosted by the Global Human Rights Hub at Arizona State University for their comments and feedback.
 reference-section-title: References
@@
 
-Governments across the globe have been cracking down on civil society organizations (CSOs), a phenomenon commonly referred to the closing or shrinking of civic space [@CarothersBrechenmacher:2014; @DPR:2016; @Chaudhry:2016; @DupuyPrakash:2018].
-The last two decades have seen a proliferation of steps designed to limit the influence of CSOs and non-governmental organizations (NGOs), and more than 100 countries have proposed or enacted 244 measures restricting, repressing, or shutting down civil society since 2013 [@icnl:2021].
+Over the last few decades, governments across the globe have been increasinly cracking down on civil society organizations (CSOs), particularly non-governmental organizations (NGOs) -- a phenomenon commonly referred to the closing or shrinking of civic space [@CarothersBrechenmacher:2014; @DPR:2016; @Chaudhry:2016; @DupuyPrakash:2018].
+More than 100 countries have proposed or enacted 244 measures restricting, repressing, or shutting down civil society since 2013 [@icnl:2021].
 In Human Rights Watch's 2016 World Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory, and over the past decade, the majority of the world has seen a substantial narrowing of allowable civic space.
-As seen in Figure \@ref(fig:civicus-map), by the end of 2020, only `r civicus$Open$prop_nice` of countries had open and unrestricted civil societies [@civicusmonitor; @ChaudhryHeiss:2021].
+As seen in Figure \@ref(fig:civicus-map), by the end of 2020, only `r civicus$Open$prop_nice` of countries had open and unrestricted civil societies [@civicusmonitor; @ChaudhryHeiss:2021].[^open]
 
@@
 This hostility to civil society is not unique to autocratic governments or even illiberal democracies [@AbramowitzSchenkkan:2018]—long-established liberal democracies have also increased restrictions on civil society in their countries.
-Over the past decade, India has canceled the licenses of tens of thousands of NGOs, targeted major groups such as Greenpeace International and Ford Foundation, and has banned 5,000 NGOs from receiving foreign funds [@press-trust-india:2015; @press-trust-india:2019].
-In 2013 Canada attempted to revoke the charitable status of civil society organizations for opposing the Northern Gateway pipeline and Canadian mining companies' initiatives abroad [@CIVICUS:2013].
+Over the past decade, India has canceled the licenses of tens of thousands of NGOs, targeted major groups such as Greenpeace International, Amnesty International and Ford Foundation, and has banned 5,000 NGOs from receiving foreign funds [@press-trust-india:2015; @press-trust-india:2019].
+In 2013 Canada attempted to revoke the charitable status of NGOs for opposing the Northern Gateway pipeline and Canadian mining companies' initiatives abroad [@CIVICUS:2013].
 In 2019, activists from the US-based nonprofit No More Deaths were arrested for providing food and water to migrants a the US-Mexico border and faced a 20-year prison sentence before their convictions were overturned in 2020 [@Cramer:2020].
 
-Anti-civil society measures are occasionally violent, but recently, government repression of NGOs has generally been non-violent.
+Much of this targeting of NGOs has been non-violent.
 Rather than publicly arrest or beat activists, states implement "administrative crackdown," or the passage of laws to create barriers to NGO advocacy, entry, and funding [@Chaudhry:2016].
 The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations [@Heiss:2019; @Heiss:2017].
-While in some cases this has led to the depoliticization of NGOs and avoidance of direct political activism by CSOs, states cannot soften or neutralize all forms of political activities in subtle, legal ways like they have with NGOs.
-Sooner or later, states need to deal with threats to their stability in a more direct, violent, confrontational manner.
-Administrative NGO laws and general civil society repression could be an important early warning sign—or a canary in the coal mine—of worsening human rights repression in a state, signaling that a state will continue down the path of further repression.
+While this can lead to the depoliticization and avoidance of direct political activism by CSOs,[CITE] states cannot soften or neutralize all forms of political activity and advocacy in subtle, legal ways like they have with NGOs.
+Sooner or later, states may need to deal with threats to their stability in a more direct, violent, confrontational manner.
+Anti-NGO laws and repression of CSOs could be an important early warning sign—or a canary in the coal mine—of worsening human rights repression in a state, signaling that a state will continue down the path of further repression.
 What does state targeting of NGOs tell us about the state's broader respect for civil society and the overall level of human rights repression?
-Can the crackdown on NGOs act as an indicator for subsequent increasing repression?
+Can the crackdown on NGOs act as a predictor of subsequent increasing repression?
 
@@
 We argue that information about NGO crackdown can be a valuable indicator of human rights trajectories.
-In some cases, such crackdown can act as an early warning signal for worsening repression, suggesting which countries are testing the waters with comparatively "milder" methods of crackdown before enacting more violent forms of repression.
+It can act as an early warning signal for worsening repression, suggesting which countries are testing the waters with comparatively "milder" methods of crackdown before enacting more violent forms of repression.
 To assess if attacks on NGOs and activists can provide us useful information about future repression, we use an original dataset on state crackdown on NGOs using legal repression across all countries from 1990–2013.
-We differentiate between two forms of civil society repression: official de jure anti-NGO restrictions that are codified in law, and general de facto levels of civil society repression.
-We propose and test two empirical expectations—that de jure and de factor restrictions predict future political terror, physical integrity rights violations, and government encroachment on private civil liberties.
-
+We differentiate between two forms of NGO repression: official de jure anti-NGO restrictions that are codified in law, and their de facto implementation.
 Using multilevel Bayesian modeling, we find that formal de jure laws provide very little additional information when attempting to predict future repression.
-However, we find that accounting for more general civil society repression does boost our models' predictive power.
+However, we find that accounting for their implementation does boost our models' predictive power.
 Increasing de facto civil society repression predicts an increase in the probability of moderate political terror and results in worsening violations of physical integrity rights and civil liberties.
@@
 As such, they may not be particularly suitable for forecasting short-term trajectories, especially for moderately repressive countries.
-On the other hand, state repression of NGOs is more dynamic and provides information about changing levels of human rights standards and repression in subsequent years.
+On the other hand, state repression of NGOs is more dynamic process than may provide insight into changing levels of human rights standards and repression in subsequent years.
+While recent research has made important contributions to studying the extent and effects of state crackdown on NGOs, much of this focuses on de jure restrictions and its impact on NGOs and donors.[CITE] By looking at both laws, as well as their implementation when combined with extra-legal means, we are able to assess the long-term effects of closing civic space on broader patterns of repression as well.
 
@@
 Using both original data as well as data from several existing datasets, we build an ensemble of predictive models and explore (1) the marginal effects of civil society repression on different forms of broader human rights repression, and (2) the out-of-sample predictive performance of each model.
-We conclude with a discussion of our findings and their implications for assessing the repression of human rights.
+We conclude by discussing the implications of our findings on the role of NGOs in the international community and prospects of democratic backsliding.
 
@@
 Repression is the use of coercive action against an individual or organization, within the territorial jurisdiction of the state, for the purpose of imposing a cost on the target as well as deterring specific activities and/or beliefs perceived to be challenging to government personnel, practices, or institutions [@Goldstein:1978, p.
-xxvii; @PoeTate:1994; @Davenport:2007; and @RitterConrad:2016].
-
+xxvii; @Davenport:2007, 487; and @RitterConrad:2019, 15].
 Early literature on repression focused on the role of structural factors such as levels of democracy, economic development, electoral competitiveness in predisposing a state to increased use of repression.
@@
 In addition to attacking groups willingness to organize against states, such preventive repression also damages states' capacity to impose costs [@Davenport:2007a, 47].
-NGOs are one actor that can pose challenges to political authorities, and state repression of these actors, especially through legal restrictions or administrative crackdown can also be considered a form of preventive repression [@Chaudhry:2016].
-
-A robust, strong civil society is widely considered as an important component on democratic transition and consolidation [@Putnam:1994].
-Politically, as important civil society actors, NGOs enable citizens to voice their grievances, seek redress, and carry out lobbying and advocacy activities to further their interests.
-They help keep government accountable, monitor human rights violations and corruption.
-From an economic perspective, NGOs provide services when the state falls short.
-As a result of these roles, NGOs can wield real influence, which can be threatening to states.
-State crackdown on NGOs has become pervasive as these organizations have the ability to influence electoral politics [@DPR:2016; @Weiss:2009], aid mobilization [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
-
-There is no doubt that violence is often effective at curbing dissent.
-But it can also backfire, leading to widespread protests, decreasing leaders' legitimacy and increasing their criminal liability [@KimSikkink:2010; @Sikkink:2011].
+NGOs are one actor that can pose challenges to political authorities, and state repression of these actors, especially through legal restrictions can be considered a form of preventive repression [@Chaudhry:2016].
+
+While many saw the initial proliferation of NGOs as leading to a "symbiotic relationship" between NGOs and states due to their mutual goals, this perception changed over time (Reimann 2006, 63).
+With expanded powers and their perceived role in the Color Revolutions, NGOs began to be seen as having a real influence.
+(CITE) State crackdown on NGOs became pervasive as these organizations have the ability to influence electoral politics [@DPR:2016; @Weiss:2009], aid mobilization [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
+
+Given this threat, a number of states decided to repress threatening NGOs.
+While violence is often effective at curbing dissent, it can also backfire, leading to widespread protests, decreasing leaders' legitimacy and increasing their criminal liability [@KimSikkink:2010; @Sikkink:2011].
 In contrast to violence, administrative crackdown has fewer adverse consequences—citizens may see it as regulation rather than repression, resulting in little to no counter-mobilization.
@@
 
-We argue that crackdown on NGOs foreshadows future government transgressions.
+This administrative crackdown via anti-NGO laws may foreshadow future government transgressions.
 Autocratic leaders want to avoid accountability, and NGOs often stand in conflict with that goal.
@@
 Such repression reflects the government's willingness and capability to use measures that can make it avoid accountability.
-Once a state targets NGOs, over time it may grow less hesitant to apply repression more widely and more severely.
+Once a state targets NGOs, over time it may grow less hesitant to apply violent repression more widely and more severely.
 
@@
 Rather, the law would be a "weapon hanging on the wall that never fires" and stand as a warning to potentially uncooperative NGOs [@Kozenko:2015].
+Similarly, Egypt's 2002 NGO law instated severe barriers to freedom of association, banned NGOs from engaging in activities that "threaten national unity or violate public order or morality," and also prevented groups for receiving foreign funding.
+But despite the harsh legal framework, the NGO sector nearly doubled in size between 1993-2011.
+This was because of the state's limited targeting of groups working on politically sensitive issues such as human rights and democracy, while tolerating other kinds of organizations (@Brechenmacher 2017).
 
@@
 
-To measure de jure repression, we use data on anti-NGO laws from @Chaudhry:2016 which includes official NGO laws for 162 countries between 1990 and 2013.
-We create indexes of the total number of laws passed in each country based on three broad categories of laws related to barriers to entry, funding, and advocacy, and we also sum each of these indexes to create a count of total legal barriers.
+To measure de jure repression, we use data on anti-NGO laws from @Chaudhry:2016 which includes official NGO laws for all countries (excluding micro-states) between 1990 and 2013.
+We create indeces of the total number of laws passed in each country based on three broad categories of laws related to barriers to entry, funding, and advocacy, and we also sum each of these indeces to create a count of total legal barriers.
 We also create a yearly indicator variable to show if a country increased its count of anti-NGO laws (models using this outcome are included in the online appendix).
@@
 
-As mentioned previously, simply counting the number of NGO laws does not necessarily capture the restrictiveness of the general civil society environment in a country.
-Governments might repress civil society without formal laws or pass restrictive laws that they can keep in reserve for later emergencies.
-To measure the general level of civil society repression in a country, we use V-Dem's CSO repression indicator (`v2csreprss` in @vdem-v10), which captures the extent to which governments harass, deter, liquidate, and arrest members of civil society organizations.
-Figure \@ref(fig:barriers) shows each of these types of legal barriers per country over time, as well as average levels of civil society repression by regime type.
-While anti-NGO laws have increased steadily since 1990—particularly laws related to foreign funding—there has not necessarily been a corresponding rise in civil society repression, which has remained fairly constant across different regime types.
+To measure de facto civil society repression in a country, we use Varieties of Democracy's (V-Dem) CSO repression indicator (`v2csreprss` in @vdem-v10), which captures the extent to which governments harass, deter, liquidate, and arrest members of civil society organizations.
+Figure \@ref(fig:barriers) shows each of these types of legal barriers per country over time, as well as average levels of de facto civil society repression by regime type.
+While anti-NGO laws have increased steadily since 1990—particularly laws related to foreign funding—there has not necessarily been a corresponding rise in de facto civil society repression, which has remained fairly constant across different regime types.
 This divergence is likely indicative of the split between de jure laws and their de facto implementation—a rise in laws is not necessarily tied to direct CSO repression.
@@
 First, following @GohdesCarey:2017, who use the killing of journalists to predict worsening human rights conditions, we use the Political Terror Scale (PTS), which assigns countries to five different categories of repression each year [@GibneyCornettWood:2019], with Level 5 representing widespread political violence, including arrests, political murders, disappearances, and torture.
-As seen in the left panel of Figure \@ref(fig:repression), the number of countries at Level 5 has decreased since the 1990s, while most countries are coded as Levels 2 and 3.
+As seen in the left panel of Figure \@ref(fig:repression), the number of countries at Level 5 has decreased since the 1990s, while most countries are coded as Levels 2 and 3 (moderate levels of political terror).
 
@@
 
-Our main question in this paper is whether civil society laws and restrictions serve as an early warning signal to other future forms of repression.
-As such, we are primarily interested in *predicting* repression and not isolating the causal effect of civil society repression on general human rights abuses.
+Since we look at whether anti-NGO laws and their implementation can serve as an early warning signal for broader repression, we are primarily interested in *predicting* repression and not isolating the causal effect of civil society repression on general human rights abuses.
 We do not include a complete set of covariates to remove confounding relationships, but instead use a more parsimonious set of explanatory variables that strongly predict repression.
@@
 Additionally, as a robustness check, we account for within-country and between-country variation by splitting each numeric explanatory variable into its country-level mean and its variation from the mean, following @BellJones:2015.
-The results from these random effects—within/between (REWB) models are nearly identical to those with the untransformed covariates, so for the sake of simplicity here, we only include results from basic multilevel random effects models.
+[@TODO: Footnote this REWB stuff] The results from these random effects—within/between (REWB) models are nearly identical to those with the untransformed covariates, so for the sake of simplicity here, we only include results from basic multilevel random effects models.
 
@@
 - **Expectation 1~b~**: Anti-NGO laws signal worsening physical violence
-- **Expectation 1~c~**: Anti-NGO laws signal constricting private civil liberties
-- **Expectation 1~d~**: Anti-NGO laws signal decreasing latent human rights
+- **Expectation 1~c~**: Anti-NGO laws signal constricting civil liberties
+- **Expectation 1~d~**: Anti-NGO laws signal decreasing latent human rights respect
 - **Expectation 2~a~**: Civil society repression signals worsening political terror
 - **Expectation 2~b~**: Civil society repression signals worsening physical violence
-- **Expectation 2~c~**: Civil society repression signals constricting private civil liberties
-- **Expectation 2~d~**: Civil society repression signals decreasing latent human rights
+- **Expectation 2~c~**: Civil society repression signals constricting civil liberties
+- **Expectation 2~d~**: Civil society repression signals decreasing latent human rights respect
 
@@
 As V-Dem's physical violence index and private civil liberties index and latent human rights values are all measured continuously, we predict these values with Gaussian models.
-We use median values from the models' posterior distributions as our point estimates and provide credible intervals using the 95% highest posterior density.[^bayes] We declare an effect statistically "significant" if the posterior probability of being different from zero exceeds 0.95.
+We use median values from the models' posterior distributions as our point estimates and provide credible intervals using the 95% highest posterior density.[^bayes] We declare an effect statistically "significant" if the posterior probability of being different from zero (i.e.
+above or below) exceeds 0.95.
+
+[^open]: Defined as the state both enabling and safeguarding citizens' freedom to form associations, authorities being tolerant of criticism from CSOs and laws governing freedom of peaceful assembly adhere to international laws and standards.
 
@@
 
-Complete results from all the models (including REWB models), along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion website at <https://stats.andrewheiss.com/canary-ngos/>.
+@TODO: FOOTNOTE or APPENDIX: Complete results from all the models (including REWB models), along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion website at <https://stats.andrewheiss.com/canary-ngos/>.
 Our general modeling approach can be summarized as follows:
@@
 We present the results of our models in two stages.
-First, in order to see how minor shifts in civil society laws and repression influence future human rights, we examine the marginal effects of our main explanatory variables when all other model covariates are held constant.
-These effects are by no means causal—rather, they demonstrate how much variation in predicted human rights is possible as the legal environment for civil society shifts up and down within a typical country.
+First, to see how minor shifts in civil society laws and repression influence future human rights, we examine the marginal effects of our main explanatory variables when all other model covariates are held constant.
+These effects are by no means causal—rather, they demonstrate how much variation in predicted human rights is possible as the legal environment for civil society improves or deteriorates within a typical country.
 Second, we present predictive diagnostics for each of our models to examine the improvements in predictions.
@@
 Specifically, in addition to measuring the scope and intensity of government violence, the PTS scale also looks at the proportion of population targeted for abuse.
-Countries that receive a 5 are rare, as this score captures physical abuses routinely perpetrated against citizens not involved in politics, and includes cases where governments engage in "scorched earth" counterinsurgency policies or summary executions based on class or ethnic affiliation [@GibneyCornettWood:2019].
+Countries that receive a 4 and 5 are rare, as 4 denotes that murders, disappearances, and torture are a common part of life, while 5 denotes that physical abuses routinely perpetrated against citizens not involved in politics, and includes cases where governments engage in "scorched earth" counterinsurgency policies or summary executions based on class or ethnic affiliation [@GibneyCornettWood:2019].
 The majority of movement across PTS categories should thus occur between Levels 1–3.
@@
 Each barrier-based posterior coefficient is essentially zero with narrow credible intervals that include large proportions of both negative and positive values.
-The marginal effects of additional laws on physical violence appear to show a positive relationship—that additional laws lead to less violence in the future—but the uncertainty in these estimates eliminates such an interpretation.
 Within the categories of anti-NGO laws, it appears that additional advocacy and entry laws might reduce future violence, but again, these predictions are indistinguishable from each other.
@@
 When looking at other specific forms of political repression, though, such as physical violence and private civil liberties, NGO legal barriers do not change predicted values in any meaningful way.
-But looking more broadly, civil society laws are associated with a worse predicted underlying human rights environment.
 
@@
 
-The weak (or even non-existent) predictive power of formal NGO laws is likely attributable to fact that de jure NGO legislation is rare and slow-moving and not always explicitly linked to repression—again, states that engage in political repression can do so with or without legal justification.
+The weak (or even non-existent) predictive power of formal NGO laws is likely attributable to fact that de jure NGO legislation may take time to implement - many states need to first establish institutions that oversee the operation and funding of these groups or incorporate threatening NGOs into the regime apparatus (Naim 2007).
+Further, states that engage in political repression can do so with or without legal justification.
 De facto civil society repression, on the other hand, represents the actual implementation of anti-NGO strategies—both legal and extralegal—and might be more indicative of future human rights abuses.
@@
 
-The effect of civil society repression on predicted values of the Political Terror Scale mirrors what we found previously with our first empirical expectation.
+The effect of de facto civil society repression on predicted values of the Political Terror Scale mirrors what we found previously with our first empirical expectation.
 As seen in Figure \@ref(fig:plot-mfx-e2a), at the lowest levels of repression, Levels 1 and 2 are the most common predicted outcomes and are each equiprobable at roughly 50%.
@@
 
-When holding all other factors equal, the de factor implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passing of formal de jure laws.
-Increasing civil society repression in countries with low levels of political terror can again potentially serve as a weak signal of more a more general increase in political violence in the future, while crackdowns on civil society predict more substantial changes in physical integrity rights, threats to civil liberties, and latent respect for human rights more broadly.
+When holding all other factors equal, the de facto implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passing of formal de jure laws.
+In countries with low levels of political terror, it can potentially serve as a weak signal of a more general increase in political violence in the future, but predict more substantial changes in physical integrity rights, threats to civil liberties, and latent respect for human rights.
+The difference in the effects of de jure laws v/s.
+their de facto implementation could also potentially be explained by the time frame of these strategies.
+De jure laws are a long-term strategy to prevent threats to the regime from coalescing in the first place.
+For instance, Egypt's NGO law had been on the books since 2002, but only over the past five years have post-revolutionary regimes used it more broadly (CITATION).
+As such, the long-term effects of these laws in terms of their predictive power may require a much longer time period under study.
+In contrast, de fact crackdown on NGOs may signal the need to react sooner due to the immediacy of the threat.
 
@@
 They do not show how well these models work with actual data.
-Following @WardBeger:2017 and @GohdesCarey:2017, test the predictive power of both sets of our models using out-of-sample prediction.
+Following @WardBeger:2017 and @GohdesCarey:2017, we test the predictive power of both sets of our models using out-of-sample prediction.
 We divide our complete data into a training set and a test set—the training set includes data from all countries from 1990–2010, and the test set includes the last three years of data (2011–2013).
@@
 
-When looking at the level of physical violence in a country, including civil society laws and repression also does very little to improve predictive accuracy.
+When looking at the level of physical violence in a country, including de jure and de facto repression does very little to improve predictive accuracy.
 As Table \@ref(tab:tbl-rmse) shows, accounting for legal barriers and civil society repression only reduces the RMSE by at most 0.4% compared to the baseline model.
 This is likely related to the lack of improvements in predicting political terror—both indexes measure similar phenomena.
-Similarly, accounting for civil society repression when modeling latent human rights only results in slight changes to the RMSE.
+Similarly, accounting for de facto civil society repression when modeling latent human rights only results in slight changes to the RMSE.
 However, including civil society-related predictors when modeling private civil liberties does result in small gains in accuracy, reducing the RMSE by as much as 2% compared to the baseline model.
@@
 Strengthening civil society is an important precondition for democratic transition and consolidation.
-It keeps governments accountable and protects civilians from the worst excesses of an abusive government.
 When governments restrict civil society, it reduces these organizations' ability to maintain accountability and protect against abuse.
-Given these potential knock-on effects, in this paper, we posited that the ongoing global crackdown on civil society could predict worsening human rights in a country interested in political and civil repression.
-Passing restrictive laws, imposing barriers to NGO advocacy, entry, and funding, and arresting and expelling NGO staff could pave the way for future repression.
-
-We outline two empirical expectations: that (1) official de jure anti-NGO laws and (2) general de facto civil society restrictions would predict future repression in a country, including political terror, physical violence, and violations of private civil liberties.
-We find little support for the predictive power of de jure restriction.
+Given these potential knock-on effects, in this paper, we posited that the ongoing global crackdown on NGOs could predict worsening human rights abuses and levels of political and civil rights repression.
+Using original data on de jure and de facto NGO repression from 1990-2013, we find little support for the predictive power of de jure restriction on political terror, physical violence, and violations of private civil liberties.
 Marginal predictions show that, all else held equal, adding new anti-NGO laws increases the probability of seeing moderate levels of political terror, but does not change predicted values of physical integrity or civil liberties rights violations.
@@
 
-We do, however, find some predictive power when accounting for general civil society restrictions.
-As with formal laws, rising civil society repression tends to increase the probability of more moderate political terror.
-Additionally, increasing civil society repression is associated with worsening respect for physical integrity rights and civil liberties in the future.
+We do, however, find some predictive power when accounting for de facto levels of NGO repression, which includes both legal and extra-legal means of crackdown.
+As with formal laws, rising NGO repression tends to increase the probability of more moderate political terror.
+Additionally, this repression is associated with worsening respect for physical integrity rights and civil liberties in the future.
 In out-of-sample predictions, including civil society restrictions improves model accuracy by 1–2% over the baseline.
 
-Importantly, the lack of predictive power when modeling political violence and the modest improvements in predictive power when modeling civil liberties likely reflects the purpose of civil society restrictions.
+Importantly, the lack of predictive power when modeling political violence and the modest improvements in predictive power when modeling civil liberties likely reflects the purpose of NGO restrictions.
 Encroachments on private civil liberties such as restricting freedom of association are not nearly as violent as events like government-sponsored murders.

### 2021-07-20 manuscript/manuscript.Rmd
More edits by me

@@
 ---
-title: "Canary in the Coal Mine? Civil Society Repression as a Predictor of Human Rights Abuses"
-short-title: "Canary in the Coal Mine"
+title: "Civil Society Repression as a Predictor of Worsening Human Rights Abuses"
+short-title: "Civil Society Repression"
 author:
@@
   url: https://www.andrewheiss.com/
-date: "April 12, 2021"
-published: This is an early draft of a working paper.
+date: "July 17, 2021"
+published: Under review
 code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/canary-ngos/>"
@@
 thanks: >-
-  We would like to thank participants of the 2021 International Studies Association (ISA) convention, and the Human Rights on the Edge: The Future of International Human Rights Law and Practice hosted by the Global Human Rights Hub at Arizona State University for their comments and feedback.
+  We would like to thank participants of the 2021 International Studies Association (ISA) convention, and the "Human Rights on the Edge: The Future of International Human Rights Law and Practice" workshop hosted by the Global Human Rights Hub at Arizona State University for their comments and feedback.
 reference-section-title: References
@@
 
-Over the last few decades, governments across the globe have been increasinly cracking down on civil society organizations (CSOs), particularly non-governmental organizations (NGOs) -- a phenomenon commonly referred to the closing or shrinking of civic space [@CarothersBrechenmacher:2014; @DPR:2016; @Chaudhry:2016; @DupuyPrakash:2018].
-More than 100 countries have proposed or enacted 244 measures restricting, repressing, or shutting down civil society since 2013 [@icnl:2021].
+Over the last few decades, governments across the globe have been increasingly cracking down on civil society organizations (CSOs), particularly non-governmental organizations (NGOs)—a phenomenon commonly known as closing civic space [@CarothersBrechenmacher:2014; @DPR:2016; @Chaudhry:2016; @DupuyPrakash:2018].
+More than 100 countries have proposed or enacted 244 different measures that have restricted, repressed, or shut down civil society since 2013 [@icnl:2021].
 In Human Rights Watch's 2016 World Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory, and over the past decade, the majority of the world has seen a substantial narrowing of allowable civic space.
@@
   coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
-  scale_fill_viridis_d(option = "plasma", end = 0.9, 
+  scale_fill_viridis_d(option = "rocket", direction = -1,
                        na.translate = FALSE, name = "Civic space") +
@@
 The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations [@Heiss:2019; @Heiss:2017].
-While this can lead to the depoliticization and avoidance of direct political activism by CSOs,[CITE] states cannot soften or neutralize all forms of political activity and advocacy in subtle, legal ways like they have with NGOs.
+While this can lead to the depoliticization and avoidance of direct political activism by CSOs [@Bush:2015], states cannot soften or neutralize all forms of political activity and advocacy in subtle, legal ways like they have with NGOs.
 Sooner or later, states may need to deal with threats to their stability in a more direct, violent, confrontational manner.
@@
 On the other hand, state repression of NGOs is more dynamic process than may provide insight into changing levels of human rights standards and repression in subsequent years.
-While recent research has made important contributions to studying the extent and effects of state crackdown on NGOs, much of this focuses on de jure restrictions and its impact on NGOs and donors.[CITE] By looking at both laws, as well as their implementation when combined with extra-legal means, we are able to assess the long-term effects of closing civic space on broader patterns of repression as well.
+While recent research has made important contributions to studying the extent and effects of state crackdown on NGOs, much of this focuses on de jure restrictions and its impact on NGOs and donors [@christensen2013; @BromleySchoferLonghofer:2020; @BakkeMitchellSmidt:2020; @SmidtPereraMitchell:2021].
+By looking at laws *and* their implementation, as well as the extra-legal treatment of NGOs, we are able to assess the long-term effects of closing civic space on broader patterns of repression.
 
@@
 Repression is the use of coercive action against an individual or organization, within the territorial jurisdiction of the state, for the purpose of imposing a cost on the target as well as deterring specific activities and/or beliefs perceived to be challenging to government personnel, practices, or institutions [@Goldstein:1978, p.
-xxvii; @Davenport:2007, 487; and @RitterConrad:2019, 15].
+xxvii; @Davenport:2007, 487; and @ConradRitter:2019, 15].
 Early literature on repression focused on the role of structural factors such as levels of democracy, economic development, electoral competitiveness in predisposing a state to increased use of repression.
@@
 
-While many saw the initial proliferation of NGOs as leading to a "symbiotic relationship" between NGOs and states due to their mutual goals, this perception changed over time (Reimann 2006, 63).
-With expanded powers and their perceived role in the Color Revolutions, NGOs began to be seen as having a real influence.
-(CITE) State crackdown on NGOs became pervasive as these organizations have the ability to influence electoral politics [@DPR:2016; @Weiss:2009], aid mobilization [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
+While many saw the initial proliferation of NGOs as leading to a "symbiotic relationship" between NGOs and states due to their mutual goals, this perception changed over time [@Reimann:2006, 63].
+With expanded powers and their perceived role in the Color Revolutions, NGOs began to be seen as having a real influence on domestic and international politics [@CarothersBrechenmacher:2014].
+State crackdown on NGOs became pervasive as these organizations have the ability to influence electoral politics [@DPR:2016; @Weiss:2009], aid mobilization [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
 
@@
 In exploring the impact of state crackdown on NGOs on subsequent human rights conditions, we look at both *de jure* measures—or formal legislation that seeks to repress NGOs—as well as the *de facto* implementation of these measures.
-This distinction is important.
-While states may pass anti-NGO laws, these laws can also lie dormant.
+This distinction is important—while states may pass anti-NGO laws, these laws can also lie dormant until governments feel the need to enforce them.
 For instance, Russia passed its 2015 Undesirable Organizations Law with the purpose of targeting and eliminating specific foreign-connected NGOs it deemed dangerous.
@@
 Similarly, Egypt's 2002 NGO law instated severe barriers to freedom of association, banned NGOs from engaging in activities that "threaten national unity or violate public order or morality," and also prevented groups for receiving foreign funding.
-But despite the harsh legal framework, the NGO sector nearly doubled in size between 1993-2011.
-This was because of the state's limited targeting of groups working on politically sensitive issues such as human rights and democracy, while tolerating other kinds of organizations (@Brechenmacher 2017).
+But despite the harsh legal framework, the NGO sector nearly doubled in size between 1993–2011.
+The state targeted a limited number of organizations working on politically sensitive issues such as human rights and democracy, while simultaneously tolerating organizations working on tamer issues [@Brechenmacher:2017].
 
@@
 
-Based on these purposes of civil society restrictions and the different methods states use to implement them, we propose two empirical expectations about the relationship between civil society repression and general human rights:
+Based on these various purposes of civil society restrictions and the different methods states use to implement them, we propose two empirical expectations about the relationship between civil society repression and general human rights:
 
@@
   "Private civil liberties index", NA, "0–1; higher values indicate greater respect for civil liberties", "(ref:vdem); v2x_clpriv",
-  "Latent human rights values", NA, "≈ -3–5; higher values indicate greater respect for human rights", "(ref:lhr)",
+  "Latent human rights values", NA, "≈ −3–5; higher values indicate greater respect for human rights", "(ref:lhr)",
   "Total legal barriers", "De jure laws", "Count of all anti-NGO legal barriers", "(ref:chaudhry)",
@@
   mutate(barrier_display = str_replace(barrier_display, "XXX", "\n")) %>%
-  arrange(desc(value)) %>% 
+  arrange(year, desc(value)) %>% 
   mutate(barrier_display = fct_inorder(barrier_display, ordered = TRUE))
@@
                          color = barrier_display)) +
-  geom_line(size = 0.75) +
+  geom_line(size = 1.25) +
   expand_limits(y = c(0, 90)) +
@@
                      expand = c(0, 0)) +
-  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  scale_color_viridis_d(option = "plasma", end = 0.92, name = NULL) +
   coord_cartesian(xlim = c(1990, 2015), ylim = c(0, 90)) +
@@
   theme(legend.justification = "left",
-        legend.key.size = unit(0.7, "lines")) +
+        legend.key.height = unit(0.7, "lines"),
+        legend.key.width = unit(1, "lines")) +
   facet_wrap(vars(barrier_group))
@@
                            linetype = barrier_display)) +
-  geom_line(size = 0.75) +
+  geom_line(size = 1.25) +
   scale_y_continuous(sec.axis = sec_axis(~ . / num_countries,
@@
                      expand = c(0, 0)) +
-  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  scale_color_viridis_d(option = "plasma", end = 0.92, name = NULL) +
   scale_linetype_manual(values = c("solid", "21", "solid", "21", "solid"), name = NULL) +
@@
                             color = barrier_display)) +
-  geom_line(size = 0.75) +
+  geom_line(size = 1.25) +
   scale_y_continuous(sec.axis = sec_axis(~ . / num_countries,
@@
   theme_ngo(9) + 
-  theme(legend.justification = "left") +
+  theme(legend.justification = "left",
+        legend.key.height = unit(0.7, "lines"),
+        legend.key.width = unit(1, "lines")) +
   facet_wrap(vars(barrier_group))
@@
   geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = autocracy), alpha = 0.2,) +
-  geom_line(aes(color = autocracy), size = 0.75) +
+  geom_line(aes(color = autocracy), size = 1.25) +
   scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
@@
   theme(legend.justification = "left",
-        legend.key.size = unit(0.7, "lines")) +
+        legend.key.height = unit(0.7, "lines"),
+        legend.key.width = unit(1, "lines")) +
   facet_wrap(vars(fake_facet_title))
@@
 
-```{r repression, fig.width=7.5, fig.height=2.5, fig.asp=NULL, fig.cap="Key measures of repression over time"}
+```{r repression, fig.width=6.5, fig.height=7, fig.asp=NULL, fig.cap="Key measures of repression over time"}
 pts_plot <- canary %>% 
@@
   ggplot(aes(x = year, y = count, color = PTS_factor)) +
-  geom_line(size = 0.75) +
-  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  geom_line(size = 1) +
+  scale_color_viridis_d(option = "rocket", end = 0.85, direction = -1) +
   coord_cartesian(xlim = c(1990, 2015)) +
-  guides(color = guide_legend(nrow = 2)) +
-  labs(y = "Number of countries", x = NULL) +
+  guides(color = guide_legend(title = NULL)) +
+  labs(y = "Number of countries", x = NULL, caption = "(Higher PTS levels = more repression)") +
   theme_ngo(9) +
   theme(legend.justification = "left",
-        legend.key.size = unit(0.7, "lines")) +
+        legend.key.height = unit(0.7, "lines"),
+        legend.key.width = unit(1, "lines"),
+        plot.caption = element_text(margin = margin(t = -1, unit = "lines"))) +
   facet_wrap(vars(fake_facet_title))
@@
   geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = nice_name), alpha = 0.2,) +
-  geom_line(aes(color = nice_name), size = 0.75) +
-  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
-  scale_fill_viridis_d(option = "plasma", end = 0.8, name = NULL) +
+  geom_line(aes(color = nice_name), size = 1) +
+  scale_color_manual(values = c("#433E85", "#4DC36B"), name = NULL) +
+  scale_fill_manual(values = c("#433E85", "#4DC36B"), name = NULL) +
   coord_cartesian(xlim = c(1990, 2015)) +
-  guides(color = guide_legend(nrow = 2, reverse = TRUE),
-         fill = guide_legend(nrow = 2, reverse = TRUE)) +
-  labs(y = "Average index value\n(Higher values = less repression)", x = NULL) +
+  guides(color = guide_legend(reverse = TRUE),
+         fill = guide_legend(reverse = TRUE)) +
+  labs(y = "Average index value", x = NULL, caption = "(Higher values = less repression)") +
   theme_ngo(9) +
   theme(legend.justification = "left",
-        legend.key.size = unit(0.7, "lines")) +
+        legend.key.height = unit(0.7, "lines"),
+        legend.key.width = unit(1, "lines"),
+        plot.caption = element_text(margin = margin(t = -1, unit = "lines"))) +
   facet_wrap(vars(fake_facet_title))
@@
 lhr_plot <- ggplot(df_lhr_plot, aes(x = year, y = y)) +
-  geom_ribbon(aes(ymin = ymin, ymax = ymax), alpha = 0.2, fill = "#433E85") +
-  geom_line(size = 0.75, color = "#433E85") +
+  geom_ribbon(aes(ymin = ymin, ymax = ymax), alpha = 0.2, fill = "#FF4136") +
+  geom_line(size = 1, color = "#FF4136") +
   coord_cartesian(xlim = c(1990, 2015)) +
-  guides(color = guide_legend(nrow = 2, reverse = TRUE),
-         fill = guide_legend(nrow = 2, reverse = TRUE)) +
-  labs(y = "Average value\n(Higher values = less repression)", x = NULL) +
+  labs(y = "Average value", x = NULL, caption = "(Higher values = less repression)") +
   theme_ngo(9) +
@@
 
-(pts_plot | vdem_outcome_plot | lhr_plot) &
+(pts_plot / vdem_outcome_plot / lhr_plot) &
   theme(legend.text = element_text(size = rel(0.7)),
@@
 We extend @GohdesCarey:2017's previous modeling approach by accounting for country-level variation in repression with multilevel modeling and we include random effects for each country.
-Accounting for the country this way results in intraclass correlation coefficients of around 0.7 for each of our three outcome variables, which means that the country-based structure of the data explains more than 70% of the variation in outcome, resulting in model estimates that are arguably more precisely measured.
-Additionally, as a robustness check, we account for within-country and between-country variation by splitting each numeric explanatory variable into its country-level mean and its variation from the mean, following @BellJones:2015.
-[@TODO: Footnote this REWB stuff] The results from these random effects—within/between (REWB) models are nearly identical to those with the untransformed covariates, so for the sake of simplicity here, we only include results from basic multilevel random effects models.
-
+Accounting for country differences this way results in intraclass correlation coefficients of around 0.7 for each of our three outcome variables, which means that the country-based structure of the data explains more than 70% of the variation in outcome, resulting in model estimates that are arguably more precisely measured.
 We run multiple models for each of our empirical expectations, based on different combinations of our outcomes and key explanatory variables:
@@
 
-We generate our predictions with two families of Bayesian regression models.
+We generate predictions with two families of Bayesian regression models.
 Because the Political Terror Scale is measured as an ordered category, we use ordered logistic regression to predict future values of the PTS.
 As V-Dem's physical violence index and private civil liberties index and latent human rights values are all measured continuously, we predict these values with Gaussian models.
-We use median values from the models' posterior distributions as our point estimates and provide credible intervals using the 95% highest posterior density.[^bayes] We declare an effect statistically "significant" if the posterior probability of being different from zero (i.e.
+The appendix contains complete details of our modeling approach.
+We use median values from the models' posterior distributions as our point estimates and provide credible intervals using the 95% highest posterior density.
+We declare an effect statistically "significant" if the posterior probability of being different from zero (i.e.
 above or below) exceeds 0.95.
@@
 [^open]: Defined as the state both enabling and safeguarding citizens' freedom to form associations, authorities being tolerant of criticism from CSOs and laws governing freedom of peaceful assembly adhere to international laws and standards.
-
-[^bayes]: We use Stan [@stan] through R [@r-project] and brms [@brms-jss] to estimate our models.
-We generate 4 MCMC chains for each model with 2,000 iterations in each chain, 1,000 of which are used for warmup.
-All chains converge; we assess convergence with visual inspection.
-
-@TODO: FOOTNOTE or APPENDIX: Complete results from all the models (including REWB models), along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion website at <https://stats.andrewheiss.com/canary-ngos/>.
-Our general modeling approach can be summarized as follows:
-
-\footnotesize
-
-$$
-\begin{aligned}
-y_{i, t+1} \mid u_i, x_{i, t} \sim&\ \operatorname{Ordered Logistic}(y^*_{i, t + 1}, \sigma^2_m) & \text{[likelihood for ordinal PTS models]} \\
-y_{i, t+1} \mid u_i, x_{i, t} \sim&\ \mathcal{N}(y^*_{i, t + 1}, \sigma^2_m) & \text{[likelihood for Gaussian V-Dem models]} \\
-y^*_{i, t + 1} =&\ \beta_0 + \beta_1 \text{Civil society repression}_{i, t} + & \text{[model with covariates]}\\
-&\ \beta_2 \text{Civil society repression}_{i, t - 1} + \\
-&\ \beta_3 \text{Outcome}_{i, t} + \beta_4 \text{Polyarchy}_{i, t} + \\
-&\ \beta_5 \log (\text{GDP per capita}) + \\
-&\ \beta_6 \text{Trade as } \% \text{ of GDP}_{i, t} + \\
-&\ \beta_7 \text{Armed conflict}_{i, t} + u_i + \sigma^2_e \\
-u_i =&\ \mathcal{N}(0, \sigma^2_u) & \text{[country-specific intercepts]} \\
-\ \\
-\beta_0 \sim&\ \mathcal{N}(0, 10) & \text{[prior population intercept]} \\
-\beta_{1-7} \sim&\ \mathcal{N}(0, 3) & \text{[prior population effects]} \\
-\sigma^2_m, \sigma^2_e, \sigma^2_u \sim&\ \operatorname{Cauchy}(0, 1) & \text{[prior sd for model, population, and country error]} \\
-\end{aligned}
-$$
-\normalsize
 
@@
                   position = position_dodge(width = 0.2),
-                  fatten = 1) +
+                  fatten = 1, size = 1) +
   scale_x_continuous(breaks = 0:9) +
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_color_viridis_d(option = "plasma", end = 0.9) +
+  scale_color_viridis_d(option = "rocket", end = 0.85, direction = -1) +
+  guides(color = guide_legend(override.aes = list(size = 0.5, linetype = 0))) +
   labs(x = "Count of legal barriers\n",
@@
   geom_pointrange(aes(ymin = lower__, ymax = upper__),
-                  fatten = 1) +
+                  fatten = 1, size = 1) +
   scale_x_continuous(breaks = 0:9) +
@@
   coord_cartesian(ylim = c(0.60, 0.71)) +
-  guides(color = FALSE) +
+  guides(color = "none") +
   labs(x = NULL,
@@
   geom_pointrange(aes(ymin = lower__, ymax = upper__),
-                  fatten = 1) +
+                  fatten = 1, size = 1) +
   scale_x_continuous(breaks = 0:9) +
   scale_color_viridis_d(option = "plasma", end = 0.8) +
-  guides(color = FALSE) +
+  guides(color = "none") +
   labs(x = "Count of legal barriers",
@@
   geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, color = NA) +
-  geom_line(size = 0.75) +
+  geom_line(size = 1) +
   scale_x_reverse() +
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_color_viridis_d(option = "plasma", end = 0.9) +
-  scale_fill_viridis_d(option = "plasma", end = 0.9) +
+  scale_color_viridis_d(option = "rocket", end = 0.75, direction = -1) +
+  scale_fill_viridis_d(option = "rocket", end = 0.9, direction = -1) +
   labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
@@
               fill = "#433E85", color = NA) +
-  geom_line(size = 0.75, color = "#433E85") +
+  geom_line(size = 1, color = "#433E85") +
   scale_x_reverse() +
@@
               fill = "#4DC36B", color = NA) +
-  geom_line(size = 0.75, color = "#4DC36B") +
+  geom_line(size = 1, color = "#4DC36B") +
   scale_x_reverse() +
@@
               fill = "#FF4136", color = NA) +
-  geom_line(size = 0.75, color = "#FF4136") +
+  geom_line(size = 1, color = "#FF4136") +
   scale_x_reverse() +
@@
 ```{r correct-not-correct}
+# These numbers come from the analysis notebook at 
+# https://stats.andrewheiss.com/canary-ngos/04_predictions.html#Prediction_diagnostics
 pts_pred_table <- tribble(
@@
 ```{r tbl-rmse}
+# These numbers also come from the analysis notebook at 
+# https://stats.andrewheiss.com/canary-ngos/04_predictions.html
 tbl_rmse <- tribble(
@@
 Encroachments on private civil liberties such as restricting freedom of association are not nearly as violent as events like government-sponsored murders.
+In authoritarian states in particular, administrative crackdown on NGOs can also be seen as a careful strategy for autocratic survival.
+Authoritarian leaders must carefully balance domestic and international institutional pressures—including pressure from civil society and NGOS—to remain in power [@Heiss:2019a; @LevitskyWay:2010].
+Anti-NGO laws could possibly be a side effect of authoritarian stability-seeking behavior, similar to election tampering, media censorship, cronyism, and rent-seeking, rather than an overt signal of impending serious human rights abuses.
+
 The global shrinking of civil society is thus not likely an early warning sign for future violent repression—states typically signal their future repressive intentions with more violent methods, such as the persecution and murder of activists and the media.
@@
 # Appendix
+
+## Modeling approach
+
+We use Stan [@stan] through R [@r-project] and brms [@brms-jss] to estimate our models.
+We generate 4 MCMC chains for each model with 2,000 iterations in each chain, 1,000 of which are used for warmup.
+All chains converge; we assess convergence with visual inspection.
+
+Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion website at <https://stats.andrewheiss.com/canary-ngos/>.
+Our general modeling approach can be summarized as follows:
+
+\footnotesize
+
+$$
+\begin{aligned}
+y_{i, t+1} \mid u_i, x_{i, t} \sim&\ \operatorname{Ordered Logistic}(y^*_{i, t + 1}, \sigma^2_m) & \text{[likelihood for ordinal PTS models]} \\
+y_{i, t+1} \mid u_i, x_{i, t} \sim&\ \mathcal{N}(y^*_{i, t + 1}, \sigma^2_m) & \text{[likelihood for Gaussian V-Dem models]} \\
+y^*_{i, t + 1} =&\ \beta_0 + \beta_1 \text{Civil society repression}_{i, t} + & \text{[model with covariates]}\\
+&\ \beta_2 \text{Civil society repression}_{i, t - 1} + \\
+&\ \beta_3 \text{Outcome}_{i, t} + \beta_4 \text{Polyarchy}_{i, t} + \\
+&\ \beta_5 \log (\text{GDP per capita}) + \\
+&\ \beta_6 \text{Trade as } \% \text{ of GDP}_{i, t} + \\
+&\ \beta_7 \text{Armed conflict}_{i, t} + u_i + \sigma^2_e \\
+u_i =&\ \mathcal{N}(0, \sigma^2_u) & \text{[country-specific intercepts]} \\
+\ \\
+\beta_0 \sim&\ \mathcal{N}(0, 10) & \text{[prior population intercept]} \\
+\beta_{1-7} \sim&\ \mathcal{N}(0, 3) & \text{[prior population effects]} \\
+\sigma^2_m, \sigma^2_e, \sigma^2_u \sim&\ \operatorname{Cauchy}(0, 1) & \text{[prior sd for model, population, and country error]} \\
+\end{aligned}
+$$
+\normalsize
+
+To check for robustness, we also ran models using both country and regional random effects, but doing so made no noticable difference in the results—for the sake of computational efficiency, we thus do not include regional effects.
+
+## Improved cases
+
+\newpage
 
@@
 
+## Complete model results
+
 \memSingleSmall

### 2021-07-20 manuscript/manuscript.Rmd
Final Suparna edits

@@
 ---
-title: "Civil Society Repression as a Predictor of Worsening Human Rights Abuses"
-short-title: "Civil Society Repression"
+title: "NGO Repression as a Predictor of Worsening Human Rights Abuses"
+short-title: "NGO Repression"
 author:
@@
 abstract: >-
-  An increasing number of countries cracked down on NGOs over the last few decades.
-These attempts to repress civil society organizations—many of which are sanctioned by law—represent a bureaucratic form of repression that could indicate more severe human rights abuses and democratic backsliding in the future.
+  An increasing number of countries have cracked down on non-governmental organizations (NGOs) over the last few decades.
+This crackdown—much of which is sanctioned by law—represents a bureaucratic form of repression that could indicate more severe human rights abuses in the future.
 This is especially the case for electoral democracies, which unlike autocracies, may not aggressively attack civic space.
 In this paper, we explore if crackdowns on NGOs predict broader human rights repression.
-Anti-NGO laws are among the most subtle means of repression and attract much less domestic and international condemnation compared to the use of violence, as many audiences mistake this repression as regulation.
+Anti-NGO laws are among the most subtle means of repression and attract much less domestic and international condemnation compared to the use of violence, as many audiences perceive this repression as regulation.
 These laws may also make it easier for states to prevent future large-scale popular mobilization.
-Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, physical integrity rights violations, and violations of private civil liberties.
-We find that while formal de jure laws provide little information in predicting future repression, their patterns of implementation or de facto civil society repression predicts worsening respect for physical integrity rights and civil liberties.
+Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, and violations of physical integrity rights and civil liberties.
+We find that while formal de jure laws provide little information in predicting future repression, their patterns of implementation, or de facto civil society repression, predicts worsening respect for physical integrity rights and civil liberties.
 keywords: "civil society, NGOs, repression, human rights, political terror, civil liberties"
@@
 
-Over the last few decades, governments across the globe have been increasingly cracking down on civil society organizations (CSOs), particularly non-governmental organizations (NGOs)—a phenomenon commonly known as closing civic space [@CarothersBrechenmacher:2014; @DPR:2016; @Chaudhry:2016; @DupuyPrakash:2018].
+Over the last few decades, governments across the globe have been increasingly cracking down on civil society organizations (CSOs), particularly non-governmental organizations (NGOs)—a phenomenon commonly known as closing or shrinking civic space [@CarothersBrechenmacher:2014; @DPR:2016; @Chaudhry:2016; @DupuyPrakash:2018].
 More than 100 countries have proposed or enacted 244 different measures that have restricted, repressed, or shut down civil society since 2013 [@icnl:2021].
 In Human Rights Watch's 2016 World Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory, and over the past decade, the majority of the world has seen a substantial narrowing of allowable civic space.
-As seen in Figure \@ref(fig:civicus-map), by the end of 2020, only `r civicus$Open$prop_nice` of countries had open and unrestricted civil societies [@civicusmonitor; @ChaudhryHeiss:2021].[^open]
+As seen in Figure \@ref(fig:civicus-map), by the end of 2020, only `r civicus$Open$prop_nice` of countries had open and unrestricted civic space [@civicusmonitor; @ChaudhryHeiss:2021].[^open]
 
@@
 This hostility to civil society is not unique to autocratic governments or even illiberal democracies [@AbramowitzSchenkkan:2018]—long-established liberal democracies have also increased restrictions on civil society in their countries.
-Over the past decade, India has canceled the licenses of tens of thousands of NGOs, targeted major groups such as Greenpeace International, Amnesty International and Ford Foundation, and has banned 5,000 NGOs from receiving foreign funds [@press-trust-india:2015; @press-trust-india:2019].
+Over the past decade, India has canceled the licenses of tens of thousands of NGOs, targeted major groups such as Greenpeace International, Amnesty International and Ford Foundation, and has banned thousands of NGOs from receiving foreign funds [@press-trust-india:2015; @press-trust-india:2019].
 In 2013 Canada attempted to revoke the charitable status of NGOs for opposing the Northern Gateway pipeline and Canadian mining companies' initiatives abroad [@CIVICUS:2013].
-In 2019, activists from the US-based nonprofit No More Deaths were arrested for providing food and water to migrants a the US-Mexico border and faced a 20-year prison sentence before their convictions were overturned in 2020 [@Cramer:2020].
+In 2019, activists from the US-based nonprofit No More Deaths were arrested for providing food and water to migrants at the US-Mexico border and faced a 20-year prison sentence before their convictions were overturned in 2020 [@Cramer:2020].
 
@@
 The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations [@Heiss:2019; @Heiss:2017].
-While this can lead to the depoliticization and avoidance of direct political activism by CSOs [@Bush:2015], states cannot soften or neutralize all forms of political activity and advocacy in subtle, legal ways like they have with NGOs.
+While this can lead to the depoliticization and avoidance of direct political activism by CSOs [@BloodgoodTremblay-Boire:2017], states cannot soften or neutralize all forms of political activity and advocacy in subtle, legal ways like they have with NGOs.
 Sooner or later, states may need to deal with threats to their stability in a more direct, violent, confrontational manner.
-Anti-NGO laws and repression of CSOs could be an important early warning sign—or a canary in the coal mine—of worsening human rights repression in a state, signaling that a state will continue down the path of further repression.
+Anti-NGO laws could be an important early warning sign—or a canary in the coal mine—of worsening human rights repression, signaling that a state will continue down the path of further repression.
 What does state targeting of NGOs tell us about the state's broader respect for civil society and the overall level of human rights repression?
@@
 As such, they may not be particularly suitable for forecasting short-term trajectories, especially for moderately repressive countries.
-On the other hand, state repression of NGOs is more dynamic process than may provide insight into changing levels of human rights standards and repression in subsequent years.
-While recent research has made important contributions to studying the extent and effects of state crackdown on NGOs, much of this focuses on de jure restrictions and its impact on NGOs and donors [@christensen2013; @BromleySchoferLonghofer:2020; @BakkeMitchellSmidt:2020; @SmidtPereraMitchell:2021].
+On the other hand, state repression of NGOs is a more dynamic process that may provide insight into changing levels of human rights standards and repression in subsequent years.
+While recent research has made important contributions to studying the extent and effects of state crackdown on NGOs, much of this focuses on de jure restrictions and its impact on NGOs and donors [@christensen2013; @DPR:2016; @DupuyPrakash:2018; @BromleySchoferLonghofer:2020; @BakkeMitchellSmidt:2020; @SmidtPereraMitchell:2021].
 By looking at laws *and* their implementation, as well as the extra-legal treatment of NGOs, we are able to assess the long-term effects of closing civic space on broader patterns of repression.
@@
 Using both original data as well as data from several existing datasets, we build an ensemble of predictive models and explore (1) the marginal effects of civil society repression on different forms of broader human rights repression, and (2) the out-of-sample predictive performance of each model.
-We conclude by discussing the implications of our findings on the role of NGOs in the international community and prospects of democratic backsliding.
+We conclude by discussing the implications of our findings on autocratic survival, and how states may manage NGOs as a strategy to remain in power.
 
@@
 
-Repression is the use of coercive action against an individual or organization, within the territorial jurisdiction of the state, for the purpose of imposing a cost on the target as well as deterring specific activities and/or beliefs perceived to be challenging to government personnel, practices, or institutions [@Goldstein:1978, p.
+Repression is the use of coercive action against an individual or organization, within the territorial jurisdiction of the state, for the purpose of imposing a cost on the target as well as deterring specific activities perceived to be challenging to government personnel, practices, or institutions [@Goldstein:1978, p.
 xxvii; @Davenport:2007, 487; and @ConradRitter:2019, 15].
-Early literature on repression focused on the role of structural factors such as levels of democracy, economic development, electoral competitiveness in predisposing a state to increased use of repression.
+Early literature on repression focused on the role of structural factors such as levels of democracy, economic development, and electoral competitiveness in predisposing a state to the increased use of repression.
 Most notably, democratic forms of government—and democratization in general—has a pacifying effect on state repression [@DavenportArmstrong:2004; @Krain:1997; @Richards:1999].
@@
 However, dissent and repression have an endogenous relationship: state authorities also frequently engage in preventive repression to undermine or restrict groups' abilities to dissent [@RitterConrad:2016; @ConradRitter:2019].
-In addition to attacking groups willingness to organize against states, such preventive repression also damages states' capacity to impose costs [@Davenport:2007a, 47].
+Such preventive repression also damages organizations' capacity to impose costs [@Davenport:2007a, 47].
 NGOs are one actor that can pose challenges to political authorities, and state repression of these actors, especially through legal restrictions can be considered a form of preventive repression [@Chaudhry:2016].
 
-While many saw the initial proliferation of NGOs as leading to a "symbiotic relationship" between NGOs and states due to their mutual goals, this perception changed over time [@Reimann:2006, 63].
+This preventive repression of NGOs is a recent phenomenon.
+While many saw the initial proliferation of NGOs in the 1980s and 1990s as leading to a "symbiotic relationship" between NGOs and states due to their mutual goals, this perception changed over time [@Reimann:2006, 63].
 With expanded powers and their perceived role in the Color Revolutions, NGOs began to be seen as having a real influence on domestic and international politics [@CarothersBrechenmacher:2014].
-State crackdown on NGOs became pervasive as these organizations have the ability to influence electoral politics [@DPR:2016; @Weiss:2009], aid mobilization [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
+State perception of NGOS as threatening became pervasive as these organizations demonstrated their ability to influence electoral politics [@DPR:2016; @Weiss:2009], mobilize aid [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
 
@@
 For instance, Russia passed its 2015 Undesirable Organizations Law with the purpose of targeting and eliminating specific foreign-connected NGOs it deemed dangerous.
-One of the law's sponsors, Aleksandr Tarnavsky, described the law as a preventative measure that would not affect the majority of NGOs working in Russia.
+One of the law's sponsors, Aleksandr Tarnavsky, described the law as a preventive measure that would not affect the majority of NGOs working in Russia.
 Rather, the law would be a "weapon hanging on the wall that never fires" and stand as a warning to potentially uncooperative NGOs [@Kozenko:2015].
-Similarly, Egypt's 2002 NGO law instated severe barriers to freedom of association, banned NGOs from engaging in activities that "threaten national unity or violate public order or morality," and also prevented groups for receiving foreign funding.
-But despite the harsh legal framework, the NGO sector nearly doubled in size between 1993–2011.
-The state targeted a limited number of organizations working on politically sensitive issues such as human rights and democracy, while simultaneously tolerating organizations working on tamer issues [@Brechenmacher:2017].
+Similarly, Egypt's 2002 NGO law instated severe barriers to freedom of association, banned NGOs from engaging in activities that "threaten national unity or violate public order or morality," and also prevented groups from receiving foreign funding.
+But despite the harsh legal framework, the Egyptian NGO sector nearly doubled in size between 1993–2011.
+This is because the state targeted a limited number of organizations working on politically sensitive issues such as human rights and democracy, while simultaneously tolerating organizations working on tamer issues [@Brechenmacher:2017].
 
@@
 Moreover, the implementation of these laws may not be limited to its legal character.
-The government may also engage in harassment of NGOs and activists to dissuade NGOs from operation or expressing themselves.
+The government may also engage in harassment of NGOs and activists to dissuade NGOs from carrying out their operations.
 This may include measures such as detentions, short-term incarceration, as well as beatings, threats to families and destruction of valuable property.
 
-Finally, counting official laws can also undermeasure civil society repression because governments can repress NGOs without passing or relying on formal laws.
+Finally, counting official laws can also undermeasure civil society repression because governments can repress NGOs without relying on formal laws.
 As prior research in Egypt, Ethiopia, and Russia points out, "rather than systematically enforcing all repressive legal measures-often impossible owing to capacity constraints," governments may choose to use extra-legal means to intimidate, harass or prosecute a few NGOs or activists.
@@
 
-Based on these various purposes of civil society restrictions and the different methods states use to implement them, we propose two empirical expectations about the relationship between civil society repression and general human rights:
+Based on these various purposes of NGO restrictions and the different methods states use to implement them, we propose two empirical expectations about the relationship between civil society repression and general human rights:
 
@@
 To measure de jure repression, we use data on anti-NGO laws from @Chaudhry:2016 which includes official NGO laws for all countries (excluding micro-states) between 1990 and 2013.
-We create indeces of the total number of laws passed in each country based on three broad categories of laws related to barriers to entry, funding, and advocacy, and we also sum each of these indeces to create a count of total legal barriers.
+We create indices of the total number of laws passed in each country based on three broad categories of laws related to barriers to entry, funding, and advocacy, and we also sum each of these indices to create a count of total legal barriers.
 We also create a yearly indicator variable to show if a country increased its count of anti-NGO laws (models using this outcome are included in the online appendix).
@@
 - Barriers to entry (3 possible barriers): registration is burdensome, NGOs are not allowed to appeal if denied registration, and entry requirements differ if the NGO receives foreign funding
-- Barriers to funding (5 possible barriers): NGOs need prior approval to receive foreign funding, NGOS are required to channel foreign funding to state-owned banks, NGOS face additional restrictions if receiving foreign funding, and NGOs are prohibited from receiving foreign funding
+- Barriers to funding (5 possible barriers): NGOs need prior approval to receive foreign funding, NGOs are required to channel foreign funding to state-owned banks, NGOs face additional restrictions if receiving foreign funding, and NGOs are prohibited from receiving foreign funding
 
@@
 
-However, looking at political terror, physical integrity rights, and private civil liberties captures specific dimensions of a country's respect for human rights, but isolating these trends in repression can prove difficult.
-@SchnakenbergFariss:2014, @Fariss:2014, and others have argued that a country's latent and underlying human rights environment causes a state to engage in specific actions related to human rights, such as engaging in political violence, arresting activists, or restricting freedom of religion.
-Measuring this underlying respect for human rights is difficult, however, as it is by definition unobserved.
-@FarissKenwickReuning:2020 use a Bayesian measurement model to generate estimates of latent respect for physical integrity rights.
-We use the posterior mean of their latent variable ($\theta$) as our final measure of repression in order to see how civil society restrictions predict changes in a country's future underlying human rights environment.
-The right panel of Figure \@ref(fig:repression) demonstrates the global increase in average latent human rights values over time.
+Finally, it is worth noting that these indicators of physical integrity rights violations and political terror may not account for the systematic changes in the way monitoring agencies have gathered information about human rights violations over time.
+To account for this, we use latent human rights scores as a final measure of underlying repression [@Fariss:2014; @FarissKenwickReuning:2020].
+This variable accounts for changing standards of accountability, which has led to the production of more stringent human rights reports as monitors look harder for abuse, look in more places for abuse, and classify more acts as abuse.
+When accounting for these changes, the right panel of Figure \@ref(fig:repression) demonstrates the global improvements in average latent human rights values over time.
 
@@
 Following @GohdesCarey:2017, we control for a country's previous level of repression, its level of democracy as measured by V-Dem's polyarchy index, its logged GDP per capita (measured by the UN), the percent of GDP attributed to trade (measured by the UN), and an indicator for whether the country witnessed more than 25 battle-related deaths (measured by @ucdp2020; @GleditschWallensteenEriksson:2002).
-Because changes in the human rights environment take time to be reflected by these larger indexes, we model the effect of lagged explanatory variables on repression one year in the future.
+Because changes in the human rights environment take time to be reflected by these larger indices, we model the effect of lagged explanatory variables on repression one year in the future.
 We also include the lag of civil society laws or repression to account for serial correlation.
@@
 We generate predictions with two families of Bayesian regression models.
-Because the Political Terror Scale is measured as an ordered category, we use ordered logistic regression to predict future values of the PTS.
+Because the PTS is measured as an ordered category, we use ordered logistic regression to predict future values of the scale.
 As V-Dem's physical violence index and private civil liberties index and latent human rights values are all measured continuously, we predict these values with Gaussian models.
@@
 
-[^open]: Defined as the state both enabling and safeguarding citizens' freedom to form associations, authorities being tolerant of criticism from CSOs and laws governing freedom of peaceful assembly adhere to international laws and standards.
+[^open]: Following CIVICUS, open civic space in a country indicates that the state enables and safeguards citizens' freedom to form associations, authorities are tolerant of criticism from CSOs, and that laws governing freedom of peaceful assembly adhere to international laws and standards.
 
@@
        y = "Predicted probability of category",
-       color = "Predicted political terror scale", fill = "Predicted political terror scale",
-       title = "Political terror scale") + 
+       color = "Predicted Political Terror Scale", fill = "Predicted Political Terror Scale",
+       title = "Political Terror Scale") + 
   facet_wrap(vars(plot_var_nice), scales = "free_x") +
@@
 Anti-NGO laws do not predict more dramatic shifts in the PTS.
-Across all counts of legal barriers, the overall probability of seeing Levels 4 and 5 is minuscule, and the adding new laws does little to shift that probability.
+Across all counts of legal barriers, the overall probability of seeing Levels 4 and 5 is minuscule, and the passave of additional laws does little to shift that probability.
 This is not unexpected however—the PTS has a natural ceiling at Level 5.
 Specifically, in addition to measuring the scope and intensity of government violence, the PTS scale also looks at the proportion of population targeted for abuse.
-Countries that receive a 4 and 5 are rare, as 4 denotes that murders, disappearances, and torture are a common part of life, while 5 denotes that physical abuses routinely perpetrated against citizens not involved in politics, and includes cases where governments engage in "scorched earth" counterinsurgency policies or summary executions based on class or ethnic affiliation [@GibneyCornettWood:2019].
+Countries that receive a 4 and 5 are rare, as 4 denotes that murders, disappearances, and torture are a common part of life, while 5 denotes that physical abuses are routinely perpetrated against citizens not involved in politics, and includes cases where governments engage in "scorched earth" counterinsurgency policies or summary executions based on class or ethnic affiliation [@GibneyCornettWood:2019].
 The majority of movement across PTS categories should thus occur between Levels 1–3.
@@
 Limited repression remains the most likely possible outcome, but the chance of seeing robust rule of law decreases rapidly as more laws are passed, all else equal.
-When looking at other specific forms of political repression, though, such as physical violence and private civil liberties, NGO legal barriers do not change predicted values in any meaningful way.
+When looking at other forms of political repression, though, such as physical violence and private civil liberties, NGO legal barriers do not change predicted values in any meaningful way.
 
@@
 
-The effect of de facto civil society repression on predicted values of the Political Terror Scale mirrors what we found previously with our first empirical expectation.
+The effect of de facto civil society repression on predicted values of the PTS mirrors what we found previously with our first empirical expectation.
 As seen in Figure \@ref(fig:plot-mfx-e2a), at the lowest levels of repression, Levels 1 and 2 are the most common predicted outcomes and are each equiprobable at roughly 50%.
@@
        y = "Predicted probability of category",
-       color = "Political terror scale", fill = "Political terror scale",
-       title = "Political terror scale") +
+       color = "Political Terror Scale", fill = "Political Terror Scale",
+       title = "Political Terror Scale") +
   theme_ngo()
@@
 This implies that an increase in de facto NGO restrictions predicts a `r percent_format(accuracy = 1)((0.62 - (0.62 - 0.02)) / (0.62 - 0.02))` decline in both protection from physical violence and respect for private civil liberties in the following year.
-Moreover, worsening civil society repression is strongly associated with a worse future human rights environment, as seen in the right panel of Figure \@ref(fig:plot-mfx-e2b-e2d)
-
-When holding all other factors equal, the de facto implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passing of formal de jure laws.
-In countries with low levels of political terror, it can potentially serve as a weak signal of a more general increase in political violence in the future, but predict more substantial changes in physical integrity rights, threats to civil liberties, and latent respect for human rights.
-The difference in the effects of de jure laws v/s.
+Moreover, worsening civil society repression is strongly associated with a worse future human rights environment, as seen in the right panel of Figure \@ref(fig:plot-mfx-e2b-e2d).
+
+When holding all other factors equal, the de facto implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passage of formal de jure laws.
+In countries with low levels of political terror, it can potentially serve as a weak signal of a more general increase in political violence in the future, but predict more substantial changes in physical integrity rights, threats to civil liberties, and respect for human rights.
+The difference in the effects of laws vs.
 their de facto implementation could also potentially be explained by the time frame of these strategies.
 De jure laws are a long-term strategy to prevent threats to the regime from coalescing in the first place.
-For instance, Egypt's NGO law had been on the books since 2002, but only over the past five years have post-revolutionary regimes used it more broadly (CITATION).
+For instance, Egypt's NGO law had been on the books since 2002, but only over the past five years have post-revolutionary regimes used it more broadly [@CITATION].
 As such, the long-term effects of these laws in terms of their predictive power may require a much longer time period under study.
-In contrast, de fact crackdown on NGOs may signal the need to react sooner due to the immediacy of the threat.
+In contrast, de facto crackdown on NGOs may signal the need to react sooner due to the immediacy of the threat.
 
@@
 As Table \@ref(tab:tbl-rmse) shows, accounting for legal barriers and civil society repression only reduces the RMSE by at most 0.4% compared to the baseline model.
-This is likely related to the lack of improvements in predicting political terror—both indexes measure similar phenomena.
+This is likely related to the lack of improvements in predicting political terror—both indices measure similar phenomena.
 Similarly, accounting for de facto civil society repression when modeling latent human rights only results in slight changes to the RMSE.
@@
 In authoritarian states in particular, administrative crackdown on NGOs can also be seen as a careful strategy for autocratic survival.
-Authoritarian leaders must carefully balance domestic and international institutional pressures—including pressure from civil society and NGOS—to remain in power [@Heiss:2019a; @LevitskyWay:2010].
+Authoritarian leaders must carefully balance domestic and international institutional pressures—including pressure from civil society and NGOs—to remain in power [@Heiss:2019a; @LevitskyWay:2010].
 Anti-NGO laws could possibly be a side effect of authoritarian stability-seeking behavior, similar to election tampering, media censorship, cronyism, and rent-seeking, rather than an overt signal of impending serious human rights abuses.

### 2021-07-21 _targets.R
Update templates

@@ -3,8 +3,8 @@ library(tarchetypes)
 library(tibble)
 
 # General variables
-csl <- "pandoc/csl/chicago-author-date.csl"
-bibstyle <- "bibstyle-chicago-authordate"
+csl <- "pandoc/csl/apa.csl"
+bibstyle <- "bibstyle-apa"
 
 suppressPackageStartupMessages(library(brms))
 
@@ -345,21 +345,21 @@ list(
   tar_target(pdf,
              render_pdf(
                input = main_manuscript,
-               output = here_rel("manuscript", "output/manuscript.pdf"),
+               output = here_rel("manuscript", "output", "manuscript.pdf"),
                bibstyle = bibstyle,
                bib_file),
              format = "file"),
   tar_target(ms_pdf,
              render_pdf_ms(
                input = main_manuscript,
-               output = here_rel("manuscript", "output/manuscript-ms.pdf"),
+               output = here_rel("manuscript", "output", "manuscript-ms.pdf"),
                bibstyle = bibstyle,
                bib_file),
              format = "file"),
   tar_target(docx,
              render_docx(
                input = main_manuscript,
-               output = here_rel("manuscript", "output/manuscript.docx"),
+               output = here_rel("manuscript", "output", "manuscript.docx"),
                csl = csl,
                bib_file),
              format = "file"),
@@ -368,5 +368,12 @@ list(
                input_rmd = main_manuscript,
                input_bib = bib_file,
                output = here_rel("manuscript", "output", "extracted-citations.bib")),
-             format = "file")
+             format = "file"),
+
+  # Always show a word count
+  tar_target(word_count, count_words(html)),
+  tar_force(show_word_count, print(word_count), TRUE),
+
+  # Knit the README
+  tar_render(readme, here_rel("README.Rmd"))
 )

### 2021-07-21 manuscript/manuscript.Rmd
Final edits pre-submission

@@
 title: "NGO Repression as a Predictor of Worsening Human Rights Abuses"
-short-title: "NGO Repression"
+short-title: "NGO Repression and Human Rights"
 author:
@@
   url: https://www.andrewheiss.com/
-date: "July 17, 2021"
+date: "July 20, 2021"
 published: Under review
@@
 abstract: >-
-  An increasing number of countries have cracked down on non-governmental organizations (NGOs) over the last few decades.
-This crackdown—much of which is sanctioned by law—represents a bureaucratic form of repression that could indicate more severe human rights abuses in the future.
-This is especially the case for electoral democracies, which unlike autocracies, may not aggressively attack civic space.
-In this paper, we explore if crackdowns on NGOs predict broader human rights repression.
-Anti-NGO laws are among the most subtle means of repression and attract much less domestic and international condemnation compared to the use of violence, as many audiences perceive this repression as regulation.
-These laws may also make it easier for states to prevent future large-scale popular mobilization.
-Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of political terror, and violations of physical integrity rights and civil liberties.
+  An increasing number of countries have recently cracked down on non-governmental organizations (NGOs).
+Much of this crackdown is sanctioned by law and represents a bureaucratic form of repression that could indicate more severe human rights abuses in the future.
+This is especially the case for democracies, which unlike autocracies, may not aggressively attack civic space.
+We explore if crackdowns on NGOs predict broader human rights repression.
+Anti-NGO laws are among the most subtle means of repression and attract lesser domestic and international condemnation compared to the use of violence.
+Using original data on NGO repression, we test whether NGO crackdown is a predictor of political terror, and violations of physical integrity rights and civil liberties.
 We find that while formal de jure laws provide little information in predicting future repression, their patterns of implementation, or de facto civil society repression, predicts worsening respect for physical integrity rights and civil liberties.
-keywords: "civil society, NGOs, repression, human rights, political terror, civil liberties"
+# keywords: civil society, NGOs, repression, human rights, political terror, civil liberties
+word-count: "7,159"
 thanks: >-
@@
 bibliography: bibliography.bib
+toc: false
 title-page: true
-endnotes: false
+endnotes: true
 endfloat: false
@@
 sansfont: Inter
+author-note: >-
+  Suparna Chaudhry, PhD, Assistant Professor of International Affairs, Department of International Affairs, Lewis \& Clark College; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University.
+correspondence: >-
+  Correspondence concerning this article should be addressed to Andrew Heiss, PhD, Department of Public Management and Policy, Andrew Young School of Policy Studies, Georgia State University, 14 Marietta Street NW, Suite 357, Atlanta, GA 30303.
+Contact: aheiss@gsu.edu
 editor_options: 
@@
 
-```{r barriers, fig.width=7, fig.height=6, fig.asp=NULL, fig.cap="Number of legal barriers to NGO activity per country over time (de jure legislation) and average level of CSO repression across democracies and non-democracies (de facto implementation)"}
+```{r barriers, fig.width=6, fig.height=6, fig.asp=NULL, fig.cap="Number of legal barriers to NGO activity per country over time (de jure legislation) and average level of CSO repression across democracies and non-democracies (de facto implementation)"}
 regulations <- tribble(
@@
   labs(x = NULL,
-       y = "Predicted physical violence index\n(higher values = less violence)",
-       title = "Physical violence index") +
+       y = "Predicted physical violence index",
+       title = "Physical violence index",
+       caption = "(Higher values = less violence)") +
   facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
@@
   labs(x = NULL,
-       y = "Predicted civil liberties index\n(higher values = better protection)",
-       title = "Private civil liberties index") +
+       y = "Predicted civil liberties index",
+       title = "Private civil liberties index",
+       caption = "(Higher values = better protection)") +
   facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
@@
   labs(x = "Count of legal barriers",
-       y = "Predicted latent human rights value\n(higher values = better protection)",
-       title = "Latent human rights") +
+       y = "Predicted latent human rights value",
+       title = "Latent human rights",
+       caption = "(Higher values = better protection)") +
   facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
@@
   scale_fill_viridis_d(option = "rocket", end = 0.9, direction = -1) +
-  labs(x = "Civil society repression\n(scale reversed; greater repression on the right)\n",
+  labs(x = "Civil society repression",
        y = "Predicted probability of category",
        color = "Political Terror Scale", fill = "Political Terror Scale",
-       title = "Political Terror Scale") +
-  theme_ngo()
+       title = "Political Terror Scale",
+       caption = "(x-axis reversed; greater repression on the right)") +
+  theme_ngo() +
+  theme(legend.box.margin = margin(t = 0.5, unit = "lines"))
 out_mfx_e2a
@@
 De jure laws are a long-term strategy to prevent threats to the regime from coalescing in the first place.
-For instance, Egypt's NGO law had been on the books since 2002, but only over the past five years have post-revolutionary regimes used it more broadly [@CITATION].
+For instance, Egypt's Law 84 of 2002—which outlined many anti-NGO restrictions—has been on the books for nearly two decades, but only over the past five years have post-revolutionary regimes used it more broadly [@Ruffner:2015].
 As such, the long-term effects of these laws in terms of their predictive power may require a much longer time period under study.
@@
   coord_cartesian(ylim = c(0.5, 0.75)) +
-  labs(x = "Civil society repression\n(scale reversed; greater repression on right)\n",
-       y = "Predicted physical violence index\n(higher values = less violence)",
+  labs(x = "Civil society repression",
+       y = "Predicted physical violence index",
        title = "Physical violence index") +
@@
   coord_cartesian(ylim = c(0.5, 0.75)) +
-  labs(x = "Civil society repression\n(scale reversed; greater repression on right)\n",
-       y = "Predicted civil liberties index\n(higher values = better protection)",
+  labs(x = "Civil society repression",
+       y = "Predicted civil liberties index",
        title = "Private civil liberties index") +
@@
   scale_x_reverse() +
-  labs(x = "Civil society repression\n(scale reversed; greater repression on right)\n",
-       y = "Predicted latent human rights value\n(higher values = better protection)",
+  labs(x = "Civil society repression",
+       y = "Predicted latent human rights value",
        title = "Latent human rights") +
@@
 
-out_mfx_e2b | out_mfx_e2c | out_mfx_e2d
+(out_mfx_e2b | out_mfx_e2c | out_mfx_e2d) +
+  plot_annotation(caption = "(x-axis reversed; greater repression on right\nhigher values in y-axis show less violence and better protection of rights)",
+                  theme = theme(plot.caption = element_text(size = rel(0.8), color = "grey50", face = "plain",
+                                      family = "Inter Light",
+                                      margin = margin(t = 5))))
 ```
@@
     kbl(align = "lcccccc",
-        booktabs = TRUE, linesep = "",
+        booktabs = TRUE, linesep = "\\addlinespace",
         caption = pts_pred_table_caption) %>% 
@@
     kbl(align = "lcc",
-        booktabs = TRUE, linesep = "",
+        booktabs = TRUE, linesep = "\\addlinespace",
         caption = tbl_rmse_caption) %>% 
@@
 
-Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion website at <https://stats.andrewheiss.com/canary-ngos/>.
+Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion website at `anonymized`.
 Our general modeling approach can be summarized as follows:
@@
 
-To check for robustness, we also ran models using both country and regional random effects, but doing so made no noticable difference in the results—for the sake of computational efficiency, we thus do not include regional effects.
+To check for robustness, we also ran models using both country and regional random effects, but doing so made no noticeable difference in the results—for the sake of computational efficiency, we thus do not include regional effects.
+
+\newpage
 
 ## Improved cases
-
-\newpage
 
@@
 
+\blandscape
+
 ## Complete model results
@@
 ```{r tbl-models-pts}
-model_names_tbl_pts <- c("Total barriers\n(t + 1)",
-                         "Barriers to advocacy\n(t + 1)",
-                         "Barriers to entry\n(t + 1)",
-                         "Barriers to funding\n(t + 1)",
-                         "Civil society repression\n(t + 1)")
+model_names_tbl_pts <- c("Total barriers",
+                         "Barriers to advocacy",
+                         "Barriers to entry",
+                         "Barriers to funding",
+                         "Civil society repression")
 
@@
                             caption = tbl_reg_pts_caption,
-                            notes = list("Posterior means; 95% credible intervals in brackets"))
+                            notes = list("Posterior means; 95% credible intervals in brackets"),
+                            longtable = TRUE)
 
@@
   tbl_reg_pts %>% 
-    kable_styling(font_size = ifelse(is_latex, 7, NA)) %>% 
-    column_spec(1, width = "0.10\\\\textwidth") %>% 
-    column_spec(2:6, width = "0.14\\\\textwidth")
+    kable_styling() %>% 
+    add_header_above(header = c(" " = 1, "Outcome in t + 1" = 5))
+    # kable_styling(font_size = ifelse(is_latex, 7, NA)) %>%
+    # column_spec(1, width = "0.75in", latex_valign = "b") %>%
+    # column_spec(2:6, width = "1.3in", latex_valign = "b")
+    # column_spec(1, width = "0.10\\\\textwidth") %>%
+    # column_spec(2:6, width = "0.14\\\\textwidth")
 } else {
@@
 ```{r tbl-models-clphy}
-model_names_tbl_clphy <- c("Total barriers\n(t + 1)",
-                           "Barriers to advocacy\n(t + 1)",
-                           "Barriers to entry\n(t + 1)",
-                           "Barriers to funding\n(t + 1)",
-                           "Civil society repression\n(t + 1)")
+model_names_tbl_clphy <- c("Total barriers",
+                           "Barriers to advocacy",
+                           "Barriers to entry",
+                           "Barriers to funding",
+                           "Civil society repression")
 
@@
                               caption = tbl_reg_clphy_caption,
-                              notes = list("Posterior means; 95% credible intervals in brackets"))
+                              notes = list("Posterior means; 95% credible intervals in brackets"),
+                              longtable = TRUE)
 
@@
   tbl_reg_clphy %>% 
-    kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
-    column_spec(1, width = "0.10\\\\textwidth") %>% 
-    column_spec(2:6, width = "0.14\\\\textwidth")
+    kable_styling() %>% 
+    add_header_above(header = c(" " = 1, "Outcome in t + 1" = 5))
+    # kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
+    # column_spec(1, width = "0.10\\\\textwidth") %>% 
+    # column_spec(2:6, width = "0.14\\\\textwidth")
 } else {
@@
 ```{r tbl-models-clpriv}
-model_names_tbl_clpriv <- c("Total barriers\n(t + 1)",
-                            "Barriers to advocacy\n(t + 1)",
-                            "Barriers to entry\n(t + 1)",
-                            "Barriers to funding\n(t + 1)",
-                            "Civil society repression\n(t + 1)")
+model_names_tbl_clpriv <- c("Total barriers",
+                            "Barriers to advocacy",
+                            "Barriers to entry",
+                            "Barriers to funding",
+                            "Civil society repression")
 
@@
                                caption = tbl_reg_clpriv_caption,
-                               notes = list("Posterior means; 95% credible intervals in brackets"))
+                               notes = list("Posterior means; 95% credible intervals in brackets"),
+                               longtable = TRUE)
 
@@
   tbl_reg_clpriv %>% 
-    kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
-    column_spec(1, width = "0.10\\\\textwidth") %>% 
-    column_spec(2:6, width = "0.14\\\\textwidth")
+    kable_styling() %>% 
+    add_header_above(header = c(" " = 1, "Outcome in t + 1" = 5))
+    # kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
+    # column_spec(1, width = "0.10\\\\textwidth") %>% 
+    # column_spec(2:6, width = "0.14\\\\textwidth")
 } else {
@@
 ```{r tbl-models-lhr}
-model_names_tbl_lhr <- c("Total barriers\n(t + 1)",
-                         "Barriers to advocacy\n(t + 1)",
-                         "Barriers to entry\n(t + 1)",
-                         "Barriers to funding\n(t + 1)",
-                         "Civil society repression\n(t + 1)")
+model_names_tbl_lhr <- c("Total barriers",
+                         "Barriers to advocacy",
+                         "Barriers to entry",
+                         "Barriers to funding",
+                         "Civil society repression")
 
@@
                             caption = tbl_reg_lhr_caption,
-                            notes = list("Posterior means; 95% credible intervals in brackets"))
+                            notes = list("Posterior means; 95% credible intervals in brackets"),
+                            longtable = TRUE)
 
@@
   tbl_reg_lhr %>% 
-    kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
-    column_spec(1, width = "0.10\\\\textwidth") %>% 
-    column_spec(2:6, width = "0.14\\\\textwidth")
+    kable_styling() %>% 
+    add_header_above(header = c(" " = 1, "Outcome in t + 1" = 5))
+    # kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
+    # column_spec(1, width = "0.10\\\\textwidth") %>% 
+    # column_spec(2:6, width = "0.14\\\\textwidth")
 } else {
@@
 
+\elandscape
+
 \memSingle

### 2021-07-21 README.Rmd
Add new title and abstract

@@
 # Please put your title here to include it in the file below.
-Title <- "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
+Title <- "NGO Repression as a Predictor of Worsening Human Rights Abuses"
 Authors <- "Suparna Chaudhry and Andrew Heiss"
@@
 
-[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of Political Science • Christopher Newport University  
+[Suparna Chaudhry](http://www.suparnachaudhry.com/) • Department of International Affairs • Lewis \& Clark College  
 [Andrew Heiss](https://www.andrewheiss.com/) • Andrew Young School of Policy Studies • Georgia State University
@@
 
-Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions.
-While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of laws—many of which appear mundane on their face—represent a bureaucratic form of repressive that could be indicative of more severe human rights abuses and backsliding.
-This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
-In this paper, we ask: do legal crackdowns on NGOs predict broader civil society repression?
-We argue that this is the case because anti-NGO laws are among the most subtle means of repression and attract the least least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
-These laws also make it easier for states to prevent and deter future large-scale popular mobilization.
-Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of attacks on journalists, independent media, academic freedom, and freedoms of expression and association.
-This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deteriorations in space for civil society.
+An increasing number of countries have recently cracked down on non-governmental organizations (NGOs).
+Much of this crackdown is sanctioned by law and represents a bureaucratic form of repression that could indicate more severe human rights abuses in the future.
+This is especially the case for democracies, which unlike autocracies, may not aggressively attack civic space.
+We explore if crackdowns on NGOs predict broader human rights repression.
+Anti-NGO laws are among the most subtle means of repression and attract lesser domestic and international condemnation compared to the use of violence.
+Using original data on NGO repression, we test whether NGO crackdown is a predictor of political terror, and violations of physical integrity rights and civil liberties.
+We find that while formal de jure laws provide little information in predicting future repression, their patterns of implementation, or de facto civil society repression, predicts worsening respect for physical integrity rights and civil liberties.
 

### 2021-11-11 R/funs_notebook.R
Make cleaner target names + don't get filenames from target names
When .Rmd files have illegal characters (i.e. start with digits, contain "-", etc), the resulting object names don't work in R, so we have to use make.names() to clean those up. But then that makes it so the resulting filenames are based on the cleaned up names, which we don't want, so we have to make them separate processes here.

Thanks to @tjmahr for figuring this out! https://github.com/tjmahr/notestar/commit/f1647eecabecd16011342a365228a0c2dbc9387a

@@ -45,11 +45,13 @@ tar_notebook_pages <- function(
 
   values <- lazy_list(
     rmd_file = !! rmds,
-    rmd_page = basename(.data$rmd_file),
+    rmd_page_raw = basename(.data$rmd_file),
+    rmd_page = make.names(.data$rmd_page_raw),
     sym_rmd_page = rlang::syms(.data$rmd_page),
     rmd_deps = lapply(.data$rmd_file, tarchetypes::tar_knitr_deps_expr),
     html_page = rmd_to_html(.data$rmd_page),
-    html_file = file.path(!! dir_html, .data$html_page)
+    html_page_raw = rmd_to_html(.data$rmd_page_raw),
+    html_file = file.path(!! dir_html, .data$html_page_raw)
   )
 
   list(

### 2021-11-12 manuscript/manuscript.Rmd
Fix issue 13 from R2: trichotomize the PTS

@@
 Level 1, where a country is under secure rule of law, is the second most likely outcome at slightly under 40%.
-The other categories of the PTS are extremely rare when there are no anti-NGO laws.
+The other categories of the PTS are extremely rare when there are no anti-NGO laws—as such, we collapse them into a single category.
 
@@
   mutate(x_rounded = floor(effect1__)) %>% 
+  # Collapse 3-5 to just one level, since they're all tiny
+  mutate(effect2__ = fct_collapse(effect2__, "3+" = c("3", "4", "5"))) %>% 
   group_by(x_rounded, effect2__, plot_var_nice) %>% 
   slice(1) %>% 
+  # Add up these values for the collapsed 3-5 results
+  summarize(across(c(estimate__, lower__, upper__), sum)) %>% 
   ungroup() %>% 
@@
   geom_pointrange(aes(ymin = lower__, ymax = upper__),
-                  position = position_dodge(width = 0.2),
+                  # position = position_dodge(width = 0.2),
                   fatten = 1, size = 1) +
@@
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_color_viridis_d(option = "rocket", end = 0.85, direction = -1) +
+  scale_color_viridis_d(option = "rocket", begin = 0.1, end = 0.85, direction = -1) +
   guides(color = guide_legend(override.aes = list(size = 0.5, linetype = 0))) +
@@
 Adding new barriers to advocacy, entry, and funding decreases the likelihood of seeing Level 1 and increases the probability of a country turning to either Level 2 or Level 3 (with extensive political imprisonment and trial-free detention).
-The marginal effects of all forms of NGO laws results in this turn from Level 1 to Levels 2 or 3, but this switching effect is strongest following additional barriers to advocacy.
+The marginal effects of all forms of NGO laws results in this turn from Level 1 to Levels 2 or 3+, but this switching effect is strongest following additional barriers to advocacy.
 Anti-NGO laws do not predict more dramatic shifts in the PTS.
-Across all counts of legal barriers, the overall probability of seeing Levels 4 and 5 is minuscule, and the passave of additional laws does little to shift that probability.
+Across all counts of legal barriers, the overall probability of seeing Levels 4 and 5 is minuscule, and the passage of additional laws does little to shift that probability.
 This is not unexpected however—the PTS has a natural ceiling at Level 5.
@@
 
-```{r plot-mfx-e1b-e1d, fig.width=7.5, fig.height=7.5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on V-Dem rights indexes and latent human rights"}
-out_mfx_e1b <- mfx_e1b_clphy %>% 
-  mutate(x_rounded = floor(effect1__)) %>% 
-  group_by(x_rounded, plot_var_nice) %>% 
-  slice(1) %>% 
-  ungroup() %>% 
-  mutate(plot_var_nice = fct_relabel(plot_var_nice, ~str_to_sentence(str_remove(., "Barriers to ")))) %>% 
-  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
-  geom_line(size = 0.5, color = "grey90") +
-  geom_pointrange(aes(ymin = lower__, ymax = upper__),
-                  fatten = 1, size = 1) +
-  scale_x_continuous(breaks = 0:9) +
-  scale_color_viridis_d(option = "plasma", end = 0.8) +
-  coord_cartesian(ylim = c(0.60, 0.71)) +
-  guides(color = "none") +
-  labs(x = NULL,
-       y = "Predicted physical violence index",
-       title = "Physical violence index",
-       caption = "(Higher values = less violence)") +
-  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
-  theme_ngo() +
-  theme(panel.grid.major.x = element_blank())
-
-out_mfx_e1c <- mfx_e1c_clpriv %>% 
-  mutate(x_rounded = floor(effect1__)) %>% 
-  group_by(x_rounded, plot_var_nice) %>% 
-  slice(1) %>% 
-  ungroup() %>% 
-  mutate(plot_var_nice = fct_relabel(plot_var_nice, ~str_to_sentence(str_remove(., "Barriers to ")))) %>% 
-  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
-  geom_line(size = 0.5, color = "grey90") +
-  geom_pointrange(aes(ymin = lower__, ymax = upper__),
-                  fatten = 1, size = 1) +
-  scale_x_continuous(breaks = 0:9) +
-  scale_color_viridis_d(option = "plasma", end = 0.8) +
-  coord_cartesian(ylim = c(0.60, 0.71)) +
-  guides(color = "none") +
-  labs(x = NULL,
-       y = "Predicted civil liberties index",
-       title = "Private civil liberties index",
-       caption = "(Higher values = better protection)") +
-  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
-  theme_ngo() +
-  theme(panel.grid.major.x = element_blank())
-
+```{r plot-mfx-e1b-e1d, fig.width=7.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on V-Dem rights indexes and latent human rights"}
 out_mfx_e1d <- mfx_e1d_lhr %>% 
@@
   ungroup() %>% 
-  mutate(plot_var_nice = fct_relabel(plot_var_nice, ~str_to_sentence(str_remove(., "Barriers to ")))) %>% 
+  mutate(plot_var_nice = fct_relabel(
+    plot_var_nice, ~str_to_sentence(str_remove(., "Barriers to ")))) %>% 
   ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
@@
 
-out_mfx_e1b / out_mfx_e1c / out_mfx_e1d
+out_mfx_e1d
 ```
@@
 As de facto CSO repression increases, though, the probability of seeing Level 1 decreases and is replaced with either Level 2 or Level 3.
-More severe levels of political terror remain exceptionally improbable at any level of preceding civil society repression.
+More severe levels of political terror remain exceptionally improbable at any level of preceding civil society repression—we again collapse these into a single category.
 
@@
 out_mfx_e2a <- mfx_e2a_pts %>% 
+  mutate(effect2__ = fct_collapse(effect2__, "3+" = c("3", "4", "5"))) %>% 
+  group_by(effect1__, effect2__, plot_var_nice) %>% 
+  summarize(across(c(estimate__, lower__, upper__), sum)) %>% 
+  ungroup() %>% 
   ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
@@
   scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_color_viridis_d(option = "rocket", end = 0.75, direction = -1) +
-  scale_fill_viridis_d(option = "rocket", end = 0.9, direction = -1) +
+  scale_color_viridis_d(option = "rocket", begin = 0.1, end = 0.75, direction = -1) +
+  scale_fill_viridis_d(option = "rocket", begin = 0.1, end = 0.9, direction = -1) +
   labs(x = "Civil society repression",

### 2021-11-12 manuscript/manuscript.Rmd
Change modelummary global option

@@
   kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
-  modelsummary_default = table_format  # Set modelsummary backend
+  modelsummary_factory_default = table_format  # Set modelsummary backend
 )

### 2021-11-12 manuscript/manuscript.Rmd
Add siunitx support

--- 2021-11-12 manuscript/manuscript.Rmd
@@
   kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
-  modelsummary_default = table_format  # Set modelsummary backend
+  modelsummary_factory_default = table_format,  # Set modelsummary backend
 )
+}
 ```

### 2021-11-12 manuscript/manuscript.Rmd
more modelsummary stuff

--- 2021-11-12 manuscript/manuscript.Rmd
@@
   kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
-  modelsummary_default = table_format  # Set modelsummary backend
+  modelsummary_factory_default = table_format,  # Set modelsummary backend
+  modelsummary_format_numeric_latex = "plain"  # Don't use siunitx
 )
+
+# modelsummary regression table notes
+if (is_latex) {
+  model_note <- "Posterior means; 95\\\\% credible intervals in brackets" 
+} else {
+  model_note <- "Posterior means; 95% credible intervals in brackets"
+}
 ```

### 2021-11-12 manuscript/manuscript.Rmd
Address R2's issues 10, 11, 12, and 14—RIP V-Dem repression :(

@@
 library(brms)
+library(emmeans)
+library(broom.mixed)
 
@@
              m_clpriv_total, m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding,
-             m_pts_v2csreprss, m_clphy_v2csreprss, m_clpriv_v2csreprss))
+             m_pts_v2csreprss, m_clphy_v2csreprss, m_clpriv_v2csreprss, m_lhr_v2csreprss))
 
@@
 As seen in Figure \@ref(fig:civicus-map), by the end of 2020, only `r civicus$Open$prop_nice` of countries had open and unrestricted civic space [@civicusmonitor; @ChaudhryHeiss:2021].[^open]
+
+[^open]: Following CIVICUS, open civic space in a country indicates that the state enables and safeguards citizens' freedom to form associations, authorities are tolerant of criticism from CSOs, and that laws governing freedom of peaceful assembly adhere to international laws and standards.
 
@@
 
-In this paper, we explore the power of anti-NGO repression in predicting human rights abuses, political terror, physical violence, and violations of private civil liberties.
+In this paper, we explore the power of anti-NGO repression in predicting political terror and underlying human rights abuses.
 We argue that information about NGO crackdown can be a valuable indicator of human rights trajectories.
@@
 We differentiate between two forms of NGO repression: official de jure anti-NGO restrictions that are codified in law, and their de facto implementation.
-Using multilevel Bayesian modeling, we find that formal de jure laws provide very little additional information when attempting to predict future repression.
+Using multilevel Bayesian modeling, we find that formal de jure laws potentially provide a weak signal of future repression.
 However, we find that accounting for their implementation does boost our models' predictive power.
-Increasing de facto civil society repression predicts an increase in the probability of moderate political terror and results in worsening violations of physical integrity rights and civil liberties.
+Increasing de facto civil society repression, on the other hand, predicts both a moderate increase in the probability of moderate political terror and a deterioration in the overall respect for human rights in a typical country.
 
@@
 - **Empirical expectation 1** (effect of de jure NGO repression): If a country imposes a formal anti-NGO law, then it is likely to signal future deteriorating human rights conditions.
-- **Empirical expectation 2** (effect of de facto NGO repression): If a country represses civil society, then it is likely to signal future deteriorating human rights conditions.
+- **Empirical expectation 2** (effect of de facto NGO repression): If a country implements its formal anti-NGO laws and represses civil society, then it is likely to signal future deteriorating human rights conditions.
 
@@
   "Political Terror Scale (PTS)", NA, "Ordered category ranging from 1 (least terror) to 5 (most terror)", "(ref:pts)",
-  "Physical violence index", NA, "0–1; higher values indicate less violence", "(ref:vdem); v2x_clphy",
-  "Private civil liberties index", NA, "0–1; higher values indicate greater respect for civil liberties", "(ref:vdem); v2x_clpriv",
   "Latent human rights values", NA, "≈ −3–5; higher values indicate greater respect for human rights", "(ref:lhr)",
@@
         booktabs = TRUE, linesep = "\\addlinespace") %>% 
-    pack_rows(index = c("Outcomes" = 4, "Predictors" = 5),
+    pack_rows(index = c("Outcomes" = 2, "Predictors" = 5),
               indent = FALSE) %>% 
@@
     insert_row("Outcomes", "", "", "", after = 1) %>% 
-    insert_row("Predictors", "", "", "", after = 6) %>% 
+    insert_row("Predictors", "", "", "", after = 4) %>% 
     set_bold(1, everywhere) %>%
-    set_bold(c(2, 7), everywhere) %>%
-    set_bottom_border(c(2, 7), everywhere) %>%
+    set_bold(c(2, 5), everywhere) %>%
+    set_bottom_border(c(2, 5), everywhere) %>%
     set_width(1) %>% 
@@
 To measure de jure repression, we use data on anti-NGO laws from @Chaudhry:2016 which includes official NGO laws for all countries (excluding micro-states) between 1990 and 2013.
-We create indices of the total number of laws passed in each country based on three broad categories of laws related to barriers to entry, funding, and advocacy, and we also sum each of these indices to create a count of total legal barriers.
-We also create a yearly indicator variable to show if a country increased its count of anti-NGO laws (models using this outcome are included in the online appendix).
-
-- Barriers to advocacy (2 possible barriers): NGOs are restricted from engaging in political activities, and advocacy restrictions differ if the NGO receives foreign funding
-- Barriers to entry (3 possible barriers): registration is burdensome, NGOs are not allowed to appeal if denied registration, and entry requirements differ if the NGO receives foreign funding
-- Barriers to funding (5 possible barriers): NGOs need prior approval to receive foreign funding, NGOs are required to channel foreign funding to state-owned banks, NGOs face additional restrictions if receiving foreign funding, and NGOs are prohibited from receiving foreign funding
+This measure of formal legal barriers does not necessarily represent individual laws.
+Instead, we count the presence or absence of specific types of anti-NGO legal barriers as a binary variable.
+If a country passes a broader NGO laws that implements several of these barriers simultaneously (e.g.
+making registration burdensome and restricting foreign funds), the values for each barrier will flip from 0 to 1.
+We create indices of the total number of legal barriers in each country based on three broad categories of laws: barriers to entry, funding, and advocacy.
+We also sum each of these indices to create an overall count of legal barriers.
+
+- **Barriers to advocacy** (2 possible barriers): (1) NGOs are restricted from engaging in political activities, and (2) advocacy restrictions differ if the NGO receives foreign funding
+- **Barriers to entry** (3 possible barriers): (1) registration is burdensome, (2) NGOs are not allowed to appeal if denied registration, and (3) entry requirements differ if the NGO receives foreign funding
+- **Barriers to funding** (5 possible barriers): (1) NGOs need prior approval to receive foreign funding, (2) NGOs are required to channel foreign funding to state-owned banks, (3) NGOs face additional restrictions if receiving foreign funding, and (4) NGOs are restricted or (5) prohibited from receiving foreign funding
 
@@
 
-To measure de facto civil society repression in a country, we use Varieties of Democracy's (V-Dem) CSO repression indicator (`v2csreprss` in @vdem-v10), which captures the extent to which governments harass, deter, liquidate, and arrest members of civil society organizations.
+To measure de facto civil society repression in a country, we use the Varieties of Democracy's (V-Dem) CSO repression indicator (`v2csreprss` in @vdem-v10), which captures the extent to which governments harass, deter, liquidate, and arrest members of civil society organizations.
+This variable captures repression using an ordinal scale, defining civil society repression as severe, substantial, moderate, weak, or absent.
+This ordinal scale is then aggregated with a Bayesian item response theory measurement model and converted to a continuous scale that ranges from roughly −3 to 3, with higher values indicating less repression.
+
 Figure \@ref(fig:barriers) shows each of these types of legal barriers per country over time, as well as average levels of de facto civil society repression by regime type.
@@
 To see how both de jure and de facto civil society restrictions influence general human rights repression, we use four different quantitative measures of repression, each of which capture different dimensions of political and civil violence.
-First, following @GohdesCarey:2017, who use the killing of journalists to predict worsening human rights conditions, we use the Political Terror Scale (PTS), which assigns countries to five different categories of repression each year [@GibneyCornettWood:2019], with Level 5 representing widespread political violence, including arrests, political murders, disappearances, and torture.
-As seen in the left panel of Figure \@ref(fig:repression), the number of countries at Level 5 has decreased since the 1990s, while most countries are coded as Levels 2 and 3 (moderate levels of political terror).
-
-Because the PTS captures broad notions of political terror with only five possible categories, we also look at three continuous measures of repression.
-From V-Dem, we use a physical violence index (`v2x_clphy`) that measures freedom from torture and political killings specifically, and a private civil liberties index (`v2x_clpriv`) that measures respect for property rights, labor rights, freedom of religion, freedom of movement, and other non-political human rights.
-The middle panel of Figure \@ref(fig:repression) shows that the average level of these two rights indexes has improved over time.
-
-Finally, it is worth noting that these indicators of physical integrity rights violations and political terror may not account for the systematic changes in the way monitoring agencies have gathered information about human rights violations over time.
-To account for this, we use latent human rights scores as a final measure of underlying repression [@Fariss:2014; @FarissKenwickReuning:2020].
-This variable accounts for changing standards of accountability, which has led to the production of more stringent human rights reports as monitors look harder for abuse, look in more places for abuse, and classify more acts as abuse.
-When accounting for these changes, the right panel of Figure \@ref(fig:repression) demonstrates the global improvements in average latent human rights values over time.
-
-```{r repression, fig.width=6.5, fig.height=7, fig.asp=NULL, fig.cap="Key measures of repression over time"}
+First, following @GohdesCarey:2017, who use the killing of journalists to predict worsening human rights conditions, we use the Political Terror Scale (PTS), which assigns countries to one of five possible levels of repression each year [@GibneyCornettWood:2019], with Level 5 representing widespread political violence—including arrests, imprisonment, political murders, disappearances, and torture.
+As seen in the top panel of Figure \@ref(fig:repression), the number of countries at Level 5 has decreased since the 1990s, while most countries are coded as Levels 2 and 3 (moderate levels of political terror).
+
+The five levels of the PTS are helpful for conceptualizing broader trends in human rights abuses.
+However, these categories are not always granular enough to model or predict a country's level of political terror.
+Additionally, the PTS—along with most other measures of human rights abuses—does not account for the systematic changes in the way monitoring agencies have gathered information about human rights violations over time.
+Accordingly, we use latent human rights scores as an alternative measure of underlying repression [@Fariss:2014; @FarissKenwickReuning:2020].
+This variable is generated from a Bayesian measurement model that incorporates information about human rights abuses from a variety of published repression indices, including the PTS.
+Because the resulting measure is continuous, it picks up on more minute changes in national-level human rights.
+Moreover, this variable accounts for changing standards of accountability, which has led to the production of more stringent human rights reports as monitors look harder for abuse, look in more places for abuse, and classify more acts as abuse.
+When accounting for these changes, the bottom panel of Figure \@ref(fig:repression) demonstrates the global improvements in average latent human rights values over time.
+
+```{r repression, fig.width=6.5, fig.height=4.5, fig.asp=NULL, fig.cap="Key measures of repression over time"}
 pts_plot <- canary %>% 
@@
 
-labs_lookup <- tribble(
-  ~name, ~nice_name,
-  "v2x_clphy", "Physical violence index",
-  "v2x_clpriv", "Private civil liberties index"
-) %>% 
-  mutate(nice_name = fct_inorder(nice_name, ordered = TRUE))
-
-df_outcome_plot <- canary %>%
-  select(year, v2x_clphy, v2x_clpriv) %>% 
-  pivot_longer(starts_with("v2x")) %>% 
-  group_by(year, name) %>% 
-  nest() %>% 
-  mutate(cis = data %>% map(~ mean_cl_normal(.$value))) %>% 
-  unnest(cis) %>% 
-  ungroup() %>% 
-  mutate(fake_facet_title = "V-Dem repression") %>% 
-  left_join(labs_lookup, by = "name")
-
-vdem_outcome_plot <- ggplot(df_outcome_plot, aes(x = year, y = y)) +
-  geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = nice_name), alpha = 0.2,) +
-  geom_line(aes(color = nice_name), size = 1) +
-  scale_color_manual(values = c("#433E85", "#4DC36B"), name = NULL) +
-  scale_fill_manual(values = c("#433E85", "#4DC36B"), name = NULL) +
-  coord_cartesian(xlim = c(1990, 2015)) +
-  guides(color = guide_legend(reverse = TRUE),
-         fill = guide_legend(reverse = TRUE)) +
-  labs(y = "Average index value", x = NULL, caption = "(Higher values = less repression)") +
-  theme_ngo(9) +
-  theme(legend.justification = "left",
-        legend.key.height = unit(0.7, "lines"),
-        legend.key.width = unit(1, "lines"),
-        plot.caption = element_text(margin = margin(t = -1, unit = "lines"))) +
-  facet_wrap(vars(fake_facet_title))
-
 df_lhr_plot <- canary %>% 
@@
 
-(pts_plot / vdem_outcome_plot / lhr_plot) &
+(pts_plot / lhr_plot) &
   theme(legend.text = element_text(size = rel(0.7)),
@@
 We do not include a complete set of covariates to remove confounding relationships, but instead use a more parsimonious set of explanatory variables that strongly predict repression.
-Following @GohdesCarey:2017, we control for a country's previous level of repression, its level of democracy as measured by V-Dem's polyarchy index, its logged GDP per capita (measured by the UN), the percent of GDP attributed to trade (measured by the UN), and an indicator for whether the country witnessed more than 25 battle-related deaths (measured by @ucdp2020; @GleditschWallensteenEriksson:2002).
+Following @GohdesCarey:2017, we control for a country's level of repression in the previous year (either PTS score or latent human rights value, depending on the model), its level of democracy as measured by V-Dem's polyarchy index, its logged GDP per capita (measured by the UN), the percent of GDP attributed to trade (measured by the UN), and an indicator for whether the country witnessed more than 25 battle-related deaths (measured by @ucdp2020; @GleditschWallensteenEriksson:2002).
 Because changes in the human rights environment take time to be reflected by these larger indices, we model the effect of lagged explanatory variables on repression one year in the future.
@@
 
-- **Expectation 1~a~**: Anti-NGO laws (total, advocacy, entry, funding separately) signal worsening political terror
-- **Expectation 1~b~**: Anti-NGO laws signal worsening physical violence
-- **Expectation 1~c~**: Anti-NGO laws signal constricting civil liberties
-- **Expectation 1~d~**: Anti-NGO laws signal decreasing latent human rights respect
+- **Expectation 1~a~**: Anti-NGO laws (total; advocacy, entry, funding separately) signal worsening political terror
+- **Expectation 1~b~**: Anti-NGO laws signal decreasing latent human rights respect
 - **Expectation 2~a~**: Civil society repression signals worsening political terror
-- **Expectation 2~b~**: Civil society repression signals worsening physical violence
-- **Expectation 2~c~**: Civil society repression signals constricting civil liberties
-- **Expectation 2~d~**: Civil society repression signals decreasing latent human rights respect
+- **Expectation 2~b~**: Civil society repression signals decreasing latent human rights respect
 
@@
 Because the PTS is measured as an ordered category, we use ordered logistic regression to predict future values of the scale.
-As V-Dem's physical violence index and private civil liberties index and latent human rights values are all measured continuously, we predict these values with Gaussian models.
+We predict the continuous latent human rights values with Gaussian models.
 The appendix contains complete details of our modeling approach.
@@
 above or below) exceeds 0.95.
-
-[^open]: Following CIVICUS, open civic space in a country indicates that the state enables and safeguards citizens' freedom to form associations, authorities are tolerant of criticism from CSOs, and that laws governing freedom of peaceful assembly adhere to international laws and standards.
 
@@
 The results of the ordered logistic regression models can be unwieldy to interpret with plain numbers due to varying intercepts and thresholds between PTS levels.
-Accordingly, we present graphical results for all our models wherever possible and include complete tables of model results in the appendix (see Tables \@ref(tab:tbl-models-pts), \@ref(tab:tbl-models-clphy), \@ref(tab:tbl-models-clpriv), and \@ref(tab:tbl-models-lhr)).
+Accordingly, we present graphical results for all our models wherever possible and include complete tables of model results in the appendix (see Tables \@ref(tab:tbl-models-pts) and \@ref(tab:tbl-models-lhr)).
 For ease in comparing the count of NGO laws with civil society repression, we reverse the x-axis in the marginal effects plots for our second empirical expectation so that increasing the civil society repression represents *worse* repression rather than less.
@@
 
-Figure \@ref(fig:plot-mfx-e1b-e1d) shows the marginal effects of additional NGO legislation on V-Dem's physical violence index and private civil liberties index.
-Across all four models for different categories of legal barriers, holding all other values constant, neither rights index moves much in response to new NGO laws.
-Each barrier-based posterior coefficient is essentially zero with narrow credible intervals that include large proportions of both negative and positive values.
-Within the categories of anti-NGO laws, it appears that additional advocacy and entry laws might reduce future violence, but again, these predictions are indistinguishable from each other.
-The null effect of legal barriers on private civil liberties is even more stark—a typical country is predicted to have a score of 0.69 regardless of the addition of any kind of NGO law.
-However, when looking at latent human rights values, adding a new NGO law is associated with a -0.013 decline in the level of respect for human rights in the following year, on average.
+Figure \@ref(fig:plot-mfx-e1b) shows the marginal effects of additional NGO legislation on latent human rights scores.
+Across all four models for different categories of legal barriers, holding all other values constant, the predicted level of human rights respect decreases.
+Adding a new NGO law is associated with a -0.013-point decline in the level of respect for human rights in the following year, on average.
 The marginal effect is larger (-0.02) for additional barriers to advocacy and entry, which represent more burdensome restrictions than limits to funding.
 
-At a marginal level, therefore, adding additional anti-NGO laws in countries with low levels of political terror could signal (albeit weakly) that higher levels of political repression are more likely in the future.
+At a marginal level, therefore, adding additional anti-NGO laws in countries with low levels of political terror could signal that higher levels of political repression are more likely in the future.
 Limited repression remains the most likely possible outcome, but the chance of seeing robust rule of law decreases rapidly as more laws are passed, all else equal.
-When looking at other forms of political repression, though, such as physical violence and private civil liberties, NGO legal barriers do not change predicted values in any meaningful way.
-
-```{r plot-mfx-e1b-e1d, fig.width=7.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on V-Dem rights indexes and latent human rights"}
-out_mfx_e1d <- mfx_e1d_lhr %>% 
+This pattern holds when looking at a more continuous measure of human rights protection—countries with a low count of anti-NGO legal barriers tend to have higher predicted values of latent human rights scores, and average protection against abuses decreases as more laws are added.
+
+```{r plot-mfx-e1b, fig.width=7.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on latent human rights scoress"}
+# TODO: Andrew: Add more specific coefficients and percent changes to the prose above
+out_mfx_e1b <- mfx_e1d_lhr %>% 
   mutate(x_rounded = floor(effect1__)) %>% 
@@
 
-out_mfx_e1d
+out_mfx_e1b
 ```
@@
 
-The weak (or even non-existent) predictive power of formal NGO laws is likely attributable to fact that de jure NGO legislation may take time to implement - many states need to first establish institutions that oversee the operation and funding of these groups or incorporate threatening NGOs into the regime apparatus (Naim 2007).
+The weaker predictive power of formal NGO laws is likely attributable to fact that de jure NGO legislation may take time to implement—many states need to first establish institutions that oversee the operation and funding of these groups or incorporate threatening NGOs into the regime apparatus [@Naim:2007].
 Further, states that engage in political repression can do so with or without legal justification.
 De facto civil society repression, on the other hand, represents the actual implementation of anti-NGO strategies—both legal and extralegal—and might be more indicative of future human rights abuses.
-The results from our second set of models, using V-Dem's civil society repression index as the key predictor, confirm this.
+The results from our second set of models, using V-Dem;s civil society repression index as the key predictor, confirm this.
 
@@
 
-In contrast with formal laws, civil society repression does have a noticeable effect on the predicted values of the other rights indexes (see Figure \@ref(fig:plot-mfx-e2b-e2d)).
-When holding all other model parameters at their typical values, increased civil society repression predicts increases in both the physical violence index and private civil liberties index: a one standard deviation change in civil society repression is associated with a 0.02 change in overall rights.
-In other words, a typical country with a civil society repression score of 0 is predicted to have a physical violence index of 0.62 and civil liberties index of 0.67.
-This implies that an increase in de facto NGO restrictions predicts a `r percent_format(accuracy = 1)((0.62 - (0.62 - 0.02)) / (0.62 - 0.02))` decline in both protection from physical violence and respect for private civil liberties in the following year.
-Moreover, worsening civil society repression is strongly associated with a worse future human rights environment, as seen in the right panel of Figure \@ref(fig:plot-mfx-e2b-e2d).
+```{r lhr-trends, include=FALSE, warning=FALSE}
+lhr_csreprss_stats <- m_lhr_v2csreprss %>% 
+  tidy(effects = "fixed") %>% 
+  mutate(term = janitor::make_clean_names(term)) %>%
+  split(.$term)
+
+lhr_csreprss_diffs <- m_lhr_v2csreprss %>% 
+  emmeans(~ v2csreprss + gwcode, var = "v2csreprss", 
+           at = list(gwcode = 999,
+                     v2csreprss = c(0, -1)),
+           epred = TRUE, re_formula = NULL,
+           allow_new_levels = TRUE, sample_new_levels = "gaussian") %>% 
+  tidy() %>% 
+  mutate(pct_change = (estimate - lag(estimate)) / lag(estimate),
+         id = janitor::make_clean_names(v2csreprss)) %>% 
+  split(.$id)
+```
+
+De facto civil society repression has a noticeable effect on latent human rights values (see Figure \@ref(fig:plot-mfx-e2b)).
+When holding all other model parameters at their typical values, increased civil society repression predicts a strong decrease in respect for broader human rights: a one unit change in civil society repression is associated with a `r round(lhr_csreprss_stats$v2csreprss$estimate, 2)`-unit change in overall latent human rights.
+To illustrate the magnitude of this effect, a typical simulated country with a civil society repression index of 0 is predicted to have a latent human rights score of `r round(lhr_csreprss_diffs$x0$estimate, 2)`.
+This predicted outcome drops to `r round(lhr_csreprss_diffs$x1$estimate, 2)` with a 1-unit decrease in civil society repression, representing a `r percent_format(accuracy = 1)(abs(lhr_csreprss_diffs$x1$pct_change))` decline in respect for human rights in the following year.
 
 When holding all other factors equal, the de facto implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passage of formal de jure laws.
-In countries with low levels of political terror, it can potentially serve as a weak signal of a more general increase in political violence in the future, but predict more substantial changes in physical integrity rights, threats to civil liberties, and respect for human rights.
+In countries with low levels of political terror, it can potentially serve as a weak signal of a more general increase in political violence in the future, but predict more substantial changes in general respect for human rights.
 The difference in the effects of laws vs.
@@
 
-```{r plot-mfx-e2b-e2d, fig.width=9.5, fig.height=3.5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on V-Dem rights indexes and latent human rights"}
-out_mfx_e2b <- mfx_e2b_clphy %>% 
-  ggplot(aes(x = effect1__, y = estimate__)) +
-  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
-              fill = "#433E85", color = NA) +
-  geom_line(size = 1, color = "#433E85") +
-  scale_x_reverse() +
-  coord_cartesian(ylim = c(0.5, 0.75)) +
-  labs(x = "Civil society repression",
-       y = "Predicted physical violence index",
-       title = "Physical violence index") +
-  theme_ngo(8)
-
-out_mfx_e2c <- mfx_e2c_clpriv %>% 
-  ggplot(aes(x = effect1__, y = estimate__)) +
-  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
-              fill = "#4DC36B", color = NA) +
-  geom_line(size = 1, color = "#4DC36B") +
-  scale_x_reverse() +
-  coord_cartesian(ylim = c(0.5, 0.75)) +
-  labs(x = "Civil society repression",
-       y = "Predicted civil liberties index",
-       title = "Private civil liberties index") +
-  theme_ngo(8)
-
+```{r plot-mfx-e2b, fig.width=6.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on latent human rights"}
+# TODO: Combine with previous plot so there's just one, with fake facet titles
 out_mfx_e2d <- mfx_e2d_lhr %>% 
@@
        y = "Predicted latent human rights value",
-       title = "Latent human rights") +
+       title = "Latent human rights", 
+       caption = "(x-axis reversed; greater repression on right\nhigher values in y-axis show less violence and better protection of rights)") +
   theme_ngo(8)
-
-(out_mfx_e2b | out_mfx_e2c | out_mfx_e2d) +
-  plot_annotation(caption = "(x-axis reversed; greater repression on right\nhigher values in y-axis show less violence and better protection of rights)",
-                  theme = theme(plot.caption = element_text(size = rel(0.8), color = "grey50", face = "plain",
-                                      family = "Inter Light",
-                                      margin = margin(t = 5))))
+out_mfx_e2d
 ```
@@
 ## Predictions
+
+```{r eval=FALSE, include=FALSE}
+# TODO: Andrew: Streamline this section
+```
 
@@
 tbl_rmse <- tribble(
-                      ~Model,     ~RMSE, ~`% change from baseline`,
-                  "Baseline", 0.0462298,                       "—",
-      "Total legal barriers", 0.0460839,                  "-0.32%",
-      "Barriers to advocacy", 0.0460425,                  "-0.41%",
-         "Barriers to entry", 0.0461553,                  "-0.16%",
-       "Barriers to funding", 0.0462081,                  "-0.05%",
-  "Civil society repression",  0.046175,                  "-0.12%",
-                  "Baseline",  0.033909,                       "—",
-      "Total legal barriers", 0.0333961,                  "-1.51%",
-      "Barriers to advocacy", 0.0336028,                  "-0.90%",
-         "Barriers to entry", 0.0334257,                  "-1.43%",
-       "Barriers to funding", 0.0335855,                  "-0.95%",
-  "Civil society repression", 0.0332081,                  "-2.07%",
+  ~`Latent human rights values`,  ~RMSE, ~`% change from baseline`,
                   "Baseline", 0.1861944,                       "—",
@@
 
-tbl_rmse_caption <- "Root mean squared error across models predicting physical violence, private civil liberties, and latent human rights"
+tbl_rmse_caption <- "Root mean squared error across models predicting latent human rights"
 
@@
         caption = tbl_rmse_caption) %>% 
-    pack_rows(index = c("Physical violence index" = 6, 
-                        "Private civil liberties index" = 6,
-                        "Latent human rights values" = 6)) %>% 
     kable_styling()
@@
     set_align(everywhere, 2:3, "center") %>% 
-    insert_row("Physical violence index", "", "", after = 1) %>% 
-    insert_row("Private civil liberties index", "", "", after = 8) %>% 
-    insert_row("Latent human rights values", "", "", after = 15) %>% 
     set_bold(1, everywhere) %>%
-    set_bold(c(2, 9, 16), everywhere) %>%
-    set_bottom_border(c(2, 9, 16), everywhere) %>%
     set_width(1) %>% 
@@
 \begin{aligned}
-y_{i, t+1} \mid u_i, x_{i, t} \sim&\ \operatorname{Ordered Logistic}(y^*_{i, t + 1}, \sigma^2_m) & \text{[likelihood for ordinal PTS models]} \\
-y_{i, t+1} \mid u_i, x_{i, t} \sim&\ \mathcal{N}(y^*_{i, t + 1}, \sigma^2_m) & \text{[likelihood for Gaussian V-Dem models]} \\
-y^*_{i, t + 1} =&\ \beta_0 + \beta_1 \text{Civil society repression}_{i, t} + & \text{[model with covariates]}\\
+& \textbf{Likelihoods} \\
+y_{i, t+1} \sim&\ \operatorname{Ordered Logistic}(y^*_{i, t + 1}, \sigma^2_m) & \text{[PTS]} \\
+y_{i, t+1} \sim&\ \mathcal{N}(y^*_{i, t + 1}, \sigma^2_m) & \text{[latent human rights]} \\
+\ \\
+& \textbf{Parameters} \\
+y^*_{i, t + 1} =&\ \alpha_i + \beta_1 \text{Civil society repression}_{i, t} + & \text{[model with covariates]}\\
 &\ \beta_2 \text{Civil society repression}_{i, t - 1} + \\
@@
 &\ \beta_6 \text{Trade as } \% \text{ of GDP}_{i, t} + \\
-&\ \beta_7 \text{Armed conflict}_{i, t} + u_i + \sigma^2_e \\
-u_i =&\ \mathcal{N}(0, \sigma^2_u) & \text{[country-specific intercepts]} \\
+&\ \beta_7 \text{Armed conflict}_{i, t} + \sigma^2_e \\
+\alpha_i =&\ \mathcal{N}(0, \sigma^2_\alpha) & \text{[country-specific intercepts]} \\
 \ \\
-\beta_0 \sim&\ \mathcal{N}(0, 10) & \text{[prior population intercept]} \\
-\beta_{1-7} \sim&\ \mathcal{N}(0, 3) & \text{[prior population effects]} \\
-\sigma^2_m, \sigma^2_e, \sigma^2_u \sim&\ \operatorname{Cauchy}(0, 1) & \text{[prior sd for model, population, and country error]} \\
+& \textbf{Priors} \\
+\alpha \sim&\ \mathcal{N}(0, 10) & \text{[population intercept]} \\
+\beta_{1-7} \sim&\ \mathcal{N}(0, 3) & \text{[population effects]} \\
+\sigma^2_m, \sigma^2_e, \sigma^2_\alpha \sim&\ \operatorname{Cauchy}(0, 1) & \text{[sd for model, population,} \\
+&&\text{and country error]}
 \end{aligned}
@@
                             caption = tbl_reg_pts_caption,
-                            notes = list("Posterior means; 95% credible intervals in brackets"),
+                            notes = c(model_note),
                             longtable = TRUE)
@@
 
-```{r tbl-models-clphy}
-model_names_tbl_clphy <- c("Total barriers",
-                           "Barriers to advocacy",
-                           "Barriers to entry",
-                           "Barriers to funding",
-                           "Civil society repression")
-
-names(models_paper_clphy) <- model_names_tbl_clphy
-
-tbl_reg_clphy_caption <- "Full results from Gaussian regression models predicting physical violence"
-
-tbl_reg_clphy <- modelsummary(models_paper_clphy,
-                              output = table_format,
-                              statistic = "[{conf.low}, {conf.high}]",
-                              coef_map = coef_list,
-                              gof_omit = "ELPD",
-                              escape = FALSE,
-                              caption = tbl_reg_clphy_caption,
-                              notes = list("Posterior means; 95% credible intervals in brackets"),
-                              longtable = TRUE)
-
-if (!is_docx) {
-  tbl_reg_clphy %>% 
-    kable_styling() %>% 
-    add_header_above(header = c(" " = 1, "Outcome in t + 1" = 5))
-    # kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
-    # column_spec(1, width = "0.10\\\\textwidth") %>% 
-    # column_spec(2:6, width = "0.14\\\\textwidth")
-} else {
-  tbl_reg_clphy %>% 
-    set_font_size(10) %>% 
-    set_all_padding(1) %>% 
-    set_align(everywhere, 2:6, "center") %>% 
-    set_bold(1, everywhere) %>% 
-    set_width(1) %>% 
-    set_wrap(TRUE) %>% 
-    huxtable::set_caption(tbl_reg_clphy_caption) %>% 
-    huxtable::as_flextable()
-}
-```
-
-\clearpage
-
-```{r tbl-models-clpriv}
-model_names_tbl_clpriv <- c("Total barriers",
-                            "Barriers to advocacy",
-                            "Barriers to entry",
-                            "Barriers to funding",
-                            "Civil society repression")
-
-names(models_paper_clpriv) <- model_names_tbl_clpriv
-
-tbl_reg_clpriv_caption <- "Full results from Gaussian regression models predicting private civil liberties"
-
-tbl_reg_clpriv <- modelsummary(models_paper_clpriv,
-                               output = table_format,
-                               statistic = "[{conf.low}, {conf.high}]",
-                               coef_map = coef_list,
-                               gof_omit = "ELPD",
-                               escape = FALSE,
-                               caption = tbl_reg_clpriv_caption,
-                               notes = list("Posterior means; 95% credible intervals in brackets"),
-                               longtable = TRUE)
-
-if (!is_docx) {
-  tbl_reg_clpriv %>% 
-    kable_styling() %>% 
-    add_header_above(header = c(" " = 1, "Outcome in t + 1" = 5))
-    # kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
-    # column_spec(1, width = "0.10\\\\textwidth") %>% 
-    # column_spec(2:6, width = "0.14\\\\textwidth")
-} else {
-  tbl_reg_clpriv %>% 
-    set_font_size(10) %>% 
-    set_all_padding(1) %>% 
-    set_align(everywhere, 2:6, "center") %>% 
-    set_bold(1, everywhere) %>% 
-    set_width(1) %>% 
-    set_wrap(TRUE) %>% 
-    huxtable::set_caption(tbl_reg_clpriv_caption) %>% 
-    huxtable::as_flextable()
-}
-```
-
-\clearpage
-
 ```{r tbl-models-lhr}
@@
                             caption = tbl_reg_lhr_caption,
-                            notes = list("Posterior means; 95% credible intervals in brackets"),
+                            notes = c(model_note),
                             longtable = TRUE)

### 2021-11-15 manuscript/manuscript.Rmd
Suparna edits

@@
 By looking at laws *and* their implementation, as well as the extra-legal treatment of NGOs, we are able to assess the long-term effects of closing civic space on broader patterns of repression.
+
+Second, by examining the growth in anti-NGO laws and their effects on patterns of human rights abuses, our results also have important implications for understanding the future of human rights legislation.
+Existing research on international human rights law shows that civil society groups play an important role in highlighting states' violations of their treaty commitments.
+By revealing the gap between treaty provisions and actual state behavior, these organizations play a vital role in reducing the "compliance gap" between legal commitments and state practices [@Hathaway:2002; @HafnerBurtonTsutsui:2005; @Simmons:2009].
+The dramatic rise in anti-NGO laws and their implementation through de facto civil society repression threatens to exacerbate this compliance gap.
+Indeed, recent research finds that when governments have committed to human rights treaties and continue to commit severe human rights abuses, they impose anti-NGO laws to escape monitoring [@Bakke2020].
+Our findings support these arguments by showing that de facto levels of NGO repression are a possible predictor of broader patterns of human rights violations.
 
@@
 Strengthening civil society is an important precondition for democratic transition and consolidation.
-When governments restrict civil society, it reduces these organizations' ability to maintain accountability and protect against abuse.
-Given these potential knock-on effects, in this paper, we posited that the ongoing global crackdown on NGOs could predict worsening human rights abuses and levels of political and civil rights repression.
-Using original data on de jure and de facto NGO repression from 1990-2013, we find little support for the predictive power of de jure restriction on political terror, physical violence, and violations of private civil liberties.
-Marginal predictions show that, all else held equal, adding new anti-NGO laws increases the probability of seeing moderate levels of political terror, but does not change predicted values of physical integrity or civil liberties rights violations.
-When comparing out-of-sample predictions to a baseline model, including de jure restrictions as predictors does not improve our models' predictive accuracy.
-
-We do, however, find some predictive power when accounting for de facto levels of NGO repression, which includes both legal and extra-legal means of crackdown.
-As with formal laws, rising NGO repression tends to increase the probability of more moderate political terror.
-Additionally, this repression is associated with worsening respect for physical integrity rights and civil liberties in the future.
-In out-of-sample predictions, including civil society restrictions improves model accuracy by 1–2% over the baseline.
-
-Importantly, the lack of predictive power when modeling political violence and the modest improvements in predictive power when modeling civil liberties likely reflects the purpose of NGO restrictions.
-Encroachments on private civil liberties such as restricting freedom of association are not nearly as violent as events like government-sponsored murders.
-In authoritarian states in particular, administrative crackdown on NGOs can also be seen as a careful strategy for autocratic survival.
-Authoritarian leaders must carefully balance domestic and international institutional pressures—including pressure from civil society and NGOs—to remain in power [@Heiss:2019a; @LevitskyWay:2010].
+This article shows dramatic growth in de jure regulations constraining NGOs; laws that can lay the foundation for subsequent de facto repression of civil society.
+Given these potential knock-on effects, in this paper, we posited that the ongoing global crackdown on NGOs could predict worsening human rights abuses.
+Using original data on de jure and de facto NGO repression from 1990–2013, we find weal support for the predictive power of de jure restriction on political terror and overall latent human rights values.
+Marginal predictions show that—all else held equal—adding new anti-NGO laws increases the probability of seeing moderate levels of political terror and is associated with worsening human rights conditions more generally.
+However, in contrast to de jure laws, de facto levels of NGO repression—including both legal and extra-legal means of crackdown—tend to increase the probability of more moderate political terror.
+Additionally, this repression is associated with worsening respect for broader human rights in the future.
+
+Importantly, the weak predictive power of anti-NGO laws by themselves reflects the purpose of NGO restrictions.
+Encroachments on private civil liberties such as restricting freedom of association and funding are not nearly as violent as events like physical integrity rights violations and political terror.
 Anti-NGO laws could possibly be a side effect of authoritarian stability-seeking behavior, similar to election tampering, media censorship, cronyism, and rent-seeking, rather than an overt signal of impending serious human rights abuses.
-
-The global shrinking of civil society is thus not likely an early warning sign for future violent repression—states typically signal their future repressive intentions with more violent methods, such as the persecution and murder of activists and the media.
+The global shrinking of civic space or increasing passage of anti-NGO laws is thus not likely an early warning sign for future violent repression—states typically signal their future repressive intentions with more violent methods, such as the persecution and murder of civil society activists and the media.
 Instead, civil society is a possible "canary in the coal mine" for impending violations of other civil rights, such as the freedom of religion, labor rights, property rights, and the freedom of movement.
+
+However, it is also important to state that while anti-NGO laws do not seem to be a predictor of broader human rights repression over the period under study, it does not imply they are not having a chilling effect on NGO operations.
+The broader literature on state repression of NGOs has shown that de jure laws can have numerous adverse consequences.
+Foreign funding laws have led to a 32% decline in bilateral aid flows [@DP:2018].
+NGOs that are underfunded, understaffed tend to shut down when faced with increasing restrictions [@Heiss:2019].
+In sum, while de jure laws do not effect levels of physical integrity and civil liberties violations, they have been shown to have other adverse consequences in the literature.
+Moreover, since the actual implementation of these laws through de facto civl society repression can have negative impacts of broader patterns of human rights abuses, the passage of these laws may still be a concerning first step that paves the path for implementation.
+
+The dramatic growth in these laws has important implications for the power of the human rights regime and international human rights law.
+The UN Special Rapporteur on the Right to Freedom of Peaceful Assembly and Association has pointed out that the right of NGOs to seek, receive and utilize resources is an essential component of the right to association [@citeme].
+Anti-NGO laws, including barriers to funding, violate core human rights treaties such as the International Covenant on Civil and Political Rights (ICCPR).
+In contrast to the influential work on the impact of transnational advocacy networks and international law, which places immense value on the ability of civil society groups to monitor, shame and reform state behavior, the results in this article show that reforms resulting from international legal pressure and mobilization may be short-lived.
+Rather, states may be learning to counter these dynamics by ramping up repression.
 

### 2021-11-15 manuscript/appendix.Rmd
Move appendix to separate document

--- 2021-11-12 manuscript/manuscript.Rmd
@@
 
-```{r setup, include=FALSE}
-# Figure out output format
-is_docx <- knitr::pandoc_to("docx") | knitr::pandoc_to("odt")
-is_latex <- knitr::pandoc_to("latex")
-is_html <- knitr::pandoc_to("html")
-
-# Word-specific things
-table_format <- ifelse(is_docx, "huxtable", "kableExtra")  # Huxtable tables
-conditional_dpi <- ifelse(is_docx, 300, 300)  # Higher DPI
-conditional_align <- ifelse(is_docx, "default", "center")  # Word doesn't support align
-
-# Knitr options
-knitr::opts_chunk$set(
-  echo = FALSE, warning = FALSE, message = FALSE,
-  tidy.opts = list(width.cutoff = 120),  # Code width
-  fig.retina = 3, dpi = conditional_dpi,
-  fig.width = 7, fig.asp = 0.618,
-  fig.align = conditional_align, out.width = "100%",
-  fig.path = "output/figures/",
-  cache.path = "output/_cache/",
-  fig.process = function(x) {  # Remove "-1" from figure names
-    x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
-    if (file.rename(x, x2)) x2 else x
-  }
-)
-
-# R options
-options(
-  width = 90,  # Output width
-  dplyr.summarise.inform = FALSE,  # Turn off dplyr's summarize() auto messages
-  knitr.kable.NA = "",  # Make NAs blank in kables
-  kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
-  modelsummary_factory_default = table_format,  # Set modelsummary backend
-  modelsummary_format_numeric_latex = "plain"  # Don't use siunitx
-)
-
-# modelsummary regression table notes
-if (is_latex) {
-  model_note <- "Posterior means; 95\\\\% credible intervals in brackets" 
-} else {
-  model_note <- "Posterior means; 95% credible intervals in brackets"
-}
-```
-
-```{r libraries-data, include=FALSE}
-library(tidyverse)
-library(targets)
-library(kableExtra)
-library(modelsummary)
-library(patchwork)
-library(scales)
-library(ggtext)
-library(sf)
-library(here)
-library(brms)
-library(emmeans)
-library(broom.mixed)
-
-withr::with_dir(here::here(), {
-  source(tar_read(plot_funs))
-
-  canary <- tar_read(panel)
-  tar_load(civicus_map_data)
-  tar_load(civicus_clean)
-
-  tar_load(c(m_pts_total, m_pts_advocacy, m_pts_entry, m_pts_funding,
-             m_clphy_total, m_clphy_advocacy, m_clphy_entry, m_clphy_funding,
-             m_clpriv_total, m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding,
-             m_pts_v2csreprss, m_clphy_v2csreprss, m_clpriv_v2csreprss, m_lhr_v2csreprss))
-
-  # Model tables
-  tar_load(c(models_paper_pts, models_paper_clphy, 
-             models_paper_clpriv, models_paper_lhr))
-
-  # Load lookup list for coefficients in regression tables
-  tar_load(coef_list)
-
-  # Load marginal effects
-  tar_load(c(mfx_e1a_pts, mfx_e1b_clphy, mfx_e1c_clpriv, mfx_e1d_lhr,
-             mfx_e2a_pts, mfx_e2b_clphy, mfx_e2c_clpriv, mfx_e2d_lhr))
-})
-```
-
-```{r calc-civicus}
-civicus <- civicus_clean %>%
-  count(category) %>% 
-  mutate(prop = n / sum(n)) %>% 
-  mutate(prop_nice = percent_format(accuracy = 1)(prop)) %>% 
-  split(.$category)
-```
-
-\memSingle
-
-Over the last few decades, governments across the globe have been increasingly cracking down on civil society organizations (CSOs), particularly non-governmental organizations (NGOs)—a phenomenon commonly known as closing or shrinking civic space [@CarothersBrechenmacher:2014; @DPR:2016; @Chaudhry:2016; @DupuyPrakash:2018].
-More than 100 countries have proposed or enacted 244 different measures that have restricted, repressed, or shut down civil society since 2013 [@icnl:2021].
-In Human Rights Watch's 2016 World Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory, and over the past decade, the majority of the world has seen a substantial narrowing of allowable civic space.
-As seen in Figure \@ref(fig:civicus-map), by the end of 2020, only `r civicus$Open$prop_nice` of countries had open and unrestricted civic space [@civicusmonitor; @ChaudhryHeiss:2021].[^open]
-
-[^open]: Following CIVICUS, open civic space in a country indicates that the state enables and safeguards citizens' freedom to form associations, authorities are tolerant of criticism from CSOs, and that laws governing freedom of peaceful assembly adhere to international laws and standards.
-
-```{r civicus-map, fig.cap="2020 CIVICUS Monitor civic space ratings", fig.pos="h"}
-ggplot() +
-  geom_sf(data = civicus_map_data, aes(fill = fct_rev(category)), size = 0.15, color = "black") +
-  coord_sf(crs = st_crs("ESRI:54030"), datum = NA) +  # Robinson
-  scale_fill_viridis_d(option = "rocket", direction = -1,
-                       na.translate = FALSE, name = "Civic space") +
-  theme_void(base_size = 9, base_family = "Inter Light") +
-  theme(legend.position = "bottom",
-        legend.key.size = unit(0.7, "lines"))
-```
-
-This hostility to civil society is not unique to autocratic governments or even illiberal democracies [@AbramowitzSchenkkan:2018]—long-established liberal democracies have also increased restrictions on civil society in their countries.
-Over the past decade, India has canceled the licenses of tens of thousands of NGOs, targeted major groups such as Greenpeace International, Amnesty International and Ford Foundation, and has banned thousands of NGOs from receiving foreign funds [@press-trust-india:2015; @press-trust-india:2019].
-In 2013 Canada attempted to revoke the charitable status of NGOs for opposing the Northern Gateway pipeline and Canadian mining companies' initiatives abroad [@CIVICUS:2013].
-In 2019, activists from the US-based nonprofit No More Deaths were arrested for providing food and water to migrants at the US-Mexico border and faced a 20-year prison sentence before their convictions were overturned in 2020 [@Cramer:2020].
-
-Much of this targeting of NGOs has been non-violent.
-Rather than publicly arrest or beat activists, states implement "administrative crackdown," or the passage of laws to create barriers to NGO advocacy, entry, and funding [@Chaudhry:2016].
-The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations [@Heiss:2019; @Heiss:2017].
-While this can lead to the depoliticization and avoidance of direct political activism by CSOs [@BloodgoodTremblay-Boire:2017], states cannot soften or neutralize all forms of political activity and advocacy in subtle, legal ways like they have with NGOs.
-Sooner or later, states may need to deal with threats to their stability in a more direct, violent, confrontational manner.
-Anti-NGO laws could be an important early warning sign—or a canary in the coal mine—of worsening human rights repression, signaling that a state will continue down the path of further repression.
-What does state targeting of NGOs tell us about the state's broader respect for civil society and the overall level of human rights repression?
-Can the crackdown on NGOs act as a predictor of subsequent increasing repression?
-
-In this paper, we explore the power of anti-NGO repression in predicting political terror and underlying human rights abuses.
-We argue that information about NGO crackdown can be a valuable indicator of human rights trajectories.
-It can act as an early warning signal for worsening repression, suggesting which countries are testing the waters with comparatively "milder" methods of crackdown before enacting more violent forms of repression.
-To assess if attacks on NGOs and activists can provide us useful information about future repression, we use an original dataset on state crackdown on NGOs using legal repression across all countries from 1990–2013.
-We differentiate between two forms of NGO repression: official de jure anti-NGO restrictions that are codified in law, and their de facto implementation.
-Using multilevel Bayesian modeling, we find that formal de jure laws potentially provide a weak signal of future repression.
-However, we find that accounting for their implementation does boost our models' predictive power.
-Increasing de facto civil society repression, on the other hand, predicts both a moderate increase in the probability of moderate political terror and a deterioration in the overall respect for human rights in a typical country.
-
-Our paper makes an important contribution in predicting the onset of repressive state policies.
-While structural factors such as levels of democracy, economic development, electoral competitiveness can identify countries that are likely to have more or less respect for civic freedoms, these factors are also slow to change over time.
-As such, they may not be particularly suitable for forecasting short-term trajectories, especially for moderately repressive countries.
-On the other hand, state repression of NGOs is a more dynamic process that may provide insight into changing levels of human rights standards and repression in subsequent years.
-While recent research has made important contributions to studying the extent and effects of state crackdown on NGOs, much of this focuses on de jure restrictions and its impact on NGOs and donors [@christensen2013; @DPR:2016; @DupuyPrakash:2018; @BromleySchoferLonghofer:2020; @BakkeMitchellSmidt:2020; @SmidtPereraMitchell:2021].
-By looking at laws *and* their implementation, as well as the extra-legal treatment of NGOs, we are able to assess the long-term effects of closing civic space on broader patterns of repression.
-
-Below, we first look at existing literature on repression and political violence, outlining state motivations to repress NGOs.
-We then elaborate on why attacking NGOs may be an important predictor of subsequent repression.
-Using both original data as well as data from several existing datasets, we build an ensemble of predictive models and explore (1) the marginal effects of civil society repression on different forms of broader human rights repression, and (2) the out-of-sample predictive performance of each model.
-We conclude by discussing the implications of our findings on autocratic survival, and how states may manage NGOs as a strategy to remain in power.
-
-# Government repression and NGO restrictions
-
-Repression is the use of coercive action against an individual or organization, within the territorial jurisdiction of the state, for the purpose of imposing a cost on the target as well as deterring specific activities perceived to be challenging to government personnel, practices, or institutions [@Goldstein:1978, p.
-xxvii; @Davenport:2007, 487; and @ConradRitter:2019, 15].
-Early literature on repression focused on the role of structural factors such as levels of democracy, economic development, and electoral competitiveness in predisposing a state to the increased use of repression.
-Most notably, democratic forms of government—and democratization in general—has a pacifying effect on state repression [@DavenportArmstrong:2004; @Krain:1997; @Richards:1999].
-Democracies have a negative effect on repression largely because of the increased probability of sanctions against authorities for undesirable behavior [@Davenport:2007a, 47].
-
-More recent research focuses on how the behavior of various actors shapes government response.
-One of the most consistent findings in the political violence literature is that authorities repress to counter ongoing challenges to the status quo.
-In other words, dissent increases repressive behavior [@Davenport:2007].
-However, dissent and repression have an endogenous relationship: state authorities also frequently engage in preventive repression to undermine or restrict groups' abilities to dissent [@RitterConrad:2016; @ConradRitter:2019].
-Such preventive repression also damages organizations' capacity to impose costs [@Davenport:2007a, 47].
-NGOs are one actor that can pose challenges to political authorities, and state repression of these actors, especially through legal restrictions can be considered a form of preventive repression [@Chaudhry:2016].
-
-This preventive repression of NGOs is a recent phenomenon.
-While many saw the initial proliferation of NGOs in the 1980s and 1990s as leading to a "symbiotic relationship" between NGOs and states due to their mutual goals, this perception changed over time [@Reimann:2006, 63].
-With expanded powers and their perceived role in the Color Revolutions, NGOs began to be seen as having a real influence on domestic and international politics [@CarothersBrechenmacher:2014].
-State perception of NGOS as threatening became pervasive as these organizations demonstrated their ability to influence electoral politics [@DPR:2016; @Weiss:2009], mobilize aid [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
-
-Given this threat, a number of states decided to repress threatening NGOs.
-While violence is often effective at curbing dissent, it can also backfire, leading to widespread protests, decreasing leaders' legitimacy and increasing their criminal liability [@KimSikkink:2010; @Sikkink:2011].
-In contrast to violence, administrative crackdown has fewer adverse consequences—citizens may see it as regulation rather than repression, resulting in little to no counter-mobilization.
-It may also circumvent concerns among state security or bureaucratic agents about illegitimate orders based on violent repression [@StephanChenoweth:2008].
-There are also fewer international consequences since laws—unlike violence—rarely invite condemnation or threats of aid withdrawal [@CarothersBrechenmacher:2014].
-
-This administrative crackdown via anti-NGO laws may foreshadow future government transgressions.
-Autocratic leaders want to avoid accountability, and NGOs often stand in conflict with that goal.
-Civil society organizations, including NGOs, can help shape the narrative of leaders' performance both domestically and internationally.
-Monitoring by NGOs and subsequent shaming can include significant external revenue loss to states in the form of loss of aid, trade, and foreign direct investments [@KeckSikkink:1998; @BarryClayFlynn:2013].
-Government attempts to repress NGOs can signal the beginning of a deteriorating human rights situation.
-Such repression reflects the government's willingness and capability to use measures that can make it avoid accountability.
-Once a state targets NGOs, over time it may grow less hesitant to apply violent repression more widely and more severely.
-
-In exploring the impact of state crackdown on NGOs on subsequent human rights conditions, we look at both *de jure* measures—or formal legislation that seeks to repress NGOs—as well as the *de facto* implementation of these measures.
-This distinction is important—while states may pass anti-NGO laws, these laws can also lie dormant until governments feel the need to enforce them.
-For instance, Russia passed its 2015 Undesirable Organizations Law with the purpose of targeting and eliminating specific foreign-connected NGOs it deemed dangerous.
-One of the law's sponsors, Aleksandr Tarnavsky, described the law as a preventive measure that would not affect the majority of NGOs working in Russia.
-Rather, the law would be a "weapon hanging on the wall that never fires" and stand as a warning to potentially uncooperative NGOs [@Kozenko:2015].
-Similarly, Egypt's 2002 NGO law instated severe barriers to freedom of association, banned NGOs from engaging in activities that "threaten national unity or violate public order or morality," and also prevented groups from receiving foreign funding.
-But despite the harsh legal framework, the Egyptian NGO sector nearly doubled in size between 1993–2011.
-This is because the state targeted a limited number of organizations working on politically sensitive issues such as human rights and democracy, while simultaneously tolerating organizations working on tamer issues [@Brechenmacher:2017].
-
-Simply noting the passage of (or counting) these laws may therefore miss the effect of their de facto implementation.
-Moreover, the implementation of these laws may not be limited to its legal character.
-The government may also engage in harassment of NGOs and activists to dissuade NGOs from carrying out their operations.
-This may include measures such as detentions, short-term incarceration, as well as beatings, threats to families and destruction of valuable property.
-
-Finally, counting official laws can also undermeasure civil society repression because governments can repress NGOs without relying on formal laws.
-As prior research in Egypt, Ethiopia, and Russia points out, "rather than systematically enforcing all repressive legal measures-often impossible owing to capacity constraints," governments may choose to use extra-legal means to intimidate, harass or prosecute a few NGOs or activists.
-These cases, especially during moments or crises or contention, "highlight to the wider NGO community-and citizenry-that the government is willing and capable of using the law to repress dissent" [@Brechenmacher:2017, 94].
-
-Based on these various purposes of NGO restrictions and the different methods states use to implement them, we propose two empirical expectations about the relationship between civil society repression and general human rights:
-
-- **Empirical expectation 1** (effect of de jure NGO repression): If a country imposes a formal anti-NGO law, then it is likely to signal future deteriorating human rights conditions.
-- **Empirical expectation 2** (effect of de facto NGO repression): If a country implements its formal anti-NGO laws and represses civil society, then it is likely to signal future deteriorating human rights conditions.
-
-# Data and modeling approach
-
-To test these empirical expectations, we use a new dataset of civil society laws, as well as measures from several other larger datasets focused on human rights, political terror, and democratization.
-Table \@ref(tab:var-summary) provides a summary of our key variables.
-
-(ref:pts) @GibneyCornettWood:2019
-
-(ref:vdem) @vdem-v10
-
-(ref:lhr) @FarissKenwickReuning:2020
-
-(ref:chaudhry) @Chaudhry:2016
-
-```{r var-summary}
-# For whatever reason, bookdown::pdf_document2 can't process in-table citations
-# like @vdem-v10; it just skips them. bookdown::html_document2 works just fine,
-# though. This is a known issue (see
-# https://github.com/haozhu233/kableExtra/issues/214#issuecomment-421706528),
-# and the solution is to use bookdown text references
-# (https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#text-references)
-# out in the main text and then include the reference key in the table:
-# 
-# In the text:
-# (ref:vdem) @vdem-v10
-#
-# In the table:
-# (ref:vdem)
-# 
-# It's weird, but it works
-#
-# BUT it doesn't work with Word, and flextable specifically. (ref:vdem) gets
-# correctly replaced with @vdem-10, but then it doesn't get processed by pandoc.
-# One way around this is to use the ftExtra package, which has colformat_md()
-# that will treat a column like Markdown and will allow pandoc to process
-# citations (see https://github.com/davidgohel/flextable/issues/243 and
-# ftExtra's citation support here:
-# https://ftextra.atusy.net/articles/format_columns.html#citations). BUT BUT the
-# ordering of bookdown's text references replacement messes with flextable's
-# citation processing or something, so pandoc references that are inserted with
-# (ref:vdem) remain as @vdem-10 when knitted. The way around *this* is to use
-# the raw @citekey in the table. Oof.
-#
-# Here's a minimal example:
-#
-# bloop <- tribble(
-#   ~Thing, ~Source, ~Source_word,
-#   "This *is* a test", "(ref:vdem)", "@vdem-v10"
-# ) 
-# 
-# if (is_docx) {
-#   bloop %>% 
-#     select(Thing, Source = Source_word) %>% 
-#     hux() %>% 
-#     huxtable::as_flextable() %>% 
-#     ftExtra::colformat_md() 
-# } else {
-#   bloop %>% 
-#     select(-Source_word) %>% 
-#     kbl(booktabs = TRUE) %>% 
-#     kable_styling()
-# }
-
-tbl_var_summary_caption <- "Outcomes and predictors"
-
-tbl_var_summary <- tribble(
-  ~Measure, ~Category, ~Description, ~Source,
-  "Political Terror Scale (PTS)", NA, "Ordered category ranging from 1 (least terror) to 5 (most terror)", "(ref:pts)",
-  "Latent human rights values", NA, "≈ −3–5; higher values indicate greater respect for human rights", "(ref:lhr)",
-  "Total legal barriers", "De jure laws", "Count of all anti-NGO legal barriers", "(ref:chaudhry)",
-  "Barriers to advocacy", "De jure laws", "Count of laws restricting NGO advocacy", "(ref:chaudhry)",
-  "Barriers to entry", "De jure laws", "Count of laws restricting NGO entry, including registration", "(ref:chaudhry)",
-  "Barriers to funding", "De jure laws", "Count of laws restricting NGO funding sources", "(ref:chaudhry)",
-  "CSO repression", "De facto repression", "≈ −3–3; higher values indicate less repression", "(ref:vdem); v2csreprss"
-)
-
-if (!is_docx) {
-  tbl_var_summary %>%
-    kbl(caption = tbl_var_summary_caption,
-        booktabs = TRUE, linesep = "\\addlinespace") %>% 
-    pack_rows(index = c("Outcomes" = 2, "Predictors" = 5),
-              indent = FALSE) %>% 
-    kable_styling(font_size = ifelse(is_latex, 8.5, NA)) %>% 
-    column_spec(1, width = "0.16\\\\textwidth") %>% 
-    column_spec(2, width = "0.1\\\\textwidth") %>% 
-    column_spec(3, width = "0.4\\\\textwidth") %>% 
-    column_spec(4, width = "0.2\\\\textwidth")
-} else {
-  tbl_var_summary %>% 
-    hux() %>% 
-    set_font_size(10) %>%
-    set_all_padding(3) %>% 
-    insert_row("Outcomes", "", "", "", after = 1) %>% 
-    insert_row("Predictors", "", "", "", after = 4) %>% 
-    set_bold(1, everywhere) %>%
-    set_bold(c(2, 5), everywhere) %>%
-    set_bottom_border(c(2, 5), everywhere) %>%
-    set_width(1) %>% 
-    set_wrap(TRUE) %>% 
-    huxtable::set_caption(tbl_var_summary_caption) %>% 
-    huxtable::as_flextable()
-}
-```
-
-## Measuring de jure and de facto civil society repression
-
-To measure de jure repression, we use data on anti-NGO laws from @Chaudhry:2016 which includes official NGO laws for all countries (excluding micro-states) between 1990 and 2013.
-This measure of formal legal barriers does not necessarily represent individual laws.
-Instead, we count the presence or absence of specific types of anti-NGO legal barriers as a binary variable.
-If a country passes a broader NGO laws that implements several of these barriers simultaneously (e.g.
-making registration burdensome and restricting foreign funds), the values for each barrier will flip from 0 to 1.
-We create indices of the total number of legal barriers in each country based on three broad categories of laws: barriers to entry, funding, and advocacy.
-We also sum each of these indices to create an overall count of legal barriers.
-
-- **Barriers to advocacy** (2 possible barriers): (1) NGOs are restricted from engaging in political activities, and (2) advocacy restrictions differ if the NGO receives foreign funding
-- **Barriers to entry** (3 possible barriers): (1) registration is burdensome, (2) NGOs are not allowed to appeal if denied registration, and (3) entry requirements differ if the NGO receives foreign funding
-- **Barriers to funding** (5 possible barriers): (1) NGOs need prior approval to receive foreign funding, (2) NGOs are required to channel foreign funding to state-owned banks, (3) NGOs face additional restrictions if receiving foreign funding, and (4) NGOs are restricted or (5) prohibited from receiving foreign funding
-
-```{r barriers, fig.width=6, fig.height=6, fig.asp=NULL, fig.cap="Number of legal barriers to NGO activity per country over time (de jure legislation) and average level of CSO repression across democracies and non-democracies (de facto implementation)"}
-regulations <- tribble(
-    ~question, ~barrier,       ~question_clean,                  ~ignore_in_index, ~question_display,
-    "q1a",     "association",  "const_assoc",                    TRUE,             "Constitutional associational rights",
-    "q1b",     "association",  "political_parties",              TRUE,             "Citizens form political parties",
-    "q4b",     "advocacy",     "ngo_politics_intimidation",      TRUE,             "NGOs intimidated from politics",
-    "q4c",     "advocacy",     "ngo_politics_foreign_fund",      FALSE,            "Political barriers differentXXXif foreign funds involved",
-    "q2a",     "entry",        "ngo_register",                   TRUE,             "NGO registration required",
-    "q2b",     "entry",        "ngo_register_burden",            FALSE,            "NGO registration burdensome",
-    "q2c",     "entry",        "ngo_register_appeal",            FALSE,            "NGO registration appealXXXnot allowed",
-    "q2d",     "entry",        "ngo_barrier_foreign_funds",      FALSE,            "Registration barriers differentXXXif foreign funds involved",
-    "q3a",     "funding",      "ngo_disclose_funds",             TRUE,             "Funds must be disclosed",
-    "q3b",     "funding",      "ngo_foreign_fund_approval",      FALSE,            "Prior approval requiredXXXfor foreign funds",
-    "q3c",     "funding",      "ngo_foreign_fund_channel",       FALSE,            "Foreign funds channeledXXXthrough government",
-    "q3d",     "funding",      "ngo_foreign_fund_restrict",      FALSE,            "Foreign funds restricted",
-    "q3e",     "funding",      "ngo_foreign_fund_prohibit",      FALSE,            "Foreign funds prohibited",
-    "q3f",     "funding",      "ngo_type_foreign_fund_prohibit", FALSE,            "Foreign funds prohibitedXXXfor some types of NGOs",
-    "q4a",     "advocacy",     "ngo_politics",                   FALSE,            "NGOs restricted from politics"
-) %>% 
-  filter(!ignore_in_index) %>% 
-  mutate(barrier_group = paste0("Barriers to ", str_to_lower(barrier))) %>% 
-  select(barrier_group, barrier = question_clean, barrier_display = question_display)
-
-df_barriers <- canary %>% 
-  group_by(gwcode, year) %>% 
-  summarize(across(one_of(regulations$barrier), ~. > 0)) %>% 
-  group_by(year) %>% 
-  summarize(across(-gwcode, ~sum(., na.rm = TRUE))) %>% 
-  ungroup() %>% 
-  pivot_longer(names_to = "barrier", values_to = "value", -year) %>% 
-  left_join(regulations, by = "barrier") %>% 
-  mutate(barrier_display = str_replace(barrier_display, "XXX", "\n")) %>%
-  arrange(year, desc(value)) %>% 
-  mutate(barrier_display = fct_inorder(barrier_display, ordered = TRUE))
-
-num_countries <- length(unique(canary$gwcode))
-
-entry_plot <- ggplot(filter(df_barriers, 
-                            barrier_group == "Barriers to entry"), 
-                     aes(x = year, y = value, 
-                         color = barrier_display)) +
-  geom_line(size = 1.25) +
-  expand_limits(y = c(0, 90)) +
-  scale_y_continuous(sec.axis = sec_axis(~ . / num_countries,
-                                         labels = percent_format(accuracy = 1)),
-                     expand = c(0, 0)) +
-  scale_color_viridis_d(option = "plasma", end = 0.92, name = NULL) +
-  coord_cartesian(xlim = c(1990, 2015), ylim = c(0, 90)) +
-  guides(color = guide_legend(nrow = 2)) +
-  labs(x = NULL, y = "Number of countries") +
-  theme_ngo(9) + 
-  theme(legend.justification = "left",
-        legend.key.height = unit(0.7, "lines"),
-        legend.key.width = unit(1, "lines")) +
-  facet_wrap(vars(barrier_group))
-
-funding_plot <- ggplot(filter(df_barriers, 
-                              barrier_group == "Barriers to funding"), 
-                       aes(x = year, y = value, 
-                           color = barrier_display,
-                           linetype = barrier_display)) +
-  geom_line(size = 1.25) +
-  scale_y_continuous(sec.axis = sec_axis(~ . / num_countries,
-                                         labels = percent_format(accuracy = 1)),
-                     expand = c(0, 0)) +
-  scale_color_viridis_d(option = "plasma", end = 0.92, name = NULL) +
-  scale_linetype_manual(values = c("solid", "21", "solid", "21", "solid"), name = NULL) +
-  coord_cartesian(xlim = c(1990, 2015), ylim = c(0, 45)) +
-  guides(color = guide_legend(nrow = 3),
-         linetype = guide_legend(nrow = 3)) +
-  labs(x = NULL, y = "Number of countries") +
-  theme_ngo(9) + 
-  theme(legend.justification = "left",
-        legend.key.height = unit(0.7, "lines"),
-        legend.key.width = unit(1, "lines")) +
-  facet_wrap(vars(barrier_group))
-
-advocacy_plot <- ggplot(filter(df_barriers, 
-                               barrier_group == "Barriers to advocacy"), 
-                        aes(x = year, y = value, 
-                            color = barrier_display)) +
-  geom_line(size = 1.25) +
-  scale_y_continuous(sec.axis = sec_axis(~ . / num_countries,
-                                         labels = percent_format(accuracy = 1)),
-                     expand = c(0, 0)) +
-  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
-  coord_cartesian(xlim = c(1990, 2015), ylim = c(0, 60)) +
-  guides(color = guide_legend(nrow = 2)) +
-  labs(x = NULL, y = "Number of countries",
-       legend.key.size = unit(0.7, "lines")) +
-  theme_ngo(9) + 
-  theme(legend.justification = "left",
-        legend.key.height = unit(0.7, "lines"),
-        legend.key.width = unit(1, "lines")) +
-  facet_wrap(vars(barrier_group))
-
-df_csreprss_plot <- canary %>%
-  group_by(year, autocracy = v2x_regime <= 1) %>%
-  nest() %>% 
-  mutate(cis = data %>% map(~ mean_cl_normal(.$v2csreprss))) %>% 
-  unnest(cis) %>% 
-  ungroup() %>% 
-  filter(!is.na(autocracy)) %>% 
-  mutate(fake_facet_title = "CSO repression",
-         autocracy = factor(autocracy, 
-                            labels = c("Democracies (Regimes of the World > 1)",
-                                       "Non-democracies (Regimes of the World ≤ 1)"), 
-                            ordered = TRUE))
-
-csreprss_plot <- ggplot(df_csreprss_plot, aes(x = year, y = y)) +
-  geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = autocracy), alpha = 0.2,) +
-  geom_line(aes(color = autocracy), size = 1.25) +
-  scale_color_viridis_d(option = "plasma", end = 0.8, name = NULL) +
-  scale_fill_viridis_d(option = "plasma", end = 0.8, name = NULL) +
-  coord_cartesian(xlim = c(1990, 2015)) +
-  guides(color = guide_legend(nrow = 2)) +
-  labs(y = "Average CSO repression", x = NULL) +
-  theme_ngo(9) +
-  theme(legend.justification = "left",
-        legend.key.height = unit(0.7, "lines"),
-        legend.key.width = unit(1, "lines")) +
-  facet_wrap(vars(fake_facet_title))
-
-barriers_summary <- 
-  ((advocacy_plot | entry_plot) / 
-     (funding_plot | csreprss_plot)) &
-  theme(legend.text = element_text(size = rel(0.7)),
-        axis.title.y = element_text(margin = margin(r = 3)),
-        legend.box.margin = margin(t = -0.5, unit = "lines"))
-
-barriers_summary
-```
-
-To measure de facto civil society repression in a country, we use the Varieties of Democracy's (V-Dem) CSO repression indicator (`v2csreprss` in @vdem-v10), which captures the extent to which governments harass, deter, liquidate, and arrest members of civil society organizations.
-This variable captures repression using an ordinal scale, defining civil society repression as severe, substantial, moderate, weak, or absent.
-This ordinal scale is then aggregated with a Bayesian item response theory measurement model and converted to a continuous scale that ranges from roughly −3 to 3, with higher values indicating less repression.
-
-Figure \@ref(fig:barriers) shows each of these types of legal barriers per country over time, as well as average levels of de facto civil society repression by regime type.
-While anti-NGO laws have increased steadily since 1990—particularly laws related to foreign funding—there has not necessarily been a corresponding rise in de facto civil society repression, which has remained fairly constant across different regime types.
-This divergence is likely indicative of the split between de jure laws and their de facto implementation—a rise in laws is not necessarily tied to direct CSO repression.
-
-## Measuring repression
-
-To see how both de jure and de facto civil society restrictions influence general human rights repression, we use four different quantitative measures of repression, each of which capture different dimensions of political and civil violence.
-First, following @GohdesCarey:2017, who use the killing of journalists to predict worsening human rights conditions, we use the Political Terror Scale (PTS), which assigns countries to one of five possible levels of repression each year [@GibneyCornettWood:2019], with Level 5 representing widespread political violence—including arrests, imprisonment, political murders, disappearances, and torture.
-As seen in the top panel of Figure \@ref(fig:repression), the number of countries at Level 5 has decreased since the 1990s, while most countries are coded as Levels 2 and 3 (moderate levels of political terror).
-
-The five levels of the PTS are helpful for conceptualizing broader trends in human rights abuses.
-However, these categories are not always granular enough to model or predict a country's level of political terror.
-Additionally, the PTS—along with most other measures of human rights abuses—does not account for the systematic changes in the way monitoring agencies have gathered information about human rights violations over time.
-Accordingly, we use latent human rights scores as an alternative measure of underlying repression [@Fariss:2014; @FarissKenwickReuning:2020].
-This variable is generated from a Bayesian measurement model that incorporates information about human rights abuses from a variety of published repression indices, including the PTS.
-Because the resulting measure is continuous, it picks up on more minute changes in national-level human rights.
-Moreover, this variable accounts for changing standards of accountability, which has led to the production of more stringent human rights reports as monitors look harder for abuse, look in more places for abuse, and classify more acts as abuse.
-When accounting for these changes, the bottom panel of Figure \@ref(fig:repression) demonstrates the global improvements in average latent human rights values over time.
-
-```{r repression, fig.width=6.5, fig.height=4.5, fig.asp=NULL, fig.cap="Key measures of repression over time"}
-pts_plot <- canary %>% 
-  filter(!is.na(PTS_factor)) %>% 
-  group_by(PTS_factor, year) %>% 
-  summarize(count = n()) %>% 
-  mutate(fake_facet_title = "Political Terror Scale") %>% 
-  ggplot(aes(x = year, y = count, color = PTS_factor)) +
-  geom_line(size = 1) +
-  scale_color_viridis_d(option = "rocket", end = 0.85, direction = -1) +
-  coord_cartesian(xlim = c(1990, 2015)) +
-  guides(color = guide_legend(title = NULL)) +
-  labs(y = "Number of countries", x = NULL, caption = "(Higher PTS levels = more repression)") +
-  theme_ngo(9) +
-  theme(legend.justification = "left",
-        legend.key.height = unit(0.7, "lines"),
-        legend.key.width = unit(1, "lines"),
-        plot.caption = element_text(margin = margin(t = -1, unit = "lines"))) +
-  facet_wrap(vars(fake_facet_title))
-
-df_lhr_plot <- canary %>% 
-  as_tibble() %>% 
-  select(year, latent_hr_mean) %>% 
-  group_by(year) %>% 
-  nest() %>% 
-  mutate(cis = data %>% map(~ mean_cl_normal(.$latent_hr_mean))) %>% 
-  unnest(cis) %>% 
-  ungroup() %>% 
-  mutate(fake_facet_title = "Latent human rights")
-
-lhr_plot <- ggplot(df_lhr_plot, aes(x = year, y = y)) +
-  geom_ribbon(aes(ymin = ymin, ymax = ymax), alpha = 0.2, fill = "#FF4136") +
-  geom_line(size = 1, color = "#FF4136") +
-  coord_cartesian(xlim = c(1990, 2015)) +
-  labs(y = "Average value", x = NULL, caption = "(Higher values = less repression)") +
-  theme_ngo(9) +
-  theme(legend.justification = "left") +
-  facet_wrap(vars(fake_facet_title))
-
-(pts_plot / lhr_plot) &
-  theme(legend.text = element_text(size = rel(0.7)),
-        axis.title.y = element_text(margin = margin(r = 3)),
-        legend.box.margin = margin(t = -0.5, unit = "lines"))
-```
-
-## Modeling approach
-
-Since we look at whether anti-NGO laws and their implementation can serve as an early warning signal for broader repression, we are primarily interested in *predicting* repression and not isolating the causal effect of civil society repression on general human rights abuses.
-We do not include a complete set of covariates to remove confounding relationships, but instead use a more parsimonious set of explanatory variables that strongly predict repression.
-Following @GohdesCarey:2017, we control for a country's level of repression in the previous year (either PTS score or latent human rights value, depending on the model), its level of democracy as measured by V-Dem's polyarchy index, its logged GDP per capita (measured by the UN), the percent of GDP attributed to trade (measured by the UN), and an indicator for whether the country witnessed more than 25 battle-related deaths (measured by @ucdp2020; @GleditschWallensteenEriksson:2002).
-Because changes in the human rights environment take time to be reflected by these larger indices, we model the effect of lagged explanatory variables on repression one year in the future.
-We also include the lag of civil society laws or repression to account for serial correlation.
-
-We extend @GohdesCarey:2017's previous modeling approach by accounting for country-level variation in repression with multilevel modeling and we include random effects for each country.
-Accounting for country differences this way results in intraclass correlation coefficients of around 0.7 for each of our three outcome variables, which means that the country-based structure of the data explains more than 70% of the variation in outcome, resulting in model estimates that are arguably more precisely measured.
-We run multiple models for each of our empirical expectations, based on different combinations of our outcomes and key explanatory variables:
-
-- **Expectation 1~a~**: Anti-NGO laws (total; advocacy, entry, funding separately) signal worsening political terror
-- **Expectation 1~b~**: Anti-NGO laws signal decreasing latent human rights respect
-- **Expectation 2~a~**: Civil society repression signals worsening political terror
-- **Expectation 2~b~**: Civil society repression signals decreasing latent human rights respect
-
-We generate predictions with two families of Bayesian regression models.
-Because the PTS is measured as an ordered category, we use ordered logistic regression to predict future values of the scale.
-We predict the continuous latent human rights values with Gaussian models.
-The appendix contains complete details of our modeling approach.
-We use median values from the models' posterior distributions as our point estimates and provide credible intervals using the 95% highest posterior density.
-We declare an effect statistically "significant" if the posterior probability of being different from zero (i.e.
-above or below) exceeds 0.95.
-
-# Results and analysis
-
-We present the results of our models in two stages.
-First, to see how minor shifts in civil society laws and repression influence future human rights, we examine the marginal effects of our main explanatory variables when all other model covariates are held constant.
-These effects are by no means causal—rather, they demonstrate how much variation in predicted human rights is possible as the legal environment for civil society improves or deteriorates within a typical country.
-Second, we present predictive diagnostics for each of our models to examine the improvements in predictions.
-The results of the ordered logistic regression models can be unwieldy to interpret with plain numbers due to varying intercepts and thresholds between PTS levels.
-Accordingly, we present graphical results for all our models wherever possible and include complete tables of model results in the appendix (see Tables \@ref(tab:tbl-models-pts) and \@ref(tab:tbl-models-lhr)).
-For ease in comparing the count of NGO laws with civil society repression, we reverse the x-axis in the marginal effects plots for our second empirical expectation so that increasing the civil society repression represents *worse* repression rather than less.
-
-## Marginal results
-
-### How does repression change following increases in NGO laws?
-
-In general, when holding all other covariates constant, the passage of an additional anti-NGO legal barrier is generally associated with a higher probability of more severe level of political terror in the following year.
-The probability of seeing different levels of political terror varies across different possible counts of NGO laws (see Figure \@ref(fig:plot-mfx-e1a)).
-In the absence of formal legal barriers, Level 2 of the PTS—an environment where political imprisonment, torture, and beatings are rare—is the most likely category of political terror across all models, appearing a predicted 60% of the time.
-Level 1, where a country is under secure rule of law, is the second most likely outcome at slightly under 40%.
-The other categories of the PTS are extremely rare when there are no anti-NGO laws—as such, we collapse them into a single category.
-
-```{r plot-mfx-e1a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on the probability of specific levels of political terror"}
-mfx_e1a_pts %>% 
-  mutate(x_rounded = floor(effect1__)) %>% 
-  # Collapse 3-5 to just one level, since they're all tiny
-  mutate(effect2__ = fct_collapse(effect2__, "3+" = c("3", "4", "5"))) %>% 
-  group_by(x_rounded, effect2__, plot_var_nice) %>% 
-  slice(1) %>% 
-  # Add up these values for the collapsed 3-5 results
-  summarize(across(c(estimate__, lower__, upper__), sum)) %>% 
-  ungroup() %>% 
-  ggplot(aes(x = x_rounded, y = estimate__, color = effect2__)) +
-  geom_line(aes(group = effect2__), size = 0.5, color = "grey90") +
-  geom_pointrange(aes(ymin = lower__, ymax = upper__),
-                  # position = position_dodge(width = 0.2),
-                  fatten = 1, size = 1) +
-  scale_x_continuous(breaks = 0:9) +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_color_viridis_d(option = "rocket", begin = 0.1, end = 0.85, direction = -1) +
-  guides(color = guide_legend(override.aes = list(size = 0.5, linetype = 0))) +
-  labs(x = "Count of legal barriers\n",
-       y = "Predicted probability of category",
-       color = "Predicted Political Terror Scale", fill = "Predicted Political Terror Scale",
-       title = "Political Terror Scale") + 
-  facet_wrap(vars(plot_var_nice), scales = "free_x") +
-  theme_ngo() +
-  theme(panel.grid.major.x = element_blank())
-```
-
-As new laws are added, though, the distribution of probabilities for each of the PTS levels shifts.
-Adding new barriers to advocacy, entry, and funding decreases the likelihood of seeing Level 1 and increases the probability of a country turning to either Level 2 or Level 3 (with extensive political imprisonment and trial-free detention).
-The marginal effects of all forms of NGO laws results in this turn from Level 1 to Levels 2 or 3+, but this switching effect is strongest following additional barriers to advocacy.
-Anti-NGO laws do not predict more dramatic shifts in the PTS.
-Across all counts of legal barriers, the overall probability of seeing Levels 4 and 5 is minuscule, and the passage of additional laws does little to shift that probability.
-This is not unexpected however—the PTS has a natural ceiling at Level 5.
-Specifically, in addition to measuring the scope and intensity of government violence, the PTS scale also looks at the proportion of population targeted for abuse.
-Countries that receive a 4 and 5 are rare, as 4 denotes that murders, disappearances, and torture are a common part of life, while 5 denotes that physical abuses are routinely perpetrated against citizens not involved in politics, and includes cases where governments engage in "scorched earth" counterinsurgency policies or summary executions based on class or ethnic affiliation [@GibneyCornettWood:2019].
-The majority of movement across PTS categories should thus occur between Levels 1–3.
-
-Figure \@ref(fig:plot-mfx-e1b) shows the marginal effects of additional NGO legislation on latent human rights scores.
-Across all four models for different categories of legal barriers, holding all other values constant, the predicted level of human rights respect decreases.
-Adding a new NGO law is associated with a -0.013-point decline in the level of respect for human rights in the following year, on average.
-The marginal effect is larger (-0.02) for additional barriers to advocacy and entry, which represent more burdensome restrictions than limits to funding.
-
-At a marginal level, therefore, adding additional anti-NGO laws in countries with low levels of political terror could signal that higher levels of political repression are more likely in the future.
-Limited repression remains the most likely possible outcome, but the chance of seeing robust rule of law decreases rapidly as more laws are passed, all else equal.
-This pattern holds when looking at a more continuous measure of human rights protection—countries with a low count of anti-NGO legal barriers tend to have higher predicted values of latent human rights scores, and average protection against abuses decreases as more laws are added.
-
-```{r plot-mfx-e1b, fig.width=7.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on latent human rights scoress"}
-# TODO: Andrew: Add more specific coefficients and percent changes to the prose above
-out_mfx_e1b <- mfx_e1d_lhr %>% 
-  mutate(x_rounded = floor(effect1__)) %>% 
-  group_by(x_rounded, plot_var_nice) %>% 
-  slice(1) %>% 
-  ungroup() %>% 
-  mutate(plot_var_nice = fct_relabel(
-    plot_var_nice, ~str_to_sentence(str_remove(., "Barriers to ")))) %>% 
-  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
-  geom_line(size = 0.5, color = "grey90") +
-  geom_pointrange(aes(ymin = lower__, ymax = upper__),
-                  fatten = 1, size = 1) +
-  scale_x_continuous(breaks = 0:9) +
-  scale_color_viridis_d(option = "plasma", end = 0.8) +
-  guides(color = "none") +
-  labs(x = "Count of legal barriers",
-       y = "Predicted latent human rights value",
-       title = "Latent human rights",
-       caption = "(Higher values = better protection)") +
-  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
-  theme_ngo() +
-  theme(panel.grid.major.x = element_blank())
-
-out_mfx_e1b
-```
-
-### How does general repression change following civil society repression?
-
-The weaker predictive power of formal NGO laws is likely attributable to fact that de jure NGO legislation may take time to implement—many states need to first establish institutions that oversee the operation and funding of these groups or incorporate threatening NGOs into the regime apparatus [@Naim:2007].
-Further, states that engage in political repression can do so with or without legal justification.
-De facto civil society repression, on the other hand, represents the actual implementation of anti-NGO strategies—both legal and extralegal—and might be more indicative of future human rights abuses.
-The results from our second set of models, using V-Dem;s civil society repression index as the key predictor, confirm this.
-
-The effect of de facto civil society repression on predicted values of the PTS mirrors what we found previously with our first empirical expectation.
-As seen in Figure \@ref(fig:plot-mfx-e2a), at the lowest levels of repression, Levels 1 and 2 are the most common predicted outcomes and are each equiprobable at roughly 50%.
-As de facto CSO repression increases, though, the probability of seeing Level 1 decreases and is replaced with either Level 2 or Level 3.
-More severe levels of political terror remain exceptionally improbable at any level of preceding civil society repression—we again collapse these into a single category.
-
-```{r plot-mfx-e2a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on the probability of specific levels of political terror", out.width="75%"}
-out_mfx_e2a <- mfx_e2a_pts %>% 
-  mutate(effect2__ = fct_collapse(effect2__, "3+" = c("3", "4", "5"))) %>% 
-  group_by(effect1__, effect2__, plot_var_nice) %>% 
-  summarize(across(c(estimate__, lower__, upper__), sum)) %>% 
-  ungroup() %>% 
-  ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
-  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, color = NA) +
-  geom_line(size = 1) +
-  scale_x_reverse() +
-  scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  scale_color_viridis_d(option = "rocket", begin = 0.1, end = 0.75, direction = -1) +
-  scale_fill_viridis_d(option = "rocket", begin = 0.1, end = 0.9, direction = -1) +
-  labs(x = "Civil society repression",
-       y = "Predicted probability of category",
-       color = "Political Terror Scale", fill = "Political Terror Scale",
-       title = "Political Terror Scale",
-       caption = "(x-axis reversed; greater repression on the right)") +
-  theme_ngo() +
-  theme(legend.box.margin = margin(t = 0.5, unit = "lines"))
-out_mfx_e2a
-```
-
-```{r lhr-trends, include=FALSE, warning=FALSE}
-lhr_csreprss_stats <- m_lhr_v2csreprss %>% 
-  tidy(effects = "fixed") %>% 
-  mutate(term = janitor::make_clean_names(term)) %>%
-  split(.$term)
-
-lhr_csreprss_diffs <- m_lhr_v2csreprss %>% 
-  emmeans(~ v2csreprss + gwcode, var = "v2csreprss", 
-           at = list(gwcode = 999,
-                     v2csreprss = c(0, -1)),
-           epred = TRUE, re_formula = NULL,
-           allow_new_levels = TRUE, sample_new_levels = "gaussian") %>% 
-  tidy() %>% 
-  mutate(pct_change = (estimate - lag(estimate)) / lag(estimate),
-         id = janitor::make_clean_names(v2csreprss)) %>% 
-  split(.$id)
-```
-
-De facto civil society repression has a noticeable effect on latent human rights values (see Figure \@ref(fig:plot-mfx-e2b)).
-When holding all other model parameters at their typical values, increased civil society repression predicts a strong decrease in respect for broader human rights: a one unit change in civil society repression is associated with a `r round(lhr_csreprss_stats$v2csreprss$estimate, 2)`-unit change in overall latent human rights.
-To illustrate the magnitude of this effect, a typical simulated country with a civil society repression index of 0 is predicted to have a latent human rights score of `r round(lhr_csreprss_diffs$x0$estimate, 2)`.
-This predicted outcome drops to `r round(lhr_csreprss_diffs$x1$estimate, 2)` with a 1-unit decrease in civil society repression, representing a `r percent_format(accuracy = 1)(abs(lhr_csreprss_diffs$x1$pct_change))` decline in respect for human rights in the following year.
-
-When holding all other factors equal, the de facto implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passage of formal de jure laws.
-In countries with low levels of political terror, it can potentially serve as a weak signal of a more general increase in political violence in the future, but predict more substantial changes in general respect for human rights.
-The difference in the effects of laws vs.
-their de facto implementation could also potentially be explained by the time frame of these strategies.
-De jure laws are a long-term strategy to prevent threats to the regime from coalescing in the first place.
-For instance, Egypt's Law 84 of 2002—which outlined many anti-NGO restrictions—has been on the books for nearly two decades, but only over the past five years have post-revolutionary regimes used it more broadly [@Ruffner:2015].
-As such, the long-term effects of these laws in terms of their predictive power may require a much longer time period under study.
-In contrast, de facto crackdown on NGOs may signal the need to react sooner due to the immediacy of the threat.
-
-```{r plot-mfx-e2b, fig.width=6.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on latent human rights"}
-# TODO: Combine with previous plot so there's just one, with fake facet titles
-out_mfx_e2d <- mfx_e2d_lhr %>% 
-  ggplot(aes(x = effect1__, y = estimate__)) +
-  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
-              fill = "#FF4136", color = NA) +
-  geom_line(size = 1, color = "#FF4136") +
-  scale_x_reverse() +
-  labs(x = "Civil society repression",
-       y = "Predicted latent human rights value",
-       title = "Latent human rights", 
-       caption = "(x-axis reversed; greater repression on right\nhigher values in y-axis show less violence and better protection of rights)") +
-  theme_ngo(8)
-out_mfx_e2d
-```
-
-## Predictions
-
-```{r eval=FALSE, include=FALSE}
-# TODO: Andrew: Streamline this section
-```
-
-These predicted probabilities and outcomes are conditional on all other model parameters being held at their average values and show the effect of hypothetically changing a single predictor to different values.
-They do not show how well these models work with actual data.
-Following @WardBeger:2017 and @GohdesCarey:2017, we test the predictive power of both sets of our models using out-of-sample prediction.
-We divide our complete data into a training set and a test set—the training set includes data from all countries from 1990–2010, and the test set includes the last three years of data (2011–2013).
-We re-run each of our models using our training data and then use the estimated parameters to predict political terror, physical violence, and private civil liberties for the test data.
-Additionally, we estimate a model for each outcome without predictor variables for civil society laws or repression as a baseline measure of model performance.
-
-```{r correct-not-correct}
-# These numbers come from the analysis notebook at 
-# https://stats.andrewheiss.com/canary-ngos/04_predictions.html#Prediction_diagnostics
-pts_pred_table <- tribble(
-  ~Prediction, ~Baseline, ~total, ~advocacy, ~entry, ~funding, ~repression,
-  "Wrong",     108,       108,    110,       108,    109,      111,
-  "Correct",   377,       377,    375,       377,    376,      374
-) %>% 
-  rename("Total legal barriers included" = total,
-         "Barriers to advocacy included" = advocacy,
-         "Barriers to entry included" = entry,
-         "Barriers to funding included" = funding,
-         "Civil society repression included" = repression)
-
-pts_pred_table_caption <- "Counts of correctly and incorrectly predicted cases across different PTS models"
-
-if (!is_docx) {
-  pts_pred_table %>% 
-    kbl(align = "lcccccc",
-        booktabs = TRUE, linesep = "\\addlinespace",
-        caption = pts_pred_table_caption) %>% 
-    kable_styling(font_size = ifelse(is_latex, 8.5, NA)) %>%
-    kable_styling() %>% 
-    column_spec(1, width = "0.07\\\\textwidth") %>% 
-    column_spec(2, width = "0.05\\\\textwidth") %>% 
-    column_spec(3:7, width = "0.13\\\\textwidth")
-} else {
-  pts_pred_table %>% 
-    hux() %>% 
-    set_font_size(10) %>%
-    set_all_padding(3) %>% 
-    set_bold(1, everywhere) %>%
-    set_bottom_border(1, everywhere) %>%
-    # set_col_width(1, 0.05) %>%
-    # set_col_width(2:7, 0.14) %>% 
-    set_width(1) %>% 
-    set_wrap(TRUE) %>% 
-    huxtable::set_caption(pts_pred_table_caption) %>% 
-    huxtable::as_flextable()
-}
-```
-
-We assess predictive power in a few different ways, depending on the model used to predict the outcome.
-For the ordinal Political Terror Scale, Table \@ref(tab:correct-not-correct) shows a count of correct and incorrect predictions from each model.
-Because the physical violence and private civil liberties indexes are predicted with Gaussian models, we measure predictive accuracy with the root mean squared error, provided in Table \@ref(tab:tbl-rmse).
-In the appendix we include lists of country-year cases that see improved predictions when taking civil society laws and repression into account.
-
-Including civil society restrictions—both de jure and de facto—does very little to improve predictions of political terror.
-As seen in Table \@ref(tab:correct-not-correct), no model provides more correct predictions than the baseline model, and some models perform worse.
-Accounting for anti-NGO activities does improve predictions in eight cases (see Table \@ref(tab:tbl-improved-pts)), but it also results in an equal number of incorrect predictions.
-
-```{r tbl-rmse}
-# These numbers also come from the analysis notebook at 
-# https://stats.andrewheiss.com/canary-ngos/04_predictions.html
-tbl_rmse <- tribble(
-  ~`Latent human rights values`,  ~RMSE, ~`% change from baseline`,
-                  "Baseline", 0.1861944,                       "—",
-      "Total legal barriers", 0.1872427,                   "0.56%",
-      "Barriers to advocacy", 0.1871498,                   "0.51%",
-         "Barriers to entry", 0.1862244,                   "0.02%",
-       "Barriers to funding", 0.1879829,                   "0.96%",
-  "Civil society repression", 0.1856543,                  "-0.29%"
-) %>% 
-  mutate(RMSE = round(RMSE, 4))
-
-tbl_rmse_caption <- "Root mean squared error across models predicting latent human rights"
-
-if (!is_docx) {
-  tbl_rmse %>% 
-    kbl(align = "lcc",
-        booktabs = TRUE, linesep = "\\addlinespace",
-        caption = tbl_rmse_caption) %>% 
-    kable_styling()
-} else {
-  tbl_rmse %>% 
-    hux() %>% 
-    set_font_size(10) %>%
-    set_all_padding(3) %>% 
-    set_align(everywhere, 1, "left") %>% 
-    set_align(everywhere, 2:3, "center") %>% 
-    set_bold(1, everywhere) %>%
-    set_width(1) %>% 
-    set_wrap(TRUE) %>% 
-    huxtable::set_caption(tbl_rmse_caption) %>% 
-    huxtable::as_flextable()
-}
-```
-
-When looking at the level of physical violence in a country, including de jure and de facto repression does very little to improve predictive accuracy.
-As Table \@ref(tab:tbl-rmse) shows, accounting for legal barriers and civil society repression only reduces the RMSE by at most 0.4% compared to the baseline model.
-This is likely related to the lack of improvements in predicting political terror—both indices measure similar phenomena.
-Similarly, accounting for de facto civil society repression when modeling latent human rights only results in slight changes to the RMSE.
-However, including civil society-related predictors when modeling private civil liberties does result in small gains in accuracy, reducing the RMSE by as much as 2% compared to the baseline model.
-
-While these gains in predictive power appear negligible, they are somewhat comparable with the findings of previous work.
-For instance, in their work on the effect of the murder of journalists on predicting future political terror, @GohdesCarey:2017 find that accounting for violence against the media adds five correctly predicted cases of PTS scores and improves predictions in seven cases.
-
-# Conclusion and implications
-
-Strengthening civil society is an important precondition for democratic transition and consolidation.
-When governments restrict civil society, it reduces these organizations' ability to maintain accountability and protect against abuse.
-Given these potential knock-on effects, in this paper, we posited that the ongoing global crackdown on NGOs could predict worsening human rights abuses and levels of political and civil rights repression.
-Using original data on de jure and de facto NGO repression from 1990-2013, we find little support for the predictive power of de jure restriction on political terror, physical violence, and violations of private civil liberties.
-Marginal predictions show that, all else held equal, adding new anti-NGO laws increases the probability of seeing moderate levels of political terror, but does not change predicted values of physical integrity or civil liberties rights violations.
-When comparing out-of-sample predictions to a baseline model, including de jure restrictions as predictors does not improve our models' predictive accuracy.
-
-We do, however, find some predictive power when accounting for de facto levels of NGO repression, which includes both legal and extra-legal means of crackdown.
-As with formal laws, rising NGO repression tends to increase the probability of more moderate political terror.
-Additionally, this repression is associated with worsening respect for physical integrity rights and civil liberties in the future.
-In out-of-sample predictions, including civil society restrictions improves model accuracy by 1–2% over the baseline.
-
-Importantly, the lack of predictive power when modeling political violence and the modest improvements in predictive power when modeling civil liberties likely reflects the purpose of NGO restrictions.
-Encroachments on private civil liberties such as restricting freedom of association are not nearly as violent as events like government-sponsored murders.
-In authoritarian states in particular, administrative crackdown on NGOs can also be seen as a careful strategy for autocratic survival.
-Authoritarian leaders must carefully balance domestic and international institutional pressures—including pressure from civil society and NGOs—to remain in power [@Heiss:2019a; @LevitskyWay:2010].
-Anti-NGO laws could possibly be a side effect of authoritarian stability-seeking behavior, similar to election tampering, media censorship, cronyism, and rent-seeking, rather than an overt signal of impending serious human rights abuses.
-
-The global shrinking of civil society is thus not likely an early warning sign for future violent repression—states typically signal their future repressive intentions with more violent methods, such as the persecution and murder of activists and the media.
-Instead, civil society is a possible "canary in the coal mine" for impending violations of other civil rights, such as the freedom of religion, labor rights, property rights, and the freedom of movement.
-
-\clearpage
-
 # Appendix
@@
 
-Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion website at `anonymized`.
+To check for robustness, we also ran models using both country and regional random effects, but doing so made no noticeable difference in the results—for the sake of computational efficiency, we thus do not include regional effects.
+
+Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion statistical analysis notebook at <https://doi.org/10.17605/OSF.IO/MTR6X>.
 Our general modeling approach can be summarized as follows:
 
-\footnotesize
+### Equation for PTS models
 
@@
 \begin{aligned}
-& \textbf{Likelihoods} \\
-y_{i, t+1} \sim&\ \operatorname{Ordered Logistic}(y^*_{i, t + 1}, \sigma^2_m) & \text{[PTS]} \\
-y_{i, t+1} \sim&\ \mathcal{N}(y^*_{i, t + 1}, \sigma^2_m) & \text{[latent human rights]} \\
+& \textbf{Likelihood for ordinal outcome} \\
+& \text{Political Terror Scores (PTS)} \\
+y_{i, t+1} \sim&\ \operatorname{Categorical}(p_{i, t + 1}) \\
 \ \\
 & \textbf{Parameters} \\
-y^*_{i, t + 1} =&\ \alpha_i + \beta_1 \text{Civil society repression}_{i, t} + & \text{[model with covariates]}\\
-&\ \beta_2 \text{Civil society repression}_{i, t - 1} + \\
+\operatorname{logit}(p_i) =&\ \alpha_{j[i]} - \phi_{k, t + 1} \\
+\phi_{k, t + 1} =&\ \beta_1 \text{PTS}_{i, t} + \beta_2 \text{PTS}_{i, t - 1} + \\
 &\ \beta_3 \text{Outcome}_{i, t} + \beta_4 \text{Polyarchy}_{i, t} + \\
@@
 &\ \beta_6 \text{Trade as } \% \text{ of GDP}_{i, t} + \\
-&\ \beta_7 \text{Armed conflict}_{i, t} + \sigma^2_e \\
-\alpha_i =&\ \mathcal{N}(0, \sigma^2_\alpha) & \text{[country-specific intercepts]} \\
+&\ \beta_7 \text{Armed conflict}_{i, t} \\ \\
+\alpha_j \sim&\ \mathcal{N} (\mu_{\alpha_j}, \sigma_{\alpha_j}), \text{ for country } j \text{ in } 1 .. J & \text{[country-specific intercepts]} \\ \\
 \ \\
 & \textbf{Priors} \\
-\alpha \sim&\ \mathcal{N}(0, 10) & \text{[population intercept]} \\
+\mu_{\alpha_j} \sim&\ \mathcal{N}(0, 10) & \text{[country-specific intercepts]} \\
 \beta_{1-7} \sim&\ \mathcal{N}(0, 3) & \text{[population effects]} \\
-\sigma^2_m, \sigma^2_e, \sigma^2_\alpha \sim&\ \operatorname{Cauchy}(0, 1) & \text{[sd for model, population,} \\
-&&\text{and country error]}
+\sigma_{\alpha_j} \sim&\ \operatorname{Cauchy}(0, 1) & \text{[sd for population \& country]}
 \end{aligned}
 $$
-\normalsize
 
-To check for robustness, we also ran models using both country and regional random effects, but doing so made no noticeable difference in the results—for the sake of computational efficiency, we thus do not include regional effects.
+### R code for PTS models
+
+The actual R code for this model is included in the replication code at <https://doi.org/10.17605/OSF.IO/MTR6X>. This is a simplified representation of the **brms** [@brms-jss] model code.
+
+```{r echo=TRUE, eval=FALSE}
+# Ordinal logistic regression for political terror
+# (replace `cs_repression` with different measures of de jure and 
+# de facto civil society repression: barriers_total, advocacy, entry, 
+# funding, and v2csreprss)
+brm(
+  bf(PTS_lead1 ~ cs_repression + cs_repression_lag1 +
+       PTS + v2x_polyarchy + gdpcap_log +
+       un_trade_pct_gdp + armed_conflict + (1 | gwcode)),
+  family = cumulative(),
+  prior = c(set_prior("normal(0, 10)", class = "Intercept"),
+            set_prior("normal(0, 3)", class = "b"),
+            set_prior("cauchy(0, 1)", class = "sd")),
+  ...
+)
+```
+
+### Equation for latent human rights models
+
+$$
+\begin{aligned}
+& \textbf{Likelihood for continuous outcome} \\
+& \text{Latent human rights (LHR) values} \\
+y_{i, t+1} \sim&\ \mathcal{N}(y^*_{i, t + 1}, \sigma_i) \\
+\ \\
+& \textbf{Parameters} \\
+y^*_{i, t + 1} =&\ \alpha_{j[i]} + \beta_1 \text{LHR}_{i, t} +  \beta_2 \text{LHR}_{i, t - 1}\\
+&\ \beta_3 \text{Outcome}_{i, t} + \beta_4 \text{Polyarchy}_{i, t} + \\
+&\ \beta_5 \log (\text{GDP per capita}) + \\
+&\ \beta_6 \text{Trade as } \% \text{ of GDP}_{i, t} + \\
+&\ \beta_7 \text{Armed conflict}_{i, t}\\ \\
+\alpha_j \sim&\ \mathcal{N} (\mu_{\alpha_j}, \sigma_{\alpha_j}), \text{ for country } j \text{ in } 1 .. J & \text{[country-specific intercepts]} \\ \\
+& \textbf{Priors} \\
+\mu_{\alpha_j} \sim&\ \mathcal{N}(0, 10) & \text{[country-specific intercepts]} \\
+\beta_{1-7} \sim&\ \mathcal{N}(0, 3) & \text{[population effects]} \\
+\sigma_i, \sigma_{\alpha_j} \sim&\ \operatorname{Cauchy}(0, 1) & \text{[sd for population \& country]}
+\end{aligned}
+$$
+
+### R code for latent human rights models
+
+The actual R code for this model is included in the replication code at <https://doi.org/10.17605/OSF.IO/MTR6X>. This is a simplified representation of the **brms** [@brms-jss] model code.
+
+```{r echo=TRUE, eval=FALSE}
+# Gaussian regression for latent human rights
+# (replace `cs_repression` with different measures of de jure and 
+# de facto civil society repression: barriers_total, advocacy, entry, 
+# funding, and v2csreprss)
+brm(
+  bf(latent_hr_mean_lead1 ~ cs_repression + cs_repression_lag1 +
+       latent_hr_mean + v2x_polyarchy + gdpcap_log +
+       un_trade_pct_gdp + armed_conflict + (1 | gwcode)),
+  family = gaussian(),
+  prior = c(set_prior("normal(0, 10)", class = "Intercept"),
+            set_prior("normal(0, 3)", class = "b"),
+            set_prior("cauchy(0, 1)", class = "sd")),
+  ...
+)
+```
 

### 2021-11-15 manuscript/manuscript.Rmd
Move appendix to separate document

@@
 The results of the ordered logistic regression models can be unwieldy to interpret with plain numbers due to varying intercepts and thresholds between PTS levels.
-Accordingly, we present graphical results for all our models wherever possible and include complete tables of model results in the appendix (see Tables \@ref(tab:tbl-models-pts) and \@ref(tab:tbl-models-lhr)).
+Accordingly, we present graphical results for all our models wherever possible and include complete tables of model results in the appendix (see Tables A2 and A3).
 For ease in comparing the count of NGO laws with civil society repression, we reverse the x-axis in the marginal effects plots for our second empirical expectation so that increasing the civil society repression represents *worse* repression rather than less.
@@
 As seen in Table \@ref(tab:correct-not-correct), no model provides more correct predictions than the baseline model, and some models perform worse.
-Accounting for anti-NGO activities does improve predictions in eight cases (see Table \@ref(tab:tbl-improved-pts)), but it also results in an equal number of incorrect predictions.
+Accounting for anti-NGO activities does improve predictions in eight cases (see Table A1 in the appendix), but it also results in an equal number of incorrect predictions.
 
@@
 Rather, states may be learning to counter these dynamics by ramping up repression.
-
-\clearpage
-
-# Appendix
-
-## Modeling approach
-
-We use Stan [@stan] through R [@r-project] and brms [@brms-jss] to estimate our models.
-We generate 4 MCMC chains for each model with 2,000 iterations in each chain, 1,000 of which are used for warmup.
-All chains converge; we assess convergence with visual inspection.
-
-Complete results from all the models, along with posterior predictive checks, goodness-of-fit measures, and prediction diagnostics are all available at a companion website at `anonymized`.
-Our general modeling approach can be summarized as follows:
-
-\footnotesize
-
-$$
-\begin{aligned}
-& \textbf{Likelihoods} \\
-y_{i, t+1} \sim&\ \operatorname{Ordered Logistic}(y^*_{i, t + 1}, \sigma^2_m) & \text{[PTS]} \\
-y_{i, t+1} \sim&\ \mathcal{N}(y^*_{i, t + 1}, \sigma^2_m) & \text{[latent human rights]} \\
-\ \\
-& \textbf{Parameters} \\
-y^*_{i, t + 1} =&\ \alpha_i + \beta_1 \text{Civil society repression}_{i, t} + & \text{[model with covariates]}\\
-&\ \beta_2 \text{Civil society repression}_{i, t - 1} + \\
-&\ \beta_3 \text{Outcome}_{i, t} + \beta_4 \text{Polyarchy}_{i, t} + \\
-&\ \beta_5 \log (\text{GDP per capita}) + \\
-&\ \beta_6 \text{Trade as } \% \text{ of GDP}_{i, t} + \\
-&\ \beta_7 \text{Armed conflict}_{i, t} + \sigma^2_e \\
-\alpha_i =&\ \mathcal{N}(0, \sigma^2_\alpha) & \text{[country-specific intercepts]} \\
-\ \\
-& \textbf{Priors} \\
-\alpha \sim&\ \mathcal{N}(0, 10) & \text{[population intercept]} \\
-\beta_{1-7} \sim&\ \mathcal{N}(0, 3) & \text{[population effects]} \\
-\sigma^2_m, \sigma^2_e, \sigma^2_\alpha \sim&\ \operatorname{Cauchy}(0, 1) & \text{[sd for model, population,} \\
-&&\text{and country error]}
-\end{aligned}
-$$
-\normalsize
-
-To check for robustness, we also ran models using both country and regional random effects, but doing so made no noticeable difference in the results—for the sake of computational efficiency, we thus do not include regional effects.
-
-\newpage
-
-## Improved cases
-
-```{r tbl-improved-pts}
-tbl_improved_pts <- tribble(
-               ~Country, ~Year,   ~Actual, ~`Baseline prediction`, ~`Total NGO barriers included`, ~`Civil society repression included`,
-            "Guatemala", 2013L, "Level 3", "Level 2",                    "Level 3",                          "Level 3",
-               "Kosovo", 2012L, "Level 1", "Level 2",                    "Level 1",                          "Level 1",
-         "Sierra Leone", 2011L, "Level 3", "Level 2",                    "Level 3",                                "—",
-  "Congo - Brazzaville", 2011L, "Level 3", "Level 2",                    "Level 3",                          "Level 3",
-              "Somalia", 2013L, "Level 5", "Level 4",                    "Level 5",                                "—",
-              "Bahrain", 2011L, "Level 3", "Level 2",                    "Level 3",                          "Level 3",
-              "Bahrain", 2013L, "Level 3", "Level 2",                    "Level 3",                          "Level 3",
-                "Libya", 2011L, "Level 4", "Level 5",                          "—",                          "Level 4"
-  )
-
-tbl_improved_pts_caption <- "Country-year cases where including civil society restrictions improved PTS predictions"
-
-if (!is_docx) {
-  tbl_improved_pts %>% 
-    kbl(align = "llcccc",
-        booktabs = TRUE, linesep = "\\addlinespace",
-        caption = tbl_improved_pts_caption) %>% 
-    kable_styling(latex_options = c("hold_position")) %>% 
-    row_spec(0, bold = TRUE) %>% 
-    column_spec(1, width = "0.1\\\\textwidth") %>% 
-    column_spec(2, width = "0.05\\\\textwidth") %>% 
-    column_spec(3:6, width = "0.16\\\\textwidth")
-} else {
-  tbl_improved_pts %>% 
-    hux() %>% 
-    set_font_size(10) %>%
-    set_all_padding(3) %>% 
-    set_align(everywhere, 1:2, "left") %>% 
-    set_align(everywhere, 3:6, "center") %>% 
-    set_bold(1, everywhere) %>%
-    set_bottom_border(1, everywhere) %>%
-    set_width(1) %>% 
-    set_wrap(TRUE) %>% 
-    huxtable::set_caption(tbl_improved_pts_caption) %>% 
-    huxtable::as_flextable()
-}
-```
-
-\newpage
-
-\blandscape
-
-## Complete model results
-
-\memSingleSmall
-
-```{r tbl-models-pts}
-model_names_tbl_pts <- c("Total barriers",
-                         "Barriers to advocacy",
-                         "Barriers to entry",
-                         "Barriers to funding",
-                         "Civil society repression")
-
-names(models_paper_pts) <- model_names_tbl_pts
-
-tbl_reg_pts_caption <- "Full results from ordered logistic regression models predicting political terror"
-
-tbl_reg_pts <- modelsummary(models_paper_pts,
-                            output = table_format,
-                            statistic = "[{conf.low}, {conf.high}]",
-                            coef_map = coef_list,
-                            gof_omit = "ELPD",
-                            escape = FALSE,
-                            caption = tbl_reg_pts_caption,
-                            notes = c(model_note),
-                            longtable = TRUE)
-
-if (!is_docx) {
-  tbl_reg_pts %>% 
-    kable_styling() %>% 
-    add_header_above(header = c(" " = 1, "Outcome in t + 1" = 5))
-    # kable_styling(font_size = ifelse(is_latex, 7, NA)) %>%
-    # column_spec(1, width = "0.75in", latex_valign = "b") %>%
-    # column_spec(2:6, width = "1.3in", latex_valign = "b")
-    # column_spec(1, width = "0.10\\\\textwidth") %>%
-    # column_spec(2:6, width = "0.14\\\\textwidth")
-} else {
-  tbl_reg_pts %>% 
-    set_font_size(10) %>% 
-    set_all_padding(1) %>% 
-    set_align(everywhere, 2:6, "center") %>% 
-    set_bold(1, everywhere) %>% 
-    # set_col_width(1, 0.1) %>% 
-    # set_col_width(2:6, 0.14) %>% 
-    set_width(1) %>% 
-    set_wrap(TRUE) %>% 
-    huxtable::set_caption(tbl_reg_pts_caption) %>% 
-    huxtable::as_flextable()
-}
-```
-
-\clearpage
-
-```{r tbl-models-lhr}
-model_names_tbl_lhr <- c("Total barriers",
-                         "Barriers to advocacy",
-                         "Barriers to entry",
-                         "Barriers to funding",
-                         "Civil society repression")
-
-names(models_paper_lhr) <- model_names_tbl_lhr
-
-tbl_reg_lhr_caption <- "Full results from Gaussian regression models predicting latent human rights"
-
-tbl_reg_lhr <- modelsummary(models_paper_lhr,
-                            output = table_format,
-                            statistic = "[{conf.low}, {conf.high}]",
-                            coef_map = coef_list,
-                            gof_omit = "ELPD",
-                            escape = FALSE,
-                            caption = tbl_reg_lhr_caption,
-                            notes = c(model_note),
-                            longtable = TRUE)
-
-if (!is_docx) {
-  tbl_reg_lhr %>% 
-    kable_styling() %>% 
-    add_header_above(header = c(" " = 1, "Outcome in t + 1" = 5))
-    # kable_styling(font_size = ifelse(is_latex, 7.5, NA)) %>% 
-    # column_spec(1, width = "0.10\\\\textwidth") %>% 
-    # column_spec(2:6, width = "0.14\\\\textwidth")
-} else {
-  tbl_reg_lhr %>% 
-    set_font_size(10) %>% 
-    set_all_padding(1) %>% 
-    set_align(everywhere, 2:6, "center") %>% 
-    set_bold(1, everywhere) %>% 
-    set_width(1) %>% 
-    set_wrap(TRUE) %>% 
-    huxtable::set_caption(tbl_reg_lhr_caption) %>% 
-    huxtable::as_flextable()
-}
-```
-
-\clearpage
-
-\elandscape
-
-\memSingle

### 2021-11-15 _targets.R
Better comments and headings here

@@ -2,12 +2,12 @@ library(targets)
 library(tarchetypes)
 library(tibble)
 
-# General variables
+# General pipeline settings ----
+
 csl <- "pandoc/csl/apa.csl"
 bibstyle <- "bibstyle-apa"
 
 suppressPackageStartupMessages(library(brms))
-
 
 # Bayes-specific stuff
 options(mc.cores = 4,
@@ -44,11 +44,17 @@ set.seed(9936)  # From random.org
 
 future::plan(future::multisession)
 
+# haha this project was the first time I'd used {targets} and I wasn't *quite*
+# sure what this option did back then, so I shoved a billion packages in here
+# needlessly and we don't have time to go back and be more specific about which
+# targets need which packages, so we'll live with this mega list :shrug:
 tar_option_set(packages = c("tidyverse", "countrycode", "states", "WDI", "here", "fs",
                             "readxl", "haven", "sf", "lubridate", "scales",
                             "janitor", "kableExtra", "huxtable", "modelsummary",
                             "knitr", "withr", "flextable", "testthat", "DT",
                             "brms", "tidybayes", "broom", "cmdstanr", "jsonlite"))
+
+# R functions ----
 
 source("R/funs_data-cleaning.R")
 source("R/funs_knitting.R")
@@ -68,8 +74,10 @@ source("R/models_lhr.R")
 here_rel <- function(...) {fs::path_rel(here::here(...))}
 
 
+# Pipeline ----
+
 list(
-  # Define raw data files
+  ## Define raw data files ----
   tar_target(chaudhry_raw_file,
              here_rel("data", "raw_data", "Chaudhry restrictions", "SC_Expanded.dta"),
              format = "file"),
@@ -111,10 +119,10 @@ list(
              here_rel("data", "raw_data", "Civicus", "civicus_2021-03-19.json"),
              format = "file"),
 
-  # Define helper functions
+  ## Define helper functions ----
   tar_target(plot_funs, here_rel("lib", "graphics.R"), format = "file"),
 
-  # Load and clean data
+  ## Load and clean data ----
   tar_target(world_map, load_world_map(naturalearth_raw_file)),
   tar_target(civicus_clean, load_clean_civicus(civicus_raw_file)),
[…]

### 2021-11-15 manuscript/manuscript.Rmd
Expand Egypt case study

@@
   canary <- tar_read(panel)
+  tar_load(vdem_clean)
   tar_load(civicus_map_data)
@@
 Rather, the law would be a "weapon hanging on the wall that never fires" and stand as a warning to potentially uncooperative NGOs [@Kozenko:2015].
-Similarly, Egypt's 2002 NGO law instated severe barriers to freedom of association, banned NGOs from engaging in activities that "threaten national unity or violate public order or morality," and also prevented groups from receiving foreign funding.
-But despite the harsh legal framework, the Egyptian NGO sector nearly doubled in size between 1993–2011.
-This is because the state targeted a limited number of organizations working on politically sensitive issues such as human rights and democracy, while simultaneously tolerating organizations working on tamer issues [@Brechenmacher:2017].
 
@@
 their de facto implementation could also potentially be explained by the time frame of these strategies.
-De jure laws are a long-term strategy to prevent threats to the regime from coalescing in the first place.
-For instance, Egypt's Law 84 of 2002—which outlined many anti-NGO restrictions—has been on the books for nearly two decades, but only over the past five years have post-revolutionary regimes used it more broadly [@Ruffner:2015].
+As we explore in the next section, de jure civil society laws are a long-term strategy to prevent threats to the regime from coalescing in the first place.
 As such, the long-term effects of these laws in terms of their predictive power may require a much longer time period under study.
@@
 
+# Discretionary disconnect between de jure and de facto NGO regulations: the case of Egypt
+
+When looking both at marginal effects and improvements in predictive power, we thus find that the de facto implementation of anti-civil society measures are a stronger indicator of future repression than formal de jure laws.
+One reason for this disconnect between law and implementation is that laws targeted at NGOs are often not designed to be used immediately, but instead serve to protect regimes against potential threats in the future.
+Egypt provides a prime example of this mechanism.
+
+```{r plot-egypt-cs, fig.width=6.5, fig.height=2, fig.asp=NULL, fig.cap="The disconnect between Egypt's de jure 2002 law and the widespread de facto repression of civil society a decade later"}
+egypt_cs <- vdem_clean %>% 
+  filter(gwcode == 651)
+
+cs_color <- viridisLite::plasma(5, end = 0.8)[3]
+law_color <- viridisLite::plasma(5, end = 0.8)[1]
+event_color <- viridisLite::plasma(5, end = 0.8)[5]
+
+ggplot(egypt_cs, aes(x = year, y = v2csreprss)) +
+  geom_vline(xintercept = 2002, color = law_color) +
+  geom_vline(xintercept = 2011, color = event_color) +
+  geom_point(color = cs_color, size = 2) +
+  geom_line(color = cs_color, size = 0.5) +
+  annotate(geom = "segment", x = 2000, xend = 2002, y = -1.05, yend = -1.05, 
+           arrow = arrow(angle = 15, length = unit(0.5, "lines"))) +
+  annotate(geom = "segment", x = 2014, xend = 2011, y = -0.65, yend = -0.65, 
+           arrow = arrow(angle = 15, length = unit(0.5, "lines"))) +
+  annotate(geom = "label", x = 1999, y = -1.05, size = pts(9),
+           label = "Law 84\nof 2002\npassed") +
+  annotate(geom = "label", x = 2014, y = -0.65, size = pts(9),
+           label = "2011\nuprising") +
+  labs(x = "Year", y = "De facto CSO repression") +
+  theme_ngo(9)
+```
+
+In the wake of domestic terrorist attacks in the late 1990s, the Egyptian parliament passed Law 84 of 2002, or the Law on Associations and Foundations [@Agati:2007, 60].
+The new law imposed specific limits on international and foreign-connected NGOs and required that all NGOs register with the Ministry of Social Solidarity.
+Any revenue from foreign associations to nonprofit organizations working in Egypt required both recipients and donors to submit multiple applications to the Ministry of Foreign Affairs and state security, and the latter maintained ultimate veto power over the approval process [@Thabet:2004, 162].
+Though it granted the government substantial oversight power over NGOs, Law 84 also allowed for enormous discretion in enforcement.
+In spite of the strict legal framework, the Egyptian NGO sector nearly doubled in size between 1993–2011 [@Brechenmacher:2017], largely because of the government's selective and targeted enforcement of the law.
+When NGOs become too contentious or pose a threat to the regime, officials could use minor infractions in more obscure parts of the law to fine or shut down the organization, but these attacks on NGOs were limited to specific NGOs.
+As seen in Figure \@ref(fig:plot-egypt-cs), Egypt saw its highest, most stable, and most open level of broader civil society repression in the decade following the passage of Law 84.
+
+The calculus of enforcement changed as the state faced increased threats to its stability.
+Following Hosni Mubarak's removal as president in February 2011, the Supreme Council of the Armed Forces (SCAF) took temporary control over governing the country.
+SCAF worked throughout the year to curtail protests and often resorted to violence to break up demonstrations, which then led to larger and more violent protests in response.
+The tension culminated on December 16, when troops filled Tahrir Square to put down an anti-SCAF demonstration, killing 10 and wounding more than 400.
+Two weeks later, Egyptian security forces raided the offices of 17 local and international NGOs (Fadel and Warrick 2011)—including Freedom House, the National Democratic Institute, and the International Republican Institute—and arrested dozens of domestic and international NGO staff.
+The stated legal pretext for this raid was that the organizations were not officially registered and thus in violation of Law 84.
+The de jure law—constantly looming in the background, but enforced selectively—was finally implemented and enforced more expansively.
+In the years after the 2011 uprising, post-revolutionary regimes have enforced the law more consistently, further constricting the space for civil society [@Ruffner:2015], as seen in the rapid drop in broader civil society repression in Figure \@ref(fig:plot-egypt-cs).
+
+Law 84 (and its replacement Law 70 of 2017) is thus a useful lever for selectively controlling the allowable space for dissidence and leaving open the possibility of future human rights abuses.
+The law's built-in discretionary authority permits the government to give the appearance of concessions and openness to civil society while simultaneously providing the government with the ability to target individual NGOs and reserving the right to engage in broader crackdowns of associational rights.
+This trend holds across many other countries—anti-NGO laws can serve as a useful avenue for future human rights abuses, sometimes with years separating the official passage of the law and the large-scale implementation of the law.
+
 # Conclusion and implications
@@
 Given these potential knock-on effects, in this paper, we posited that the ongoing global crackdown on NGOs could predict worsening human rights abuses.
-Using original data on de jure and de facto NGO repression from 1990–2013, we find weal support for the predictive power of de jure restriction on political terror and overall latent human rights values.
+Using original data on de jure and de facto NGO repression from 1990–2013, we find weak support for the predictive power of de jure restriction on political terror and overall latent human rights values.
 Marginal predictions show that—all else held equal—adding new anti-NGO laws increases the probability of seeing moderate levels of political terror and is associated with worsening human rights conditions more generally.
@@
 NGOs that are underfunded, understaffed tend to shut down when faced with increasing restrictions [@Heiss:2019].
-In sum, while de jure laws do not effect levels of physical integrity and civil liberties violations, they have been shown to have other adverse consequences in the literature.
-Moreover, since the actual implementation of these laws through de facto civl society repression can have negative impacts of broader patterns of human rights abuses, the passage of these laws may still be a concerning first step that paves the path for implementation.
+In sum, while de jure laws do not effect levels of physical integrity and civil liberties violations in particular, research has found that they other adverse consequences.
+Moreover, since the actual implementation of these laws through de facto civl society repression can have negative effects on broader patterns of human rights abuses, the passage of these laws may still be a concerning first step that paves the path for future implementation.
 

### 2021-11-15 lib/graphics.R

@@ -1,3 +1,6 @@
+# Make labels use Barlow by default
+update_geom_defaults("label", list(family = "Inter"))
+
 # ggplot themes -----------------------------------------------------------
 
 #' theme_ngo

### 2021-11-15 manuscript/manuscript.Rmd
Mention Egypt case study in intro roadmap
Address Reviewer 2's issue 9 about connection between CS and HR violations

@@
 Using both original data as well as data from several existing datasets, we build an ensemble of predictive models and explore (1) the marginal effects of civil society repression on different forms of broader human rights repression, and (2) the out-of-sample predictive performance of each model.
+We then illustrate one of the mechanisms of our findings—the disconnect between de jure and de facto anti-NGO repression—with a brief case study of Egypt's treatment of civil society since 2002.
 We conclude by discussing the implications of our findings on autocratic survival, and how states may manage NGOs as a strategy to remain in power.
@@
 
-This administrative crackdown via anti-NGO laws may foreshadow future government transgressions.
-Autocratic leaders want to avoid accountability, and NGOs often stand in conflict with that goal.
+This administrative crackdown via anti-NGO laws can provide convenient avenues for more violent repression and can foreshadow future government transgressions.
+Autocratic leaders want to avoid accountability and NGOs often stand in conflict with that goal.
 Civil society organizations, including NGOs, can help shape the narrative of leaders' performance both domestically and internationally.
@@
 Such repression reflects the government's willingness and capability to use measures that can make it avoid accountability.
-Once a state targets NGOs, over time it may grow less hesitant to apply violent repression more widely and more severely.
+Once a state targets NGOs, over time it may grow less hesitant to apply violent repression more widely and more severely, thus leading to broader contractions of civil and human rights throughout the country.
 

### 2021-11-15 manuscript/manuscript.Rmd
Addressed R2's issue 16, streamlining the prediction part

@@
 For the ordinal Political Terror Scale, Table \@ref(tab:correct-not-correct) shows a count of correct and incorrect predictions from each model.
-Because the physical violence and private civil liberties indexes are predicted with Gaussian models, we measure predictive accuracy with the root mean squared error, provided in Table \@ref(tab:tbl-rmse).
+We measure the predicted accuracy of our latent human rights models with the root mean squared error, provided in Table \@ref(tab:tbl-rmse).
 In the appendix we include lists of country-year cases that see improved predictions when taking civil society laws and repression into account.
@@
         caption = tbl_rmse_caption) %>% 
+    pack_rows(index = c(" " = 1, "De jure repression" = 4, "De facto repression" = 1)) %>% 
     kable_styling()
@@
     set_all_padding(3) %>% 
+    insert_row("De jure repression", "", "", after = 2) %>% 
+    insert_row("De facto repression", "", "", after = 7) %>% 
     set_align(everywhere, 1, "left") %>% 
@@
     set_bold(1, everywhere) %>%
+    set_bold(c(3, 8), everywhere) %>%
+    set_bottom_border(c(3, 8), everywhere) %>%
     set_width(1) %>% 
@@
 
-When looking at the level of physical violence in a country, including de jure and de facto repression does very little to improve predictive accuracy.
-As Table \@ref(tab:tbl-rmse) shows, accounting for legal barriers and civil society repression only reduces the RMSE by at most 0.4% compared to the baseline model.
-This is likely related to the lack of improvements in predicting political terror—both indices measure similar phenomena.
-Similarly, accounting for de facto civil society repression when modeling latent human rights only results in slight changes to the RMSE.
-However, including civil society-related predictors when modeling private civil liberties does result in small gains in accuracy, reducing the RMSE by as much as 2% compared to the baseline model.
-
+When looking at the overall latent human rights values in a country, including de jure and de facto repression does very little to improve predictive accuracy.
+As Table \@ref(tab:tbl-rmse) shows, accounting for de facto civil society repression only reduces the RMSE by 0.29% compared to the baseline, while accounting for de jure laws worsen the models' predictive power slightly.
 While these gains in predictive power appear negligible, they are somewhat comparable with the findings of previous work.
 For instance, in their work on the effect of the murder of journalists on predicting future political terror, @GohdesCarey:2017 find that accounting for violence against the media adds five correctly predicted cases of PTS scores and improves predictions in seven cases.
+
+We thus again find that de facto civil society repression is a stronger predictor of worsening human rights in the future than formal laws on their own.
+Actual government interference in civil society act as a possible signal of future abuses of civil and human rights better than simply the presence of a law that could potentially be used at some point in the future.
 

### 2021-11-15 manuscript/manuscript.Rmd
Tweaks to figures; fill in missing references

@@
   tar_load(c(m_pts_total, m_pts_advocacy, m_pts_entry, m_pts_funding,
-             m_clphy_total, m_clphy_advocacy, m_clphy_entry, m_clphy_funding,
-             m_clpriv_total, m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding,
-             m_pts_v2csreprss, m_clphy_v2csreprss, m_clpriv_v2csreprss, m_lhr_v2csreprss))
+             m_lhr_total, m_lhr_advocacy, m_lhr_entry, m_lhr_funding,
+             m_pts_v2csreprss, m_lhr_v2csreprss))
 
   # Model tables
-  tar_load(c(models_paper_pts, models_paper_clphy, 
-             models_paper_clpriv, models_paper_lhr))
+  tar_load(c(models_paper_pts, models_paper_lhr))
 
@@
   # Load marginal effects
-  tar_load(c(mfx_e1a_pts, mfx_e1b_clphy, mfx_e1c_clpriv, mfx_e1d_lhr,
-             mfx_e2a_pts, mfx_e2b_clphy, mfx_e2c_clpriv, mfx_e2d_lhr))
+  tar_load(c(mfx_e1a_pts, mfx_e1d_lhr, mfx_e2a_pts, mfx_e2d_lhr))
 })
@@
 Existing research on international human rights law shows that civil society groups play an important role in highlighting states' violations of their treaty commitments.
-By revealing the gap between treaty provisions and actual state behavior, these organizations play a vital role in reducing the "compliance gap" between legal commitments and state practices [@Hathaway:2002; @HafnerBurtonTsutsui:2005; @Simmons:2009].
+By revealing the gap between treaty provisions and actual state behavior, these organizations play a vital role in reducing the "compliance gap" between legal commitments and state practices [@Hathaway:2002; @Hafner-BurtonTsutsui:2005; @Simmons:2009].
 The dramatic rise in anti-NGO laws and their implementation through de facto civil society repression threatens to exacerbate this compliance gap.
-Indeed, recent research finds that when governments have committed to human rights treaties and continue to commit severe human rights abuses, they impose anti-NGO laws to escape monitoring [@Bakke2020].
+Indeed, recent research finds that when governments have committed to human rights treaties and continue to commit severe human rights abuses, they impose anti-NGO laws to escape monitoring [@BakkeMitchellSmidt:2020].
 Our findings support these arguments by showing that de facto levels of NGO repression are a possible predictor of broader patterns of human rights violations.
@@
 
-```{r barriers, fig.width=6, fig.height=6, fig.asp=NULL, fig.cap="Number of legal barriers to NGO activity per country over time (de jure legislation) and average level of CSO repression across democracies and non-democracies (de facto implementation)"}
+```{r barriers, fig.width=7, fig.height=5.5, fig.asp=NULL, fig.cap="Number of legal barriers to NGO activity per country over time (de jure legislation) and average level of CSO repression across democracies and non-democracies (de facto implementation)"}
 regulations <- tribble(
@@
   labs(x = NULL, y = "Number of countries") +
-  theme_ngo(9) + 
+  theme_ngo() + 
   theme(legend.justification = "left",
@@
        legend.key.size = unit(0.7, "lines")) +
-  theme_ngo(9) + 
+  theme_ngo() + 
   theme(legend.justification = "left",
@@
   labs(y = "Average CSO repression", x = NULL) +
-  theme_ngo(9) +
+  theme_ngo() +
   theme(legend.justification = "left",
@@
 
-To see how both de jure and de facto civil society restrictions influence general human rights repression, we use four different quantitative measures of repression, each of which capture different dimensions of political and civil violence.
+To see how both de jure and de facto civil society restrictions influence general human rights repression, we use two different quantitative measures of repression, each of which capture different dimensions of political and civil violence.
 First, following @GohdesCarey:2017, who use the killing of journalists to predict worsening human rights conditions, we use the Political Terror Scale (PTS), which assigns countries to one of five possible levels of repression each year [@GibneyCornettWood:2019], with Level 5 representing widespread political violence—including arrests, imprisonment, political murders, disappearances, and torture.
@@
 
-```{r repression, fig.width=6.5, fig.height=4.5, fig.asp=NULL, fig.cap="Key measures of repression over time"}
+```{r repression, fig.width=5.5, fig.height=4, fig.asp=NULL, fig.cap="Key measures of repression over time"}
 pts_plot <- canary %>% 
@@
   labs(y = "Number of countries", x = NULL, caption = "(Higher PTS levels = more repression)") +
-  theme_ngo(9) +
+  theme_ngo() +
   theme(legend.justification = "left",
@@
   labs(y = "Average value", x = NULL, caption = "(Higher values = less repression)") +
-  theme_ngo(9) +
+  theme_ngo() +
   theme(legend.justification = "left") +
@@
 
+```{r lhr-barriers-trends, include=FALSE, warning=FALSE}
+lhr_barriers_stats <- m_lhr_total %>% 
+  tidy(effects = "fixed") %>% 
+  mutate(term = janitor::make_clean_names(term)) %>%
+  split(.$term)
+
+lhr_advocacy_stats <- m_lhr_advocacy %>% 
+  tidy(effects = "fixed") %>% 
+  mutate(term = janitor::make_clean_names(term)) %>%
+  split(.$term)
+
+lhr_barriers_diffs <- m_lhr_total %>% 
+  emmeans(~ barriers_total + gwcode, var = "barriers_total", 
+          at = list(gwcode = 999,
+                    barriers_total = c(0:9)),
+          epred = TRUE, re_formula = NULL,
+          allow_new_levels = TRUE, sample_new_levels = "gaussian") %>% 
+  tidy() %>% 
+  mutate(pct_change = (estimate - lag(estimate)) / lag(estimate),
+         id = janitor::make_clean_names(barriers_total)) %>% 
+  split(.$id)
+
+lhr_advocacy_diffs <- m_lhr_advocacy %>% 
+  emmeans(~ advocacy + gwcode, var = "advocacy", 
+          at = list(gwcode = 999,
+                    advocacy = c(0:1)),
+          epred = TRUE, re_formula = NULL,
+          allow_new_levels = TRUE, sample_new_levels = "gaussian") %>% 
+  tidy() %>% 
+  mutate(pct_change = (estimate - lag(estimate)) / lag(estimate),
+         id = janitor::make_clean_names(advocacy)) %>% 
+  split(.$id)
+```
+
 As new laws are added, though, the distribution of probabilities for each of the PTS levels shifts.
@@
 Across all four models for different categories of legal barriers, holding all other values constant, the predicted level of human rights respect decreases.
-Adding a new NGO law is associated with a -0.013-point decline in the level of respect for human rights in the following year, on average.
-The marginal effect is larger (-0.02) for additional barriers to advocacy and entry, which represent more burdensome restrictions than limits to funding.
+Adding a new NGO law is associated with a `r round(lhr_barriers_stats$barriers_total$estimate, 3)`-point decline in the level of respect for human rights in the following year, on average, representing a roughly 5% decline in predicted the predicted value.
+The marginal effect is larger (`r round(lhr_advocacy_stats$advocacy$estimate, 2)`, or a 9% decline) for additional barriers to advocacy and entry, which represent more burdensome restrictions than limits to funding.
 
@@
 ```{r plot-mfx-e1b, fig.width=7.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on latent human rights scoress"}
-# TODO: Andrew: Add more specific coefficients and percent changes to the prose above
 out_mfx_e1b <- mfx_e1d_lhr %>% 
@@
 The effect of de facto civil society repression on predicted values of the PTS mirrors what we found previously with our first empirical expectation.
-As seen in Figure \@ref(fig:plot-mfx-e2a), at the lowest levels of repression, Levels 1 and 2 are the most common predicted outcomes and are each equiprobable at roughly 50%.
+As seen in left panel of Figure \@ref(fig:plot-mfx-e2ab), at the lowest levels of repression, Levels 1 and 2 are the most common predicted outcomes and are each equiprobable at roughly 50%.
 As de facto CSO repression increases, though, the probability of seeing Level 1 decreases and is replaced with either Level 2 or Level 3.
@@
 
-```{r plot-mfx-e2a, fig.width=6.5, fig.height=5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on the probability of specific levels of political terror", out.width="75%"}
+```{r plot-mfx-e2ab, fig.width=7, fig.height=4.5, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on the probability of specific levels of political terror and predicted latent human rights values"}
 out_mfx_e2a <- mfx_e2a_pts %>% 
@@
   ungroup() %>% 
+  mutate(fake_facet_title = "Political Terror Scale") %>% 
   ggplot(aes(x = effect1__, y = estimate__, color = effect2__, fill = effect2__)) +
@@
        color = "Political Terror Scale", fill = "Political Terror Scale",
-       title = "Political Terror Scale",
        caption = "(x-axis reversed; greater repression on the right)") +
+  facet_wrap(vars(fake_facet_title)) +
   theme_ngo() +
   theme(legend.box.margin = margin(t = 0.5, unit = "lines"))
-out_mfx_e2a
+
+out_mfx_e2b <- mfx_e2d_lhr %>% 
+  mutate(fake_facet_title = "Latent human rights values") %>% 
+  ggplot(aes(x = effect1__, y = estimate__)) +
+  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
+              fill = "#FF4136", color = NA) +
+  geom_line(size = 1, color = "#FF4136") +
+  scale_x_reverse() +
+  labs(x = "Civil society repression",
+       y = "Predicted latent human rights value",
+       caption = "(x-axis reversed; greater repression on right\nhigher values in y-axis show less violence and better protection of rights)") +
+  facet_wrap(vars(fake_facet_title)) +
+  theme_ngo()
+
+out_mfx_e2a | out_mfx_e2b
 ```
@@
 
-De facto civil society repression has a noticeable effect on latent human rights values (see Figure \@ref(fig:plot-mfx-e2b)).
+De facto civil society repression has a noticeable effect on latent human rights values (see the right panel of Figure \@ref(fig:plot-mfx-e2ab)).
 When holding all other model parameters at their typical values, increased civil society repression predicts a strong decrease in respect for broader human rights: a one unit change in civil society repression is associated with a `r round(lhr_csreprss_stats$v2csreprss$estimate, 2)`-unit change in overall latent human rights.
@@
 
-```{r plot-mfx-e2b, fig.width=6.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of changing levels of civil society repression on latent human rights"}
-# TODO: Combine with previous plot so there's just one, with fake facet titles
-out_mfx_e2d <- mfx_e2d_lhr %>% 
-  ggplot(aes(x = effect1__, y = estimate__)) +
-  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
-              fill = "#FF4136", color = NA) +
-  geom_line(size = 1, color = "#FF4136") +
-  scale_x_reverse() +
-  labs(x = "Civil society repression",
-       y = "Predicted latent human rights value",
-       title = "Latent human rights", 
-       caption = "(x-axis reversed; greater repression on right\nhigher values in y-axis show less violence and better protection of rights)") +
-  theme_ngo(8)
-out_mfx_e2d
-```
-
 ## Predictions
-
-```{r eval=FALSE, include=FALSE}
-# TODO: Andrew: Streamline this section
-```
 
@@
   labs(x = "Year", y = "De facto CSO repression") +
-  theme_ngo(9)
+  theme_ngo()
 ```
@@
 The broader literature on state repression of NGOs has shown that de jure laws can have numerous adverse consequences.
-Foreign funding laws have led to a 32% decline in bilateral aid flows [@DP:2018].
+Foreign funding laws have led to a 32% decline in bilateral aid flows [@DupuyPrakash:2018].
 NGOs that are underfunded, understaffed tend to shut down when faced with increasing restrictions [@Heiss:2019].
@@
 The dramatic growth in these laws has important implications for the power of the human rights regime and international human rights law.
-The UN Special Rapporteur on the Right to Freedom of Peaceful Assembly and Association has pointed out that the right of NGOs to seek, receive and utilize resources is an essential component of the right to association [@citeme].
+The UN Special Rapporteur on the Right to Freedom of Peaceful Assembly and Association has pointed out that the right of NGOs to seek, receive and utilize resources is an essential component of the right to association [@Kiai:2013].
 Anti-NGO laws, including barriers to funding, violate core human rights treaties such as the International Covenant on Civil and Political Rights (ICCPR).

### 2021-11-15 manuscript/manuscript.Rmd
Update word count

@@
   url: https://www.andrewheiss.com/
-date: "July 20, 2021"
-published: Under review
+date: "November 15, 2021"
+published: "Conditionally accepted at the *Journal of Human Rights*"
 code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/canary-ngos/>"
@@
 # keywords: civil society, NGOs, repression, human rights, political terror, civil liberties
-word-count: "7,159"
+word-count: "8,007"
 thanks: >-

### 2021-11-17 manuscript/manuscript.Rmd
Suparna edits

@@
 Using original data on NGO repression, we test whether NGO crackdown is a predictor of political terror, and violations of physical integrity rights and civil liberties.
-We find that while formal de jure laws provide little information in predicting future repression, their patterns of implementation, or de facto civil society repression, predicts worsening respect for physical integrity rights and civil liberties.
+We find that while de jure anti-NGO laws provide little information in predicting future repression, their patterns of implementation—or de facto civil society repression—predicts worsening respect for physical integrity rights and civil liberties.
 # keywords: civil society, NGOs, repression, human rights, political terror, civil liberties
@@
 More than 100 countries have proposed or enacted 244 different measures that have restricted, repressed, or shut down civil society since 2013 [@icnl:2021].
-In Human Rights Watch's 2016 World Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory, and over the past decade, the majority of the world has seen a substantial narrowing of allowable civic space.
+In Human Rights Watch's 2016 World Report, Executive Director Kenneth Roth argued that civil society was under more aggressive attack than at any time in recent memory.
 As seen in Figure \@ref(fig:civicus-map), by the end of 2020, only `r civicus$Open$prop_nice` of countries had open and unrestricted civic space [@civicusmonitor; @ChaudhryHeiss:2021].[^open]
@@
 Much of this targeting of NGOs has been non-violent.
-Rather than publicly arrest or beat activists, states implement "administrative crackdown," or the passage of laws to create barriers to NGO advocacy, entry, and funding [@Chaudhry:2016].
-The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations [@Heiss:2019; @Heiss:2017].
+Rather than publicly arrest or beat activists, states implement "administrative crackdown," or the passage of anti-NGO laws to create barriers to NGO advocacy, entry, and funding [@Chaudhry:2022].[^1] The use of legal tools instead of violent repression means that NGOs have to adapt their practices to stay within the bounds of permitted activities and operations [@Heiss:2019; @Heiss:2017].
 While this can lead to the depoliticization and avoidance of direct political activism by CSOs [@BloodgoodTremblay-Boire:2017], states cannot soften or neutralize all forms of political activity and advocacy in subtle, legal ways like they have with NGOs.
@@
 
-In this paper, we explore the power of anti-NGO repression in predicting political terror and underlying human rights abuses.
+In this paper, we explore the power of anti-NGO repression in predicting political terror and broader patterns of human rights abuses.
 We argue that information about NGO crackdown can be a valuable indicator of human rights trajectories.
@@
 To assess if attacks on NGOs and activists can provide us useful information about future repression, we use an original dataset on state crackdown on NGOs using legal repression across all countries from 1990–2013.
-We differentiate between two forms of NGO repression: official de jure anti-NGO restrictions that are codified in law, and their de facto implementation.
+We differentiate between two forms of NGO repression: de jure anti-NGO laws, and their de facto implementation.
+While the former captures anti-NGO laws that seek to repress these organizations, the latter captures their effects when they are actually implemented or enforced.
+The distinction is important—laws may frequently be passed to create a chilling effect on civil society.
+They provide a legal threat that could compel NGOs to self-censor, without actually seeing any uniform or widespread implementation.
+
 Using multilevel Bayesian modeling, we find that formal de jure laws potentially provide a weak signal of future repression.
-However, we find that accounting for their implementation does boost our models' predictive power.
 Increasing de facto civil society repression, on the other hand, predicts both a moderate increase in the probability of moderate political terror and a deterioration in the overall respect for human rights in a typical country.
 
-Our paper makes an important contribution in predicting the onset of repressive state policies.
-While structural factors such as levels of democracy, economic development, electoral competitiveness can identify countries that are likely to have more or less respect for civic freedoms, these factors are also slow to change over time.
+Our paper makes two important contributions to the fields of repression and international human rights law.
+First, in predicting the onset of repressive state policies, while structural factors such as levels of democracy, economic development, electoral competitiveness can identify countries that are likely to have more or less respect for civic freedoms, these factors are also slow to change over time.
 As such, they may not be particularly suitable for forecasting short-term trajectories, especially for moderately repressive countries.
@@
 While recent research has made important contributions to studying the extent and effects of state crackdown on NGOs, much of this focuses on de jure restrictions and its impact on NGOs and donors [@christensen2013; @DPR:2016; @DupuyPrakash:2018; @BromleySchoferLonghofer:2020; @BakkeMitchellSmidt:2020; @SmidtPereraMitchell:2021].
-By looking at laws *and* their implementation, as well as the extra-legal treatment of NGOs, we are able to assess the long-term effects of closing civic space on broader patterns of repression.
+By looking at laws *and* their actual practices of implementation, we are able to assess the long-term effects of closing civic space on broader patterns of repression.
+
+[^1]: In this article, we use the terms "anti-NGO laws" and "de jure NGO laws" interchangeably.
 
@@
 Using both original data as well as data from several existing datasets, we build an ensemble of predictive models and explore (1) the marginal effects of civil society repression on different forms of broader human rights repression, and (2) the out-of-sample predictive performance of each model.
-We then illustrate one of the mechanisms of our findings—the disconnect between de jure and de facto anti-NGO repression—with a brief case study of Egypt's treatment of civil society since 2002.
+We then illustrate one of the mechanisms of our findings—the distinct impact of de jure and de facto anti-NGO repression—with a brief case illustration of Egypt's treatment of civil society since 2002.
 We conclude by discussing the implications of our findings on autocratic survival, and how states may manage NGOs as a strategy to remain in power.
@@
 
-Repression is the use of coercive action against an individual or organization, within the territorial jurisdiction of the state, for the purpose of imposing a cost on the target as well as deterring specific activities perceived to be challenging to government personnel, practices, or institutions [@Goldstein:1978, p.
+Repression is the use of coercive action against an individual or organization, for the purpose of imposing a cost on the target as well as deterring specific activities perceived to be challenging to government personnel, practices, or institutions [@Goldstein:1978, p.
 xxvii; @Davenport:2007, 487; and @ConradRitter:2019, 15].
@@
 However, dissent and repression have an endogenous relationship: state authorities also frequently engage in preventive repression to undermine or restrict groups' abilities to dissent [@RitterConrad:2016; @ConradRitter:2019].
-Such preventive repression also damages organizations' capacity to impose costs [@Davenport:2007a, 47].
-NGOs are one actor that can pose challenges to political authorities, and state repression of these actors, especially through legal restrictions can be considered a form of preventive repression [@Chaudhry:2016].
+NGOs are one actor that can pose challenges to political authorities, and state repression of these actors—especially through anti-NGO laws—can be considered a form of preventive repression [@Chaudhry:2022].
 
@@
 While violence is often effective at curbing dissent, it can also backfire, leading to widespread protests, decreasing leaders' legitimacy and increasing their criminal liability [@KimSikkink:2010; @Sikkink:2011].
-In contrast to violence, administrative crackdown has fewer adverse consequences—citizens may see it as regulation rather than repression, resulting in little to no counter-mobilization.
+In contrast to violence, anti-NGO laws have fewer adverse consequences—citizens may see it as regulation rather than repression.
 It may also circumvent concerns among state security or bureaucratic agents about illegitimate orders based on violent repression [@StephanChenoweth:2008].
@@
 
-This administrative crackdown via anti-NGO laws can provide convenient avenues for more violent repression and can foreshadow future government transgressions.
+These anti-NGO laws can provide convenient avenues for more violent repression and can foreshadow future government transgressions.
 Autocratic leaders want to avoid accountability and NGOs often stand in conflict with that goal.
@@
 Monitoring by NGOs and subsequent shaming can include significant external revenue loss to states in the form of loss of aid, trade, and foreign direct investments [@KeckSikkink:1998; @BarryClayFlynn:2013].
-Government attempts to repress NGOs can signal the beginning of a deteriorating human rights situation.
+Government attempts to repress NGOs through the use of law can signal the beginning of a deteriorating human rights situation.
 Such repression reflects the government's willingness and capability to use measures that can make it avoid accountability.
@@
 Simply noting the passage of (or counting) these laws may therefore miss the effect of their de facto implementation.
-Moreover, the implementation of these laws may not be limited to its legal character.
+Some governments may even pass laws to create a chilling effect on these organizations.
+By providing a legal threat, they could compel these organizations to self-censor without even needing to implement these laws in any systematic or meaningful capacity.
+These laws, especially during moments or crises or contention, "highlight to the wider NGO community-and citizenry-that the government is willing and capable of using the law to repress dissent" [@Brechenmacher:2017, 94].
+
+Moreover, the implementation of these laws may not be limited to their legal character.
 The government may also engage in harassment of NGOs and activists to dissuade NGOs from carrying out their operations.
-This may include measures such as detentions, short-term incarceration, as well as beatings, threats to families and destruction of valuable property.
-
-Finally, counting official laws can also undermeasure civil society repression because governments can repress NGOs without relying on formal laws.
+This may include measures such as detentions, short-term incarceration, as well as destruction of valuable property.
+Finally, counting official laws can also underestimate levels of NGO repression because governments can repress these organizations without relying on formal laws.
 As prior research in Egypt, Ethiopia, and Russia points out, "rather than systematically enforcing all repressive legal measures-often impossible owing to capacity constraints," governments may choose to use extra-legal means to intimidate, harass or prosecute a few NGOs or activists.
-These cases, especially during moments or crises or contention, "highlight to the wider NGO community-and citizenry-that the government is willing and capable of using the law to repress dissent" [@Brechenmacher:2017, 94].
+These can include arrests, trials, imprisonment, and other violent sanctions against NGO activists such as beatings, threats to families, and attacks on property.
+As such, de facto crackdown in the form of not just legal harassment but also material and violent sanctions could lead to increases in both physical integrity and civil liberties violations.
 
@@
 
-(ref:chaudhry) @Chaudhry:2016
+(ref:chaudhry) @Chaudhry:2022
 
@@
 
-To measure de jure repression, we use data on anti-NGO laws from @Chaudhry:2016 which includes official NGO laws for all countries (excluding micro-states) between 1990 and 2013.
+To measure de jure repression, we use data on anti-NGO laws from @Chaudhry:2022 which includes official NGO laws for all countries (excluding micro-states) between 1990 and 2013.
 This measure of formal legal barriers does not necessarily represent individual laws.
 Instead, we count the presence or absence of specific types of anti-NGO legal barriers as a binary variable.
-If a country passes a broader NGO laws that implements several of these barriers simultaneously (e.g.
+If a country passes a law that implements several of these barriers simultaneously (e.g.
 making registration burdensome and restricting foreign funds), the values for each barrier will flip from 0 to 1.
@@
 This variable captures repression using an ordinal scale, defining civil society repression as severe, substantial, moderate, weak, or absent.
+At the most severe levels, the government violently and actively pursues NGOs, seeking to not only deter their activities but also liquidate them.
+On the least repressive end of the spectrum, NGOs are free to organize, associate, express themselves and criticize the government without fear of government sanctions or harassment.
 This ordinal scale is then aggregated with a Bayesian item response theory measurement model and converted to a continuous scale that ranges from roughly −3 to 3, with higher values indicating less repression.
@@
 While anti-NGO laws have increased steadily since 1990—particularly laws related to foreign funding—there has not necessarily been a corresponding rise in de facto civil society repression, which has remained fairly constant across different regime types.
-This divergence is likely indicative of the split between de jure laws and their de facto implementation—a rise in laws is not necessarily tied to direct CSO repression.
+This divergence is likely indicative of the split between de jure laws and their de facto implementation—new legislation is not necessarily implemented immediately and does not always lead to broader NGO repression.
 
@@
 We present the results of our models in two stages.
-First, to see how minor shifts in civil society laws and repression influence future human rights, we examine the marginal effects of our main explanatory variables when all other model covariates are held constant.
+First, to see how minor shifts in anti-NGOs laws and de facto repression influence future human rights, we examine the marginal effects of our main explanatory variables when all other model covariates are held constant.
 These effects are by no means causal—rather, they demonstrate how much variation in predicted human rights is possible as the legal environment for civil society improves or deteriorates within a typical country.
@@
 
-In general, when holding all other covariates constant, the passage of an additional anti-NGO legal barrier is generally associated with a higher probability of more severe level of political terror in the following year.
+In general, when holding all other covariates constant, the passage of an additional anti-NGO law is generally associated with a higher probability of more severe level of political terror in the following year.
 The probability of seeing different levels of political terror varies across different possible counts of NGO laws (see Figure \@ref(fig:plot-mfx-e1a)).
-In the absence of formal legal barriers, Level 2 of the PTS—an environment where political imprisonment, torture, and beatings are rare—is the most likely category of political terror across all models, appearing a predicted 60% of the time.
+In the absence of formal laws, Level 2 of the PTS—an environment where political imprisonment, torture, and beatings are rare—is the most likely category of political terror across all models, appearing a predicted 60% of the time.
 Level 1, where a country is under secure rule of law, is the second most likely outcome at slightly under 40%.
@@
 Adding new barriers to advocacy, entry, and funding decreases the likelihood of seeing Level 1 and increases the probability of a country turning to either Level 2 or Level 3 (with extensive political imprisonment and trial-free detention).
-The marginal effects of all forms of NGO laws results in this turn from Level 1 to Levels 2 or 3+, but this switching effect is strongest following additional barriers to advocacy.
+The marginal effects of all forms of anti-NGO laws results in this turn from Level 1 to Levels 2 or 3+, but this switching effect is strongest following additional barriers to advocacy.
 Anti-NGO laws do not predict more dramatic shifts in the PTS.
-Across all counts of legal barriers, the overall probability of seeing Levels 4 and 5 is minuscule, and the passage of additional laws does little to shift that probability.
+Across all counts of anti-NGO laws, the overall probability of seeing Levels 4 and 5 is minuscule, and the passage of additional laws does little to shift that probability.
 This is not unexpected however—the PTS has a natural ceiling at Level 5.
@@
 
-Figure \@ref(fig:plot-mfx-e1b) shows the marginal effects of additional NGO legislation on latent human rights scores.
+Figure \@ref(fig:plot-mfx-e1b) shows the marginal effects of additional anti-NGO laws on latent human rights scores.
 Across all four models for different categories of legal barriers, holding all other values constant, the predicted level of human rights respect decreases.
-Adding a new NGO law is associated with a `r round(lhr_barriers_stats$barriers_total$estimate, 3)`-point decline in the level of respect for human rights in the following year, on average, representing a roughly 5% decline in predicted the predicted value.
-The marginal effect is larger (`r round(lhr_advocacy_stats$advocacy$estimate, 2)`, or a 9% decline) for additional barriers to advocacy and entry, which represent more burdensome restrictions than limits to funding.
+Adding a new anti-NGO law is associated with a `r round(lhr_barriers_stats$barriers_total$estimate, 3)`-point decline in the level of respect for human rights in the following year, on average, representing a roughly 5% decline in predicted the predicted value.
+The marginal effect is larger (`r round(lhr_advocacy_stats$advocacy$estimate, 2)`, or a 9% decline) for additional barriers to advocacy and entry, which represent more burdensome registration requirements than barriers to funding.
 
@@
 
-### How does general repression change following civil society repression?
+### How does general repression change following de facto civil society repression?
 
@@
 
-When holding all other factors equal, the de facto implementation of anti-civil society measures thus appear to be a stronger marginal indicator of future repression than the passage of formal de jure laws.
+When holding all other factors equal, the de facto implementation of anti-NGO laws thus appear to be a stronger marginal indicator of future repression than simply the passage of these laws.
+While these laws may be intended to have a chilling effect on civil society (and certainly have a chilling effect on levels of aid and NGO operations as shown by recent literature), these de jure laws by themselves do not have similar adverse consequences on respect for physical integrity rights and civil liberties.
 In countries with low levels of political terror, it can potentially serve as a weak signal of a more general increase in political violence in the future, but predict more substantial changes in general respect for human rights.
@@
 We assess predictive power in a few different ways, depending on the model used to predict the outcome.
-For the ordinal Political Terror Scale, Table \@ref(tab:correct-not-correct) shows a count of correct and incorrect predictions from each model.
+For the ordinal PTS, Table \@ref(tab:correct-not-correct) shows a count of correct and incorrect predictions from each model.
 We measure the predicted accuracy of our latent human rights models with the root mean squared error, provided in Table \@ref(tab:tbl-rmse).
@@
 
-# Discretionary disconnect between de jure and de facto NGO regulations: the case of Egypt
+# Discretionary disconnect between de jure and de facto NGO repression: The case of Egypt
 
-When looking both at marginal effects and improvements in predictive power, we thus find that the de facto implementation of anti-civil society measures are a stronger indicator of future repression than formal de jure laws.
+When looking both at marginal effects and improvements in predictive power, we find that the de facto implementation of anti-civil society measures are a stronger indicator of future repression than de jure anti-NGO laws.
 One reason for this disconnect between law and implementation is that laws targeted at NGOs are often not designed to be used immediately, but instead serve to protect regimes against potential threats in the future.
@@
 Any revenue from foreign associations to nonprofit organizations working in Egypt required both recipients and donors to submit multiple applications to the Ministry of Foreign Affairs and state security, and the latter maintained ultimate veto power over the approval process [@Thabet:2004, 162].
+
 Though it granted the government substantial oversight power over NGOs, Law 84 also allowed for enormous discretion in enforcement.
 In spite of the strict legal framework, the Egyptian NGO sector nearly doubled in size between 1993–2011 [@Brechenmacher:2017], largely because of the government's selective and targeted enforcement of the law.
-When NGOs become too contentious or pose a threat to the regime, officials could use minor infractions in more obscure parts of the law to fine or shut down the organization, but these attacks on NGOs were limited to specific NGOs.
+When NGOs became too contentious or posed a threat to the regime, officials could use minor infractions in more obscure parts of the law to fine or shut down the organization, but these attacks on NGOs were limited to specific NGOs.
 As seen in Figure \@ref(fig:plot-egypt-cs), Egypt saw its highest, most stable, and most open level of broader civil society repression in the decade following the passage of Law 84.
@@
 Law 84 (and its replacement Law 70 of 2017) is thus a useful lever for selectively controlling the allowable space for dissidence and leaving open the possibility of future human rights abuses.
-The law's built-in discretionary authority permits the government to give the appearance of concessions and openness to civil society while simultaneously providing the government with the ability to target individual NGOs and reserving the right to engage in broader crackdowns of associational rights.
-This trend holds across many other countries—anti-NGO laws can serve as a useful avenue for future human rights abuses, sometimes with years separating the official passage of the law and the large-scale implementation of the law.
+The law's built-in discretionary authority permits the government to give the appearance of concessions and openness to civil society while simultaneously provides the government the ability to target individual NGOs and reserving the right to engage in broader crackdowns of associational rights.
+
+This trend holds across many other countries as well.
+For instance, even though India passed an anti-NGO law (containing multiple bariers to funding and advocacy) in 1976, it has not always been uniformly implemented.
+Rather, having an anti-NGO law on the books serves the state's long-term strategic interests, enabling it to crack down on NGOs when they start posing electoral or economic threats to the state [Chaudhry:2022].
+Anti-NGO laws can therefore serve as a useful avenue for future human rights abuses, sometimes with years separating the official passage of the law and the large-scale implementation of the law, explaining why de facto levels of NGO repression serve as a stronger predictor of worsening respect for human rights abuses.
 

### 2021-11-17 manuscript/manuscript.Rmd
Add @

@@
 For instance, even though India passed an anti-NGO law (containing multiple bariers to funding and advocacy) in 1976, it has not always been uniformly implemented.
-Rather, having an anti-NGO law on the books serves the state's long-term strategic interests, enabling it to crack down on NGOs when they start posing electoral or economic threats to the state [Chaudhry:2022].
+Rather, having an anti-NGO law on the books serves the state's long-term strategic interests, enabling it to crack down on NGOs when they start posing electoral or economic threats to the state [@Chaudhry:2022].
 Anti-NGO laws can therefore serve as a useful avenue for future human rights abuses, sometimes with years separating the official passage of the law and the large-scale implementation of the law, explaining why de facto levels of NGO repression serve as a stronger predictor of worsening respect for human rights abuses.

### 2021-11-17 manuscript/appendix.Rmd
Build appendix with targets

@@
 ---
-title: "NGO Repression as a Predictor of Worsening Human Rights Abuses"
-short-title: "NGO Repression and Human Rights"
+title: 'Appendix for "NGO Repression as a Predictor of Worsening Human Rights Abuses"'
+short-title: 'Appendix for "NGO Repression"'
 author:
@@
   url: https://www.andrewheiss.com/
-date: "July 20, 2021"
-published: Under review
+date: "November 16, 2021"
+# published: Under review
 code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/canary-ngos/>"
-abstract: >-
-  An increasing number of countries have recently cracked down on non-governmental organizations (NGOs).
-Much of this crackdown is sanctioned by law and represents a bureaucratic form of repression that could indicate more severe human rights abuses in the future.
-This is especially the case for democracies, which unlike autocracies, may not aggressively attack civic space.
-We explore if crackdowns on NGOs predict broader human rights repression.
-Anti-NGO laws are among the most subtle means of repression and attract lesser domestic and international condemnation compared to the use of violence.
-Using original data on NGO repression, we test whether NGO crackdown is a predictor of political terror, and violations of physical integrity rights and civil liberties.
-We find that while formal de jure laws provide little information in predicting future repression, their patterns of implementation, or de facto civil society repression, predicts worsening respect for physical integrity rights and civil liberties.
-# keywords: civil society, NGOs, repression, human rights, political terror, civil liberties
-word-count: "7,159"
-thanks: >-
-  We would like to thank participants of the 2021 International Studies Association (ISA) convention, and the "Human Rights on the Edge: The Future of International Human Rights Law and Practice" workshop hosted by the Global Human Rights Hub at Arizona State University for their comments and feedback.
 reference-section-title: References
@@
 toc: false
-title-page: true
-endnotes: true
-endfloat: false
+appendix: true
 mainfont: Cochineal
 sansfont: Inter
-author-note: >-
-  Suparna Chaudhry, PhD, Assistant Professor of International Affairs, Department of International Affairs, Lewis \& Clark College; Andrew Heiss, PhD, Assistant Professor of Public Management, Andrew Young School of Policy Studies, Georgia State University.
-correspondence: >-
-  Correspondence concerning this article should be addressed to Andrew Heiss, PhD, Department of Public Management and Policy, Andrew Young School of Policy Studies, Georgia State University, 14 Marietta Street NW, Suite 357, Atlanta, GA 30303.
-Contact: aheiss@gsu.edu
 editor_options: 
@@
 
-# Appendix
+```{r setup, include=FALSE}
+# Figure out output format
+is_docx <- knitr::pandoc_to("docx") | knitr::pandoc_to("odt")
+is_latex <- knitr::pandoc_to("latex")
+is_html <- knitr::pandoc_to("html")
 
-## Modeling approach
+# Word-specific things
+table_format <- ifelse(is_docx, "huxtable", "kableExtra")  # Huxtable tables
+conditional_dpi <- ifelse(is_docx, 300, 300)  # Higher DPI
+conditional_align <- ifelse(is_docx, "default", "center")  # Word doesn't support align
+
+# Knitr options
+knitr::opts_chunk$set(
+  echo = FALSE, warning = FALSE, message = FALSE,
+  tidy.opts = list(width.cutoff = 120),  # Code width
+  fig.retina = 3, dpi = conditional_dpi,
+  fig.width = 7, fig.asp = 0.618,
+  fig.align = conditional_align, out.width = "100%",
+  fig.path = "output/figures/",
+  cache.path = "output/_cache/",
+  fig.process = function(x) {  # Remove "-1" from figure names
+    x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
+    if (file.rename(x, x2)) x2 else x
+  }
+)
+
+# R options
+options(
+  width = 90,  # Output width
+  dplyr.summarise.inform = FALSE,  # Turn off dplyr's summarize() auto messages
+  knitr.kable.NA = "",  # Make NAs blank in kables
+  kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
+  modelsummary_factory_default = table_format,  # Set modelsummary backend
+  modelsummary_format_numeric_latex = "plain"  # Don't use siunitx
+)
+
+# modelsummary regression table notes
+if (is_latex) {
+  model_note <- "Posterior means; 95\\\\% credible intervals in brackets" 
+} else {
+  model_note <- "Posterior means; 95% credible intervals in brackets"
+}
+```
+
+```{r libraries-data, include=FALSE}
+library(tidyverse)
+library(targets)
+library(kableExtra)
+library(modelsummary)
+
+withr::with_dir(here::here(), {
+  source(tar_read(plot_funs))
+
+  # Model tables
+  tar_load(c(models_paper_pts, models_paper_lhr))
+
+  # Load lookup list for coefficients in regression tables
+  tar_load(coef_list)
+})
+```
+
+# Modeling approach
 
@@
 
-### Equation for PTS models
+## PTS models
+
+### Equation
 
@@
 
-### R code for PTS models
+### R code
 
@@
 
-### Equation for latent human rights models
+## Latent human rights models
+
+### Equation
 
@@
 
-### R code for latent human rights models
+### R code
 
@@
 
-## Improved cases
+# Improved cases
 
@@
 
-## Complete model results
+# Complete model results
 

### 2021-11-17 _targets.R

@@ -383,6 +383,41 @@ list(
                output = here_rel("manuscript", "output", "extracted-citations.bib")),
              format = "file"),
 
+  ## Render the appendix ----
+  tar_target_raw("appendix", here_rel("manuscript", "appendix.Rmd"),
+                 format = "file",
+                 deps = c("bib_file",
+                          tar_knitr_deps(here_rel("manuscript", "appendix.Rmd")))),
+  tar_target(app_html,
+             render_html(
+               input = appendix,
+               output = here_rel("manuscript", "output", "appendix.html"),
+               csl = csl,
+               bib_file,
+               support_folder = "output/html-support"),
+             format = "file"),
+  tar_target(app_pdf,
+             render_pdf(
+               input = appendix,
+               output = here_rel("manuscript", "output", "appendix.pdf"),
+               bibstyle = bibstyle,
+               bib_file),
+             format = "file"),
+  tar_target(app_ms_pdf,
+             render_pdf_ms(
+               input = appendix,
+               output = here_rel("manuscript", "output", "appendix-ms.pdf"),
+               bibstyle = bibstyle,
+               bib_file),
+             format = "file"),
+  tar_target(app_docx,
+             render_docx(
+               input = appendix,
+               output = here_rel("manuscript", "output", "appendix.docx"),
+               csl = csl,
+               bib_file),
+             format = "file"),
+
   ## Always show a word count ----
   tar_target(word_count, count_words(html)),
   tar_force(show_word_count, print(word_count), TRUE),

### 2021-11-17 manuscript/manuscript.Rmd
Minor typos

@@
 Law 84 (and its replacement Law 70 of 2017) is thus a useful lever for selectively controlling the allowable space for dissidence and leaving open the possibility of future human rights abuses.
-The law's built-in discretionary authority permits the government to give the appearance of concessions and openness to civil society while simultaneously provides the government the ability to target individual NGOs and reserving the right to engage in broader crackdowns of associational rights.
+The law's built-in discretionary authority permits the government to give the appearance of concessions and openness to civil society while simultaneously providing the government with the ability to target individual NGOs and reserving the right to engage in broader crackdowns of associational rights.
 
 This trend holds across many other countries as well.
-For instance, even though India passed an anti-NGO law (containing multiple bariers to funding and advocacy) in 1976, it has not always been uniformly implemented.
+For instance, even though India passed an anti-NGO law (containing multiple barriers to funding and advocacy) in 1976, it has not always been uniformly implemented.
 Rather, having an anti-NGO law on the books serves the state's long-term strategic interests, enabling it to crack down on NGOs when they start posing electoral or economic threats to the state [@Chaudhry:2022].

### 2021-11-18 manuscript/manuscript.Rmd
Suparna edits

@@
 It can act as an early warning signal for worsening repression, suggesting which countries are testing the waters with comparatively "milder" methods of crackdown before enacting more violent forms of repression.
-To assess if attacks on NGOs and activists can provide us useful information about future repression, we use an original dataset on state crackdown on NGOs using legal repression across all countries from 1990–2013.
+To assess if attacks on NGOs and activists can provide us useful information about future repression, we use an original dataset on state crackdown on NGOs using anti-NGO laws across all countries from 1990–2013.
 We differentiate between two forms of NGO repression: de jure anti-NGO laws, and their de facto implementation.
@@
 
-Using multilevel Bayesian modeling, we find that formal de jure laws potentially provide a weak signal of future repression.
+Using multilevel Bayesian modeling, we find that formal de jure laws provide a weak signal of future repression.
 Increasing de facto civil society repression, on the other hand, predicts both a moderate increase in the probability of moderate political terror and a deterioration in the overall respect for human rights in a typical country.
@@
 
-[^1]: In this article, we use the terms "anti-NGO laws" and "de jure NGO laws" interchangeably.
+[^1]: In this article, we use the terms "anti-NGO laws" and "de jure NGO laws" and "NGO restrictions" interchangeably.
 
@@
 In other words, dissent increases repressive behavior [@Davenport:2007].
-However, dissent and repression have an endogenous relationship: state authorities also frequently engage in preventive repression to undermine or restrict groups' abilities to dissent [@RitterConrad:2016; @ConradRitter:2019].
+However, dissent and repression have an endogenous relationship: state authorities frequently engage in preventive repression to undermine or restrict groups' abilities to dissent [@RitterConrad:2016; @ConradRitter:2019].
 NGOs are one actor that can pose challenges to political authorities, and state repression of these actors—especially through anti-NGO laws—can be considered a form of preventive repression [@Chaudhry:2022].
@@
 While many saw the initial proliferation of NGOs in the 1980s and 1990s as leading to a "symbiotic relationship" between NGOs and states due to their mutual goals, this perception changed over time [@Reimann:2006, 63].
-With expanded powers and their perceived role in the Color Revolutions, NGOs began to be seen as having a real influence on domestic and international politics [@CarothersBrechenmacher:2014].
-State perception of NGOS as threatening became pervasive as these organizations demonstrated their ability to influence electoral politics [@DPR:2016; @Weiss:2009], mobilize aid [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
+With expanded powers and their perceived role in the Color Revolutions, NGOs began to be seen as having a real influence on both domestic and international politics [@CarothersBrechenmacher:2014].
+State perception of NGOs as threatening became pervasive as these organizations demonstrated their ability to influence electoral politics [@DPR:2016; @Weiss:2009], mobilize aid [@MurdieBhasin:2011; @BBCM2014; @Boulding:2014], and threaten a state's economic interests [@DietrichMurdie:2017; @LebovicVoeten:2009; @Nielsen:2013].
 
@@
 Finally, counting official laws can also underestimate levels of NGO repression because governments can repress these organizations without relying on formal laws.
-As prior research in Egypt, Ethiopia, and Russia points out, "rather than systematically enforcing all repressive legal measures-often impossible owing to capacity constraints," governments may choose to use extra-legal means to intimidate, harass or prosecute a few NGOs or activists.
-These can include arrests, trials, imprisonment, and other violent sanctions against NGO activists such as beatings, threats to families, and attacks on property.
+As prior research in Egypt, Ethiopia, and Russia points out, "rather than systematically enforcing all repressive legal measures-often impossible owing to capacity constraints," governments may choose to use extra-legal means to intimidate, harass or prosecute a few NGOs or activists [@Brechenmacher:2017, 94] These can include arrests, trials, imprisonment, and other violent sanctions against NGO activists such as beatings, threats to families, and attacks on property.
 As such, de facto crackdown in the form of not just legal harassment but also material and violent sanctions could lead to increases in both physical integrity and civil liberties violations.
@@
 
-To test these empirical expectations, we use a new dataset of civil society laws, as well as measures from several other larger datasets focused on human rights, political terror, and democratization.
+To test these empirical expectations, we use data on anti-NGO laws, as well as measures from several other larger datasets focused on human rights, political terror, and democratization.
 Table \@ref(tab:var-summary) provides a summary of our key variables.
@@
 Figure \@ref(fig:barriers) shows each of these types of legal barriers per country over time, as well as average levels of de facto civil society repression by regime type.
-While anti-NGO laws have increased steadily since 1990—particularly laws related to foreign funding—there has not necessarily been a corresponding rise in de facto civil society repression, which has remained fairly constant across different regime types.
+While anti-NGO laws have increased steadily since 1990, there has not necessarily been a corresponding rise in de facto civil society repression, which has remained fairly constant across different regime types.
 This divergence is likely indicative of the split between de jure laws and their de facto implementation—new legislation is not necessarily implemented immediately and does not always lead to broader NGO repression.
@@
 We present the results of our models in two stages.
-First, to see how minor shifts in anti-NGOs laws and de facto repression influence future human rights, we examine the marginal effects of our main explanatory variables when all other model covariates are held constant.
+First, to see how minor shifts in anti-NGO laws and de facto repression influence future human rights, we examine the marginal effects of our main explanatory variables when all other model covariates are held constant.
 These effects are by no means causal—rather, they demonstrate how much variation in predicted human rights is possible as the legal environment for civil society improves or deteriorates within a typical country.
@@
 
-The weaker predictive power of formal NGO laws is likely attributable to fact that de jure NGO legislation may take time to implement—many states need to first establish institutions that oversee the operation and funding of these groups or incorporate threatening NGOs into the regime apparatus [@Naim:2007].
+The weaker predictive power of formal NGO laws is likely attributable to the fact that de jure NGO legislation may take time to implement—many states need to first establish institutions that oversee the operation and funding of these groups or incorporate threatening NGOs into the regime apparatus [@Naim:2007].
 Further, states that engage in political repression can do so with or without legal justification.
 De facto civil society repression, on the other hand, represents the actual implementation of anti-NGO strategies—both legal and extralegal—and might be more indicative of future human rights abuses.
-The results from our second set of models, using V-Dem;s civil society repression index as the key predictor, confirm this.
+The results from our second set of models, using V-Dem's civil society repression index as the key predictor, confirm this.
 
@@
 As we explore in the next section, de jure civil society laws are a long-term strategy to prevent threats to the regime from coalescing in the first place.
-As such, the long-term effects of these laws in terms of their predictive power may require a much longer time period under study.
-In contrast, de facto crackdown on NGOs may signal the need to react sooner due to the immediacy of the threat.
+As such, the effects of these laws in terms of their predictive power may require a much longer time period under study.
+In contrast, de facto crackdown on NGOs may signal that a state needs to react sooner due to the immediacy of the threat.
 
@@
 
-When looking both at marginal effects and improvements in predictive power, we find that the de facto implementation of anti-civil society measures are a stronger indicator of future repression than de jure anti-NGO laws.
+When looking at both marginal effects and improvements in predictive power, we find that the de facto implementation of anti-civil society measures are a stronger indicator of future repression than de jure anti-NGO laws.
 One reason for this disconnect between law and implementation is that laws targeted at NGOs are often not designed to be used immediately, but instead serve to protect regimes against potential threats in the future.
@@
 The tension culminated on December 16, when troops filled Tahrir Square to put down an anti-SCAF demonstration, killing 10 and wounding more than 400.
-Two weeks later, Egyptian security forces raided the offices of 17 local and international NGOs (Fadel and Warrick 2011)—including Freedom House, the National Democratic Institute, and the International Republican Institute—and arrested dozens of domestic and international NGO staff.
+Two weeks later, Egyptian security forces raided the offices of 17 local and international NGOs—including Freedom House, the National Democratic Institute, and the International Republican Institute—and arrested dozens of domestic and international NGO staff [@FadelWarrick:2011].
 The stated legal pretext for this raid was that the organizations were not officially registered and thus in violation of Law 84.
@@
 Law 84 (and its replacement Law 70 of 2017) is thus a useful lever for selectively controlling the allowable space for dissidence and leaving open the possibility of future human rights abuses.
-The law's built-in discretionary authority permits the government to give the appearance of concessions and openness to civil society while simultaneously providing the government with the ability to target individual NGOs and reserving the right to engage in broader crackdowns of associational rights.
+The law's built-in discretionary authority permits the government to give the appearance of concessions and openness to civil society while simultaneously providing the government with the ability to target individual NGOs and the right to engage in broader crackdowns of associational rights.
 
@@
 Foreign funding laws have led to a 32% decline in bilateral aid flows [@DupuyPrakash:2018].
-NGOs that are underfunded, understaffed tend to shut down when faced with increasing restrictions [@Heiss:2019].
-In sum, while de jure laws do not effect levels of physical integrity and civil liberties violations in particular, research has found that they other adverse consequences.
+NGOs that are underfunded and understaffed tend to shut down when faced with increasing restrictions [@Heiss:2019].
+In sum, while de jure laws do not effect levels of physical integrity and civil liberties violations in particular, research has found that they do have other adverse consequences.
 Moreover, since the actual implementation of these laws through de facto civl society repression can have negative effects on broader patterns of human rights abuses, the passage of these laws may still be a concerning first step that paves the path for future implementation.

### 2021-11-19 R/models_lhr.R
Use cmdstanr threading

@@ -8,6 +8,7 @@ lhr_setup <- function() {
   ITER <- 2000
   WARMUP <- 1000
   BAYES_SEED <- 4045  # From random.org
+  threads <- getOption("mc.threads")
 
   # Priors
   priors_vague <- c(set_prior("normal(0, 10)", class = "Intercept"),
@@ -15,7 +16,7 @@ lhr_setup <- function() {
                     set_prior("cauchy(0, 1)", class = "sd"))
 
   return(list(chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
-              priors_vague = priors_vague))
+              threads = threads, priors_vague = priors_vague))
 }
 
 
@@ -38,6 +39,7 @@ f_lhr_baseline <- function(dat) {
     prior = lhr_settings$priors_vague,
     control = list(adapt_delta = 0.9),
     data = dat,
+    threads = threading(lhr_settings$threads),
     chains = lhr_settings$chains, iter = lhr_settings$iter,
     warmup = lhr_settings$warmup, seed = lhr_settings$seed)
 
@@ -62,6 +64,7 @@ f_lhr_total <- function(dat) {
     prior = lhr_settings$priors_vague,
     control = list(adapt_delta = 0.9),
     data = dat,
+    threads = threading(lhr_settings$threads),
     chains = lhr_settings$chains, iter = lhr_settings$iter,
     warmup = lhr_settings$warmup, seed = lhr_settings$seed)
 
@@ -86,6 +89,7 @@ f_lhr_total_new <- function(dat) {
     prior = lhr_settings$priors_vague,
     control = list(adapt_delta = 0.9),
     data = dat,
+    threads = threading(lhr_settings$threads),
     chains = lhr_settings$chains, iter = lhr_settings$iter,
     warmup = lhr_settings$warmup, seed = lhr_settings$seed)
 
@@ -110,6 +114,7 @@ f_lhr_advocacy <- function(dat) {
     prior = lhr_settings$priors_vague,
     control = list(adapt_delta = 0.9),
     data = dat,
+    threads = threading(lhr_settings$threads),
     chains = lhr_settings$chains, iter = lhr_settings$iter,
     warmup = lhr_settings$warmup, seed = lhr_settings$seed)
 
@@ -134,6 +139,7 @@ f_lhr_entry <- function(dat) {
     prior = lhr_settings$priors_vague,
     control = list(adapt_delta = 0.9),
     data = dat,
[…]

### 2021-11-19 R/models_pts.R

@@ -10,14 +10,15 @@ pts_setup <- function() {
   ITER <- 2000
   WARMUP <- 1000
   BAYES_SEED <- 2009  # From random.org
+  threads <- getOption("mc.threads")
 
   # Priors
-  priors_vague <- c(set_prior("normal(0, 10)", class = "Intercept"),
+  priors_vague <- c(set_prior("normal(0, 3)", class = "Intercept"),
                     set_prior("normal(0, 3)", class = "b"),
                     set_prior("cauchy(0, 1)", class = "sd"))
 
   return(list(chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
-              priors_vague = priors_vague))
+              threads = threads, priors_vague = priors_vague))
 }
 
 
@@ -39,6 +40,7 @@ f_pts_baseline <- function(dat) {
     family = cumulative(),
     prior = pts_settings$priors_vague,
     data = dat,
+    threads = threading(pts_settings$threads),
     chains = pts_settings$chains, iter = pts_settings$iter,
     warmup = pts_settings$warmup, seed = pts_settings$seed)
 
@@ -62,6 +64,7 @@ f_pts_total <- function(dat) {
     family = cumulative(),
     prior = pts_settings$priors_vague,
     data = dat,
+    threads = threading(pts_settings$threads),
     chains = pts_settings$chains, iter = pts_settings$iter,
     warmup = pts_settings$warmup, seed = pts_settings$seed)
 
@@ -85,6 +88,7 @@ f_pts_total_new <- function(dat) {
     family = cumulative(),
     prior = pts_settings$priors_vague,
     data = dat,
+    threads = threading(pts_settings$threads),
     chains = pts_settings$chains, iter = pts_settings$iter,
     warmup = pts_settings$warmup, seed = pts_settings$seed)
 
@@ -108,6 +112,7 @@ f_pts_advocacy <- function(dat) {
     family = cumulative(),
     prior = pts_settings$priors_vague,
     data = dat,
+    threads = threading(pts_settings$threads),
     chains = pts_settings$chains, iter = pts_settings$iter,
     warmup = pts_settings$warmup, seed = pts_settings$seed)
 
@@ -131,6 +136,7 @@ f_pts_entry <- function(dat) {
     family = cumulative(),
     prior = pts_settings$priors_vague,
     data = dat,
+    threads = threading(pts_settings$threads),
[…]

### 2021-11-19 _targets.R

@@ -10,7 +10,16 @@ bibstyle <- "bibstyle-apa"
 suppressPackageStartupMessages(library(brms))
 
 # Bayes-specific stuff
+# Specify the number of cores and threads
+#
+# If using brms's default rstan backend, set mc.threads to NULL
+#
+#   - If using cmdstanr, you can use within-chain threading
+#   - (https://cran.r-project.org/web/packages/brms/vignettes/brms_threading.html)
+#   - On a four-core computer, use mc.cores = 2 and threads = threading(2)
+#   - On an eight+-core computer, use mc.cores = 4 and threads = threading(2)
 options(mc.cores = 4,
+        mc.threads = 2,
         brms.backend = "cmdstanr")
 
 options(tidyverse.quiet = TRUE,
@@ -36,7 +45,7 @@ options(contrasts = rep("contr.treatment", 2))
 # vs. my 16-core work laptop).
 
 # Pass these options to workers using options(worker_options)
-worker_options <- options()[c("mc.cores", "brms.backend",
+worker_options <- options()[c("mc.cores", "mc.threads", "brms.backend",
                               "contrasts", "tidyverse.quiet",
                               "dplyr.summarise.inform")]
 

### 2021-11-19 analysis/01_data-overview.Rmd
Remove REWB stuff
Remove all civlib and clphy models

@@
   tar_load(latent_hr_clean)
-  tar_load(killings_all)
   tar_load(vdem_clean)
@@
 glimpse(latent_hr_clean)
-```
-
-## Gohdes and Carey journalist deaths
-
-We use data from [Gohdes and Carey (2017)](https://doi.org/10.1177/0022343316680859) for the number of journalists murdered between 2002 and 2014.
-They provide two `.Rdata` files in their replication materials—one is a list of all journalist deaths, and one is a TSCS dataset they use in their main analysis, with summary values of journalist deaths for each country/year.
-Their panel data does not include 2002 for some reason, so we ignore the panel data and recreate the summary values by hand here.
-
-```{r glimpse-gh-journalists}
-glimpse(killings_all)
 ```
@@
 
-There are only a tiny handful of rows with missing data: Serbia pre-2006.
+There are only a tiny handful of rows with missing NGO law data: Serbia pre-2006 and Russia pre-1992
 
@@
 
-There are just two instances of missing data with PTS scores:
+There are a handful of instances of missing data with PTS scores:
 

### 2021-11-19 analysis/02_descriptive-analysis.Rmd
Remove all civlib and clphy models

@@
   ),
-  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
-  file = here("analysis", "cache", "diff_cs_pts")
+  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED
 )
@@
   modelr::data_grid(PTS_factor) %>% 
-  add_predicted_draws(diff_cs_pts, seed = BAYES_SEED)
+  add_epred_draws(diff_cs_pts, seed = BAYES_SEED)
 ```
@@
   scale_x_reverse() +
-  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
+  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = "none") +
   labs(x = "Civil society repression", y = "Political Terror Scale (PTS)") +
@@
 ```{r plot-posterior-preds-pts-cs, warning=FALSE, message=FALSE}
-ggplot(diff_cs_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
+ggplot(diff_cs_pts_posterior, aes(x = .epred, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
   stat_dots(quantiles = 100, shape = 19) +
@@
   scale_x_reverse() +
-  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
+  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = "none") +
   labs(x = "Civil society repression", y = "Political Terror Scale (PTS)",
@@
 ```
-
-## Chaudhry NGO regulations and the PTS
-
-```{r model-pts-restrictions, message=FALSE, warning=FALSE, results="hide"}
-diff_ngo_pts <- brm(
-  bf(barriers_total ~ 0 + PTS_factor, sigma ~ 0 + PTS_factor),
-  family = student,
-  data = select(canary, barriers_total, PTS_factor),
-  prior = c(
-    # Set group mean prior
-    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
-    # Set group variance priors. We keep the less informative cauchy(0, 1).
-    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
-    set_prior("exponential(1.0/29)", class = "nu")
-  ),
-  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
-  file = here("analysis", "cache", "diff_ngo_pts")
-)
-```
-
-```{r draws-pts-ngo}
-diff_ngo_pts_summary <- diff_ngo_pts %>%
-  gather_draws(`b_PTS.*`, regex = TRUE) %>% 
-  median_hdci(.width = 0.95) %>% 
-  to_broom_names()
-
-diff_ngo_pts_draws <- diff_ngo_pts %>% 
-  gather_draws(`b_PTS.*`, regex = TRUE) %>% 
-  ungroup() %>% 
-  mutate(.variable = str_replace(.variable, "b_PTS_factorLevel", "Level ")) %>% 
-  mutate(pts_level = fct_rev(.variable))
-
-diff_ngo_pts_posterior <- canary %>% 
-  filter(year == 2010) %>% 
-  modelr::data_grid(PTS_factor) %>% 
-  add_predicted_draws(diff_ngo_pts, seed = BAYES_SEED)
-```
-
-```{r plot-draws-pts-ngo}
-ggplot(diff_ngo_pts_draws, aes(y = pts_level, x = .value, fill = pts_level)) + 
-  stat_halfeye() +
-  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
-  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)") +
-  theme_ngo()
-```
-
-```{r plot-posterior-preds-pts-ngo, warning=FALSE, message=FALSE}
-ggplot(diff_ngo_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
-  stat_dots(quantiles = 100, shape = 19) +
-  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
-                         interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
-  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
-  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)",
-       caption = "Each • represents an equally likely outcome from the posterior distribution") +
-  theme_ngo()
-```
-
-# Conflict and civil society restrictions
-
-```{r model-conflict-cs, message=FALSE, results="hide"}
-diff_cs_conflict <- brm(
-  bf(v2csreprss ~ 0 + armed_conflict, sigma ~ 0 + armed_conflict),
-  family = student,
-  data = select(canary, v2csreprss, armed_conflict),
-  prior = c(
-    # Set group mean prior
-    set_prior("normal(0, 1)", class = "b", lb = -4, ub = 4),
-    # Set group variance priors. We keep the less informative cauchy(0, 1).
-    set_prior("cauchy(0, 1)", class = "b", dpar = "sigma"),
-    set_prior("exponential(1.0/29)", class = "nu")
-  ),
-  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
-  file = here("analysis", "cache", "diff_cs_conflict")
-)
-```
-
-```{r draws-conflict-cs}
-diff_cs_conflict_summary <- diff_cs_conflict %>%
-  gather_draws(`b_armed.*`, regex = TRUE) %>% 
-  median_hdci(.width = 0.95) %>% 
-  to_broom_names()
-
-diff_cs_conflict_draws <- diff_cs_conflict %>% 
-  gather_draws(`b_armed.*`, regex = TRUE) %>% 
-  ungroup() %>% 
-  mutate(.variable = recode(.variable, `b_armed_conflictFALSE` = "No armed conflict",
-                            `b_armed_conflictTRUE` = "Armed conflict"))
-
-diff_cs_conflict_posterior <- canary %>% 
-  filter(year == 2010) %>% 
-  modelr::data_grid(armed_conflict) %>% 
-  add_predicted_draws(diff_cs_conflict, seed = BAYES_SEED) %>% 
-  ungroup() %>% 
-  mutate(armed_conflict = factor(armed_conflict, labels = c("No armed conflict", "Armed conflict")))
-```
-
-```{r plot-draws-conflict-cs}
-ggplot(diff_cs_conflict_draws, aes(y = .variable, x = .value, fill = .variable)) + 
-  stat_halfeye() +
-  scale_x_reverse() +
-  scale_fill_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
-  labs(x = "Civil society repression", y = "Armed conflict") +
-  theme_ngo()
-```
-
-```{r plot-posterior-preds-conflict-cs, warning=FALSE, message=FALSE}
-ggplot(diff_cs_conflict_posterior, aes(x = .prediction, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
-  stat_dots(quantiles = 100, shape = 19) +
-  stat_pointinterval(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
-                         interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
-  scale_x_reverse() +
-  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
-  labs(x = "Civil society repression", y = "Armed conflict",
-       caption = "Each • represents an equally likely outcome from the posterior distribution") +
-  theme_ngo()
-```

### 2021-11-19 analysis/03_environment-repression.Rmd
Remove all civlib and clphy models

@@
 library(targets)
-library(broom)
-library(broom.mixed)
 library(tidybayes)
@@
   tar_load(c(m_pts_baseline, m_pts_v2csreprss, 
-             m_clphy_baseline, m_clphy_v2csreprss, 
-             m_clpriv_baseline, m_clpriv_v2csreprss, 
              m_lhr_baseline, m_lhr_v2csreprss))
@@
   # Load regression tables
-  tar_load(c(models_tbl_e2a, models_tbl_e2b, models_tbl_e2c, models_tbl_e2d))
+  tar_load(c(models_tbl_e2a, models_tbl_e2b))
 
@@
   geom_vline(xintercept = 0) +
-  guides(fill = FALSE, alpha = FALSE) +
+  guides(fill = "none", alpha = "none") +
   scale_alpha_manual(values = c(1, 0.4)) +
@@
 
-# E~2b~: Civil society environment and physical violence
-
-## Results table
+# E~2b~: Civil society environment and latent physical integrity rights
 
@@
 models_for_table_e2b <- models %>% 
-  filter(outcome_var == "Physical violence") %>% 
+  filter(outcome_var == "Latent human rights") %>% 
   mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
@@
 coef_plots <- models %>% 
-  filter(model == "m_clphy_v2csreprss") %>% 
-  mutate(coef_draws = map(
-    actual_model, 
-    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
-  select(-actual_model) %>% 
-  unnest(coef_draws) %>% 
-  left_join(coefs_clean, by = c(".variable" = "coef"))
-
-coef_plots %>% 
-  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
-  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
-  geom_vline(xintercept = 0) +
-  guides(fill = FALSE, alpha = FALSE) +
-  scale_alpha_manual(values = c(1, 0.4)) +
-  labs(x = "Coefficient", y = NULL) +
-  theme_ngo()
-```
-
-## Marginal effects
-
-```{r plot-mfx-e2b}
-mfx <- models %>% 
-  filter(model == "m_clphy_v2csreprss") %>% 
-  mutate(plot_vars = "v2csreprss") %>% 
-  mutate(fx = map2(actual_model, plot_vars, 
-                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
-  select(-actual_model) %>% 
-  unnest(fx)
-
-mfx %>% 
-  ggplot(aes(x = effect1__, y = estimate__)) +
-  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
-              fill = "#FF4136", color = NA) +
-  geom_line(size = 1, color = "#FF4136") +
-  labs(x = "Civil society repression\n(higher values = less repression)",
-       y = "Predicted physical violence index\n(higher values = less violence)") +
-  theme_ngo()
-```
-
-\
-
-# E~2c~: Civil society environment and civil liberties
-
-```{r tbl-e2c}
-# Build nicer column names
-models_for_table_e2c <- models %>% 
-  filter(outcome_var == "Private civil liberties") %>% 
-  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
-
-# Make a named vector of original model names and nice names
-model_names_tbl_e2c <- models_for_table_e2c %>% 
-  pull(model_name) %>% 
-  set_names(models_for_table_e2c$model)
-
-# Rename the columns
-names(models_tbl_e2c) <- recode(names(models_tbl_e2c), !!!model_names_tbl_e2c)
-
-modelsummary(models_tbl_e2c,
-             statistic = "[{conf.low}, {conf.high}]",
-             coef_map = coef_list,
-             gof_omit = "ELPD",
-             escape = FALSE,
-             notes = list("Posterior means; 95% credible intervals in brackets"))
-```
-
-## Coefficients
-
-```{r plot-coefs-e2c}
-coef_plots <- models %>% 
-  filter(model == "m_clpriv_v2csreprss") %>% 
-  mutate(coef_draws = map(
-    actual_model, 
-    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
-  select(-actual_model) %>% 
-  unnest(coef_draws) %>% 
-  left_join(coefs_clean, by = c(".variable" = "coef"))
-
-coef_plots %>% 
-  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
-  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
-  geom_vline(xintercept = 0) +
-  guides(fill = FALSE, alpha = FALSE) +
-  scale_alpha_manual(values = c(1, 0.4)) +
-  labs(x = "Coefficient", y = NULL) +
-  theme_ngo()
-```
-
-## Marginal effects
-
-```{r plot-mfx-e2c}
-mfx <- models %>% 
-  filter(model == "m_clpriv_v2csreprss") %>% 
-  mutate(plot_vars = "v2csreprss") %>% 
-  mutate(fx = map2(actual_model, plot_vars, 
-                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
-  select(-actual_model) %>% 
-  unnest(fx)
-
-mfx %>% 
-  ggplot(aes(x = effect1__, y = estimate__)) +
-  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
-              fill = "#FF4136", color = NA) +
-  geom_line(size = 1, color = "#FF4136") +
-  labs(x = "Civil society repression\n(higher values = less repression)",
-       y = "Predicted civil liberties index\n(higher values = less violence)") +
-  theme_ngo()
-```
-
-\
-
-# E~2d~: Civil society environment and latent physical integrity rights
-
-```{r tbl-e2d}
-# Build nicer column names
-models_for_table_e2d <- models %>% 
-  filter(outcome_var == "Latent human rights") %>% 
-  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
-
-# Make a named vector of original model names and nice names
-model_names_tbl_e2d <- models_for_table_e2d %>% 
-  pull(model_name) %>% 
-  set_names(models_for_table_e2d$model)
-
-# Rename the columns
-names(models_tbl_e2d) <- recode(names(models_tbl_e2d), !!!model_names_tbl_e2d)
-
-modelsummary(models_tbl_e2d,
-             statistic = "[{conf.low}, {conf.high}]",
-             coef_map = coef_list,
-             gof_omit = "ELPD",
-             escape = FALSE,
-             notes = list("Posterior means; 95% credible intervals in brackets"))
-```
-
-## Coefficients
-
-```{r plot-coefs-e2d}
-coef_plots <- models %>% 
   filter(model == "m_lhr_v2csreprss") %>% 
@@
 
-```{r plot-mfx-e2d}
+```{r plot-mfx-e2b}
 mfx <- models %>% 

### 2021-11-19 analysis/03_laws-repression.Rmd
Remove all civlib and clphy models

@@
 library(modelsummary)
-library(lubridate)
 library(here)
@@
              m_pts_advocacy, m_pts_entry, m_pts_funding,
-             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
-             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
-             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new,
-             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
              m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
@@
   # Load regression tables
-  tar_load(c(models_tbl_e1a_re, models_tbl_e1b_re, 
-             models_tbl_e1c_re, models_tbl_e1d_re))
+  tar_load(c(models_tbl_e1a, models_tbl_e1b))
 
@@
 # Build nicer column names
-models_for_table_e1a_re <- models %>% 
+models_for_table_e1a <- models %>% 
   filter(outcome_var == "Political terror") %>% 
@@
 # Make a named vector of original model names and nice names
-models_names_table_e1a_re <- models_for_table_e1a_re %>% 
+models_names_table_e1a <- models_for_table_e1a %>% 
   pull(model_name) %>% 
-  set_names(models_for_table_e1a_re$model)
+  set_names(models_for_table_e1a$model)
 
 # Rename the columns
-names(models_tbl_e1a_re) <- recode(names(models_tbl_e1a_re), 
-                                   !!!models_names_table_e1a_re)
+names(models_tbl_e1a) <- recode(names(models_tbl_e1a), 
+                                !!!models_names_table_e1a)
 
-modelsummary(models_tbl_e1a_re,
+modelsummary(models_tbl_e1a,
              statistic = "[{conf.low}, {conf.high}]",
@@
 
-# E~1b~: NGO laws and physical violence
+# E~1b~: NGO laws and latent human rights
 
@@
 
-```{r tbl-e1b-re}
-models_for_table_e1b_re <- models %>% 
-  filter(outcome_var == "Physical violence") %>% 
+```{r tbl-e1b}
+models_for_table_e1b <- models %>% 
+  filter(outcome_var == "Latent human rights") %>% 
   mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
 
-model_names_tbl_e1b_re <- models_for_table_e1b_re %>% 
+model_names_tbl_e1b <- models_for_table_e1b %>% 
   pull(model_name) %>% 
-  set_names(models_for_table_e1b_re$model)
+  set_names(models_for_table_e1b$model)
 
-names(models_tbl_e1b_re) <- recode(names(models_tbl_e1b_re), 
-                                   !!!model_names_tbl_e1b_re)
+names(models_tbl_e1b) <- recode(names(models_tbl_e1b), 
+                                !!!model_names_tbl_e1b)
 
-modelsummary(models_tbl_e1b_re,
+modelsummary(models_tbl_e1b,
              statistic = "[{conf.low}, {conf.high}]",
@@
 ```{r plot-coefs-e1b}
-coef_plots <- models %>% 
-  filter(str_detect(model, "clphy"), !str_detect(model, "baseline")) %>% 
-  mutate(coef_draws = map(
-    actual_model, 
-    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
-  select(-actual_model) %>% 
-  unnest(coef_draws) %>% 
-  left_join(coefs_clean, by = c(".variable" = "coef"))
-
-coef_plots %>% 
-  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
-  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
-  geom_vline(xintercept = 0) +
-  guides(fill = FALSE, alpha = FALSE) +
-  scale_alpha_manual(values = c(1, 0.4)) +
-  labs(x = "Coefficient", y = NULL) +
-  theme_ngo()
-```
-
-## Marginal effects
-
-```{r plot-mfx-e1b}
-plot_clphy_vars_lookup <- tribble(
-  ~model, ~plot_var, ~plot_var_nice,
-  "m_clphy_total", "barriers_total", "Total legal barriers",
-  "m_clphy_total_new", "barriers_total_new", "New legal barriers",
-  "m_clphy_advocacy", "advocacy", "Advocacy",
-  "m_clphy_entry", "entry", "Entry",
-  "m_clphy_funding", "funding", "Funding"
-) %>% 
-  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
-
-mfx <- models %>% 
-  filter(str_detect(model, "clphy"), !str_detect(model, "new|baseline")) %>% 
-  left_join(plot_clphy_vars_lookup, by = "model") %>% 
-  mutate(fx = map2(actual_model, plot_var, 
-                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
-  select(-actual_model) %>% 
-  unnest(fx)
-
-mfx %>% 
-  mutate(x_rounded = floor(effect1__)) %>% 
-  group_by(x_rounded, plot_var_nice) %>% 
-  slice(1) %>% 
-  ungroup() %>% 
-  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
-  geom_line(size = 0.5, color = "grey90") +
-  geom_pointrange(aes(ymin = lower__, ymax = upper__),
-                  fatten = 1) +
-  scale_x_continuous(breaks = 0:9) +
-  scale_color_viridis_d(option = "plasma", end = 0.8) +
-  guides(color = FALSE) +
-  labs(x = "Count of legal barriers",
-       y = "Predicted physical violence index\n(higher values = less violence)") +
-  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
-  theme_ngo() +
-  theme(panel.grid.major.x = element_blank())
-```
-
-\
-
-# E~1c~: NGO laws and civil liberties
-
-## Results table
-
-```{r tbl-e1c-re}
-models_for_table_e1c_re <- models %>% 
-  filter(outcome_var == "Private civil liberties") %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
-
-model_names_tbl_e1c_re <- models_for_table_e1c_re %>% 
-  pull(model_name) %>% 
-  set_names(models_for_table_e1c_re$model)
-
-names(models_tbl_e1c_re) <- recode(names(models_tbl_e1c_re), 
-                                   !!!model_names_tbl_e1c_re)
-
-modelsummary(models_tbl_e1c_re,
-             statistic = "[{conf.low}, {conf.high}]",
-             coef_map = coef_list,
-             gof_omit = "ELPD",
-             escape = FALSE,
-             notes = list("Posterior means; 95% credible intervals in brackets"))
-```
-
-## Coefficients
-
-```{r plot-coefs-e1c}
-coef_plots <- models %>% 
-  filter(str_detect(model, "clpriv"), !str_detect(model, "baseline")) %>% 
-  mutate(coef_draws = map(
-    actual_model, 
-    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
-  select(-actual_model) %>% 
-  unnest(coef_draws) %>% 
-  left_join(coefs_clean, by = c(".variable" = "coef"))
-
-coef_plots %>% 
-  ggplot(aes(y = fct_rev(coef_clean), x = .value)) +
-  stat_halfeye(aes(alpha = lagging), .width = c(0.8, 0.95)) +
-  geom_vline(xintercept = 0) +
-  guides(fill = FALSE, alpha = FALSE) +
-  scale_alpha_manual(values = c(1, 0.4)) +
-  labs(x = "Coefficient", y = NULL) +
-  theme_ngo()
-```
-
-## Marginal effects
-
-```{r plot-mfx-e1c}
-plot_clpriv_vars_lookup <- tribble(
-  ~model, ~plot_var, ~plot_var_nice,
-  "m_clpriv_total", "barriers_total", "Total legal barriers",
-  "m_clpriv_total_new", "barriers_total_new", "New legal barriers",
-  "m_clpriv_advocacy", "advocacy", "Advocacy",
-  "m_clpriv_entry", "entry", "Entry",
-  "m_clpriv_funding", "funding", "Funding"
-) %>% 
-  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))
-
-mfx <- models %>% 
-  filter(str_detect(model, "clpriv"), !str_detect(model, "new|baseline")) %>% 
-  left_join(plot_clpriv_vars_lookup, by = "model") %>% 
-  mutate(fx = map2(actual_model, plot_var, 
-                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
-  select(-actual_model) %>% 
-  unnest(fx)
-
-mfx %>% 
-  mutate(x_rounded = floor(effect1__)) %>% 
-  group_by(x_rounded, plot_var_nice) %>% 
-  slice(1) %>% 
-  ungroup() %>% 
-  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
-  geom_line(size = 0.5, color = "grey90") +
-  geom_pointrange(aes(ymin = lower__, ymax = upper__),
-                  fatten = 1) +
-  scale_x_continuous(breaks = 0:9) +
-  scale_color_viridis_d(option = "plasma", end = 0.8) +
-  guides(color = FALSE) +
-  labs(x = "Count of legal barriers",
-       y = "Predicted civil liberties index\n(higher values = better protection)") +
-  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
-  theme_ngo() +
-  theme(panel.grid.major.x = element_blank())
-```
-
-\
-
-# E~1d~: NGO laws and latent physical integrity rights
-
-## Results table
-
-```{r tbl-e1d-re}
-models_for_table_e1d_re <- models %>% 
-  filter(outcome_var == "Latent human rights") %>% 
-  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var})"))
-
-model_names_tbl_e1d_re <- models_for_table_e1d_re %>% 
-  pull(model_name) %>% 
-  set_names(models_for_table_e1d_re$model)
-
-names(models_tbl_e1d_re) <- recode(names(models_tbl_e1d_re), 
-                                   !!!model_names_tbl_e1d_re)
-
-modelsummary(models_tbl_e1d_re,
-             statistic = "[{conf.low}, {conf.high}]",
-             coef_map = coef_list,
-             gof_omit = "ELPD",
-             escape = FALSE,
-             notes = list("Posterior means; 95% credible intervals in brackets"))
-```
-
-## Coefficients
-
-```{r plot-coefs-e1d}
 coef_plots <- models %>% 
@@
 
-```{r plot-mfx-e1d}
+```{r plot-mfx-e1b}
 plot_lhr_vars_lookup <- tribble(
@@
   scale_color_viridis_d(option = "plasma", end = 0.8) +
-  guides(color = FALSE) +
+  guides(color = "none") +
   labs(x = "Count of legal barriers",

### 2021-11-19 analysis/03_model-details.Rmd
Remove all civlib and clphy models

@@
   # This also works but again doesn't register correctly as dependencies
-  # tar_load(starts_with("m_clpriv"))
+  # tar_load(starts_with("m_pts"))
 
@@
              m_pts_v2csreprss, 
-             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
-             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
-             m_clphy_v2csreprss, 
-             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new, 
-             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
-             m_clpriv_v2csreprss, 
              m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
@@
              m_pts_v2csreprss_train,
-             m_clphy_baseline_train, m_clphy_total_train, 
-             m_clphy_advocacy_train, m_clphy_entry_train, m_clphy_funding_train, 
-             m_clphy_v2csreprss_train, 
-             m_clpriv_baseline_train, m_clpriv_total_train, 
-             m_clpriv_advocacy_train, m_clpriv_entry_train, m_clpriv_funding_train, 
-             m_clpriv_v2csreprss_train))
+             m_lhr_baseline_train, m_lhr_total_train, m_lhr_total_new_train, 
+             m_lhr_advocacy_train, m_lhr_entry_train, m_lhr_funding_train, 
+             m_lhr_v2csreprss_train))
 })
@@
 ```{r set-computer-details}
-computer <- "Work"
+computer <- "Personal"
 
@@
 } else {
-  computer_details <- "2016 MacBook Pro with 4 cores and 16 GB of RAM, using Stan through brms through cmdstanr"
+  computer_details <- "2021 MacBook Pro M1 Max with 10 cores and 32 GB of RAM, using Stan through brms through cmdstanr"
 }
@@
 
-## Models for E~1~ (civil society laws)
+## Models for E~1~ (de jure civil society laws)
 
@@
 
-## Models for E~2~ (civil society environment)
+## Models for E~2~ (de facto civil society environment)
 
@@
 - `R/models_pts.R` (for PTS-based models)
-- `R/models_clphy.R` (for V-Dem physical violence-based models)
-- `R/models_clpriv.R` (for V-Dem private civil liberties-based models)
 - `R/models_lhr.R` (for latent human rights-based models)
@@
 
-#### `R/models_clphy.R`
-
-```{r, code=xfun::read_utf8(here::here("R", "models_clphy.R")), eval=FALSE, class.source="fold-hide"}
-```
-
-#### `R/models_clpriv.R`
-
-```{r, code=xfun::read_utf8(here::here("R", "models_clpriv.R")), eval=FALSE, class.source="fold-hide"}
-```
-
 #### `R/models_lhr.R`

### 2021-11-19 analysis/03_modeling-choices.Rmd
Remove all civlib and clphy models

@@
 library(targets)
-library(broom)
-library(janitor)
-library(brms)
 library(lme4)
 library(lmtest)  # For log ratio tests
-library(performance)  # For ICCs
+library(performance)
+library(modelsummary)
 library(scales)
-library(modelsummary)
+library(janitor)
 library(here)
-
-CHAINS <- 4
-ITER <- 2000
-WARMUP <- 1000
-BAYES_SEED <- 1234
-
-options(mc.cores = parallel::detectCores(),
-        brms.backend = "cmdstanr")
 
@@
 })
+
+# Goodness-of-fit measures to include
+gm <- tribble(
+  ~raw, ~clean, ~fmt,
+  "nobs", "Num.Obs.", 3,
+  "icc", "ICC", 3
+)
 ```
-
-# Interpretation reminders
-
-I always forget how to interpret these dang within/between coefficients in REWB models, so here's a reminder:
-
-- "Within" coefficients show what happens as you move up and down from the average level.
-  - Template = increasing 1 unit of `x` above the average in a typical country is associated with a β change in `y`
-- "Between" coefficients show what happens as you move the whole average up.
-They're trickier (and less important) to interpret.
-[This post](https://statisticalhorizons.com/between-within-contextual-effects) explains more, along with [Bell, Fairbrother, and Jones (2018)](https://doi.org/10.1007/s11135-018-0802-x).
 
@@
                REML = FALSE, data = canary)
-m0_clphy <- lmer(v2x_clphy_lead1 ~ (1 | year) + (1 | gwcode),
-               REML = FALSE, data = canary)
-m0_clpriv <- lmer(v2x_clpriv_lead1 ~ (1 | year) + (1 | gwcode),
+m0_lhr <- lmer(latent_hr_mean_lead1 ~ (1 | year) + (1 | gwcode),
                REML = FALSE, data = canary)
@@
 ```{r icc-models}
-# This shows just the ICC. modelsummary() helpfully includes it.
-# icc(m0_pts)
-
-modelsummary(list(m0_pts, m0_clphy, m0_clpriv),
+modelsummary(list(m0_pts, m0_lhr),
              estimate = "{estimate}", statistic = NULL,
-             gof_map = list(list("raw" = "icc", "clean" = "ICC", "fmt" = 4)))
+             group = group + term ~ model,
+             gof_map = gm)
 ```
@@
 These values represent the variation in the outcome variable that can be explained by the country/year structure, which is a *ton*!
-For the PTS model, for instance, the ICC is `r round(icc(m0_pts)$ICC_adjusted, 4)`, meaning that the random effects structure explains `r percent(icc(m0_pts)$ICC_adjusted)` of the variation in PTS.
+For the PTS model, for instance, the ICC is `r round(performance::icc(m0_pts)$ICC_adjusted, 4)`, meaning that the random effects structure explains `r percent(performance::icc(m0_pts)$ICC_adjusted)` of the variation in PTS.
 
@@
 ```{r icc-models-by-group}
-icc(m0_pts, by_group = TRUE)
-icc(m0_clphy, by_group = TRUE)
-icc(m0_clpriv, by_group = TRUE)
+performance::icc(m0_pts, by_group = TRUE)
+performance::icc(m0_lhr, by_group = TRUE)
 ```
@@
 modelsummary(list("Null model" = m1),
-             coef_omit = "sd__")
+             group = group + term ~ model,
+             coef_omit = "sd__", gof_map = gm)
 ```
@@
 modelsummary(list("Null model" = m1, "Within/between model" = m2),
-             coef_omit = "sd__")
+             group = group + term ~ model,
+             coef_omit = "sd__", gof_map = gm)
 ```
@@
 The predictive results are nearly identical to models without the split, and since we're more interested in prediction than in individual coefficient effects, we don't need to wait hours for the same results we'd get with the original non-demeaned values.
+
+## Interpretation reminders
+
+NB: We ultimately don't use this within/between difference since the random effects within/between models take forever to run and provide no improvement over the more basic models, but I'll keep this here as a reminder to future me in future projects:
+
+I always forget how to interpret these dang within/between coefficients in REWB models, so here's a reminder:
+
+- "Within" coefficients show what happens as you move up and down from the average level.
+  - Template = increasing 1 unit of `x` above the average in a typical country is associated with a β change in `y`
+- "Between" coefficients show what happens as you move the whole average up.
+They're trickier (and less important) to interpret.
+[This post](https://statisticalhorizons.com/between-within-contextual-effects) explains more, along with [Bell, Fairbrother, and Jones (2018)](https://doi.org/10.1007/s11135-018-0802-x).

### 2021-11-19 analysis/04_predictions.Rmd
Remove all civlib and clphy models

@@
              m_pts_entry_train, m_pts_funding_train,
-             m_clphy_baseline_train, m_clphy_v2csreprss_train, 
-             m_clphy_total_train, m_clphy_advocacy_train, 
-             m_clphy_entry_train, m_clphy_funding_train,
-             m_clpriv_baseline_train, m_clpriv_v2csreprss_train,
-             m_clpriv_total_train, m_clpriv_advocacy_train, 
-             m_clpriv_entry_train, m_clpriv_funding_train,
              m_lhr_baseline_train, m_lhr_v2csreprss_train,
@@
   scale_fill_manual(values = c("grey90", "#2ECC40")) +
-  guides(fill = FALSE) +
+  guides(fill = "none") +
   facet_wrap(vars(plot_level), ncol = 1, scales = "free_x") +
@@
 
-# E~1b~: NGO laws and physical violence
-
-```{r e1b-predictions, warning=FALSE}
-seed_clphy_prediction <- 7285  # From random.org
-
-set.seed(seed_clphy_prediction)
-pred_clphy_baseline <- predict(m_clphy_baseline_train, 
-                               newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
-                               allow_new_levels = TRUE)
-
-set.seed(seed_clphy_prediction)
-pred_clphy_total <- predict(m_clphy_total_train, 
-                            newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
-                            allow_new_levels = TRUE)
-
-set.seed(seed_clphy_prediction)
-pred_clphy_advocacy <- predict(m_clphy_advocacy_train, 
-                               newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
-                               allow_new_levels = TRUE)
-
-set.seed(seed_clphy_prediction)
-pred_clphy_entry <- predict(m_clphy_entry_train, 
-                            newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
-                            allow_new_levels = TRUE)
-
-set.seed(seed_clphy_prediction)
-pred_clphy_funding <- predict(m_clphy_funding_train, 
-                              newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
-                              allow_new_levels = TRUE)
-
-pred_clphy_baseline_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clphy_lead1) %>% 
-  bind_cols(as_tibble(pred_clphy_baseline)) %>% 
-  filter(!is.na(v2x_clphy_lead1))
-
-pred_clphy_total_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clphy_lead1) %>% 
-  bind_cols(as_tibble(pred_clphy_total)) %>% 
-  filter(!is.na(v2x_clphy_lead1))
-
-pred_clphy_advocacy_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clphy_lead1) %>% 
-  bind_cols(as_tibble(pred_clphy_advocacy)) %>% 
-  filter(!is.na(v2x_clphy_lead1))
-
-pred_clphy_entry_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clphy_lead1) %>% 
-  bind_cols(as_tibble(pred_clphy_entry)) %>% 
-  filter(!is.na(v2x_clphy_lead1))
-
-pred_clphy_funding_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clphy_lead1) %>% 
-  bind_cols(as_tibble(pred_clphy_funding)) %>% 
-  filter(!is.na(v2x_clphy_lead1))
-```
-
-## Improvement from baseline models
-
-```{r e1b-pred-plots, warning=FALSE}
-plot_baseline <- ggplot(pred_clphy_baseline_test, 
-                        aes(x = v2x_clphy_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Baseline",
-       x = "Actual physical violence index (t + 1)",
-       y = "Predicted physical violence index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_total <- ggplot(pred_clphy_total_test, 
-                     aes(x = v2x_clphy_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Total legal barriers",
-       x = "Actual physical violence index (t + 1)",
-       y = "Predicted physical violence index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_advocacy <- ggplot(pred_clphy_advocacy_test, 
-                        aes(x = v2x_clphy_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Barriers to advocacy",
-       x = "Actual physical violence index (t + 1)",
-       y = "Predicted physical violence index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_entry <- ggplot(pred_clphy_entry_test, 
-                     aes(x = v2x_clphy_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Barriers to entry",
-       x = "Actual physical violence index (t + 1)",
-       y = "Predicted physical violence index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_funding <- ggplot(pred_clphy_funding_test, 
-                       aes(x = v2x_clphy_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Barriers to funding",
-       x = "Actual physical violence index (t + 1)",
-       y = "Predicted physical violence index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-(plot_baseline | plot_total) / (plot_advocacy | plot_entry | plot_funding)
-```
-
-```{r e1b-metrics}
-lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
-
-bind_rows(lotsa_metrics(pred_clphy_baseline_test, 
-                        truth = v2x_clphy_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Baseline"),
-          lotsa_metrics(pred_clphy_total_test, 
-                        truth = v2x_clphy_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Total legal barriers"),
-          lotsa_metrics(pred_clphy_advocacy_test, 
-                        truth = v2x_clphy_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Barriers to advocacy"),
-          lotsa_metrics(pred_clphy_entry_test, 
-                        truth = v2x_clphy_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Barriers to entry"),
-          lotsa_metrics(pred_clphy_funding_test, 
-                        truth = v2x_clphy_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Barriers to funding")) %>% 
-  select(Model, .metric, .estimate) %>% 
-  pivot_wider(names_from = ".metric", values_from = ".estimate")
-```
-
-## Most improved countries
-
-### Total legal barriers
-
-```{r e1b-most-improved-total}
-most_improved_clphy_total <- bind_cols(
-  pred_clphy_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
-    select(country, gwcode, year, v2x_clphy_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clphy_total_test %>% 
-    mutate(error_total = Estimate - v2x_clphy_lead1) %>% 
-    select(estimate_total = Estimate, error_total)
-) %>% 
-  mutate(improved = error_total < 0 & abs(error_total) < abs(error_baseline)) %>% 
-  mutate(diff = error_total - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clphy_total)
-
-most_improved_clphy_total %>% 
-  select(Country = country, Year = year, 
-         `Actual physical violence index (t + 1)` = v2x_clphy_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_total,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-### Barriers to advocacy
-
-```{r e1b-most-improved-advocacy}
-most_improved_clphy_advocacy <- bind_cols(
-  pred_clphy_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
-    select(country, gwcode, year, v2x_clphy_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clphy_advocacy_test %>% 
-    mutate(error_advocacy = Estimate - v2x_clphy_lead1) %>% 
-    select(estimate_advocacy = Estimate, error_advocacy)
-) %>% 
-  mutate(improved = error_advocacy < 0 & abs(error_advocacy) < abs(error_baseline)) %>% 
-  mutate(diff = error_advocacy - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clphy_advocacy)
-
-most_improved_clphy_advocacy %>% 
-  select(Country = country, Year = year, 
-         `Actual physical violence index (t + 1)` = v2x_clphy_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_advocacy,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-### Barriers to entry
-
-```{r e1b-most-improved-entry}
-most_improved_clphy_entry <- bind_cols(
-  pred_clphy_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
-    select(country, gwcode, year, v2x_clphy_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clphy_entry_test %>% 
-    mutate(error_entry = Estimate - v2x_clphy_lead1) %>% 
-    select(estimate_entry = Estimate, error_entry)
-) %>% 
-  mutate(improved = error_entry < 0 & abs(error_entry) < abs(error_baseline)) %>% 
-  mutate(diff = error_entry - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clphy_entry)
-
-most_improved_clphy_entry %>% 
-  select(Country = country, Year = year, 
-         `Actual physical violence index (t + 1)` = v2x_clphy_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_entry,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-### Barriers to funding
-
-```{r e1b-most-improved-funding}
-most_improved_clphy_funding <- bind_cols(
-  pred_clphy_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
-    select(country, gwcode, year, v2x_clphy_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clphy_funding_test %>% 
-    mutate(error_funding = Estimate - v2x_clphy_lead1) %>% 
-    select(estimate_funding = Estimate, error_funding)
-) %>% 
-  mutate(improved = error_funding < 0 & abs(error_funding) < abs(error_baseline)) %>% 
-  mutate(diff = error_funding - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clphy_funding)
-
-most_improved_clphy_funding %>% 
-  select(Country = country, Year = year, 
-         `Actual physical violence index (t + 1)` = v2x_clphy_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_funding,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-\
-
-# E~1c~: NGO laws and civil liberties
-
-```{r e1c-predictions, warning=FALSE}
-seed_clpriv_prediction <- 6670  # From random.org
-
-set.seed(seed_clpriv_prediction)
-pred_clpriv_baseline <- predict(m_clpriv_baseline_train, 
-                                newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
-                                allow_new_levels = TRUE)
-
-set.seed(seed_clpriv_prediction)
-pred_clpriv_total <- predict(m_clpriv_total_train, 
-                             newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
-                             allow_new_levels = TRUE)
-
-set.seed(seed_clpriv_prediction)
-pred_clpriv_advocacy <- predict(m_clpriv_advocacy_train, 
-                                newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
-                                allow_new_levels = TRUE)
-
-set.seed(seed_clpriv_prediction)
-pred_clpriv_entry <- predict(m_clpriv_entry_train, 
-                             newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
-                             allow_new_levels = TRUE)
-
-set.seed(seed_clpriv_prediction)
-pred_clpriv_funding <- predict(m_clpriv_funding_train, 
-                               newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
-                               allow_new_levels = TRUE)
-
-pred_clpriv_baseline_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
-  bind_cols(as_tibble(pred_clpriv_baseline)) %>% 
-  filter(!is.na(v2x_clpriv_lead1))
-
-pred_clpriv_total_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
-  bind_cols(as_tibble(pred_clpriv_total)) %>% 
-  filter(!is.na(v2x_clpriv_lead1))
-
-pred_clpriv_advocacy_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
-  bind_cols(as_tibble(pred_clpriv_advocacy)) %>% 
-  filter(!is.na(v2x_clpriv_lead1))
-
-pred_clpriv_entry_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
-  bind_cols(as_tibble(pred_clpriv_entry)) %>% 
-  filter(!is.na(v2x_clpriv_lead1))
-
-pred_clpriv_funding_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
-  bind_cols(as_tibble(pred_clpriv_funding)) %>% 
-  filter(!is.na(v2x_clpriv_lead1))
-```
-
-## Improvement from baseline models
-
-```{r e1c-pred-plots, warning=FALSE}
-plot_baseline <- ggplot(pred_clpriv_baseline_test, 
-                        aes(x = v2x_clpriv_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Baseline",
-       x = "Actual private civil liberties index (t + 1)",
-       y = "Predicted private civil liberties index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_total <- ggplot(pred_clpriv_total_test, 
-                     aes(x = v2x_clpriv_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Total legal barriers",
-       x = "Actual private civil liberties index (t + 1)",
-       y = "Predicted private civil liberties index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_advocacy <- ggplot(pred_clpriv_advocacy_test, 
-                        aes(x = v2x_clpriv_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Barriers to advocacy",
-       x = "Actual private civil liberties index (t + 1)",
-       y = "Predicted private civil liberties index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_entry <- ggplot(pred_clpriv_entry_test, 
-                     aes(x = v2x_clpriv_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Barriers to entry",
-       x = "Actual private civil liberties index (t + 1)",
-       y = "Predicted private civil liberties index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_funding <- ggplot(pred_clpriv_funding_test, 
-                       aes(x = v2x_clpriv_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Barriers to funding",
-       x = "Actual private civil liberties index (t + 1)",
-       y = "Predicted private civil liberties index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-(plot_baseline | plot_total) / (plot_advocacy | plot_entry | plot_funding)
-```
-
-```{r e1c-metrics}
-lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
-
-bind_rows(lotsa_metrics(pred_clpriv_baseline_test, 
-                        truth = v2x_clpriv_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Baseline"),
-          lotsa_metrics(pred_clpriv_total_test, 
-                        truth = v2x_clpriv_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Total legal barriers"),
-          lotsa_metrics(pred_clpriv_advocacy_test, 
-                        truth = v2x_clpriv_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Barriers to advocacy"),
-          lotsa_metrics(pred_clpriv_entry_test, 
-                        truth = v2x_clpriv_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Barriers to entry"),
-          lotsa_metrics(pred_clpriv_funding_test, 
-                        truth = v2x_clpriv_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Barriers to funding")) %>% 
-  select(Model, .metric, .estimate) %>% 
-  pivot_wider(names_from = ".metric", values_from = ".estimate")
-```
-
-## Most improved countries
-
-### Total legal barriers
-
-```{r e1c-most-improved-total}
-most_improved_clpriv_total <- bind_cols(
-  pred_clpriv_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
-    select(country, gwcode, year, v2x_clpriv_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clpriv_total_test %>% 
-    mutate(error_total = Estimate - v2x_clpriv_lead1) %>% 
-    select(estimate_total = Estimate, error_total)
-) %>% 
-  mutate(improved = error_total < 0 & abs(error_total) < abs(error_baseline)) %>% 
-  mutate(diff = error_total - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clpriv_total)
-
-most_improved_clpriv_total %>% 
-  select(Country = country, Year = year, 
-         `Actual physical violence index (t + 1)` = v2x_clpriv_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_total,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-### Barriers to advocacy
-
-```{r e1c-most-improved-advocacy}
-most_improved_clpriv_advocacy <- bind_cols(
-  pred_clpriv_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
-    select(country, gwcode, year, v2x_clpriv_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clpriv_advocacy_test %>% 
-    mutate(error_advocacy = Estimate - v2x_clpriv_lead1) %>% 
-    select(estimate_advocacy = Estimate, error_advocacy)
-) %>% 
-  mutate(improved = error_advocacy < 0 & abs(error_advocacy) < abs(error_baseline)) %>% 
-  mutate(diff = error_advocacy - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clpriv_advocacy)
-
-most_improved_clpriv_advocacy %>% 
-  select(Country = country, Year = year, 
-         `Actual physical violence index (t + 1)` = v2x_clpriv_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_advocacy,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-### Barriers to entry
-
-```{r e1c-most-improved-entry}
-most_improved_clpriv_entry <- bind_cols(
-  pred_clpriv_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
-    select(country, gwcode, year, v2x_clpriv_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clpriv_entry_test %>% 
-    mutate(error_entry = Estimate - v2x_clpriv_lead1) %>% 
-    select(estimate_entry = Estimate, error_entry)
-) %>% 
-  mutate(improved = error_entry < 0 & abs(error_entry) < abs(error_baseline)) %>% 
-  mutate(diff = error_entry - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clpriv_entry)
-
-most_improved_clpriv_entry %>% 
-  select(Country = country, Year = year, 
-         `Actual physical violence index (t + 1)` = v2x_clpriv_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_entry,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-### Barriers to funding
-
-```{r e1c-most-improved-funding}
-most_improved_clpriv_funding <- bind_cols(
-  pred_clpriv_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
-    select(country, gwcode, year, v2x_clpriv_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clpriv_funding_test %>% 
-    mutate(error_funding = Estimate - v2x_clpriv_lead1) %>% 
-    select(estimate_funding = Estimate, error_funding)
-) %>% 
-  mutate(improved = error_funding < 0 & abs(error_funding) < abs(error_baseline)) %>% 
-  mutate(diff = error_funding - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clpriv_funding)
-
-most_improved_clpriv_funding %>% 
-  select(Country = country, Year = year, 
-         `Actual physical violence index (t + 1)` = v2x_clpriv_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_funding,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-\
-
-# E~1d~: NGO laws and latent human rights
+# E~1b~: NGO laws and latent human rights
 
@@
 
-# E~2b~: Civil society environment and physical violence
+# E~2b~: Civil society environment and latent human rights
 
 ```{r e2b-predictions, warning=FALSE}
-seed_clphy_prediction <- 7285  # From random.org
-
-set.seed(seed_clphy_prediction)
-pred_clphy_baseline <- predict(m_clphy_baseline_train, 
-                          newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
-                          allow_new_levels = TRUE)
-
-set.seed(seed_clphy_prediction)
-pred_clphy_v2csreprss <- predict(m_clphy_v2csreprss_train, 
-                 newdata = select(canary_testing_lagged, -v2x_clphy_lead1),
-                 allow_new_levels = TRUE)
-
-pred_clphy_baseline_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clphy_lead1) %>% 
-  bind_cols(as_tibble(pred_clphy_baseline)) %>% 
-  filter(!is.na(v2x_clphy_lead1))
-
-pred_clphy_v2csreprss_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clphy_lead1) %>% 
-  bind_cols(as_tibble(pred_clphy_v2csreprss)) %>% 
-  filter(!is.na(v2x_clphy_lead1))
-```
-
-## Improvement from baseline models
-
-```{r e2b-pred-plots, warning=FALSE}
-plot_baseline <- ggplot(pred_clphy_baseline_test, 
-                        aes(x = v2x_clphy_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Baseline",
-       x = "Actual physical violence index (t + 1)",
-       y = "Predicted physical violence index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_v2csreprss <- ggplot(pred_clphy_v2csreprss_test, 
-                          aes(x = v2x_clphy_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Added predictor",
-       x = "Actual physical violence index (t + 1)",
-       y = "Predicted physical violence index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_baseline | plot_v2csreprss
-```
-
-```{r e2b-metrics}
-lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
-
-bind_rows(lotsa_metrics(pred_clphy_baseline_test, 
-                        truth = v2x_clphy_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Baseline"),
-          lotsa_metrics(pred_clphy_v2csreprss_test, 
-                        truth = v2x_clphy_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Added predictor")) %>% 
-  select(Model, .metric, .estimate) %>% 
-  pivot_wider(names_from = ".metric", values_from = ".estimate")
-```
-
-## Most improved countries
-
-```{r e2b-most-improved}
-most_improved_clphy <- bind_cols(
-  pred_clphy_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clphy_lead1) %>% 
-    select(country, gwcode, year, v2x_clphy_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clphy_v2csreprss_test %>% 
-    mutate(error_v2csreprss = Estimate - v2x_clphy_lead1) %>% 
-    select(estimate_v2csreprss = Estimate, error_v2csreprss)
-) %>% 
-  # mutate(across(starts_with("error"), ~round(., 4))) %>% 
-  mutate(improved = error_v2csreprss < 0 & abs(error_v2csreprss) < abs(error_baseline)) %>% 
-  mutate(diff = error_v2csreprss - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clphy)
-
-most_improved_clphy %>% 
-  select(Country = country, Year = year, 
-         `Actual physical violence index (t + 1)` = v2x_clphy_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_v2csreprss,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-\
-
-# E~2c~: Civil society environment and civil liberties
-
-```{r e2c-predictions, warning=FALSE}
-seed_clpriv_prediction <- 6670  # From random.org
-
-set.seed(seed_clpriv_prediction)
-pred_clpriv_baseline <- predict(m_clpriv_baseline_train, 
-                                newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
-                                allow_new_levels = TRUE)
-
-set.seed(seed_clpriv_prediction)
-pred_clpriv_v2csreprss <- predict(m_clpriv_v2csreprss_train, 
-                                  newdata = select(canary_testing_lagged, -v2x_clpriv_lead1),
-                                  allow_new_levels = TRUE)
-
-pred_clpriv_baseline_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
-  bind_cols(as_tibble(pred_clpriv_baseline)) %>% 
-  filter(!is.na(v2x_clpriv_lead1))
-
-pred_clpriv_v2csreprss_test <- canary_testing_lagged %>% 
-  select(country, gwcode, year, v2x_clpriv_lead1) %>% 
-  bind_cols(as_tibble(pred_clpriv_v2csreprss)) %>% 
-  filter(!is.na(v2x_clpriv_lead1))
-```
-
-## Improvement from baseline models
-
-```{r e2c-pred-plots, warning=FALSE}
-plot_baseline <- ggplot(pred_clpriv_baseline_test, 
-                        aes(x = v2x_clpriv_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Baseline",
-       x = "Actual private civil liberties index (t + 1)",
-       y = "Predicted private civil liberties index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_v2csreprss <- ggplot(pred_clpriv_v2csreprss_test, 
-                          aes(x = v2x_clpriv_lead1, y = Estimate)) +
-  geom_abline(lty = 2) +
-  geom_point(alpha = 0.5) +
-  labs(title = "Added predictor",
-       x = "Actual private civil liberties index (t + 1)",
-       y = "Predicted private civil liberties index (t + 1)") +
-  coord_equal() +
-  theme_ngo()
-
-plot_baseline | plot_v2csreprss
-```
-
-```{r e2c-metrics}
-lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
-
-bind_rows(lotsa_metrics(pred_clpriv_baseline_test, 
-                        truth = v2x_clpriv_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Baseline"),
-          lotsa_metrics(pred_clpriv_v2csreprss_test, 
-                        truth = v2x_clpriv_lead1, 
-                        estimate = Estimate) %>% 
-            mutate(Model = "Added predictor")) %>% 
-  select(Model, .metric, .estimate) %>% 
-  pivot_wider(names_from = ".metric", values_from = ".estimate")
-```
-
-Hey! This one has a somewhat better change in MSE!
-
-```{r}
-percent_format(accuracy = 0.01)((0.0332 - 0.0339) / 0.0339)
-```
-
-## Most improved countries
-
-```{r e2c-most-improved}
-most_improved_clpriv <- bind_cols(
-  pred_clpriv_baseline_test %>% 
-    mutate(error_baseline = Estimate - v2x_clpriv_lead1) %>% 
-    select(country, gwcode, year, v2x_clpriv_lead1, 
-           estimate_baseline = Estimate, error_baseline),
-  pred_clpriv_v2csreprss_test %>% 
-    mutate(error_v2csreprss = Estimate - v2x_clpriv_lead1) %>% 
-    select(estimate_v2csreprss = Estimate, error_v2csreprss)
-) %>% 
-  # mutate(across(starts_with("error"), ~round(., 4))) %>% 
-  mutate(improved = error_v2csreprss < 0 & abs(error_v2csreprss) < abs(error_baseline)) %>% 
-  mutate(diff = error_v2csreprss - error_baseline) %>% 
-  mutate(abs_diff = abs(diff)) %>% 
-  filter(improved) %>% 
-  arrange(desc(abs_diff))
-
-nrow(most_improved_clpriv)
-
-most_improved_clpriv %>% 
-  select(Country = country, Year = year, 
-         `Actual private civil liberties index (t + 1)` = v2x_clpriv_lead1,
-         `Predicted (baseline)` = estimate_baseline,
-         `Predicted (CS repression)` = estimate_v2csreprss,
-         `|CS repression − baseline|` = abs_diff) %>% 
-  head(5) %>% 
-  kbl(digits = 3, align = "lccccc") %>% 
-  kable_styling()
-```
-
-\
-
-# E~2d~: Civil society environment and latent human rights
-
-```{r e2d-predictions, warning=FALSE}
 seed_lhr_prediction <- 3207  # From random.org
@@
 
-```{r e2d-pred-plots, warning=FALSE}
+```{r e2b-pred-plots, warning=FALSE}
 plot_baseline <- ggplot(pred_lhr_baseline_test, 
@@
 
-```{r e2d-metrics}
+```{r e2b-metrics}
 lotsa_metrics <- metric_set(rmse, rsq, mae, ccc)
@@
 
-```{r e2d-most-improved}
+```{r e2b-most-improved}
 most_improved_lhr <- bind_cols(

### 2021-11-19 analysis/index.Rmd
Add thing about PTS ceiling effect
Remove all civlib and clphy models

--- 2021-03-23 analysis/index.Rmd
@@
 ---
-title: "Canary in the Coal Mine: Anti-NGO Legislation as a Predictor of Civil Society Repression"
+title: "NGO Repression as a Predictor of Worsening Human Rights Abuses"
 author: "Suparna Chaudhry and Andrew Heiss"
@@
 
-Many countries across the globe are increasingly cracking down on civil society groups through legal restrictions.
-While research on democratic backsliding has tended to focus on rights and institutions in the electoral arena, this new wave of laws—many of which appear mundane on their face—represent a bureaucratic form of repression that could indicate more severe human rights abuses and backsliding.
-This is especially the case for electoral democracies, which unlike autocracies do not aggressively and openly attack civic space.
-Do legal crackdowns on NGOs predict broader civil society repression?
-We argue they do, given that anti-NGO laws are among the most subtle means of repression and attract the least domestic and international condemnation, as many audiences mistake this repression as regulation and are not personally affected by it.
-Using original data on civil society restrictions over the last three decades, we test whether NGO crackdown is a predictor of attacks on journalists, independent media, academic freedom, and freedoms of expression and association.
-This project has important implications: if crackdown on NGOs is indeed an early warning, it can potentially prevent further deteriorations in space for civil society.
+An increasing number of countries have recently cracked down on non-governmental organizations (NGOs).
+Much of this crackdown is sanctioned by law and represents a bureaucratic form of repression that could indicate more severe human rights abuses in the future.
+This is especially the case for democracies, which unlike autocracies, may not aggressively attack civic space.
+We explore if crackdowns on NGOs predict broader human rights repression.
+Anti-NGO laws are among the most subtle means of repression and attract lesser domestic and international condemnation compared to the use of violence.
+Using original data on NGO repression, we test whether NGO crackdown is a predictor of political terror, and violations of physical integrity rights and civil liberties.
+We find that while de jure anti-NGO laws provide little information in predicting future repression, their patterns of implementation—or de facto civil society repression—predicts worsening respect for physical integrity rights and civil liberties.

### 2021-11-19 manuscript/appendix.Rmd
Remove all civlib and clphy models

@@
   url: https://www.andrewheiss.com/
-date: "November 16, 2021"
+date: "November 19, 2021"
 # published: Under review
@@
 library(modelsummary)
+
+if (is_docx) {
+  library(huxtable)
+}
 

### 2021-11-19 manuscript/manuscript.Rmd
Remove all civlib and clphy models

@@
   url: https://www.andrewheiss.com/
-date: "November 15, 2021"
+date: "November 19, 2021"
 published: "Conditionally accepted at the *Journal of Human Rights*"
@@
 # keywords: civil society, NGOs, repression, human rights, political terror, civil liberties
-word-count: "8,007"
+word-count: "8,343"
 thanks: >-
@@
 
+if (is_docx) {
+  library(huxtable)
+}
+
 withr::with_dir(here::here(), {
@@
 
+  # Load general data
   canary <- tar_read(panel)
   tar_load(vdem_clean)
-  tar_load(civicus_map_data)
-  tar_load(civicus_clean)
-
-  tar_load(c(m_pts_total, m_pts_advocacy, m_pts_entry, m_pts_funding,
-             m_lhr_total, m_lhr_advocacy, m_lhr_entry, m_lhr_funding,
-             m_pts_v2csreprss, m_lhr_v2csreprss))
-
-  # Model tables
-  tar_load(c(models_paper_pts, models_paper_lhr))
-
-  # Load lookup list for coefficients in regression tables
-  tar_load(coef_list)
+
+  # Load Civicus stuff
+  tar_load(c(civicus_map_data, civicus_clean))
+
+  # Load models
+  tar_load(c(m_lhr_total, m_lhr_advocacy, m_lhr_v2csreprss))
 
   # Load marginal effects
-  tar_load(c(mfx_e1a_pts, mfx_e1d_lhr, mfx_e2a_pts, mfx_e2d_lhr))
+  tar_load(c(mfx_e1a_pts, mfx_e1b_lhr, mfx_e2a_pts, mfx_e2b_lhr))
 })
@@
 
-```{r civicus-map, fig.cap="2020 CIVICUS Monitor civic space ratings", fig.pos="h"}
+```{r civicus-map, fig.width=6.5, fig.height=3.1, fig.asp=NULL, fig.cap="2020 CIVICUS Monitor civic space ratings", fig.pos="h"}
 ggplot() +
@@
 
-Simply noting the passage of (or counting) these laws may therefore miss the effect of their de facto implementation.
+Simply counting these laws may therefore miss the effect of their de facto implementation.
 Some governments may even pass laws to create a chilling effect on these organizations.
@@
   guides(color = guide_legend(title = NULL)) +
-  labs(y = "Number of countries", x = NULL, caption = "(Higher PTS levels = more repression)") +
+  labs(y = "Number of countries", x = NULL, caption = "(Higher levels = more repression)") +
   theme_ngo() +
@@
   # Collapse 3-5 to just one level, since they're all tiny
-  mutate(effect2__ = fct_collapse(effect2__, "3+" = c("3", "4", "5"))) %>% 
+  mutate(effect2__ = fct_collapse(effect2__, "Level 3+" = 
+                                    c("Level 3", "Level 4", "Level 5"))) %>% 
   group_by(x_rounded, effect2__, plot_var_nice) %>% 
@@
   labs(x = "Count of legal barriers\n",
-       y = "Predicted probability of category",
+       y = "Predicted probability of level",
        color = "Predicted Political Terror Scale", fill = "Predicted Political Terror Scale",
@@
 ```{r plot-mfx-e1b, fig.width=7.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on latent human rights scoress"}
-out_mfx_e1b <- mfx_e1d_lhr %>% 
+out_mfx_e1b <- mfx_e1b_lhr %>% 
   mutate(x_rounded = floor(effect1__)) %>% 
@@
 out_mfx_e2a <- mfx_e2a_pts %>% 
-  mutate(effect2__ = fct_collapse(effect2__, "3+" = c("3", "4", "5"))) %>% 
+  mutate(effect2__ = fct_collapse(effect2__, "Level 3+" = 
+                                    c("Level 3", "Level 4", "Level 5"))) %>% 
   group_by(effect1__, effect2__, plot_var_nice) %>% 
@@
   labs(x = "Civil society repression",
-       y = "Predicted probability of category",
-       color = "Political Terror Scale", fill = "Political Terror Scale",
+       y = "Predicted probability of level",
+       color = NULL, fill = NULL,
        caption = "(x-axis reversed; greater repression on the right)") +
@@
 
-out_mfx_e2b <- mfx_e2d_lhr %>% 
+out_mfx_e2b <- mfx_e2b_lhr %>% 
   mutate(fake_facet_title = "Latent human rights values") %>% 
@@
   ~Prediction, ~Baseline, ~total, ~advocacy, ~entry, ~funding, ~repression,
-  "Wrong",     108,       108,    110,       108,    109,      111,
-  "Correct",   377,       377,    375,       377,    376,      374
+  "Wrong",     109,       107,    110,       108,    108,      111,
+  "Correct",   376,       378,    375,       377,    376,      374
 ) %>% 
@@
 # https://stats.andrewheiss.com/canary-ngos/04_predictions.html
+baseline_rmse <- 0.1862156
 tbl_rmse <- tribble(
-  ~`Latent human rights values`,  ~RMSE, ~`% change from baseline`,
-                  "Baseline", 0.1861944,                       "—",
-      "Total legal barriers", 0.1872427,                   "0.56%",
-      "Barriers to advocacy", 0.1871498,                   "0.51%",
-         "Barriers to entry", 0.1862244,                   "0.02%",
-       "Barriers to funding", 0.1879829,                   "0.96%",
-  "Civil society repression", 0.1856543,                  "-0.29%"
+  ~`Latent human rights values`, ~RMSE,
+                  "Baseline",    baseline_rmse,
+      "Total legal barriers",    0.1872181,
+      "Barriers to advocacy",    0.1872011,
+         "Barriers to entry",    0.1862635,
+       "Barriers to funding",    0.1879768,
+  "Civil society repression",    0.1857038
 ) %>% 
+  mutate(`% change from baseline` = (RMSE - baseline_rmse) / baseline_rmse,
+         `% change from baseline` = percent(`% change from baseline`, accuracy = 0.01)) %>% 
+  mutate(`% change from baseline` = recode(`% change from baseline`, "0.00%" = "—")) %>% 
   mutate(RMSE = round(RMSE, 4))
@@
 When looking at the overall latent human rights values in a country, including de jure and de facto repression does very little to improve predictive accuracy.
-As Table \@ref(tab:tbl-rmse) shows, accounting for de facto civil society repression only reduces the RMSE by 0.29% compared to the baseline, while accounting for de jure laws worsen the models' predictive power slightly.
+As Table \@ref(tab:tbl-rmse) shows, accounting for de facto civil society repression only reduces the RMSE by 0.27% compared to the baseline, while accounting for de jure laws worsen the models' predictive power slightly.
 While these gains in predictive power appear negligible, they are somewhat comparable with the findings of previous work.

### 2021-11-19 R/funs_data-cleaning.R

@@ -1,7 +1,14 @@
-# The PTS data and journalist data are saved as .RData files, so they load into
-# R with their original object names. This function lets you load an .RData file
-# directly to a new object instead of bringing in the original name.
-# (via https://stackoverflow.com/a/25455968/120898)
+library(scales)
+library(countrycode)
+library(readxl)
+library(haven)
+library(jsonlite)
+suppressPackageStartupMessages(library(sf))
+
+# The PTS data is saved as an .RData file, so it loads into R with its original
+# object name. This function lets you load an .RData file directly to a new
+# object instead of bringing in the original name. (via
+# https://stackoverflow.com/a/25455968/120898)
 load_rdata <- function(filename) {
   load(filename)
   get(ls()[ls() != "filename"])
@@ -9,6 +16,8 @@ load_rdata <- function(filename) {
 
 
 create_panel_skeleton <- function() {
+  library(states)
+
   microstates <- gwstates %>%
     filter(microstate) %>% distinct(gwcode)
 
@@ -189,43 +198,6 @@ load_clean_pts <- function(path, skeleton) {
 }
 
 
-load_clean_journalists <- function(path) {
-  gh_journalists_raw <- load_rdata(path) %>% as_tibble()
-
-  gh_journalists <- gh_journalists_raw %>%
-    select(year = Year, gwno, country = Country, in_rog, in_cpj, in_ipi, date = Date,
-           perpetrator = Perpetrator, foreigner = Foreigner, perp_cat = perp.cat, pts,
-           intra, inter, international, minor, major, armedconf)
-
-  # Count of perpetrators
-  killings_perp <- gh_journalists %>%
-    mutate(perp_cat = recode(perp_cat, "non-state" = "polgroup")) %>%
-    group_by(year, gwno, perp_cat) %>%
-    summarize(n = n()) %>%
-    pivot_wider(names_from = perp_cat, values_from = n)
-
-  # Count of foreign vs. local journalist
-  killings_foreigner <- gh_journalists %>%
-    mutate(foreigner = recode(foreigner, "no" = "local", "yes" = "foreign")) %>%
-    group_by(year, gwno, foreigner) %>%
-    summarize(n = n()) %>%
-    pivot_wider(names_from = foreigner, values_from = n)
-
-  # Combine everything
[…]

### 2021-11-19 R/models_clphy.R

@@ -1,187 +1,0 @@
-# Settings ----------------------------------------------------------------
-
-clphy_setup <- function() {
-  options(worker_options)
-
-  # Settings
-  CHAINS <- 4
-  ITER <- 2000
-  WARMUP <- 1000
-  BAYES_SEED <- 4045  # From random.org
-
-  # Priors
-  priors_vague <- c(set_prior("normal(0, 10)", class = "Intercept"),
-                    set_prior("normal(0, 3)", class = "b"),
-                    set_prior("cauchy(0, 1)", class = "sd"))
-
-  return(list(chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
-              priors_vague = priors_vague))
-}
-
-
-# Regular models ----------------------------------------------------------
-
-f_clphy_baseline <- function(dat) {
-  clphy_settings <- clphy_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clphy_lead1 ~ v2x_clphy +
-         v2x_polyarchy +
-         gdpcap_log +
-         un_trade_pct_gdp +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = clphy_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = clphy_settings$chains, iter = clphy_settings$iter,
-    warmup = clphy_settings$warmup, seed = clphy_settings$seed)
-
-  return(model)
-}
-
-f_clphy_total <- function(dat) {
-  clphy_settings <- clphy_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clphy_lead1 ~ barriers_total + barriers_total_lag1 +
-         v2x_clphy +
-         v2x_polyarchy +
-         gdpcap_log +
-         un_trade_pct_gdp +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = clphy_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = clphy_settings$chains, iter = clphy_settings$iter,
-    warmup = clphy_settings$warmup, seed = clphy_settings$seed)
-
-  return(model)
-}
-
-f_clphy_total_new <- function(dat) {
[…]

### 2021-11-19 R/models_clpriv.R

@@ -1,187 +1,0 @@
-# Settings ----------------------------------------------------------------
-
-clpriv_setup <- function() {
-  options(worker_options)
-
-  # Settings
-  CHAINS <- 4
-  ITER <- 2000
-  WARMUP <- 1000
-  BAYES_SEED <- 9324  # From random.org
-
-  # Priors
-  priors_vague <- c(set_prior("normal(0, 10)", class = "Intercept"),
-                    set_prior("normal(0, 3)", class = "b"),
-                    set_prior("cauchy(0, 1)", class = "sd"))
-
-  return(list(chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED,
-              priors_vague = priors_vague))
-}
-
-
-# Regular models ----------------------------------------------------------
-
-f_clpriv_baseline <- function(dat) {
-  clpriv_settings <- clpriv_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clpriv_lead1 ~ v2x_clpriv +
-         v2x_polyarchy +
-         gdpcap_log +
-         un_trade_pct_gdp +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = clpriv_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = clpriv_settings$chains, iter = clpriv_settings$iter,
-    warmup = clpriv_settings$warmup, seed = clpriv_settings$seed)
-
-  return(model)
-}
-
-f_clpriv_total <- function(dat) {
-  clpriv_settings <- clpriv_setup()
-
-  dat <- dat %>% filter(laws)
-
-  model <- brm(
-    bf(v2x_clpriv_lead1 ~ barriers_total + barriers_total_lag1 +
-         v2x_clpriv +
-         v2x_polyarchy +
-         gdpcap_log +
-         un_trade_pct_gdp +
-         armed_conflict +
-         (1 | gwcode)
-    ),
-    family = gaussian(),
-    prior = clpriv_settings$priors_vague,
-    control = list(adapt_delta = 0.9),
-    data = dat,
-    chains = clpriv_settings$chains, iter = clpriv_settings$iter,
-    warmup = clpriv_settings$warmup, seed = clpriv_settings$seed)
-
-  return(model)
-}
-
[…]

### 2021-11-19 R/models_details.R

@@ -10,24 +10,6 @@ create_model_df <- function() {
     "m_pts_funding", "Political terror", "Barriers to funding",
     "m_pts_v2csreprss", "Political terror", "Civil society repression",
 
-    # Models for physical violence (v2x_clphy)
-    "m_clphy_baseline", "Physical violence", "Baseline",
-    "m_clphy_total", "Physical violence", "Total legal barriers",
-    "m_clphy_total_new", "Physical violence", "New legal barriers",
-    "m_clphy_advocacy", "Physical violence", "Barriers to advocacy",
-    "m_clphy_entry", "Physical violence", "Barriers to entry",
-    "m_clphy_funding", "Physical violence", "Barriers to funding",
-    "m_clphy_v2csreprss", "Physical violence", "Civil society repression",
-
-    # Models for private civil liberties (v2x_clpriv)
-    "m_clpriv_baseline", "Private civil liberties", "Baseline",
-    "m_clpriv_total", "Private civil liberties", "Total legal barriers",
-    "m_clpriv_total_new", "Private civil liberties", "New legal barriers",
-    "m_clpriv_advocacy", "Private civil liberties", "Barriers to advocacy",
-    "m_clpriv_entry", "Private civil liberties", "Barriers to entry",
-    "m_clpriv_funding", "Private civil liberties", "Barriers to funding",
-    "m_clpriv_v2csreprss", "Private civil liberties", "Civil society repression",
-
     # Models for latent human rights (latent_hr_mean)
     "m_lhr_baseline", "Latent human rights", "Baseline",
     "m_lhr_total", "Latent human rights", "Total legal barriers",
@@ -45,21 +27,14 @@ create_model_df <- function() {
     "m_pts_funding_train", "Political terror", "Barriers to funding",
     "m_pts_v2csreprss_train", "Political terror", "Civil society repression",
 
-    ## Models for physical violence using training data
-    "m_clphy_baseline_train", "Physical violence", "Baseline",
-    "m_clphy_total_train", "Physical violence", "Total legal barriers",
-    "m_clphy_advocacy_train", "Physical violence", "Barriers to advocacy",
-    "m_clphy_entry_train", "Physical violence", "Barriers to entry",
-    "m_clphy_funding_train", "Physical violence", "Barriers to funding",
-    "m_clphy_v2csreprss_train", "Physical violence", "Civil society repression",
-
[…]

### 2021-11-19 _targets.R

@@ -53,15 +53,9 @@ set.seed(9936)  # From random.org
 
 future::plan(future::multisession)
 
-# haha this project was the first time I'd used {targets} and I wasn't *quite*
-# sure what this option did back then, so I shoved a billion packages in here
-# needlessly and we don't have time to go back and be more specific about which
-# targets need which packages, so we'll live with this mega list :shrug:
-tar_option_set(packages = c("tidyverse", "countrycode", "states", "WDI", "here", "fs",
-                            "readxl", "haven", "sf", "lubridate", "scales",
-                            "janitor", "kableExtra", "huxtable", "modelsummary",
-                            "knitr", "withr", "flextable", "testthat", "DT",
-                            "brms", "tidybayes", "broom", "cmdstanr", "jsonlite"))
+# Packages accessible to all targets
+tar_option_set(packages = c("tidyverse", "here", "fs", "withr"))
+
 
 # R functions ----
 
@@ -71,8 +65,6 @@ source("R/funs_notebook.R")
 source("R/models_details.R")
 source("R/models_analysis.R")
 source("R/models_pts.R")
-source("R/models_clphy.R")
-source("R/models_clpriv.R")
 source("R/models_lhr.R")
 
 # here::here() returns an absolute path, which then gets stored in tar_meta and
@@ -96,10 +88,6 @@ list(
   tar_target(latent_hr_raw_file,
              here_rel("data", "raw_data", "Latent Human Rights Protection Scores",
                       "HumanRightsProtectionScores_v4.01.csv"),
-             format = "file"),
-  tar_target(journalists_raw_file,
-             here_rel("data", "raw_data", "Gohdes Carey journalists",
-                  "journalist-data-incl-pts.RData"),
              format = "file"),
   tar_target(ucdp_raw_file,
              here_rel("data", "raw_data", "UCDP PRIO", "ucdp-prio-acd-191.csv"),
@@ -141,7 +129,6 @@ list(
   tar_target(chaudhry_clean, load_clean_chaudhry(chaudhry_raw_file)),
   tar_target(pts_clean, load_clean_pts(pts_raw_file, skeleton)),
   tar_target(latent_hr_clean, load_clean_latent_hr(latent_hr_raw_file, skeleton)),
[…]

### 2021-11-19 README.Rmd
Update abstract

@@
 Using original data on NGO repression, we test whether NGO crackdown is a predictor of political terror, and violations of physical integrity rights and civil liberties.
-We find that while formal de jure laws provide little information in predicting future repression, their patterns of implementation, or de facto civil society repression, predicts worsening respect for physical integrity rights and civil liberties.
+We find that while de jure anti-NGO laws provide little information in predicting future repression, their patterns of implementation—or de facto civil society repression—predicts worsening respect for physical integrity rights and civil liberties.
 

### 2021-11-19 README.Rmd
Better more stable project name

@@
 
+### `r emoji::emoji_glue(":warning::bird:")`: "Cautioning canary" project name
+
+Because project titles change all the time with revisions, rewriting, and peer review, we use "cautioning canary" as an internal-to-us project name that won't change.
+(We chose this name before the [**codename**](http://svmiller.com/codename/) was invented—had it existed already, we would have used that to generate the name.)
+
 ### Licenses

### 2021-11-19 manuscript/appendix.Rmd
Better more stable project name

@@
 # published: Under review
-code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/canary-ngos/>"
+code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/cautioning-canary/>"
 reference-section-title: References

### 2021-11-19 manuscript/manuscript.Rmd
Better more stable project name

@@
 published: "Conditionally accepted at the *Journal of Human Rights*"
-code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/canary-ngos/>"
+code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/cautioning-canary/>"
 abstract: >-
@@
 # These numbers come from the analysis notebook at 
-# https://stats.andrewheiss.com/canary-ngos/04_predictions.html#Prediction_diagnostics
+# https://stats.andrewheiss.com/cautioning-canary/04_predictions.html#Prediction_diagnostics
 pts_pred_table <- tribble(
@@
 # These numbers also come from the analysis notebook at 
-# https://stats.andrewheiss.com/canary-ngos/04_predictions.html
+# https://stats.andrewheiss.com/cautioning-canary/04_predictions.html
 baseline_rmse <- 0.1862156

### 2021-11-19 R/funs_knitting.R
Add a prefix to the word count so it displays nicely in targets output

@@ -211,5 +211,5 @@ count_words <- function(html) {
 }
 
 print.wordcount <- function(x) {
-  cat(scales::comma(x), "words in manuscript\n")
+  cat("*", scales::comma(x), "words in manuscript\n")
 }

### 2021-11-19 manuscript/appendix.Rmd
Final minor edits pre-submission

--- 2021-11-19 manuscript/appendix.Rmd
@@
 ---
-title: 'Appendix for "NGO Repression as a Predictor of Worsening Human Rights Abuses"'
-short-title: 'Appendix for "NGO Repression"'
+title: 'Online appendix for "NGO Repression as a Predictor of Worsening Human Rights Abuses"'
+short-title: 'Online appendix for "NGO Repression"'
 author:
@@
 # published: Under review
-code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/canary-ngos/>"
+code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/cautioning-canary/>"
 reference-section-title: References
 bibliography: bibliography.bib
-toc: false
 appendix: true
+toc: true
+title-page: false
 mainfont: Cochineal
@@
   fig.align = conditional_align, out.width = "100%",
-  fig.path = "output/figures/",
+  fig.path = "output/figures-appendix/",
   cache.path = "output/_cache/",
@@
 
+\memSingle
+
 # Modeling approach
 
-We use Stan [@stan] through R [@r-project] and brms [@brms-jss] to estimate our models.
+We use Stan [@stan] through R [@r-project] and **brms** [@brms-jss] to estimate our models.
 We generate 4 MCMC chains for each model with 2,000 iterations in each chain, 1,000 of which are used for warmup.
@@
 & \textbf{Priors} \\
-\mu_{\alpha_j} \sim&\ \mathcal{N}(0, 10) & \text{[country-specific intercepts]} \\
+\mu_{\alpha_j} \sim&\ \mathcal{N}(0, 3) & \text{[country-specific intercepts]} \\
 \beta_{1-7} \sim&\ \mathcal{N}(0, 3) & \text{[population effects]} \\
@@
   family = cumulative(),
-  prior = c(set_prior("normal(0, 10)", class = "Intercept"),
+  prior = c(set_prior("normal(0, 3)", class = "Intercept"),
             set_prior("normal(0, 3)", class = "b"),
@@
 \elandscape
-
-\memSingle

### 2021-11-19 manuscript/manuscript.Rmd
Final minor edits pre-submission

@@
 
-```{r plot-mfx-e1b, fig.width=7.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on latent human rights scoress"}
+```{r plot-mfx-e1b, fig.width=7.5, fig.height=4, fig.asp=NULL, fig.cap="Marginal effects of increasing anti-NGO legal barriers on latent human rights values"}
 out_mfx_e1b <- mfx_e1b_lhr %>% 
@@
   ~`Latent human rights values`, ~RMSE,
-                  "Baseline",    baseline_rmse,
+            "Baseline model",    baseline_rmse,
       "Total legal barriers",    0.1872181,

### 2021-11-19 _targets.R
Finally include data

@@ -143,9 +143,29 @@ list(
                                            un_pop, un_gdp)),
   # THIS is the final 2014-less data
   tar_target(panel, trim_data(panel_with_2014)),
+  tar_target(panel_csv, {
+    filename <- here_rel("data", "derived_data", "panel.csv")
+    readr::write_csv(panel, filename)
+    filename
+  }, format = "file"),
+  tar_target(panel_rds, {
+    filename <- here_rel("data", "derived_data", "panel.rds")
+    saveRDS(panel, filename)
+    filename
+  }, format = "file"),
 
   # Lagging/leading
   tar_target(panel_lagged, trim_data(lag_data(panel_with_2014))),
+  tar_target(panel_lagged_csv, {
+    filename <- here_rel("data", "derived_data", "panel_lagged.csv")
+    readr::write_csv(panel_lagged, filename)
+    filename
+  }, format = "file"),
+  tar_target(panel_lagged_rds, {
+    filename <- here_rel("data", "derived_data", "panel_lagged.rds")
+    saveRDS(panel_lagged, filename)
+    filename
+  }, format = "file"),
 
   # Training/testing
   tar_target(panel_training_lagged, create_training(panel_lagged)),

### 2021-11-19 README.Rmd
Update README with fancy instructions

@@
 
-# Abstract
+---
+
+[![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FMTR6X-blue)](https://dx.doi.org/10.17605/OSF.IO/MTR6X) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4058987.svg)](https://doi.org/10.5281/zenodo.4058987)
+
+> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.1177/0899764020971045) *Journal of Human Rights* (forthcoming).
+
+**All this project's materials are free and open:**
+
+- [Download the data](#data)
+- [See the analysis notebook website](https://stats.andrewheiss.com/cautioning-canary/)
+
+![Open data](img/data_large_color.png) &emsp; ![Open](img/materials_large_color.png)
+
+---
+
+## Abstract
 
@@
 
-This repository contains the data and code for our paper:
+This repository contains the data and code for our paper. Our pre-print is online here:
 
-> `r Authors`. (`r Year`). *`r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`.
+> `r Authors`. `r Year`. "`r Title`"". Accessed `r format(Sys.time(), '%B %e, %Y')`. Online at <https://dx.doi.org/10.17605/OSF.IO/MTR6X>
 
-Our pre-print is online here:
-
-> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
-
-## How to cite
-
-Please cite this compendium as:
-
-> `r Authors`. (`r format(Sys.Date(), "%Y")`). *Compendium of R code and data for `r Title`*. Accessed `r format(Sys.time(), '%B %e, %Y')`.
-
-### How to download or install
+## How to download and replicate
 
@@
 
-In order to reproduce this project, you'll need to install ASDF:
+We use the [**renv** package](https://rstudio.github.io/renv/articles/renv.html) to create a stable version-specific library of packages, and we use the [**targets** package](https://docs.ropensci.org/targets/) to manage all file dependencies and run the analysis.
+([See this for a short helpful walkthrough of **targets**.](https://books.ropensci.org/targets/walkthrough.html)).
 
-### `r emoji::emoji_glue(":warning::bird:")`: "Cautioning canary" project name
+To reproduce the findings and re-run the analysis, do the following:
+
+1. Download and install these fonts (if you’re using Windows, make sure you right click on the font files and choose “Install for all users” when installing these fonts):
+    - [Cochineal](https://fontesk.com/cochineal-typeface/)
+    - [Inter](https://fonts.google.com/specimen/Inter)
+    - [Linux Libertine O](https://www.cufonfonts.com/font/linux-libertine-o) (also [here](https://sourceforge.net/projects/linuxlibertine/))
+    - [Libertinus Math](https://github.com/alerque/libertinus)
+    - [InconsolataGo](https://github.com/ryanoasis/nerd-fonts/tree/master/patched-fonts/InconsolataGo)
+2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
+    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/), so that you have access to the Cairo graphics library
+    - If you’re using Windows, [install RTools too](https://cran.r-project.org/bin/windows/Rtools/) and add it to your PATH so that you can install packages from source if needed
+3. Open `cautioning-canary.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).
+4. Make sure you have a working installation of LaTeX:
+    - *Easy-and-recommended way*: Install the [**tinytex** package](https://yihui.org/tinytex/) by running `install.packages("tinytex")` in the R console, then running `tinytex::install_tinytex()`
+    - *Easy-but-requires-huge-4+-GB-download way*: Download TeX Live ([macOS](http://www.tug.org/mactex/); [Windows](https://miktex.org/))
+5.
+If it's not installed already, R *should* try to install the **renv** package when you open the RStudio Project for the first time.
+If you don't see a message about package installation, install it yourself by running `install.packages("renv")` in the R console.
+6. Run `renv::restore()` in the R console to install all the required packages for this project.
+7. Run `targets::tar_make()` in the R console to automatically download all data files, process the data, run the analysis, and compile the paper and appendix.
+
+Running `targets::tar_make()` will create several helpful outputs:
+
+1. All project data in `data/`
+2. An analysis notebook website in `analysis/_site/index.html`
+3. PDF, HTML, and Word versions of the manuscript in `manuscript/output/`
+
+## Data
+
+<div style="color:#FF4136">
+**NB**: If you're reproducing this project, it is best if you rely on the **targets** package and all the functions in `R/funs_data-cleaning.R` to handle the cleaning, processing, tidying, and merging.
+All the analysis in the project depends on having a **targets**-created object named `panel`.
+</div>
+
+For reference, though, we export CSV and RDS files of the final dataset:
+
+- [**`data/derived_data/panel.csv`**](data/derived_data/panel.csv) and [**`data/derived_data/panel.rds`**](data/derived_data/panel.rds): CSV and RDS versions of our final combined dataset
+- [**`data/derived_data/panel_lagged.csv`**](data/derived_data/panel_lagged.csv) and [**`data/derived_data/panel_lagged.rds`**](data/derived_data/panel_lagged.rds): CSV and RDS versions of our final combined dataset with lagged and leaded versions of variables
+
+This data is derived from many different original data sources.
+See the ["Process and merge data" page of our analysis notebook](https://stats.andrewheiss.com/cautioning-canary/01_data-overview.html) for details about both the original data and the merging process.
+
+- **Chaudhry NGO restrictions**: We use counts of anti-NGO legal barriers from [the replication data](https://doi.org/10.7910/DVN/JHOGNX) for Suparna Chaudhry's "The Assault on Civil Society: Explaining State Repression of NGOs" (*International Organization*, 2022).
+    - `data/raw_data/Chaudhry restrictions/SC_Expanded.dta`
+- **Political Terror Scores**: We use data from the [Political Terror Scale (PTS) project](http://www.politicalterrorscale.org/) to measure state repression.
+This project uses reports from the US State Department, Amnesty International, and Human Rights Watch and codes political repression on a scale of 1-5.
+    - `data/raw_data/Political Terror Scale/PTS-2019.RData`, v2019
+- **Latent Human Rights Protection Scores**: We use Chris Fariss's [Latent Human Rights Protection Scores](https://doi.org/10.7910/DVN/RQ85GK), which are estimates from fancy Bayesian models that capture a country's respect for physical integrity rights.
+    - `data/raw_data/Latent Human Rights Protection Scores/HumanRightsProtectionScores_v4.01.csv`, v4.01
+- **Varieties of Democracy data**: We use a bunch of variables from the [Varieties of Democracy (V-Dem) project](https://www.v-dem.net/en/).
+    - `data/raw_data/Country_Year_V-Dem_Full+others_R_v10/V-Dem-CY-Full+Others-v10.rds`, v10
+- **UN data**: We use [the **WDI** package](https://vincentarelbundock.github.io/WDI/) to collect data from the World Bank.
+However, we don't use WDI data for GDP and % of GDP from trade because the WDI data is incomplete (especially pre-1990, but that's not an issue in this project) To get around that, we create our own GDP and trade measures using data directly from the UN (at [UNData](https://data.un.org/)).
+They don't have a neat API like the World Bank, so you have to go to their website and export the data manually.
+We collect three variables:
+    - [GDP at constant 2015 prices](http://data.un.org/Data.aspx?q=gdp&d=SNAAMA&f=grID%3a102%3bcurrID%3aUSD%3bpcFlag%3a0) (`data/raw_data/UN data/UNdata_Export_20210118_034054729.csv`)
+    - [GDP at current prices](http://data.un.org/Data.aspx?q=gdp&d=SNAAMA&f=grID%3a101%3bcurrID%3aUSD%3bpcFlag%3a0) (`data/raw_data/UN data/UNdata_Export_20210118_034311252.csv`)
+    - [Population](https://population.un.org/wpp/Download/Standard/Population/) (`data/raw_data/UN data/WPP2019_POP_F01_1_TOTAL_POPULATION_BOTH_SEXES.xlsx`)
+- **UCDP/PRIO Armed Conflict Data**: We use [UCDP/PRIO Armed Conflict data](https://ucdp.uu.se/downloads/index.html#armedconflict) to create an indicator marking if a country-year was involved in armed conflict that resulted in at least 25 battle-related deaths.
+    - `data/raw_data/UCDP PRIO/ucdp-prio-acd-191.csv`, v19.1
+- **Natural Earth shapefiles**: We use the ["Admin 0 - Countries" 1:110m cultural shapefiles](https://www.naturalearthdata.com/downloads/110m-cultural-vectors/) for maps.
+    - `data/raw_data/ne_110m_admin_0_countries/`
+- **2020 Civicus Monitor ratings**: CIVICUS rates countries [using a 5-item scale of civic space openness](https://monitor.civicus.org/widgets/world/), but getting their data in a machine-readable format is a little tricky.
+We downloaded [the standalone embeddable widget](https://monitor.civicus.org/widgets/world/) as an HTML file with `wget https://monitor.civicus.org/widgets/world/` and saved it as `index_2021-03-19.html`.
+We then extracted the `COUNTRIES_DATA` variable embedded in a `<script>` tag (`xpath = /html/body/script[5]`), which is JSON-ish, but not quite.
+The **jsonlite** R package couldn't parse it for whatever reason, but some random online JSON formatter and validator could, so we ran it through that and saved the resulting clean file.
+    - `data/raw_data/Civicus/index_2021-03-19.html`
+    - `data/raw_data/Civicus/civicus_2021-03-19.json`
+
+**BUT AGAIN** we *highly* recommend just relying on the **targets** pipeline to construct this data rather than doing it all yourself!
+([See this for a short helpful walkthrough.](https://books.ropensci.org/targets/walkthrough.html))
+
+## `r emoji::emoji_glue(":warning::bird:")`: "Cautioning canary" project name
 
@@
 
-### Licenses
+## Licenses
 
@@
 
-### Contributions
+## Contributions
 

### 2021-11-19 README.Rmd
Add Zenodo DOI

@@
 
-[![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FMTR6X-blue)](https://dx.doi.org/10.17605/OSF.IO/MTR6X) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4058987.svg)](https://doi.org/10.5281/zenodo.4058987)
+[![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FMTR6X-blue)](https://dx.doi.org/10.17605/OSF.IO/MTR6X) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5715402.svg)](https://doi.org/10.5281/zenodo.5715402)
 

### 2021-11-19 R/funs_notebook.R
Include site building as a target

@@ -84,3 +84,7 @@ tar_notebook_pages <- function(
     )
   )
 }
+
+copy_notebook_supporting_files <- function(rmd, ...) {
+  rmarkdown::render_site(rmd, encoding = "UTF-8")
+}

### 2021-11-19 _targets.R

@@ -270,6 +270,16 @@ list(
   ## Render the analysis notebook ----
   tar_notebook_pages(),
 
+  # This is only here to trigger a re-build of the R Markdown website's
+  # supporting files in `_site`, which copies the files in `output` to
+  # `_site/output`. I unfortunately haven't found a way to make it so that the
+  # site building occurs independently of `rmarkdown::render()`, so this is the
+  # workaround: re-knit index.Rmd
+  tar_target(supporting_files,
+             copy_notebook_supporting_files(here_rel("analysis", "index.Rmd"),
+                                            main_manuscript, html,
+                                            appendix, app_html)),
+
   ## Render the manuscript into a bunch of different outputs ----
 
   # tarchetypes::tar_render() automatically detects target dependencies in Rmd

### 2022-01-05 manuscript/manuscript.Rmd
Add "forthcoming"

@@
 date: "November 19, 2021"
-published: "Conditionally accepted at the *Journal of Human Rights*"
+published: "Forthcoming at the *Journal of Human Rights*"
 code-repo: "Access the code and full analysis notebook at <https://stats.andrewheiss.com/cautioning-canary/>"
